Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/us}{U.S.}\textbar{}Jacob Blake, Rare Survivor at Center
of Police Protests, Starts Telling His Own Story

\url{https://nyti.ms/3h7reQL}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{race-and-america}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/george-floyd-protests-minneapolis-new-york-los-angeles?name=styln-george-floyd\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Article\&impression_id=cbd261b0-f52c-11ea-a089-112dddf69edf\&variant=undefined}{Race
and America}}{Race and America}}\label{race-and-america}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/11/us/black-police-chiefs-reform.html?name=styln-george-floyd\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Article\&impression_id=cbd288c0-f52c-11ea-a089-112dddf69edf\&variant=undefined}{Black
  Police Chiefs}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/04/nyregion/rochester-police-daniel-prude.html?name=styln-george-floyd\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Article\&impression_id=cbd2afd0-f52c-11ea-a089-112dddf69edf\&variant=undefined}{What
  Happened in Rochester, N.Y.}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/08/30/us/portland-shooting-explained.html?name=styln-george-floyd\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Article\&impression_id=cbd2d6e0-f52c-11ea-a089-112dddf69edf\&variant=undefined}{Portland
  Shooting}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/08/30/us/breonna-taylor-police-killing.html?name=styln-george-floyd\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Article\&impression_id=cbd2d6e1-f52c-11ea-a089-112dddf69edf\&variant=undefined}{Breonna
  Taylor's Life and Death}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{jacob-blake-rare-survivor-at-center-of-police-protests-starts-telling-his-own-story}{%
\section{Jacob Blake, Rare Survivor at Center of Police Protests, Starts
Telling His Own
Story}\label{jacob-blake-rare-survivor-at-center-of-police-protests-starts-telling-his-own-story}}

In a video recorded from his hospital bed, Mr. Blake, who was shot by
the police, says, ``It hurts to breathe; it hurts to sleep.''

By
\href{https://www.nytimes3xbfgragh.onion/by/nicholas-bogel-burroughs}{Nicholas
Bogel-Burroughs}

\begin{itemize}
\item
  Published Sept. 7, 2020Updated Sept. 10, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

\emph{{[}Here's what we know about the}
\href{https://www.nytimes3xbfgragh.onion/article/jacob-blake-shooting-kenosha.html}{\emph{Jacob
Blake shooting in Kenosha, Wisconsin}}\emph{.{]}}

KENOSHA, Wis. ---~Demonstrations against police violence have been
filled with the chants of victims' names: George Floyd, Breonna Taylor,
Tamir Rice, Eric Garner. In recent days, a new name --- Jacob Blake ---
has been called out in protests across the country.

In that list, though, Mr. Blake, a Black man who was repeatedly shot in
the back by a white police officer in Kenosha, Wis., is also set apart.
Unlike so many of the people who have become grim symbols for a
movement, Mr. Blake survived and has begun to tell his own story.

``Your life --- and not only just your life, your legs, something that
you need to move around and move forward in life --- could be taken from
you like this, man,'' Mr. Blake says from his hospital bed, snapping his
fingers for emphasis, in a video released over the weekend. In the
video, he speaks publicly for the first time about what happened to him.
His injuries are severe, and his family says he was paralyzed from the
waist down in the
\href{https://www.nytimes3xbfgragh.onion/2020/09/08/us/salt-lake-city-autism-shooting.html}{shooting}
last month.

\begin{quote}
Words from brother who can't be silent Mr Jacob Blake
\href{https://t.co/cc6pEdlvRQ}{pic.twitter.com/cc6pEdlvRQ}

--- Our Lives Matter! (@GHOGM)
\href{https://twitter.com/GHOGM/status/1302314554278412288?ref_src=twsrc\%5Etfw}{September
5, 2020}
\end{quote}

In the video, which was recorded by an activist from New York who
distributed it on social media, Mr. Blake describes his injuries, which
he says left him with staples in his back and stomach.

``Every 24 hours, it's pain --- it's nothing but pain,'' Mr. Blake says.
``It hurts to breathe; it hurts to sleep. It hurts to move from side to
side. It hurts to eat.''

Shermaine Laster, the activist, said he had showed up unannounced at the
Milwaukee hospital where Mr. Blake is being treated and was meeting Mr.
Blake for the first time.

For demonstrators seeking broad changes to American policing, the
prospect of Mr. Blake's presenting the public with a personal voice to
his experience was encouraging.

``My son is gone,'' said Monique West, whose 18-year-old son, Ty'Rese
West, was
\href{https://journaltimes.com/news/local/i-miss-my-babys-smile-hear-what-tyrese-wests-mom-has-to-say-about-her/article_83ec91ab-1aae-57e4-8554-1858de35b5ba.html}{shot
and killed in 2019 by a police officer} in Racine County, not far from
Kenosha. ``He's not here to tell nothing. There's only two stories ---
either the officer or the person that's gone.''

A Kenosha officer,
\href{https://www.nytimes3xbfgragh.onion/2020/08/27/us/kenosha-police-officer-rusten-sheskey.html}{Rusten
Sheskey}, fired seven times on Aug. 23 at Mr. Blake, who was trying to
get into a car. The shooting was captured by a neighbor on a disturbing
video that quickly drew outrage on social media. It set off sometimes
destructive demonstrations in Kenosha and quickly became a topic in the
presidential race, drawing visits
\href{https://www.nytimes3xbfgragh.onion/2020/09/01/us/politics/trump-conspiracy-theory-thugs-plane.html}{from
President Trump} and
\href{https://www.nytimes3xbfgragh.onion/2020/09/03/us/politics/joe-biden-kenosha.html}{Joseph
R. Biden Jr}.

Cortez Rice, a nephew of George Floyd, the man who was
\href{https://www.nytimes3xbfgragh.onion/2020/05/31/us/george-floyd-investigation.html}{killed
by the police in Minneapolis} in May, said Mr. Blake's own words about
what had happened to him would hold a unique value. ``Jacob's got the
chance --- he's going to get to speak,'' Mr. Rice said.

Gregory Bennett Jr. organized a community event on Sunday in Kenosha at
which state lawmakers heard demands from residents for change. A seat
was left empty for Mr. Blake at the event --- a reminder, organizers
said, that he might yet be a voice for needed reform. Without such
survivors, Mr. Bennett said, the stories are often muted.

``It would have been swept under the rug,'' Mr. Bennett said. ``There's
people whose family members have been shot and killed here in this city,
and guess what? You never see a news camera or nothing.''

To be sure, others who became symbols of abuse at the hands of the
police have survived to tell their stories. Rodney King, who
\href{https://www.nytimes3xbfgragh.onion/2020/06/03/us/rodney-king-george-floyd-los-angeles.html}{was
beaten by Los Angeles police officers} in 1991, and Abner Louima, who
was tortured by New York police officers
\href{https://www.nytimes3xbfgragh.onion/1999/05/26/nyregion/louima-case-overview-officer-seeking-some-mercy-admits-louima-s-torture.html}{in
1997}, both lived to describe what had been done to them. Mr. King, who
\href{https://www.nytimes3xbfgragh.onion/2012/06/18/us/rodney-king-whose-beating-led-to-la-riots-dead-at-47.html}{died
in 2012}, and Mr. Louima, who
\href{https://www.nytimes3xbfgragh.onion/2002/06/23/magazine/no-way-out.html}{started
a real estate business} in Florida,
\href{https://www.nytimes3xbfgragh.onion/2004/09/19/us/12-years-after-the-riots-rodney-king-gets-along.html}{largely
tried to move on}.

Of people shot at by officers from the nation's 50 largest police
departments between 2010 and 2016, about two-thirds survived, according
to \href{https://news.vice.com/en_us/article/xwvv3a/shot-by-cops}{data
obtained by Vice News}.

``There's an invisibility to it,'' Frank Edwards, an assistant professor
of criminal justice at Rutgers, said of people who survive police
shootings, adding that many of those survivors are charged with crimes
and rarely draw public attention or speak publicly about their cases.
``They fear retribution if they do speak,'' he said.

What role Mr. Blake will choose to play in demonstrations remains to be
seen. He still faces significant medical challenges, and one of his
lawyers has said that his walking again would be a ``miracle.'' Mr.
Blake also is contending with legal charges.

By videoconference from his hospital bed, Mr. Blake pleaded not guilty
on Friday to three domestic charges against him, including a sexual
assault count. The charges were filed in July. On the day Mr. Blake was
shot, the woman who reported the assault called 911, saying that Mr.
Blake was at her home. The Kenosha police said they were trying to
arrest Mr. Blake when the shooting occurred.

The trial in that case has been scheduled for November, although it
could be delayed.

Ben Crump, a civil rights lawyer who is representing Mr. Blake and has
represented families of many Black people killed by the police, said Mr.
Blake was still coming to terms with the public attention to what had
happened to him and what that might mean in the months ahead.

``He hasn't been able to fully grasp what a symbol he has become,'' Mr.
Crump said, adding that Mr. Blake was mostly focused on making sure that
his young children --- three of whom witnessed the shooting --- are not
traumatized and that they understand that he will emerge from this.

``The way he's trying to be a strong Black father for his children is
the way that he's taking on the mission of this movement,'' Mr. Crump
said.

Porche Bennett, an organizer with Black Lives Activists Kenosha, or
BLAK, said on Sunday that there would be no pressure on Mr. Blake to
publicly take up their cause or to become an outspoken advocate for the
movement.

``We know we've got his support,'' she said.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
