 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{/section/politics}{Politics} \textbar{}Trump Impeachment Results:
How Democrats and Republicans Voted

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2ShCZtA}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-politics-}{%
\subsection{\texorpdfstring{ \href{/section/politics}{Politics}
}{ Politics }}\label{-politics-}}

\hypertarget{trump-impeachment-results-how-democrats-and-republicans-voted}{%
\section{Trump Impeachment Results: How Democrats and Republicans
Voted}\label{trump-impeachment-results-how-democrats-and-republicans-voted}}

FEB. 5, 2020

Article I: Abuse of Power

If all 100 Senators are present, 67 votes are needed to convict.

Vote expected later

Total

Dem.Democrats

Rep.Republicans

Guilty

48

47

1

67 votes needed to convict

Not Guilty

52

0

52

Article II: Obstruction of Congress

Vote expected later

Total

Dem.Democrats

Rep.Republicans

Guilty

47

47

0

67 votes needed to convict

Not Guilty

53

0

53

The deeply divided Senate on Wednesday acquitted President Donald J.
Trump on the two articles of impeachment --- abuse of power and
obstruction of Congress --- brought by the House. See how every senator
voted below.

The votes fell far short of the two-thirds majority required to convict
and remove the president from office. The Senate rejected the abuse of
power charge 52 to 48, largely along party lines. Senators then voted 53
to 47 to defeat the second article charging Mr. Trump with obstruction
of Congress.

One Republican, Senator Mitt Romney of Utah,
\href{https://www.nytimes3xbfgragh.onion/2020/02/05/us/politics/trump-acquitted-impeachment.html}{broke
with his party} and voted in favor of the first article of impeachment,
supporting the effort to remove the president.

Motion to Consider Witnesses or Documents

Vote failed on Friday.

More than 50 votes

would ensure passage

Dem.

Rep.

Total

Yes

47

2

49

No

0

51

51

Motion to Consider Witnesses or Documents

Vote failed on Friday.

More than 50 votes

would ensure passage

Dem.

Rep.

Total

Yes

47

2

49

No

0

51

51

Motion to Consider

Witnesses or Documents

Vote failed on Friday.

More than 50 votes

would ensure passage

Dem.

Rep.

Total

Yes

47

2

49

No

0

51

51

On Friday, Senate Republicans succeeded in blocking a motion to consider
additional witnesses and documents in the trial, including testimony
from John R. Bolton, the president's former national security adviser.

The crucial vote was cast largely along party lines and paved the way
for Mr. Trump's acquittal in the third presidential impeachment trial in
the nation's history.

\emph{For the latest updates,}
\href{https://www.nytimes3xbfgragh.onion/2020/02/05/us/politics/impeachment-vote.html}{follow
our live coverage of the impeachment trial}\emph{.}

\hypertarget{how-every-senator-voted}{%
\subsection{How Every Senator Voted}\label{how-every-senator-voted}}

For the votes on the articles of impeachment, ``guilty'' votes are
recorded as ``Y'' and ``not guilty'' votes are recorded as ``N.''

Democrats

 \#1 Article I

 \#2 Article II

 \#3 Witnesses

Tammy Baldwin Wis.

Y

Y

Y

Michael Bennet Colo.

Y

Y

Y

Richard Blumenthal Conn.

Y

Y

Y

Cory Booker N.J.

Y

Y

Y

Sherrod Brown Ohio

Y

Y

Y

Maria Cantwell Wash.

Y

Y

Y

Benjamin L. Cardin Md.

Y

Y

Y

Thomas R. Carper Del.

Y

Y

Y

Bob Casey Pa.

Y

Y

Y

Chris Coons Del.

Y

Y

Y

Catherine Cortez Masto Nev.

Y

Y

Y

Tammy Duckworth Ill.

Y

Y

Y

Richard J. Durbin Ill.

Y

Y

Y

Dianne Feinstein Calif.

Y

Y

Y

Kirsten Gillibrand N.Y.

Y

Y

Y

Kamala Harris Calif.

Y

Y

Y

Maggie Hassan N.H.

Y

Y

Y

Martin Heinrich N.M.

Y

Y

Y

Mazie K. Hirono Hawaii

Y

Y

Y

Doug Jones Ala.

Y

Y

Y

Tim Kaine Va.

Y

Y

Y

Amy Klobuchar Minn.

Y

Y

Y

Patrick J. Leahy Vt.

Y

Y

Y

Joe Manchin III W.Va.

Y

Y

Y

Edward J. Markey Mass.

Y

Y

Y

Robert Menendez N.J.

Y

Y

Y

Jeff Merkley Ore.

Y

Y

Y

Christopher S. Murphy Conn.

Y

Y

Y

Patty Murray Wash.

Y

Y

Y

Gary Peters Mich.

Y

Y

Y

Jack Reed R.I.

Y

Y

Y

Jacky Rosen Nev.

Y

Y

Y

Brian Schatz Hawaii

Y

Y

Y

Chuck Schumer N.Y.

Y

Y

Y

Jeanne Shaheen N.H.

Y

Y

Y

Kyrsten Sinema Ariz.

Y

Y

Y

Tina Smith Minn.

Y

Y

Y

Debbie Stabenow Mich.

Y

Y

Y

Jon Tester Mont.

Y

Y

Y

Tom Udall N.M.

Y

Y

Y

Chris Van Hollen Md.

Y

Y

Y

Mark Warner Va.

Y

Y

Y

Elizabeth Warren Mass.

Y

Y

Y

Sheldon Whitehouse R.I.

Y

Y

Y

Ron Wyden Ore.

Y

Y

Y

Angus King Me.

Y

Y

Y

Bernie Sanders Vt.

Y

Y

Y

Republicans

 \#1 Article I

 \#2 Article II

 \#3 Witnesses

Mitt Romney Utah

Y

N

Y

Susan Collins Me.

N

N

Y

Lamar Alexander Tenn.

N

N

N

John Barrasso Wyo.

N

N

N

Marsha Blackburn Tenn.

N

N

N

Roy Blunt Mo.

N

N

N

John Boozman Ark.

N

N

N

Mike Braun Ind.

N

N

N

Richard M. Burr N.C.

N

N

N

Shelley Moore Capito W.Va.

N

N

N

Bill Cassidy La.

N

N

N

John Cornyn Tex.

N

N

N

Tom Cotton Ark.

N

N

N

Kevin Cramer N.D.

N

N

N

Michael D. Crapo Idaho

N

N

N

Ted Cruz Tex.

N

N

N

Steve Daines Mont.

N

N

N

Michael B. Enzi Wyo.

N

N

N

Joni Ernst Iowa

N

N

N

Deb Fischer Neb.

N

N

N

Cory Gardner Colo.

N

N

N

Lindsey Graham S.C.

N

N

N

Charles E. Grassley Iowa

N

N

N

Josh Hawley Mo.

N

N

N

John Hoeven N.D.

N

N

N

Cindy Hyde-Smith Miss.

N

N

N

James M. Inhofe Okla.

N

N

N

Ron Johnson Wis.

N

N

N

John Kennedy La.

N

N

N

James Lankford Okla.

N

N

N

Mike Lee Utah

N

N

N

Kelly Loeffler Ga.

N

N

N

Mitch McConnell Ky.

N

N

N

Martha E. McSally Ariz.

N

N

N

Jerry Moran Kan.

N

N

N

Lisa Murkowski Alaska

N

N

N

Rand Paul Ky.

N

N

N

David Perdue Ga.

N

N

N

Rob Portman Ohio

N

N

N

Jim Risch Idaho

N

N

N

Pat Roberts Kan.

N

N

N

Michael Rounds S.D.

N

N

N

Marco Rubio Fla.

N

N

N

Ben Sasse Neb.

N

N

N

Rick Scott Fla.

N

N

N

Tim Scott S.C.

N

N

N

Richard C. Shelby Ala.

N

N

N

Dan Sullivan Alaska

N

N

N

John Thune S.D.

N

N

N

Thom Tillis N.C.

N

N

N

Patrick J. Toomey Pa.

N

N

N

Roger Wicker Miss.

N

N

N

Todd Young Ind.

N

N

N

Note: Democratic totals include two independents who caucus with the
Democrats.

\textbf{Correction: Feb. 5, 2020}

An earlier version of this article incorrectly named the state that
Senator Mitt Romney represents. It is Utah, not Massachusetts, where he
served as governor.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
