Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

Jackie O.'s Bag of Choice, Rebranded in Her Name

\url{https://nyti.ms/3hCORBH}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

First of Its Kind, Last of Its Kind

\hypertarget{jackie-os-bag-of-choice-rebranded-in-her-name}{%
\section{Jackie O.'s Bag of Choice, Rebranded in Her
Name}\label{jackie-os-bag-of-choice-rebranded-in-her-name}}

The former first lady owned several versions of the Gucci saddlebag, to
which Alessandro Michele has added a few new touches.

By \href{https://www.nytimes3xbfgragh.onion/by/lindsay-talbot}{Lindsay
Talbot}

\begin{itemize}
\item
  Aug. 28, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Image

Jacqueline Kennedy Onassis with the original Gucci saddlebag in New York
in 1970.Credit...Fairchild Archive/Penske Media/Shutterstock

Image

The latest edition, in pastel pink leather. \$1,990,
\href{https://www.gucci.com/us/en/}{gucci.com}.Credit...Anthony
Cotsifas. Styled by Marci Leiseth

IT'S A FAMILIAR picture: a post-Camelot Jacqueline Kennedy Onassis, with
her windswept coif, giant tortoiseshell glasses and that classic
saddlebag perpetually swung over one arm. The story goes that the former
first lady used Gucci's slouchy leather tote, originally named the
G1244, to shield herself from the paparazzi. In the '70s and '80s, she
was photographed carrying the bag so often --- arriving at her Manhattan
apartment, whizzing through Heathrow Airport --- that the Italian
fashion house at some point began internally referring to it as ``the
Jackie.''

With its rounded trapezoidal base, short buckled strap and piston-shaped
closure, the soft, crescent-shaped accessory debuted in 1961 in canvas
and brown boar skin, 40 years after Guccio Gucci opened his first
luggage and saddlery shop in Florence. Since its inception, the shoulder
bag has reappeared in chamois, vermilion-and-red grosgrain stripe, white
calfskin and diamond-patterned cloth --- Kennedy Onassis owned several
versions, including one in natural canvas, which she wore while walking
barefoot on Capri.

The company's series of half-moon hobo-style totes, to which the G1244
belonged, was once also a favorite of men. Peter Sellers carried one in
the '70s, and so did Samuel Beckett, on holiday on the Ligurian coast in
1971. This year, the brand has officially renamed the G1244 the
\href{https://www.gucci.com/us/en/st/capsule/jackie-1961}{Jackie 1961},
which made its debut at the Gucci men's fall 2020 show in Milan. Using a
vintage Jackie from his personal archive for inspiration, creative
director
\href{https://www.nytimes3xbfgragh.onion/2018/10/15/t-magazine/alessandro-michele-gucci-interview.html}{Alessandro
Michele} scaled down its silhouette and rendered the piston lock in
gold. For women, he reimagined it in miniature, in shades of pastel
pink, butter, lavender and blue patent leathers. On the runway, models
who carried the very small saddlebag were outfitted with elbow-length
opera gloves in matching candy-colored hues --- most certainly a nod to
another of the first lady's signatures, as well as to the timeless
nature of not fashion, but style.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
