Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

Poem: Bad Sons Anonymous

\url{https://nyti.ms/2X94JEC}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{poem-bad-sons-anonymous}{%
\section{Poem: Bad Sons Anonymous}\label{poem-bad-sons-anonymous}}

By Virgil Suárez

Selected by Naomi Shihab Nye

\begin{itemize}
\item
  April 2, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

We were all sons and daughters who ostensibly learned simple ethical
codes: Thou shalt not tell a lie. Thou shalt not beat your child. What
mirrors, then, held up to whom? In his captivating new book, ``The
Painted Bunting's Last Molt,'' Virgil Suárez examines the mixed brew of
childhood memory, exile, ornithology, contrasts and conflicts that build
a life. His eye remains tuned to details, turning them over like shining
geodes. The darkly humorous twists of ``Bad Sons Anonymous'' remind us
that it's never just one clear story. \emph{Poem Selected by Naomi
Shihab Nye}

Image

\hypertarget{bad-sons-anonymous}{%
\subsection{Bad Sons Anonymous}\label{bad-sons-anonymous}}

By Virgil Suárez

At this year's convention\\
we gather to pay homage\\
to our fathers, responsible\\
men who worked hard:

laborers, stone cutters, welders,\\
carpenters --- blue collar all,\\
men who raged, stormed\\
their anger through the house,

our mothers couldn't manage,\\
swept with brooms the debris\\
of broken things, in silence\\
they took it out on us, belts

in hand, we stood there, cried,\\
long days turned to long nights,\\
our fathers, mothers, damages\\
done, we, as their only sons,

remember. We, as bad sons,\\
pay them back, one mirror held\\
up to another, an infinity\\
of their gnarled faces, red-blue-fire

what has become lost in all of us.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{Naomi Shihab Nye} is the 2019-21 Young People's Poet Laureate of
the Poetry Foundation in Chicago. Her new book is ``Cast Away''
(Greenwillow Books). \textbf{Virgil Suárez} was born in Cuba and
educated in the United States from age 12. A writer of novels, stories
and memoirs, Suárez lives in Florida and is author of ``The Painted
Bunting's Last Molt,'' which was published by the University of
Pittsburgh Press in March.

Illustration by R.O. Blechman

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
