\href{//www.nytimes3xbfgragh.onion}{}
\href{//elections.nytimes3xbfgragh.onion}{ Election 2016}

\href{//www.nytimes3xbfgragh.onion}{ Home}

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/senate}{Senate}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/house}{House}
\href{//www.nytimes3xbfgragh.onion/interactive/2016/11/08/us/politics/election-exit-polls.html}{Exit
Polls} \href{//www.nytimes3xbfgragh.onion/elections\#}{More}

Close

Forecast

\href{//www.nytimes3xbfgragh.onion/elections/2016/forecast/president}{}

\hypertarget{election-night-estimates-from-the-upshot}{%
\subsubsection{Election Night Estimates from The
Upshot}\label{election-night-estimates-from-the-upshot}}

Key States

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Arizona}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colorado}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Florida}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nevada}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{New
Hampshire}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{North
Carolina}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pennsylvania}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Virginia}

All States

Alabama Alaska Arizona Arkansas California Colorado Connecticut Delaware
District of Columbia Florida Georgia Hawaii Idaho Illinois Indiana Iowa
Kansas Kentucky Louisiana Maine Maryland Massachusetts Michigan
Minnesota Mississippi Missouri Montana Nebraska Nevada New Hampshire New
Jersey New Mexico New York North Carolina North Dakota Ohio Oklahoma
Oregon Pennsylvania Rhode Island South Carolina South Dakota Tennessee
Texas Utah Vermont Virginia Washington West Virginia Wisconsin Wyoming

The data for the results on this site are reported by the Associated
Press through the week of Nov. 8, 2016. Presidential results are updated
as of Feb. 2017.

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/senate}{Senate}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/house}{House}
\href{//www.nytimes3xbfgragh.onion/elections/2016/forecast/president}{Forecast}
\href{//www.nytimes3xbfgragh.onion/interactive/2016/11/08/us/politics/election-exit-polls.html}{Exit
Polls} \href{//www.nytimes3xbfgragh.onion/elections\#}{State Results}
\href{//www.nytimes3xbfgragh.onion/elections\#}{More}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alabama}{Ala.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alaska}{Alaska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Ariz.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arkansas}{Ark.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/california}{Calif.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colo.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/connecticut}{Conn.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/delaware}{Del.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/district-of-columbia}{D.C.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Fla.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/georgia}{Ga.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/hawaii}{Hawaii}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/idaho}{Idaho}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/illinois}{Ill.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/indiana}{Ind.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kansas}{Kan.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kentucky}{Ky.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/louisiana}{La.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maine}{Me.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maryland}{Md.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/massachusetts}{Mass.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/michigan}{Mich.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/minnesota}{Minn.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Miss.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/missouri}{Mo.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/montana}{Mont.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nebraska}{Neb.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nev.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{N.H.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-jersey}{N.J.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-mexico}{N.M.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-york}{N.Y.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{N.C.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-dakota}{N.D.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oklahoma}{Okla.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oregon}{Ore.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pa.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/rhode-island}{R.I.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-carolina}{S.C.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-dakota}{S.D.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/tennessee}{Tenn.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/texas}{Tex.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/utah}{Utah}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/vermont}{Vt.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Va.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/washington}{Wash.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/west-virginia}{W.Va.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wisconsin}{Wis.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wyoming}{Wyo.}
\end{itemize}

\hypertarget{arizona-results}{%
\section{Arizona Results}\label{arizona-results}}

 Aug. 1, 2017, 11:22 AM ET

\protect\hyperlink{president}{ President Pres. Trump }
\protect\hyperlink{senate}{ Senate Sen. McCain }
\protect\hyperlink{house}{House 4 D 5 R }
\protect\hyperlink{state-legislature}{State Legislature}
\protect\hyperlink{ballot-measure}{Ballot Measures}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/primaries/arizona}{Primary
Results}

\hypertarget{president}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona-president-clinton-trump}{President}}{President}}\label{president}}

Candidate

Party

Votes

Pct.

E.V.

Republican Rep.

1,252,401

48.1\%

11

Democrat Dem.

1,161,167

44.6\%

---

Libertarian Lib.

106,327

4.1\%

---

Independent Ind.

50,417

1.9\%

---

Green Green

34,345

1.3\%

---

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Full
Ariz. Results »}

2,604,657 votes, 100\% reporting (1,469 of 1,469 precincts)

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President
Map »}

Race Preview: Democrats believe they have a chance of winning Arizona's
11 electoral votes for the first time since Bill Clinton carried the
state in 1996, but polls show the race leaning in Mr. Trump's favor.
\href{//elections.nytimes3xbfgragh.onion/2012/results/states/arizona}{Mitt
Romney won Arizona in 2012} by 9 percentage points.

Vote share

Dem. 40 50 60

Rep. 40 50 60

Other 40 50 60

 No results

Vote by county

Trump

Clinton

Maricopa

747,361

702,907

Pima

167,428

224,661

Pinal

72,819

47,892

Yavapai

71,330

35,590

Mohave

58,282

17,455

Coconino

21,108

32,404

Yuma

25,165

24,605

Cochise

28,092

17,450

Navajo

20,577

16,459

Apache

8,240

17,083

Gila

14,182

7,003

Santa Cruz

3,897

11,690

Graham

8,025

3,301

La Paz

4,003

1,575

Greenlee

1,892

1,092

\protect\hyperlink{}{+ Show all counties -- Hide smaller counties}

\hypertarget{us-senate}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona-senate-mccain-kirkpatrick}{U.S.
Senate}}{U.S. Senate}}\label{us-senate}}

Candidate

Party

Votes

Pct.

Republican Rep.

1,359,267

53.7\%

Democrat Dem.

1,031,245

40.8\%

Green Green

138,634

5.5\%

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Full
Ariz. Results »}

2,529,146 votes, 100\% reporting (1,469 of 1,469 precincts)

* Incumbent

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/senate}{U.S.
Senate Map »}

Vote share

Dem. 40 50 60

Rep. 40 50 60

Other 40 50 60

 No results

Vote by county

McCain

Kirkpatrick

Maricopa

842,425

602,635

Pima

187,910

202,213

Pinal

72,787

45,402

Yavapai

68,032

34,527

Mohave

50,486

19,045

Coconino

24,031

31,695

Yuma

27,290

19,451

Cochise

27,636

17,642

Navajo

18,760

17,645

Apache

7,944

18,446

Gila

13,157

6,701

Santa Cruz

5,635

9,745

Graham

7,728

3,280

La Paz

3,662

1,629

Greenlee

1,784

1,189

\protect\hyperlink{}{+ Show all counties -- Hide smaller counties}

\hypertarget{us-house}{%
\subsection{U.S. House}\label{us-house}}

Dem. 4 Dem.

Rep. 5 Rep.

Ind. 0 Ind.

No net change

\begin{longtable}[]{@{}lllll@{}}
\toprule
District Dist. & Leader & & Rpt. &\tabularnewline
\midrule
\endhead
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-1-ohalleran-babeu}{1}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-1-ohalleran-babeu}{
51\%O'Halleran Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-1-ohalleran-babeu}{
43\%Babeu Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-1-ohalleran-babeu}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-1-ohalleran-babeu}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-2-mcsally-heinz}{2}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-2-mcsally-heinz}{
57\%McSally* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-2-mcsally-heinz}{
43\%Heinz Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-2-mcsally-heinz}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-2-mcsally-heinz}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-3}{3}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-3}{
0\%Grijalva* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-3}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-3}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-3}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-4-gosar-weisser}{4}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-4-gosar-weisser}{
72\%Gosar* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-4-gosar-weisser}{
29\%Weisser Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-4-gosar-weisser}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-4-gosar-weisser}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-5-fuentes-biggs}{5}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-5-fuentes-biggs}{
64\%Biggs Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-5-fuentes-biggs}{
36\%Fuentes Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-5-fuentes-biggs}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-5-fuentes-biggs}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-6-schweikert-williamson}{6}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-6-schweikert-williamson}{
62\%Schweikert* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-6-schweikert-williamson}{
38\%Williamson Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-6-schweikert-williamson}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-6-schweikert-williamson}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-7-gallego-nunez}{7}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-7-gallego-nunez}{
75\%Gallego* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-7-gallego-nunez}{
25\%Nunez Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-7-gallego-nunez}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-7-gallego-nunez}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-8}{8}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-8}{
69\%Franks* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-8}{
31\%Salazar Green} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-8}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-8}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-9-sinema-giles}{9}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-9-sinema-giles}{
61\%Sinema* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-9-sinema-giles}{
39\%Giles Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-9-sinema-giles}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-house-district-9-sinema-giles}{}\tabularnewline
\bottomrule
\end{longtable}

* Incumbent~

 Lead Win Flip Dem.

 Lead Win Flip Rep.

 Lead Win Flip Other

 Runoff

 No election

 No results

\hypertarget{state-senate}{%
\subsection{State Senate}\label{state-senate}}

Dem. 12 Dem.

Rep. 15 Rep.

Ind. 0 Ind.

No net change

\begin{longtable}[]{@{}lllll@{}}
\toprule
Seat Seat & Leader & & Rpt. &\tabularnewline
\midrule
\endhead
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-1}{1}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-1}{
0\%Fann Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-1}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-1}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-1}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-2}{2}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-2}{
59\%Dalessandro* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-2}{
41\%Kais Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-2}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-2}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-3}{3}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-3}{
0\%Cajero Bedford* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-3}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-3}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-3}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-4}{4}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-4}{
0\%Otondo Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-4}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-4}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-4}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-5}{5}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-5}{
0\%Borrelli Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-5}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-5}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-5}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-6}{6}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-6}{
52\%Allen* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-6}{
48\%Bagley Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-6}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-6}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-7}{7}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-7}{
0\%Peshlakai Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-7}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-7}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-7}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-8}{8}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-8}{
53\%Pratt Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-8}{
47\%McGuire* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-8}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-8}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-9}{9}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-9}{
0\%Farley* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-9}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-9}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-9}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-10}{10}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-10}{
54\%Bradley* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-10}{
46\%Phelps Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-10}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-10}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-11}{11}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-11}{
59\%Smith* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-11}{
41\%Atchue Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-11}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-11}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-12}{12}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-12}{
64\%Petersen Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-12}{
36\%Brown Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-12}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-12}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-13}{13}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-13}{
0\%Montenegro Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-13}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-13}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-13}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-14}{14}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-14}{
63\%Griffin* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-14}{
37\%Alvarez Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-14}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-14}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-15}{15}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-15}{
63\%Barto* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-15}{
38\%MacBeth Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-15}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-15}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-16}{16}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-16}{
64\%Farnsworth* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-16}{
36\%Prior Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-16}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-16}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-17}{17}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-17}{
57\%Yarbrough* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-17}{
44\%Weichert Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-17}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-17}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-18}{18}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-18}{
52\%Bowie Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-18}{
49\%Schmuck Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-18}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-18}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-19}{19}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-19}{
0\%Chavira Contreras* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-19}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-19}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-19}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-20}{20}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-20}{
50\%Yee* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-20}{
36\%Herrera Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-20}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-20}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-21}{21}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-21}{
0\%Lesko* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-21}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-21}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-21}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-22}{22}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-22}{
65\%Burges* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-22}{
35\%Muscato Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-22}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-22}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-23}{23}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-23}{
0\%Kavanagh* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-23}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-23}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-23}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-24}{24}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-24}{
0\%Hobbs* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-24}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-24}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-24}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-25}{25}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-25}{
0\%Worsley* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-25}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-25}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-25}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-26}{26}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-26}{
0\%Mendez Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-26}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-26}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-26}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-27}{27}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-27}{
81\%Miranda* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-27}{
19\%Torres Green} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-27}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-27}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-28}{28}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-28}{
51\%McGee Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-28}{
49\%Meyer Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-28}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-28}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-29}{29}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-29}{
67\%Quezada* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-29}{
33\%Nuttle Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-29}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-29}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-30}{30}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-30}{
65\%Meza* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-30}{
35\%Lyon Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-30}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-senate-district-30}{}\tabularnewline
\bottomrule
\end{longtable}

* Incumbent~

\protect\hyperlink{}{+ Show all races-- Show less races}

\hypertarget{state-house}{%
\subsection{State House}\label{state-house}}

Dem. 26 Dem.

Rep. 32 Rep.

Ind. 0 Ind.

No net change

\begin{longtable}[]{@{}lllll@{}}
\toprule
District Dist. & Leader & & Rpt. &\tabularnewline
\midrule
\endhead
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{1}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{
36\%Stringer Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{
39\%Campbell* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-1}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{2}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{
35\%Gabaldon* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{
34\%Hernandez Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-2}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{3}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{
50\%Gonzales* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{
38\%Saldate* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-3}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{4}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{
0\%Fernandez* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{0\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{
0\%Rubalcava Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-4}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{5}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{
39\%Mosley Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{
38\%Cobb* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-5}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{6}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{
35\%Thorpe* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{
34\%Barton* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-6}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{7}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{
0\%Descheenie Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{0\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{
0\%Benally* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-7}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{8}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{
34\%Shope* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{
36\%Cook Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-8}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{9}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{
33\%Hannley Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{
37\%Friese* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-9}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{10}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{
33\%Mach* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{
34\%Engel Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-10}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{11}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{
34\%Leach* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{
36\%Finchem* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-11}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{12}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{
0\%Farnsworth* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{0\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{
0\%Grantham Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-12}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{13}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{
38\%Mitchell* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{
39\%Shooter Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-13}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{14}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{
33\%John Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{
31\%Nutt Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-14}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{15}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{
40\%Carter* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{
35\%Allen* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-15}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{16}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{
33\%Coleman* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{
33\%Townsend* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-16}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{17}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{
36\%Weninger* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{
33\%Mesnard* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-17}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-18}{18}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-18}{
31\%Epstein Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-18}{
30\%Norgaard* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-18}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-18}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{19}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{
0\%Espinoza* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{0\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{
0\%Cardenas* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-19}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{20}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{
34\%Kern* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{
35\%Boyer* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-20}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{21}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{
36\%Rivero* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{
37\%Payne Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-21}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{22}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{
40\%Livingston* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{
37\%Lovas* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-22}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{23}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{
36\%Lawrence* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{
38\%Ugenti-Rita* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-23}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{24}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{
0\%Clark* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{0\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{
0\%Alston* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-24}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{25}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{
40\%Udall Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{
36\%Bowers* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-25}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{26}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{
32\%Blanc Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{
33\%Salman Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-26}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{27}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{
0\%Bolding* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{0\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{
0\%Rios* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-27}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-28}{28}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-28}{
36\%Butler Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-28}{
33\%Syms Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-28}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-28}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{29}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{
41\%Chavez Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{
35\%Andrade* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-29}{~}
&\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{30}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{
38\%Martinez Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{
37\%Navarrete Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{~}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-state-house-district-30}{~}
&\tabularnewline
\bottomrule
\end{longtable}

* Incumbent~

\protect\hyperlink{}{+ Show all races-- Show less races}

\hypertarget{ballot-measures}{%
\subsection{Ballot Measures}\label{ballot-measures}}

\hypertarget{proposition-205legalize-marijuana}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-ballot-measure-205-legalize-marijuana}{Proposition
205Legalize
Marijuana}}{Proposition 205Legalize Marijuana}}\label{proposition-205legalize-marijuana}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Answer & Votes & Pct. &\tabularnewline
\midrule
\endhead
 Yes Yes & 1,233,323 & 48.7\% &\tabularnewline
 No No & 1,300,344 & 51.3\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Full
Ariz. Results »}

2,533,667 votes, 100\% reporting (1,469 of 1,469 precincts)

\hypertarget{proposition-206increase-minimum-wage}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona-ballot-measure-206-increase-minimum-wage}{Proposition
206Increase Minimum
Wage}}{Proposition 206Increase Minimum Wage}}\label{proposition-206increase-minimum-wage}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Answer & Votes & Pct. &\tabularnewline
\midrule
\endhead
 Yes Yes & 1,465,639 & 58.3\% &\tabularnewline
 No No & 1,046,945 & 41.7\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Full
Ariz. Results »}

2,512,584 votes, 100\% reporting (1,469 of 1,469 precincts)

\hypertarget{corporation-commissioner}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona-corporation-commissioner-4-year-term}{Corporation
Commissioner}}{Corporation Commissioner}}\label{corporation-commissioner}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Votes & Pct. &\tabularnewline
\midrule
\endhead
 Dunn Boyd Dunn & Republican Rep. & 864,490 & 19.6\% &\tabularnewline
 Burns* Robert Burns* & Republican Rep. & 986,395 & 22.4\%
&\tabularnewline
 Tobin* Andy Tobin* & Republican Rep. & 917,085 & 20.8\%
&\tabularnewline
 Mundell William Mundell & Democrat Dem. & 835,210 & 18.9\%
&\tabularnewline
 Chabin Tom Chabin & Democrat Dem. & 808,593 & 18.3\% &\tabularnewline
 Others Others & & 1,643,803 & 37.3\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Full
Ariz. Results »}

4,411,773 votes, 100\% reporting (1,469 of 1,469 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

* Incumbent

\hypertarget{maricopa-sheriff}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona-sheriff-maricopa}{Maricopa
Sheriff}}{Maricopa Sheriff}}\label{maricopa-sheriff}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Votes & Pct. &\tabularnewline
\midrule
\endhead
 Penzone Paul Penzone & Democrat Dem. & 665,478 & 55.6\%
&\tabularnewline
 Arpaio* Joe Arpaio* & Republican Rep. & 531,674 & 44.4\%
&\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Full
Ariz. Results »}

1,197,152 votes, 100\% reporting (724 of 724 precincts)

* Incumbent

\hypertarget{supreme-court-retain-ann-timmer}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona-supreme-court-retain-ann-timmer}{Supreme
Court Retain Ann
Timmer}}{Supreme Court Retain Ann Timmer}}\label{supreme-court-retain-ann-timmer}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Answer & Votes & Pct. &\tabularnewline
\midrule
\endhead
 Yes Yes & 1,099,222 & 76.9\% &\tabularnewline
 No No & 330,693 & 23.1\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Full
Ariz. Results »}

1,429,915 votes, 100\% reporting (1,469 of 1,469 precincts)

\hypertarget{president-1}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President}}{President}}\label{president-1}}

\hypertarget{senate}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/senate}{Senate}}{Senate}}\label{senate}}

\hypertarget{house}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/house}{House}}{House}}\label{house}}

\hypertarget{state-results}{%
\subsubsection{State Results}\label{state-results}}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alabama}{Alabama}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alaska}{Alaska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Arizona}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arkansas}{Arkansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/california}{California}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colorado}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/connecticut}{Connecticut}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/delaware}{Delaware}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/district-of-columbia}{District
  of Columbia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Florida}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/georgia}{Georgia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/hawaii}{Hawaii}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/idaho}{Idaho}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/illinois}{Illinois}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/indiana}{Indiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kansas}{Kansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kentucky}{Kentucky}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/louisiana}{Louisiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maine}{Maine}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maryland}{Maryland}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/massachusetts}{Massachusetts}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/michigan}{Michigan}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/minnesota}{Minnesota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Mississippi}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/missouri}{Missouri}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/montana}{Montana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nebraska}{Nebraska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nevada}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{New
  Hampshire}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-jersey}{New
  Jersey}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-mexico}{New
  Mexico}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-york}{New
  York}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{North
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-dakota}{North
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oklahoma}{Oklahoma}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oregon}{Oregon}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pennsylvania}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/rhode-island}{Rhode
  Island}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-carolina}{South
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-dakota}{South
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/tennessee}{Tennessee}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/texas}{Texas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/utah}{Utah}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/vermont}{Vermont}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/washington}{Washington}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/west-virginia}{West
  Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wisconsin}{Wisconsin}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wyoming}{Wyoming}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alabama}{Alabama}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alaska}{Alaska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Arizona}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arkansas}{Arkansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/california}{California}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colorado}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/connecticut}{Connecticut}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/delaware}{Delaware}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/district-of-columbia}{District
  of Columbia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Florida}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/georgia}{Georgia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/hawaii}{Hawaii}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/idaho}{Idaho}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/illinois}{Illinois}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/indiana}{Indiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kansas}{Kansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kentucky}{Kentucky}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/louisiana}{Louisiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maine}{Maine}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maryland}{Maryland}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/massachusetts}{Massachusetts}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/michigan}{Michigan}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/minnesota}{Minnesota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Mississippi}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/missouri}{Missouri}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/montana}{Montana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nebraska}{Nebraska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nevada}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{New
  Hampshire}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-jersey}{New
  Jersey}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-mexico}{New
  Mexico}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-york}{New
  York}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{North
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-dakota}{North
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oklahoma}{Oklahoma}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oregon}{Oregon}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pennsylvania}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/rhode-island}{Rhode
  Island}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-carolina}{South
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-dakota}{South
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/tennessee}{Tennessee}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/texas}{Texas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/utah}{Utah}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/vermont}{Vermont}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/washington}{Washington}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/west-virginia}{West
  Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wisconsin}{Wisconsin}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wyoming}{Wyoming}
\end{itemize}

Sources: Election results from The Associated Press, Dave Leip's Atlas
of U.S. Presidential Elections and David Wasserman of the Cook Political
Report

By The New York Times

\begin{itemize}
\tightlist
\item
  \href{//www.nytco.com}{© 2017 The New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytco.com}{© 2017 The New York Times Company}
\item
  \href{//www.nytimes3xbfgragh.onion/ref/membercenter/help/infoservdirectory.html}{Contact
  Us}
\item
  \href{//www.nytco.com/careers}{Work With Us}
\item
  \href{//www.nytimes.whsites.net/mediakit}{Advertise}
\item
  \href{//www.nytimes3xbfgragh.onion/content/help/rights/privacy/policy/privacy-policy.html\#pp}{Your
  Ad Choices}
\item
  \href{//www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{//www.nytimes3xbfgragh.onion/ref/membercenter/help/agree.html}{Terms
  of Service}
\item
  \href{//www.nytimes3xbfgragh.onion/content/help/rights/sale/terms-of-sale.html}{Terms
  of Sale}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{//www.nytimes3xbfgragh.onion/membercenter/sitehelp.html}{Help}
\item
  \href{https://myaccount.nytimes3xbfgragh.onion/membercenter/feedback.html}{Site
  Feedback}
\item
  \href{//www.nytimes3xbfgragh.onion/subscriptions/Multiproduct/lp5558.html?campaignId=37WXW}{Subscriptions}
\end{itemize}
