Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/sports}{Sports}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/sports}{Sports}\textbar{}A Friendship Built for Long
Distance

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{a-friendship-built-for-long-distance}{%
\section{A Friendship Built for Long
Distance}\label{a-friendship-built-for-long-distance}}

By Sarah Bowen Shea

\begin{itemize}
\item
  May 8, 2010
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

In January, when the elite marathoner
\href{http://www.usatf.org/athletes/bios/Grgas-Wheeler_Kara.asp}{Kara
Goucher} found out she was pregnant, she knew exactly whom to ask for
advice. Paula Radcliffe, the women's world-record holder and mother of a
3-year-old daughter, had just arrived in Portland, Ore., to train with
her.

The topic of pregnancy became more personal for Radcliffe a few days
later when she, too, learned she was expecting. She and Goucher are due
to give birth on the same date in late September.

``We were both really excited and really happy,'' said Goucher, who had
been forthright in her desire to have a baby in time to regroup for the
2012 Olympics.

Before this year, the friendship between Goucher, a 32-year-old
American, and Radcliffe, a 36-year-old Briton, was based mainly on
e-mail messages with occasional meetings at races. They became
acquainted at the 2007 Great North Run, a prestigious half-marathon in
England, in which Goucher staged a surprise win over Radcliffe. A few
weeks later, Goucher watched Radcliffe win the New York City Marathon.

``There was a lot of respect there, but I didn't know her well enough to
classify her as a good friend,'' Radcliffe said in a phone interview.

They grew close while spending their first trimester together.

``She's now one of my very best friends,'' Goucher said in a recent
interview at Nike headquarters in Beaverton, Ore. ``I feel I can ask her
anything, and she'll tell me. That came over time. It wasn't like I
asked her everything on our first run.''

Image

Kara Goucher, right, with Paula Radcliffe. They became friends while
training together in Oregon after they each found out they were
pregnant.Credit...Nike

In the first few weeks of pregnancy, Goucher and Radcliffe met every
morning at 9:30, after Radcliffe dropped off her daughter, Isla. They
ran together, doing tempo runs, hill repeats and track workouts wearing
heart-rate monitors to gauge their intensity. They occasionally met in
the afternoon for a second workout, although Goucher often napped
instead because of pregnancy-induced fatigue.

``It helped to have someone going through it at the same time even
though we didn't have the exact same feelings on the exact same day,''
Radcliffe said. ``If you haven't gone through pregnancy, you don't know
what that type of tiredness feels like, what being wiped out feels
like.''

Goucher, who finished third in the 2008 New York City and 2009 Boston
marathons, benefited from Radcliffe's advice to leave her watch at home
during hill repeats and to cut runs short when she feels a twinge.

``She's been giving me a lot of advice on chilling out,'' Goucher said.
``She helped me realize I'm not failing. She's helped me realize I can
just push to my limits.''

Radcliffe said she did not see herself as a ``mommy mentor.''

She added: ``I didn't sit down and lecture her; I passed along bits to
her,'' by consulting the training diary she kept during her first
pregnancy. ``It helped her accept it.''

Radcliffe reminded Goucher to eat before lifting weights, which they
started doing together at Week 8 of their pregnancies.

Image

Kara Goucher with her husband, Adam. Kara said she was planning to
compete at the 2012 Olympics.Credit...Leah Nash for The New York Times

``I felt a bit like a mum when I'd nag her to eat,'' Radcliffe said,
laughing.

Goucher cited recent solo workouts as proof she had listened.

On May 2, she ran 13 miles at 6 minutes 50 seconds per mile. But the
next day, she ran six miles at an 8:15 pace.

``I was tired on that run,'' Goucher said. ``That used to upset me when
I'd have a bad day, but now I know it is what it is. When I feel really
tired, I'll just cut my mileage back and in the afternoon do the
elliptical or bike.''

But Radcliffe said they were ``competitive animals'' who occasionally
pushed themselves too hard. They told of a track workout that consisted
of various sprints, and they took turns leading.

Goucher said she ran too fast ``because it was Paula Radcliffe running
behind me.'' Then Radcliffe felt she had to lead as fast as Goucher had.
Looking at their monitors during a brief respite, their heart rates
skyrocketed, Goucher said. They recruited Radcliffe's husband, Gary
Lough, to lead them for the remainder of the workout.

Their training is intense but within the most recent physical-activity
guidelines for pregnant women from the United States Department of
Health and Human Services.

Image

At the 2008 New York City Marathon, Kara Goucher, center, briefly led
Paula Radcliffe, left, who eventually won. Goucher was
third.Credit...Michelle V. Agins/The New York Times

``The recommendations say women can sustain the level of their activity
prior to pregnancy,'' said Danielle Symons Downs, an associate professor
of kinesiology and obstetrics and gynecology at Penn State who
researches pregnancy and exercise.

Radcliffe and Goucher, she said, are ``right in the guidelines with
their vigorous activity.''

Other experts disagree.

``I don't know it's safe for high-level marathon runners to run at that
level during pregnancy,'' said Dr. Mona Shangold, the director of the
Center for Women's Health and Sports Gynecology in Philadelphia. ``It
has not been shown that running for that long, for that intensity, is
safe.''

Nonetheless, Goucher and Radcliffe are planning to convene for the New
York Mini 10K, a women's race on June 12 in Central Park put on by the
New York Road Runners.

``It's an excuse for us to get together; a chance to hang together
before we get too pregnant to travel,'' Goucher said with a laugh. ``We
are really just running it for fun. Not racing.''

Radcliffe agreed, adding that they may have Mary Wittenberg, the Road
Runners' president, accompany them to ensure that they do not go too
fast.

As for their competitive paths and relationship after they give birth,
Goucher and Radcliffe intend to qualify for the 2012 Olympic marathon in
London.

``When both of us stand on the start line and the gun goes off, we both
want to win that race,'' Radcliffe said. ``But there's room for a really
good friendship at the same time.''

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
