Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{Remembering the 100,000 Lives Lost to Coronavirus in
America}\href{}{Skip to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@nytimes.com}{\nolinkurl{letters@nytimes.com}}.

\hypertarget{remembering-the-100000-lives-lost-to-coronavirus-in-america}{%
\section{Remembering the 100,000 Lives Lost to Coronavirus in
America}\label{remembering-the-100000-lives-lost-to-coronavirus-in-america}}

By \href{https://www.nytimes.com/by/dan-barry}{Dan Barry},
\href{https://www.nytimes.com/by/larry-buchanan}{Larry Buchanan},
Clinton Cargill, \href{https://www.nytimes.com/by/annie-daniel}{Annie
Daniel}, Alain Delaquérière,
\href{https://www.nytimes.com/by/lazaro-gamio}{Lazaro Gamio}, Gabriel
Gianordoli, Richard Harris, Barbara Harvey, John Haskins,
\href{https://www.nytimes.com/by/jon-huang}{Jon Huang}, Simone Landon,
Juliette Love, Grace Maalouf, Alex Matthews, Farah Mohamed, Steven
Moity, Destinée-Charisse Royal, Matt Ruby and
\href{https://www.nytimes.com/by/eden-weingart}{Eden Weingart}Updated
Updated May 27, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{52}
\end{itemize}

As the U.S. reached a grim milestone in the outbreak, The New York Times
gathered names of the dead and memories of their lives from obituaries
across the country.

\hypertarget{an-incalculable-loss}{%
\section{An Incalculable Loss}\label{an-incalculable-loss}}

America has reached a grim milestone in the coronavirus outbreak ---
each figure here represents one of the 100,000 lives lost so far. But a
count reveals only so much. Memories, gathered from obituaries across
the country, help us to reckon with what was lost.

By The New York Times Updated May 27, 2020

One hundred thousand.

Toward the end of May in the year 2020, the number of people in the
United States who have died from the coronavirus passed 100,000 ---
almost all of them within a three-month span. An average of more than
1,100 deaths a day.

One hundred thousand.

A number is an imperfect measure when applied to the human condition. A
number provides an answer to how many, but it can never convey the
individual arcs of life, the 100,000 ways of greeting the morning and
saying good night.

One hundred thousand.

The immensity of such a sudden toll taxes our ability to comprehend, to
understand that each number adding up to 100,000 represents someone
among us just yesterday. Who was the 1,233rd person to die? The
27,587th? The 98,431st?

She may have died in a jam-packed hospital, with no family member at her
bedside to whisper a final thank you, Mom, I love you.

He may have died in a locked-down nursing home, his wife peering
helplessly through a streaked window as a part of her slips away.

They may have died in subdivided city apartments, too sick or too scared
to go to a hospital, their closest relatives a half-world away.

This highly contagious virus has forced us to suppress our nature as
social creatures, for fear that we might infect or be infected. Among
the many indignities, it has denied us the grace of being present for a
loved one's last moments. Age-old customs that lend meaning to existence
have been upended, including the sacred rituals of how we mourn.

Before, we came together in halls and bars and places of worship to
remember and honor the dead. We recited prayers or raised glasses or
retold familiar stories so funny they left us nodding and crying through
our laughter.

In these vital moments of communion, it could feel as though the
departed were with us one last time, briefly resurrected by the sheer
power of our collective love, to share that closing prayer, that parting
glass, that final hug.

Even in the horrible times of wars and hurricanes and terrorist attacks
that seemed to crumble the ground beneath our feet, we at least had
time-tested ways of grieving that helped us take that first hesitant
step forward.

Not now.

Now, for most of those who died in the past few months, there were no
large gatherings of consolation and recited prayers for peaceful rest.
The obituaries that filled our local newspapers and Facebook pages
sometimes read like an unending roll call of the coronavirus dead.

Every death notice, virus-related or not, seemed to close with:
\emph{Due to health concerns and restrictions on gatherings, there will
be no funeral services at this time. A celebration of life will be held
at a time to be announced.}

A virtual memorial service was held instead, perhaps, with mourners
praying into laptop screens. Followed by a burial, perhaps, with masked
mourners watching from their cars as another coffin was received by the
earth.

In a larger sense, the suspension of our familiar rituals of burial or
cremation reflected what life in a pandemic has been like. The absence
of any clear end.

Even the dead have to wait.

Why has this happened in the United States of 2020? Why has the virus
claimed a disproportionately large number of black and Latino victims?
Why were nursing homes so devastated? These questions of why and how and
whom will be asked for decades to come.

For now, all we can do is hold our collective breath, inch toward some
approximation of how things were --- and try to process a loss of life
greater than what the country incurred in several decades of war, from
Vietnam to Iraq.

One hundred thousand.

A threshold number. It is the number celebrated when the family car's
odometer ticks once more to reach six digits. It is the number of
residents that can make a place feel fully like a city: San Angelo,
Texas; Kenosha, Wisconsin; Vacaville, California.

So imagine a city of 100,000 residents that was here for New Year's Day
but has now been wiped from the American map.

One hundred thousand.

Den mother for Cub Scout Pack 9. Manager of the produce department.
Tavern owner. Nurse to the end.

Loved baseball. Loved playing euchre. Loved seeing the full moon rise
above the ocean.

Man, could she cook.

Always first on the dance floor. Always ready to party. Always gave
back.

Preferred bolo ties and suspenders.

Awarded the Bronze Star. Served in the Women's Army Corps. Survived the
sinking of the Andrea Doria. Competed in the Special Olympics.
Immigrated to achieve the American dream.

Could quote Tennyson from memory.

A number is an imperfect measure when applied to the human condition.

One. Hundred. Thousand.

**** total deaths

\hypertarget{about-this-project}{%
\paragraph{About this project}\label{about-this-project}}

The descriptions of the lives of a thousand people in the United States
who died because of the coronavirus were drawn from hundreds of
obituaries, news articles and paid death notices that have appeared in
newspapers and digital media over the past few months. They have been
lightly edited for clarity.

They were compiled from the following publications:

\begin{itemize}
\tightlist
\item
  \href{https://www.crowleypostsignal.com/}{Acadia Parish Today}
\item
  \href{https://www.theadanews.com/\%20}{The Ada News}
\item
  \href{https://www.theadvocate.com/}{The Advocate}
\item
  \href{https://www.beaconjournal.com/}{The Akron Beacon Journal}
\item
  \href{https://www.albanyherald.com/}{The Albany Herald}
\item
  \href{https://www.the-review.com/}{The Alliance Review}
\item
  \href{https://www.argusleader.com/}{The Argus Leader}
\item
  \href{https://www.azcentral.com/}{The Arizona Republic}
\item
  \href{https://www.app.com/}{The Asbury Park Press}
\item
  \href{https://www.citizen-times.com/}{The Asheville Citizen-Times}
\item
  \href{https://apnews.com/}{The Associated Press}
\item
  \href{https://www.baltimoresun.com/}{The Baltimore Sun}
\item
  \href{https://www.timesargus.com/}{The Barre-Montpelier Times Argus}
\item
  \href{https://www.battlecreekenquirer.com/}{The Battle Creek Enquirer}
\item
  \href{https://www.mlive.com/saginaw-bay-city/}{The Bay City Times}
\item
  \href{https://www.liherald.com/bellmore/}{The Bellmore Herald}
\item
  \href{https://www.berkshireeagle.com/}{The Berkshire Eagle}
\item
  \href{https://bossierpress.com/}{The Bossier Press-Tribune}
\item
  \href{https://www.bostonglobe.com/}{The Boston Globe}
\item
  \href{https://www.bradenton.com/}{The Bradenton Herald}
\item
  \href{https://www.reformer.com/}{The Brattleboro Reformer}
\item
  \href{http://www.bristolpress.com/}{The Bristol Press}
\item
  \href{https://www.brunswickbeacon.com/}{The Brunswick Beacon}
\item
  \href{https://www.buckscountycouriertimes.com/}{The Bucks County
  Courier Times}
\item
  \href{https://buffalonews.com/}{The Buffalo News}
\item
  \href{https://www.burlingtonfreepress.com/}{The Burlington Free Press}
\item
  \href{https://www.woonsocketcall.com/}{The Call}
\item
  \href{https://www.capecodtimes.com/}{The Cape Cod Times}
\item
  \href{https://madison.com/ct/}{The Capital Times}
\item
  \href{https://www.baltimoresun.com/maryland/carroll/}{The Carroll
  County Times}
\item
  \href{https://www.wrbl.com/}{CBS 3 (WRBL)}
\item
  CE Noticias Financieras
\item
  \href{http://www.chestercounty.com/}{The Chester County Press}
\item
  \href{https://www.chestnuthilllocal.com/}{The Chestnut Hill Local}
\item
  \href{https://www.chicagotribune.com/}{The Chicago Tribune}
\item
  \href{https://www.cincinnati.com/}{The Cincinnati Enquirer}
\item
  \href{https://www.clintonherald.com/}{The Clinton Herald}
\item
  \href{https://www.dispatch.com/}{The Columbus Dispatch}
\item
  \href{https://www.ctpost.com/}{The Connecticut Post}
\item
  \href{https://www.gazettetimes.com/}{The Corvallis Gazette-Times}
\item
  \href{https://bellingham.wickedlocal.com/}{The Country Gazette}
\item
  \href{https://www.mycentraljersey.com/}{The Courier News}
\item
  \href{https://www.courier-journal.com/}{The Courier-Journal}
\item
  \href{https://www.courierpostonline.com/}{The Courier-Post}
\item
  \href{https://www.crowleypostsignal.com/}{The Crowley Post-Signal}
\item
  \href{https://www.times-news.com/}{The Cumberland Times-News}
\item
  \href{https://www.theadvertiser.com/}{The Daily Advertiser}
\item
  \href{https://www.dailybreeze.com/}{The Daily Breeze}
\item
  \href{https://dailygazette.com/}{The Daily Gazette}
\item
  \href{https://www.gazettenet.com/}{The Daily Hampshire Gazette}
\item
  \href{https://www.dailyherald.com/}{The Daily Herald}
\item
  \href{https://www.dailyiowegian.com/}{The Daily Iowegian}
\item
  \href{https://www.dailyitem.com/}{The Daily Item}
\item
  \href{http://www.dailyjournal.net/}{The Daily Journal}
\item
  \href{https://dailymemphian.com/}{The Daily Memphian}
\item
  The Daily News
\item
  \href{https://www.newburyportnews.com/}{The Daily News of Newburyport}
\item
  \href{https://www.dnronline.com/}{The Daily News-Record}
\item
  \href{https://www.dailyprogress.com/}{The Daily Progress}
\item
  \href{https://www.dailyrecord.com/}{The Daily Record}
\item
  \href{https://www.chicagotribune.com/suburbs/daily-southtown/}{The
  Daily Southtown}
\item
  \href{https://www.dailyworld.com/}{The Daily World}
\item
  \href{https://www.adelnews.com/}{The Dallas County News}
\item
  \href{https://www.theday.com/}{The Day}
\item
  \href{https://delawarestatenews.net/}{Delaware State News}
\item
  \href{https://www.democratandchronicle.com/}{The Democrat and
  Chronicle}
\item
  \href{https://www.derrynews.com/}{Derry News}
\item
  \href{https://www.desmoinesregister.com/}{The Des Moines Register}
\item
  \href{https://www.freep.com/}{The Detroit Free Press}
\item
  \href{https://www.detroitnews.com/}{The Detroit News}
\item
  \href{https://www.leaderpub.com/category/news/dowagiac-news/}{The
  Dowagiac Daily News}
\item
  \href{https://www.eagletribune.com/}{The Eagle-Tribune}
\item
  \href{https://www.eastbaytimes.com/}{The East Bay Times}
\item
  \href{https://dailyvoice.com/new-york/eastchester/}{The Eastchester
  Daily Voice}
\item
  \href{https://www.enterprisenews.com/}{The Enterprise}
\item
  \href{https://www.goerie.com/}{The Erie Times-News}
\item
  \href{https://www.essence.com/}{Essence}
\item
  \href{https://www.eunicetoday.com/}{The Eunice News}
\item
  \href{https://www.lehighvalleylive.com/}{The Express-Times}
\item
  \href{https://www.daily-times.com/}{The Farmington Daily News}
\item
  \href{https://www.daily-times.com/}{The Farmington Daily Times}
\item
  \href{https://www.fijitimes.com/}{The Fiji Times}
\item
  \href{https://www.mlive.com/flint/}{The Flint Journal}
\item
  \href{https://www.jacksonville.com/}{The Florida Times-Union}
\item
  \href{https://kdvr.com/}{FOX 31 (KDVR)}
\item
  \href{https://fox6now.com/}{FOX 6 (WITI)}
\item
  \href{https://www.petoskeynews.com/gaylord/}{The Gaylord Herald Times}
\item
  \href{https://www.thegazette.com/}{The Gazette}
\item
  \href{https://www.gloucestertimes.com/}{The Gloucester Daily Times}
\item
  \href{https://www.grandforksherald.com/}{The Grand Forks Herald}
\item
  \href{https://www.theindependent.com/}{The Grand Island Independent}
\item
  \href{https://www.mlive.com/grand-rapids-muskegon/}{The Grand Rapids
  Press}
\item
  \href{https://www.greatfallstribune.com/}{The Great Falls Tribune}
\item
  \href{https://www.greenbaypressgazette.com/}{The Green Bay
  Press-Gazette}
\item
  \href{https://dailyvoice.com/new-york/greenburgh/}{The Greenburgh
  Daily Voice}
\item
  \href{https://www.greensburgdailynews.com/}{The Greensburg Daily News}
\item
  \href{https://www.greenvilleonline.com/}{The Greenville News}
\item
  \href{https://griffindailynews.com/}{The Griffin Daily News}
\item
  \href{https://thesunpapers.com/haddonfield-sun/}{The Haddonfield Sun}
\item
  \href{https://www.courant.com/}{The Hartford Courant}
\item
  The Herald
\item
  \href{https://www.htrnews.com/}{The Herald Times Reporter}
\item
  \href{https://www.heraldpalladium.com/}{The Herald-Palladium}
\item
  \href{https://www.heraldstandard.com/}{The Herald-Standard}
\item
  \href{https://www.hibbingmn.com/}{The Hibbing Daily Tribune}
\item
  \href{https://www.houmatoday.com/}{The Houma Courier}
\item
  \href{https://hudsonreporter.com/}{The Hudson Reporter}
\item
  \href{https://www.independenttribune.com/}{The Independent Tribune}
\item
  \href{https://indiancountrytoday.com/}{Indian Country Today}
\item
  \href{https://www.idsnews.com/}{The Indiana Daily Student}
\item
  \href{https://www.indystar.com/}{The Indianapolis Star}
\item
  \href{https://www.indianz.com/}{Indianz.com}
\item
  \href{https://www.dailybulletin.com/}{The Inland Valley Daily
  Bulletin}
\item
  \href{https://www.mlive.com/jackson/}{The Jackson Citizen-Patriot}
\item
  \href{https://www.jacksonsun.com/}{The Jackson Sun}
\item
  \href{https://www.newstribune.com/}{The Jefferson City News-Tribune}
\item
  \href{https://www.johnsoncitypress.com/}{The Johnson City Press}
\item
  \href{https://www.journalgazette.net/}{The Journal Gazette}
\item
  \href{https://www.journalinquirer.com/}{The Journal Inquirer}
\item
  \href{https://www.lohud.com/}{The Journal News}
\item
  \href{https://www.journalreview.com/}{The Journal Review}
\item
  \href{https://journaltimes.com/}{Journal-Times}
\item
  \href{https://www.kansascity.com/}{The Kansas City Star}
\item
  \href{https://www.myeasternshoremd.com/qa/bay_times/}{The Kent Island
  Bay Times}
\item
  \href{https://www.jconline.com/}{The Lafayette Journal \& Courier}
\item
  \href{https://www.lansingstatejournal.com/}{The Lansing State Journal}
\item
  \href{https://www.reviewjournal.com/}{The Las Vegas Review-Journal}
\item
  \href{https://www.ledger-enquirer.com/}{The Ledger-Enquirer}
\item
  \href{https://lmtribune.com/}{The Lewiston Morning Tribune}
\item
  \href{https://www.kentucky.com/}{The Lexington Herald-Leader}
\item
  \href{https://www.news-journal.com/}{The Longview News-Journal}
\item
  \href{https://www.latimes.com/}{The Los Angeles Times}
\item
  \href{https://www.lubbockonline.com/}{The Lubbock Avalanche-Journal}
\item
  \href{https://lynnwoodtoday.com/}{Lynnwood Today}
\item
  \href{https://www.mansfieldnewsjournal.com/}{The Mansfield News
  Journal}
\item
  \href{https://www.mdjonline.com/}{The Marietta Daily Journal}
\item
  \href{https://www.marketwatch.com/}{MarketWatch}
\item
  \href{https://www.marshallnewsmessenger.com/}{The Marshall News
  Messenger}
\item
  \href{https://www.somdnews.com/independent/}{The Maryland Independent}
\item
  \href{https://www.messenger-inquirer.com/}{The Messenger-Inquirer}
\item
  \href{https://www.miamiherald.com/}{The Miami Herald}
\item
  \href{https://www.northjersey.com/local/montclair/}{The Montclair
  Times}
\item
  \href{https://www.mooresvilletribune.com/}{The Mooresville Tribune}
\item
  \href{https://www.mcall.com/}{The Morning Call}
\item
  \href{http://www.morning-times.com/}{The Morning Times}
\item
  \href{https://dnews.com/}{The Moscow-Pullman Daily News}
\item
  \href{https://www.motherjones.com/}{Mother Jones}
\item
  \href{https://dailyvoice.com/new-york/mtkisco/}{The Mt. Kisco Daily
  Voice}
\item
  \href{https://muscatinejournal.com/}{The Muscatine Journal}
\item
  \href{https://www.liherald.com/fivetowns/}{The Nassau Herald}
\item
  \href{https://navajotimes.com/}{The Navajo Times}
\item
  \href{https://www.unionleader.com/}{The New Hampshire Union Leader}
\item
  \href{https://www.nhregister.com/}{The New Haven Register}
\item
  \href{https://www.nytimes.com/}{The New York Times}
\item
  \href{https://times-herald.com/}{The Newnan Times-Herald}
\item
  \href{https://www.newsobserver.com/}{The News \& Observer}
\item
  \href{https://www.greensboro.com/}{The News \& Record}
\item
  \href{https://www.morganton.com/}{The News Herald}
\item
  \href{https://www.delawareonline.com/}{The News Journal}
\item
  \href{https://www.thenewsenterprise.com/}{The News-Enterprise}
\item
  \href{https://www.news-press.com/}{The News-Press}
\item
  \href{https://www.thenewsstar.com/}{The News-Star}
\item
  \href{https://www.newstimes.com/}{The News-Times}
\item
  \href{https://www.newsday.com/}{Newsday}
\item
  \href{https://www.niagara-gazette.com/}{The Niagara Gazette}
\item
  \href{https://www.nptelegraph.com/}{The North Platte Telegraph}
\item
  \href{http://northernvalleysuburbanite.newspaperdirect.com/epaper/viewer.aspx?newspaper=northern+valley+suburbanite+-+north+edition\&cid=7705\&google=1}{The
  Northern Valley Suburbanite}
\item
  \href{https://www.nwherald.com/}{The Northwest Herald}
\item
  \href{http://nutleysun.newspaperdirect.com/epaper/viewer.aspx?newspaper=nutley+sun\&cid=7704\&google=1}{The
  Nutley Sun}
\item
  \href{https://obittree.com/}{ObitTree}
\item
  \href{https://www.hometownlife.com/}{The Observer \& Eccentric
  Newspapers}
\item
  \href{https://observer-reporter.com/}{The Observer-Reporter}
\item
  \href{https://www.odmp.org/}{The Officer Down Memorial Page}
\item
  \href{https://www.oanow.com/}{The Opelika-Auburn News}
\item
  \href{https://www.ocregister.com/}{The Orange County Register}
\item
  \href{https://www.oregonlive.com/}{The Oregonian}
\item
  \href{https://www.orlandosentinel.com/}{The Orlando Sentinel}
\item
  \href{https://www.ourtimepress.com/}{Our Time Press}
\item
  \href{https://www.gmtoday.com/}{The Ozaukee County News Graphic}
\item
  \href{https://www.pacificcitizen.org/}{The Pacific Citizen}
\item
  \href{https://www.palmbeachpost.com/}{The Palm Beach Post}
\item
  \href{https://www.patriotledger.com/}{The Patriot Ledger}
\item
  \href{https://www.pennlive.com/perry-county-times/}{The Perry County
  Times}
\item
  The Philadelphia Daily News
\item
  \href{https://www.inquirer.com/}{The Philadelphia Inquirer}
\item
  \href{https://www.phillytrib.com/}{The Philadelphia Tribune}
\item
  The Pilot
\item
  \href{https://www.post-gazette.com/}{The Pittsburgh Post-Gazette}
\item
  \href{https://www.plaindealer.com/}{The Plain Dealer}
\item
  \href{https://www.pressherald.com/}{The Portland Press Herald}
\item
  \href{https://www.seacoastonline.com/portsmouthherald}{The Portsmouth
  Herald}
\item
  \href{https://www.postandcourier.com/}{The Post and Courier}
\item
  \href{https://www.postcrescent.com/}{The Post-Crescent}
\item
  \href{https://www.syracuse.com/poststandard/}{The Post-Standard}
\item
  \href{https://www.poughkeepsiejournal.com/}{The Poughkeepsie Journal}
\item
  \href{https://www.pressconnects.com/}{The Press \& Sun-Bulletin}
\item
  \href{https://www.pressofatlanticcity.com/}{The Press of Atlantic
  City}
\item
  \href{https://www.pe.com/}{The Press-Enterprise}
\item
  \href{https://www.al.com/mobile/}{The Press-Register}
\item
  \href{https://www.pressrepublican.com/}{The Press-Republican}
\item
  \href{https://rapidcityjournal.com/}{The Rapid City Journal}
\item
  \href{https://www.readingeagle.com/}{The Reading Eagle}
\item
  \href{https://www.northjersey.com/}{The Record}
\item
  \href{https://www.myrecordjournal.com/}{The Record-Journal}
\item
  \href{https://dailyreporter.com/}{The Reporter}
\item
  \href{https://www.cantonrep.com/}{The Repository}
\item
  \href{http://www.therepublic.com/}{The Republic}
\item
  \href{https://springfieldrepublican-ma.newsmemory.com/}{The
  Republican}
\item
  \href{https://www.richmond.com/}{The Richmond Times-Dispatch}
\item
  \href{https://rbj.net/}{The Rochester Business Journal}
\item
  \href{https://www.rockdalenewtoncitizen.com/}{The Rockdale Citizen}
\item
  \href{https://www.liherald.com/rockvillecentre/}{The Rockville Centre
  Herald}
\item
  \href{https://www.northwestgeorgianews.com/rome/}{The Rome News
  Tribune}
\item
  \href{https://www.rushvillerepublican.com/}{The Rushville Republican}
\item
  \href{https://www.rutlandherald.com/}{The Rutland Herald}
\item
  \href{https://www.sacbee.com/}{The Sacramento Bee}
\item
  \href{https://www.salemnews.com/}{The Salem News}
\item
  \href{https://www.mysanantonio.com/}{The San Antonio Express-News}
\item
  \href{https://www.sandiegouniontribune.com/}{The San Diego
  Union-Tribune}
\item
  \href{https://www.sfchronicle.com/}{The San Francisco Chronicle}
\item
  \href{https://www.smdailyjournal.com/}{The San Mateo Daily Journal}
\item
  \href{https://sanduskyregister.com/}{The Sandusky Register}
\item
  \href{https://www.sctonline.net/}{The Scott County Times}
\item
  \href{https://www.seattletimes.com/}{The Seattle Times}
\item
  \href{https://www.sentinelandenterprise.com/}{The Sentinel and
  Enterprise}
\item
  \href{https://www.sent-trib.com/}{The Sentinel-Tribune}
\item
  \href{https://www.sheboyganpress.com/}{The Sheboygan Press}
\item
  \href{https://www.shreveporttimes.com/}{The Shreveport Times}
\item
  \href{https://www.singtaousa.com/}{The Sing Tao Daily}
\item
  \href{https://siouxcityjournal.com/}{The Sioux City Journal}
\item
  \href{https://www.siskiyoudaily.com/}{The Siskiyou Daily News}
\item
  \href{https://www.sonomanews.com/}{The Sonoma Index-Tribune}
\item
  \href{https://www.sun-sentinel.com/}{The South Florida Sun-Sentinel}
\item
  \href{https://www.spectator.co.uk/}{The Spectator}
\item
  \href{https://www.samessenger.com/}{The St. Albans Messenger}
\item
  \href{https://www.twincities.com/}{The St. Paul Pioneer Press}
\item
  \href{https://www.stamfordadvocate.com/}{The Stamford Advocate}
\item
  \href{https://www.standardspeaker.com/}{The Standard-Speaker}
\item
  \href{https://www.thesnaponline.com/}{The Stanly News and Press}
\item
  \href{https://www.startribune.com/}{The Star Tribune}
\item
  \href{https://www.nj.com/starledger/}{The Star-Ledger}
\item
  \href{https://www.thestate.com/}{The State}
\item
  \href{https://www.sj-r.com/}{The State Journal-Register}
\item
  \href{https://www.silive.com/}{The Staten Island Advance}
\item
  \href{https://www.statesmanjournal.com/}{The Statesman Journal}
\item
  \href{https://www.lowellsun.com/}{The Sun}
\item
  \href{https://www.thesunchronicle.com/}{The Sun Chronicle}
\item
  The Sunday Star
\item
  \href{https://dailyvoice.com/new-york/tarrytown/}{The Tarrytown-Sleepy
  Hollow Daily Voice}
\item
  \href{https://www.telegram.com/}{The Telegram \& Gazette}
\item
  \href{https://www.telegraphherald.com/}{The Telegraph Herald}
\item
  \href{https://www.thetimesherald.com/}{The Times Herald}
\item
  \href{https://www.timesunion.com/}{The Times Union}
\item
  \href{https://www.hoosiertimes.com/tmnews/}{The Times-Mail}
\item
  \href{https://www.nola.com/}{The Times-Picayune}
\item
  \href{https://www.tri-cityherald.com/}{The Tri-City Herald}
\item
  \href{https://www.tribstar.com/}{The Tribune-Star}
\item
  \href{https://www.tulsaworld.com/}{The Tulsa World}
\item
  \href{https://www.liherald.com/valleystream/}{The Valley Stream
  Herald}
\item
  \href{https://variety.com/}{Variety}
\item
  \href{https://www.vcstar.com/}{The Ventura County Star}
\item
  \href{https://www.vermiliontoday.com/}{Vermilion Today}
\item
  \href{https://www.pilotonline.com/}{The Virginian Pilot}
\item
  \href{https://www.visaliatimesdelta.com/}{The Visalia Times-Delta}
\item
  \href{https://www.wsj.com/}{The Wall Street Journal}
\item
  \href{https://www.washingtonpost.com/}{The Washington Post}
\item
  \href{https://wcfcourier.com/}{The Waterloo-Cedar Falls Courier}
\item
  \href{https://www.waxahachietx.com/}{The Waxahachie Daily Light}
\end{itemize}

Daily death data is from
\href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html}{a
New York Times database} of reports from state and local health
agencies.

By \href{https://www.nytimes.com/by/dan-barry}{Dan Barry},
\href{https://www.nytimes.com/by/larry-buchanan}{Larry Buchanan},
Clinton Cargill, \href{https://www.nytimes.com/by/annie-daniel}{Annie
Daniel}, Alain Delaquérière,
\href{https://www.nytimes.com/by/lazaro-gamio}{Lazaro Gamio}, Gabriel
Gianordoli, \href{https://www.nytimes.com/by/rich-harris}{Rich Harris},
Barbara Harvey, \href{https://www.nytimes.com/by/john-haskins}{John
Haskins}, \href{https://www.nytimes.com/by/jon-huang}{Jon Huang}, Simone
Landon, Juliette Love, Grace Maalouf, Alex Leeds Matthews, Farah
Mohamed, Steven Moity, Destinée-Charisse Royal,
\href{https://www.nytimes.com/by/matt-ruby}{Matt Ruby} and
\href{https://www.nytimes.com/by/eden-weingart}{Eden Weingart}.

Additional research by Yuriria Avila, Nicholas Bogel-Burroughs, Penn
Bullock, Sophia June,
\href{https://www.nytimes.com/by/lauren-leatherby}{Lauren Leatherby},
Alex Lemonides, \href{https://www.nytimes.com/by/denise-lu}{Denise Lu},
Aimee Ortiz, \href{https://www.nytimes.com/by/anjali-singhvi}{Anjali
Singhvi} and Chi Zhang. Additional editing by
\href{https://www.nytimes.com/by/jason-bailey}{Jason Bailey}, Eric Morse
and Alison Peterson.

\textbf{Auditor in Silicon Valley.} \emph{Patricia Dowd, 57, San Jose,
Calif.}

\textbf{Great-grandmother with an easy laugh.} \emph{Marion Krueger, 85,
Kirkland, Wash.}

\textbf{Wife with little time to enjoy a new marriage.} \emph{Jermaine
Ferro, 77, Lee County, Fla.}

\textbf{Sharecropper's son.} \emph{Cornelius Lawyer, 84, Bellevue,
Wash.}

\textbf{Cancer survivor born in the Philippines.} \emph{Loretta Mendoza
Dionisio, 68, Los Angeles}

\textbf{Former nurse.} \emph{Patricia Frieson, 61, Chicago}

\textbf{Ordained minister.} \emph{Merle C. Dry, 55, Tulsa, Okla.}

\textbf{Traveled often in the United States and Mexico.} \emph{Luis
Juarez, 54, Romeoville, Ill.}

\textbf{Bounce D.J. and radio personality.} \emph{Black N Mild, 44, New
Orleans}

\textbf{Vietnam veteran.} \emph{Michael Mika, 73, Chicago}

\textbf{Administered Holy Eucharist to hospital patients.} \emph{Donald
Raymond Haws, 88, Jacksonville, Fla.}

\textbf{Administrator at a nursing facility.} \emph{John Cofrancesco,
52, New Jersey}

\textbf{Conductor with ``the most amazing ear.''} \emph{Alan Lund, 81,
Washington}

\textbf{Preserver of the city's performance traditions.} \emph{Ronald W.
Lewis, 68, New Orleans}

\textbf{Loved to travel and covered much of the globe.} \emph{JoAnn
Stokes-Smith, 87, Charleston, S.C.}

\textbf{Liked his bacon and hash browns crispy.} \emph{Fred Walter Gray,
75, Benton County, Wash.}

\textbf{Member of a Franciscan monastery.} \emph{John-Sebastian
Laird-Hammond, 59, Washington, D.C.}

\textbf{Squeezed in every moment he could with his only grandchild.}
\emph{Carl Redd, 62, Chicago}

\textbf{Followed in his father's footsteps as a pipefitter.} \emph{Alvin
Elton, 56, Chicago}

\textbf{Jazz pianist, composer and educator.} \emph{Mike Longo, 83, New
York City}

\textbf{Educator and marathoner.} \emph{Arnold Obey, 73, San Juan, P.R.}

\textbf{Co-wrote nine books about computing.} \emph{Donald J. Horsfall,
72, Rydal, Pa.}

\textbf{Active in the AIDS Foundation.} \emph{Kevin Charles Patz, 64,
Seattle}

\textbf{Engineer behind the first 200-m.p.h. stock car.} \emph{Larry
Rathgeb, 90, West Bloomfield Hills, Mich.}

\textbf{Could make anything grow.} \emph{George Freeman Winfield, 72,
Shelburne, Vt.}

\textbf{Early woman on Wall Street and a World Bank official.}
\emph{Carole Brookins, 76, Palm Beach, Fla.}

\textbf{Ballroom dancing star.} \emph{Laneeka Barksdale, 47, Detroit}

\textbf{Innovative high school principal.} \emph{Dez-Ann Romain, 36, New
York City}

\textbf{College basketball assist wizard.} \emph{Dave Edwards, 48, New
York City}

\textbf{Former General Electric Co. executive.} \emph{Walter Robb, 91,
New York}

\textbf{Tony-winning playwright of gay life.} \emph{Terrence McNally,
81, Sarasota, Fla.}

\textbf{Unflappable New York Times journalist.} \emph{Alan Finder, 72,
Ridgewood, N.J.}

\textbf{Indian chef of fine dining.} \emph{Floyd Cardoz, 59, Montclair,
N.J.}

\textbf{Nurse in the Covid fight.} \emph{Kious Kelly, 48, New York City}

\textbf{Saved 56 Jewish families from the Gestapo.} \emph{Romi Cohn, 91,
New York City}

\textbf{Conducted clinical research at Walter Reed Army Medical Center.}
\emph{Harold L. Upjohn, 91, Burlingame, Calif.}

\textbf{Green Bay Packers season ticket holder for 50 years.}
\emph{Kenneth R. Going, 87, Grafton, Wis.}

\textbf{Renowned for her business making detailed pins and corsages.}
\emph{Theresa Elloie, 63, New Orleans}

\textbf{Developer known for his friendliness.} \emph{Sterling Maddox
Jr., 78, Arlington, Va.}

\textbf{School custodian and steppin' aficionado.} \emph{Joseph Graham,
67, Chicago}

\textbf{Played the saxophone at Denver's oldest jazz club for 40 years.}
\emph{Freddy Rodriguez Sr., 89, Denver}

\textbf{Never at a loss for words.} \emph{Christine McLaurin, 86,
Chicago}

\textbf{Loved reading, especially mystery novels.} \emph{Peggy
Rakestraw, 72, Matteson, Ill.}

\textbf{One of nine siblings.} \emph{Wanda Bailey, 63, Crete, Ill.}

\textbf{An exuberant laugh.} \emph{Frederick Carl Harris, 70,
Massachusetts}

\textbf{Navy man modest about his service in the Pacific.} \emph{Irvin
Herman, 94, Indianapolis}

\textbf{Caricaturist and psychiatrist who served his patients until the
end.} \emph{Ricardo Castaneda, 64, New York City}

\textbf{Obie Award-winning stage and screen actor.} \emph{Mark Blum, 69,
New York City}

\textbf{Radiologist, woodworker, artist and scholar.} \emph{Robert Earl
Schaefer, 87, Seattle}

\textbf{Avid observer and participant in South Carolina politics.}
\emph{John C. West Jr., 71, Camden, S.C.}

\textbf{An encyclopedic knowledge of old Hollywood.} \emph{Gerald
Anthony Morales, 91, Louisiana}

\textbf{Preacher and blues guitarist.} \emph{Landon Spradlin, 66,
Concord, N.C.}

\textbf{Organized food programs for children in the Philippines.}
\emph{Maria Linda Villanueva Sun, 61, Newport News, Va.}

\textbf{Reading tutor focused on student success.} \emph{Susan Rokus,
73, Hamilton, Va.}

\textbf{Ultimate entertainer.} \emph{Leroy Perryman Jr., 74, Hazel
Crest, Ill.}

\textbf{Devoured art in every medium.} \emph{Mary Virginia McKeon, 65,
Chicago}

\textbf{Could be a real jokester.} \emph{Roger Lehne, 93, Fargo, N.D.}

\textbf{Engineer forever chasing the wind.} \emph{Sandy Pratt, 92,
Bellevue, Wash.}

\textbf{Preceded in death by his wife of 65 years.} \emph{Rocco Patrick
Ursino, 90, Bellevue, Wash.}

\textbf{Champion of social justice through architecture.} \emph{Michael
Sorkin, 71, New York City}

\textbf{Proud single mother of three.} \emph{Louvenia Henderson, 44,
Tonawanda, N.Y.}

\textbf{Grandmother who was always full of ideas.} \emph{Lynne Sierra,
68, Roselle, Ill.}

\textbf{Coached several championship-winning junior high girls
basketball teams.} \emph{Huguette Dorsey, 94, Somerville, N.J.}

\textbf{Member of Del Amo Flyers.} \emph{Robert Manley Argo Jr., 75,
South Bay, Calif.}

\textbf{Loyal and generous friend to many.} \emph{Susan McPherson
Gottsegen, 74, Palm Beach, Fla.}

\textbf{Architect of Boston's monumental City Hall.} \emph{Michael
McKinnell, 84, Beverly, Mass.}

\textbf{Created many wonderful memories for his family.} \emph{Thomas E.
Anglin, 85, Cumming, Ga.}

\textbf{Trailblazer for TriBeCa.} \emph{Andreas Koutsoudakis, 59, New
York City}

\textbf{Leader in Florida Pride events.} \emph{Bob Barnum, 64, St.
Petersburg, Fla.}

\textbf{Nurse planning for retirement.} \emph{Noel Sinkiat, 64, Olney,
Md.}

\textbf{Lawyer who mentored others.} \emph{George Valentine, 66,
Washington, D.C.}

\textbf{Rebel of the family.} \emph{James Quigley, 77, Chicago}

\textbf{Dedicated his life to his church and his neighborhood.}
\emph{Sherman Pittman, 61, Chicago}

\textbf{Loved big and told people she loved them all the time.}
\emph{Minette Goff Cooper, 79, Louisiana}

\textbf{Was at peace on his Harley.} \emph{Thomas A. Real, 61, Newtown,
Pa.}

\textbf{Life of the party.} \emph{Julian Anguiano-Maya, 51, Chicago}

\textbf{Leaves behind many lifelong friends, including the Bunco Girls.}
\emph{Sandra Piotrowski, 77, Tinley Park, Ill.}

\textbf{Loved travel, mahjong and crossword puzzles.} \emph{Carol Sue
Rubin, 69, West Bloomfield, Mich.}

\textbf{Would use chalk and oil paints to capture family portraits.}
\emph{Marion Lucille Kujda, 92, Royal Oak, Mich.}

\textbf{Loving, generous and adventurous spirit.} \emph{Alice
Chavdarian, 92, Michigan}

\textbf{Saw friends at their worst but brought out their best.}
\emph{Bassey Offiong, 25, Michigan}

\textbf{A 33-year career with the Louisiana Department of
Transportation.} \emph{Bobby Joseph Hebert, 81, Cut Off, La.}

\textbf{Competitive athlete, up until his last years.} \emph{Robert
Rust, 88, Greensburg, Ind.}

\textbf{Immigrated to the United States three years ago.} \emph{Jéssica
Beatriz Cortez, 32, Los Angeles}

\textbf{Iconic figure in the Inwood community.} \emph{Marie Caronia, 84,
Inwood, N.Y.}

\textbf{Advocate for disability rights.} \emph{April Dunn, 33, Baton
Rouge, La.}

\textbf{Police detective in Harlem with a gift for interrogation.}
\emph{Cedric Dixon, 48, New York City}

\textbf{Sociologist who walked New York City.} \emph{William Helmreich,
74, Great Neck, N.Y.}

\textbf{Grew up directly across the street from the old Yankee Stadium.}
\emph{Harvey Bayard, 88, New York}

\textbf{Founded the Association for Chemoreception Sciences.}
\emph{Maxwell M. Mozell, 90, Syracuse, N.Y.}

\textbf{Active member of the South Carolina Progressive Network.}
\emph{Timothy J. Liszewski, 60, Columbia, S.C.}

\textbf{Veteran with a gift for peacemaking.} \emph{Eastern Stewart Jr.,
71, Annapolis, Md.}

\textbf{Nurse with a zest for travel and knowledge.} \emph{Freda Ocran,
51, New York City}

\textbf{Military's first virus casualty.} \emph{Douglas Hickok, 57,
Pennsylvania}

\textbf{Emigrated from Ukraine.} \emph{Luiza Ogorodnik, 84, Skokie,
Ill.}

\textbf{Passionate about retaining his town's small-town atmosphere.}
\emph{John Joseph Reed Jr., 74, Edmonds, Wash.}

\textbf{Former speaker of the Utah House, auto executive and
philanthropist.} \emph{Robert Garff, 77, Utah}

\textbf{His Walmart co-workers were like family.} \emph{Phillip Thomas,
48, Chicago}

\textbf{Relished his role as a mentor.} \emph{Melvin Pumphrey, 80,
Chicago Heights, Ill.}

\textbf{Assistant pastor.} \emph{Angel Escamilla, 67, Naperville, Ill.}

\textbf{Her hospitality was known throughout Toole County and beyond.}
\emph{Marguerite M. Horgus, 86, Sweetgrass, Mont.}

\textbf{Represented theatrical, TV and movie personalities.}
\emph{Joseph Micajah Thomas II, 88, New York City}

\textbf{Actress and children's TV host.} \emph{Beryl Bernay, 94, New
York City}

\textbf{Songwriter of ``I Love Rock 'n' Roll.''} \emph{Alan Merrill, 69,
New York City}

\textbf{Pioneer in the promotional products industry.} \emph{Sidney
Siegel, 92, Woodbury, N.Y.}

\textbf{A long career in the import-export business.} \emph{Robert M.
Weintraub, 96, New York}

\textbf{Grammy-winning country music star.} \emph{Joe Diffie, 61,
Nashville}

\textbf{Retired architect always eager to travel.} \emph{Herman Boehm,
86, Florida}

\textbf{Tailor.} \emph{Horace Saunders, 96, Mount Airy, Md.}

\textbf{Retired firefighter.} \emph{Gary Holmberg, 77, Mount Airy, Md.}

\textbf{I.T. project manager remembered for his love of trivia.}
\emph{Chad Capule, 49, Fond du Lac, Wis.}

\textbf{Loved taking care of people.} \emph{Sandra Lee deBlecourt, 61,
Maryland}

\textbf{Husband and father.} \emph{Jose Vazquez, 51, Chicago}

\textbf{Ran an animal hospital.} \emph{Peter Sakas, 67, Northbrook,
Ill.}

\textbf{Made time to create and listen to music.} \emph{Alberto Castro,
86, Melrose Park, Ill.}

\textbf{Mentor and friend to many.} \emph{Joseph Yaggi, 65, Indiana}

\textbf{Shot-put champion and fixture in local politics.} \emph{Mary
Roman, 84, Norwalk, Conn.}

\textbf{Transgender immigrant activist.} \emph{Lorena Borjas, 59, New
York City}

\textbf{Surgeon who separated conjoined twins.} \emph{James T. Goodrich,
73, New York City}

\textbf{Founded a food pantry.} \emph{Janice Preschel, 60, Teaneck,
N.J.}

\textbf{Always rode Harley-Davidsons.} \emph{Jean-Claude Henrion, 72,
Atlantis, Fla.}

\textbf{Retired meter-reader.} \emph{Joseph J. Deren Jr., 75, Turners
Falls, Mass.}

\textbf{Owner of Shamrock Salvage \& Appraisal Inc.} \emph{Gerald
Cassidy, 66, Peachtree Corners, Ga.}

\textbf{Retired from the U.S. Customs Agency after 28 years.}
\emph{David Reissig, 82, Vermont}

\textbf{Known for serenading friends with Tony Bennett songs.}
\emph{Angelo Piro, 87, New York City}

\textbf{Retired firefighter and old-school barber.} \emph{Roger Eckart,
78, Indiana}

\textbf{Mentor to other Memphis artists.} \emph{Daniel Spector, 68,
Memphis}

\textbf{Lead singer of a Yiddish folk group.} \emph{Alby Kass, 89,
California}

\textbf{Jazz trumpet virtuoso.} \emph{Wallace Roney, 59, Paterson, N.J.}

\textbf{Maestro of a steel-pan band.} \emph{Martin Douglas, 71, New York
City}

\textbf{Beloved public school teacher.} \emph{Sandra Santos-Vizcaino,
54, New York City}

\textbf{Downtown New York singer with a cult following.} \emph{Cristina,
64, New York City}

\textbf{Statesman in the construction industry.} \emph{Robert H.
Westphal, 75, Fond du Lac, Wis.}

\textbf{Pilot still teaching people to fly at 88.} \emph{Clair Dunlap,
89, Washington}

\textbf{Veteran police detective.} \emph{Marylou Armer, 43, Sonoma
Valley, Calif.}

\textbf{Small in stature but strong in spirit.} \emph{Regina D. Cullen,
81, Shrewsbury, Mass.}

\textbf{Retired police sergeant.} \emph{Jerry Manley, 58, Prince
Frederick, Md.}

\textbf{Emergency room doctor who died in husband's arms.} \emph{Frank
Gabrin, 60, New York City}

\textbf{Cancer survivor who served as a deacon.} \emph{Sterling E.
Matthews, 60, Midlothian, Va.}

\textbf{Famous in family circles for his birria beef stew.} \emph{Jesus
Roman Melendez, 49, New York}

\textbf{``we called him the Grand Poobah.''} \emph{Ralph Plaisance, 87,
Massapequa, N.Y.}

\textbf{Sang gospel music as a member of the Malone Sisters.}
\emph{Audrey Malone, 68, Chicago}

\textbf{Sign-language interpreter.} \emph{Mary Minervini, 91, Oak Lawn,
Ill.}

\textbf{Loved to figure out how things worked.} \emph{Salomon S.
Podgursky, 84, Morristown, N.J.}

\textbf{Tailor known for his exacting work and strong opinions.}
\emph{Dale E. Thurman, 65, Lexington, Ky.}

\textbf{Jazz pianist and patriarch of a family of musicians.}
\emph{Ellis Marsalis, 85, New Orleans}

\textbf{Rocket engineer in the early days of supersonic flight.}
\emph{Richard Passman, 94, Silver Spring, Md.}

\textbf{Champion of African-American art.} \emph{David Driskell, 88,
Hyattsville, Md.}

\textbf{Master of jazz guitar.} \emph{Bucky Pizzarelli, 94, Saddle
River, N.J.}

\textbf{Belfast-born fighter for L.B.G.T. and disability rights.}
\emph{Tarlach MacNiallais, 57, New York City}

\textbf{Social worker.} \emph{Antonio Checo, 67, New York City}

\textbf{Fire chief who answered the call on 9/11.} \emph{Albert
Petrocelli, 73, New York City}

\textbf{Songwriter for rock, film and the stage.} \emph{Adam
Schlesinger, 52, Poughkeepsie, N.Y.}

\textbf{Liked the mental challenges of business.} \emph{Frederick Brown
Starr, 87, Greensboro, N.C.}

\textbf{Authority on aviation.} \emph{Douglas Alan Roberts, 69,
Vancouver, Wash.}

\textbf{Taught her girls sheepshead and canasta.} \emph{Muriel M. Going,
92, Cedarburg, Wis.}

\textbf{Longtime registered nurse and hospital volunteer.} \emph{Beverly
Collins, 83, Portland, Maine}

\textbf{Worked as an engineer with Comcast.} \emph{Scott Melter, 60,
Wyoming, Minn.}

\textbf{One-man army.} \emph{Florencio Almazo Morán, 65, New York City}

\textbf{Broadway costume dresser.} \emph{Jennifer Robin Arnold, 67, New
York City}

\textbf{Coach and Scout leader.} \emph{John Nakawatase, 62, Lincolnwood,
Ill.}

\textbf{Mom to six sons.} \emph{Norma Hoza, 101, Wilmette, Ill.}

\textbf{Dubbed the ``pistol-packing preacher.''} \emph{Lucius Hall, 87,
Chicago}

\textbf{Original member of the Navy's elite Underwater Demolition Team.}
\emph{Harold L. Hayes, 96, Fort Wright, Ky.}

\textbf{Father figure.} \emph{Terrence George Driscoll, 87, Plymouth,
Mich.}

\textbf{Town councilman.} \emph{Glenn Daniel Bellitto, 62, New York}

\textbf{Always wanted to be near the ocean.} \emph{Ronnie Estes, 73,
Stevensville, Md.}

\textbf{Marketing expert who brought exotic foods to green grocers.}
\emph{Anita Fial, 87, New York City}

\textbf{Actress who wrote biographies of famous friends.} \emph{Patricia
Bosworth, 86, New York City}

\textbf{Two-time cancer survivor.} \emph{Azade Kilic, 69, New York}

\textbf{Honored to march with the American Legion in many parades.}
\emph{John E. Broadly, 84, Scituate, Mass.}

\textbf{Taught math, English and history for over 30 years.} \emph{Julia
Maye Alexander, 81, Upland, Calif.}

\textbf{Found his special place at Big Bowman Pond.} \emph{Bruce W.
Sowalski, 68, Sand Lake, N.Y.}

\textbf{Congregation's founding member.} \emph{Samuel Kramer, 91,
Potomac, Md.}

\textbf{Pharmacy manager with young daughters.} \emph{Sean Boynes, 46,
Annapolis, Md.}

\textbf{True community activist.} \emph{Nancy Ferguson, 77, Chicago}

\textbf{Police officer who was never at a loss for words.} \emph{Marco
DiFranco, 50, Chicago}

\textbf{True outdoorsman.} \emph{John A. Bailargeon, 72, Dennisport,
Mass.}

\textbf{Known for her Greek chicken and stuffed peppers.} \emph{Helen
Kafkis, 91, Chicago}

\textbf{Entrepreneur and adventurer.} \emph{Coby Adolph, 44, Chicago}

\textbf{Noted voiceover artist for radio and TV.} \emph{Judith
Plotkin-Goldberg, 88, Massachusetts}

\textbf{Inveterate harmonica player.} \emph{Lloyd Paul Leftwich, 91,
Louisiana}

\textbf{Proud Union Ironworker of Local 7 for 45 years.} \emph{Chester
Dwulet, 68, Burlington, Mass.}

\textbf{Loved creating perfect smiles.} \emph{Steven J. Huber, 64,
Jefferson City, Mo.}

\textbf{Sports fan who loved Purdue University.} \emph{Don Whan, 67,
Indiana}

\textbf{Executive behind New York Philharmonic's economic growth.}
\emph{Albert K. Webster, 82, New York City}

\textbf{Joined Goldman Sachs in 1975.} \emph{Kevin Masterson, 74, New
York City}

\textbf{Survived being shot in the line of duty in 1984.} \emph{Randy G.
Addison, 64, Carrollton, Ga.}

\textbf{Proud to have logged over five million miles behind the wheel.}
\emph{Ronald Willenkamp, 75, Wisconsin}

\textbf{Expert marksman and firearms instructor.} \emph{Robert Lee Amos,
66, Columbus, Ind.}

\textbf{All-around supporter of the Washington Huskies.} \emph{Helen
Molina, 85, Washington}

\textbf{Helped countless people by providing housing and support.}
\emph{Ronald Burdette Culp, 84, Redding, Calif.}

\textbf{Shared his produce with food pantries and his neighbors.}
\emph{Norman Walker Jr., 80, China Township, Mich.}

\textbf{Former aerospace engineering professor at Howard University.}
\emph{Peter Bainum, 82, Bethesda, Md.}

\textbf{Worker at O'Hare International Airport.} \emph{Viraf
Darukhanawalla, 77, Hoffman Estates, Ill.}

\textbf{Part of a tightknit family.} \emph{Lula Fitzpatrick, 85, Dolton,
Ill.}

\textbf{Retired therapist and mentor.} \emph{Charles Miles, 72, Chatham,
Ill.}

\textbf{Leader in integrating schools.} \emph{Ann Kolb, 78, New York
City}

\textbf{Always seemed to be busy with some home project.} \emph{Antonio
Nieves, 73, Chicago}

\textbf{First in her family to graduate college.} \emph{Rhoda Hatch, 73,
Chicago}

\textbf{Stalwart church gospel singer.} \emph{Regina Dix-Parsons, 75,
Schenectady, N.Y.}

\textbf{Trustee for the Retired Detroit Police and Firefighters
Association.} \emph{John Timothy Barr, 76, Rochester Hills, Mich.}

\textbf{Veterinarian who served Harlem.} \emph{Julie Butler, 62, New
York City}

\textbf{First black woman to graduate from Harvard Law School.}
\emph{Lila A. Fenwick, 87, New York City}

\textbf{Met Opera violist and youth orchestra conductor.} \emph{Vincent
Lionti, 60, New York City}

\textbf{Had a passion for social justice.} \emph{Ann Youngerman Smoler,
87, New York City}

\textbf{Armed the affordable housing movement with data and analysis.}
\emph{Thomas Waters, 56, New York City}

\textbf{His relentless passion was for his family and friends.}
\emph{Luke Workoff, 33, Huntington, N.Y.}

\textbf{Served with the Palm Beach County Sheriff's Office for 14
years.} \emph{José Díaz- Ayala, 38, Palm Beach, Fla.}

\textbf{Was helping to raise some of her dozen grandchildren.}
\emph{Lakisha Willis White, 45, Orlando, Fla.}

\textbf{Received numerous awards for her accounting skills.}
\emph{Jeanne Hammond Byrnes, 97, Danbury, Conn.}

\textbf{In the first class of girls admitted to the Bronx High School of
Science.} \emph{Alice Coopersmith Furst, 87, Kentfield, Calif.}

\textbf{Seahawks season-ticket holder.} \emph{Bobby Lee Barber, 84,
Buckley, Wash.}

\textbf{Especially proud of his Lithuanian heritage.} \emph{Thomas A.
Adamavich, 78, Sheboygan, Wis.}

\textbf{Volunteered for pet rescue organizations.} \emph{Kyra Swartz,
33, New York}

\textbf{Loved the Jersey Shore music scene.} \emph{Allan Joseph Dickson
Jr., 67, New Jersey}

\textbf{Family jokester.} \emph{John Cassano, 70, Palos Park, Ill.}

\textbf{She was known to many as Babs.} \emph{Barbara Yazbeck Vethacke,
74, St. Clair Shores, Mich.}

\textbf{Loved automobiles, especially trucks.} \emph{Eugene Lamar
Limbrick, 41, Colorado Springs}

\textbf{No one made creamed potatoes or fried sweet corn the way she
did.} \emph{June Beverly Hill, 85, Sacramento}

\textbf{Writer who inspired her Brooklyn high school students.}
\emph{Kimarlee Nguyen, 33, Everett, Mass.}

\textbf{Hotel banquet worker and Bangladeshi leader.} \emph{Kamal Ahmed,
69, New York City}

\textbf{Sanitation worker living his fullest days.} \emph{Raymond
Copeland, 46, New York City}

\textbf{New father.} \emph{Israel Sauz, 22, Broken Arrow, Okla.}

\textbf{Worked for over six decades in the wine and liquor industry.}
\emph{Lester Eber, 82, New York}

\textbf{Loved the ocean and enjoyed swimming and boating.} \emph{Harry
P. Misthos, 87, San Francisco Bay Area, Calif.}

\textbf{Preferred bolo ties to neckties, suspenders to belts.} \emph{Leo
Sreebny, 98, Seattle}

\textbf{Could fix almost anything.} \emph{Robert Barghaan, 88, New York
City}

\textbf{Sang in her church choir for 42 years.} \emph{Patricia H.
Thatcher, 79, Clifton Park, N.Y.}

\textbf{Strong advocate for health care policy.} \emph{Howard Alexander
Nelson Jr., 84, New Orleans}

\textbf{Unwavering faith and dedication to the Catholic Church.}
\emph{Elizabeth Batista, 57, Waterbury, Conn.}

\textbf{Nicknamed ``Boxcar Bob'' for his luck in shaking dice.}
\emph{Robert L. Crahen, 87, Waunakee, Wis.}

\textbf{Always busy looking out for others.} \emph{Timothy Branscomb,
32, Chicago}

\textbf{Known as ``Big Wolf'' to the basketball players he coached.}
\emph{Jim J. Wolf Sr., 72, South Holland, Ill.}

\textbf{Worked in construction and served in the Army.} \emph{Robert
LeBlanc, 87, Cambridge, Mass.}

\textbf{Widely surmised he could have played Major League Baseball.}
\emph{Paul Warech, 86, Vineland, N.J.}

\textbf{Candy striper at St. Raphael's Hospital.} \emph{Antoinette Marie
Lutz, 91, Chester, Conn.}

\textbf{Owned Frainee Water Trucks for 44 years.} \emph{Vincent G.
Frainee, 68, Redlands, Calif.}

\textbf{A heart of service.} \emph{Andrew Kowalczyk, 63, Coral Gables,
Fla.}

\textbf{Social worker who dedicated her life to others.} \emph{Jana
Prince, 43, Gretna, La.}

\textbf{Fourth-generation owner of Mario's restaurant, a Bronx
institution.} \emph{Joseph Migliucci, 81, White Plains, N.Y.}

\textbf{Founded Strategy Associates.} \emph{Reuben Gutoff, 92, New York
City}

\textbf{Retired New York Supreme Court justice.} \emph{Gerard Rosenberg,
85, New York City}

\textbf{Loved to referee basketball games.} \emph{Marty Derer, 56, New
Jersey}

\textbf{Took furniture repair to the level of an art form.} \emph{Harold
Reisner, 78, Pittsburgh}

\textbf{Well known in the world of agility dog training.} \emph{Clark
Osojnicki, 56, Stillwater, Minn.}

\textbf{Directed Alba House Cornerstone Bookstore in lower Manhattan.}
\emph{Kevin John Cahill, 83, New York City}

\textbf{Known for having a smile on her face.} \emph{Janissa Delacruz,
31, Haverstraw, N.Y.}

\textbf{Member for over 46 years of the Operating Engineers Union, Local
No. 106.} \emph{Clifford J. Williams, 81, Schaghticoke, N.Y.}

\textbf{Pastor of Mt. Sinai Church of God in Christ.} \emph{James
O'Brien Johnson, 74, Joplin, Mo.}

\textbf{Stopped working to look after his aging parents.} \emph{Joseph
W. Hammond, 64, Chicago}

\textbf{Endlessly curious, never really finished.} \emph{Morris Loeb,
90, Northbrook, Ill.}

\textbf{People were her hobby.} \emph{Mari Jo Davitto, 82, Thornton,
Ill.}

\textbf{Bus driver and school security guard.} \emph{Marlon Alston, 46,
Chicago}

\textbf{Gentle giant, athlete and musician.} \emph{Torrin Jamal Howard,
26, Waterbury, Conn.}

\textbf{Volunteered his time to church car raffles, fund-raisers and
picnics.} \emph{James V. Walsh, 78, New Jersey}

\textbf{Immigrated to New York from a German refugee camp after World
War II.} \emph{Liudas Karolis Mikalonis, 86, Berkley, Mich.}

\textbf{Fierce advocate for educational opportunity.} \emph{Gene Zahas,
78, Oakland, Calif.}

\textbf{Thought it was important to know a person's life story.}
\emph{William D. Greeke, 55, Massachusetts}

\textbf{Her size belied her strength and spirit.} \emph{Beatrice Rubin,
96, New Jersey}

\textbf{Lived in the house he grew up in.} \emph{Jack Butler, 78,
Indiana}

\textbf{Took great joy in writing little ditties under her pen name,
Penelope Penwiper.} \emph{Susan Grey Hopp Crofoot, 97, Westwood, N.J.}

\textbf{Spent some of his happiest hours hiking in the Adirondacks.}
\emph{James David Gewirtzman, 72, New City, N.Y.}

\textbf{Columbia University historian of U.S. presidents.} \emph{Henry
F. Graff, 98, Greenwich, Conn.}

\textbf{Budding therapist with a gift for empathy.} \emph{Hailey
Herrera, 25, New York City}

\textbf{Leader of the Novominsker Hasidic dynasty.} \emph{Yaakov Perlow,
89, New York City}

\textbf{Did two tours through the Panama Canal to Antarctica.}
\emph{Joseph F. Kelly, 81, New York City}

\textbf{Country-folk singer who was a favorite of Bob Dylan.} \emph{John
Prine, 73, Nashville}

\textbf{Quiet hero.} \emph{Perry Buchalter, 63, Florida}

\textbf{Loved animals, had dogs and cats, and rode horses.} \emph{Monica
Maley, 74, Rehoboth Beach, Del.}

\textbf{Mentored by the computer science pioneer Grace Hopper.}
\emph{Thomas Tarbell Russell, 83, Longmeadow, Mass.}

\textbf{Backyard birds were known to eat from her hand.} \emph{Ruth
Skapinok, 85, Roseville, Calif.}

\textbf{Her favorite thing was meeting new people.} \emph{Faralyn Havir,
92, Minnesota}

\textbf{Chicago firefighter.} \emph{Mario Araujo, 49, Chicago}

\textbf{Featured in multiple Broadway productions.} \emph{Ilona Murai
Kerman, 96, New York}

\textbf{Sang her grandchildren a song on the first day of school each
year.} \emph{Clara Louise Bennett, 91, Albany, Ga.}

\textbf{Worked mostly factory jobs to support his family.} \emph{Peter
Kafkis, 91, Chicago}

\textbf{Longtime dentist.} \emph{Conrad Duncker, 99, Chicago}

\textbf{Moved antiques for more than 25 years.} \emph{Tommie Adams, 71,
Chicago}

\textbf{Teacher's aide.} \emph{Johnnie D. Veasley, 76, Country Club
Hills, Ill.}

\textbf{More adept than many knew.} \emph{Myra Helen Robinson, 57,
Detroit}

\textbf{Professor at the Salter School.} \emph{Roger Mckinney-Wagner,
73, Lowell, Mass.}

\textbf{Enjoyed talking sports with family.} \emph{Sean Christian
Keville, 47, New Providence, N.J.}

\textbf{One of the few African-American corporate bond traders on Wall
Street.} \emph{John Herman Clomax, Jr., 62, Newark}

\textbf{Restaurateur favored by salsa music's stars.} \emph{José Torres,
73, New York City}

\textbf{Brooklyn cabbie who found a home in Buddhism.} \emph{Stuart
Cohen, 73, New York City}

\textbf{His greatest accomplishment was his relationship with his wife.}
\emph{Dante Dennis Flagello, 62, Rome, Ga.}

\textbf{Member of the Literacy Volunteers of America.} \emph{Mary M.
Desole, 93, Poughkeepsie, N.Y.}

\textbf{Face behind the counter at a family-owned grocery store.}
\emph{Vera Flint, 97, Beverly, Mass.}

\textbf{First responder during the 9/11 attacks.} \emph{Mike Field, 59,
Valley Stream, N.Y.}

\textbf{Social worker and then a political fundraiser.} \emph{Chianti
Jackson Harpool, 51, Baltimore}

\textbf{Never drew attention to herself.} \emph{Marie Scanlan Walker,
99, Louisiana}

\textbf{Known as Big Momma to all who loved her.} \emph{Frances M.
Pilot, 81, Wall, N.J.}

\textbf{Called ``The Captain'' by friends and family.} \emph{George J.
Foerst Jr., 99, New Jersey}

\textbf{Wanted everyone to feel welcome.} \emph{Mauricio Valdivia, 52,
Chicago}

\textbf{Advocate for others with disabilities.} \emph{Robert Dugal, 58,
Oak Park, Ill.}

\textbf{Photographer, gourmet cook, sparkling hostess and traveler.}
\emph{Sharyn Lynn Vogel, 74, Aurora, Colo.}

\textbf{Helped drive the family car along Route 66.} \emph{Robert
Charles Bazzell, 88, Novi, Mich.}

\textbf{Deep-hearted country girl.} \emph{Claudia Obermiller, 73,
Nebraska}

\textbf{Republican freshman in the state Legislature.} \emph{Reggie
Bagala, 54, Lockport, La.}

\textbf{Man of faith and a proud Irish-American.} \emph{Richard Joseph
Lenihan Jr., 55, Pearl River, N.Y.}

\textbf{Made friends everywhere he went.} \emph{Deyrold Arteaga, 66,
Central Valley, N.Y.}

\textbf{Secretary to a New Jersey judge.} \emph{Estelle Kestenbaum, 91,
Leonia, N.J.}

\textbf{Opened a Los Angeles preschool.} \emph{Artemis Nazarian, 88,
Englewood Cliffs, N.J.}

\textbf{Freed from life in prison.} \emph{Myles Coker, 69, New York
City}

\textbf{Lifelong karate instructor.} \emph{Richard Alexander Ross Jr.,
66, Boynton Beach, Fla.}

\textbf{Made what she had work for her.} \emph{Helen Boles Days, 96,
Wynnewood, Pa.}

\textbf{He loved his wife and said, ``Yes, dear'' a lot.} \emph{Marcus
Edward Cooper Jr., 83, Louisiana}

\textbf{Veteran corrections officer and father of three.} \emph{Nelson
Perdomo, 44, Middlesex County, N.J.}

\textbf{Retired bank teller.} \emph{Rosemarie Amerosi, 87, New York
City}

\textbf{Worked for the Orange County Highway Department.} \emph{Timothy
H. Gray, 66, Orleans, Ind.}

\textbf{Security worker who died the same day as his wife.} \emph{Tommie
Brown, 82, Gary, Ind.}

\textbf{Died on the same day as her husband.} \emph{Doris Brown, 79,
Gary, Ind.}

\textbf{Caretaker of her neighborhood.} \emph{Arlola Rawls, 81, Chicago}

\textbf{Brought smiles to everyone he interacted with.} \emph{Roger
Liddell, 65, Flint, Mich.}

\textbf{Loved writing birthday and holiday cards, poems and lists.}
\emph{Denise Camille Buczek, 72, Bristol, Conn.}

\textbf{Lifelong pacifist.} \emph{John B. Ahrens, 96, Newton, Mass.}

\textbf{A decades-long career in ministry.} \emph{Parker Knoll, 68,
Indiana}

\textbf{Worked as a special education teacher for many years.}
\emph{Kerri Ann Kennedy-Tompkins, 48, Garrison, N.Y.}

\textbf{Former hairstylist and avid New York Yankees fan.}
\emph{Rosemarie Franzese, 70, Nevada}

\textbf{Math reader for Recordings for the Blind.} \emph{Bernard David
Seckler, 95, Newton, Mass.}

\textbf{Owner of Paris Blues, a beloved Harlem jazz joint.} \emph{Samuel
Hargress Jr., 84, New York City}

\textbf{Retired from Sears Outlet Stores as an assistant manager.}
\emph{Michael Lee Jordan, 69, McLeansville, N.C.}

\textbf{Nothing delighted him more than picking up the bill.}
\emph{Merrick Dowson, 67, San Francisco Bay Area, Calif.}

\textbf{Known for his knowledge of local history.} \emph{Wesley Richard
Fahrbach II, 69, Fremont, Ohio}

\textbf{Discovered his true calling when he started driving a school
bus.} \emph{Harley E. Acker, 79, Troupsburg, N.Y.}

\textbf{Loved to dance.} \emph{Josephine Posnanski, 98, New Jersey}

\textbf{Stockbroker who founded Doherty Financial Services.} \emph{Ben
Doherty, 83, Boston}

\textbf{Member of Harness Racing Hall of Fame.} \emph{Phil Langley, 83,
Frankfort, Ill.}

\textbf{Man who seemed to know everything.} \emph{Luther Coleman, 108,
Evergreen Park, Ill.}

\textbf{Excelled in the kitchen.} \emph{Doris Mae Burkhart Kale, 98,
Pennsylvania}

\textbf{Worked 40 years for The New York Times.} \emph{Charles
Constantino, 86, Menlo Park, N.J.}

\textbf{Mathematician known as the ``magical genius.''} \emph{John
Horton Conway, 82, New Brunswick, N.J.}

\textbf{Developer and friend of the president.} \emph{Stanley Chera, 77,
New York City}

\textbf{Realtor and philanthropist who socialized with celebrities.}
\emph{Robby Browne, 72, New York City}

\textbf{Acting teacher and a founder of the American Place Theater.}
\emph{Wynn Handman, 97, New York City}

\textbf{Cartoonist and an expert on musicals.} \emph{Adam Kovacs, 72,
New York City}

\textbf{Manager of the S.W. Brown \& Son Funeral Home.} \emph{Peter
Brown, 53, New Jersey}

\textbf{Great-grandmother with a flair for pizzelles.} \emph{Irene
Gasior, 94, Pennsylvania}

\textbf{Trombonist who once turned down an offer to join Duke
Ellington's orchestra.} \emph{Stanley L. Morse, 88, Stark County, Ohio}

\textbf{Had a mystic's direct sense of wonder and oneness.}
\emph{Margaret Laughlin, 91, Massachusetts}

\textbf{Retiree determined to spoil her granddaughter.} \emph{Cynthia
Whiting, 66, La Plata, Md.}

\textbf{I.T. manager with ``an eye for beautiful and unusual things.''}
\emph{Steve Joltin, 75, Rockville, Md.}

\textbf{Police officer turned pastor.} \emph{Gerald Glenn, 66, Richmond,
Va.}

\textbf{Inspiring math teacher.} \emph{Maclear Jacoby Jr., 93,
Washington, D.C.}

\textbf{``Mayor of Martin Avenue.''} \emph{Michael Giangrande Sr., 78,
Bellmore, N.Y.}

\textbf{Radio host and youth advocate.} \emph{Harold Davis Jr., 63,
Chicago}

\textbf{Collector of stamps and coins.} \emph{Alan A. Potanka, 68,
Berlin, Conn.}

\textbf{Would walk her children to school every morning.} \emph{Maria
Garcia-Rodelo, 52, Nevada}

\textbf{Left Peru and grabbed hold of the American dream.} \emph{Orlando
Moncada, 56, Bronxville, N.Y.}

\textbf{Graffiti artist with a generous spirit.} \emph{Fernando Miteff,
60, New York City}

\textbf{Anywhere he went, he took pictures.} \emph{John Watson, 73,
Philadelphia}

\textbf{Editor at the Ladies' Home Journal.} \emph{Joyce Posson Winston,
93, North Bergen, N.J.}

\textbf{Lifelong educator.} \emph{John B. Lynch, 76, Wilmington, Mass.}

\textbf{Co-owned the Bark-and-All logging company.} \emph{Vinton Timely
Mason, 86, Beaumont, Mich.}

\textbf{Volunteer youth football coach.} \emph{John Schoffstall, 41,
Terre Haute, Ind.}

\textbf{Photographer of the Freedom Riders.} \emph{Theodore Gaffney, 92,
Washington, D.C.}

\textbf{Staff member and mentor at the Milwaukee Rescue Mission.}
\emph{Billy Ross, 53, Milwaukee}

\textbf{Brought the family to church every week.} \emph{Michael Wrotniak
Jr., 92, Glen Cove, N.Y.}

\textbf{A million dollar-smile.} \emph{Marvin L. Thomas, 81, Sun Lakes,
Ariz.}

\textbf{Worked more than 30 years for General Motors.} \emph{Timothy
Ross, 68, Michigan}

\textbf{Active in her church.} \emph{Sherrell Stokes, 54, Chicago}

\textbf{Longtime high school referee.} \emph{Larry Jones, 61, Chicago}

\textbf{Reader of books on birds and other wildlife.} \emph{Shirley S.
D'Stefan, 90, Florham Park, N.J.}

\textbf{Pillar in the Detroit community.} \emph{Edmon C. Carmichael, 79,
Detroit}

\textbf{Known as the ``fashionista'' in her nursing home.} \emph{Helen
Silvia, 96, Brockton, Mass.}

\textbf{Worked at the Home Depot.} \emph{Davis Begaye, 48, Cudei, N.M.}

\textbf{Daughter of Italian immigrants.} \emph{Rose Mary Infantino, 88,
Rye Brook, N.Y.}

\textbf{Animator for Disney films, including ``The Little Mermaid.''}
\emph{Ann Sullivan, 91, Woodland Hills, Calif.}

\textbf{Art supply businessman with a romantic streak.} \emph{Norman
Gulamerian, 92, New Providence, N.J.}

\textbf{Exceptional radiologist.} \emph{Kenneth L. Jewel, 78, Mountain
Lakes, N.J.}

\textbf{Last of the WWII Polish fighter pilots.} \emph{Jerzy
Glowczewski, 97, New York City}

\textbf{Built the family heating-oil business into a successful
company.} \emph{Joan M. Heaney, 77, Upper Brookville, N.Y.}

\textbf{Always put her children first.} \emph{Delia Regina DiTullio, 91,
Jamaica Plain, Mass.}

\textbf{Classy lady with style and elegance.} \emph{Jeanne Stone Rusnak,
84, Endicott, N.Y.}

\textbf{Shared her knowledge and love of reading.} \emph{Anita Robinson,
94, Minnesota}

\textbf{Enjoyed being a waterman on his work boat on Chesapeake Bay.}
\emph{William U. Roulette III, 93, Stroudsburg, Pa.}

\textbf{Trailblazing deputy sheriff.} \emph{Antoinette Meyer, 95,
Crownsville, Md.}

\textbf{Accountant who achieved the American dream by founding a firm.}
\emph{Sushil Kumar, 63, Roslyn Heights, N.Y.}

\textbf{Alabama native who led travel agencies in Florida.} \emph{Carol
Davis, 80, Manatee County, Fla.}

\textbf{Home helper for many years.} \emph{Linda Nute, 61, Hazel Crest,
Ill.}

\textbf{Former art teacher.} \emph{Tom Ferguson, 71, Chicago}

\textbf{Babysitter for the local church.} \emph{Lela Reed, 95, Country
Club Hills, Ill.}

\textbf{Known for her amazing sense of humor.} \emph{Joan Cecile
Berngen, 69, Burbank, Ill.}

\textbf{Definition of love, loyalty, and the ability to serve others.}
\emph{Gwendolyn A. Carmichael, 72, Detroit}

\textbf{Known as the bonfire builder.} \emph{James Lowell Miller Jr.,
64, Cedar Rapids, Iowa}

\textbf{Her hobbies included reading, especially cookbooks.}
\emph{Dolores A. Vail, 89, Torrington, Conn.}

\textbf{Great mentor to many.} \emph{William Brett Tracy, 61,
Snellville, Ga.}

\textbf{Principal's assistant.} \emph{Ellen Spencer, 70, Newburgh, N.Y.}

\textbf{Encyclopedia executive with perfect timing.} \emph{Stanley
Moser, 88, Fort Lee, N.J.}

\textbf{Trailblazing New Jersey nurse.} \emph{Corliss Henry, 95, Summit,
N.J.}

\textbf{Distinguished scholar.} \emph{William H. Gerdts, 91, New York
City}

\textbf{Dedicated her life to peace, diplomacy and human rights.}
\emph{Ella King Russell Torrey, 94, Philadelphia}

\textbf{Railroad worker with a big, joyful personality.} \emph{Michael
Hill, 58, Glassboro, N.J.}

\textbf{Boxing aficionado.} \emph{Richard Kiddle, 76, Beverly, Mass.}

\textbf{Retail executive who led Selfridges.} \emph{Roy Northway
Stephens, 85, New Canaan, Conn.}

\textbf{Survivor who taught about the Holocaust.} \emph{Margit
Buchhalter Feldman, 90, Somerset, N.J.}

\textbf{Taught senior citizens computer and Internet skills.}
\emph{Shidao Wang, 72, New York City}

\textbf{Bravely fought a monthlong battle with Covid-19.} \emph{John
Joseph Crowe, 56, Saint Johns, Fla.}

\textbf{Worked as a secretary for Grumman Aerospace for nearly 25
years.} \emph{Ida Esposito, 92, Melville, N.Y.}

\textbf{While revelers did the ``Soul Train'' line at a wedding, he
combined it with ``The Worm.''} \emph{Levie Barkley, 69, Chicago}

\textbf{Restaurant owner.} \emph{Saul Moreno, 58, Chicago}

\textbf{Volunteered for her parish, hand-making rosaries.} \emph{Manda
Klancir, 90, Brookfield, Ill.}

\textbf{Father figure to hundreds of young men.} \emph{Milton Sivels
Jr., 68, Richton Park, Ill.}

\textbf{Brakeman for the Chicago and Northwestern railroad.} \emph{Frank
Miszkiewicz, 94, Aurora, Ill.}

\textbf{Artist, photographer and mentor.} \emph{Philemon Najieb, 70,
Chicago}

\textbf{Worked on construction projects.} \emph{Albert H. Irwin, 86,
Brownsville, Ore.}

\textbf{Gained notoriety for his freeform dancing at family functions.}
\emph{Philip A. Scardilli, 91, Colonia, N.J.}

\textbf{Work was a big part of her life, and she derived much
satisfaction from it.} \emph{Shirley Eileen Zimmerman, 92, Dearborn,
Mich.}

\textbf{First woman on her block to work outside the home.}
\emph{Marlene B. Mandle, 88, Collingswood, N.J.}

\textbf{Big guy with an even bigger heart.} \emph{Jeffrey Ronald Henry
Muzljakovich, 56, Centerbrook, Conn.}

\textbf{The rock that held her family together.} \emph{Mary E. Mack, 84,
Athens, Pa.}

\textbf{Film professor and screenwriter.} \emph{Milena Jelinek, 84, New
York City}

\textbf{Inventive landscape photographer.} \emph{John Pfahl, 81,
Buffalo}

\textbf{Architect and Holocaust survivor.} \emph{Joseph Feingold, 97,
New York City}

\textbf{Saxophonist and master of ``cool'' jazz.} \emph{Lee Konitz, 92,
New York City}

\textbf{Survived by his wife of 61 years.} \emph{John Bradford Hubert
II, 83, Beverly Hills, Mich.}

\textbf{Always ready with a one-liner to lighten the mood.} \emph{Ken
Caley, 59, San Clemente, Calif.}

\textbf{Never let anyone mess with his younger brother.} \emph{Rodrick
Samuels, 49, Orlando, Fla.}

\textbf{Longtime member of the Quincy Republican City Committee.}
\emph{Sandra McCauley, 83, Quincy, Mass.}

\textbf{Coached youth baseball.} \emph{Harold Dixon, 60, Egg Harbor
Township, N.J.}

\textbf{A 25-year career at IBM.} \emph{Charles Robert Keal, 84, Maple
Grove, Minn.}

\textbf{Many appreciated his straight talk.} \emph{Jerome Michael
Zottolo, 75, San Diego}

\textbf{His ``all in the pot'' cookies will remain a family tradition.}
\emph{Benjamin DiGiovanni, 90, New York City}

\textbf{Loved to read and play bingo.} \emph{Nancy M. Allen, 91, New
York City}

\textbf{Longshoreman for New York piers.} \emph{Onielo De Luzio, 90, New
York City}

\textbf{Nursing assistant at the center of an outbreak.} \emph{Lawrence
Nokes, 69, Maryland}

\textbf{Transport worker.} \emph{Michael Miller, 60, Clinton, Md.}

\textbf{Jazz bassist who returned to music after 30 years.} \emph{Henry
Grimes, 84, New York City}

\textbf{Represented Delaware in senior bowling tournaments.} \emph{Owen
Moreland Parks, 80, Milford, Del.}

\textbf{He deserved the title Coach.} \emph{Marcus Pino Sr., 42, Alamo,
N.M.}

\textbf{Was never afraid to sing or dance.} \emph{Angeline Michalopulos,
92, Des Plaines, Ill.}

\textbf{Loved to don Groucho glasses and tell jokes.} \emph{Allen Joseph
Spinner, 71, Streamwood, Ill.}

\textbf{Delighted in educating thousands of children over three
decades.} \emph{Elaine Cupka, 86, Potomac, Md.}

\textbf{Sang at countless weddings.} \emph{James Kevin Malloy, 67,
Oxford, Miss.}

\textbf{Championed desegregation.} \emph{Robert Bruce Harrell, 90,
Carbondale, Ill.}

\textbf{Smithsonian music curator.} \emph{James Merle Weaver, 82, New
York}

\textbf{Great-great-grandmother.} \emph{Cathryn Wood, 94, Detroit}

\textbf{His ever-morphing and repetitive stories will be missed.}
\emph{Ronald Wilfred LePage, 81, Grand Rapids, Mich.}

\textbf{Worked tirelessly as a mental health advocate.} \emph{Laurie
Appell, 70, Hartford, Conn.}

\textbf{Nurse with a love for language.} \emph{Verla L. Courey, 88,
South Windsor, Conn.}

\textbf{Quoted Longfellow and Tennyson from memory.} \emph{Alan F.
Krupp, 83, Newton, Mass.}

\textbf{Known to many for his amazing Donald Duck impersonation.}
\emph{Stanley Marvin Grossman, 83, Nanuet, N.Y.}

\textbf{Taught French and etymology for 27 years.} \emph{Kim A. Replogle
Blanchar, 68, Avon, Ind.}

\textbf{Presented quilts annually at the East Cobb Quilting Guild Show.}
\emph{Nola Kathleen LaBudde, 71, Smyrna, Ga.}

\textbf{Soft-spoken and genuine.} \emph{Alex Ruperto, 52, Glen Ridge,
N.J.}

\textbf{Subway car inspector in Manhattan.} \emph{Ferdi German, 41,
Poughkeepsie, N.Y.}

\textbf{Spent her youth at foreign service postings.} \emph{Martha Leroy
Wilson, 76, Arlington, Va.}

\textbf{A long career as a pharmacist.} \emph{Thomas William Campbell,
87, Midlothian, Va.}

\textbf{Would hold scientific discussions over dinner.} \emph{Ina Shaw
Mirviss, 93, Stamford, Conn.}

\textbf{Former Angolan freedom fighter.} \emph{Zoao Makumbi Sr., 75,
Lanham, Md.}

\textbf{Lifetime member of the Ladies' Auxiliary, V.F.W. Post 9400.}
\emph{Patricia Plante, 84, Peoria, Ariz.}

\textbf{His name was engraved on the Stanley Cup.} \emph{Barry G.
Fisher, 69, Old Brookville, N.Y.}

\textbf{Survived the sinking of his troopship in the English Channel.}
\emph{Robert R. Stout, 95, Dennis, Mass.}

\textbf{Glue to the family.} \emph{Moses Jones, 83, Chicago}

\textbf{Family man, risk-taker, teaser and sports lover.} \emph{Paul J.
Foley Jr., 77, Chicago}

\textbf{Driving force in establishing L.S.U.-Eunice.} \emph{Veil David
DeVillier, 85, Baton Rouge, La.}

\textbf{Young, healthy guy who took care of himself.} \emph{Ronaldo
Ferrari, 42, Berlin, Conn.}

\textbf{There is not a Louis L'Amour Western he had not read three
times.} \emph{Arthur Winthrop Barstow, 93, Hadley, Mass.}

\textbf{Seminole Police Department officer.} \emph{Calvin Harrison, 78,
Florida}

\textbf{Medal of Honor winner for Vietnam War heroics.} \emph{Bennie G.
Adkins, 86, Opelika, Ala.}

\textbf{Uniter of Nigerians in New York.} \emph{Jonathan Adewumi, 57,
Bayonne, N.J.}

\textbf{Bakery owner attuned to the West Indies.} \emph{Conrad Ifill,
81, Hempstead, N.Y.}

\textbf{Clarinetist who wanted music to be easily accessible.}
\emph{Paul Shelden, 79, Hewlett, N.Y.}

\textbf{Soprano of opera companies in New York and Hamburg.}
\emph{Arlene Saunders, 89, New York City}

\textbf{World War II veteran whose twin died in the Spanish Flu epidemic
a century ago.} \emph{Philip Kahn, 100, Westbury, N.Y.}

\textbf{Art historian of East Harlem, N.Y.} \emph{Mario César Romero,
78, New York City}

\textbf{Stylish archaeologist and champion dachshund breeder.}
\emph{Iris Love, 86, New York City}

\textbf{Winner of the art prize at Mt. Holyoke.} \emph{Andrea Ruth
Ludgin, 81, Oyster Bay, N.Y.}

\textbf{Vice president at an insurance firm.} \emph{Jane Krumrine, 82,
Merion Station, Pa.}

\textbf{Former firefighter.} \emph{Charlie Hopper, 78, Augusta, Maine}

\textbf{Secretary turned tax consultant.} \emph{Judith Lee Arkerson, 77,
Dover, N.H.}

\textbf{Played football for Terre Haute South.} \emph{Larry Sylvester
Hutchinson Jr., 27, Terre Haute, Ind.}

\textbf{Helped establish many credit unions.} \emph{Charles Donald Neal,
Sr., 91, Broken Arrow, Okla.}

\textbf{Optimist.} \emph{Bill Mantell, 68, East Meadow, N.Y.}

\textbf{Voice of the Naval Academy football stadium for three decades.}
\emph{William E. Jackman, 85, Reston, Va.}

\textbf{Secretary for the chairman of the Joint Chiefs of Staff.}
\emph{Ruth Hunter, 96, Washington, D.C.}

\textbf{Ticket clerk who rose to lead the L.I.R.R.} \emph{Raymond Kenny,
68, Lindenhurst, N.Y.}

\textbf{Owned and operated Carey's Supermarket for many years.}
\emph{Carol Carey, 84, Cuthbert, Ga.}

\textbf{Husband lost two days before his wife of 62 years.} \emph{Thomas
Neal Therrian, 84, Ellenton, Fla.}

\textbf{Rose each morning at 5 a.m. to read the Bible.} \emph{John Larry
Sartain, 77, Des Plaines, Ill.}

\textbf{Dedicated nurse.} \emph{Josephine Tapiru, 56, Chicago}

\textbf{Formidable professor, amiable pastor.} \emph{Herbert Nygren, 91,
Carol Stream, Ill.}

\textbf{Served in Belgium, France and Germany during WWII.} \emph{Joseph
J. Angi Sr., 95, New York}

\textbf{Los Angeles sports fan.} \emph{Paul Martinez, 70, West Covina,
Calif.}

\textbf{Enjoyed taking walks through town.} \emph{Michael I. Sumergrad,
64, Mansfield, Ohio}

\textbf{Enjoyed attending reunions with fellow sailors.} \emph{John F.
Cannon, 89, Allentown, Pa.}

\textbf{Well-regarded bailiff and mentor to colleagues.} \emph{Eric
Frazier, 44, New Orleans}

\textbf{Civic leader and mediating force.} \emph{Kenneth Saunders III,
43, Decatur, Ga.}

\textbf{Worked for Radio Free Europe.} \emph{Justin Liuba, 95,
Springfield, Mass.}

\textbf{General surgeon who volunteered to treat Covid-19 patients.}
\emph{Barry Webber, 67, New York City}

\textbf{Exemplified the women of the Greatest Generation.} \emph{Gloria
Zimmerman, 97, White Plains, N.Y.}

\textbf{Sympathetic ear.} \emph{Ruthie Jacqueline Stephens Turner, 86,
Alabama}

\textbf{Stylish dancer who could lead or follow.} \emph{Gerry Ellis, 91,
Philadelphia}

\textbf{Authored a well-regarded biography of Sarah Tyson Rorer.}
\emph{Emma Weigley, 87, Philadelphia}

\textbf{Attended every weekend A's game, almost without exception.}
\emph{Scott Douglas Woodard, 67, Oakland, Calif.}

\textbf{Always chose to work with the most at-risk students.}
\emph{Steven L. Freedman, 71, Syosset, N.Y.}

\textbf{Loved art and making cards.} \emph{Carla Thompson, 67,
Washington, D.C.}

\textbf{Immigrated from Hong Kong.} \emph{Yuet Ming Wong, 91, Chicago}

\textbf{Known for throwing an annual Fourth of July party.} \emph{Craig
Franken, 61, Sioux Falls, S.D.}

\textbf{Firefighter and part-time Santa.} \emph{Fred J. Felella Jr., 58,
Sugar Grove, Ill.}

\textbf{Co-owned and operated Atwood Television and Radio Service.}
\emph{Thomas I. Atwood, 80, Bluffton, S.C.}

\textbf{Faithful in corresponding through cards and handwritten notes.}
\emph{Beverly J. Plessinger, 88, Wooster, Ohio}

\textbf{Survived by her husband of 70 years.} \emph{Norma Jean Knight,
93, Des Moines}

\textbf{Worked in maintenance for the public schools.} \emph{Ralph R.
Loranger, 74, Farmington, Conn.}

\textbf{Master electrician.} \emph{John Joseph Christiana Jr., 80,
Hartford, Conn.}

\textbf{Gifted pitcher who never made the big leagues.} \emph{Steve
Dalkowski, 80, New Britain, Conn.}

\textbf{Dispensed tough but empathetic love to her students.}
\emph{Patricia McGowan, 80, New York City}

\textbf{Patent lawyer who recovered a family painting looted by the
Nazis.} \emph{David Toren, 94, New York City}

\textbf{Combative councilman and judge.} \emph{Noach Dear, 66, New York
City}

\textbf{Modern-day renaissance woman.} \emph{Myrtha Celifie, 91,
McHenry, Ill.}

\textbf{Her sarcastic sense of humor always made everyone smile.}
\emph{Alice Fraher-Mason, 91, Weymouth, Mass.}

\textbf{Cancer survivor at 88 years old.} \emph{Stephen J. Clinton, 94,
Rockland, Mass.}

\textbf{Taught elementary school for more than 30 years.} \emph{Kathleen
Devon Domenick, 67, Devon, Pa.}

\textbf{Loved playing tennis.} \emph{Roxana Griswold Foreman, 85,
Richmond, Va.}

\textbf{Stayed home to raise her children.} \emph{Audrey L. Ercha, 92,
Beverly, Mass.}

\textbf{Michigan's youngest victim of the coronavirus pandemic.}
\emph{Skylar Herbert, 5, Detroit}

\textbf{Loved the grocery business.} \emph{John Fusco, 68, Rochester,
N.Y.}

\textbf{Teacher passionate about respecting people with different
abilities.} \emph{Cynthia Jean Falle, 72, Troy, N.Y.}

\textbf{Active member and leader of the Taconic Hiking Club.}
\emph{Willard John Hoyt, 87, Schodack, N.Y.}

\textbf{Therapist for military veterans.} \emph{Calvin Richardson Jr.,
57, La Plata, Md.}

\textbf{A zest for life.} \emph{Ethel R. Fonti, 77, Beverly, Mass.}

\textbf{Enjoyed the theaters of New York.} \emph{Joseph M. Kissane, 89,
New York City}

\textbf{Taught himself to play the drums.} \emph{Charles Dow Long, 82,
Tempe, Ariz.}

\textbf{Wife who outlived her husband by less than two days.} \emph{Judy
Therrian, 80, Ellenton, Fla.}

\textbf{Corporate leader and animal rescue advocate.} \emph{Herb Baum,
83, Florida}

\textbf{Youngest of 21 siblings.} \emph{Sawarrelita Redmond, 52,
Riverdale, Ill.}

\textbf{Her strength was a thing of wonder.} \emph{Linda L. Orendorff,
80, Hilliard, Ohio}

\textbf{Hospitality came easy to her.} \emph{Florence Marks, 96,
Lancaster, Pa.}

\textbf{Notorious for receiving the most holding calls.} \emph{Boro
Lalich, 68, Indianapolis}

\textbf{Well-respected criminal defense attorney.} \emph{Richard Emmett
Powers, 76, Detroit}

\textbf{Cherished grandfather.} \emph{John Francis McClintock, 84,
Farmington Hills, Mich.}

\textbf{Always had a smile and a twinkle in her eye.} \emph{Vincie
Teresa DeRose, 57, Arlington, Mass.}

\textbf{Her gardens flourished.} \emph{Mary Ann Scata, 90, Wethersfield,
Conn.}

\textbf{Proud of her Italian heritage.} \emph{Dorothy Cembrano Jay, 92,
East Windsor, Conn.}

\textbf{Highly successful Avon representative.} \emph{Edith Costanzo,
93, Wethersfield, Conn.}

\textbf{Roaring voice that filled lecture halls.} \emph{Dennis Peters,
82, Indiana}

\textbf{Exceptional billiard player.} \emph{Gaetano Lombardo, 70,
Rockland County, N.Y.}

\textbf{Her zest for life will live on.} \emph{Marie A. Detrick, 88,
Sayre, Pa.}

\textbf{Worked for more than 40 years at the U.S. Department of
Education.} \emph{Stanley M. Cohen, 86, Chevy Chase, Md.}

\textbf{Lifelong dedication to family.} \emph{Carol Freedman, 88, New
Rochelle, N.Y.}

\textbf{Popular figure in the Philadelphia wine and spirits community.}
\emph{Ron Waxman, 88, Pennsylvania}

\textbf{``adventurer and a charmer.''} \emph{Peter Laker, 93, Chicago}

\textbf{Professor of English and philosophy at Gloucester County
College.} \emph{Henry Burk Sullivan, 90, Haddonfield, N.J.}

\textbf{New Hampshire state legislator and Dover City councilman.}
\emph{Paul R. McQuade, 88, Dover, N.H.}

\textbf{Loved bird-watching, fishing and listening to music.}
\emph{Frederick Koerner, 86, Minnesota}

\textbf{Spent countless hours coaching baseball in Bartlesville.}
\emph{Malcolm C. Shaw Jr, 77, Bartlesville, Okla.}

\textbf{A passion for slot machines.} \emph{Dalma Holloway Torres, 73,
Uniondale, N.Y.}

\textbf{Talented athlete who played football, baseball and basketball.}
\emph{Peter P. DeLuise, 63, New Jersey}

\textbf{Had been planning to retire in April.} \emph{Celia Yap-Banago,
69, Kansas City, Mo.}

\textbf{Taught at several Baltimore-area schools.} \emph{Barbara Ann
Loreck, 90, Pikesville, Md.}

\textbf{A long career in horticulture.} \emph{Antoinette Tosco, 77,
Bridgewater, N.J.}

\textbf{Known in English as ``Grandpa Boom'' and in Lithuanian as
``Senelis.''} \emph{Anthony V. Racka, 86, Farmington Hills, Mich.}

\textbf{France was always first and foremost in her heart.}
\emph{Suzanne Raynal Gijsbers, 93, Michigan}

\textbf{A 30-year career at the Gillette Company.} \emph{Kenneth Richard
Coombs, 75, Methuen, Mass.}

\textbf{Worked as a computer specialist for the Department of
Agriculture.} \emph{Eric F. Anderson, 80, Southfield, Mich.}

\textbf{Gardener who won the title of Pickle King.} \emph{Theodore
Robert Zaterka, 89, South Windsor, Conn.}

\textbf{Avid fly fisherman.} \emph{Richard J. Conway III, 64, Amston,
Conn.}

\textbf{Pastor who ``preached with a lot of strength and voice and
sweat.''} \emph{David Ford, 59, DeWitt Township, Mich.}

\textbf{Longtime educator who was also a police officer.} \emph{Willie
Gene Whitaker, 85, Texas}

\textbf{Emmy-nominated TV producer behind ``Knight Rider'' and ``Magnum,
P.I.''} \emph{Joel Rogosin, 87, Los Angeles}

\textbf{Worked as a carpenter for more than 40 years.} \emph{William F.
Latimer, 75, Maryland}

\textbf{Lifetime resident of Lewiston.} \emph{Crystal LaBelle, 87,
Lewiston, Idaho}

\textbf{Former president of Stanford University.} \emph{Donald Kennedy,
88, Redwood City, Calif.}

\textbf{Boxing gym owner and beloved trainer.} \emph{Francisco Mendez,
61, Jersey City, N.J.}

\textbf{Served in the U.S. Army.} \emph{Louis B. Bernstein, 92,
Roseland, N.J.}

\textbf{Prosecuted mobsters, drug dealers and corrupt politicians.}
\emph{Phil Foglia, 69, New York City}

\textbf{Brother of Senator Elizabeth Warren.} \emph{Donald Reed Herring,
86, Norman, Okla.}

\textbf{Loved dancing, opera, art, British mysteries and animals of all
kinds.} \emph{Billie Jean Michael Habermehl, 90, Manassas, Va.}

\textbf{Raised five children.} \emph{Mary Therese Loughery, 89,
Abington, Pa.}

\textbf{Motivating ``legend'' in a southwest Philadelphia school.}
\emph{Gloria Allen Moskowitz, 88, Ardmore, Pa.}

\textbf{Inducted into the Aircraft Engine Hall of Fame.} \emph{Stephen
J. Chamberlin Jr., 91, Worcester, Mass.}

\textbf{Insurance salesman famous for his self-help books.} \emph{Barry
Kaye, 91, Boca Raton, Fla.}

\textbf{Nurse working night shifts in the ICU.} \emph{Patricia Gibbons,
76, Naples, Fla.}

\textbf{Mother outlived by her newborn.} \emph{Wogene Debele, 43,
Baltimore}

\textbf{Political scientist and congressional scholar.} \emph{Richard F.
Fenno Jr., 93, Rye, N.Y.}

\textbf{Art director for the ABC television shows ``Emergence,'' ``Luke
Cage'' and ``The Punisher.''} \emph{Matteo De Cosmo, 52, New York}

\textbf{Skilled cook.} \emph{Mark Schroeder, 54, New York}

\textbf{Loved seeing the full moon rise over the ocean.} \emph{Norman
Leslie Jenkins, 91, Hingham, Mass.}

\textbf{Enjoyed gardening, fishing, hunting, playing pranks and spending
time with family.} \emph{Celestino Padilla Sr., 82, Rochester, N.Y.}

\textbf{Always enjoyed a good discussion involving politics.}
\emph{Retha Elizabeth Contri Sharp, 98, Iowa}

\textbf{Owned and operated Big Bob's Pizzerias.} \emph{Robert Adam
Burns, 85, Michigan}

\textbf{Last of his generation for his 60 nieces and nephews.}
\emph{Raymond Paul Janssen, 96, Dowagiac, Mich.}

\textbf{Shining light and an uplifting presence.} \emph{Kerry Lehman,
62, Jackson, Mich.}

\textbf{Loved his truck, Dorney Park, Disney World, model trains and
especially California cheeseburgers.} \emph{James W. Landis, 57,
Krocksville, Pa.}

\textbf{E.M.T. and former Marine who rushed to the World Trade Center on
9/11.} \emph{Idris Bey, 60, New York City}

\textbf{Served in the U.S. Army in Iran and with the C.D.C. fighting
cholera in the Philippines.} \emph{Paul Ronald Joseph, 87, Forest Hills,
N.Y.}

\textbf{Member of Bethlehem United Methodist Church.} \emph{Bette Allred
Weatherly, 93, Pleasant Garden, N.C.}

\textbf{Feisty, unique lady to the end.} \emph{Anna Sternik Warren, 100,
Binghamton, N.Y.}

\textbf{Widely respected tenor saxophone player.} \emph{Robert Barnes,
82, Philadelphia}

\textbf{Enjoyed bingo, watching TV and spending time with her family.}
\emph{Dawn M. Peryer, 61, Plattsburgh, N.Y.}

\textbf{She and her husband were pioneers in industrial catering.}
\emph{Alma M. Carney, 91, Florida}

\textbf{Senior corrections police officer.} \emph{Maria Gibbs, 47,
Burlington County, N.J.}

\textbf{Cherished grandfather.} \emph{Robert C. Moen Sr., 83,
Schenectady, N.Y.}

\textbf{Would talk to anybody about anything.} \emph{Jerry Alford, 60,
Tuscaloosa, Ala.}

\textbf{Cheerful, upbeat, thankful person.} \emph{Paul Edward Herbst,
92, Vernon, Conn.}

\textbf{Hunted and fished and cooked what he caught.} \emph{Charles
Willis Alston, 74, Seaford, Del.}

\textbf{Tried to make everyone around him laugh.} \emph{Jeffrey Stanley
Lin, 70, Middletown, N.J.}

\textbf{Expert polygraph examiner.} \emph{John J. Valentine, 86, Long
Branch, N.J.}

\textbf{Taught the fourth and fifth grades.} \emph{Virginia Alice Rauth,
85, Lakewood, N.J.}

\textbf{Will be remembered for her spirit of adventure and wanderlust.}
\emph{Marcia Rushford, 80, Alexandria, Va.}

\textbf{Nurse for more than 30 years.} \emph{Joyce Pacubas-Le Blanc, 53,
Darien, Ill.}

\textbf{Enjoyed gardening, decorating and cooking.} \emph{Lucille
Dolores Romer, 80, New Jersey}

\textbf{Taught junior high science and math and farmed full time.}
\emph{Gerald Ringdahl, 87, North Dakota}

\textbf{Minor league baseball player.} \emph{Ed Smrekar, 88,
Pennsylvania}

\textbf{Outspoken, loving, caring and compassionate.} \emph{Rachel
Walters, 68, Cudei, N.M.}

\textbf{Served as interim pastor to churches during difficult
transitions.} \emph{Allen Francis Tinkham, 91, Newington, Conn.}

\textbf{Aspiring leader in the Navajo Nation.} \emph{Valentina
Blackhorse, 28, Kayenta, Ariz.}

\textbf{Rapper known for sharp wordplay.} \emph{Fred the Godson, 41, New
York City}

\textbf{Was 13 during World War II when she and her family were
incarcerated at Manzanar.} \emph{Lillian Kimura, 91, Albany, N.Y.}

\textbf{Enjoyed the church's women's bowling league.} \emph{Carol A.
Castle, 80, Weymouth, Mass.}

\textbf{Educator who said: ``I didn't teach a subject. I taught
children.''} \emph{Ethel Hamburger, 92, Elkins Park, Pa.}

\textbf{Vermont shop owner.} \emph{William Harrison Goldman, 87, New
Jersey}

\textbf{Longtime soccer referee.} \emph{Ronald Clark, 70, Ballston Lake,
N.Y.}

\textbf{Enjoyed spending time with her family and reminiscing about her
horses.} \emph{Audrey LeMaire Morvant, 76, Abbeville, La.}

\textbf{Involved in the early days of aerobic exercise.} \emph{Rona Iris
Gertz, 74, New Jersey}

\textbf{She helped immigrants and refugees get on their feet.}
\emph{Patricia Rowe, 94, Buffalo}

\textbf{Buffalo front-line hospital worker.} \emph{John Poleon, 63, Erie
County, N.Y.}

\textbf{Social butterfly.} \emph{Elizabeth Tevenan, 82, Brewster, Mass.}

\textbf{Made his living from police work.} \emph{Joseph T. Cappello, 55,
Melrose Park, Ill.}

\textbf{Generous, blunt, and forever centered on her family.}
\emph{Oluwayemisi Ogunnubi, 59, Chicago}

\textbf{Loved art, music and animals.} \emph{Joan M. Cargill, 81, New
Brunswick, N.J.}

\textbf{Served in the Korean War and the Berlin airlift.} \emph{Kenneth
K. Skoog, 90, Fargo, N.D.}

\textbf{Worked as a maintenance man for J.M. Smucker for 25 years.}
\emph{Quentin Cormell, 84, Orrville, Ohio}

\textbf{Collector and talented artist.} \emph{Carl Robert Bentley, 78,
Glastonbury, Conn.}

\textbf{Enjoyed dancing, shooting pool and going to Soundview Beach.}
\emph{Ronald Boccacio, 80, Hartford, Conn.}

\textbf{Never seemed to know a stranger.} \emph{Clyde Addison
Reichelderfer, 86, Ohio}

\textbf{Had an exceptional recollection of local history.} \emph{Betty
Jean Ringle, 87, Idaho}

\textbf{Founder of PBS.} \emph{Gerald Slater, 86, Washington, D.C.}

\textbf{Kept a scrapbook of the places he saw.} \emph{Walter M. Eagles
Jr., 95, Fort Washington, Pa.}

\textbf{Former merchant marine from Cape Verde.} \emph{Anibal Francisco
de Brito, 90, Philadelphia}

\textbf{Remained proud of her Greek heritage.} \emph{Helen Demetoglous,
96, New Jersey}

\textbf{Organized his Class of 1943 high school reunions through the
70th in 2013.} \emph{Calvin Tompkins Lucy Jr., 93, Virginia}

\textbf{Enjoyed a 37-year career with the Rockville Centre Police
Department.} \emph{John McKeon, 68, Islip, N.Y.}

\textbf{High school library aide and a teacher's aide.} \emph{Margaret
Skaliotis, 92, Boston}

\textbf{If you asked her to do something, she did it.} \emph{Marion
Klein, 87, St. Louis Park, Minn.}

\textbf{Always the first to offer help to those in need.} \emph{Latasha
Andrews, 33, New Jersey}

\textbf{Avid reader and book club member.} \emph{Dorothy Alma Ennis
D'Ostilio, 95, Fairfield, Conn.}

\textbf{Studio musician in the late '60s in New York City.} \emph{Ron
Frangipane, 75, Tinton Falls, N.J.}

\textbf{Awarded the Combat Infantryman Badge, Purple Heart and Bronze
Star.} \emph{Richard M. Glidden, 95, Orleans, Mass.}

\textbf{Enlisted in the Women's Army Corps on her 21st birthday in
1944.} \emph{Britta Lou Miller, 97, Ohio}

\textbf{Created her own version of ``meals on wheels'' for those in
need.} \emph{Barbara Stack, 76, Perth Amboy, N.J.}

\textbf{Faithfully served his country with the Air Force.} \emph{Robert
Michael Sedor, 77, Hillsborough, N.J.}

\textbf{Never knew anything but work.} \emph{Terry G. Thompson, 75,
Indiana}

\textbf{Her passion was geriatric care.} \emph{Brenda Lee Orebaugh, 62,
Dayton, Va.}

\textbf{Put himself through college.} \emph{Jorge F. Casals, 75,
Manchester, Conn.}

\textbf{Owned her own small businesses.} \emph{Lucille Marie Resto, 77,
Rocky Hill, Conn.}

\textbf{Performed in renowned venues such as Madison Square Garden.}
\emph{Luis A. Frias, 65, Las Vegas}

\textbf{Accomplished artist.} \emph{Pierina D. Borsoi, 90, Bethlehem,
Pa.}

\textbf{Scientist who explained the physics of sports.} \emph{Peter J.
Brancazio, 81, Manhasset, N.Y.}

\textbf{Haitian immigrant with a big heart.} \emph{Edith Richemond, 88,
New York City}

\textbf{Collector of dictionaries and lover of words.} \emph{Madeline
Kripke, 76, New York City}

\textbf{Spent his working years in the insurance industry.}
\emph{Raphael Kaminer, 86, New York City}

\textbf{Loving father.} \emph{Richard J. Rome, 91, Roslindale, Mass.}

\textbf{Actively involved in the United Methodist Women.} \emph{Barbara
J. Norris, 90, Weymouth, Mass.}

\textbf{One of the first women of her generation to drive a car.}
\emph{Eve Rudin, 103, Philadelphia}

\textbf{His greatest accomplishment was serving as an ordained deacon.}
\emph{Raymond W. Wilkinson Sr., 91, Weatherly, Pa.}

\textbf{Only things he was more proud of than his military service were
his children.} \emph{Bruce P. Biesenbach Sr., 74, Albany, N.Y.}

\textbf{Loved karaoke, dancing, singing and playing bingo.} \emph{Louise
N. Walsh, 71, Massachusetts}

\textbf{Her will was indomitable.} \emph{Nora Malis, 97, Salem, N.H.}

\textbf{Worked at Goodwill for more than 25 years.} \emph{Michael Albert
Shubak, 60, Coraopolis, Pa.}

\textbf{Worked for the F.A.A. as a flight operations safety officer,
retiring at 85.} \emph{Ross L. Saddlemire, 87, Port Jefferson, N.Y.}

\textbf{Had a vision to provide sophisticated medical care to rural
areas.} \emph{John Robert Oglesbee, 80, Tahlequah, Okla.}

\textbf{Lifelong teacher with a master's degree in special education.}
\emph{Martha Eddy O'Brien, 86, Hartford, Conn.}

\textbf{Enjoyed family dinners and celebrations.} \emph{Ellen Elizabeth
Fabry, 70, Burlington, N.J.}

\textbf{City planner and longtime community volunteer.} \emph{Norton A.
Kent, 96, Gwynedd, Pa.}

\textbf{Quiet and humble member of a prayer circle.} \emph{Mary Gilbert,
84, Mansfield, Mass.}

\textbf{Started his own business.} \emph{Henry N. Dubois, 84, East
Hartford, Conn.}

\textbf{Loved to watch old Western movies.} \emph{Joseph Colasurdo, 85,
Jersey City, N.J.}

\textbf{His family was the most important accomplishment of his life.}
\emph{Edward A. Masterson, 56, Yonkers, N.Y.}

\textbf{Award-winning journalist, author and community activist.}
\emph{Robert C. Samuels, 83, New York}

\textbf{Dearly loved Kentucky.} \emph{Lillian Press, 95, Kentucky}

\textbf{Outlet to talk about everything and anything.} \emph{Rosemarie
Theresa Torrance, 60, Wilmington, Del.}

\textbf{Enjoyed gardening, camping and making people laugh.}
\emph{Clarence Robert Ellis, 93, Rochester, N.Y.}

\textbf{Member of the Bell retirees.} \emph{Mary Frances Parsels Dennis,
82, Mechanicsville, Va.}

\textbf{Had a knack for games of chance.} \emph{Richard Daniel Harris,
86, Danvers, Mass.}

\textbf{Major college donor in Florida.} \emph{Carole Kaye, 87, Boca
Raton, Fla.}

\textbf{Swam over one mile each week.} \emph{Eva Charlotte Julewitz, 91,
Woonsocket, R.I.}

\textbf{Loved old Western movies, Elvis's music and the Dallas Cowboys.}
\emph{Tony Maldonado, 66, Waxahachie, Texas}

\textbf{Excellent cook, though she hated the task.} \emph{Asela E. Gejo,
92, New Jersey}

\textbf{Army veteran, business owner, free spirit and kvetch.}
\emph{Daniel S. Pincu, 80, Asheville, N.C.}

\textbf{Worked for more than two decades as a social worker.}
\emph{Catherine Drouin, 69, Methuen, Mass.}

\textbf{Surgical technologist.} \emph{Juan Martinez, 60, Chicago}

\textbf{Always the first one out on the dance floor.} \emph{Leslie
Kalmus, 57, New Jersey}

\textbf{He could spit a watermelon seed halfway across a double lot.}
\emph{Kenneth James Godwin, 94, Michigan}

\textbf{Pastor at Navajo Baptist Temple.} \emph{Jimmy Walters, 71,
Cudei, N.M.}

\textbf{Rose to leadership of the Republican Party of Iowa.} \emph{Linda
Joy Nassif, 76, Iowa}

\textbf{Staff member at Trinity Elementary School in New Rochelle.}
\emph{Emmy Falta, 41, New York}

\textbf{Computer engineer at Pratt and Whitney for many years.}
\emph{Anthony J. Valdati Jr., 83, Glastonbury, Conn.}

\textbf{Celebrated Hartford Public High School basketball player.}
\emph{Charles Jernigan, 61, Hartford, Conn.}

\textbf{Selected by the F.B.I. as a top recruit.} \emph{Irene Ann Allen,
80, Simsbury, Conn.}

\textbf{Volunteered as a firehouse cook for over 50 years.} \emph{Hilda
R. Nagel, 99, Whitehall, Pa.}

\textbf{Worked for over 33 years at Westinghouse.} \emph{William G.
Bennett, 84, Waverly, N.Y.}

\textbf{Master jeweler and goldsmith.} \emph{Fritz Wilhelm Reisgies, 87,
Alpine, N.J.}

\textbf{Fought against the Covid-19 pandemic to save patients.}
\emph{James Mahoney, 62, New York City}

\textbf{In the Pennsylvania Voter Hall of Fame for voting in every
November election for 50 years.} \emph{Wayne L. Wolford, 95,
Pennsylvania}

\textbf{Portrait oil and landscape watercolor painter.} \emph{Joan M.
Hackney, 91, West Chester, Pa.}

\textbf{Grammy-nominated gospel singer and record label founder.}
\emph{Troy Sneed, 52, Jacksonville, Fla.}

\textbf{Avid reader and knitter.} \emph{Karen Kay Bentley, 79, Sturgeon
Bay, Wis.}

\textbf{Master storyteller, with a quick wit and a flair for the
dramatic.} \emph{Ronald Jacobus, 81, Galloway, N.J.}

\textbf{Had a love of everything automotive.} \emph{Russell Aucott, 71,
Linwood, N.J.}

\textbf{A 56-year career as a produce manager at Stop and Shop.}
\emph{Robert N. Winsor, 78, Marblehead, Mass.}

\textbf{He was a master of all tools.} \emph{Daniel James Callahan, 90,
Massachusetts}

\textbf{Known for her strength and devotion to family.} \emph{Carole
Montalbano, 83, Springfield, Ill.}

\textbf{Former students will remember his brush cut and dry humor.}
\emph{Alexander Webster Cruden Jr., 87, New York}

\textbf{Accomplished quilter, calligrapher and gardener.} \emph{Ann
Bonville Trombly, 88, New York}

\textbf{Loved jeeping, camping, barbecuing, building and socializing.}
\emph{Gary Tillery, 66, Tulare, Calif.}

\textbf{Inspirational basketball coach.} \emph{Terrance Burke, 54,
Maryland}

\textbf{Ground mechanic for TWA.} \emph{Robert C. Blades, 84, Groveland,
Mass.}

\textbf{Shared a special bond with both of her sons.} \emph{Dorothy
Murphy, 83, Salem, Mass.}

\textbf{Proud of recently being promoted to Grampy.} \emph{Conrad Warren
Buckley, 52, Clermont, Fla.}

\textbf{Highly respected by those who worked with him.} \emph{Michael L.
Trombley, 79, West Brattleboro, Vt.}

\textbf{Professional land surveyor and civil engineer.} \emph{Paul
Nathan Fontenot, 80, Lafayette, La.}

\textbf{Core member of her congregation.} \emph{Dorthe J. Flick, 97,
Clinton, Iowa}

\textbf{Enjoyed entertaining his family by playing guitar and mandolin.}
\emph{Peter Crisanti, 84, West Haven, Conn.}

\textbf{Endeared himself to his nephews.} \emph{Joseph J. Ingram Jr.,
66, New Britain, Conn.}

\textbf{Enjoyed novels, crossword puzzles, art and TV shows.}
\emph{Yvonne S. Orlando, 81, Bethlehem, Pa.}

\textbf{Renegade nun who ran a nonprofit anchor in Brooklyn.}
\emph{Georgianna Glose, 73, New York City}

\textbf{Fashionista.} \emph{Jean Adele Walkins, 92, Whitman, Mass.}

\textbf{Worked at American Tobacco for 31 years.} \emph{Barbara Mae
Barham, 88, Richmond, Va.}

\textbf{Former A's minor-leaguer.} \emph{Miguel Marte, 30, New Jersey}

\textbf{Enjoyed golfing.} \emph{Earl Avers, 92, Oregon, Ohio}

\textbf{Retired from H\&W Motor Express after 30 years.} \emph{John
Pearson Brucher, 81, Cedar Rapids, Iowa}

\textbf{Her greatest joy was spending time with her family.}
\emph{Virginia Bettencourt, 92, Peabody, Mass.}

\textbf{Visited many countries.} \emph{Dean Leroy Drake, 79, Chandler,
Ariz.}

\textbf{Helped friends and neighbors train their dogs.} \emph{Edward
Russell Helfrich, 72, West Keansburg, N.J.}

\textbf{Trained and accomplished singer.} \emph{Barbara Helen
Richardson, 97, Bristol, Conn.}

\textbf{Non-judgmental and empathetic listener.} \emph{Daniel James
Parr, 60, Cape Cod, Mass.}

\textbf{Nigerian immigrant studying to become a nurse.} \emph{Ijeoma
Afuke, 35, Chicago}

\textbf{Often the one to pick out birthday cakes for his children.}
\emph{Isaias Mendoza, 63, Evanston, Ill.}

\textbf{Enjoyed long drives, late nights and huge meals.} \emph{Jerome
Berrien, 64, Chicago}

\textbf{Go-to person for everybody.} \emph{Floyd Bluntson, 66, Chicago}

\textbf{Voted ``most debonair'' in her high school yearbook.} \emph{Edie
Morello, 97, Barrington, Ill.}

\textbf{Strong-willed enough to keep her family in line.} \emph{Edith
Gallo, 94, Palos Heights, Ill.}

\textbf{Avid, lifelong trap shooter.} \emph{Paul Francis Siefert Sr.,
77, Colerain Township, Ohio}

\textbf{Traced her roots back over 10 generations.} \emph{Dorothy May
Thompson, 105, Des Moines}

\textbf{Would stay awake on the night shift because she didn't want
anyone to die alone.} \emph{Margaret Busha, 89, Mystic, Conn.}

\textbf{Enjoyed international, square and round dancing.}
\emph{Frederick Anthony Palazzo, 87, Woburn, Mass.}

\textbf{Worked at the Memorial Hospital of Rhode Island for 23 years.}
\emph{Suchendra Singh, 43, Pawtucket, R.I.}

\textbf{Huge Elvis fan.} \emph{Carmen Lydia Muniz Rodriguez, 76,
Glastonbury, Conn.}

\textbf{Ran Brownstone Amusements Carnival with her husband.}
\emph{Elsie Rossitto, 92, Portland, Conn.}

\textbf{Decorated Vietnam War veteran and member of the Seminole Tribe.}
\emph{Don Osceola, 77, Hollywood, Fla.}

\textbf{Mainstay of the Valhalla School District.} \emph{Nicholas
Modugno, 91, New York}

\textbf{Served in the Army Air Corps as an aviation electrician.}
\emph{Charles Walter Calhoun, 93, Alexander City, Ala.}

\textbf{Enjoyed planting perennial flower beds.} \emph{Marie Virginia
Leto, 92, Kennett Square, Pa.}

\textbf{Self-taught legal wiz.} \emph{Thomas Cotton, 54, Philadelphia}

\textbf{Served in the Marine Corps from 1958 to 1961.} \emph{James E.
Mann Jr., 86, Richmond, Va.}

\textbf{Church choir director, soloist and organist.} \emph{Alice Louise
Trout, 81, Pendleton, Ind.}

\textbf{Loved his whole family.} \emph{Arthur Louis Thibault, 75,
Andover, Mass.}

\textbf{Author of children's stories.} \emph{Helen Wall, 91, Lawrence,
Mass.}

\textbf{Owned one of the first Spanish bodegas in the city of Lawrence.}
\emph{Mercedes Santiago, 82, Lawrence, Mass.}

\textbf{Gentle soul who appreciated the simple things in life.}
\emph{Robert Steven Seldin, 62, Toms River, N.J.}

\textbf{Bowled for over 50 years in various leagues.} \emph{Corinne
Rhodes, 93, Oxford, Pa.}

\textbf{Huge fan of Waynedale High School sports.} \emph{Calvin E.
Messner, 77, Wooster, Ohio}

\textbf{Hobbies included sewing, knitting, crafts, puzzles, painting,
golf, bowling and euchre.} \emph{Janet M. Brown, 91, Greece, N.Y.}

\textbf{Had a passion for soul food, cooking, music and her church.}
\emph{Adrienne Eugina Doolin Howard, 75, Cedar Rapids, Iowa}

\textbf{Authored the book ``Making It In Radio.''} \emph{Daniel Blume,
89, West Hartford, Conn.}

\textbf{Enjoyed traveling throughout New England.} \emph{Jean Munson,
92, Plainville, Conn.}

\textbf{Helped form an advocacy group for Latino families.} \emph{Jose
Vitelio Gregorio, 61, New City, N.Y.}

\textbf{Emergency worker in the Seminole Tribe.} \emph{Donald
DiPetrillo, 70, Florida}

\textbf{Writer who captured the Chinese experience abroad.} \emph{Yu
Lihua, 90, Gaithersburg, Md.}

\textbf{Professor at New York University Medical School.} \emph{Charles
Goodstein, 82, Tenafly, N.J.}

\textbf{Knew how to make an entrance.} \emph{Melita Baker, 86, Norwell,
Mass.}

\textbf{Intelligent and industrious.} \emph{Joraine Sieber Groat, 97,
Ann Arbor, Mich.}

\textbf{Perfectionist and an excellent cook.} \emph{Nancy Reid, 97,
Topsfield, Mass.}

\textbf{Police detective who was once a firefighter.} \emph{Randall
Clayton French, 39, Troy, N.Y.}

\textbf{Paramedic who drove to New York to help fight the virus.}
\emph{Paul Cary, 66, New York City}

\textbf{Psychiatrist specializing in substance abuse.} \emph{Alyce
Gullattee, 91, Washington, D.C.}

\textbf{One of the first in Massachusetts to compete in the Special
Olympics.} \emph{Emmanuel Demetri, 61, Gloucester, Mass.}

\textbf{Had a dog named Chelsea whom she loved dearly.} \emph{Jolene
Blackburn Robison Wahgren, 68, Oceanport, N.J.}

\textbf{Wasn't afraid to try new things.} \emph{Patricia Yanni, 78,
Geneva, Ill.}

\textbf{Loved classical and choral music.} \emph{Elizabeth Harris
Tirrell, 95, Hillsborough, N.J.}

\textbf{Often at the farm tending to his flock and managing his
inventory of acquired wonders.} \emph{Thomas Allen Catron, 65, Adel,
Iowa}

\textbf{Enjoyed antiquing with her daughter.} \emph{Teresa A. Olbrich,
79, Rockford, Ill.}

\textbf{Enjoyed winters in Florida and traveling with the Aircraft
Campmates.} \emph{Helen Sutton, 93, Rocky Hill, Conn.}

\textbf{Was pursuing a degree in history and anthropology.}
\emph{Jonathan Crachat Carreira Ferreira, 26, Newington, Conn.}

\textbf{Served as a Eucharistic minister and lector.} \emph{Anna Marie
Lopiccolo, 74, Bristol, Conn.}

\textbf{Enjoyed her friends and listening to music.} \emph{Julia
Martinez, 62, Lubbock, Texas}

\textbf{Beloved mother, grandmother, great-grandmother and
great-great-grandmother.} \emph{Betty Sue Harber Carney, 81, Grapevine,
Texas}

\textbf{Served on the Manhattan Project.} \emph{Arthur Rogers, 93,
Mooresville, N.C.}

\textbf{Beloved Westchester deputy fire chief.} \emph{Edward Ciocca, 62,
White Plains, N.Y.}

\textbf{Lifelong political radical.} \emph{David Bernstein, 78, New York
City}

\textbf{Employee of the Pilgrim's Pride poultry processing plant.}
\emph{Adelfo Ruiz Calvo, 65, Sanford, N.C.}

\textbf{His love of wildlife and the marshes fueled his soul.}
\emph{Stewart Markham Fish, 58, Hingham, Mass.}

\textbf{Worked long, hard hours and still made time for everyone.}
\emph{Wee Chu Wong, 90, Worcester, Pa.}

\textbf{Would give up the shirt on his back if you needed it.}
\emph{David E. Carman, 89, Egg Harbor Township, N.J.}

\textbf{Educator who taught many offspring of her former students.}
\emph{Marjorie L. Goolsby, 89, Marblehead, Mass.}

\textbf{Child of San Francisco who walked across the Golden Gate Bridge
on opening day.} \emph{Jean Marie Hazelwood, 93, San Mateo, Calif.}

\textbf{Spent her last working days helping those who had the virus.}
\emph{Sheena Renee Comfort Miles, 60, Morton, Miss.}

\textbf{Advocate for gender, racial and L.G.B.T. equality.} \emph{Ruth
E. Shinn, 97, Washington, D.C.}

\textbf{Former mayor, sportscaster.} \emph{Raymond Geraci, 91, Highland
Park, Ill.}

\textbf{Vintage Mississippi macho man.} \emph{Bennie Webb, 85,
Bolingbrook, Ill.}

\textbf{Fierce and vivacious.} \emph{Krist Angielen Guzman, 35,
Bolingbrook, Ill.}

\textbf{Loved Jesus, Elvis, Dr. Pepper and her family.} \emph{Myra Janet
Headley, 72, Memphis}

\textbf{World War II defense worker.} \emph{Jeannette M. Brown, 94,
Amesbury, Mass.}

\textbf{Successful business owner in construction and recycling.}
\emph{Richard M. Cieslak, 76, Red Bud, Ill.}

\textbf{Loved traveling in an R.V.} \emph{Irvin Alder, 91, Novi, Mich.}

\textbf{Artist at heart.} \emph{Patricia L. Henry, 102, Dearborn, Mich.}

\textbf{Taught math for 25 years at Voluntown Elementary School.}
\emph{Ina Macko, 96, Griswold, Conn.}

\textbf{He loved all animals, music and community bingo.} \emph{Randolph
Maitz, 56, Madison, Conn.}

\textbf{Teacher and reading specialist.} \emph{Mary Elizabeth Parr, 80,
Connecticut}

\textbf{Her family believed she would have stayed with them through the
traditional Navajo lifespan of 102 years.} \emph{Mary Ann Yazzie, 96,
Farmington, N.M.}

\textbf{Epic in every sense of the word.} \emph{Richard L. Houle, 86,
Bedford, N.H.}

\textbf{Agent who turned on the C.I.A.} \emph{Ralph W. McGehee, 92,
Falmouth, Maine}

\textbf{Worked in libraries for over 20 years.} \emph{Rosemary Ann
Hughes, 90, Danbury, Conn.}

\textbf{Made the best baklava ever.} \emph{Maria Tassiopoulos, 78,
Braintree, Mass.}

\textbf{Worked beside her husband to transform a rundown dairy farm into
a flourishing business.} \emph{Edna Saikkonen Alve, 92, Spencer, N.Y.}

\textbf{Longtime member of the Sandston Garden Club.} \emph{Gertrude
Clemmer, 91, Sandston, Va.}

\textbf{Enjoyed serving as registrar with the D.A.R.} \emph{Patricia A.
Carrigan, 85, Rush County, Ind.}

\textbf{Her dinners were mouthwateringly good and usually topped off
with a homemade pie or cake.} \emph{Nancy A. Richard, 83, Marblehead,
Mass.}

\textbf{Passionate Boston sports fan.} \emph{Edgar Orlando De La Roca,
46, Peabody, Mass.}

\textbf{Faced the challenges of life with a smile and positive
attitude.} \emph{Clementine E. Jamgochian, 95, Peabody, Mass.}

\textbf{Enjoyed a career in wholesale floorcovering.} \emph{Douglas
Hanby, 86, Shreveport, La.}

\textbf{``uncannily accurate'' in his predictions.} \emph{Philip
Braverman, 87, East Northport, N.Y.}

\textbf{Survived by her longtime companion and many nieces and nephews.}
\emph{Rosalie J. Downes Emrich, 97, Catonsville, Md.}

\textbf{Self-taught musician.} \emph{Kenneth A. Rago, 85, Pocasset,
Mass.}

\textbf{Two-time Purple Heart recipient.} \emph{Patrick Conran, 91,
Riverside, Ill.}

\textbf{Stockbroker and a great listener.} \emph{Edward L. Ghidotti, 87,
Upper Arlington, Ohio}

\textbf{Talented painter well known for his landscapes.} \emph{Joseph
Angeline, 74, Edison, N.J.}

\textbf{Worked for years at many local nursing homes.} \emph{John Pope,
53, Haydenville, Mass.}

\textbf{Made his career as a groundbreaking photographic chemist with
Polaroid.} \emph{Paul James Nagy, 83, Charlottesville, Va.}

\textbf{Longtime AT\&T executive.} \emph{Frank McClellan Worthington,
84, Morristown, N.J.}

\textbf{Retired head nurse who mastered Persian cooking.} \emph{Marjorie
P. Tabechian, 86, New York}

\textbf{Retired as the postmaster at the Mingo Post Office.}
\emph{Jeanette Marie Baldwin, 88, Mingo, Iowa}

\textbf{Quick with his fists in the ring.} \emph{Robert William Dietz,
86, Michigan}

\textbf{Talented tennis player.} \emph{Muriel E. Lundgren, 91,
Haverhill, Mass.}

\textbf{A long career in finance.} \emph{Lawrence Littig, 81, Norwalk,
Conn.}

\textbf{Collector of people, laughter and good stories.} \emph{Bette
Jones, 80, Farmington, Conn.}

\textbf{Explored his Scandinavian roots.} \emph{Arthur Charles Lindholm,
69, Minnesota}

\textbf{World War II veteran, and he proudly drove for generals.}
\emph{Frank M. Goewey Jr., 95, North Carolina}

\textbf{Skilled artist, professional wedding cake decorator and
quilter.} \emph{Mae T. Roser, 92, Manchester, Conn.}

\textbf{A 27-year career at General Motors.} \emph{Shirley Crute, 83,
Ossining, N.Y.}

\textbf{Was in charge of The Bethlehem Globe Times's printing department
for many years.} \emph{John P. Derrico, 78, Fountain Hill, Pa.}

\textbf{Followed her passion in breeding dogs.} \emph{Constance M.
O'Connor, 76, South Berwick, Maine}

\textbf{Rising phoenix.} \emph{Arlene M. Horowitz, 78, Wynnewood, Pa.}

\textbf{Blessed with a coloratura soprano voice and loved to sing ``Ave
Maria.''} \emph{Pilar Molina Reyes Rodriques, 89, Plantsville, Conn.}

\textbf{Loved being Grandpa to his ``little man'' and ``sweet pea.''}
\emph{Robert M. Shaw, 69, Beverly, Mass.}

\textbf{Foster mother for over 10 years.} \emph{Marsha Lee Holiday, 75,
North Andover, Mass.}

\textbf{Went to college at 45.} \emph{Rosemary Hoell Rushka, 89, San
Mateo, Calif.}

\textbf{Loved to travel and dance.} \emph{Maria Lopez, 63, Burbank,
Ill.}

\textbf{Taught in the Bridgewater public elementary schools.}
\emph{Dorothy V. Indeck, 95, Bridgewater, N.J.}

\textbf{All-American athlete.} \emph{Gomer Richards Jr., 84, West
Hurley, N.Y.}

\textbf{Extraordinary photographer, amateur radio operator and gifted
musician.} \emph{Edward J. Deasy Jr., 71, Charlottesville, Va.}

\textbf{Spent countless hours teaching friends how to water ski.}
\emph{Harrison Solliday, 85, Des Moines}

\textbf{Town official in Massachusetts.} \emph{Robert F. Brady Jr., 65,
Avon, Mass.}

\textbf{Loving stay-at-home mom.} \emph{Eileen Marie Stanton, 73, Grand
Forks, N.D.}

\textbf{Loved all animals.} \emph{Cheryl E. Petty, 67, Columbus, Ind.}

\textbf{Proud of her Scottish heritage.} \emph{Arlene Muriel MacIntyre,
84, West Hartford, Conn.}

\textbf{Played for the New York Giants as a halfback.} \emph{Deane K.
Felter, 82, Cromwell, Conn.}

\textbf{Enjoyed crafts, crocheting, playing cards and board games.}
\emph{Elaine Jeannette Beaulieu, 90, East Hartford, Conn.}

\textbf{Known for her respect for animals and her love of physical
health.} \emph{Laura Yopp, 85, South Windsor, Conn.}

\textbf{Raised and trained Labrador retrievers for search and rescue
operations.} \emph{Robert Woodward, 70, Phenix City, Ala.}

\textbf{Decorated Vietnam War veteran.} \emph{Vince Woodward, 77,
Columbus, Ga.}

\textbf{Last living woman member of the W.W. II Monuments team.}
\emph{Motoko Fujishiro Huthwaite, 92, Taylor, Mich.}

\textbf{Onetime publisher of the newspaper The Phoenix.} \emph{Michael
Armstrong, 79, New York City}

\textbf{Many will miss her infectious, sometimes mischievous laughter.}
\emph{Durlene Clontz Shuffler, 85, Morganton, N.C.}

\textbf{His passion for learning was insatiable.} \emph{Carl Gunther
Reiss, 81, Winston-Salem, N.C.}

\textbf{Loved music, especially Christmas carols.} \emph{Michael James
Reagan, 69, Georgetown, Del.}

\textbf{Retired school counselor.} \emph{Loida Cruz Arroyo, 66,
Radcliff, Ky.}

\textbf{Had a passion for cars.} \emph{Kelly Doyle Oliver, 66, Hastings,
Neb.}

\textbf{Talented knitter, a voracious reader, a current events
aficionado.} \emph{Mary T. King, 94, Dorchester, Mass.}

\textbf{Active in the League of Women Voters.} \emph{Mary Doyle Hovanec,
84, Baltimore}

\textbf{Held membership in genealogy societies too numerous to mention.}
\emph{Anna Elizabeth Pearson Lugg, 90, Hillsborough, N.J.}

\textbf{Housekeeper at Riverside Community Hospital for 25 years.}
\emph{Rosa Luna, 68, California}

\textbf{Remembered for the ``nana blankets'' she made for her newborn
grandchildren.} \emph{Anna M. Gayton, 82, Peabody, Mass.}

\textbf{Sheriff's dispatcher.} \emph{Nikima Thompson, 41, Broward
County, Fla.}

\textbf{Avid skier.} \emph{Donald Martin Puffer, 84, Foxboro, Mass.}

\textbf{Navy veteran and the proprietor of Ed's Variety Store in
Selkirk.} \emph{Edward J. Bridgeford Jr., 90, Albany, N.Y.}

\textbf{Very active in the support of 4-H clubs.} \emph{Betty Jo Barney,
91, Green Valley, Ariz.}

\textbf{Served in the Army and worked 40-plus years at Chase Bank.}
\emph{Guy A. LaVignera, 76, Morganville, N.J.}

\textbf{Loved being quiet at the beach.} \emph{Jeanne Madden Cibroski,
79, Cape Cod, Mass.}

\textbf{Woman of many talents.} \emph{Susan C. Menoche, 69, Lincoln,
R.I.}

\textbf{Artist specializing in pastels and sketches.} \emph{Geraldine
Marie McGovern, 72, Massachusetts}

\textbf{Belonged to several fraternal organizations.} \emph{Gerald Alton
Cook, 86, New Jersey}

\textbf{Certified horticulturist.} \emph{Jean M. Winterbottom, 82,
Farmington Hills, Mich.}

\textbf{The presence of Paul Bunyan and the demeanor of a kitten.}
\emph{William Jonathan Glenney, 73, Vernon, Conn.}

\textbf{Feisty and fun to be with.} \emph{Wilma Ruth Montgomery, 91,
Phoenix}

\textbf{Amazing in every sense of the word.} \emph{Mary Ellen Houle, 80,
Bedford, N.H.}

\textbf{Engineer always interested in learning new things.} \emph{Thomas
F. McDermott, 84, Massachusetts}

\textbf{Entered real estate in 1995 as a second career.} \emph{Deloris
C. Traver, 79, Poughkeepsie, N.Y.}

\textbf{Founded his own company, World Insurance Association, Inc.}
\emph{Wayne Drye, 78, Atlanta}

\textbf{Always trying to better herself and family.} \emph{Hildur T.
Stanton, 91, New York}

\textbf{Champion for the rights of Hispanic women.} \emph{Juanita
Sanchez-Valdez, 90, Glendale, Ariz.}

\textbf{Interior designer blending Sikhism through her life.}
\emph{Jaimala Singh, 65, Baltimore}

\textbf{Remembered for his successful career as a tango dancer.}
\emph{Wilman Sanchez Cabrera, 59, New York City}

\textbf{Owner of the beloved Bread Stuy coffee shop.} \emph{Lloyd
Cornelius Porter, 49, New York City}

\textbf{Well-known for her ready smile.} \emph{Linda Benedict, 63,
Lakewood, N.J.}

\textbf{Longtime grocery store manager and sports team booster.}
\emph{James Ronald Conley, 68, Battle Creek, Mich.}

\textbf{She had that Irish wit.} \emph{Florence Cahill Flaherty, 96,
Brewster, Mass.}

\textbf{Always room at the table for her to feed anyone who showed up.}
\emph{Grace Lee Hargrave Cradeur, 83, Crowley, La.}

\textbf{If anyone enjoyed the variety life has to offer, he did.}
\emph{Richard Lynn Heggen, 72, Des Moines}

\textbf{Loved photography, fishing, road trips with friends and time
with her family.} \emph{Terri Lynn Clark, 60, Des Moines}

\textbf{Authored many stories, articles, and an unpublished novel.}
\emph{Richard Edward Rutledge, 87, Folsom, Calif.}

\textbf{Gave every bit of herself to her family.} \emph{Barbara E.
Woznicki, 85, Newington, Conn.}

\textbf{Worked as a school bus driver for 30 years.} \emph{Betty Eleanor
Fennelly, 87, Cromwell, Conn.}

\textbf{Enjoyed playing euchre with her lifelong girlfriends.}
\emph{Evelyn Gertrude Brant-Graf, 87, Zionsville, Ind.}

\textbf{Attended every Presidential inauguration from 1965 until 2012.}
\emph{Alexander Leon Lloyd, 76, Maryland}

\textbf{Fell ill in prison shortly before he was to be released.}
\emph{Melford Henson, 65, Chino, Calif.}

\textbf{First woman elected to the Pohick vestry.} \emph{Anne Turner
Gaillard, 76, Mobile, Ala.}

\textbf{Worked for the F.B.I. during World War II.} \emph{Grace Nutland,
102, Paramus, N.J.}

\textbf{Graduated from high school at the age of 16.} \emph{Georgia
Pearl Lincecum Alebis, 88, Texas}

\textbf{Only one in the family unable to get a green card.} \emph{Carlos
Ernesto Escobar Mejia, 57, San Diego}

\textbf{Known as the ``Bookie,'' she would take and place bets on
anything.} \emph{Merlene Sue Hughes, 67, South Sioux City, Neb.}

\textbf{Cosmetologist who long survived a brain aneurysm.} \emph{Arlene
Chesley, 78, La Plata, Md.}

\textbf{Man of few words.} \emph{Claude Reno Doucette, 84, Connecticut}

\textbf{Advocate for the Alliance for the Mentally Ill.} \emph{Roberta
Gulick, 90, Wrentham, Mass.}

\textbf{Bob Dylan's No. 1 fan and a lover of nature.} \emph{Alexandra
Louise Polansky, 62, New Jersey}

\textbf{Member of the Old Coots on Scoots motorcycle club.} \emph{John
F. Von Sternberg Jr., 79, Mountain Lakes, N.J.}

\textbf{Co-owner of Johnnies Sandwich Shop.} \emph{Dale A. Boston, 81,
Massachusetts}

\textbf{Former member of the Quadrille and Colonial Dames of America.}
\emph{Bettie London Traxler, 97, Greenville, S.C.}

\textbf{Truly a free spirit.} \emph{Lawrence W. Stedl, 68, Green Bay,
Wis.}

\textbf{Avid reader, an accomplished chess player and an exceptional
marksman.} \emph{Thomas Kevin Milo Jr., 43, Westchester County, N.Y.}

\textbf{Long-time member of Grace Lutheran Church.} \emph{Florence Ethel
Buenzly, 99, Allentown, Pa.}

\textbf{Former boxing trainer who owned a well-known Times Square bar.}
\emph{Jimmy Glenn, 89, Manhattan, N.Y.}

\textbf{Found joy in every aspect of her life.} \emph{Amelia Scott
Dougherty, 84, Media, Pa.}

\textbf{Never far from his motorcycles or hot rods.} \emph{Billy
Ostland, 64, Delaware County, Pa.}

\textbf{Seamstress who worked at several sewing mills.} \emph{Joan A.
Lenhart, 84, Wyomissing, Pa.}

\textbf{Involved with the development of Air Force technologies.}
\emph{Douglas H. Diamond, 82, Chelmsford, Mass.}

\textbf{Nothing brought him greater joy than taking his boys on hikes.}
\emph{Robert Grant Conner, 96, Easthampton, Mass.}

\textbf{Lifelong resident of Parsippany, where he was a friend to
everyone.} \emph{Leon Martin Beels, 69, Morristown, N.J.}

\textbf{Served with the Army National Guard for 20 years.} \emph{Frankie
L. Morris Sr., 64, Wooster, Ohio}

\textbf{Served on the Pulaski Polka Days Committee for many years.}
\emph{Randy Wichlacz, 62, Pulaski, Wis.}

\textbf{Enjoyed her daily coffee with her mother-in-law.} \emph{Cindy
Lou Mack, 62, Waverly, N.Y.}

\textbf{One half of Siegfried \& Roy.} \emph{Roy Horn, 75, Las Vegas}

\textbf{Was married for 59 years.} \emph{Lucy Yanushefski, 95, West
Chester, Pa.}

\textbf{Had a passion for cooking, fishing, skiing and cars.}
\emph{Walter Everett Barton, 67, Poughkeepsie, N.Y.}

\textbf{Served as a deacon and especially enjoyed a mission trip to
Peru.} \emph{James C. Whittemore, 83, Johnson City, N.Y.}

\textbf{Cherished mother.} \emph{Alice Glazer, 79, Silver Spring, Md.}

\textbf{He trained aboard the first nuclear-powered vessel in the U.S.
fleet.} \emph{Donald Geoffrey Helliwell, 86, Westfield, Mass.}

\textbf{Very active in the Portuguese community.} \emph{Peter S. Miguel
Jr., 66, Nashua, N.H.}

\textbf{Served as the Iowa president of the League of Women Voters.}
\emph{Janice L. McNelly, 79, Iowa}

\textbf{Loved to spend time at the beach soaking in the sun.}
\emph{Ellen Marie Pauze, 94, Londonderry, N.H.}

\textbf{Loved painting, crocheting and spending time with her family.}
\emph{Tracie L. Heverly, 58, Sebring, Ohio}

\textbf{Held many jobs throughout the years.} \emph{Wilfred Jay Sikkema,
81, Clinton, Iowa}

\textbf{Long-term school district employee.} \emph{Michael Angelo
Church, 72, Plainfield, N.J.}

\textbf{Graduate of Gloucester City High School class of 2009.}
\emph{Rocco Anthony Ward Jr., 29, Gloucester City, N.J.}

\textbf{Lifelong resident of Westernport.} \emph{Tonna Lee Pratt, 69,
Westernport, Md.}

\textbf{We will forever remember her saying, ``Keep the water in the
pool!.''} \emph{Elizabeth N. Updegrave, 91, Reading, Pa.}

\textbf{Performed in many productions at the Salt City Playhouse.}
\emph{Elaine Menchel Marcus, 75, Syracuse, N.Y.}

\textbf{Lifelong career in health care.} \emph{Katherine Ann Birkmaier,
64, Bridgeport, Conn.}

\textbf{Admired for her fashion sense, especially her collection of
hats.} \emph{Mattie F. Adams, 89, Niagara Falls, N.Y.}

\textbf{World War II veteran.} \emph{Nelson Henry Jr., 96, Philadelphia}

\textbf{An esoteric sense of humor.} \emph{P. Michael Baillargeon, 75,
Massachusetts}

\textbf{Died after being released from ICE detention.} \emph{Oscar López
Acosta, 42, Morrow County, Ohio}

\textbf{Had a passion for decorating and an artistic streak.}
\emph{Margaret MacVeagh Schweers, 93, New Jersey}

\textbf{Made each of her children and grandchildren a quilt.}
\emph{Londia Viola Mongold Deavers, 88, Harrisonburg, Va.}

\textbf{Enjoyed delivering day-old bread to church, family and friends.}
\emph{Raymond Gayle Burgett, 86, Des Moines}

\textbf{Kind and brave man, never forgetful of his roots.} \emph{James
Ventrillo, 77, Methuen, Mass.}

\textbf{Lifetime resident of Easton.} \emph{Carl A. Philipp, 84, Easton,
Pa.}

\textbf{Enjoyed golf and watching the Hawkeyes.} \emph{Mary A. Cole, 93,
Cedar Rapids, Iowa}

\textbf{Veteran of the Vietnam War.} \emph{Randolph Warren Whipple, 78,
Plainville, Conn.}

\textbf{Korean War hero and inventor.} \emph{Francis A. Kennedy, 95,
Clarence, N.Y.}

\textbf{Mother to a generation of AIDS patients.} \emph{Nita Pippins,
93, Manhattan, N.Y.}

\textbf{Lifelong Phillies and Eagles fan.} \emph{Michael J. Mchugh, 88,
Philadelphia}

\textbf{Liked golfing and sewing, but loved spending time with family
and friends.} \emph{Mary Ann Bregar, 91, Ohio}

\textbf{Many will remember her half-moon cookies.} \emph{Jeanette
Gilmour, 86, Marcellus, N.Y.}

\textbf{True renaissance man.} \emph{Steven P. St. Laurent, 67, East
Syracuse, N.Y.}

\textbf{Hauled milk by the can, and later with a bulk milk truck.}
\emph{Howard J. Bender, 88, Lancaster, Wis.}

\textbf{Managed Answer Iowa Answering Service in Waterloo for many
years.} \emph{JoAnne Katherine Walther, 74, Cedar Falls, Iowa}

\textbf{Loved going to the zoo, watching soap operas and window
shopping.} \emph{Marilyn Luella Tayse, 75, Ohio}

\textbf{Avid member of the Antique Automobile Club of America.}
\emph{Betty M. Bradshaw, 87, Charlottesville, Va.}

\textbf{Sunday school teacher.} \emph{Mildred W. Blough, 92, Wooster,
Ohio}

\textbf{67-year member of Pipefitters Local 636.} \emph{Ronald R.
Erdman, 90, Novi, Mich.}

\textbf{Priest who sought ``to help people to be happy and holy.''}
\emph{Roland Henry Lacasse, 88, Massachusetts}

\textbf{Avid St. Louis Cardinals and Minnesota Vikings fan.} \emph{Danny
Ray Bierman, 61, Muscatine, Iowa}

\textbf{Painted Hudson River landscapes, portraits and still lifes.}
\emph{Marguerite Peyser, 89, Irvington, N.Y.}

\textbf{Enjoyed trying her luck in the casino.} \emph{Irene S. Allen,
93, Ambler, Pa.}

\textbf{Loved dogs, puzzles and books.} \emph{Darla Eileen Brown, 54,
Sioux City, Iowa}

\textbf{Voracious reader.} \emph{Margueritte Martha McCain, 96, Tulsa,
Okla.}

\textbf{Retired from Verizon after over 40 years of service.}
\emph{Timothy E. Murray, 82, Ocean View, Del.}

\textbf{Her famous quote was ``I am as good as you are, as bad as I
am.''} \emph{Nancy Taylor, 85, Tinton Falls, N.J.}

\textbf{Loved being a mom.} \emph{Mary Santiago, 44, Evanston, Ill.}

\textbf{Pioneer in the field of autism research.} \emph{Thomas A.
Williams, 62, Ohio}

\textbf{Enjoyed visiting casinos, playing bingo and scratching lottery
tickets.} \emph{Carmen Rodriguez, 85, Windsor Locks, Conn.}

\textbf{Attended electronics schools in the Navy.} \emph{Russell D.
Green, 92, Crawfordsville, Ind.}

\textbf{Proud Army veteran who served during WWII.} \emph{Duane G. Vock,
92, Mission, Kan.}

\textbf{Emigrated to the United States in 1963 as a medical resident.}
\emph{Pio Mactal Vilar Jr., 81, Summerlin, Nev.}

\textbf{28-year veteran of the United States Army.} \emph{Alan Michael
Twofoot, 51, Nashua, N.H.}

\textbf{Engine technician in the New Hampshire Air National Guard.}
\emph{Carl J. Hebert Sr., 76, Manchester, N.H.}

\textbf{Had a passion for golf and bridge.} \emph{Joyce Roberts, 96,
Portland, Maine}

\textbf{Proud member of the Ancient Order of Hibernians.} \emph{Robert
M. Sullivan, 88, Springfield, Pa.}

\textbf{Employed at General Electric for 38 years.} \emph{Richard C.
Schug, 83, Syracuse, N.Y.}

\textbf{Survived the German invasion and occupation of Poland during
World War II.} \emph{Genowefa Kochanek, 98, Massachusetts}

\textbf{An Iowa Air National Guardsman.} \emph{Patrick C. Parks, 85,
Sergeant Bluff, Iowa}

\textbf{Attended the Illinois College of Optometry.} \emph{Russell
Arnold Nielsen, 96, Cedar Falls, Iowa}

\textbf{Filled her life by caring for her children and grandchildren.}
\emph{Diana G. DeVito Swist, 80, Norwalk, Conn.}

\textbf{Will be missed at Mad Jack Brewing.} \emph{Dennis Alan Bradt,
29, Colonie, N.Y.}

\textbf{Favorite of all her nieces and nephews.} \emph{Janice Lin
Bisley, 70, Bristol, Conn.}

\textbf{A long, successful retail career, primarily at Macy's.}
\emph{Joel I. Sneider, 74, Miami Beach}

\textbf{Navajo teacher with a sense of duty.} \emph{Marie Pino, 67,
Albuquerque}

\textbf{Happiest when she was barefoot in her flower garden.} \emph{Jean
D. Tobin, 91, Bucks County, Pa.}

\textbf{Her last words were ``thank you.''} \emph{Cornelia Ann Hunt, 87,
Virginia Beach}

\textbf{Never missed ``Wheel of Fortune,'' ``Jeopardy'' or ``Lawrence
Welk.''} \emph{Rita Paas, 88, Comstock Park, Mich.}

\textbf{Her authentic Greek cooking and dancing was second to none.}
\emph{Dorothy Spanos, 90, Orangeburg, N.Y.}

\textbf{A lifelong career with WHIL radio.} \emph{David F. Savitt, 86,
Ludlow, Mass.}

\textbf{Served with the U.S. Marines during the Vietnam War.} \emph{Paul
A. Hamel, 80, Westminster, Mass.}

\textbf{Sketched advertisements for large department stores.}
\emph{Frances A. Orsini, 91, Brick, N.J.}

\textbf{Social worker and political fundraiser.} \emph{Dolores M.
DeLaurentis, 89, Bethlehem, Pa.}

\textbf{Owned a local bar.} \emph{William Hrabnicky, 76, Cleveland}

\textbf{Lived in many places as an Army wife before settling in New
Jersey.} \emph{Dolores M. Madera, 91, Oceanport, N.J.}

\textbf{Champion of people with speech disorders.} \emph{Annie Glenn,
100, St. Paul, Minn.}

\textbf{Correction:}~June 15, 2020

An earlier version of this article misstated Randall Clayton French's
age. He was 39, not 29. The article also misstated the profession of
Sandra Piotrowski, who worked in the accounting departments of several
manufacturing companies, not as a meat-cutter. Additionally, the article
misstated the branch of the military where Irvin Herman served. He
served in the Navy, not the Army.

\textbf{Correction:}~June 23, 2020

An earlier version of this article misstated the age and city of Melita
Baker. She was 86, not 89, and of Norwell, Mass., not Irvington, N.Y.

Read 52 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
