Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/world}{World}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/world}{World}\textbar{}Bush Steps Away From Victory
Banner

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{bush-steps-away-from-victory-banner}{%
\section{Bush Steps Away From Victory
Banner}\label{bush-steps-away-from-victory-banner}}

Oct. 29, 2003

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

The triumphal ''Mission Accomplished'' banner was the pride of the White
House advance team, the image makers who set the stage for the
president's close-ups. On May 1, on a golden Pacific evening aboard the
carrier Abraham Lincoln, they made sure that the banner was perfectly
captured in the camera shots of President Bush's speech declaring major
combat in Iraq at an end.

But on Tuesday in the Rose Garden, Mr. Bush publicly disavowed the
banner that had come to symbolize what his critics said was a premature
declaration that the United States had prevailed.

''The 'Mission Accomplished' sign, of course, was put up by the members
of the U.S.S. Abraham Lincoln, saying that their mission was
accomplished,'' Mr. Bush told reporters. ''I know it was attributed
somehow to some ingenious advance man from my staff. They weren't that
ingenious, by the way.''

Well, yes and no. After the news conference, the White House press
secretary, Scott McClellan, carefully elaborated on the president's
words.

The banner ''was suggested by those on the ship,'' he said. ''They asked
us to do the production of the banner, and we did. They're the ones who
put it up.''

The man responsible for the banner, Scott Sforza, a former ABC producer
now with the White House communications office, was traveling overseas
on Tuesday and declined to answer questions. He is known for the
production of the sophisticated backdrops that appear behind Mr. Bush
with the White House message of the day, like ''Helping Small
Business,'' repeated over and over.

Mr. Bush's Democratic competitors for president immediately pounced on
his disavowal.

Gen. Wesley K. Clark, for one, said that Mr. Bush's comments blaming the
sailors ''for something his advance team staged'' were ''outrageous.''

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
