Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/news-event/2020-election}{Elections}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/news-event/2020-election}{Elections}\textbar{}2020 Presidential
Primary Election Calendar

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\begin{itemize}
\item
  \href{https://www.nytimes.com/2020/07/31/us/elections/biden-vs-trump.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Election
  Updates}
\item
  \href{https://www.nytimes.com/article/biden-vice-president-2020.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Biden's
  V.P. Search}
\item
  \href{https://www.nytimes.com/interactive/2020/07/24/us/politics/trump-biden-campaign-donors.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Map
  of Donations}
\item
  \href{https://www.nytimes.com/interactive/2020/us/elections/delegate-count-primary-results.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Delegate
  Count}
\item
  \href{https://www.nytimes.com/interactive/2019/us/politics/2020-presidential-candidates.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{The
  Candidates}
\item
  \href{https://www.nytimes.com/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Politics
  Newsletter}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{2020 Presidential Primary Election Calendar}\href{}{Skip to
Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@nytimes.com}{\nolinkurl{letters@nytimes.com}}.

\hypertarget{2020-presidential-primary-election-calendar}{%
\section{2020 Presidential Primary Election
Calendar}\label{2020-presidential-primary-election-calendar}}

By \href{https://www.nytimes.com/by/sarah-almukhtar}{Sarah Almukhtar},
\href{https://www.nytimes.com/by/jonathan-martin}{Jonathan Martin} and
\href{https://www.nytimes.com/by/matt-stevens}{Matt Stevens}Updated June
12, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{11}
\end{itemize}

144 days

until Election Day

The 2020 presidential election may still be months away, but the primary
process is now underway. Numerous states and territories have
\href{https://www.nytimes.com/article/2020-campaign-primary-calendar-coronavirus.html}{rescheduled
their primaries} because of the coronavirus outbreak. Here's a calendar
of key events.
(\href{https://www.nytimes.com/interactive/2020/us/elections/delegate-count-primary-results.html}{Looking
for results?})

Debates

Primaries and Caucuses

National Conventions

General Election

\hypertarget{january}{%
\subsection{January}\label{january}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & & 1 & 2 & 3 & 4\tabularnewline
5 & 6 & 7 & 8 & 9 & 10 & 11\tabularnewline
12 & 13 & 14 & 15 & 16 & 17 & 18\tabularnewline
19 & 20 & 21 & 22 & 23 & 24 & 25\tabularnewline
26 & 27 & 28 & 29 & 30 & 31 &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{february}{%
\subsection{February}\label{february}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & & & & & 1\tabularnewline
2 & 3 & 4 & 5 & 6 & 7 & 8\tabularnewline
9 & 10 & 11 & 12 & 13 & 14 & 15\tabularnewline
16 & 17 & 18 & 19 & 20 & 21 & 22\tabularnewline
23 & 24 & 25 & 26 & 27 & 28 & 29\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{march}{%
\subsection{March}\label{march}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
1 & 2 & 3 & 4 & 5 & 6 & 7\tabularnewline
8 & 9 & 10 & 11 & 12 & 13 & 14\tabularnewline
15 & 16 & 17 & 18 & 19 & 20 & 21\tabularnewline
22 & 23 & 24 & 25 & 26 & 27 & 28\tabularnewline
29 & 30 & 31 & & & &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{april}{%
\subsection{April}\label{april}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & & 1 & 2 & 3 & 4\tabularnewline
5 & 6 & 7 & 8 & 9 & 10 & 11\tabularnewline
12 & 13 & 14 & 15 & 16 & 17 & 18\tabularnewline
19 & 20 & 21 & 22 & 23 & 24 & 25\tabularnewline
26 & 27 & 28 & 29 & 30 & &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{may}{%
\subsection{May}\label{may}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & & & & 1 & 2\tabularnewline
3 & 4 & 5 & 6 & 7 & 8 & 9\tabularnewline
10 & 11 & 12 & 13 & 14 & 15 & 16\tabularnewline
17 & 18 & 19 & 20 & 21 & 22 & 23\tabularnewline
24 & 25 & 26 & 27 & 28 & 29 & 30\tabularnewline
31 & & & & & &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{june}{%
\subsection{June}\label{june}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& 1 & 2 & 3 & 4 & 5 & 6\tabularnewline
7 & 8 & 9 & 10 & 11 & 12 & 13\tabularnewline
14 & 15 & 16 & 17 & 18 & 19 & 20\tabularnewline
21 & 22 & 23 & 24 & 25 & 26 & 27\tabularnewline
28 & 29 & 30 & & & &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{july}{%
\subsection{July}\label{july}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & & 1 & 2 & 3 & 4\tabularnewline
5 & 6 & 7 & 8 & 9 & 10 & 11\tabularnewline
12 & 13 & 14 & 15 & 16 & 17 & 18\tabularnewline
19 & 20 & 21 & 22 & 23 & 24 & 25\tabularnewline
26 & 27 & 28 & 29 & 30 & 31 &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{august}{%
\subsection{August}\label{august}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & & & & & 1\tabularnewline
2 & 3 & 4 & 5 & 6 & 7 & 8\tabularnewline
9 & 10 & 11 & 12 & 13 & 14 & 15\tabularnewline
16 & 17 & 18 & 19 & 20 & 21 & 22\tabularnewline
23 & 24 & 25 & 26 & 27 & 28 & 29\tabularnewline
30 & 31 & & & & &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{september}{%
\subsection{September}\label{september}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & 1 & 2 & 3 & 4 & 5\tabularnewline
6 & 7 & 8 & 9 & 10 & 11 & 12\tabularnewline
13 & 14 & 15 & 16 & 17 & 18 & 19\tabularnewline
20 & 21 & 22 & 23 & 24 & 25 & 26\tabularnewline
27 & 28 & 29 & 30 & & &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{october}{%
\subsection{October}\label{october}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
& & & & 1 & 2 & 3\tabularnewline
4 & 5 & 6 & 7 & 8 & 9 & 10\tabularnewline
11 & 12 & 13 & 14 & 15 & 16 & 17\tabularnewline
18 & 19 & 20 & 21 & 22 & 23 & 24\tabularnewline
25 & 26 & 27 & 28 & 29 & 30 & 31\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{november}{%
\subsection{November}\label{november}}

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\endhead
1 & 2 & 3 & 4 & 5 & 6 & 7\tabularnewline
8 & 9 & 10 & 11 & 12 & 13 & 14\tabularnewline
15 & 16 & 17 & 18 & 19 & 20 & 21\tabularnewline
22 & 23 & 24 & 25 & 26 & 27 & 28\tabularnewline
29 & 30 & & & & &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{primaries-and-caucuses}{%
\subsection{Primaries and Caucuses}\label{primaries-and-caucuses}}

From the Iowa caucuses to Election Day, here is a look at which states
vote when, and where the largest troves of delegates are at stake.

February 2020

Dem.

Democratic

Rep.

Republican

3 Mon.

Iowa caucuses

Because these are the first votes cast, there is a lot at stake in terms
of momentum and attention from donors and the news media. The results
here will winnow the field.

41

40

11 Tue.

New Hampshire primaries

Don't be surprised if only a few candidates are still standing after the
votes are counted here.

24

22

22 Sat.

Nevada Democratic caucuses

Another key early state with a high-turnout caucus, and the first one
with a significant Hispanic population.

36

29 Sat.

South Carolina Democratic primary

This state will offer the first real indication of the candidates'
strengths with black voters.

54

March 2020

Dem.

Democratic

Rep.

Republican

3 Tue.

Alabama primaries

Super Tuesday accounts for about one-third of total delegate allocation.

52

50

American Samoa Democratic caucus

6

Arkansas primaries

31

40

California primaries

Because it has the largest delegate trove in the country, California is
key to Super Tuesday.

415

172

Colorado primaries

67

34

Maine primaries

24

22

Massachusetts primaries

91

41

Minnesota primaries

75

39

North Carolina primaries

110

71

Oklahoma primaries

37

43

Tennessee primaries

64

58

Texas primaries*

The third-largest delegate trove of the primary.

228

155

Utah primaries

29

40

Vermont primaries

16

17

Virginia Democratic primary

99

Democrats Abroad primary

13

10 Tue.

Idaho primaries

20

32

Michigan primaries

Midwestern powerhouses like Michigan will test the candidates' appeal
among suburbanites, African-Americans and working-class white voters. If
the race is not decided on Super Tuesday, this could be a line of
demarcation.

125

73

Mississippi primaries

36

40

Missouri primaries

68

54

North Dakota Democratic caucuses

14

Washington primaries

89

44

12 Thu.

Virgin Islands Republican caucus*

6

14 Sat.

Guam Republican caucus*

6

Northern Marianas Democratic convention

6

17 Tue.

Arizona Democratic primary

If one candidate sweeps Arizona, Florida and Illinois, there will be
immense pressure on the other candidates to exit the race.

67

Florida primaries

219

122

Illinois primaries

155

67

Northern Marianas Republican caucus*

9

24 Tue.

American Samoa Republican caucus*

6

T.B.D.

Wyoming Republican county conventions

12

April 2020

Dem.

Democratic

Rep.

Republican

7 Tue.

Wisconsin primaries

Wisconsin's Supreme Court ruled on Monday, April 6, that the governor
could not postpone the state's primary over concerns about the
coronavirus.

84

52

10 Fri.

Alaska Democratic primary

Alaska canceled in-person voting and extended its deadline for mail-in
ballots until April 10 because of the coronavirus pandemic. Voting was
originally scheduled for April 4.

15

17 Fri.

Wyoming Democratic caucuses

Wyoming canceled in-person caucuses and extended its deadline for
mail-in ballots until April 17 because of the coronavirus pandemic.
Voting was originally scheduled for April 4.

14

28 Tue.

Ohio primaries

Ohio postponed its presidential primary, originally scheduled on March
17, because of the coronavirus pandemic. Most voters must cast their
ballot by mail.

136

82

May 2020

Dem.

Democratic

Rep.

Republican

2 Sat.

Kansas Democratic primary

39

7-9 Thu.

Wyoming Republican state convention

14

12 Tue.

Nebraska primaries

29

36

19 Tue.

Oregon primaries

61

28

22 Fri.

Hawaii Democratic primary

Hawaii canceled in-person voting and extended its deadline for mail-in
ballots until May 22 because of the coronavirus pandemic. Voting was
originally scheduled for April 4.

24

T.B.D.

Guam Democratic caucus

Guam's Democratic caucus, originally scheduled for May 2, was postponed
because of the coronavirus pandemic. A new date has not been set.

7

June 2020

Dem.

Democratic

Rep.

Republican

2 Tue.

District of Columbia primaries

20

19

Indiana primaries

Indiana postponed its presidential primary, originally scheduled on May
5, because of the coronavirus pandemic.

82

58

Maryland primaries

Maryland postponed its presidential primary, originally scheduled on
April 28, because of the coronavirus pandemic. Most voters must cast
their ballot by mail.

96

38

Montana primaries

19

27

New Mexico primaries

34

22

Pennsylvania primaries

Pennsylvania postponed its presidential primary, originally scheduled on
April 28, because of the coronavirus pandemic.

186

34

Rhode Island primaries

Rhode Island postponed its presidential primary, originally scheduled on
April 28, because of the coronavirus pandemic.

26

19

South Dakota primaries*

16

29

6 Sat.

Virgin Islands Democratic caucuses

7

7 Sun.

Puerto Rico Republican primary*

23

9 Tue.

Georgia primaries

Georgia postponed its presidential primary, originally scheduled on
March 24, because of the coronavirus pandemic.

105

76

West Virginia primaries

West Virginia postponed its presidential primary, originally scheduled
on May 12, because of the coronavirus pandemic.

28

34

23 Tue.

Kentucky primaries

Kentucky postponed its presidential primary, originally scheduled on May
19, because of the coronavirus pandemic.

54

46

New York primaries

New York canceled its already-postponed presidential primary after the
Democratic presidential race was settled, but a federal judge has now
ordered that the election go forward in June.

274

95

July 2020

Dem.

Democratic

Rep.

Republican

7 Tue.

Delaware primaries

Delaware postponed its presidential primary, originally scheduled on
April 28, because of the coronavirus pandemic.

21

16

New Jersey primaries

New Jersey postponed its presidential primary, originally scheduled on
June 2, because of the coronavirus pandemic.

126

49

11 Sat.

Louisiana primaries

Louisiana postponed its presidential primary, originally scheduled on
April 4, because of the coronavirus pandemic.

54

46

12 Sun.

Puerto Rico Democratic primary

Puerto Rico postponed its presidential primary, originally scheduled on
March 29, because of the coronavirus pandemic.

51

August 2020

Dem.

Democratic

Rep.

Republican

11 Tue.

Connecticut primaries

Connecticut postponed its presidential primary, originally scheduled on
April 28, because of the coronavirus pandemic.

60

28

17-20 Mon.

Democratic National Convention

Democratic officials postponed the convention, originally planned for
mid-July, because of the coronavirus pandemic. It will still be held in
Milwaukee, placing a spotlight on a key Midwestern battleground state.

24-27 Mon.

Republican National Convention

The Republicans are scheduled to hold their convention in Charlotte,
N.C. Mr. Trump will deliver his convention speech in Jacksonville, Fla.,
on Aug. 27.

November 2020

3 Tue.

Election Day

Canceled

Dem.

Democratic

Rep.

Republican

Alaska Republican polls

28

Arizona Republican primary

58

Hawaii Republican caucuses

19

Kansas Republican caucuses

39

Nevada Republican caucuses

25

South Carolina Republican primary

50

Virginia Republican primary

49

*The date for one or more listed events is tentative.\\
A darker shade of red or blue indicates states with more delegates.·Some
states' Republican parties have
\href{https://www.nytimes.com/2019/09/06/us/politics/states-drop-republican-primaries.html}{canceled
presidential primaries}, saying the practice is not unusual when an
incumbent is running for re-election. President Trump's challengers have
denounced the move as undemocratic.

\hypertarget{upcoming-debates}{%
\subsection{Upcoming Debates}\label{upcoming-debates}}

Democrats held six
\href{https://www.nytimes.com/news-event/democratic-debates}{primary
debates} in 2019 and five in 2020 so far.

2020

Sept. 29

Notre Dame, Ind.

First presidential debate

University of Notre Dame

Oct. 7

Salt Lake City

Vice presidential debate

University of Utah

Oct. 15

Ann Arbor

Second presidential debate

University of Michigan

Oct. 22

Nashville

Third presidential debate

Belmont University

\hypertarget{past-debates}{%
\subsection{Past Debates}\label{past-debates}}

2019

June 26-27

Miami

First Democratic primary debate

Split over two nights; broadcast on NBC, MSNBC and Telemundo.

July 30-31

Detroit

Second Democratic primary debate

Also held over two nights; broadcast on CNN, CNN International and CNN
en Español.

Sept. 12

Houston

Third Democratic primary debate

Broadcast on ABC and Univision.

Oct. 15

Westerville, Ohio

Fourth Democratic primary debate

Co-hosted by The New York Times and CNN.

Nov. 20

Atlanta

Fifth Democratic primary debate

Co-hosted by MSNBC and The Washington Post.

Dec. 19

Los Angeles

Sixth Democratic primary debate

Co-hosted by PBS NewsHour and Politico at Loyola Marymount University.

2020

Jan. 14

Des Moines

Seventh Democratic primary debate

Co-hosted by CNN and The Des Moines Register at Drake University.

Feb. 7

Manchester, N.H.

Eighth Democratic primary debate

Co-hosted by ABC, WMUR and Apple News at St. Anselm College.

Feb. 19

Las Vegas

Ninth Democratic primary debate

Co-hosted by NBC News, MSNBC, Twitter and The Nevada Independent at The
Paris Theater.

Feb. 25

Charleston, S.C.

Tenth Democratic primary debate

Co-hosted by CBS News and the Congressional Black Caucus Institute at
The Gaillard Center. Twitter will be a debate partner.

March 15

Washington, D.C.

Eleventh Democratic primary debate

Co-hosted by CNN and Univision. The debate was moved from Phoenix to
Washington because of concerns about the coronavirus.

April

Twelfth Democratic primary debate

No date has been scheduled.

Sources: The Green Papers, Democratic National Committee \textbar{}
Note: Graphic only includes pledged delegates. Dates and delegate
allocations may change, and this page will be updated as we learn of
them. \href{mailto:election@nytimes.com}{Email us} with any updates.

Additional work by Aliza Aufrichtig.

\textbf{Correction:}~June 24, 2019

An earlier version of this article misspelled a state name. It is
Massachusetts, not Massachussetts.

\textbf{Correction:}~June 25, 2019

An earlier version of this article omitted Utah's presidential
primaries. They will be held on March 3, 2020.

\textbf{Correction:}~March 30, 2020

An earlier version of this article misstated the day of the week of the
Alaska Democratic primary. April 10, 2020, is a Friday, not a Saturday.

Read 11 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

\hypertarget{our-2020-election-guide}{%
\section{Our 2020 Election Guide}\label{our-2020-election-guide}}

Updated July 31, 2020

\begin{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{the-latest}{%
  \subsection{The Latest}\label{the-latest}}

  \begin{itemize}
  \tightlist
  \item
    President Trump's assault on the Postal Service is intersecting with
    his attacks on mail-in voting.
    \href{https://www.nytimes.com/2020/07/31/us/politics/trump-usps-mail-delays.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{Voting
    rights groups say it is a recipe for disaster.}
  \end{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{bidens-vp-search}{%
  \subsection{Biden's V.P. Search}\label{bidens-vp-search}}

  \begin{itemize}
  \tightlist
  \item
    \href{https://www.nytimes.com/article/biden-vice-president-2020.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{Here
    are 13 women} who have been under consideration to be Joe Biden's
    running mate, and why each might be chosen --- and might not be.
  \end{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{keep-up-with-our-coverage}{%
  \subsection{Keep Up With Our
  Coverage}\label{keep-up-with-our-coverage}}

  \begin{itemize}
  \tightlist
  \item
    Get an
    \href{https://www.nytimes.com/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{email}
    recapping the day's news
  \end{itemize}

  \begin{itemize}
  \tightlist
  \item
    Download our mobile app on
    \href{https://apps.apple.com/us/app/nytimes/id284862083?ls=1\&mat_click_id=5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\&referrer=mat_click_id\%3D5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\%26link_click_id\%3D722930677036718082}{iOS}
    and
    \href{http://a.localytics.com/android?id=com.nytimes.android\&referrer=utm_source\%3Dother_nyt_mobile_web\%26utm_medium\%3DWeb\%2520page\%26utm_term\%3DGeneral\%2520Mobile\%2520Page\%26utm_campaign\%3DNYT\%2520Mobile\%2520General\%2520Page}{Android}
    and turn on Breaking News and Politics alerts
  \end{itemize}
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
