\href{//www.nytimes3xbfgragh.onion}{}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{
Election 2018}

\href{//www.nytimes3xbfgragh.onion}{ Home}

\hypertarget{washington-primary-election-results-third-house-district}{%
\section{Washington Primary Election Results: Third House
District}\label{washington-primary-election-results-third-house-district}}

By THE NEW YORK TIMES Sept. 24, 2018, 6:06 PM ET

Statewide vote totals are official tallies from the secretary of state.
County totals are unofficial results from the Associated Press and may
be incomplete.

\href{https://www.nytimes3xbfgragh.onion/2018/08/07/us/politics/primary-election-today.html}{\emph{Read
more about today's most important races.}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Herrera Beutler* Jaime Herrera Beutler* & Republican Rep. & 68,961 &
42.1\% &\tabularnewline
 Long Carolyn Long & Democrat Dem. & 57,798 & 35.3\% &\tabularnewline
 McDevitt David McDevitt & Democrat Dem. & 13,124 & 8.0\%
&\tabularnewline
 Bowerman Earl Bowerman & Republican Rep. & 9,018 & 5.5\%
&\tabularnewline
 Gasque Dorothy Gasque & Democrat Dem. & 7,983 & 4.9\% &\tabularnewline
 Cortney Michael Cortney & Republican Rep. & 5,528 & 3.4\%
&\tabularnewline
 Hash Martin Hash & Democrat Dem. & 1,498 & 0.9\% &\tabularnewline
 Others Others & & 24,027 & 14.7\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

163,910 votes, 100\% reporting (202 of 202 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

* Incumbent

Leader

 Herrera Beutler

 Long

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{2016
Washington Results »}

Source: Election results and race calls from The Associated Press.
Official statewide congressional results from the Washington State
secretary of state

By Sarah Almukhtar, Wilson Andrews, Matthew Bloch, Jeremy Bowers, Tom
Giratikanon, Jasmine C. Lee and Paul Murray.

\hypertarget{see-election-results-for-2018-2017-2016-2014-2012-2010-2008}{%
\subsubsection{\texorpdfstring{See election results for
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{2018}
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/us/elections/election-calendar.html}{2017}
\href{https://www.nytimes3xbfgragh.onion/elections/results/president}{2016}
\href{https://www.nytimes3xbfgragh.onion/elections/2014/results/senate}{2014}
\href{https://www.nytimes3xbfgragh.onion/elections/2012/results/president.html}{2012}
\href{https://www.nytimes3xbfgragh.onion/elections/2010/results/senate.html}{2010}
\href{https://www.nytimes3xbfgragh.onion/elections/2008/results/president/map.html}{2008}}{See election results for 2018 2017 2016 2014 2012 2010 2008}}\label{see-election-results-for-2018-2017-2016-2014-2012-2010-2008}}

\hypertarget{more-on-nytimescom}{%
\subsubsection{More on NYTimes.com}\label{more-on-nytimescom}}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2018 The New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2018 The New York Times Company}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/infoservdirectory.html}{Contact
  Us}
\item
  \href{http://www.nytco.com/careers}{Work With Us}
\item
  \href{http://www.nytimes.whsites.net/mediakit}{Advertise}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/privacy/policy/privacy-policy.html\#pp}{Your
  Ad Choices}
\item
  \href{http://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/agree.html}{Terms
  of Service}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/sale/terms-of-sale.html}{Terms
  of Sale}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{http://www.nytimes3xbfgragh.onion/membercenter/sitehelp.html}{Help}
\item
  \href{https://myaccount.nytimes3xbfgragh.onion/membercenter/feedback.html}{Site
  Feedback}
\item
  \href{http://www.nytimes3xbfgragh.onion/subscriptions/Multiproduct/lp5558.html?campaignId=37WXW}{Subscriptions}
\end{itemize}
