Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/corrections}{Corrections}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/corrections}{Corrections}\textbar{}Corrections: Aug. 5,
2020

\url{https://nyti.ms/2BYk2Ie}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{corrections-aug-5-2020}{%
\section{Corrections: Aug. 5, 2020}\label{corrections-aug-5-2020}}

Corrections that appeared in print on Wednesday, Aug. 5, 2020.

Aug. 4, 2020

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{front-page}{%
\subsection{FRONT PAGE}\label{front-page}}

An
\href{https://www.nytimes.com/2020/08/01/world/europe/germany-nazi-infiltration.html}{article}
on Sunday about a far-right network in Germany misstated one of the uses
of quicklime. It can be used to mask the stench of decomposing bodies,
not to decompose organic material.

\hypertarget{international}{%
\subsection{INTERNATIONAL}\label{international}}

An
\href{https://www.nytimes.com/2020/07/31/world/americas/brazil-trump-ethanol-chapman.html}{article}
on Saturday about an inquiry by the House Foreign Affairs Committee into
reports that the U.S. ambassador to Brazil framed negotiations over
ethanol tariffs in partisan terms misstated the date of Brazil's
municipal elections. They are scheduled to take place in November, not
September.

An
\href{https://www.nytimes.com/2020/08/02/world/europe/genoa-Morandi-bridge-replacement.html}{article}
on Monday about the new Genoa San Giorgio bridge misstated the location
of Genoa, Italy. It is in the country's northwest, not northeast.

\hypertarget{sports}{%
\subsection{SPORTS}\label{sports}}

An
\href{https://www.nytimes.com/2020/08/03/sports/baseball/indians-team-names-mascots.html}{article}
on Tuesday about a minor-league baseball team that chose to keep its
name despite a reference to Native Americans misstated the month that a
football team said it would change its name. The Washington N.F.L. Team
abandoned its nickname last month, not earlier this month.

\hypertarget{dining}{%
\subsection{DINING}\label{dining}}

An
\href{https://www.nytimes.com/2020/01/06/dining/indian-pickle-queen-usha-prabakaran.html}{article}
on Jan. 8 about Usha Prabakaran, the Indian author of a classic cookbook
on pickling, described incorrectly the soup known as rasam. It is often
vegetarian, but not always. (This correction was delayed because the
error was only recently brought to editors' attention.)

\emph{Errors are corrected during the press run whenever possible, so
some errors noted here may not have appeared in all editions.}

\emph{To contact the newsroom regarding correction requests, complaints
or other comments about our coverage, please email}
\href{mailto:nytnews@nytimes.com}{\emph{nytnews@nytimes.com}}\emph{.}

\emph{Comments on editorials may be emailed to}
\href{mailto:letters@nytimes.com}{\emph{letters@nytimes.com}}\emph{.}

\emph{For newspaper delivery questions: 1-800-NYTIMES (1-800-698-4637)
or email}
\href{mailto:customercare@nytimes.com}{\emph{customercare@nytimes.com}}\emph{.}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
