Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/books}{Books}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/books}{Books}\textbar{}Daniel Nieh's `Beijing Payback' Is
August's Book Club Pick

\url{https://nyti.ms/2FkT3n6}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

Now Read This

\hypertarget{daniel-niehs-beijing-payback-is-augusts-book-club-pick}{%
\section{Daniel Nieh's `Beijing Payback' Is August's Book Club
Pick}\label{daniel-niehs-beijing-payback-is-augusts-book-club-pick}}

Jan. 9, 2018

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Introducing the PBS NewsHour-New York Times book
clubCredit...CreditVideo by PBS NewsHour

\emph{Now Read This is a book club offered jointly from the PBS NewsHour
and The New York Times. Every month, we'll pick a book that helps us
make sense of the world we're living in --- fiction, history, memoir and
more.}

\textbf{How long do I have to read the book?}

A month! We'll announce the book pick at the beginning of every month.

\textbf{What else does the book club provide?}

As you read, we'll post discussion questions and other material related
to the book, including reviews from The Times reviews and writing advice
from the author, as well as inside looks at how the book was written. Be
sure to join our Facebook group,
\href{https://www.facebookcorewwwi.onion/groups/NowReadThisBookClub/}{Now
Read This}, and visit throughout the month, where we'll discuss the book
with you as you read along.

\textbf{How do I get a question to the author?}

You can submit questions about the book on our
\href{https://www.facebookcorewwwi.onion/groups/NowReadThisBookClub/}{Facebook
group} or to our
\href{https://docs.google.com/forms/d/e/1FAIpQLScCrXPslIAloxbvQHhHrNmhhzQ2_dfzJu-FP7ja8XpQnDPhpw/viewform}{Google
form}, if you are not on Facebook. At the end of the month, the author
will appear on the PBS NewsHour and take your questions.

\textbf{Can my book club read along?}

Absolutely! We'd love it if your local book club read along with us. We
invite you to use our
\href{https://www.pbs.org/newshour/features/now-read-this/}{discussion
questions} and author insight as a guide, to submit your members' own
questions for the author, and to play our video interviews with the
author during your book club meetings.

\textbf{Where can I get the book?}

Most of our book picks will be in paperback. You can find the book in
your local library, bookstore or online.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
