Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/world/asia}{Asia
Pacific}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/world/asia}{Asia Pacific}\textbar{}Japan Protests
Indictment of Journalist by South Korea

\url{https://nyti.ms/1tgk9Dl}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{japan-protests-indictment-of-journalist-by-south-korea}{%
\section{Japan Protests Indictment of Journalist by South
Korea}\label{japan-protests-indictment-of-journalist-by-south-korea}}

By \href{http://www.nytimes3xbfgragh.onion/by/martin-fackler}{Martin
Fackler}

\begin{itemize}
\item
  Oct. 9, 2014
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

ASAHIKAWA, Japan --- Japan's Foreign Ministry summoned a South Korean
diplomat on Thursday to protest the filing of charges against a Japanese
journalist in Seoul, in the latest spat to divide the two countries.

The ministry made the move to oppose the indictment the day before of
Tatsuya Kato, 48, the former Seoul bureau chief for the Japanese
newspaper Sankei Shimbun. South Korean prosecutors charged Mr. Kato with
defaming the South Korean president, Park Geun-hye. Mr. Kato has not
been arrested, but he is barred from leaving South Korea.

Mr. Kato was indicted over an article published in early August that
suggested, without providing evidence, that Ms. Park was slow to respond
to the deadly sinking in April of the ferry Sewol because she might have
been having a romantic encounter with a former aide at the time. South
Korean officials have dismissed the allegation as false.

In his article, Mr. Kato cited as a source an earlier column by the
Chosun Ilbo, a major South Korean newspaper, that made oblique
references to rumors about what Ms. Park was doing in the early hours of
the disaster.

The fact that Korean prosecutors have not pressed charges against the
Korean newspaper, but only against the Sankei, a conservative newspaper
that has been critical of South Korea on history issues, has led some
Japanese to call the indictment politically motivated.

In its indictment, the Seoul Central District Prosecutors' Office
accused Mr. Kato of not making ``minimum efforts'' to verify what he
wrote.

On Thursday, Junichi Ihara, Japan's Foreign Ministry official in charge
of Asian affairs, called in Kim Won-jin, a minister at the South Korean
Embassy in Tokyo, to protest the indictment.

Mr. Ihara told Mr. Kim that the charges were ``extremely regrettable in
the view of the freedom of the press and Japan-South Korea relations,''
according to Japan's Kyodo News agency.

Mr. Kim defended the prosecutors' actions, saying that they were based
on South Korean law and had nothing to do with diplomatic relations,
Kyodo said.

If found guilty, Mr. Kato faces up to seven years in prison.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
