 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{/section/climate}{Climate} \textbar{}The Trump Administration Is
Reversing 100 Environmental Rules. Here's the Full List.

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\href{}{}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-climate-}{%
\subsection{\texorpdfstring{ \href{/section/climate}{Climate}
}{ Climate }}\label{-climate-}}

\hypertarget{the-trump-administration-is-reversing-100-environmental-rules-heres-the-full-list}{%
\section{The Trump Administration Is Reversing 100 Environmental Rules.
Here's the Full
List.}\label{the-trump-administration-is-reversing-100-environmental-rules-heres-the-full-list}}

68

completed

32

in progress

100

total rollbacks

After three years in office, the Trump administration has dismantled
most of the major climate and environmental policies the president
promised to undo.

Calling the rules unnecessary and burdensome to the fossil fuel industry
and other businesses, his administration has weakened Obama-era limits
on planet-warming carbon dioxide emissions
\href{https://www.nytimes3xbfgragh.onion/2019/06/19/climate/epa-coal-emissions.html}{from
power plants} and from
\href{https://www.nytimes3xbfgragh.onion/2020/03/30/climate/trump-fuel-economy.html}{cars
and trucks}, and rolled back many more rules governing clean air, water
and toxic chemicals. Several major reversals have been finalized in
recent months as the country has struggled to contain the spread of the
new coronavirus.

In all, a New York Times analysis, based on research from
\href{https://eelp.law.harvard.edu/regulatory-rollback-tracker/}{Harvard
Law School},
\href{http://columbiaclimatelaw.com/resources/climate-deregulation-tracker/}{Columbia
Law School} and other sources, counts nearly 70 environmental rules and
regulations officially reversed, revoked or otherwise rolled back under
Mr. Trump. More than 30 additional rollbacks are still in progress.

\subsection{}

Completed

In progress

Total

Air pollution and emissions

 19 overturned

 8 in progress

 27 total

Drilling and extraction

 11 overturned

 8 in progress

 19 total

Infrastructure and planning

 12 overturned

 1 in progress

 13 total

Animals

 11 overturned

 1 in progress

 12 total

Water pollution

 4 overturned

 7 in progress

 11 total

Toxic substances and safety

 6 overturned

 2 in progress

 8 total

Other

 5 overturned

 5 in progress

 10 total

All

 68 overturned

 32 in progress

 100 total

With elections looming, the administration has sought to wrap up some of
its biggest regulatory priorities quickly, said Hana V. Vizcarra, a
staff attorney at Harvard Law School's Environmental and Energy Law
Program. Further delays could leave the new rules
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/05/01/us/politics/trump-obama-regulations-reversed.html}{vulnerable
to reversal under the Congressional Review Act} if Democrats are able to
retake Congress and the White House in November, she said.

The bulk of the rollbacks identified by the Times have been carried out
by the Environmental Protection Agency, which repealed and replaced the
Obama-era emissions rules for power plants and vehicles; weakened
\href{https://www.nytimes3xbfgragh.onion/2020/01/22/climate/trump-environment-water.html}{protections
for more than half the nation's wetlands}; and withdrew
\href{https://www.nytimes3xbfgragh.onion/2020/04/16/climate/epa-mercury-coal.html}{the
legal justification for restricting mercury emissions from power
plants}.

At the same time, the Interior Department has worked to open up more
land for oil and gas leasing by
\href{https://www.nytimes3xbfgragh.onion/2017/12/04/us/trump-bears-ears.html}{cutting
back protected areas} and
\href{https://www.nytimes3xbfgragh.onion/2019/03/15/climate/trump-sage-grouse.html}{limiting
wildlife protections}.

``Over the past three years, we have fulfilled President Trump's
promises to provide certainty for states, tribes, and local
governments,'' a spokeswoman for the E.P.A. said in a statement to The
Times, adding that the agency was ``delivering on President Trump's
commitment to return the agency to its core mission: Providing cleaner
air, water and land to the American people.''

But environmental and legal groups said the rollbacks have not served
that mission. Ms. Vizcarra, who has tracked environmental rollbacks for
Harvard since 2018, said the agency under Mr. Trump has often limited
its own power to regulate environmental harm, especially when it comes
to climate change.

Many of the rollbacks have faced legal challenges by states,
environmental groups and others, and some could remain mired in court
beyond November, regardless of the outcome of the election.

Hillary Aidun, who tracks deregulation at Columbia University's Sabin
Center for Climate Change Law, said many of the rollbacks had not been
adequately justified, leaving them vulnerable to legal challenge.

The New York Times analysis identified 10 rules that were initially
reversed or suspended but later reinstated, often
\href{https://www.nytimes3xbfgragh.onion/2017/10/06/climate/trump-administration-environmental-regulations.html}{following
lawsuits} and other challenges. Other rollbacks were rebuffed by the
courts but later revised by the administration and remain in effect.

All told, the Trump administration's environmental rollbacks could
\href{https://rhg.com/research/fuel-economy-1-5/}{significantly increase
greenhouse gas emissions} and lead to
\href{https://www.law.nyu.edu/sites/default/files/climate-and-health-showdown-in-the-courts.pdf}{thousands
of extra deaths from poor air quality each year}, according to energy
and legal analysts.

Below, we have summarized each rule that has been targeted for reversal
over the past three years.

\emph{Are there rollbacks we missed? Email}
\href{mailto:climateteam@NYTimes.com}{\nolinkurl{climateteam@NYTimes.com}}
\emph{or tweet}
\href{https://twitter.com/nytclimate}{@nytclimate}\emph{.}

Jump to section Air pollution and emissions Drilling and extraction
Infrastructure and planning Critters Toxic substances and safety Water
pollution Other Reinstated rules

\hypertarget{air-pollution-and-emissions}{%
\subsection{Air pollution and
emissions}\label{air-pollution-and-emissions}}

\hypertarget{completed}{%
\paragraph{Completed}\label{completed}}

1. Weakened Obama-era fuel economy and greenhouse gas standards for
passenger cars and light trucks.

 E.P.A. and Transportation Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2020/03/30/climate/trump-fuel-economy.html}{Read
more »}

2. Revoked California's power to set stricter tailpipe emissions
standards than the federal government.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/09/17/climate/trump-california-emissions-waiver.html}{Read
more »}

3. Withdrew the legal justification for an Obama-era rule that limited
mercury emissions from coal power plants.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2020/04/16/climate/epa-mercury-coal.html}{Read
more »}

4. Replaced the Obama-era Clean Power Plan, which would have set strict
limits on carbon emissions from coal- and gas-fired power plants, with a
new version that would let states set their own rules.

 Executive Order; E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/06/19/climate/epa-coal-emissions.html}{Read
more »}

5. Canceled a requirement for oil and gas companies to report methane
emissions.

 E.P.A. \textbar{}
\href{https://www.epa.gov/newsreleases/epa-withdraws-information-request-oil-and-gas-industry}{Read
more »}

6. Revised and partially repealed an Obama-era rule limiting methane
emissions on public lands, including intentional venting and flaring
from drilling operations.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2018/09/18/climate/trump-methane-rollback.html}{Read
more »}

7. Loosened a Clinton-era rule designed to limit toxic emissions from
major industrial polluters.

 E.P.A. \textbar{}
\href{https://www.vox.com/energy-and-environment/2018/1/26/16936104/epa-trump-toxic-air-pollution}{Read
more »}

8. Revised a program designed to safeguard communities from increases in
pollution from new power plants to make it easier for facilities to
avoid emissions regulations.

 E.P.A. \textbar{}
\href{https://eelp.law.harvard.edu/2018/12/new-source-review/}{Read more
»}

9. Amended rules that govern how refineries monitor pollution in
surrounding communities.

 E.P.A. \textbar{}
\href{https://eelp.law.harvard.edu/2018/12/petroleum-refinery-sector-rule-neshaps-nsps/}{Read
more »}

10. Weakened an Obama-era rule meant to reduce air pollution in national
parks and wilderness areas.

 E.P.A. \textbar{}
\href{https://www.eenews.net/eenewspm/2019/08/20/stories/1061013699}{Read
more »}

11. Weakened oversight of some state plans for reducing air pollution in
national parks.

 E.P.A. \textbar{}
\href{https://eelp.law.harvard.edu/2018/04/regional-haze-state-implementation-plans/}{Read
more »}

12. Relaxed air pollution regulations for a handful of plants that burn
waste coal for electricity.

 E.P.A. \textbar{}
\href{https://whyy.org/articles/epa-rolls-back-air-regulations-for-waste-coal-plants-in-western-pa-w-va/}{Read
more »}

13. Repealed rules meant to reduce leaking and venting of powerful
greenhouse gases known as hydrofluorocarbons from large refrigeration
and air conditioning systems.

 E.P.A. \textbar{}
\href{https://climate.law.columbia.edu/content/epa-rolls-back-rule-climate-super-pollutants}{Read
more »}

14. Directed agencies to stop using an Obama-era calculation of the
social cost of carbon that rulemakers used to estimate the long-term
economic benefits of reducing carbon dioxide emissions.

 Executive Order \textbar{}
\href{http://www.sciencemag.org/news/2017/08/trump-s-attack-social-cost-carbon-could-end-hurting-his-fossil-fuel-push}{Read
more »}

15. Withdrew guidance directing federal agencies to include greenhouse
gas emissions in environmental reviews. But several district courts have
ruled that emissions must be included in such reviews.

 Executive Order; Council on Environmental Quality \textbar{}
\href{https://www.eenews.net/greenwire/stories/1060052285}{Read more »}

16. Revoked an Obama executive order that set a goal of cutting the
federal government's greenhouse gas emissions by 40 percent over 10
years.

 Executive Order \textbar{}
\href{http://columbiaclimatelaw.com/climate-deregulation-tracker/president-issues-executive-order-revoking-federal-sustainability-plan/}{Read
more »}

17. Repealed a requirement that state and regional authorities track
tailpipe emissions from vehicles on federal highways.

 Transportation Department \textbar{}
\href{https://usa.streetsblog.org/2018/05/31/trump-admin-snuffs-out-climate-progress-at-u-s-dot/}{Read
more »}

18. Lifted a summertime ban on the use of E15, a gasoline blend made of
15 percent ethanol. (Burning gasoline with a higher concentration of
ethanol in hot conditions increases smog.)

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/05/31/climate/trump-ethanol-fuel-ban.html}{Read
more »}

19. Changed rules to allow states and the E.P.A. to take longer to
develop and approve plans aimed at cutting methane emissions from
existing landfills.

 E.P.A. \textbar{}
\href{https://eelp.law.harvard.edu/2017/09/municipal-solid-waste-landfill-new-source-performance-standards-and-emissions-guidelines/}{Read
more »}

\hypertarget{in-progress}{%
\paragraph{In progress}\label{in-progress}}

20. Submitted notice of intent to withdraw the United States from the
Paris climate agreement. (The process of withdrawing cannot be completed
until November 2020.)

 Executive Order \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/11/04/climate/trump-paris-agreement-climate.html}{Read
more »}

21. Proposed relaxing Obama-era requirements that companies monitor and
repair methane leaks at oil and gas facilities.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/08/29/climate/epa-methane-greenhouse-gas.html}{Read
more »}

22. Proposed eliminating Obama-era restrictions that, in effect,
required newly built coal power plants to capture carbon dioxide
emissions.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2018/12/04/climate/epa-coal-carbon-capture.html}{Read
more »}

23. Proposed revisions to standards for carbon dioxide emissions from
new, modified and reconstructed power plants.

 Executive Order; E.P.A. \textbar{}
\href{https://eelp.law.harvard.edu/2017/09/ghg-new-source-performance-standards-for-power-plants/}{Read
more »}

24. Began a review of emissions rules for power plant start-ups,
shutdowns and malfunctions. One outcome of that review: In February
2020, E.P.A. reversed a requirement that Texas follow emissions rules
during certain malfunction events.

 E.P.A. \textbar{}
\href{https://www.texasobserver.org/the-epa-told-texas-to-crack-down-on-dangerous-air-emissions-in-2015-the-state-never-did-and-now-it-wont-have-to/}{Read
more »}

25. Opened for comment a proposal limiting the ability of individuals
and communities to challenge E.P.A.-issued pollution permits before a
panel of agency judges.

 E.P.A. \textbar{}
\href{https://www.federalregister.gov/documents/2019/12/03/2019-24940/modernizing-the-administrative-exhaustion-requirement-for-permitting-decisions-and-streamlining}{Read
more »}

26. Delayed issuing a rule limiting greenhouse gas emissions from
aircraft. (The E.P.A. acknowledged it is legally required to issue the
rule, but has not done so yet. The delay is being challenged by
environmental groups.)

 E.P.A. \textbar{}
\href{https://www.eenews.net/climatewire/stories/1060417953}{Read more
»}

27. Proposed limiting pesticide application buffer zones that are
intended to protect farmworkers and bystanders from accidental exposure.

 E.P.A. \textbar{}
\href{https://www.agriculture.com/news/business/epa-proposal-would-shrink-buffer-zones-around-farm-pesticides}{Read
more »}

\hypertarget{drilling-and-extraction}{%
\subsection{Drilling and extraction}\label{drilling-and-extraction}}

\hypertarget{completed-1}{%
\paragraph{Completed}\label{completed-1}}

28. Made significant cuts to the borders of two national monuments in
Utah and recommended border and resource-management changes to several
more.

 Presidential Proclamation; Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2017/12/04/us/trump-bears-ears.html}{Read
more »}

29. Lifted ban on drilling in the Arctic National Wildlife Refuge.

 Congress; Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/08/21/us/oil-drilling-arctic.html}{Read
more »}

30. Rescinded water pollution regulations for fracking on federal and
Indian lands.

 Interior Department \textbar{}
\href{https://www.washingtonpost.com/news/energy-environment/wp/2018/01/24/california-sues-trump-administration-over-repeal-of-fracking-rule/}{Read
more »}

31. Scrapped a proposed rule that required mines to prove they could pay
to clean up future pollution.

 E.P.A. \textbar{}
\href{https://www.theguardian.com/environment/2017/dec/17/donald-trump-epa-mining-pollution-rules}{Read
more »}

32. Withdrew a requirement that Gulf oil rig owners prove they can cover
the costs of removing rigs once they stop producing.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2018/03/10/business/offshore-drilling-trump-administration.html}{Read
more »}

33. Moved the permitting process for certain projects that cross
international borders, such as oil pipelines, to the office of the
president from the State Department, exempting them from environmental
review.

 Executive Order \textbar{}
\href{https://eelp.law.harvard.edu/2019/04/energy-eos-in-depth-new-presidential-permit-for-keystone-xl-and-changes-to-presidential-permitting/}{Read
more »}

34. Changed how the Federal Energy Regulatory Commission considers the
indirect effects of greenhouse gas emissions in environmental reviews of
pipelines.

 Federal Energy Regulatory Commission \textbar{}
\href{https://www.eenews.net/eenewspm/stories/1060082141}{Read more »}

35. Revoked an Obama-era executive order designed to preserve ocean,
coastal and Great Lakes waters in favor of a policy focused on energy
production and economic growth.

 Executive Order \textbar{}
\href{https://www.apnews.com/57d405229ba844f59f9f2d06c65c4318}{Read more
»}

36. Permitted the use of seismic air guns for gas and oil exploration in
the Atlantic Ocean. The practice, which can kill marine life and disrupt
fisheries, was blocked under the Obama administration.

 National Oceanic and Atmospheric Administration \textbar{}
\href{https://apnews.com/3bd02acc43aa4cecada19d87d20edd31}{Read more »}

37. Loosened offshore drilling safety regulations implemented by the
Obama after following the 2010 Deepwater Horizon explosion and oil
spill, including reduced testing requirements for blowout prevention
systems.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/05/02/climate/offshore-drilling-safety-rollback-deepwater-horizon.html}{Read
more »}

38. Lifted an Obama-era freeze on new coal leases on public lands. In
April 2019, a judge ruled that the Interior Department could not begin
selling new leases without completing an environmental review. In
February, the agency published an assessment that concluded restarting
federal coal leasing would have little environmental impact.

 Executive Order; Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/04/19/climate/court-trump-coal-mining-setback.html}{Read
more »}

\hypertarget{in-progress-1}{%
\paragraph{In progress}\label{in-progress-1}}

39. Approved construction of the Dakota Access pipeline less than a mile
from the Standing Rock Sioux Reservation. (The Obama administration had
halted the project, with the Army Corps of Engineers saying it would
explore alternative routes). But, following a lengthy legal battle, in
July 2020 a federal judge ruled the pipeline must be shut down and
drained of oil while the Corps completes a review of its impact on the
environment.

 Executive Order; Army \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2020/07/06/us/dakota-access-pipeline.html}{Read
more »}

40. Proposed opening most of America's coastal waters to offshore oil
and gas drilling but delayed the plan after a federal judge ruled that
Mr. Trump's reversal of an Obama-era ban on drilling in the Atlantic and
Arctic Oceans was unlawful.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/04/25/climate/offshore-drilling-delay.html}{Read
more »}

41. Repealed an Obama-era rule governing royalties for oil, gas and coal
leases on federal lands, which replaced a 1980s rule that critics said
allowed companies to underpay the federal government. A federal judge
struck down the Trump administration's repeal. The Interior Department
is reviewing the decision.

 Interior Department \textbar{}
\href{https://www.reuters.com/article/us-usa-interior-royalties/federal-court-dismisses-trump-administrations-repeal-of-coal-oil-valuation-rule-idUSKCN1RR1K1}{Read
more »}

42. Proposed revising regulations on offshore oil and gas exploration by
floating vessels in the Arctic that were developed after a
\href{http://www.nytimes3xbfgragh.onion/2013/01/02/business/energy-environment/breakaway-oil-rig-runs-aground-in-gulf-of-alaska.html}{2013
accident}. The Interior Department previously said it was ``considering
full rescission or revision of this rule.''

 Executive Order; Interior Department \textbar{}
\href{https://www.reginfo.gov/public/do/eAgendaViewRule?pubId=201910\&RIN=1082-AA01}{Read
more »}

43. Proposed ``streamlining'' the approval process for drilling for oil
and gas in national forests.

 Agriculture Department; Interior Department \textbar{}
\href{https://www.outsideonline.com/2373896/trump-wants-speed-drilling-national-forests}{Read
more »}

44. Proposed opening more land in the Alaska National Petroleum Reserve
for oil drilling. The Obama administration had designated about half of
the reserve as a conservation area.

 Interior Department \textbar{}
\href{https://www.reuters.com/article/us-usa-alaska-oil/u-s-government-releases-draft-proposal-for-expanded-alaska-oil-development-idUSKBN1XW1SK}{Read
more »}

45. Proposed lifting a Clinton-era policy that banned logging and road
construction in Tongass National Forest, Alaska.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/10/15/climate/tongass-forest-roads.html}{Read
more »}

46. Approved the Keystone XL pipeline rejected by President Barack
Obama, but a federal judge blocked the project from going forward
without an adequate environmental review process. Mr. Trump later
attempted to sidestep the ruling by issuing a presidential permit.
Initial construction has started, but the project remains tied up in
court.

 Executive Order; State Department \textbar{}
\href{https://www.pri.org/stories/2019-11-28/keystone-oil-spill-casts-doubt-safety-proposed-keystone-xl-pipeline}{Read
more »}

\hypertarget{infrastructure-and-planning}{%
\subsection{Infrastructure and
planning}\label{infrastructure-and-planning}}

\hypertarget{completed-2}{%
\paragraph{Completed}\label{completed-2}}

47. Weakened the National Environmental Policy Act, one of the country's
most significant environmental laws, in order to expedite the approval
of public infrastructure projects, such as roads, pipelines and
telecommunications networks. The new rules shorten the time frame for
completing environmental studies, limit the types of projects subject to
review, and no longer require federal agencies to account for a
project's cumulative effects on the environment, such as climate change.

 Council on Environmental Quality \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2020/07/15/climate/trump-environment-nepa.html}{Read
more »}

48. Revoked Obama-era flood standards for federal infrastructure
projects that required the government to account for sea level rise and
other climate change effects.

 Executive Order \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2017/08/15/climate/flooding-infrastructure-climate-change-trump-obama.html}{Read
more »}

49. Relaxed the environmental review process for federal infrastructure
projects.

 Executive Order \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2017/08/15/climate/flooding-infrastructure-climate-change-trump-obama.html}{Read
more »}

50. Overturned an Obama-era guidance that ended U.S. government
financing for new coal plants overseas except in rare circumstances.

 Executive Order; Treasury Department \textbar{}
\href{https://www.devex.com/news/will-new-us-guidance-for-mdbs-mean-more-coal-financing-90836}{Read
more »}

51. Revoked a directive for federal agencies to minimize impacts on
water, wildlife, land and other natural resources when approving
development projects.

 Executive Order \textbar{}
\href{https://www.whitehouse.gov/presidential-actions/presidential-executive-order-promoting-energy-independence-economic-growth/}{Read
more »}

52. Revoked an Obama executive order promoting climate resilience in the
northern Bering Sea region of Alaska, which withdrew local waters from
oil and gas leasing and established a tribal advisory council to consult
on local environmental issues.

 Executive Order \textbar{}
\href{https://www.adn.com/arctic/2017/04/29/bering-sea-tribal-groups-slam-alaska-delegation-for-standing-by-as-trump-struck-order-giving-them-voice/}{Read
more »}

53. Reversed an update to the Bureau of Land Management's public
land-use planning process.

 Congress \textbar{}
\href{https://www.reuters.com/article/us-usa-congress-publicland/senate-revokes-obama-federal-land-planning-rule-idUSKBN16E2UZ}{Read
more »}

54. Withdrew an Obama-era order to consider climate change in the
management of natural resources in national parks.

 National Park Service \textbar{}
\href{https://www.eenews.net/stories/1060059511}{Read more »}

55. Restricted most Interior Department environmental studies to one
year in length and a maximum of 150 pages, citing a need to reduce
paperwork.

 Interior Department \textbar{}
\href{https://www.eenews.net/stories/1060059865}{Read more »}

56. Withdrew a number of Obama-era Interior Department climate change
and conservation policies that the agency said could ``burden the
development or utilization of domestically produced energy resources.''

 Interior Department \textbar{}
\href{https://www.hcn.org/articles/climate-change-interior-department-revokes-climate-change-and-mitigation-policies}{Read
more »}

57. Eliminated the use of an Obama-era planning system designed to
minimize harm from oil and gas activity on sensitive landscapes, such as
national parks.

 Interior Department \textbar{}
\href{https://climate.law.columbia.edu/content/blm-issues-internal-policy-streamline-oil-and-gas-permitting-0}{Read
more »}

58. Withdrew Obama-era policies designed to maintain or, ideally,
improve natural resources affected by federal projects.

 Interior Department \textbar{}
\href{https://www.eenews.net/stories/1060091417}{Read more »}

\hypertarget{in-progress-2}{%
\paragraph{In progress}\label{in-progress-2}}

59. Proposed plans to speed up the environmental review process for
Forest Service projects.

 Agriculture Department \textbar{}
\href{https://www.fs.fed.us/emc/nepa/revisions/includes/docs/36CFR220ProposedRuleFRN.pdf}{Read
more »}

\hypertarget{animals}{%
\subsection{Animals}\label{animals}}

\hypertarget{completed-3}{%
\paragraph{Completed}\label{completed-3}}

60. Changed the way the Endangered Species Act is applied, making it
more difficult to protect wildlife from long-term threats posed by
climate change.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/08/12/climate/endangered-species-act-changes.html}{Read
more »}

61. Relaxed environmental protections for salmon and smelt in
California's Central Valley in order to free up water for farmers.

 Executive Order; Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/10/22/climate/trump-delta-smelt.html}{Read
more »}

62. Overturned a ban on the use of lead ammunition and fishing tackle on
federal lands.

 Interior Department \textbar{}
\href{https://www.reuters.com/article/us-usa-Interior\%20Department-zinke-idUSKBN16930Z}{Read
more »}

63. Overturned a ban on the hunting of predators in Alaskan wildlife
refuges.

 Congress \textbar{}
\href{http://www.adn.com/alaska-news/wildlife/2017/04/10/congress-and-trump-revoked-the-predator-control-ban-on-alaskas-refuges-now-what/}{Read
more »}

64. Reversed an Obama-era rule that barred using bait, such as
grease-soaked doughnuts, to lure and kill grizzly bears, among other
sport hunting practices that many people consider extreme, on some
public lands in Alaska.

 National Park Service; Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2020/06/09/climate/trump-bear-hunting.html}{Read
more »}

65. Amended fishing regulations to loosen restrictions on the harvest of
a number of species.

 National Oceanic and Atmospheric Administration \textbar{}
\href{https://www.usatoday.com/story/news/politics/2018/03/21/go-fish-under-president-trump-changing-political-tide-opens-water-anglers/384747002/}{Read
more »}

66. Removed restrictions on commercial fishing in a protected marine
preserve southeast of Cape Cod that is home to rare corals and a number
of endangered sea animals. The Trump administration has suggested
changing the management or size of two other marine protected areas in
the Pacific Ocean.

 Executive Order; National Oceanic and Atmospheric Administration
\textbar{}
\href{https://www.wbur.org/earthwhile/2020/06/05/trump-roll-back-marine-monument-protections}{Read
more »}

67. Proposed revising limits on the number of endangered marine mammals
and sea turtles that can be unintentionally killed or injured with
sword-fishing nets on the West Coast. (The Obama-era rules were
initially withdrawn by the National Oceanic and Atmospheric
Administration, but were later finalized following a court order. The
agency has said it plans to revise the limits.)

 National Oceanic and Atmospheric Administration \textbar{}
\href{https://eelp.law.harvard.edu/2017/10/pacific-bycatch-limits-for-whales-dolphins-and-sea-turtles/}{Read
more »}

68. Loosened fishing restrictions intended to reduce bycatch of Atlantic
Bluefin Tuna.

 National Oceanic and Atmospheric Administration \textbar{}
\href{https://eelp.law.harvard.edu/2019/10/atlantic-bluefin-tuna-protection-pelagic-longline-fishery-management/}{Read
more »}

69. Rolled back a roughly 40-year-old interpretation of a policy aimed
at protecting migratory birds, potentially running afoul of treaties
with Canada and Mexico.

 Interior Department \textbar{}
\href{https://www.washingtonpost.com/news/energy-environment/wp/2018/04/13/the-trump-administration-officially-clipped-the-wings-of-the-migratory-bird-treaty-act/}{Read
more »}

70. Overturned a ban on using parts of migratory birds in handicrafts
made by Alaskan Natives.

 Interior Department \textbar{}
\href{https://www.fws.gov/alaska/ambcc/News_files/NR\%2007-21-2017\%20Migratory\%20Birdpart\%20Native\%20Handicrafts\%20FINAL\%20DOI\%20(3).pdf}{Read
more »}

\hypertarget{in-progress-3}{%
\paragraph{In progress}\label{in-progress-3}}

71. Opened nine million acres of Western land to oil and gas drilling by
weakening habitat protections for the sage grouse, an imperiled bird. An
Idaho District Court injunction temporarily blocked the measure.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/10/16/climate/trump-sage-grouse.html}{Read
more »}

\hypertarget{water-pollution}{%
\subsection{Water pollution}\label{water-pollution}}

\hypertarget{completed-4}{%
\paragraph{Completed}\label{completed-4}}

72. Scaled back pollution protections for certain tributaries and
wetlands that were regulated under the Clean Water Act by the Obama
administration.

 E.P.A.; Army \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/09/12/climate/trump-administration-to-finalize-rollback-of-clean-water-protections.html}{Read
more »}

73. Revoked a rule that prevented coal companies from dumping mining
debris into local streams.

 Congress \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2017/02/02/business/energy-environment/senate-coal-regulations.html}{Read
more »}

74. Withdrew a proposed rule aimed at reducing pollutants, including air
pollution, at sewage treatment plants.

 E.P.A. \textbar{}
\href{https://www.govinfo.gov/content/pkg/FR-2017-10-26/pdf/2017-23067.pdf}{Read
more »}

75. Withdrew a proposed rule requiring groundwater protections for
certain uranium mines. Recently, the administration's Nuclear Fuel
Working Group proposed opening up 1,500 acres outside the Grand Canyon
to nuclear production.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2018/01/13/climate/trump-uranium-bears-ears.html}{Read
more »}

\hypertarget{in-progress-4}{%
\paragraph{In progress}\label{in-progress-4}}

76. Attempted to weaken federal rules regulating the disposal and
storage of coal ash waste from power plants, but a court determined the
rules were already insufficient. Proposed a new rule to allow coal ash
impoundments of a type previously deemed unsafe a pathway to proving
safety.

 E.P.A.

77. Proposed a rule exempting certain types of power plants from parts
of an E.P.A. rule limiting toxic discharge from power plants into public
waterways.

 E.P.A. \textbar{}
\href{https://www.washingtonpost.com/news/energy-environment/wp/2017/04/13/trump-administration-halts-obama-era-rule-aimed-at-curbing-toxic-wastewater-from-coal-plants/?utm_term=.e69ccd855117}{Read
more »}

78. Weakened a portion of the Clean Water Act to make it easier for
federal agencies to issue permits for federal projects over state
objections if the projects don't meet local water quality standards,
including for pipelines and other fossil fuel facilities.

 Executive Order; E.P.A. \textbar{}
\href{https://news.bloomberglaw.com/environment-and-energy/white-house-begins-review-of-water-rule-easing-state-veto-power}{Read
more »}

79. Proposed extending the lifespan of unlined coal ash holding areas,
which can spill their contents because they lack a protective underlay.

 E.P.A. \textbar{}
\href{https://stateimpact.npr.org/pennsylvania/2019/11/04/trump-administration-proposes-rollbacks-for-two-obama-era-coal-pollution-rules/}{Read
more »}

80. Proposed a regulation limiting the scope of an Obama-era rule under
which companies had to prove that large deposits of recycled coal ash
would not harm the environment.

 E.P.A. \textbar{}
\href{https://www.federalregister.gov/documents/2019/08/14/2019-16916/hazardous-and-solid-waste-management-system-disposal-of-coal-combustion-residuals-from-electric\#}{Read
more »}

81. Proposed a new rule allowing the federal government to issue permits
for coal ash waste in Indian Country and some states without review if
the disposal site is in compliance with federal regulations.

 E.P.A. \textbar{}
\href{https://www.epa.gov/sites/production/files/2019-12/documents/pre_pub_version_federal_ccr_permitting_program_nprm_rin_2050-ah07_121819_514pm_for_ao_signature.pdf}{Read
more »}

82. Proposed doubling the time allowed to remove lead pipes from water
systems with high levels of lead.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/10/10/climate/epa-lead-water-pipes.html}{Read
more »}

\hypertarget{toxic-substances-and-safety}{%
\subsection{Toxic substances and
safety}\label{toxic-substances-and-safety}}

\hypertarget{completed-5}{%
\paragraph{Completed}\label{completed-5}}

83. Rejected a proposed ban on chlorpyrifos, a pesticide linked to
developmental disabilities in children. (Several states have banned its
use and the main manufacturer of the pesticide in 2020 stopped producing
the product because of shrinking demand.)

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/07/18/climate/epa-chlorpyrifos-pesticide-ban.html}{Read
more »}

84. Narrowed the scope of a 2016 law mandating safety assessments for
potentially toxic chemicals like dry-cleaning solvents. The E.P.A. said
it would focus on direct exposure and exclude indirect exposure such as
from air or water contamination. In November 2019, a court of appeals
ruled the agency must widen its scope to consider full exposure risks.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2018/06/07/us/politics/epa-toxic-chemicals.html}{Read
more »}

85. Reversed an Obama-era rule that required braking system upgrades for
``high hazard'' trains hauling flammable liquids like oil and ethanol.

 Transportation Department \textbar{}
\href{https://www.opb.org/news/article/oil-train-safety-rule-rollback-by-trump/}{Read
more »}

86. Removed copper filter cake, an electronics manufacturing byproduct
comprised of heavy metals, from the ``hazardous waste'' list.

 E.P.A. \textbar{}
\href{https://www.federalregister.gov/documents/2017/10/02/2017-21112/hazardous-waste-management-system-identification-and-listing-of-hazardous-waste}{Read
more »}

87. Ended an Occupational Safety and Health Administration program to
reduce risks of workers developing the lung disease silicosis. In
February released guidance to include silica in OSHA's National Emphasis
Program, a worker safety program.

 Labor Department \textbar{}
\href{https://www.npr.org/sections/health-shots/2019/10/02/766028237/workers-are-falling-ill-even-dying-after-making-kitchen-countertops}{Read
more »}

88. Rolled back most of the requirements of a 2017 rule aimed at
improving safety at sites that use hazardous chemicals that was
instituted after a chemical plant exploded in Texas.

 E.P.A. \textbar{}
\href{https://eelp.law.harvard.edu/2017/09/chemical-disaster-rule/}{Read
more »}

\hypertarget{in-progress-5}{%
\paragraph{In progress}\label{in-progress-5}}

89. Proposed changing safety rules to allow for rail transport of the
highly flammable liquefied natural gas.

 Transportation Department \textbar{}
\href{https://climate.law.columbia.edu/content/dot-proposes-allowing-lng-rail}{Read
more »}

90. Announced a review of an Obama-era rule lowering coal dust limits in
mines. The head of the Mine Safety and Health Administration said there
were no immediate plans to change the dust limit but has extended a
public comment period until 2022.

 Labor Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/02/22/climate/black-lung-resurgence.html}{Read
more »}

\hypertarget{other}{%
\subsection{Other}\label{other}}

\hypertarget{completed-6}{%
\paragraph{Completed}\label{completed-6}}

91. Repealed an Obama-era regulation that would have nearly doubled the
number of light bulbs subject to energy-efficiency standards starting in
January 2020. The Energy Department also blocked the next phase of
efficiency standards for general-purpose bulbs already subject to
regulation.

 Energy Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/09/04/climate/trump-light-bulb-rollback.html}{Read
more »}

92. Changed a 25-year-old policy to allow coastal replenishment projects
to use sand from protected ecosystems.

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/11/07/climate/trump-beaches-sand-protected-areas.html}{Read
more »}

93. Limited funding of environmental and community development projects
through corporate settlements of federal lawsuits.

 Justice Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2017/06/09/us/politics/settlements-sessions-attorney-general.html}{Read
more »}

94. Stopped payments to the Green Climate Fund, a United Nations program
to help poorer countries reduce carbon emissions.

 Executive Order \textbar{}
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/06/02/climate/trump-paris-green-climate-fund.html}{Read
more »}

95. Reversed restrictions on the sale of plastic water bottles in
national parks desgined to cut down on litter, despite a
\href{https://www.nps.gov/aboutus/foia/upload/Disposable-Plastic-Water-Bottle-Evaluation-Report_5_11_17.pdf}{Park
Service report} that the effort worked.

 Interior Department \textbar{}
\href{https://www.npr.org/sections/thesalt/2017/08/18/544456726/trump-administration-reverses-bottled-water-ban-in-national-parks}{Read
more »}

\hypertarget{in-progress-6}{%
\paragraph{In progress}\label{in-progress-6}}

96. Proposed limiting the studies used by the E.P.A. for rulemaking to
only those that make data publicly available. (Scientists widely
criticized the proposal, saying it would effectively block the agency
from considering landmark research that relies on confidential health
data.)

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/11/11/climate/epa-science-trump.html}{Read
more »}

97. Proposed changes to the way cost-benefit analyses are conducted
under the Clean Air Act, Clean Water Act and other environmental
statutes.

 E.P.A. \textbar{}
\href{https://www.scientificamerican.com/article/planned-changes-to-epa-pollution-analyses-align-with-industry-requests/}{Read
more »}

98. Proposed withdrawing efficiency standards for residential furnaces
and commercial water heaters designed to reduce energy use.

 Energy Department \textbar{}
\href{https://www.federalregister.gov/documents/2018/11/01/2018-23885/energy-conservation-program-energy-conservation-standards-for-residential-furnaces-and-commercial}{Read
more »}

99. Created a product category that would allow some dishwashers to be
exempt from energy efficiency standards.

 Energy Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2019/09/17/climate/trump-dishwasher-regulatory-rollback.html}{Read
more »}

100. Initially withdrew, and then delayed, a proposed rule that would
inform car owners about fuel-efficient replacement tires. (The
Transportation Department has scheduled a new rulemaking notice for
2020.)

 Transportation Department \textbar{}
\href{https://www.reginfo.gov/public/do/eAgendaViewRule?pubId=201904\&RIN=2127-AK76}{Read
more »}

\hypertarget{some-rules-were-rolled-back-then-reinstated}{%
\subsection{Some rules were rolled back, then
reinstated}\label{some-rules-were-rolled-back-then-reinstated}}

These rules were initially reversed by the Trump administration but were
later reinstated, often following lawsuits and other challenges.

1. Stopped enforcing a 2015 rule that prohibited the use of
hydrofluorocarbons, powerful greenhouse gases, in air-conditioners and
refrigerators. A court later restored the prohibition.

 E.P.A. \textbar{} \href{https://www.eenews.net/stories/1062812525}{Read
more}

2. Sought to repeal emissions standards for ``glider'' trucks ---
vehicles retrofitted with older, often dirtier engines --- but reversed
course after Andrew Wheeler took over as head of the E.P.A.

 E.P.A. \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2018/07/27/climate/wheeler-pruitt-glider-truck-reversal.html}{Read
more}

3. Sought to lift restrictions on mining in Bristol Bay, Alaska, but
later suspended the effort. (A court ruled the E.P.A. could withdraw a
2014 determination that the project was a too great a threat to the
Bay's salmon. The federal permit for the mine is pending with the U.S.
Army Corps of Engineers.)

 E.P.A.; Army \textbar{}
\href{https://www.adn.com/business-economy/energy/2020/04/20/pebble-mine-opponents-lose-court-case-over-2014-epa-report/}{Read
more}

4. Delayed a compliance deadline for new national ozone pollution
standards by one year, but later reversed course.

 E.P.A. \textbar{}
\href{https://eelp.law.harvard.edu/2017/09/ozone-national-ambient-air-quality-standards/}{Read
more}

5. Delayed implementation of a rule regulating the certification and
training of pesticide applicators, but a judge ruled that the E.P.A. had
done so illegally and declared the rule still in effect.

 E.P.A. \textbar{}
\href{https://www.eenews.net/eenewspm/2018/03/22/stories/1060077215}{Read
more}

6. Initially delayed publishing efficiency standards for household
appliances, but later published them after multiple states and
environmental groups sued.

 Energy Department \textbar{}
\href{https://www.washingtonpost.com/climate-environment/after-three-years-and-a-lawsuit-trump-administration-publishes-efficiency-standards-for-big-equipment/2020/01/10/d641474a-33c3-11ea-9313-6cba89b1b9fb_story.html}{Read
more}

7. Removed the Yellowstone grizzly bear from the Endangered Species
List, but the protections were later reinstated by a federal judge. (The
Trump administration appealed the ruling in May 2019.)

 Interior Department \textbar{}
\href{https://www.nytimes3xbfgragh.onion/2018/09/25/science/yellowstone-grizzly-hunt.html}{Read
more}

8. Reissued a rule limiting the discharge of mercury by dental offices
into municipal sewers after a lawsuit by the Natural Resources Defense
Council, an advocacy group.

 E.P.A. \textbar{} \href{https://www.eenews.net/stories/1060056173}{Read
more}

9. Delayed federal building efficiency standards until Sept. 30, 2017,
at which time the rules went into effect.

 Energy Department \textbar{}
\href{https://www.federalregister.gov/documents/2017/03/21/2017-05485/energy-efficiency-standards-for-the-design-and-construction-of-new-federal-low-rise-residential}{Read
more}

10. Ordered a review of water efficiency standards in bathroom fixtures,
including toilets. E.P.A. determined existing standards were sufficient.

 E.P.A. \textbar{}
\href{https://www.vox.com/policy-and-politics/2019/12/7/21000314/trump-toilet-10-15-times-epa-rules}{Read
more}

Note: This list does not include new rules proposed by the Trump
administration that do not roll back previous policies, nor does it
include court actions that have affected environmental policies
independent of executive or legislative action.

Sources: Harvard Law School's
\href{http://environment.law.harvard.edu/policy-initiative/regulatory-rollback-tracker/}{Environmental
Regulation Rollback Tracker}; Columbia Law School's
\href{http://columbiaclimatelaw.com/resources/climate-deregulation-tracker/}{Climate
Deregulation Tracker}; Brookings Institution; Federal Register;
Environmental Protection Agency; Interior Department; U.S. Chamber of
Commerce; White House.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
