Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/world/asia}{Asia Pacific}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/world/asia}{Asia Pacific}\textbar{}Wuhan Coronavirus Map:
Tracking the Spread of the Outbreak

\url{https://nyti.ms/2TFYMxs}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\href{https://www.nytimes.com/news-event/coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{The
Coronavirus Outbreak}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes.com/2020/08/02/world/coronavirus-updates.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Latest
  Updates}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Maps
  and Cases}
\item
  \href{https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes.com/interactive/2020/07/29/us/schools-reopening-coronavirus.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{What
  School May Look Like}
\item
  \href{https://www.nytimes.com/live/2020/07/31/business/stock-market-today-coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Economy}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{wuhan-coronavirus-map-tracking-the-spread-of-the-outbreak}{%
\section{Wuhan Coronavirus Map: Tracking the Spread of the
Outbreak}\label{wuhan-coronavirus-map-tracking-the-spread-of-the-outbreak}}

By \href{https://www.nytimes.com/by/kk-rebecca-lai}{K.K. Rebecca Lai},
\href{https://www.nytimes.com/by/jin-wu}{Jin Wu},
\href{https://www.nytimes.com/by/allison-mccann}{Allison McCann},
\href{https://www.nytimes.com/by/derek-watkins}{Derek Watkins},
\href{https://www.nytimes.com/by/jugal-k-patel}{Jugal K. Patel} and
Richard HarrisUpdated January 31, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

The
\href{https://www.nytimes.com/2020/01/28/world/asia/china-coronavirus.html}{Wuhan
coronavirus} has sickened more than 4,500 people in Asia, according to
statements from health officials. Many other cases are suspected but not
confirmed. As of Tuesday morning, at least 106 people have died, all in
China.

\hypertarget{confirmed-cases}{%
\subsubsection{Confirmed cases}\label{confirmed-cases}}

Wuhan

2,714

14

7

7

4

4

2

1

1

1

JAPAN

S. KOREA

TAIWAN

CHINA

NEPAL

THAILAND

VIETNAM

CAMBODIA

MALAYSIA

Sources: The Center for Systems Science and Engineering (CSSE) at Johns
Hopkins University; National Health Commission of the People's Republic
of China; local governments. Note: Data as of 8 a.m. E.T., Jan. 28

The disease has been detected in at least 13 other countries, almost all
involving people who traveled from China.

2 CANADA

5 UNITED STATES

3 FRANCE

1 GERMANY

4,600+ CHINA

7 SINGAPORE

5 AUSTRALIA

Five cases have been confirmed in the United States: a woman in her 60s
in Chicago, a man in his 30s in Washington state, two people in southern
California, and one person in Arizona.

1 Washington

2 California

1 Arizona

1 Illinois

UNITED STATES

Source: Centers for Disease Control and Prevention

The
\href{https://www.nytimes.com/2020/01/08/health/china-pneumonia-outbreak-virus.html}{outbreak
began} in a seafood and poultry market in Wuhan, a city of 11 million
people in central China. But which animal is the source of the virus and
how many people are at risk remain unclear. The virus can spread from
\href{https://www.nytimes.com/2020/01/20/world/asia/coronavirus-china-symptoms.html}{person
to person}, but it is not known how easily.

\href{https://www.nytimes.com/2020/01/28/world/asia/china-coronavirus.html}{Follow
the latest updates} on the coronavirus outbreak.

\hypertarget{whats-being-done-to-contain-the-outbreak}{%
\subsection{What's being done to contain the
outbreak?}\label{whats-being-done-to-contain-the-outbreak}}

The Chinese authorities took the
\href{https://www.nytimes.com/2020/01/22/world/asia/coronavirus-quarantines-history.html}{extraordinary
step} of closing off Wuhan, canceling planes and trains leaving the city
and suspending buses, subways and ferries within it. By Friday, at least
12 other cities in Hubei Province had issued travel restrictions,
including Huanggang, home to seven million people, and Ezhou, a city of
about one million.

Railway

networks

About 20 million people live

in these three cities.

XIAOGAN

HUANGGANG

WUHAN

EZHOU

CHINA

Wuhan

About 20 million people

live in these three cities.

Railway

networks

WUHAN

HUANGGANG

EZHOU

CHINA

Wuhan

Source: OpenStreetMap

The restrictions on trains and other forms of public transportation come
just before the Lunar New Year holiday, when hundreds of millions of
people travel around and out of the country.

The restrictions also began spreading beyond Hubei. On Saturday, the
Beijing city government announced that it would suspend all
inter-province buses, effectively limiting road travel into the capital.

\hypertarget{how-big-could-the-outbreak-be}{%
\subsection{How big could the outbreak
be?}\label{how-big-could-the-outbreak-be}}

Researchers at
\href{https://www.mobs-lab.org/2019ncov.html}{Northeastern University}
and
\href{https://www.imperial.ac.uk/mrc-global-infectious-disease-analysis/news--wuhan-coronavirus/}{Imperial
College London} estimate that the number of cases may be five or ten
times higher than what has been reported. Thousands of suspected cases
are yet to be confirmed with tests, and others with the virus may not
have sought medical attention.

On Monday, the Northeastern researchers estimated there may be around
25,000 cases. The estimates will change as more cases are reported and
more information about the virus becomes known.

\hypertarget{estimated-number-of-coronavirus-cases}{%
\subsubsection{Estimated number of coronavirus
cases}\label{estimated-number-of-coronavirus-cases}}

Estimates say there may be about 25,000 cases of the virus in Wuhan.

More likely

0

10k

20k

30k

40k

Number of cases

Estimates say there may be about 25,000 cases of the virus in Wuhan.

More likely

0

10k

20k

30k

40k

Number of cases

Source: Northeastern University's
\href{https://www.mobs-lab.org/2019ncov.html}{Laboratory for the
Modeling of Biological and Socio-technical Systems}. Estimates as of
Jan. 27.

These estimates are based on
\href{https://www.mobs-lab.org/2019ncov.html}{an analysis} of the
population of Wuhan, the number of cases detected outside of China and
the number of people who travel from Wuhan to other areas. Public health
officials still do not know how the disease is transmitted, and experts
urged caution in interpreting the estimates.

``These are very early models that make several assumptions based on
what evidence is available,'' said David Heymann, an epidemiologist at
the London School of Hygiene and Tropical Medicine. ``They aren't truth
--- they're just one step in trying to better understand this
outbreak.''

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
