Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/world/asia}{Asia
Pacific}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/world/asia}{Asia Pacific}\textbar{}China Claims Air
Rights Over Disputed Islands

\url{https://nyti.ms/1ccML3y}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{china-claims-air-rights-over-disputed-islands}{%
\section{China Claims Air Rights Over Disputed
Islands}\label{china-claims-air-rights-over-disputed-islands}}

By \href{https://www.nytimes3xbfgragh.onion/by/chris-buckley}{Chris
Buckley}

\begin{itemize}
\item
  Nov. 23, 2013
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

HONG KONG --- The Chinese government on Saturday claimed the right to
identify, monitor and possibly take military action against aircraft
that enter a newly declared ``air defense identification zone,'' which
covers sea and islands also claimed by Japan and threatens to escalate
an already tense dispute over some of the maritime territory.

The move appeared to be another step in China's efforts to intensify
pressure on Japan over the Japanese-controlled islands in the East China
Sea that are at the heart of the dispute.

The declaration, from a Ministry of National Defense spokesman, Col.
Yang Yujun, accompanied the ministry's
\href{http://eng.mod.gov.cn/HomePicture/2013-11/23/content_4476177.htm}{release
of a map}, geographic coordinates
and\href{http://eng.mod.gov.cn/TopNews/2013-11/23/content_4476138.htm}{rules}
in Chinese and English that said ``China's armed forces will take
defensive emergency measures to respond to aircraft that do not
cooperate in identification or refuse to follow orders.''

``The objective is to defend national sovereignty and territorial and
air security, as well as to maintain orderly aviation,'' Colonel Yang
said in comments issued on the ministry's website.

Later Saturday, China's air force said it had sent its first planes,
including fighter jets, to enforce the rules. Soon afterward, Japan
scrambled its own fighter jets, Reuters reported, citing Japan's Defense
Ministry. A ministry spokesman said two Chinese reconnaissance planes
had flown within about 25 miles of what Japan considers its airspace,
Reuters said.

The Chinese announcement followed months of increasing tension over the
uninhabited islands as China appeared to be taking moves to establish
its claim to them, including more frequent ship patrols in the area.
Those patrols have led to cat-and-mouse games between Chinese and
Japanese ships near the islands, known as the Senkaku in Japan and the
Diaoyu in China.

But trying to control the airspace over the islands could prove
particularly problematic. Japan considers that airspace its own and has
scrambled fighter jets in the past to try to ensure that Chinese
aircraft did not enter. As the potential for a miscalculation that leads
to conflict has increased, the United States has become worried that as
an ally of Japan, it could be dragged into any conflict with China.

Secretary of State John Kerry said the United States was ``deeply
concerned'' about China's announcement. ``Escalatory action will only
increase tensions in the region and create risks of an incident,'' Mr.
Kerry said in a statement. He urged China ``to exercise caution and
restraint.''~

The Japanese Foreign Ministry said the government had lodged a ``serious
protest'' with China. An official there, speaking on the condition of
anonymity as is ministry practice, said the head of Asian affairs had
called the Chinese Embassy in Tokyo on Saturday to warn that the move
could escalate tensions and was ``extremely dangerous as it could
trigger unpredictable events.''

Colonel Yang said that the declaration of the air zone was not aimed at
any particular country, and that it would not impede the freedom of
commercial flight over the East China Sea. But his words left little
doubt that the move could be used against the Japanese government and
military aircraft.

The longstanding dispute between Beijing and Tokyo over the islands
\href{http://www.nytimes3xbfgragh.onion/2012/09/23/world/asia/islands-dispute-tests-resolve-of-china-and-japan.html}{flared
last year}, before Xi Jinping assumed leadership of the Chinese
Communist Party in November. The spark was a decision by the Japanese
government to buy some of the islands from a Japanese citizen. Japan
said the move was to keep the islands out of the hands of a nationalist
politician who might increase tensions, but China saw the purchase as
Japan's effort to strengthen its hold on the islands.

The new Chinese rules left unclear how frequently and thoroughly China
intends to enforce them. But Chinese state-run news media widely
reported the announcement, which could kindle public expectations that
the government will take steps to back up its words.

Military experts have said that even if Japan and China seek to avoid
outright confrontation over the islands, there is the risk that an
unplanned episode could spiral into a wider military conflict.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
