Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/opinion}{Opinion}\textbar{}Federal Agents Don't Need Army
Fatigues

\url{https://nyti.ms/3fhzcpM}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\href{/section/opinion}{Opinion}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{federal-agents-dont-need-army-fatigues}{%
\section{Federal Agents Don't Need Army
Fatigues}\label{federal-agents-dont-need-army-fatigues}}

If you're an officer of the law, dress like one. Leave the soldiering to
soldiers.

By
\href{https://www.nytimes3xbfgragh.onion/interactive/opinion/editorialboard.html}{The
Editorial Board}

The editorial board is a group of opinion journalists whose views are
informed by expertise, research, debate and certain longstanding ****
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/opinion/editorialboard.html}{values}.
It is separate from the newsroom.

\begin{itemize}
\item
  July 31, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Gas mask

Headphones

Radio

Semiautomatic rifle

Holographic gunsight

Spare 30-round

magazine

Flashlight

Pistol

`BOOGALOO BOY'

Anti-government group---often seen

wearing Aloha shirts---at a

demonstration in New Hampshire.

Special Forces-style

helmet

Spare 30-round

magazines

Radio

Tactical gloves

Semiautomatic rifle

Pistol

Flashlight

`MILITIA' MEMBER

Self-described ``militia'' member

during a Black Lives Matter

protest in Oakdale, Calif.

Special Forces-style

helmet

Gas mask

Spare 30-round

magazines

Radio

Holographic gunsight

Tactical gloves

Aiming laser

Military-style rifle

Flashlight

FEDERAL AGENT

Unmarked federal agent

in Portland, Ore.

Radio

Semiautomatic rifle

Spare 30-round

magazines

anti-lockdown protester

Americans opposed to

government public health measures,

seen here in Ohio.

Illustration by The New York Times. Photographs from left: Michael
Dwyer/Associated Press; Andy Alfaro/McClatchy; John Rudoff/Sipa, via
Associated Press; Josh Edelson/Agence France-Presse --- Getty Images.

Masked men, clad indistinguishably from soldiers,
\href{https://www.nytimes3xbfgragh.onion/2020/07/17/us/politics/federal-agents-portland-arrests.html}{yanking
civilians off the street} in the dead of night and throwing them into
unmarked cars is the modus operandi of totalitarian regimes --- or the
stuff of dystopian fiction.

But that's now the reality in America. In recent weeks, the Department
of Homeland Security has sent hundreds of federal agents into Portland,
Ore., to quell protests over racism and police violence.

The Justice Department and the Oregon governor
\href{https://www.nytimes3xbfgragh.onion/2020/07/29/us/protests-portland-federal-withdrawal.html?action=click\&module=Top\%20Stories\&pgtype=Homepage}{appear
to have negotiated} a withdrawal of those agents. But Bill Barr, the
attorney general, told Congress this week that federal agents would be
\href{https://www.nytimes3xbfgragh.onion/reuters/2020/07/29/us/politics/29reuters-global-race-protests.html}{headed
to other cities}, including Cleveland, Milwaukee and Detroit. On Monday,
the mayors of Chicago, Seattle, Portland, Albuquerque, Washington and
Kansas City, Mo.,
\href{https://www.npr.org/sections/live-updates-protests-for-racial-justice/2020/07/27/895904023/mayors-demand-congress-block-trump-from-deploying-federal-agents-to-cities}{sent
a letter} to Congress asking for legislation to stop the Trump
administration from deploying federal agents to cities without their
consent. Federal agents should assist local jurisdictions, if they ask.
But, at least in the case of Portland, the conduct of federal officers
clearly made a bad situation worse.

Many of those federal agents aren't easily recognizable as law
enforcement officials, nor do they act like them. Even the
\href{https://www.washingtonpost.com/national-security/2020/07/22/cbp-military-camouflage-uniforms/}{military
is concerned} about the public confusion sown into society when heavily
armed federal agents dress like soldiers. All the more reason that the
federal agents on the streets of American cities be required to wear
uniforms that clearly identify themselves and their civilian agency.

Complicating matters even more for the average American are the other
masked and armed men who have also appeared at public demonstrations in
the United States over the past few months --- lockdown protesters,
anti-government activists, white supremacists, self-declared
``militias.'' To the unschooled eye, they look remarkably similar, both
in the flesh and in the millions of images flitting around the globe at
the speed of social media.

Camouflage uniforms are intended to conceal a person's presence and
intentions from an enemy, or hunters from their quarry. But in our
masked and militarized moment, the righteous should make every effort to
publicly stand out from the wicked. The
\href{https://taskandpurpose.com/pentagon-run-down/police-military-uniforms-undermines-democracy}{only
reason} to wear camouflage in an urban setting --- be it federal agents
or self-declared militia members --- is intimidation.

If officers were easily identifiable, it would be harder for them to get
away with thrashing
\href{https://taskandpurpose.com/news/navy-veteran-christopher-david-interview-portland}{unarmed
Americans with nightsticks},
\href{https://www.washingtonpost.com/nation/2020/07/20/christopher-david-portland-protest-video/}{shattering
their bones} as the camera phones roll.

A new bill, introduced by Representatives Alexandria Ocasio-Cortez of
New York and Eleanor Holmes Norton of Washington, D.C.,
\href{https://ocasio-cortez.house.gov/sites/ocasio-cortez.house.gov/files/documents/OCASNY_076_xml.pdf}{would
require} on-duty federal and local law enforcement officers to identify
themselves at all times, by name, agency and badge number. That's a good
start, but is also insufficient.

Discarding the woodland camouflage, military-style weaponry and violent
tactics while on urban policing duty in Ohio, Illinois and Wisconsin
would send an even clearer signal that federal agents intend to protect
the peace, not wage a war.

\emph{The Times is committed to publishing}
\href{https://www.nytimes3xbfgragh.onion/2019/01/31/opinion/letters/letters-to-editor-new-york-times-women.html}{\emph{a
diversity of letters}} \emph{to the editor. We'd like to hear what you
think about this or any of our articles. Here are some}
\href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014925288-How-to-submit-a-letter-to-the-editor}{\emph{tips}}\emph{.
And here's our email:}
\href{mailto:letters@NYTimes.com}{\emph{letters@NYTimes.com}}\emph{.}

\emph{Follow The New York Times Opinion section on}
\href{https://www.facebookcorewwwi.onion/nytopinion}{\emph{Facebook}}\emph{,}
\href{http://twitter.com/NYTOpinion}{\emph{Twitter (@NYTopinion)}}
\emph{and}
\href{https://www.instagram.com/nytopinion/}{\emph{Instagram}}\emph{.}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
