Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/world/middleeast}{Middle
East}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/world/middleeast}{Middle East}\textbar{}U.S. and Syria
Discuss Missing Journalist

\url{https://nyti.ms/1NkMsFa}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{us-and-syria-discuss-missing-journalist}{%
\section{U.S. and Syria Discuss Missing
Journalist}\label{us-and-syria-discuss-missing-journalist}}

By \href{https://www.nytimes3xbfgragh.onion/by/rick-gladstone}{Rick
Gladstone}

\begin{itemize}
\item
  March 26, 2015
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

The United States and Syrian governments are engaged in direct talks
concerning the whereabouts of Austin Tice, an American freelance
journalist and photographer who disappeared in Syria more than two and a
half years ago in the midst of the country's widening civil war, a State
Department official and Mr. Tice's father said Thursday.

But they denied a recent report in
\href{http://www.lefigaro.fr/international/2015/03/20/01003-20150320ARTFIG00446-washington-et-damas-discutent-d-un-otage.php}{Le
Figaro}, a French newspaper, that talks were underway to free him and
that his location is known. The Syrian authorities have repeatedly said
they do not know where Mr. Tice is or who, if anyone, is holding him.

Nonetheless, the acknowledgment of direct contacts between American and
Syrian officials is unusual. It appeared to suggest some easing, however
slight, of the deep hostility and mistrust expressed by the United
States toward President Bashar al-Assad of Syria, whose repression of
political dissent in 2011 morphed into a civil war that has become a
political and humanitarian disaster.

A State Department official confirmed a statement reported by Reuters
that ``we have been in periodic, direct contact with Syrian government
officials strictly on consular issues, including the case of Austin
Tice.'' The official spoke on the condition of anonymity in accordance
with department policy.

Mr. Tice's father, Marc Allen Tice, said in a telephone interview from
his Houston home that the State Department had informed him and his
wife, Debra, of the contacts. ``We're really happy to hear definitively
that the United States and Syria are in direct talks,'' he said.

The father also said that ``nobody has seen or visited Austin,'' and
that the family had no information on his captors. At the same time, the
father said, he was sure that the Islamic State, the extremist group in
Syria that has abducted and killed other Americans in the country, did
not have custody of Mr. Tice. ``What we hear and understand is that he
is most very likely alive and being reasonably well treated, wherever he
is,'' the father said.

Mr. Tice, 33, who served with the Marines in Iraq and Afghanistan and
was enrolled as a student in Georgetown Law School at the time he
entered Syria, vanished in August 2012. He had done work for a number of
Western news organizations and had developed a following on Facebook and
Twitter with his accounts of the Syrian uprising against Mr. Assad.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
