Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

Ballad of the Long Shot

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\href{/column/magazine-talk}{Talk}

\hypertarget{ballad-of-the-long-shot}{%
\section{Ballad of the Long Shot}\label{ballad-of-the-long-shot}}

By Andrew Goldman

\begin{itemize}
\item
  June 30, 2011
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

\textbf{Before you announced your campaign, you said that the liberal
establishment is scared that ``a real black man might run against Barack
Obama.'' Are you suggesting Obama isn't really black?}\\
A real black man is not timid about making the right decisions, that's
what I meant. Look, I'm not getting into this whole thing about
President Obama. It is documented that his mother was white and his
father was from Africa. If he wants to call himself black, fine. If he
wants to call himself African-American, fine. I'm not going down this
color road.

\textbf{But you're saying he's not really a black man.}\\
Not in terms of a strong black man that I'm identifying with. I identify
with a strong black man like Martin Luther King Jr., or my dad, Luther
Cain Jr., who didn't have a lot of formal education, but he had a Ph.D.
in common sense.

\textbf{It has been said that the Tea Party has embraced you partly to
provide cover for some racism in its ranks --- like, How could racists
support a black guy?}\\
There's no validity to that whatsoever. People who are still making
those accusations have no other way to intimidate the growing force of
the Tea Party citizens' movement.

\textbf{At Tea Party rallies, you see signs referring to Obama as
Kenyan. Are those racist?}\\
Not if you're from Kenya.

\textbf{But he was born here.}\\
I don't think calling him a Kenyan is racist. Secondly, I think those
kinds of signs have stopped because the leaders of the Tea Party
movement have instructed their folks that we don't need to do that kind
of stuff.

Image

Credit...Carrie Thompson for The New York Times

\textbf{Did I read that you once donated money to Bob Kerrey?}\\
I was a resident of Nebraska, and Bob Kerrey wasn't just the Democratic
senator from Nebraska; he was also a restaurateur. Yes, I contributed to
his campaign. Republicans who want to crucify me for that can if they
want. I have not been a lifelong voting Republican.

\textbf{Why did you become one, by the way?}\\
When I was an adviser to Jack Kemp in 1996, I was still a registered
independent. Jack took me and as many other big black guys as he could
to Sylvia's, in the heart of Harlem. As we were walking into the
restaurant, a very large black guy yelled out: ``Black Republicans?
There's no such thing.'' When I got back to Omaha, I registered as a
Republican. It haunted me for three days that someone would dare tell me
what party affiliation I should have.

\textbf{You earned millions running Godfather's Pizza, but you once said
that unlike Mitt Romney or Jon Huntsman, you were unwilling to spend
your fortune financing your campaign.}\\
O.K., don't use the term ``fortune.'' I don't have a fortune. And since
I made that statement, I have put some of my money in to prime the pump.
What I learned is that a lot of donors were reluctant to contribute
because I didn't have immediate name ID, I didn't have lots of money of
my own and I've never held public office. Now things are starting to
take off. Guess where it's coming from? Medium- to small-dollar donors:
\$25, \$50, \$100. Why? Because the regular people are getting behind
Herman Cain.

\textbf{Waves of energized small donors? It sounds very Obama '08.}\\
David Plouffe wrote a book about how he did Obama's fund-raising
strategy. And guess what we did? We read the book. Genius! Let me tell
you something about Herman Cain, I don't have a problem taking a good
idea and using it, even if it did come from Obama.

\textbf{When did you start referring to yourself in the third person?}\\
I've always done that.

\textbf{Since you were a kid? Like, ``Herman Cain is going to the
grocery store to get Mom some eggs?''}\\
I don't talk like that when I'm home. I don't know. I've never really
been conscious of it.

\textbf{You said of the Great Wall of China, ``I think we could build
one'' as a solution to our immigration problems. Are you concerned that
as many as three million Chinese died building it?}\\
My point was, if they could build that wall centuries ago without
bulldozers, we can secure the border today. It could be a combination of
walls and high-tech equipment. Now, if accidents happen, that's one
thing. But I think we can improve upon that ratio of three million
people dying.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
