Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/us}{U.S.}\textbar{}Where Americans Live Far From the
Emergency Room

\url{https://nyti.ms/3cOQbPo}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{the-coronavirus-outbreak}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=2805e3f0-e38d-11ea-befc-036b724b9a9b}{The
Coronavirus
Outbreak}}{The Coronavirus Outbreak}}\label{the-coronavirus-outbreak}}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes3xbfgragh.onion/2020/08/20/world/coronavirus-covid.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=2805e3f1-e38d-11ea-befc-036b724b9a9b}{Latest
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/coronavirus-us-cases.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=2805e3f2-e38d-11ea-befc-036b724b9a9b}{Maps
  and Cases}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/science/coronavirus-vaccine-tracker.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=28060b00-e38d-11ea-befc-036b724b9a9b}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/08/19/us/colleges-closing-covid.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=28060b01-e38d-11ea-befc-036b724b9a9b}{Colleges
  Closing}
\item
  \href{https://www.nytimes3xbfgragh.onion/live/2020/08/20/business/stock-market-today-coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=28060b02-e38d-11ea-befc-036b724b9a9b}{Economy}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{where-americans-live-far-from-the-emergency-room}{%
\section{Where Americans Live Far From the Emergency
Room}\label{where-americans-live-far-from-the-emergency-room}}

By Ella Koeze,
\href{https://www.nytimes3xbfgragh.onion/by/jugal-k-patel}{Jugal K.
Patel} and
\href{https://www.nytimes3xbfgragh.onion/by/anjali-singhvi}{Anjali
Singhvi}April 26, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

WASH.

MONT.

MAINE

N.D.

MINN.

ORE.

VT.

N.H.

WIS.

IDAHO

S.D.

N.Y.

MASS.

WYO.

MICH.

R.I.

CONN.

IOWA

PA.

NEB.

NEV.

N.J.

OHIO

ILL.

MD.

IND.

UTAH

DEL.

D.C.

COLO.

W.VA.

CALIF.

VA.

KAN.

MO.

KY.

N.C.

TENN.

OKLA.

ARIZ.

ARK.

N.M.

S.C.

ALA.

GA.

MISS.

LA.

TEXAS

FLA.

ALASKA

HAWAII

V.I.

P.R.

WASH.

MAINE

MONT.

N.D.

MINN.

ORE.

VT.

N.H.

WIS.

IDAHO

S.D.

N.Y.

MASS.

WYO.

MICH.

R.I.

CONN.

PA.

IOWA

NEB.

N.J.

NEV.

OHIO

MD.

ILL.

IND.

DEL.

UTAH

D.C.

W.VA.

COLO.

CALIF.

VA.

KAN.

MO.

KY.

N.C.

TENN.

OKLA.

ARIZ.

ARK.

N.M.

S.C.

ALA.

GA.

MISS.

LA.

TEXAS

FLA.

ALASKA

HAWAII

V.I.

P.R.

WASH.

MONT.

MAINE

N.D.

MINN.

ORE.

VT.

N.H.

WIS.

IDAHO

S.D.

N.Y.

MASS.

WYO.

MICH.

R.I.

CONN.

IOWA

PA.

NEB.

NEV.

N.J.

OHIO

ILL.

MD.

IND.

UTAH

DEL.

D.C.

COLO.

W.VA.

CALIF.

VA.

KAN.

MO.

KY.

N.C.

TENN.

OKLA.

ARIZ.

ARK.

N.M.

S.C.

ALA.

GA.

MISS.

LA.

TEXAS

FLA.

ALASKA

HAWAII

V.I.

P.R.

WASH.

MAINE

MONT.

N.D.

MINN.

ORE.

VT.

N.H.

WIS.

IDAHO

S.D.

N.Y.

MASS.

WYO.

MICH.

R.I.

CONN.

PA.

IOWA

NEB.

N.J.

NEV.

OHIO

MD.

ILL.

IND.

DEL.

UTAH

D.C.

W.VA.

COLO.

CALIF.

VA.

KAN.

MO.

KY.

N.C.

TENN.

OKLA.

ARIZ.

ARK.

N.M.

S.C.

ALA.

GA.

MISS.

LA.

TEXAS

FLA.

ALASKA

HAWAII

V.I.

P.R.

WASH.

People living outside a 30-minute

drive from the nearest hospital

MONT.

MAINE

N.D.

0

10,000

30,000

50,000+ people

MINN.

ORE.

VT.

N.H.

WIS.

IDAHO

S.D.

N.Y.

MASS.

WYO.

MICH.

R.I.

CONN.

IOWA

PA.

NEB.

NEV.

N.J.

OHIO

ILL.

MD.

IND.

UTAH

DEL.

D.C.

COLO.

W.VA.

CALIF.

VA.

KAN.

MO.

KY.

N.C.

TENN.

OKLA.

ARIZ.

ARK.

N.M.

S.C.

ALA.

GA.

MISS.

LA.

TEXAS

FLA.

ALASKA

HAWAII

V.I.

P.R.

WASH.

50,000+

people

0

10,000

MAINE

MONT.

N.D.

MINN.

ORE.

VT.

N.H.

WIS.

IDAHO

S.D.

N.Y.

MASS.

WYO.

MICH.

R.I.

CONN.

PA.

IOWA

NEB.

N.J.

NEV.

OHIO

MD.

ILL.

IND.

DEL.

UTAH

D.C.

W.VA.

COLO.

CALIF.

VA.

KAN.

MO.

KY.

N.C.

TENN.

OKLA.

ARIZ.

ARK.

N.M.

S.C.

ALA.

GA.

MISS.

LA.

TEXAS

FLA.

ALASKA

HAWAII

V.I.

P.R.

\begin{itemize}
\item
\item
\item
\end{itemize}

This map shows everywhere \textbf{outside a 30-minute drive} from the
nearest hospital offering the kind of inpatient medical care needed to
treat coronavirus.

Even though there are about 5,250 of these \textbf{acute care and
critical access hospitals} in the United States, in large areas of the
country it is hard to reach one.

About 8.6 million people live in these areas. \textbf{Darker areas} show
where more people live far from hospital care. What will they do as the
coronavirus hits?

As the coronavirus outbreak spreads into rural parts of the United
States, more people who live far from a hospital are increasingly likely
to need one. That poses challenges for communities where hospitals are
scarce and I.C.U. beds are in short supply --- even a relatively small
outbreak there could overwhelm medical resources, with potentially grim
consequences for public health.

Research shows people are less likely to seek health care, even
emergency care, when they need to travel farther to get it, especially
when they are more than about 30 minutes from a hospital.

``We already know that people in rural regions who are located farther
from health care use care less and generally have worse outcomes,'' said
Dr. Paul Delamater, a researcher on health care access at the University
of North Carolina.

And that's under normal circumstances. In a pandemic, the problem is
twofold. Without a hospital nearby, those who are sick may not seek care
at all, leaving them to suffer and to risk spreading the infection to
others.

But if a large outbreak does occur and too many people need treatment,
rural hospitals could easily be overwhelmed and be forced to send
patients traveling even farther from their homes for care.

``I would imagine things are only going to get worse, not better,'' Dr.
Delamater said.

\textbf{Read more:}
\href{https://www.nytimes3xbfgragh.onion/2020/04/26/us/hospital-closures-west-virginia-ohio.html}{Closed
Hospitals Leave Rural Patients `Stranded' as Coronavirus Spreads}

Dozens of
\href{https://www.shepscenter.unc.edu/programs-projects/rural-health/rural-hospital-closures/}{rural
hospitals}\href{https://www.shepscenter.unc.edu/programs-projects/rural-health/rural-hospital-closures/}{have
closed in the last decade}, many of them in the Southeast. In the West,
there have been fewer closures, but hospitals are more dispersed and
many are designated
``\href{https://www.ruralhealthinfo.org/topics/critical-access-hospitals}{critical
access hospitals},'' with 25 or fewer inpatient beds. That means fewer
beds, farther apart for the sick, whether those with coronavirus or
those needing other treatment.

The problem of distance is further compounded by demographics. Rural
populations generally tend to be older and have higher rates of
underlying health conditions, making them most at risk of
hospitalization from the coronavirus.

\hypertarget{people-living-outside-a-30-minute-drive-from-the-nearest-hospital}{%
\subsubsection{People living outside a 30-minute drive from the nearest
hospital}\label{people-living-outside-a-30-minute-drive-from-the-nearest-hospital}}

\begin{longtable}[]{@{}llllll@{}}
\toprule
\textbf{Rank} & \textbf{State} & \textbf{All ages} & \textbf{Rank} &
\textbf{State} & \textbf{65 and older}\tabularnewline
\midrule
\endhead
1 & California & 794,000 & 1 & California & 151,000\tabularnewline
2 & Florida & 551,000 & 2 & Washington & 112,000\tabularnewline
3 & Arizona & 541,000 & 3 & Florida & 111,000\tabularnewline
4 & Washington & 537,000 & 4 & Arizona & 106,000\tabularnewline
5 & Missouri & 347,000 & 5 & Oregon & 82,000\tabularnewline
6 & Texas & 347,000 & 6 & Missouri & 75,000\tabularnewline
7 & Colorado & 343,000 & 7 & Texas & 75,000\tabularnewline
8 & New York & 331,000 & 8 & Virginia & 69,000\tabularnewline
9 & Oregon & 326,000 & 9 & New York & 66,000\tabularnewline
10 & Virginia & 325,000 & 10 & North Carolina & 63,000\tabularnewline
\bottomrule
\end{longtable}

By The New York Times·Source: 2014-18 American Community Survey

Alpine County, which straddles the Sierra Nevada in Northern California,
is one of more than 700 counties nationwide with no hospital at all. The
closest is in South Lake Tahoe, a 30- to 40-minute drive for most
residents, according to Nichole Williamson, the county's director for
Health and Human Services.

Just one person in the county has tested positive for coronavirus so
far, but if the outbreak were to grow, Ms. Williamson said, there would
not be much they could do. A shortage of medical personnel means that
setting up a temporary hospital would not be an option. ``We have plenty
of buildings we could use,'' she said, ``but we don't have the staff to
open up an alternate care site.''

Ms. Williamson said that if an outbreak occurred in Alpine County, she
would expect people would need to be sent to a bigger hospital in Reno,
Nev., about an hour and 15 minutes away.

In some cities where
\href{https://www.nytimes3xbfgragh.onion/2020/03/25/nyregion/nyc-coronavirus-hospitals.html}{hospitals}\href{https://www.nytimes3xbfgragh.onion/2020/03/25/nyregion/nyc-coronavirus-hospitals.html}{are
overwhelmed}, more people have been found
\href{https://www.propublica.org/article/theres-been-a-spike-in-people-dying-at-home-in-several-cities-that-suggests-coronavirus-deaths-are-higher-than-reported}{dead
at home}. Evidence is also building that people who might have otherwise
gone in for conditions unrelated to the coronavirus are
\href{https://www.nytimes3xbfgragh.onion/2020/04/06/well/live/coronavirus-doctors-hospitals-emergency-care-heart-attack-stroke.html}{avoiding
hospitals} for fear of contracting the virus.

So far, those outcomes are a risk but not yet a reality in most rural
areas. In some counties with the largest populations living far from
hospitals, local officials said they had not heard of anyone failing to
get the medical treatment they needed.

In Whatcom County, Wash., for example, 38,000 people live 30 or more
minutes from St. Joseph Medical Center in Bellingham. Cindy
Hollinsworth, an expert in communicable diseases at the county health
department, said that even though many residents did not live within
that range, all lived within a 40-minute drive and had access to
emergency medical services.

\textbf{Read more:}
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/04/08/us/coronavirus-rural-america-cases.html}{Coronavirus
Was Slow to Spread to Rural America. Not Anymore.}

A spokesman for San Bernardino County, Calif., where there are 24
hospitals but 61,000 residents still live outside the 30-minute range,
said the current public health concern there was a shortage of tests for
the virus, not hospital beds.

But some areas of the country with large populations living far from
hospitals are showing cause for concern. Rural communities in three
states where the coronavirus has spread --- Arizona, Florida and
Washington --- are already experiencing strain on their local medical
facilities.

\hypertarget{outbreak-in-navajo-nation}{%
\subsection{Outbreak in Navajo Nation}\label{outbreak-in-navajo-nation}}

Across
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/arizona-coronavirus-cases.html}{Arizona's}
remote landscape, about half a million people live more than a 30-minute
drive from the nearest hospital. Access is especially difficult in
Native American tribal areas, where coronavirus cases are growing
quickly.

An outbreak that began in mid-March had reached 350 infections just in
Navajo County as
\href{https://www.navajo-nsn.gov/News\%20Releases/OPVP/2020/Apr/FOR\%20IMMEDIATE\%20RELEASE\%20-\%2078\%20new\%20cases\%20and\%20three\%20more\%20deaths\%20related\%20to\%20COVID-19\%20reported.pdf}{of
Thursday morning}, with a higher rate of cases per capita than most
states.

\hypertarget{people-living-outside-a-30-minute-drive-from-the-nearest-hospital-1}{%
\subsubsection{People living outside a 30-minute drive from the nearest
hospital}\label{people-living-outside-a-30-minute-drive-from-the-nearest-hospital-1}}

Acute care

hospitals

Critical access

hospitals

1,000

2,000

3,000

4,000

5,000+ people

Navajo

Nation

Kingman

40

Flagstaff

17

Arizona

Phoenix

8

Yuma

Tucson

50 miles

Acute care

hospitals

Critical access

hospitals

1,000

3,000

5,000+ people

Navajo

Nation

Kingman

40

Flagstaff

17

Arizona

Phoenix

8

Yuma

Tucson

50 miles

1,000

3,000

5,000+ people

Acute care hospitals

Critical access hospitals

Navajo

Nation

40

Flagstaff

Ariz.

Phoenix

8

Tucson

50 miles

Acute care

hospitals

Critical access

hospitals

1,000

2,000

3,000

4,000

5,000+ people

Navajo

Nation

Navajo

County

Kingman

40

Flagstaff

17

Arizona

Phoenix

8

Yuma

Tucson

50 miles

By The New York Times

Anne Newland, who operates primary care clinics across Northern Arizona,
said smaller tribal clinics were already reaching capacity and
transferring patients who needed intensive care to facilities in
Flagstaff and Phoenix.

``In Navajo County, they're trying to get patients who need a ventilator
out,'' she said. ``Patients from these highly affected areas are able to
be transferred down to the valley, but that's an expense.''

Patient transfers can cost up to \$20,000, an overwhelming burden for
smaller facilities. ``Covid-19 is just a condition that's challenging
everybody,'' Dr. Newland said.

She also worries that given the severity of the outbreak, people will be
hesitant to travel long distances to hospitals at all.

``It's not just the distance, it's that people are afraid,'' she said.
``And sometimes they need to see their doctor or go into the E.R., and
they shouldn't avoid that.''

\hypertarget{fear-among-florida-farmworkers}{%
\subsection{Fear Among Florida
Farmworkers}\label{fear-among-florida-farmworkers}}

In rural
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/florida-coronavirus-cases.html}{Florida},
hospital access is the most limited in the farm towns of the panhandle
and north of the Everglades.

\hypertarget{people-living-outside-a-30-minute-drive-from-the-nearest-hospital-2}{%
\subsubsection{People living outside a 30-minute drive from the nearest
hospital}\label{people-living-outside-a-30-minute-drive-from-the-nearest-hospital-2}}

Tallahassee

Jacksonville

10

50 miles

Gainesville

1,000

2,000

3,000

4,000

5,000+ people

Acute care hospitals

Critical access

hospitals

95

Orlando

4

Tampa

Florida

Immokalee

Miami

Naples

75

10

100 miles

Gainesville

95

1,000

3,000

5,000+ people

Acute care

hospitals

Critical access

hospitals

4

Tampa

Florida

Immokalee

75

Naples

Miami

10

Gainesville

100 miles

95

4

Tampa

Fla.

1,000

3,000

5,000+ people

Acute care hospitals

Immokalee

Critical access hospitals

Naples

Miami

Tallahassee

10

Jacksonville

50 miles

Gainesville

1,000

2,000

3,000

4,000

5,000+ people

Acute care hospitals

Critical access

hospitals

95

Orlando

4

Tampa

Florida

Miami

Naples

75

By The New York Times

The lack of a nearby hospital in Immokalee, a migrant farming town of
24,000 in South Florida, creates
\href{https://www.nytimes3xbfgragh.onion/2018/09/05/us/rural-florida-hospital.html}{health
care challenges} under normal circumstances and is causing greater
concern as the coronavirus pandemic unfolds. As of Friday, 34
\href{https://www.naplesnews.com/story/news/2020/04/22/coronavirus-florida-updates-covid-19-collier-county/3002125001/}{confirmed
cases} had surfaced in the town.

Workers there produce most of the state's tomato supply. They have
called for a field hospital to be set up in town through the Coalition
of Immokalee Workers, a labor advocacy and human rights group.

``We're about 40 minutes to an hour to a hospital, so that's going to be
very limiting,'' said Lupe Gonzalo, a farm worker and staff member of
the coalition.

Farm workers are deemed essential workers, but they lack protective
equipment, and for many workers social distancing is impractical.

``The buses they ride on to go to the farms are packed, sometimes with
over 40 or 50 people,'' Mrs. Gonzalo said. ``The workers live in
confined spaces --- maybe 10 to 15 people in a trailer. So if one person
gets sick, many people will get sick.''

\hypertarget{empty-hospitals-in-washington-state}{%
\subsection{Empty Hospitals in Washington
State}\label{empty-hospitals-in-washington-state}}

In
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/washington-coronavirus-cases.html}{Washington}
State, rural hospitals are seeing problems with too few patients rather
than too many. Nonurgent procedures are suspended, and people with
chronic conditions are avoiding going to the hospital.

``We are actually seeing people delay care that's kind of concerning
right now,'' said Jacqueline Barton True, the vice president of rural
health programs at the Washington State Hospital Association.

\hypertarget{people-living-outside-a-30-minute-drive-from-the-nearest-hospital-3}{%
\subsubsection{People living outside a 30-minute drive from the nearest
hospital}\label{people-living-outside-a-30-minute-drive-from-the-nearest-hospital-3}}

Critical access

hospitals

Acute care

hospitals

1,000

3,000

5,000+ people

Three Rivers

Hospital

Seattle

WASHINGTON

Spokane

Tacoma

90

5

Longview

Walla Walla

50 miles

Acute care

hospitals

Critical access

hospitals

1,000

2,000

3,000

4,000

5,000+ people

Three Rivers Hospital

Spokane

Seattle

WASHINGTON

Tacoma

90

5

Longview

Walla Walla

50 miles

1,000

3,000

5,000+ people

Acute care hospitals

Critical access hospitals

Three Rivers

Hospital

WASH.

Spokane

Seattle

90

5

50 miles

By The New York Times

Ms. Barton True said at least six critically ill patients had had to be
airlifted from rural Columbia County since the last week of March, an
unusually high number, and none of them with coronavirus.

All over the state, rural hospitals that canceled elective surgeries to
keep beds open for coronavirus patients have taken a heavy financial
hit. On Wednesday, a spokeswoman for the Three Rivers Hospital in
Brewster said they had just 51 days of cash on hand.

``The most vulnerable rural hospitals are hardest hit by the inability
to generate revenue,'' Becky Bennett, a spokeswoman for the state health
department, said.

Despite some federal aid, there's growing concern over whether these
hospitals will be able to weather the crisis in the long term. Advance
payments from Medicare have helped, Ms. Barton True said, but ``that
money will have to be paid back in a number of months, and a lot of our
hospitals are very concerned about how and whether they're going to be
able to pay that money back.''

While cases are declining in
\href{https://www.google.com/url?q=https://www.nytimes3xbfgragh.onion/2020/04/22/us/coronavirus-sequencing.html\&sa=D\&ust=1587745484219000\&usg=AFQjCNHm73DsOS6vdq1smUt9-EwTSCISig}{the
Seattle area}, where the U.S. outbreak first began, they are still
rising in some rural counties, such as Douglas, though in far smaller
numbers. The state is able to run 21,000 tests for the virus each day,
but in Kitsap County and other rural areas, health care providers said
they were still being told to prioritize testing for high-risk groups,
not everyone who may have symptoms.

Steve Metcalf, a spokesman for the Tacoma-Pierce County Health
Department, said it was still possible that hospitals there could face
problems with capacity. ``When the time comes to reduce social
distancing --- we are not there yet --- we anticipate there could be a
bounce in cases at local hospitals,'' he said.

\hypertarget{tracking-the-coronavirus}{%
\subsection{Tracking the Coronavirus}\label{tracking-the-coronavirus}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/coronavirus-maps.html}{World}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/03/21/upshot/coronavirus-deaths-by-country.html}{Deaths}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/04/03/upshot/coronavirus-metro-area-tracker.html}{U.S.
  cities}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/04/23/upshot/five-ways-to-monitor-coronavirus-outbreak-us.html}{Look
  up your city}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/states-reopen-map-coronavirus.html}{State
  shutdown status}
\end{itemize}

Countries

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/americas/brazil-coronavirus-cases.html}{Brazil}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/canada/canada-coronavirus-cases.html}{Canada}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/europe/france-coronavirus-cases.html}{France}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/europe/germany-coronavirus-cases.html}{Germany}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/asia/india-coronavirus-cases.html}{India}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/europe/italy-coronavirus-cases.html}{Italy}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/europe/united-kingdom-coronavirus-cases.html}{U.K.}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/coronavirus-us-cases.html}{United
  States}
\end{itemize}

State by state

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/alabama-coronavirus-cases.html}{Alabama}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/alaska-coronavirus-cases.html}{Alaska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/arizona-coronavirus-cases.html}{Arizona}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/arkansas-coronavirus-cases.html}{Arkansas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/california-coronavirus-cases.html}{California}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/colorado-coronavirus-cases.html}{Colorado}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/connecticut-coronavirus-cases.html}{Connecticut}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/delaware-coronavirus-cases.html}{Delaware}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/florida-coronavirus-cases.html}{Florida}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/georgia-coronavirus-cases.html}{Georgia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/hawaii-coronavirus-cases.html}{Hawaii}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/idaho-coronavirus-cases.html}{Idaho}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/illinois-coronavirus-cases.html}{Illinois}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/indiana-coronavirus-cases.html}{Indiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/iowa-coronavirus-cases.html}{Iowa}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/kansas-coronavirus-cases.html}{Kansas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/kentucky-coronavirus-cases.html}{Kentucky}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/louisiana-coronavirus-cases.html}{Louisiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/maine-coronavirus-cases.html}{Maine}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/maryland-coronavirus-cases.html}{Maryland}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/massachusetts-coronavirus-cases.html}{Massachusetts}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/michigan-coronavirus-cases.html}{Michigan}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/minnesota-coronavirus-cases.html}{Minnesota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/mississippi-coronavirus-cases.html}{Mississippi}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/missouri-coronavirus-cases.html}{Missouri}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/montana-coronavirus-cases.html}{Montana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/nebraska-coronavirus-cases.html}{Nebraska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/nevada-coronavirus-cases.html}{Nevada}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/new-hampshire-coronavirus-cases.html}{New
  Hampshire}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/new-jersey-coronavirus-cases.html}{New
  Jersey}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/new-mexico-coronavirus-cases.html}{New
  Mexico}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/new-york-coronavirus-cases.html}{New
  York}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/north-carolina-coronavirus-cases.html}{North
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/north-dakota-coronavirus-cases.html}{North
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/ohio-coronavirus-cases.html}{Ohio}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/oklahoma-coronavirus-cases.html}{Oklahoma}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/oregon-coronavirus-cases.html}{Oregon}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/pennsylvania-coronavirus-cases.html}{Pennsylvania}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/puerto-rico-coronavirus-cases.html}{Puerto
  Rico}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/rhode-island-coronavirus-cases.html}{Rhode
  Island}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/south-carolina-coronavirus-cases.html}{South
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/south-dakota-coronavirus-cases.html}{South
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/tennessee-coronavirus-cases.html}{Tennessee}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/texas-coronavirus-cases.html}{Texas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/utah-coronavirus-cases.html}{Utah}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/vermont-coronavirus-cases.html}{Vermont}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/virginia-coronavirus-cases.html}{Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/washington-coronavirus-cases.html}{Washington}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/washington-dc-coronavirus-cases.html}{Washington,
  D.C.}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/west-virginia-coronavirus-cases.html}{West
  Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/wisconsin-coronavirus-cases.html}{Wisconsin}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/wyoming-coronavirus-cases.html}{Wyoming}
\end{itemize}

Methodology

Hospital locations include all currently open short-term acute care and
critical access hospitals with inpatient beds in the United States,
according to the \href{https://www.ahd.com/}{American Hospital
Directory}.

We generated shapes of areas within a 30-minute drive of hospital
locations using the \href{https://traveltime.com/}{TravelTime} mapping
service. We then merged those shapes to see which areas of the United
States fell outside them.

Population was counted using census block groups where populated areas
overlapped with areas outside a 30-minute drive from the hospital
locations. Population totals are approximate. Block group populations
were aggregated to the county level for the national map but shown at
the block-group level on the maps of Arizona, Florida and Washington.

Sources: American Hospital Directory (hospital locations and types);
2014-18 American Community Survey (population data); Baruch College,
City University of New York and the Census Bureau (population centers of
census block groups); TravelTime (areas within a 30-minute drive of each
hospital)

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
