\href{//www.nytimes3xbfgragh.onion}{}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{
Election 2018}

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-house-elections.html}{House
House}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-senate-elections.html}{Senate
Senate}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-house-forecast.html}{House
Forecast
Forecast}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-senate-forecast.html}{Senate
Forecast}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-governor-elections.html}{Governor}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-dashboard-live.html}{Dashboard
Dashboard}\protect\hyperlink{}{State Results States}

Elections Near You

All States

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-alabama-elections.html}{Alabama}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-alaska-elections.html}{Alaska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-arizona-elections.html}{Arizona}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-arkansas-elections.html}{Arkansas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-california-elections.html}{California}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-colorado-elections.html}{Colorado}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-connecticut-elections.html}{Connecticut}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-delaware-elections.html}{Delaware}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-district-of-columbia-elections.html}{D.C.}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-florida-elections.html}{Florida}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-georgia-elections.html}{Georgia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-hawaii-elections.html}{Hawaii}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-idaho-elections.html}{Idaho}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-illinois-elections.html}{Illinois}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-indiana-elections.html}{Indiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-iowa-elections.html}{Iowa}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-kansas-elections.html}{Kansas}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-kentucky-elections.html}{Kentucky}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-louisiana-elections.html}{Louisiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-maine-elections.html}{Maine}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-maryland-elections.html}{Maryland}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-massachusetts-elections.html}{Massachusetts}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-michigan-elections.html}{Michigan}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-minnesota-elections.html}{Minnesota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-mississippi-elections.html}{Mississippi}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-missouri-elections.html}{Missouri}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-montana-elections.html}{Montana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-north-dakota-elections.html}{North
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-nebraska-elections.html}{Nebraska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-nevada-elections.html}{Nevada}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-hampshire-elections.html}{New
  Hampshire}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-jersey-elections.html}{New
  Jersey}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-mexico-elections.html}{New
  Mexico}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{New
  York}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-north-carolina-elections.html}{North
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-ohio-elections.html}{Ohio}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-oklahoma-elections.html}{Oklahoma}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-oregon-elections.html}{Oregon}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-pennsylvania-elections.html}{Pennsylvania}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-rhode-island-elections.html}{Rhode
  Island}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-south-carolina-elections.html}{South
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-south-dakota-elections.html}{South
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-tennessee-elections.html}{Tennessee}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-texas-elections.html}{Texas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-utah-elections.html}{Utah}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-vermont-elections.html}{Vermont}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-virginia-elections.html}{Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-washington-elections.html}{Washington}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-west-virginia-elections.html}{West
  Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-wisconsin-elections.html}{Wisconsin}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-wyoming-elections.html}{Wyoming}
\end{itemize}

May 15, 2019, 2:11 PM ET

\hypertarget{new-york-election-results}{%
\section{New York Election Results}\label{new-york-election-results}}

Senate

House

Governor

Legislature

Ballot Measures

For Democrats, the road to a majority in the House of Representatives
ran through Republican-held districts in the suburbs and exurbs of
increasingly blue New York. Read more

In three such districts, scattered from Staten Island to Lake Ontario,
competitive races by Democratic newcomers proved pivotal in deciding
control of the House.

As expected, there was little suspense in the governor's race. The
Democratic incumbent, Andrew M. Cuomo,
\href{https://www.nytimes3xbfgragh.onion/2018/11/06/nyregion/andrew-cuomo-wins-governor.html}{won
a third term}, defeating the Republican candidate, the Dutchess county
executive Marcus Molinaro who gave Mr. Cuomo scant competition. Senator
Kirsten Gillibrand was also easily re-elected, securing over 76 percent
of the vote against her long-shot challenger, the Republican candidate,
Chele Chiavacci Farley.

\hypertarget{us-senate}{%
\subsection{U.S. Senate}\label{us-senate}}

Candidate

Party

Votes

Pct.

 Gillibrand* Kirsten Gillibrand*

Democrat Dem.

4,056,931

67.0\%

 Farley Chele Farley

Republican Rep.

1,998,220

33.0\%

6,055,151 votes, 100\% reporting (15,598 of 15,598 precincts)

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-senate}{See
Full Race Results~ ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-senate}{See
Full Race Results~ ›}

\hypertarget{results-map}{%
\paragraph{Results Map}\label{results-map}}

Vote share

Dem. 50 60 70

Rep. 50 60 70

No results

County

Gillibrand

Farley

Rpt.

Brooklyn

542,736

85,973

100\%

Manhattan

481,779

53,813

100\%

Suffolk

289,528

239,477

100\%

Nassau

294,186

204,875

100\%

Queens

398,414

89,810

100\%

Erie

206,024

127,860

100\%

Westchester

234,173

96,978

100\%

Bronx

257,723

23,033

100\%

Monroe

174,788

105,198

100\%

Onondaga

109,201

66,599

100\%

Staten Island

71,175

65,375

100\%

Orange

67,701

52,640

100\%

Albany

78,115

36,456

100\%

Dutchess

63,675

47,268

100\%

Rockland

59,386

39,730

100\%

Saratoga

52,523

43,114

100\%

Ulster

50,163

27,410

100\%

Oneida

38,613

37,446

100\%

Broome

41,145

30,897

100\%

Niagara

35,225

36,088

100\%

Rensselaer

34,680

25,964

100\%

Schenectady

32,735

22,005

100\%

Ontario

23,126

20,543

100\%

Chautauqua

20,810

22,361

100\%

Putnam

19,103

19,222

100\%

Oswego

17,717

20,499

100\%

Tompkins

28,818

8,399

100\%

Steuben

13,868

19,776

100\%

Saint Lawrence

17,970

14,201

100\%

Wayne

13,931

17,522

100\%

Jefferson

14,741

14,884

100\%

Chemung

14,347

14,902

100\%

Columbia

18,137

11,055

100\%

Cayuga

13,823

13,232

100\%

Clinton

15,930

10,012

100\%

Warren

14,634

11,118

100\%

Madison

12,817

12,894

100\%

Sullivan

12,937

11,319

100\%

Livingston

11,311

12,782

100\%

Cattaraugus

10,431

13,256

100\%

Otsego

11,453

9,969

100\%

Herkimer

9,395

11,742

100\%

Genesee

8,149

12,552

100\%

Washington

10,465

9,940

100\%

Greene

8,944

10,293

100\%

Tioga

8,002

10,188

100\%

Delaware

7,871

9,066

100\%

Fulton

6,896

9,790

100\%

Chenango

7,286

8,996

100\%

Cortland

9,113

7,099

100\%

Montgomery

7,024

8,131

100\%

Allegany

5,460

9,261

100\%

Essex

8,294

5,591

100\%

Franklin

8,245

5,576

100\%

Wyoming

4,330

8,837

100\%

Orleans

4,545

7,999

100\%

Schoharie

5,355

6,726

100\%

Seneca

5,997

5,484

100\%

Lewis

3,707

5,120

100\%

Yates

3,743

4,344

100\%

Schuyler

3,440

3,868

100\%

Hamilton

1,078

1,662

100\%

+ Show all counties -- Collapse counties

\hypertarget{us-house}{%
\subsection{U.S. House}\label{us-house}}

Dem. 21 won (+3 seats) 0 lead

Rep. 6 won 0 lead

Ind. 0 won 0 lead

Dem. 21 won (+3 seats) 0 lead

Rep. 6 won 0 lead

Ind. 0 won 0 lead

District Dist.

Candidate

Rpt.

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{11}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{
53\%Rose~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{
47\%Donovan*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{19}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{
51\%Delgado~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{
46\%Faso*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{22}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{
51\%Brindisi~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{
49\%Tenney*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{24}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{
53\%Katko*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{
47\%Balter~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{27}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{
49\%Collins*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{
49\%McMurray~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-1}{1}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-1}{
52\%Zeldin*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-1}{
47\%Gershon~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-1}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-1}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-2}{2}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-2}{
53\%King*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-2}{
47\%Grechen Shirley~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-2}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-2}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-3}{3}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-3}{
59\%Suozzi*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-3}{
41\%DeBono~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-3}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-3}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-4}{4}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-4}{
61\%Rice*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-4}{
39\%Benno~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-4}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-4}{}

5

 0\%Meeks*~Dem.

Uncontested

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-6}{6}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-6}{
91\%Meng*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-6}{
9\%Hillgardner~Green}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-6}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-6}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-7}{7}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-7}{
93\%Velazquez*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-7}{
6\%Lieberman~Con.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-7}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-7}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-8}{8}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-8}{
94\%Jeffries*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-8}{
5\%Johnson~Con.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-8}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-8}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-9}{9}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-9}{
89\%Clarke*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-9}{
10\%Gayot~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-9}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-9}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-10}{10}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-10}{
82\%Nadler*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-10}{
18\%Levin~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-10}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-10}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-12}{12}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-12}{
86\%Maloney*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-12}{
12\%Rabin~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-12}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-12}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-13}{13}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-13}{
95\%Espaillat*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-13}{
5\%Butler~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-13}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-13}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-14}{14}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-14}{
78\%Ocasio-Cortez~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-14}{
14\%Pappas~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-14}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-14}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-15}{15}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-15}{
96\%Serrano*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-15}{
4\%Gonzalez~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-15}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-15}{}

16

 0\%Engel*~Dem.

Uncontested

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-17}{17}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-17}{
88\%Lowey*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-17}{
12\%Ciardullo~Reform}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-17}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-17}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-18}{18}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-18}{
56\%Maloney*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-18}{
45\%O'Donnell~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-18}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-18}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-20}{20}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-20}{
67\%Tonko*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-20}{
34\%Vitollo~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-20}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-20}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-21}{21}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-21}{
56\%Stefanik*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-21}{
42\%Cobb~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-21}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-21}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-23}{23}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-23}{
54\%Reed*~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-23}{
46\%Mitrano~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-23}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-23}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-25}{25}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-25}{
59\%Morelle~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-25}{
41\%Maxwell~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-25}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-25}{}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-26}{26}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-26}{
73\%Higgins*~Dem.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-26}{
27\%Zeno~Rep.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-26}{100\%}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-26}{}

+ Show all 27 districts -- Show fewer districts

* Incumbent~

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-house-elections.html}{See
Full House Results ›}

Dem. Lead Win Flip

Rep. Lead Win Flip

Other Lead Win Flip

\hypertarget{analysis-from-our-reporters-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/live-midterm-election-analysis-updates.html}{Analysis
From Our
Reporters~›}}{Analysis From Our Reporters~›}}\label{analysis-from-our-reporters-}}

\protect\hyperlink{}{Sign up for alerts}

\hypertarget{key-house-races}{%
\subsection{Key House Races}\label{key-house-races}}

\hypertarget{us-house-district-11-}{%
\paragraph{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{U.S.
House District 11
›}}{U.S. House District 11 ›}}\label{us-house-district-11-}}

Candidate

Party

Votes

Pct.

 Rose Max Rose

Democrat Dem.

101,823

53.0\%

 Donovan* Dan Donovan*

Republican Rep.

89,441

46.6\%

 Bardel Henry Bardel

Green Green

774

0.4\%

192,038 votes, 100\% reporting (489 of 489 precincts)

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{See
Full Race Results~ ›}

Of New York City's five boroughs, only Staten Island leans Republican.
Yet Max Rose, the Democratic challenger who is also a health care
executive and National Guard
officer,\href{https://www.nytimes3xbfgragh.onion/2018/11/07/nyregion/senate-house-race.html}{won
this Congressional seat} against the Republican incumbent, Daniel
Donovan.

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-11}{See
Full Race Results~ ›}

\hypertarget{us-house-district-19-}{%
\paragraph{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{U.S.
House District 19
›}}{U.S. House District 19 ›}}\label{us-house-district-19-}}

Candidate

Party

Votes

Pct.

 Delgado Antonio Delgado

Democrat Dem.

147,873

51.4\%

 Faso* John Faso*

Republican Rep.

132,873

46.2\%

 Greenfield Steven Greenfield

Green Green

4,313

1.5\%

 Neal Diane Neal

Independent Ind.

2,835

1.0\%

287,894 votes, 100\% reporting (619 of 619 precincts)

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{See
Full Race Results~ ›}

Both parties saw opportunity in this sprawling district in the Hudson
Valley and Catskill Mountains, where a competitive race became racially
charged. The Democratic challenger, Antonio Delgado, is an
African-American Rhodes scholar who focused on universal health care and
emphasized his working-class upbringing in Schenectady, N.Y.
\href{https://www.nytimes3xbfgragh.onion/2018/11/07/nyregion/senate-house-race.html}{It
was enough to unseat} the Republican incumbent, John Faso, a lawyer and
longtime state legislator.

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-19}{See
Full Race Results~ ›}

\hypertarget{us-house-district-22-}{%
\paragraph{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{U.S.
House District 22
›}}{U.S. House District 22 ›}}\label{us-house-district-22-}}

Candidate

Party

Votes

Pct.

 Brindisi Anthony Brindisi

Democrat Dem.

127,715

50.9\%

 Tenney* Claudia Tenney*

Republican Rep.

123,242

49.1\%

250,957 votes, 100\% reporting (555 of 555 precincts)

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{See
Full Race Results~ ›}

Anthony Brindisi, a Democratic state assemblyman,
\href{https://www.nytimes3xbfgragh.onion/2018/11/07/nyregion/senate-house-race.html}{defeated}
a first-term Republican incumbent, Claudia Tenney, in a district
stretching through central New York from the Pennsylvania border to the
shores of Lake Ontario, taking in the cities of Utica and Binghamton.
Though the district is now seen as leaning Republican, Democrats
represented much of its territory in the decade before the 2012
redistricting.

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-22}{See
Full Race Results~ ›}

\hypertarget{us-house-district-24-}{%
\paragraph{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{U.S.
House District 24
›}}{U.S. House District 24 ›}}\label{us-house-district-24-}}

Candidate

Party

Votes

Pct.

 Katko* John Katko*

Republican Rep.

136,920

52.6\%

 Balter Dana Balter

Democrat Dem.

123,226

47.4\%

260,146 votes, 100\% reporting (601 of 601 precincts)

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{See
Full Race Results~ ›}

Democrats were eager to unseat the two-term Republican incumbent, John
Katko, in a district running from Syracuse to the west and southwest
that is seen as leaning slightly Democratic. But Mr. Katko prevailed
over the Democratic challenger, Dana Balter, a visiting professor at
Syracuse University.

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-24}{See
Full Race Results~ ›}

\hypertarget{us-house-district-27-}{%
\paragraph{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{U.S.
House District 27
›}}{U.S. House District 27 ›}}\label{us-house-district-27-}}

Candidate

Party

Votes

Pct.

 Collins* Chris Collins*

Republican Rep.

140,146

49.1\%

 McMurray Nate McMurray

Democrat Dem.

139,059

48.8\%

 Piegza Larry Piegza

Reform Reform

5,973

2.1\%

285,178 votes, 100\% reporting (603 of 603 precincts)

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{See
Full Race Results~ ›}

The race in a deep red district in Western New York, which President
Trump won by 25 percentage points, was thrown into disarray in August
when the Republican incumbent, Chris Collins, was charged with insider
trading. At first he said he would withdraw from the race, but he
resumed campaigning in mid-September, and polls suggest a close contest
with Nate McMurray, the Democratic town supervisor of Grand Island. Both
candidates are white, but the race took on a racial tinge when Mr.
Collins ran an attack ad showing Mr. McMurray, a lawyer who worked in
South Korea for a time, speaking Korean.

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-house-district-27}{See
Full Race Results~ ›}

\hypertarget{us-house-district-25-special-election}{%
\subsection{U.S. House District 25 Special
Election}\label{us-house-district-25-special-election}}

Candidate

Party

Votes

Pct.

 Morelle Joseph Morelle

Democrat Dem.

141,290

58.3\%

 Maxwell Jim Maxwell

Republican Rep.

101,085

41.7\%

242,375 votes, 100\% reporting (798 of 798 precincts)

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{See
Full Race Results~ ›}

\hypertarget{governor}{%
\subsection{Governor}\label{governor}}

Candidate

Party

Votes

Pct.

 Cuomo* Andrew M. Cuomo*

Democrat Dem.

3,635,340

59.6\%

 Molinaro Marc Molinaro

Republican Rep.

2,207,602

36.2\%

 Hawkins Howie Hawkins

Green Green

103,946

1.7\%

 Sharpe Larry Sharpe

Libertarian Lib.

95,033

1.6\%

 Miner Stephanie Miner

Independent Ind.

55,441

0.9\%

 Others Others

150,474

2.5\%

6,097,362 votes, 100\% reporting (15,598 of 15,598 precincts)

-- Show fewer candidates

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-governor}{See
Full Race Results~ ›}

\href{https://www.nytimes3xbfgragh.onion/elections/results/new-york-governor}{See
Full Race Results~ ›}

\hypertarget{results-map-1}{%
\paragraph{Results Map}\label{results-map-1}}

Vote share

Dem. 50 60 70

Rep. 50 60 70

Other 50 60 70

No results

County

Cuomo

Molinaro

Hawkins

Rpt.

Brooklyn

524,080

84,648

17,165

100\%

Suffolk

274,518

247,169

4,951

100\%

Manhattan

460,368

52,677

12,237

100\%

Queens

391,190

90,533

8,467

100\%

Nassau

281,730

204,399

4,067

100\%

Erie

174,766

150,679

6,108

100\%

Westchester

222,685

102,180

3,738

100\%

Bronx

260,556

23,079

2,828

100\%

Monroe

143,110

118,909

4,392

100\%

Onondaga

85,182

74,523

5,312

100\%

Staten Island

69,116

67,063

1,249

100\%

Orange

56,882

60,901

1,882

100\%

Albany

59,692

45,917

3,543

100\%

Dutchess

51,179

59,131

1,311

100\%

Rockland

54,436

44,020

1,157

100\%

Saratoga

37,133

52,337

2,095

100\%

Oneida

27,931

44,938

1,084

100\%

Ulster

41,400

33,509

1,944

100\%

Niagara

27,951

41,242

956

100\%

Broome

31,519

36,583

1,320

100\%

Rensselaer

23,633

32,362

1,802

100\%

Schenectady

23,961

27,474

1,379

100\%

Ontario

16,618

23,975

690

100\%

Chautauqua

15,447

25,823

461

100\%

Oswego

11,844

23,129

650

100\%

Putnam

16,556

20,914

458

100\%

Tompkins

24,325

8,859

1,627

100\%

Steuben

9,310

21,035

417

100\%

Saint Lawrence

11,376

18,632

538

100\%

Wayne

9,241

19,574

435

100\%

Jefferson

8,862

19,064

401

100\%

Chemung

10,191

17,294

354

100\%

Columbia

13,665

14,253

669

100\%

Cayuga

9,783

14,706

520

100\%

Clinton

11,485

13,227

391

100\%

Warren

9,815

14,745

642

100\%

Madison

9,006

14,616

510

100\%

Sullivan

10,486

12,991

379

100\%

Livingston

7,637

14,627

415

100\%

Cattaraugus

7,034

15,028

307

100\%

Herkimer

5,924

14,374

325

100\%

Otsego

8,151

11,592

422

100\%

Genesee

5,400

13,967

270

100\%

Washington

6,411

12,879

453

100\%

Greene

6,113

12,088

386

100\%

Tioga

5,978

11,045

259

100\%

Delaware

5,796

9,934

311

100\%

Fulton

4,080

11,901

203

100\%

Chenango

5,069

10,259

269

100\%

Cortland

6,383

7,953

291

100\%

Montgomery

4,384

10,153

210

100\%

Allegany

3,486

10,132

183

100\%

Franklin

5,472

7,007

236

100\%

Essex

6,489

6,705

240

100\%

Wyoming

2,612

9,997

131

100\%

Orleans

3,082

8,893

123

100\%

Schoharie

3,099

8,190

214

100\%

Seneca

4,164

6,408

209

100\%

Lewis

1,854

6,553

102

100\%

Yates

2,558

4,991

110

100\%

Schuyler

2,414

4,024

125

100\%

Hamilton

722

1,792

23

100\%

+ Show all counties -- Collapse counties

\hypertarget{attorney-general}{%
\subsection{Attorney General}\label{attorney-general}}

Candidate

Party

Votes

Pct.

 James Letitia James

Democrat Dem.

3,454,308

61.9\%

 Wofford Keith Wofford

Republican Rep.

1,993,687

35.7\%

 Sussman Michael Sussman

Green Green

66,960

1.2\%

 Garvey Christopher Garvey

Libertarian Lib.

41,085

0.7\%

 Sliwa Nancy Sliwa

Reform Reform

24,672

0.4\%

 Others Others

65,757

1.2\%

5,580,712 votes, 99\% reporting (15,519 of 15,598 precincts)

-- Show fewer candidates

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\hypertarget{results-map-2}{%
\paragraph{Results Map}\label{results-map-2}}

Vote share

Dem. 50 60 70

Rep. 50 60 70

Other 50 60 70

No results

County

James

Wofford

Sussman

Rpt.

Brooklyn

498,267

77,438

7,105

99\%

Suffolk

249,214

231,247

3,924

100\%

Manhattan

414,627

51,632

6,701

98\%

Nassau

257,498

199,104

3,621

100\%

Queens

363,194

83,914

5,220

99\%

Erie

159,414

146,536

3,422

100\%

Westchester

208,411

94,592

3,121

100\%

Monroe

145,685

109,586

2,986

100\%

Bronx

229,919

20,147

1,511

98\%

Onondaga

89,957

66,755

2,061

100\%

Staten Island

63,623

63,873

1,034

100\%

Orange

56,527

50,568

4,179

100\%

Albany

64,847

36,619

1,769

100\%

Dutchess

53,043

47,112

1,379

100\%

Rockland

53,525

35,988

1,242

100\%

Saratoga

40,755

44,424

1,162

100\%

Oneida

29,936

38,598

766

100\%

Ulster

40,392

26,793

1,860

100\%

Niagara

26,232

38,488

664

100\%

Broome

32,330

31,243

877

100\%

Rensselaer

27,020

26,043

980

100\%

Schenectady

26,432

22,655

670

100\%

Ontario

17,704

21,234

469

100\%

Chautauqua

14,524

24,288

357

100\%

Putnam

15,919

18,685

414

100\%

Oswego

13,313

20,464

391

100\%

Tompkins

24,070

8,192

691

100\%

Steuben

9,934

19,734

437

100\%

Wayne

10,366

17,693

331

100\%

Saint Lawrence

13,114

14,945

346

100\%

Jefferson

10,364

15,629

340

100\%

Chemung

10,461

15,005

367

100\%

Cayuga

10,651

13,463

322

100\%

Columbia

12,870

11,074

374

100\%

Madison

9,917

12,833

285

100\%

Livingston

8,899

13,788

301

100\%

Clinton

11,984

10,506

304

100\%

Cattaraugus

6,955

14,586

194

100\%

Warren

9,697

11,623

409

100\%

Sullivan

9,869

10,639

814

100\%

Montgomery

5,216

15,029

169

100\%

Genesee

5,544

13,143

211

100\%

Otsego

8,894

9,639

273

100\%

Herkimer

6,581

11,852

259

100\%

Washington

7,097

10,917

285

100\%

Greene

6,338

9,903

264

100\%

Tioga

6,104

9,606

188

100\%

Delaware

5,813

8,814

256

100\%

Fulton

4,800

9,845

169

100\%

Cortland

7,201

7,189

181

100\%

Chenango

5,397

8,985

203

100\%

Allegany

3,616

9,707

109

100\%

Wyoming

2,916

9,659

97

100\%

Franklin

6,126

5,868

152

100\%

Essex

5,918

5,852

186

100\%

Orleans

3,201

8,133

101

100\%

Schoharie

3,716

6,819

144

100\%

Lewis

2,380

5,336

80

100\%

Yates

2,654

4,286

93

100\%

Schuyler

2,609

3,816

121

100\%

Hamilton

728

1,553

19

100\%

Seneca

0

0

0

0\%

+ Show all counties -- Collapse counties

\hypertarget{state-senate}{%
\subsection{State Senate}\label{state-senate}}

Dem. 37 won 3 lead

Rep. 21 won 2 lead

Ind. 0 won 0 lead

Dem. 37 won 3 lead

Rep. 21 won 2 lead

Ind. 0 won 0 lead

District Dist.

Candidate

Rpt.

1

 58\%LaValle*~Rep.

 42\%Fischer~Dem.

100\%

2

 55\%Flanagan*~Rep.

 45\%Bradbury Cleary~Dem.

100\%

3

 51\%Martinez~Dem.

 49\%Murray~Rep.

100\%

4

 52\%Boyle*~Rep.

 48\%D'Amaro~Dem.

100\%

5

 54\%Gaughran~Dem.

 46\%Marcellino*~Rep.

100\%

6

 51\%Thomas~Dem.

 49\%Hannon*~Rep.

100\%

7

 55\%Kaplan~Dem.

 45\%Phillips*~Rep.

100\%

8

 55\%Brooks*~Dem.

 45\%Pravato~Rep.

100\%

9

 62\%Kaminsky*~Dem.

 38\%Becker~Rep.

100\%

10

 0\%Sanders*~Dem.

Uncontested

11

 54\%Liu~Dem.

 24\%Paladino~Rep.

99\%

12

 0\%Gianaris*~Dem.

Uncontested

13

 90\%Ramos~Dem.

 10\%Peralta~Indep.

100\%

14

 0\%Comrie*~Dem.

Uncontested

15

 64\%Addabbo*~Dem.

 36\%Sullivan~Rep.

100\%

16

 95\%Stavisky*~Dem.

 5\%Pazienza~Reform

99\%

17

 85\%Felder*~Dem.

 13\%Williams~W.F.

100\%

18

 0\%Salazar~Dem.

Uncontested

19

 90\%Persaud*~Dem.

 10\%Ferretti~Rep.

100\%

20

 93\%Myrie~Dem.

 7\%Hamilton~Indep.

100\%

21

 97\%Parker*~Dem.

 3\%Kelly~Con.

100\%

22

 51\%Gounardes~Dem.

 49\%Golden*~Rep.

100\%

23

 69\%Savino*~Dem.

 28\%Krainert~Rep.

100\%

24

 0\%Lanza*~Rep.

Uncontested

25

 0\%Montgomery*~Dem.

Uncontested

26

 88\%Kavanagh*~Dem.

 11\%Arias~Rep.

100\%

27

 0\%Hoylman*~Dem.

Uncontested

28

 82\%Krueger*~Dem.

 18\%Holmberg~Rep.

100\%

29

 93\%Serrano*~Dem.

 7\%Colon~Rep.

93\%

30

 0\%Benjamin*~Dem.

Uncontested

31

 89\%Jackson~Dem.

 6\%Crump~Rep.

98\%

32

 95\%Sepulveda~Dem.

 3\%Delices~Rep.

98\%

33

 95\%Rivera*~Dem.

 4\%Torres~Rep.

100\%

34

 76\%Biaggi~Dem.

 15\%Ribustello~Rep.

98\%

35

 0\%Stewart-Cousins*~Dem.

Uncontested

36

 98\%Bailey*~Dem.

 2\%Diamond~Con.

99\%

37

 0\%Mayer*~Dem.

Uncontested

38

 65\%Carlucci*~Dem.

 35\%Vanderhoef~Rep.

100\%

39

 54\%Skoufis~Dem.

 46\%Basile~Rep.

100\%

40

 51\%Harckham~Dem.

 49\%Murphy*~Rep.

100\%

41

 51\%Serino*~Rep.

 49\%Smythe~Dem.

100\%

42

 51\%Metzger~Dem.

 49\%Rabbitt~Rep.

100\%

43

 54\%Jordan~Rep.

 46\%Gladd~Dem.

100\%

44

 70\%Breslin*~Dem.

 30\%Davis~Rep.

100\%

45

 65\%Little*~Rep.

 36\%Martz~Dem.

100\%

46

 57\%Amedore*~Rep.

 43\%Strong~Dem.

100\%

47

 0\%Griffo*~Rep.

Uncontested

48

 0\%Ritchie*~Rep.

Uncontested

49

 60\%Tedisco*~Rep.

 41\%Ostrelich~Dem.

100\%

50

 51\%Antonacci~Rep.

 49\%Mannion~Dem.

100\%

51

 64\%Seward*~Rep.

 36\%St. George~Dem.

100\%

52

 0\%Akshar*~Rep.

Uncontested

53

 51\%May~Dem.

 37\%Burman~Rep.

100\%

54

 62\%Helming*~Rep.

 38\%Baldridge~Dem.

88\%

55

 52\%Funke*~Rep.

 48\%Lunsford~Dem.

100\%

56

 56\%Robach*~Rep.

 44\%Cooney~Dem.

100\%

57

 0\%Young*~Rep.

Uncontested

58

 60\%O'Mara*~Rep.

 40\%Kirchgessner~Dem.

100\%

59

 0\%Gallivan*~Rep.

Uncontested

60

 56\%Jacobs*~Rep.

 44\%El Behairy~Dem.

100\%

61

 55\%Ranzenhofer*~Rep.

 46\%Seamans~Dem.

100\%

62

 87\%Ortt*~Rep.

 13\%Diachun~Green

100\%

63

 0\%Kennedy*~Dem.

Uncontested

+ Show all 63 races -- Show fewer races

* Incumbent~

\hypertarget{state-assembly}{%
\subsection{State Assembly}\label{state-assembly}}

Dem. 107 won 0 lead

Rep. 42 won 1 lead

Ind. 0 won 0 lead

Dem. 107 won 0 lead

Rep. 42 won 1 lead

Ind. 0 won 0 lead

District Dist.

Candidate

Rpt.

1

 60\%Thiele*~Dem.

 40\%O'Connor~Rep.

100\%

2

 60\%Palumbo*~Rep.

 40\%Smith~Dem.

100\%

3

 55\%De Stefano~Rep.

 46\%Parker~Dem.

100\%

4

 60\%Englebright*~Dem.

 40\%Kalinowski~Rep.

100\%

5

 59\%Smith*~Rep.

 41\%Hall~Dem.

100\%

6

 0\%Ramos*~Dem.

Uncontested

7

 59\%Garbarino*~Rep.

 41\%Murray~Dem.

100\%

8

 61\%Fitzpatrick*~Rep.

 39\%Morrissey~Dem.

100\%

9

 56\%LiPetri~Rep.

 44\%Pellegrino*~Dem.

100\%

10

 60\%Stern*~Dem.

 41\%Williams~Rep.

100\%

11

 64\%Jean-Pierre*~Dem.

 36\%Sabella~Rep.

100\%

12

 56\%Raia*~Rep.

 44\%Rosen~Dem.

100\%

13

 68\%Lavine*~Dem.

 32\%Monteleone~Rep.

100\%

14

 56\%McDonough*~Rep.

 44\%Reid~Dem.

100\%

15

 53\%Montesano*~Rep.

 47\%Foley~Dem.

100\%

16

 62\%D'Urso*~Dem.

 38\%Divins~Rep.

100\%

17

 56\%Mikulin*~Rep.

 44\%Snow~Dem.

100\%

18

 90\%Raynor~Dem.

 10\%Lamarre~Rep.

100\%

19

 56\%Ra*~Rep.

 44\%Carr~Dem.

100\%

20

 54\%Miller*~Rep.

 45\%Vides~Dem.

100\%

21

 53\%Griffin~Dem.

 47\%Curran*~Rep.

100\%

22

 70\%Solages*~Dem.

 30\%Moncion~Rep.

100\%

23

 68\%Pheffer Amato*~Dem.

 32\%Pecorino~Rep.

100\%

24

 0\%Weprin*~Dem.

Uncontested

25

 0\%Rozic*~Dem.

Uncontested

26

 65\%Braunstein*~Dem.

 35\%Bressler~Rep.

100\%

27

 0\%Rosenthal*~Dem.

Uncontested

28

 73\%Hevesi*~Dem.

 27\%Maio~Rep.

100\%

29

 0\%Hyndman*~Dem.

Uncontested

30

 76\%Barnwell*~Dem.

 24\%Butkiewicz~Rep.

100\%

31

 0\%Titus*~Dem.

Uncontested

32

 0\%Cook*~Dem.

Uncontested

33

 92\%Vanel*~Dem.

 8\%Etwaroo~Rep.

100\%

34

 0\%DenDekker*~Dem.

Uncontested

35

 0\%Aubry*~Dem.

Uncontested

36

 0\%Simotas*~Dem.

Uncontested

37

 0\%Nolan*~Dem.

Uncontested

38

 0\%Miller*~Dem.

Uncontested

39

 88\%Cruz~Dem.

 10\%Espinal~W.E.

100\%

40

 87\%Kim*~Dem.

 13\%Scandalios~Reform

95\%

41

 0\%Weinstein*~Dem.

Uncontested

42

 91\%Bichotte*~Dem.

 7\%Williams~Rep.

100\%

43

 0\%Richardson*~Dem.

Uncontested

44

 86\%Carroll*~Dem.

 14\%Goldberg~Rep.

100\%

45

 0\%Cymbrowitz*~Dem.

Uncontested

46

 54\%Frontus~Dem.

 43\%Saperstein~Rep.

100\%

47

 70\%Colton*~Dem.

 31\%LaSalle~Rep.

100\%

48

 0\%Eichenstein~Dem.

Uncontested

49

 85\%Abbate*~Dem.

 16\%Mangino~Con.

100\%

50

 0\%Lentol*~Dem.

Uncontested

51

 0\%Ortiz*~Dem.

Uncontested

52

 95\%Simon*~Dem.

 3\%Ramos~Con.

100\%

53

 0\%Davila*~Dem.

Uncontested

54

 96\%Dilan*~Dem.

 4\%Chowdhury~Rep.

99\%

55

 98\%Walker*~Dem.

 2\%Jackson~Rep.

100\%

56

 0\%Wright*~Dem.

Uncontested

57

 0\%Mosley*~Dem.

Uncontested

58

 0\%Perry*~Dem.

Uncontested

59

 81\%Williams*~Dem.

 19\%Washington~Rep.

100\%

60

 96\%Barron*~Dem.

 3\%Bates~Rep.

100\%

61

 84\%Fall~Dem.

 10\%Kane~W.F.

100\%

62

 90\%Reilly~Rep.

 10\%Yost~Reform

100\%

63

 96\%Cusick*~Dem.

 4\%Dennie~Green

100\%

64

 61\%Malliotakis*~Rep.

 39\%Baumel~Dem.

100\%

65

 0\%Niou*~Dem.

Uncontested

66

 82\%Glick*~Dem.

 18\%Nixon~W.F.

100\%

67

 0\%Rosenthal*~Dem.

Uncontested

68

 93\%Rodriguez*~Dem.

 7\%Carreras~Rep.

100\%

69

 93\%O'Donnell*~Dem.

 7\%Cotenescu~Rep.

100\%

70

 0\%Dickens*~Dem.

Uncontested

71

 0\%Taylor*~Dem.

Uncontested

72

 94\%De La Rosa*~Dem.

 6\%Goodman~Rep.

100\%

73

 76\%Quart*~Dem.

 24\%Ascherman~Rep.

100\%

74

 87\%Epstein*~Dem.

 11\%Cooper~Rep.

97\%

75

 0\%Gottfried*~Dem.

Uncontested

76

 97\%Seawright*~Dem.

 4\%Puliafito~Reform

100\%

77

 97\%Joyner*~Dem.

 3\%Carmichael~Rep.

100\%

78

 94\%Rivera*~Dem.

 7\%Walters~Rep.

100\%

79

 97\%Blake*~Dem.

 3\%Torres~Rep.

100\%

80

 86\%Fernandez*~Dem.

 14\%Perri~Rep.

97\%

81

 88\%Dinowitz*~Dem.

 12\%Reed~Rep.

97\%

82

 82\%Benedetto*~Dem.

 16\%English~Rep.

98\%

83

 97\%Heastie*~Dem.

 2\%Lee~Rep.

100\%

84

 90\%Arroyo*~Dem.

 6\%Septimo~W.F.

93\%

85

 96\%Crespo*~Dem.

 4\%Lennon~Rep.

100\%

86

 96\%Pichardo*~Dem.

 4\%Rivera-Diaz~Rep.

100\%

87

 94\%Reyes~Dem.

 5\%Marcus~Rep.

95\%

88

 0\%Paulin*~Dem.

Uncontested

89

 0\%Pretlow*~Dem.

Uncontested

90

 65\%Sayegh~Dem.

 35\%Pinion~Rep.

100\%

91

 0\%Otis*~Dem.

Uncontested

92

 0\%Abinanti*~Dem.

Uncontested

93

 69\%Buchwald*~Dem.

 31\%Nuculovic~Rep.

100\%

94

 58\%Byrne*~Rep.

 42\%Gashi~Dem.

100\%

95

 68\%Galef*~Dem.

 32\%Chiulli~Rep.

100\%

96

 0\%Zebrowski*~Dem.

Uncontested

97

 62\%Jaffee*~Dem.

 38\%Presti~Rep.

81\%

98

 63\%Brabenec*~Rep.

 37\%Martens~Dem.

93\%

99

 53\%Schmitt~Rep.

 47\%Rettig~Dem.

100\%

100

 0\%Gunther*~Dem.

Uncontested

101

 59\%Miller*~Rep.

 41\%McEvoy~Dem.

100\%

102

 57\%Tague*~Rep.

 43\%O'Connor~Dem.

100\%

103

 0\%Cahill*~Dem.

Uncontested

104

 60\%Jacobson~Dem.

 40\%Manley~Rep.

100\%

105

 58\%Lalor*~Rep.

 42\%Giardino~Dem.

100\%

106

 54\%Barrett*~Dem.

 46\%Truitt~Rep.

100\%

107

 52\%Ashby*~Rep.

 49\%Houghtling~Dem.

100\%

108

 0\%McDonald*~Dem.

Uncontested

109

 71\%Fahy*~Dem.

 24\%Porter~Rep.

100\%

110

 60\%Steck*~Dem.

 40\%Carey~Rep.

100\%

111

 54\%Santabarbara*~Dem.

 46\%McGarry~Rep.

100\%

112

 0\%Walsh*~Rep.

Uncontested

113

 57\%Woerner*~Dem.

 44\%Zegers~Rep.

100\%

114

 81\%Stec*~Rep.

 19\%Wilson~W.F.

100\%

115

 0\%Jones*~Dem.

Uncontested

116

 54\%Walczyk~Rep.

 46\%Jenne*~Dem.

100\%

117

 0\%Blankenbush*~Rep.

Uncontested

118

 64\%Smullen~Rep.

 36\%Rubino~Dem.

100\%

119

 55\%Buttenschon~Dem.

 45\%Bova~Rep.

100\%

120

 69\%Barclay*~Rep.

 31\%Tosh~Dem.

100\%

121

 51\%Salka~Rep.

 49\%Magee*~Dem.

100\%

122

 85\%Crouch*~Rep.

 15\%Libous~Con.

100\%

123

 0\%Lupardo*~Dem.

Uncontested

124

 63\%Friend*~Rep.

 38\%Batrowny~Dem.

100\%

125

 0\%Lifton*~Dem.

Uncontested

126

 57\%Finch*~Rep.

 43\%Batman~Dem.

100\%

127

 58\%Stirpe*~Dem.

 42\%Paro~Rep.

100\%

128

 0\%Hunter*~Dem.

Uncontested

129

 74\%Magnarelli*~Dem.

 22\%Ott~Rep.

100\%

130

 67\%Manktelow~Rep.

 33\%Comegys~Dem.

100\%

131

 0\%Kolb*~Rep.

Uncontested

132

 0\%Palmesano*~Rep.

Uncontested

133

 55\%Byrnes~Rep.

 42\%Baer~Dem.

100\%

134

 0\%Lawrence*~Rep.

Uncontested

135

 53\%Johns*~Rep.

 48\%Gilchrist~Dem.

100\%

136

 0\%Romeo~Dem.

Uncontested

137

 0\%Gantt*~Dem.

Uncontested

138

 66\%Bronson*~Dem.

 34\%Iacovangelo~Rep.

100\%

139

 92\%Hawley*~Rep.

 8\%Glogowski~Lib.

100\%

140

 70\%Schimminger*~Dem.

 26\%Ohar~Rep.

100\%

141

 91\%Peoples*~Dem.

 10\%Kostecky~Rep.

100\%

142

 52\%Burke~Dem.

 46\%Bohen*~Rep.

100\%

143

 58\%Wallace*~Dem.

 42\%Centinello~Rep.

100\%

144

 63\%Norris*~Rep.

 37\%DiPasquale~Dem.

100\%

145

 0\%Morinello*~Rep.

Uncontested

146

 53\%McMahon~Dem.

 47\%Walter*~Rep.

100\%

147

 61\%DiPietro*~Rep.

 39\%Wochensky~Dem.

100\%

148

 0\%Giglio*~Rep.

Uncontested

149

 72\%Ryan*~Dem.

 28\%Totaro~Rep.

100\%

150

 69\%Goodell*~Rep.

 31\%Einach~Dem.

100\%

+ Show all 150 races -- Show fewer races

* Incumbent~

\hypertarget{ballot-measures}{%
\subsection{Ballot Measures}\label{ballot-measures}}

\hypertarget{question-1campaign-finance}{%
\subsubsection{Question 1Campaign
Finance}\label{question-1campaign-finance}}

Answer

Votes

Pct.

 Yes Yes

1,151,775

80.3\%

 No No

283,435

19.7\%

1,435,210 votes, 99\% reporting (5,849 of 5,901 precincts)

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\hypertarget{question-2create-civic-engagement-commission}{%
\subsubsection{Question 2Create Civic Engagement
Commission}\label{question-2create-civic-engagement-commission}}

Answer

Votes

Pct.

 Yes Yes

928,382

65.5\%

 No No

488,377

34.5\%

1,416,759 votes, 99\% reporting (5,849 of 5,901 precincts)

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\hypertarget{question-3limit-terms-of-community-board-members}{%
\subsubsection{Question 3Limit Terms of Community Board
Members}\label{question-3limit-terms-of-community-board-members}}

Answer

Votes

Pct.

 Yes Yes

1,026,929

72.3\%

 No No

393,809

27.7\%

1,420,738 votes, 99\% reporting (5,849 of 5,901 precincts)

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\hypertarget{comptroller}{%
\subsection{Comptroller}\label{comptroller}}

Candidate

Party

Votes

Pct.

 DiNapoli* Thomas DiNapoli*

Democrat Dem.

3,727,418

66.6\%

 Trichter Jonathan Trichter

Republican Rep.

1,773,570

31.7\%

 Dunlea Mark Dunlea

Green Green

63,892

1.1\%

 Gallaudet Cruger Gallaudet

Libertarian Lib.

32,366

0.6\%

5,597,246 votes, 99\% reporting (15,519 of 15,598 precincts)

* Incumbent

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{Full
New York Results ›}

\hypertarget{supreme-court}{%
\subsection{Supreme Court}\label{supreme-court}}

District Dist.

Candidate

Rpt.

1

 0\%Tisch~Dem.

~

0\%

~

 0\%Kotler~Dem.

~

~

~

 0\%Rosado~Dem.

~

~

2

 14\%Hinds-Radix~Rep.

 14\%Joseph~Dem.

99\%

3

 38\%Walsh~Dem.

 33\%Lynch~Dem.

100\%

5

 14\%Neri~Rep.

 14\%DelConte~Dem.

100\%

6

 51\%McBride~Rep.

 49\%Burns~Dem.

100\%

7

 27\%Taddeo~Rep.

 27\%Argento~Rep.

98\%

8

 0\%Feroleto~Dem.

~

0\%

~

 0\%Curran~Dem.

~

~

9

 17\%Davidson~Dem.

 12\%Zugibe~Dem.

97\%

10

 13\%Voutsinas~Dem.

 13\%Balkin~Dem.

100\%

11

 22\%Nelson~Dem.

 20\%Love~Dem.

99\%

12

 13\%Torres~Dem.

 12\%Rodriguez~Dem.

98\%

13

 51\%Mundy~Rep.

 38\%Porzio~Rep.

100\%

+ Show all races -- Show fewer races

Source: Election results and race calls from The Associated Press

By Sarah Almukhtar, Mike Andre, Wilson Andrews, Matthew Bloch, Jeremy
Bowers, Larry Buchanan, Nate Cohn, Alastair Coote, Annie Daniel, Tiff
Fehr, Samuel Jacoby, Josh Katz, Josh Keller, Aaron Krolik, Jasmine C.
Lee, Rebecca Lieberman, Blacki Migliozzi, Paul Murray, Kevin Quealy,
Jaymin Patel, Adam Pearce, Rachel Shorey, Michael Strickland, Rumsey
Taylor, Isaac White, Maxine Whitely, and Josh Williams.

Alan Blinder, Lauretta Charlton, Emily Cochrane, Catie Edmondson,
Elisabeth Goodridge, Pat Lyons, John Schwartz, Mitch Smith, Liam Stack
and Jamie Stockwell contributed reporting.

\hypertarget{state-results}{%
\subsubsection{State Results}\label{state-results}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-alabama-elections.html}{Alabama}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-alaska-elections.html}{Alaska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-arizona-elections.html}{Arizona}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-arkansas-elections.html}{Arkansas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-california-elections.html}{California}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-colorado-elections.html}{Colorado}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-connecticut-elections.html}{Connecticut}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-delaware-elections.html}{Delaware}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-district-of-columbia-elections.html}{District
  of Columbia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-florida-elections.html}{Florida}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-georgia-elections.html}{Georgia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-hawaii-elections.html}{Hawaii}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-idaho-elections.html}{Idaho}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-illinois-elections.html}{Illinois}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-indiana-elections.html}{Indiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-iowa-elections.html}{Iowa}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-kansas-elections.html}{Kansas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-kentucky-elections.html}{Kentucky}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-louisiana-elections.html}{Louisiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-maine-elections.html}{Maine}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-maryland-elections.html}{Maryland}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-massachusetts-elections.html}{Massachusetts}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-michigan-elections.html}{Michigan}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-minnesota-elections.html}{Minnesota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-mississippi-elections.html}{Mississippi}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-missouri-elections.html}{Missouri}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-montana-elections.html}{Montana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-north-dakota-elections.html}{North
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-nebraska-elections.html}{Nebraska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-nevada-elections.html}{Nevada}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-hampshire-elections.html}{New
  Hampshire}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-jersey-elections.html}{New
  Jersey}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-mexico-elections.html}{New
  Mexico}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{New
  York}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-north-carolina-elections.html}{North
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-ohio-elections.html}{Ohio}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-oklahoma-elections.html}{Oklahoma}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-oregon-elections.html}{Oregon}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-pennsylvania-elections.html}{Pennsylvania}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-rhode-island-elections.html}{Rhode
  Island}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-south-carolina-elections.html}{South
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-south-dakota-elections.html}{South
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-tennessee-elections.html}{Tennessee}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-texas-elections.html}{Texas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-utah-elections.html}{Utah}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-vermont-elections.html}{Vermont}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-virginia-elections.html}{Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-washington-elections.html}{Washington}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-west-virginia-elections.html}{West
  Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-wisconsin-elections.html}{Wisconsin}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-wyoming-elections.html}{Wyoming}
\end{itemize}

\hypertarget{state-results-1}{%
\subsubsection{State Results}\label{state-results-1}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-alabama-elections.html}{Alabama}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-alaska-elections.html}{Alaska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-arizona-elections.html}{Arizona}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-arkansas-elections.html}{Arkansas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-california-elections.html}{California}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-colorado-elections.html}{Colorado}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-connecticut-elections.html}{Connecticut}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-delaware-elections.html}{Delaware}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-district-of-columbia-elections.html}{District
  of Columbia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-florida-elections.html}{Florida}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-georgia-elections.html}{Georgia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-hawaii-elections.html}{Hawaii}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-idaho-elections.html}{Idaho}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-illinois-elections.html}{Illinois}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-indiana-elections.html}{Indiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-iowa-elections.html}{Iowa}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-kansas-elections.html}{Kansas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-kentucky-elections.html}{Kentucky}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-louisiana-elections.html}{Louisiana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-maine-elections.html}{Maine}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-maryland-elections.html}{Maryland}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-massachusetts-elections.html}{Massachusetts}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-michigan-elections.html}{Michigan}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-minnesota-elections.html}{Minnesota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-mississippi-elections.html}{Mississippi}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-missouri-elections.html}{Missouri}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-montana-elections.html}{Montana}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-north-dakota-elections.html}{North
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-nebraska-elections.html}{Nebraska}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-nevada-elections.html}{Nevada}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-hampshire-elections.html}{New
  Hampshire}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-jersey-elections.html}{New
  Jersey}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-mexico-elections.html}{New
  Mexico}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-new-york-elections.html}{New
  York}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-north-carolina-elections.html}{North
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-ohio-elections.html}{Ohio}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-oklahoma-elections.html}{Oklahoma}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-oregon-elections.html}{Oregon}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-pennsylvania-elections.html}{Pennsylvania}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-rhode-island-elections.html}{Rhode
  Island}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-south-carolina-elections.html}{South
  Carolina}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-south-dakota-elections.html}{South
  Dakota}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-tennessee-elections.html}{Tennessee}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-texas-elections.html}{Texas}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-utah-elections.html}{Utah}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-vermont-elections.html}{Vermont}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-virginia-elections.html}{Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-washington-elections.html}{Washington}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-west-virginia-elections.html}{West
  Virginia}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-wisconsin-elections.html}{Wisconsin}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-wyoming-elections.html}{Wyoming}
\end{itemize}

\hypertarget{see-election-results-for}{%
\subsubsection{See election results
for}\label{see-election-results-for}}

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{2018
›}
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/us/elections/election-calendar.html}{2017
›}
\href{https://www.nytimes3xbfgragh.onion/elections/results/president}{2016
›}
\href{https://www.nytimes3xbfgragh.onion/elections/2014/results/senate}{2014
›}
\href{https://www.nytimes3xbfgragh.onion/elections/2012/results/president.html}{2012
›}
\href{https://www.nytimes3xbfgragh.onion/elections/2010/results/senate.html}{2010
›}
\href{https://www.nytimes3xbfgragh.onion/elections/2008/results/president/map.html}{2008
›}

\hypertarget{more-on-nytimescom}{%
\subsubsection{More on NYTimes.com}\label{more-on-nytimescom}}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2019 The New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2019 The New York Times Company}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/infoservdirectory.html}{Contact
  Us}
\item
  \href{http://www.nytco.com/careers}{Work With Us}
\item
  \href{http://www.nytimes.whsites.net/mediakit}{Advertise}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/privacy/policy/privacy-policy.html\#pp}{Your
  Ad Choices}
\item
  \href{http://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/agree.html}{Terms
  of Service}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/sale/terms-of-sale.html}{Terms
  of Sale}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{http://www.nytimes3xbfgragh.onion/membercenter/sitehelp.html}{Help}
\item
  \href{https://myaccount.nytimes3xbfgragh.onion/membercenter/feedback.html}{Site
  Feedback}
\item
  \href{http://www.nytimes3xbfgragh.onion/subscriptions/Multiproduct/lp5558.html?campaignId=37WXW}{Subscriptions}
\end{itemize}
