Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/upshot}{The Upshot}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/upshot}{The Upshot}\textbar{}How Dr. Fauci Found Himself
Talking to Julia Roberts, Lil Wayne and Just About Any Podcaster Who
Asked

\url{https://nyti.ms/3lvcb79}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{the-coronavirus-outbreak}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=caee8ed0-f4d3-11ea-b0c3-9b7cad4a02b8\&variant=undefined}{The
Coronavirus
Outbreak}}{The Coronavirus Outbreak}}\label{the-coronavirus-outbreak}}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes3xbfgragh.onion/2020/09/11/world/covid-19-coronavirus.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=caee8ed1-f4d3-11ea-b0c3-9b7cad4a02b8\&variant=undefined}{Latest
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/coronavirus-us-cases.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=caeeb5e0-f4d3-11ea-b0c3-9b7cad4a02b8\&variant=undefined}{Maps
  and Cases}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/science/coronavirus-vaccine-tracker.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=caeeb5e1-f4d3-11ea-b0c3-9b7cad4a02b8\&variant=undefined}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/10/us/politics/fda-coronavirus-vaccine.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=caeeb5e2-f4d3-11ea-b0c3-9b7cad4a02b8\&variant=undefined}{F.D.A.
  Regulators' Self-Defense}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/09/upshot/coronavirus-surprise-test-fees.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=caeeb5e3-f4d3-11ea-b0c3-9b7cad4a02b8\&variant=undefined}{Surprise
  Test Fees}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{How Dr. Fauci Found Himself Talking to Julia Roberts, Lil Wayne
and Just About Any Podcaster Who Asked}\href{}{Skip to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@NYTimes.com}{\nolinkurl{letters@NYTimes.com}}.

Upshot

\hypertarget{how-dr-fauci-found-himself-talking-to-julia-roberts-lil-wayne-and-just-about-any-podcaster-who-asked}{%
\section{How Dr. Fauci Found Himself Talking to Julia Roberts, Lil Wayne
and Just About Any Podcaster Who
Asked}\label{how-dr-fauci-found-himself-talking-to-julia-roberts-lil-wayne-and-just-about-any-podcaster-who-asked}}

By \href{https://www.nytimes3xbfgragh.onion/by/quoctrung-bui}{Quoctrung
Bui},
\href{https://www.nytimes3xbfgragh.onion/by/margot-sanger-katz}{Margot
Sanger-Katz},
\href{https://www.nytimes3xbfgragh.onion/by/sheryl-gay-stolberg}{Sheryl
Gay Stolberg},
\href{https://www.nytimes3xbfgragh.onion/by/noah-weiland}{Noah Weiland}
and Kitty BennettAug. 27, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{188}
\end{itemize}

On March 15, as the novel coronavirus was beginning to surge in the
United States, Dr. Anthony S. Fauci accomplished a rare Washington feat:
He appeared on all five major Sunday talk shows.

But the
\href{https://www.nytimes3xbfgragh.onion/2020/03/23/us/politics/coronavirus-trump-fauci.html}{White
House worried}that Dr. Fauci might upstage (and sometimes contradict)
President Trump, and soon his media handlers were no longer approving
his high-profile interview requests.

So Dr. Fauci found another way to get his message out: He said yes to
pretty much every small offer that came his way: academic webinars,
Instagram feeds and niche science podcasts, as well as a few celebrity
interviews.

That's how Dr. Fauci, the country's leading infectious disease
scientist, found himself talking to the
\href{http://auanet.mediaroom.com/2020-06-11-Anthony-S-Fauci-MD-to-Deliver-Keynote-Address-During-the-2020-American-Urological-Association-Virtual-Experience}{A}\href{http://auanet.mediaroom.com/2020-06-11-Anthony-S-Fauci-MD-to-Deliver-Keynote-Address-During-the-2020-American-Urological-Association-Virtual-Experience}{merican
Urological Association} in June; the
\href{https://www.youtube.com/watch?v=ybZjaINKZ-8}{Economic Club of
Chicago} in July; and the
``\href{https://www.youtube.com/watch?v=mnEe4hdE7yE}{Brazda Breakfast}''
briefing this month.

And it may be how he ended up with a polyp on his vocal cord.
``Essentially I was talking all day without interruption for six
months,'' he wrote in an email message on Friday, the day after he had
surgery to remove it.

\begin{itemize}
\item
\item
\item
\item
\item
\item
\item
\item
\item
\end{itemize}

Early in the pandemic, Dr. Fauci was a regular on the big Sunday shows.

3.8 million television viewers \textbar{} March 15, 2020

\href{https://www.nbcnews.com/meet-the-press/video/full-fauci-the-numbers-don-t-tell-us-yet-if-virus-spread-is-blunted-80680517562?cid=sm_npd_nn_tw_mtp}{``Meet
the Press,'' NBC}

By April, he was still doing cable shows.

3.4 million television viewers \textbar{} April 16, 2020

\href{https://video.foxnews.com/v/6150154055001\#sp=show-clips}{``The
Ingraham Angle,'' Fox News}

Slowly, he began appearing at a wider array of venues, like the Economic
Club of Washington ...

9,000 YouTube views \textbar{} April 28, 2020

\href{https://www.youtube.com/watch?time_continue=5\&v=u7QlGYkqnOs\&feature=emb_logo}{Economic
Club of Washington}

\ldots{} and an Instagram chat with Julia Roberts, for the public health
nonprofit the ONE Campaign \ldots{}

355,187 Instagram views \textbar{} May 20, 2020

\href{https://www.instagram.com/p/CAdEZzBAvzf/}{Julia Roberts's
Instagram}

\ldots{} and a podcast hosted by the hip-hop star Lil Wayne.

87,500 YouTube views \textbar{} May 29, 2020

\href{https://twitter.com/LilTunechi/status/1266895927127805952}{Lil
Wayne's ``Young Money Radio''}

By the start of the summer, his news appearances had shrunk. Instead, he
spoke with journal editors ...

72,000 YouTube views \textbar{} June 2, 2020

``\href{https://www.youtube.com/watch?time_continue=20\&v=3MH-3ICY-N4\&feature=emb_logo}{Conversations
with Dr. Bauchner,'' JAMA Network}

... science podcasters ...

36,000 YouTube views \textbar{} July 17, 2020

``\href{https://bit.ly/3fznojs}{This Week in Virology}''

\ldots{} and on online education platforms.

38,000 YouTube views \textbar{} July 24, 2020

\href{https://www.youtube.com/watch?v=asVN55SS9T0}{Khan Academy}

By August, the vast majority of his public appearances were on small
media platforms, like this Instagram Live interview with Matthew
McConaughey.

1.2 million Instagram Live views \textbar{} Aug. 14, 2020

\href{https://www.instagram.com/p/CD2WoXupHV-/}{Matthew
McConaughey's}\href{https://www.instagram.com/p/CD2WoXupHV-/}{Instagram}

The coronavirus pandemic has turned Dr. Fauci, a career government
scientist first propelled into public view in the early years of the
AIDS epidemic, into a genuine celebrity. There is now all manner of
Fauci swag --- Fauci socks, T-shirts, coffee mugs, buttons, stickers and
masks. When the National Bobblehead Hall of Fame made a
\href{https://store.bobbleheadhall.com/collections/featured-product/products/drfauci}{doll
in his likeness}, it ``quickly became our best-selling bobblehead of all
time,'' said Phil Sklar, the group's chief executive officer.

That renown has pushed him into the higher echelons of media interest.
Most people need a slot on a major show to have a better chance of
reaching a huge audience. But reporters track all of Dr. Fauci's
appearances, however obscure.

``He can talk anywhere, and if he has something he wants to say, people
will notice it,'' said Brendan Buck, who was the communications director
for former House Speaker Paul Ryan, another man who could make news even
in obscure places. Dr. Fauci, he said, ``could talk to a P.T.A.
newsletter if he wanted to, and it would be covered, and there would be
follow-on eyes for it.''

Asked about his rules for media appearances, Dr. Fauci said (by email)
he frequently says yes. His only automatic nos are for fund-raisers or
``anything remotely political.''

Whether by design or not, Dr. Fauci has effectively circumvented efforts
by the White House to mute him. Since Mark Meadows took over as chief of
staff on March 31, White House communications officials have approved
very few requests from major outlets. But there is no such review
process for smaller ones, like the weekly podcast of the Journal of the
American Medical Association, or the KC O'Dea radio show.

In recent weeks, Dr. Fauci has been joining as many as five such shows a
day. On Aug. 13, he
\href{https://www.iheart.com/podcast/53-kcodearadioprogram-28305929/episode/dr-fauci-joins-kc-odea-70194725/}{appeared
on Mr. O'Dea's show}, which serves the Raleigh-Durham, N.C., market; a
podcast affiliated with the
\href{https://www.facebookcorewwwi.onion/watch/live/?v=296749178247753\&ref=watch_permalink}{Walter
Reed National Military Medical Center};
``\href{https://wbt.radio.com/blogs/the-pat-mccrory-show-w-bo-thompson/dr-fauci-never-seen-a-virus-with-such-a-broad-range}{The
Pat McCrory Show with Bo Thompson}''; a
\href{https://stoppingpandemics.com/}{National Geographic specia}l on
pandemics; and
\href{https://myfox8.com/news/coronavirus/dr-anthony-fauci-breaks-down-what-north-carolinians-need-to-know-about-schools-vaccine-progress-in-fox8-interview/}{a
local Fox affiliate} in High Point, N.C. He also appeared on
``\href{https://www.pbs.org/newshour/show/fauci-says-despite-upcoming-election-science-will-not-be-politicized}{NewsHour},''
the PBS evening news show.

His appearances are widely watched by reporters from larger outlets, who
then quote him in their news reports.

\hypertarget{dr-faucis-major-media-appearances-have-fallen-over-the-last-three-months}{%
\subsubsection{Dr. Fauci's major media appearances have fallen over the
last three
months}\label{dr-faucis-major-media-appearances-have-fallen-over-the-last-three-months}}

14 appearances

At the beginning of the pandemic, Dr. Fauci was a regular on the major
news broadcasts.

12

10

8

Sunday show

6

Now his appearances are more rare.

4

2

March 1

April 5

May 10

June 14

July 19

14 appearances

At the beginning of the pandemic, Dr. Fauci was a regular major news
broadcasts.

12

10

8

Sunday show

6

Now his appearances are more rare.

4

2

March 1

April 5

May 10

June 14

July 19

14 appearances

12

10

8

6

Sunday show

4

2

March 1

April 5

May 10

June 14

July 19

\hypertarget{meanwhile-his-appearances-on-smaller-platforms-have-grown-significantly}{%
\subsubsection{Meanwhile, his appearances on smaller platforms have
grown
significantly}\label{meanwhile-his-appearances-on-smaller-platforms-have-grown-significantly}}

14 appearances

Dr. Fauci undergoes surgery on his vocal cords

12

10

8

6

4

2

March 1

April 5

May 10

June 14

July 19

14 appearances

Dr. Fauci undergoes surgery on his vocal cords

12

10

8

6

4

2

March 1

April 5

May 10

June 14

July 19

14 appearances

12

10

8

6

4

2

March 1

April 5

May 10

June 14

July 19

Note: ``Major'' appearances include the Sunday news shows, network news,
cable news in prime time, and radio broadcasts with a national audience.
Source:
\href{https://www.niaid.nih.gov/news-events/director-in-the-news}{National
Institute of Allergy and Infectious Diseases}, and media database
searches.

Our charts track Dr. Fauci's broadcast appearances from March 1 to Aug.
20, the day of his operation. We included video and audio appearances
listed on Dr. Fauci's National Institutes of Health
\href{https://www.niaid.nih.gov/news-events/director-in-the-news}{web
page}, and others we uncovered through searches of news transcript
databases, social media and general web searches. Given the breadth of
Dr. Fauci's appearances, it is possible we missed a few.

Peter Staley, an H.I.V./AIDS activist who has been close to him for
years, said Dr. Fauci had always been a skilled public communicator,
able to promote public health messages through any available channel.

``He would prefer to go on Andrea Mitchell and Sanjay Gupta, but he has
marveled that this lower-level stuff kind of ends up the same way,'' Mr.
Staley said. ``He does the little Zoom with Harvard, and it's on CNN
that night.''

In July, Dr. Fauci
\href{https://www.facebookcorewwwi.onion/senatordougjones/videos/913960105743145}{appeared}
on a weekly video news conference that Senator Doug Jones, a Democrat
from Alabama, hosts for local media on his Facebook page. Dr. Fauci made
news when he directly contradicted Mr. Trump by saying it was a ``false
narrative to take comfort in a lower rate of death,'' comments that
rippled across the national media that day.

Dr. Fauci has rarely appeared on CNN's prime-time broadcasts, but he did
grant
\href{https://podcasts.apple.com/us/podcast/ep-396-dr-anthony-fauci/id1043593599?i=1000485884825}{an
hourlong interview} to ``The Axe Files,'' a CNN-backed podcast hosted by
David Axelrod, who was a top adviser to President Obama. ``Tony is the
personification of the nagging reality that science presents,'' Mr.
Axelrod said. ``What he understands is that it really doesn't matter
where you say what you say. We're in a digital age, and you will be
heard. And he's right. I mean, you know, when Tony Fauci speaks, people
find him.''

Journalists with major news broadcasts are frustrated they can't book
Dr. Fauci during a public health emergency. Margaret Brennan, the host
of CBS's ``Face the Nation,'' told her audience in July that the White
House had not approved any interviews with Dr. Fauci since March,
inhibiting public understanding of the pandemic. ``We will continue our
efforts,''
\href{https://www.cbsnews.com/news/full-transcript-of-face-the-nation-on-july-5-2020/}{she
said}. Mary Hager, the executive producer of the show, said they asked
for Dr. Fauci and other government scientists every week.

``We have this genius and this gold mine of a guest,'' she said. ``And
we can't use him to his absolute maximum capacity at a time when people
are dying.''

Yet Dr. Fauci's accessibility is a boon for smaller outlets that can't
always book such a prominent guest. In July, Vincent Racaniello, a
Columbia University professor and the co-host of a podcast, ``This Week
in Virology,'' inquired about an interview. Dr. Fauci agreed almost
immediately.

``I was surprised because I know he's been very busy,'' he said. ``I
figured he wouldn't have time to do it, and I also wondered whether he
would be allowed to do it.''

Dr. Fauci \href{https://bit.ly/3fznojs}{spoke on the podcast} for 30
minutes, sharing his assessments of the latest science on Covid-19 and
the strategies that various pharmaceutical companies were using to
investigate vaccines. The audience for the 12-year-old ``This Week in
Virology'' has been growing since the pandemic hit, but the Fauci
episode has been its most popular one, with close to 100,000 combined
podcast downloads and YouTube views.

``Given the urgency of the situation and the need to get correct
information out, I was doing as many as humanly possible,'' Dr. Fauci
said. He mentioned he had a soft spot for commencement addresses, of
which he had done several, even though he knew the audiences would be
small. He
\href{https://www.holycross.edu/commencement/virtual-celebration?utm_source=facebook\&utm_medium=socialmedia\&utm_campaign=2020virtualcelebration}{spoke
to the graduating class} of the College of the Holy Cross, his alma
mater, among other colleges.

He is keenly aware of his media profile; he knows, for instance, that
the March 15 string of Sunday shows amounted to a
``\href{https://www.politico.com/gallery/the-full-ginsburg?slide=0}{full
Ginsburg}.'' (The reference is to William H. Ginsburg, a lawyer for
Monica Lewinsky, who appeared on all five Sunday shows in 1998.)

But his inclination to say yes --- and his friendships with prominent
journalists --- has sometimes gotten him in trouble, as it did when his
friend Norah O'Donnell interviewed him for InStyle magazine. Dr. Fauci
was
\href{https://www.instyle.com/news/dr-fauci-says-with-all-due-modesty-i-think-im-pretty-effective}{photographed}
by his backyard pool wearing sunglasses --- an image that did not sit
well with Republicans, and one he now says he regrets.

``Not really me, and anyone who knows me understands that this is not my
style,'' he wrote. ``I can understand the criticism, and like I said, I
wish I could take it back. My bad.''

His friends say he has overextended himself; Mr. Staley said he had
lately been encouraging Dr. Fauci to ``take an axe to his schedule.''
The polyp surgery has done that for him. He can't do extended interviews
until September.

Additional work by Josh Williams

Read 188 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
