\href{//www.nytimes3xbfgragh.onion}{}
\href{//elections.nytimes3xbfgragh.onion}{ Election 2016}

\href{//www.nytimes3xbfgragh.onion}{ Home}

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/senate}{Senate}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/house}{House}
\href{//www.nytimes3xbfgragh.onion/interactive/2016/11/08/us/politics/election-exit-polls.html}{Exit
Polls} \href{//www.nytimes3xbfgragh.onion/elections\#}{More}

Close

Forecast

\href{//www.nytimes3xbfgragh.onion/elections/2016/forecast/president}{}

\hypertarget{election-night-estimates-from-the-upshot}{%
\subsubsection{Election Night Estimates from The
Upshot}\label{election-night-estimates-from-the-upshot}}

Key States

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Arizona}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colorado}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Florida}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nevada}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{New
Hampshire}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{North
Carolina}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pennsylvania}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Virginia}

All States

Alabama Alaska Arizona Arkansas California Colorado Connecticut Delaware
District of Columbia Florida Georgia Hawaii Idaho Illinois Indiana Iowa
Kansas Kentucky Louisiana Maine Maryland Massachusetts Michigan
Minnesota Mississippi Missouri Montana Nebraska Nevada New Hampshire New
Jersey New Mexico New York North Carolina North Dakota Ohio Oklahoma
Oregon Pennsylvania Rhode Island South Carolina South Dakota Tennessee
Texas Utah Vermont Virginia Washington West Virginia Wisconsin Wyoming

The data for the results on this site are reported by the Associated
Press through the week of Nov. 8, 2016. Presidential results are updated
as of Feb. 2017.

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/senate}{Senate}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/house}{House}
\href{//www.nytimes3xbfgragh.onion/elections/2016/forecast/president}{Forecast}
\href{//www.nytimes3xbfgragh.onion/interactive/2016/11/08/us/politics/election-exit-polls.html}{Exit
Polls} \href{//www.nytimes3xbfgragh.onion/elections\#}{State Results}
\href{//www.nytimes3xbfgragh.onion/elections\#}{More}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alabama}{Ala.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alaska}{Alaska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Ariz.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arkansas}{Ark.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/california}{Calif.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colo.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/connecticut}{Conn.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/delaware}{Del.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/district-of-columbia}{D.C.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Fla.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/georgia}{Ga.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/hawaii}{Hawaii}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/idaho}{Idaho}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/illinois}{Ill.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/indiana}{Ind.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kansas}{Kan.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kentucky}{Ky.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/louisiana}{La.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maine}{Me.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maryland}{Md.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/massachusetts}{Mass.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/michigan}{Mich.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/minnesota}{Minn.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Miss.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/missouri}{Mo.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/montana}{Mont.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nebraska}{Neb.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nev.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{N.H.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-jersey}{N.J.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-mexico}{N.M.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-york}{N.Y.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{N.C.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-dakota}{N.D.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oklahoma}{Okla.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oregon}{Ore.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pa.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/rhode-island}{R.I.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-carolina}{S.C.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-dakota}{S.D.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/tennessee}{Tenn.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/texas}{Tex.}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/utah}{Utah}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/vermont}{Vt.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Va.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/washington}{Wash.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/west-virginia}{W.Va.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wisconsin}{Wis.}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wyoming}{Wyo.}
\end{itemize}

\hypertarget{mississippi-results}{%
\section{Mississippi Results}\label{mississippi-results}}

 Aug. 1, 2017, 11:22 AM ET

\protect\hyperlink{president}{ President Pres. Trump }
\protect\hyperlink{house}{House 1 D 3 R }
\protect\hyperlink{state-legislature}{State Legislature}
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/primaries/mississippi}{Primary
Results}

\hypertarget{president}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-president-clinton-trump}{President}}{President}}\label{president}}

Candidate

Party

Votes

Pct.

E.V.

Republican Rep.

700,714

57.9\%

6

Democrat Dem.

485,131

40.1\%

---

Libertarian Lib.

14,435

1.2\%

---

Constitution Const.

3,987

0.3\%

---

Green Green

3,731

0.3\%

---

Independent Ind.

2,446

0.2\%

---

Independent Ind.

644

0.1\%

---

6,821

0.6\%

---

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Full
Miss. Results »}

1,211,088 votes, 100\% reporting (1,811 of 1,811 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President
Map »}

Race Preview: Mississippi has six electoral votes and is expected to
vote for Mr. Trump.
\href{//elections.nytimes3xbfgragh.onion/2012/results/states/mississippi}{Mitt
Romney won Mississippi in 2012} by 11.5 percentage points.

Vote share

Dem. 40 50 60

Rep. 40 50 60

Other 40 50 60

 No results

Vote by county

Trump

Clinton

Hinds

25,275

67,594

DeSoto

43,089

20,591

Harrison

40,354

21,169

Rankin

47,178

14,110

Madison

28,265

20,343

Jackson

33,629

14,657

Lee

22,220

10,029

Lauderdale

17,741

11,269

Jones

20,133

7,791

Forrest

15,461

11,716

Lowndes

13,271

11,819

Lamar

18,751

5,190

Pearl River

17,782

3,604

Lafayette

10,872

7,969

Warren

9,767

9,284

Oktibbeha

8,576

8,859

Hancock

13,811

3,344

Washington

5,244

11,380

Pike

8,009

8,043

Monroe

10,167

5,524

Lincoln

10,550

4,458

Panola

7,449

7,431

Marshall

6,587

8,023

Alcorn

11,819

2,684

Adams

5,874

7,757

Bolivar

4,590

9,046

Pontotoc

10,336

2,386

Copiah

6,103

6,741

Marion

7,836

3,677

Tate

7,495

3,926

Union

9,235

2,012

Simpson

7,393

3,874

Leflore

3,212

7,787

Neshoba

7,679

2,715

Scott

6,122

4,268

Grenada

5,970

4,424

Yazoo

4,598

5,369

Clay

4,150

5,722

George

8,696

1,027

Prentiss

7,648

2,067

Itawamba

8,470

1,117

Wayne

5,990

3,524

Sunflower

2,794

6,725

Newton

6,548

2,756

Tippah

7,240

1,842

Coahoma

2,426

6,378

Winston

4,910

3,850

Covington

5,435

3,276

Jasper

4,038

4,368

Leake

4,782

3,584

Tishomingo

7,166

999

Attala

4,897

3,242

Holmes

1,309

6,689

Chickasaw

4,127

3,649

Clarke

5,137

2,585

Smith

5,928

1,617

Amite

4,289

2,697

Stone

5,306

1,573

Walthall

4,056

2,790

Calhoun

4,390

1,910

Lawrence

4,091

2,195

Jeff Davis

2,466

3,720

Yalobusha

3,376

2,582

Tallahatchie

2,462

3,337

Noxubee

1,200

4,347

Carroll

3,799

1,680

Perry

4,135

1,220

Greene

4,335

974

Webster

3,976

1,019

Montgomery

2,818

2,115

Kemper

1,778

2,827

Franklin

2,721

1,502

Claiborne

540

3,708

Humphreys

1,151

3,071

Wilkinson

1,318

2,857

Choctaw

2,788

1,218

Benton

2,251

1,719

Jefferson

490

3,337

Tunica

853

2,667

Quitman

1,001

2,312

Sharkey

692

1,479

Issaquena

298

395

\protect\hyperlink{}{+ Show all counties -- Hide smaller counties}

\hypertarget{us-house}{%
\subsection{U.S. House}\label{us-house}}

Dem. 1 Dem.

Rep. 3 Rep.

Ind. 0 Ind.

No net change

\begin{longtable}[]{@{}lllll@{}}
\toprule
District Dist. & Leader & & Rpt. &\tabularnewline
\midrule
\endhead
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-1-kelly-owens}{1}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-1-kelly-owens}{
69\%Kelly* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-1-kelly-owens}{
28\%Owens Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-1-kelly-owens}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-1-kelly-owens}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-2-thompson-bouie}{2}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-2-thompson-bouie}{
67\%Thompson* Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-2-thompson-bouie}{
29\%Bouie Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-2-thompson-bouie}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-2-thompson-bouie}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-3-harper-quinn}{3}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-3-harper-quinn}{
66\%Harper* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-3-harper-quinn}{
30\%Quinn Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-3-harper-quinn}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-3-harper-quinn}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-4-palazzo-gladney}{4}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-4-palazzo-gladney}{
65\%Palazzo* Rep.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-4-palazzo-gladney}{
28\%Gladney Dem.} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-4-palazzo-gladney}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-house-district-4-palazzo-gladney}{}\tabularnewline
\bottomrule
\end{longtable}

* Incumbent~

 Lead Win Flip Dem.

 Lead Win Flip Rep.

 Lead Win Flip Other

 Runoff

 No election

 No results

\hypertarget{state-house}{%
\subsection{State House}\label{state-house}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
District Dist. & Leader & & Rpt. &\tabularnewline
\midrule
\endhead
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-89}{89†}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-89}{
47\%Scoggin} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-89}{
31\%Swindall} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-89}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-89}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-106}{106†}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-106}{
28\%Corley} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-106}{
25\%Holcomb} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-106}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-state-house-special-district-106}{}\tabularnewline
\bottomrule
\end{longtable}

~ † Special Election

 Runoff

\hypertarget{appeals-court}{%
\subsection{Appeals Court}\label{appeals-court}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Race & Leader & & Rpt. &\tabularnewline
\midrule
\endhead
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-2-position-2}{2
Position 2} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-2-position-2}{
57\%Westbrooks} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-2-position-2}{
43\%James*} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-2-position-2}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-2-position-2}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-5-position-2}{5
Position 2} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-5-position-2}{
0\%Ishee*} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-5-position-2}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-5-position-2}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-appeals-court-district-5-position-2}{}\tabularnewline
\bottomrule
\end{longtable}

* Incumbent~

\hypertarget{court-of-appeals-district-3-position-1}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-court-of-appeals-district-3-position-1}{Court
of Appeals District 3 Position
1}}{Court of Appeals District 3 Position 1}}\label{court-of-appeals-district-3-position-1}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Candidate & Votes & Pct. &\tabularnewline
\midrule
\endhead
 Wilson* Jack Wilson* & 109,864 & 49.8\% &\tabularnewline
 Hannan Ed Hannan & 81,751 & 37.1\% &\tabularnewline
 Yoder Dow Yoder & 28,864 & 13.1\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Full
Miss. Results »}

220,479 votes, 100\% reporting (373 of 373 precincts)

 Runoff

* Incumbent

\hypertarget{supreme-court}{%
\subsection{Supreme Court}\label{supreme-court}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Race & Leader & & Rpt. &\tabularnewline
\midrule
\endhead
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-1-position-3}{1
Position 3} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-1-position-3}{
54\%Kitchens*} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-1-position-3}{
46\%Griffis} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-1-position-3}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-1-position-3}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-2-position-2}{2
Position 2} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-2-position-2}{
67\%Beam*} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-2-position-2}{
33\%Shareef} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-2-position-2}{99\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-2-position-2}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-1}{3
Position 1} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-1}{
31\%Chamberlin} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-1}{
29\%Brady} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-1}{100\%}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-1}{}\tabularnewline
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-2}{3
Position 2} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-2}{
0\%Maxwell*} &
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-2}{Uncontested}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-2}{}
&
\href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi-supreme-court-district-3-position-2}{}\tabularnewline
\bottomrule
\end{longtable}

* Incumbent~

 Runoff

\hypertarget{president-1}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/president}{President}}{President}}\label{president-1}}

\hypertarget{senate}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/senate}{Senate}}{Senate}}\label{senate}}

\hypertarget{house}{%
\subsubsection{\texorpdfstring{\href{//www.nytimes3xbfgragh.onion/elections/2016/results/house}{House}}{House}}\label{house}}

\hypertarget{state-results}{%
\subsubsection{State Results}\label{state-results}}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alabama}{Alabama}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alaska}{Alaska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Arizona}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arkansas}{Arkansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/california}{California}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colorado}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/connecticut}{Connecticut}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/delaware}{Delaware}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/district-of-columbia}{District
  of Columbia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Florida}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/georgia}{Georgia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/hawaii}{Hawaii}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/idaho}{Idaho}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/illinois}{Illinois}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/indiana}{Indiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kansas}{Kansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kentucky}{Kentucky}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/louisiana}{Louisiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maine}{Maine}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maryland}{Maryland}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/massachusetts}{Massachusetts}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/michigan}{Michigan}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/minnesota}{Minnesota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Mississippi}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/missouri}{Missouri}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/montana}{Montana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nebraska}{Nebraska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nevada}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{New
  Hampshire}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-jersey}{New
  Jersey}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-mexico}{New
  Mexico}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-york}{New
  York}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{North
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-dakota}{North
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oklahoma}{Oklahoma}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oregon}{Oregon}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pennsylvania}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/rhode-island}{Rhode
  Island}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-carolina}{South
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-dakota}{South
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/tennessee}{Tennessee}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/texas}{Texas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/utah}{Utah}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/vermont}{Vermont}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/washington}{Washington}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/west-virginia}{West
  Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wisconsin}{Wisconsin}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wyoming}{Wyoming}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alabama}{Alabama}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/alaska}{Alaska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arizona}{Arizona}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/arkansas}{Arkansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/california}{California}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/colorado}{Colorado}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/connecticut}{Connecticut}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/delaware}{Delaware}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/district-of-columbia}{District
  of Columbia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/florida}{Florida}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/georgia}{Georgia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/hawaii}{Hawaii}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/idaho}{Idaho}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/illinois}{Illinois}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/indiana}{Indiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/iowa}{Iowa}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kansas}{Kansas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/kentucky}{Kentucky}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/louisiana}{Louisiana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maine}{Maine}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/maryland}{Maryland}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/massachusetts}{Massachusetts}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/michigan}{Michigan}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/minnesota}{Minnesota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/mississippi}{Mississippi}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/missouri}{Missouri}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/montana}{Montana}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nebraska}{Nebraska}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/nevada}{Nevada}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-hampshire}{New
  Hampshire}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-jersey}{New
  Jersey}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-mexico}{New
  Mexico}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/new-york}{New
  York}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-carolina}{North
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/north-dakota}{North
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/ohio}{Ohio}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oklahoma}{Oklahoma}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/oregon}{Oregon}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/pennsylvania}{Pennsylvania}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/rhode-island}{Rhode
  Island}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-carolina}{South
  Carolina}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/south-dakota}{South
  Dakota}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/tennessee}{Tennessee}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/texas}{Texas}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/utah}{Utah}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/vermont}{Vermont}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/virginia}{Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/washington}{Washington}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/west-virginia}{West
  Virginia}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wisconsin}{Wisconsin}
\item
  \href{//www.nytimes3xbfgragh.onion/elections/2016/results/wyoming}{Wyoming}
\end{itemize}

Sources: Election results from The Associated Press, Dave Leip's Atlas
of U.S. Presidential Elections and David Wasserman of the Cook Political
Report

By The New York Times

\begin{itemize}
\tightlist
\item
  \href{//www.nytco.com}{© 2017 The New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//www.nytco.com}{© 2017 The New York Times Company}
\item
  \href{//www.nytimes3xbfgragh.onion/ref/membercenter/help/infoservdirectory.html}{Contact
  Us}
\item
  \href{//www.nytco.com/careers}{Work With Us}
\item
  \href{//www.nytimes.whsites.net/mediakit}{Advertise}
\item
  \href{//www.nytimes3xbfgragh.onion/content/help/rights/privacy/policy/privacy-policy.html\#pp}{Your
  Ad Choices}
\item
  \href{//www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{//www.nytimes3xbfgragh.onion/ref/membercenter/help/agree.html}{Terms
  of Service}
\item
  \href{//www.nytimes3xbfgragh.onion/content/help/rights/sale/terms-of-sale.html}{Terms
  of Sale}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{//spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{//www.nytimes3xbfgragh.onion/membercenter/sitehelp.html}{Help}
\item
  \href{https://myaccount.nytimes3xbfgragh.onion/membercenter/feedback.html}{Site
  Feedback}
\item
  \href{//www.nytimes3xbfgragh.onion/subscriptions/Multiproduct/lp5558.html?campaignId=37WXW}{Subscriptions}
\end{itemize}
