Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{What Iowa Caucusgoers Have to Say}\href{}{Skip to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@NYTimes.com}{\nolinkurl{letters@NYTimes.com}}.

\hypertarget{what-iowa-caucusgoers-have-to-say}{%
\section{What Iowa Caucusgoers Have to
Say}\label{what-iowa-caucusgoers-have-to-say}}

Jan. 31, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{81}
\end{itemize}

\hypertarget{we-called--75299-iowans-584-took-our-poll-we-flew--to-iowa-to-meet-15-of-them}{%
\subsection{\texorpdfstring{We called 75,299 Iowans. 584 took our poll.
We flew to Iowa to meet 15 of
them.}{We called  75,299 Iowans. 584 took our poll. We flew  to Iowa to meet 15 of them.}}\label{we-called--75299-iowans-584-took-our-poll-we-flew--to-iowa-to-meet-15-of-them}}

ALL OVER IOWA --- Erika Derrick was feeding her peacocks in Springville,
Iowa, when the phone rang. It was us, The New York Times, on the other
end of the line. Hers was one of 75,299 numbers called as part of a
\href{https://www.nytimes3xbfgragh.onion/2020/01/25/us/politics/democratic-iowa-poll-sanders.html}{poll
conducted} in January by The Times and Siena College. A small subset of
these likely Democratic caucusgoers --- including Ms. Derrick --- said
they would talk to us in person. So we flew to Iowa to meet 15 of them
(plus a 9-year-old) in their homes, dorm rooms, a coffee shop and two
public libraries.

\hypertarget{colleen-sheely-said-she-could-still-be-persuaded-to-caucus-for-a-different-candidate-39-percent-of-likely-caucusgoers-felt-the-same-way-meet-her-and-14-other-iowans-below}{%
\subsection{Colleen Sheely said she could still be persuaded to caucus
for a different candidate. 39 percent of likely caucusgoers felt the
same way. Meet her and 14 other Iowans
below.}\label{colleen-sheely-said-she-could-still-be-persuaded-to-caucus-for-a-different-candidate-39-percent-of-likely-caucusgoers-felt-the-same-way-meet-her-and-14-other-iowans-below}}

\hypertarget{results-from-all-likely-caucusgoers}{%
\subsection{Results from all likely
caucusgoers}\label{results-from-all-likely-caucusgoers}}

59\% said their mind was made up.

39\% could still be persuaded.

59\% said their mind was made up.

39\% could still be persuaded.

Source: The New York Times/Siena College poll conducted Jan. 20-23.

Closed captions

Tap to unmute

\hypertarget{iowa-democrats-are-split-on-whether-to-support-a-candidate-they-agree-with-most-or-one-with-the-best-chance-of-beating-president-trump-so-is-our-group}{%
\subsection{Iowa Democrats are split on whether to support a candidate
they agree with most, or one with the best chance of beating President
Trump. So is our
group.}\label{iowa-democrats-are-split-on-whether-to-support-a-candidate-they-agree-with-most-or-one-with-the-best-chance-of-beating-president-trump-so-is-our-group}}

\hypertarget{results-from-all-likely-caucusgoers-1}{%
\subsection{Results from all likely
caucusgoers}\label{results-from-all-likely-caucusgoers-1}}

Would you be likelier to support a Democrat who ...

48\% ... you agree with most on the issues.

49\% ... has the best chance to beat President Trump.

Would you be likelier to support a Democrat who ...

49\% ... has the best chance to beat President Trump.

48\% ... you agree with most on the issues.

Source: New York Times/Siena College poll conducted Jan. 20-23.

Closed captions

Tap to unmute

\hypertarget{most-people-we-met-said-they-had-previously-attended-an-iowa-party-caucus-and-would-attend-this-year-even-if-the-weather-was-bad-that-included-richard-mendenhall-82-who-has-not-caucused-since-john-f-kennedy}{%
\subsection{Most people we met said they had previously attended an Iowa
party caucus and would attend this year, even if the weather was bad.
That included Richard Mendenhall, 82, who has not caucused since John F.
Kennedy.}\label{most-people-we-met-said-they-had-previously-attended-an-iowa-party-caucus-and-would-attend-this-year-even-if-the-weather-was-bad-that-included-richard-mendenhall-82-who-has-not-caucused-since-john-f-kennedy}}

\hypertarget{results-from-all-likely-caucusgoers-2}{%
\subsection{Results from all likely
caucusgoers}\label{results-from-all-likely-caucusgoers-2}}

71\% have attended an Iowa party caucus before.

29\% have not.

71\% have attended an Iowa party caucus before.

29\% have not.

Source: New York Times/Siena College poll conducted Jan. 20-23.

Closed captions

Tap to unmute

\hypertarget{a-number-of-worries-keeps-these-iowans-up-at-night-getting-a-job-losing-health-care-racism-some-noted-the-lack-of-diversity-in-iowa-which-is-more-than-90-percent-white}{%
\subsection{A number of worries keeps these Iowans up at night: getting
a job, losing health care, racism. Some noted the lack of diversity in
Iowa, which is more than 90 percent
white.}\label{a-number-of-worries-keeps-these-iowans-up-at-night-getting-a-job-losing-health-care-racism-some-noted-the-lack-of-diversity-in-iowa-which-is-more-than-90-percent-white}}

\hypertarget{this-question-was-not-in-the-poll-but-we-asked-it-in-person}{%
\subsection{This question was not in the poll, but we asked it in
person.}\label{this-question-was-not-in-the-poll-but-we-asked-it-in-person}}

Closed captions

Tap to unmute

\hypertarget{what-is-the-best-thing-about-iowa-the-people-the-worst-thing-the-weather-by-far}{%
\subsection{What is the best thing about Iowa? The people. The worst
thing? The weather, by
far.}\label{what-is-the-best-thing-about-iowa-the-people-the-worst-thing-the-weather-by-far}}

\hypertarget{these-questions-were-not-in-the-poll-but-we-asked-them-in-person}{%
\subsection{These questions were not in the poll, but we asked them in
person.}\label{these-questions-were-not-in-the-poll-but-we-asked-them-in-person}}

Closed captions

Tap to unmute

\emph{The New York Times/Siena College Research Institute survey of
1,689 registered voters in Iowa, including 584 Democratic caucusgoers,
was conducted from Jan. 20 to Jan. 23. The margin of error due to
sampling is plus or minus 4.8 percentage points for the Democratic
caucus electorate and plus or minus 2.8 percentage points for registered
voters. To ensure a representative sample, the types of voters least
likely to respond to telephone polls were more likely to be called.}

Reporters/Producers

Larry Buchanan

Haeyoun Park

Solana Pyne

Nilo Tabrizy

Cinematographers

Brian Dawson

Elliot deBruyn

Director of Cinematography

Jonah M. Kessel

Editors

Jeff Bernier

Meg Felling

Caroline Kim

Natalie Reneau

Design/Development

Larry Buchanan

Alastair Coote

Eden Weingart

Additional Production

Aaron Byrd

Dave DeCristo

Christina Kelso

Michael Puretz

Read 81 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
