 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

\hypertarget{-books-}{%
\subsubsection{\texorpdfstring{
\href{https://www.nytimes3xbfgragh.onion/section/books}{Books}
}{ Books }}\label{-books-}}

 \href{https://www.nytimes3xbfgragh.onion/section/books}{Books}
\textbar{}Book Your Calendar

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2EqSMyr}

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

\hypertarget{book-your-calendar}{%
\section{Book Your Calendar}\label{book-your-calendar}}

DEC. 22, 2017

Keep up with the latest and greatest in books. The New York Times Book
Review has curated a calendar of must-know literary events --- new
releases, awards, film adaptations and more.

\hypertarget{july-1}{%
\section{July 1}\label{july-1}}

\hypertarget{16-books-to-watch-for-in-july}{%
\section{16 Books to Watch For in
July}\label{16-books-to-watch-for-in-july}}

A memoir from the poet Natasha Trethewey; ``Hamnet,'' Maggie O'Farrell's
novel about Shakespeare; and ``Too Much and Never Enough,'' an exposé
about President Trump by his niece:
\href{https://nyti.ms/2Z29NKE?smid=bookscal}{https://nyti.ms/2Z29NKE.}

\hypertarget{july-11}{%
\section{July 11}\label{july-11}}

\hypertarget{jhumpa-lahiris-birthday}{%
\section{Jhumpa Lahiri's Birthday}\label{jhumpa-lahiris-birthday}}

The novelist and essayist was born on this day in 1967. Read her By the
Book interview \href{https://nyti.ms/37YC6xq?smid=bookscal}{here}.

\hypertarget{july-11-1}{%
\section{July 11}\label{july-11-1}}

\hypertarget{to-kill-a-mockingbird}{%
\section{To Kill a Mockingbird}\label{to-kill-a-mockingbird}}

Harper Lee's novel was first published on this day in 1960. On the day
of Ms. Lee's death, The New York Times asked readers to share scenes
from the novel, published in 1960, and movie (1962) that had stuck with
them. Hundreds responded --- a selection of responses are
\href{https://nyti.ms/37YK5up?smid=bookscal}{here}.

\hypertarget{july-11-2}{%
\section{July 11}\label{july-11-2}}

\hypertarget{to-kill-a-mockingbird-1}{%
\section{To Kill a Mockingbird}\label{to-kill-a-mockingbird-1}}

Harper Lee's novel was first published on this day in 1960. On the day
of Ms. Lee's death, The New York Times asked readers to share scenes
from the novel, published in 1960, and movie (1962) that had stuck with
them. Hundreds responded --- a selection of responses are
\href{https://nyti.ms/37YK5up?smid=bookscal}{here}.

\hypertarget{july-15}{%
\section{July 15}\label{july-15}}

\hypertarget{iris-murdochs-birthday}{%
\section{Iris Murdoch's Birthday}\label{iris-murdochs-birthday}}

Dame Iris Murdoch was born on this day in 1919. Murdoch wrote 26 novels
and taught philosophy at the University of Oxford.

``For decades this remarkable writer delivered prickly, sophisticated
and somewhat unearthly fiction about good and evil and sex and
morality.'' In 2019, Dwight Garner remembered the 20th-century giant on
the centennial of her birth:
\href{https://nyti.ms/2KAgUVC?smid=bookscal}{https://nyti.ms/2KAgUVC.}

\hypertarget{july-16}{%
\section{July 16}\label{july-16}}

\hypertarget{the-catcher-in-the-rye}{%
\section{The Catcher in the Rye}\label{the-catcher-in-the-rye}}

J.D. Salinger's novel was first published in full on this day in 1951.
Read The Times's 1951 review of the book
\href{https://nyti.ms/31esNIk?smid=bookscal}{here}.

\hypertarget{july-16-1}{%
\section{July 16}\label{july-16-1}}

\hypertarget{the-catcher-in-the-rye-1}{%
\section{The Catcher in the Rye}\label{the-catcher-in-the-rye-1}}

J.D. Salinger's novel was first published in full on this day in 1951.
Read The Times's 1951 review of the book
\href{https://nyti.ms/31esNIk?smid=bookscal}{here}.

\hypertarget{july-21}{%
\section{July 21}\label{july-21}}

\hypertarget{ernest-hemingways-birthday}{%
\section{Ernest Hemingway's Birthday}\label{ernest-hemingways-birthday}}

The novelist and journalist was born on this day in 1899. Read about the
Hemingway war story that came into print for the first time in 2018:
\href{https://nyti.ms/3fWpXMo?smid=bookscal}{https://nyti.ms/3fWpXMo.}

\hypertarget{july-28}{%
\section{July 28}\label{july-28}}

\hypertarget{beatrix-potters-birthday}{%
\section{Beatrix Potter's Birthday}\label{beatrix-potters-birthday}}

The writer and illustrator of ``The Tale of Peter Rabbit'' was born on
this day in 1866. Read about the manuscript of hers that was found in
2016, about a cat with a double life:
\href{https://nyti.ms/2Yv5pVt?smid=bookscal}{https://nyti.ms/2Yv5pVt.}

\hypertarget{july-28-1}{%
\section{July 28}\label{july-28-1}}

\hypertarget{beatrix-potters-birthday-1}{%
\section{Beatrix Potter's Birthday}\label{beatrix-potters-birthday-1}}

The writer and illustrator of ``The Tale of Peter Rabbit'' was born on
this day in 1866. Read about the manuscript of hers that was found in
2016, about a cat with a double life:
\href{https://nyti.ms/2Yv5pVt?smid=bookscal}{https://nyti.ms/2Yv5pVt.}

\hypertarget{answers-to-common-questions-weve-received}{%
\paragraph{Answers to common questions we've
received}\label{answers-to-common-questions-weve-received}}

\begin{itemize}
\item
  Does the calendar work with Android devices?
\item
  Yes. Use the signup at the top of this page to subscribe using your
  Google account. The calendar will be synced to your phone.
\item
  Is there a webcal/iCal feed I can use to subscribe directly?
\item
  Copied!
\item
  I subscribed to the calendar on my iPhone but it isn't showing up on
  my computer or tablet. How do I fix that?
\item
  You will need to add
  \href{https://support.apple.com/en-us/HT202361}{an iCloud Calendar
  subscription}. Use the webcal link mentioned above.
\item
  Can I subscribe if I use Outlook?
\item
  Yes. Using the webcal link above, you can add the calendar to
  \href{https://support.office.com/en-us/article/Import-or-subscribe-to-a-calendar-in-Outlook-com-or-Outlook-on-the-web-cff1429c-5af6-41ec-a5b4-74f2c278e98c}{Outlook.com}
  or an
  \href{https://support.office.com/en-us/article/View-and-subscribe-to-Internet-Calendars-7CD5D35A-4A90-4D70-A2F7-F6FADD7E2D9A}{Outlook
  desktop client}.
\item
  How do I submit feedback, or suggest another important event that I
  think you missed?
\item
  Email us at
  \href{mailto:bookyourcalendar@NYTimes.com}{\nolinkurl{bookyourcalendar@NYTimes.com}}.
\item
  How do I unsubscribe?
\item
  Google Calendar:
  \href{https://support.google.com/calendar/answer/37188}{Unsubscribe
  using a desktop computer}\\
  iCloud: \href{https://support.apple.com/kb/PH2679?locale=en_US}{Delete
  the calendar from iCloud.com}\\
  iPhone/iPad: Open ``Settings,'' then ``Accounts,'' and remove the
  calendar subscription. If you do not see any entry for the calendar,
  follow the directions for Google Calendar or iCloud.
\end{itemize}

Produced by Britt Binler and Gray Beltran. Illustration by Pablo Delcan.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
