Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/business}{Business}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/business}{Business}\textbar{}Delta, American Join United
in Dropping Most US Change Fees

\url{https://nyti.ms/2Dg6fxj}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{delta-american-join-united-in-dropping-most-us-change-fees}{%
\section{Delta, American Join United in Dropping Most US Change
Fees}\label{delta-american-join-united-in-dropping-most-us-change-fees}}

By The Associated Press

\begin{itemize}
\item
  Aug. 31, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

This could be the final boarding call for the \$200 ticket-change fee
that has enraged so many U.S. airline travelers over the past decade.

Delta Air Lines and American Airlines said Monday that they are dropping
the fee on most tickets for domestic flights, copying United Airlines'
move one day earlier.

Southwest Airlines didn't levy change fees to start with, so Monday's
announcements mean that the four biggest U.S. carriers will have roughly
similar policies.

Airlines are being battered by the coronavirus pandemic, as travel
restrictions and fear of contracting the virus are keeping travelers at
home. Normally in summer, 2 million or more people pass through security
checkpoints at U.S. airports each day, but that number hasn't been above
900,000 since mid-March, the early days of the pandemic.

To woo passengers, airlines have required face masks and stepped up
cleaning of planes. A few, including Delta, Southwest and JetBlue, limit
seating, although American and United try to sell every seat.

Wolfe Research airline analyst Hunter Keay said he believes Delta and
United were considering dropping change fees even before the pandemic
because they were seen as too punitive.

``This is another example of a crisis accelerating forward thinking
ideas,'' Keay said, adding that United could have gone further and
dropped change fees on international itineraries too.

Delta and American said they have permanently eliminated change fees for
all domestic flights for premium and most economy fares except the
lowest fare, called basic economy. American is also dropping the fee on
trips to Canada, Mexico and the Caribbean.

American said it will let all passengers fly standby for earlier
same-day flights without charge beginning Oct. 1. United is making that
change on Jan. 1.

Both carriers also extended temporary waivers on change fees for
domestic and international flights, so ditching the fees permanently
won't make much difference to passengers right away. But by doing so,
United, Delta and American are abandoning a fee that has drawn
particular scorn from customers, consumer advocates and members of
Congress.

The fee, however, has raised lots of revenue for the airlines at very
little cost. Since 2010, Delta has raked in \$8.2 billion, American has
scooped up just under \$7 billion, and United has scored nearly \$6.5
billion just from change fees.

Airline shares fell on Monday after United's decision and the
expectation that other big airlines would be forced to ditch their
change fees too. Delta and United both ended down 3.6\%, American lost
4\% and Southwest dropped 3.2\%.

Even without change fees, plenty of other extra charges will survive.
Fees for checking a bag were greatly expanded more than a decade ago.
Many airlines also charge extra for seat assignments, more legroom,
priority boarding and other perks, and those fees provided a growing
source of revenue for airlines until the pandemic hit.

\_\_\_

David Koenig can be reached at
\href{http://www.twitter.com/airlinewriter}{www.twitter.com/airlinewriter}.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
