Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\hypertarget{13000-missing-flights-the-global-consequences-of-the-coronavirus}{%
\section{13,000 Missing Flights: The Global Consequences of the
Coronavirus}\label{13000-missing-flights-the-global-consequences-of-the-coronavirus}}

By Rich Harris,
\href{https://www.nytimes3xbfgragh.onion/by/blacki-migliozzi}{Blacki
Migliozzi} and
\href{https://www.nytimes3xbfgragh.onion/by/niraj-chokshi}{Niraj
Chokshi}Feb. 21, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Loading...

Thousands of planes criss-cross China every day, but that number has
fallen sharply as flights are canceled to help combat the coronavirus.

The slowdown in air travel has started to spread to popular destinations
for Chinese travelers, like Japan and South Korea.

It is, in part, a response to fears that the virus could become a
pandemic. In Europe, 47 people in nine countries have been infected so
far.

The decline poses economic risks, too, as China is a major source of
tourism to countries like the United States.

Flight paths are approximate·Source: Flightradar24

The disappearance of tens of thousands of flights from China's skies in
recent weeks points to how the coronavirus has hobbled a nation.

The flight suspensions started to mount late last month as countries and
airlines sharply limited service in response to the accelerating spread
of the virus, which as of Friday has
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/asia/china-wuhan-coronavirus-maps.html}{infected
at least 76,000 people} and killed more than 2,200, most of them in
China.

Within just three weeks --- from Jan. 23 to Feb. 13 --- the number of
daily departures and arrivals for domestic and international flights
dropped to just 2,004, from 15,072, according to Flightradar24, an
industry data firm. Over 13,000 flights a day, lost to a crisis.

\hypertarget{chinas-daily-domestic-and-international-flights}{%
\subsubsection{China's daily domestic and international
flights}\label{chinas-daily-domestic-and-international-flights}}

\hypertarget{international-flights}{%
\subsubsection{International flights}\label{international-flights}}

Jan. 1 Feb. 13

0

1,000

2,000

3,000

4,000

\textbf{Jan. 23} Travel bans start

\hypertarget{domestic-flights}{%
\subsubsection{Domestic flights}\label{domestic-flights}}

Jan. 1 Feb. 13

0

3,000

6,000

9,000

12,000

Source: Flightradar24

Restrictive measures adopted by China helped to delay the spread of the
virus to other countries by two to three weeks, the World Health
Organization said this week.
\href{https://www.nytimes3xbfgragh.onion/2020/02/13/world/coronavirus-timeline.html}{Officials
in China closed off Wuhan}, the epicenter of the outbreak, on Jan. 23,
and began canceling train, bus and airline travel; closing schools and
factories; and pressuring residents to stay home around the country.

But China's increasing isolation from the world could have lasting
economic consequences.

When tourists stop showing up to the temples in Kyoto or the malls in
Hong Kong or the beaches in Thailand, their absence is felt. Chinese
travelers account for about a fifth of all tourism spending, more than
any other country, according to the U.N.'s World Tourism Organization.
In 2018, Chinese residents spent \$277 billion abroad, according to the
U.N., or nearly twice as much as residents of the United States.

\hypertarget{daily-flights-to-the-top-four-destinations-for-chinese-tourists}{%
\subsubsection{Daily flights to the top four destinations for Chinese
tourists}\label{daily-flights-to-the-top-four-destinations-for-chinese-tourists}}

\hypertarget{japan}{%
\subsubsection{Japan}\label{japan}}

Jan. 1 Feb. 13

0

150

300

\textbf{Jan. 23} Travel bans start

\hypertarget{hong-kong}{%
\subsubsection{Hong Kong}\label{hong-kong}}

Jan. 1 Feb. 13

0

150

300

\hypertarget{thailand}{%
\subsubsection{Thailand}\label{thailand}}

Jan. 1 Feb. 13

0

150

300

\hypertarget{south-korea}{%
\subsubsection{South Korea}\label{south-korea}}

Jan. 1 Feb. 13

0

150

300

Source: Flightradar24

It's still too early to tell what the overall impact will be, but Wall
Street firms, analysts and economists have been trying to calculate the
costs.

As China struggles to
\href{https://www.nytimes3xbfgragh.onion/2020/02/17/business/china-coronavirus-economy.html}{reopen
for business}, a range of companies have warned that the outbreak may
weigh on their financial performance. Japan, whose economy had already
been teetering,
\href{https://www.nytimes3xbfgragh.onion/2020/02/16/business/coronavirus-japan-economy.html}{is
facing a possible recession}. Oxford Economics said in a new report
that, in a worst-case scenario, the outbreak could
\href{https://twitter.com/OxfordEconomics/status/1230208948395008001}{cut
\$1.1 trillion in global output}.

If the coronavirus crisis is anything like the SARS outbreak in the
early 2000s, it could eliminate \$29 billion in global airline revenue
this year, resulting in a small industry contraction, the International
Air Transport Association said on Thursday. The vast majority of the
losses would be concentrated among airlines in the Asia-Pacific region,
it said.

The SARS outbreak wiped out about \$6 billion in annual revenue for
airlines in that part of the world and it took nine months for
international passenger traffic to recover, the association said last
month. But the coronavirus has so far proved more lethal, more
widespread and more damaging to flight traffic in China, which today
plays a far bigger role in global travel than it did two decades ago.

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
