Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/science}{Science}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/science}{Science}\textbar{}Recipient of Face Transplant
Shares Her Story and Results

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{recipient-of-face-transplant-shares-her-story-and-results}{%
\section{Recipient of Face Transplant Shares Her Story and
Results}\label{recipient-of-face-transplant-shares-her-story-and-results}}

By The Associated Press

\begin{itemize}
\item
  May 6, 2009
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

CLEVELAND (AP) --- Five years ago, a shotgun blast left a ghastly hole
where the middle of Connie Culp's face had been. Five months ago, she
received a new face from a dead woman.

Image

Connie Culp, who received the first face transplant in the United
States, at a news conference on Tuesday in Cleveland. Her head surgeon,
Dr. Maria Siemionow, is at right. Credit...Amy Sancetta/Associated Press

Ms. Culp stepped forward on Tuesday to show the results of the nation's
first face transplant. Her new look was far from the puckered, noseless
sight that had made children run away in horror.

Ms. Culp's expressions are still a bit wooden, but she can talk, smile,
smell and taste food again. Her speech is at times difficult to
understand. Her face is bloated and squarish, and her skin droops in
folds that doctors plan to pare away as her circulation improves and her
nerves grow, animating new muscles. But she had nothing but praise for
those who made her new face possible.

Image

Connie Culp, after a shotgun injury to her face, left, and as she
appears after her face transplant surgery. Credit...Cleveland Clinic-HO,
via Associated Press

``I guess I'm the one you came to see today,'' Ms. Culp, 46, said at a
news conference at the Cleveland Clinic, where the groundbreaking
operation was performed. But, she said, ``I think it's more important
that you focus on the donor family that made it so I could have this
person's face.''

Until Tuesday, Ms. Culp's identity and how she came to be disfigured
were a secret.

Ms. Culp's husband, Thomas, shot her in 2004, then turned the gun on
himself. He went to prison for seven years. She was left clinging to
life.

Image

Ms. Culp before her injury.Credit...Cleveland Clinic-HO, via Associated
Press

The blast shattered her nose and cheeks, the roof of her mouth and an
eye. Hundreds of fragments of shotgun pellet and bone splinters were
embedded in her face. She needed a tube in her windpipe to breathe. Only
her upper eyelids, forehead, lower lip and chin were left. She endured
30 operations to try to fix her face.

Ms. Culp said she wanted to help foster acceptance of those who have
suffered burns and other disfiguring injuries.

``When somebody has a disfigurement and don't look as pretty as you do,
don't judge them because you never know what happened to them,'' she
said. ``Don't judge people who don't look the same as you do. Because
you never know. One day it might be all taken away.''

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
