Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/us}{U.S.}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/us}{U.S.}\textbar{}More Than 40\% of U.S. Coronavirus
Deaths Are Linked to Nursing Homes

\href{https://nyti.ms/31mkr1B}{https://nyti.ms/31mkr1B}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\href{https://www.nytimes.com/news-event/coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{The
Coronavirus Outbreak}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes.com/2020/08/08/world/coronavirus-updates.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Latest
  Updates}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Maps
  and Cases}
\item
  \href{https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes.com/interactive/2020/world/coronavirus-tips-advice.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{F.A.Q.}
\item
  \href{https://www.nytimes.com/live/2020/08/07/business/stock-market-today-coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Markets
  \& Economy}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{more-than-40-of-us-coronavirus-deaths-are-linked-to-nursing-homes}{%
\section{More Than 40\% of U.S. Coronavirus Deaths Are Linked to Nursing
Homes}\label{more-than-40-of-us-coronavirus-deaths-are-linked-to-nursing-homes}}

By The New York TimesUpdated July 30, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

41\%

of all U.S. deaths

62,000+

8\%

of all U.S. cases

362,000+

At least 62,000 residents and workers have died from the coronavirus at
nursing homes and other long-term care facilities for older adults in
the United States, according to a New York Times database. As of July
30, the virus has infected more than 362,000 people at some 16,000
facilities.

Nursing home populations are at a high risk of being infected by --- and
dying from --- the coronavirus, according to the
\href{https://www.cdc.gov/coronavirus/2019-ncov/hcp/long-term-care.html}{Centers
for Disease Control and Prevention}. Covid-19, the disease caused by the
coronavirus, is known to be particularly lethal to adults in their 60s
and older who have underlying health conditions. And it can
\href{https://www.nytimes.com/2020/04/17/us/coronavirus-nursing-homes.html}{spread
more easily} through congregate facilities, where many people live in a
confined environment and workers move from room to room.

While 8 percent of the country's cases have occurred in long-term care
facilities, deaths related to Covid-19 in these facilities account for
more than 41 percent of the country's pandemic fatalities.

\hypertarget{in-20-states-at-least-half-of-deaths-are-linked-to-nursing-homes}{%
\subsubsection{In 20 states, at least half of deaths are linked to
nursing
homes.}\label{in-20-states-at-least-half-of-deaths-are-linked-to-nursing-homes}}

Share of state's deaths linked to long-term care facilities

0

25

50

75

100\%

Insufficient data

Ala.

Alaska

Ariz.

Ark.

28\%

Calif.

43\%

Colo.

53\%

Conn.

74\%

Del.

57\%

D.C.

29\%

Fla.

37\%

Ga.

44\%

Hawaii

Idaho

45\%

Ill.

53\%

Ind.

55\%

Iowa

53\%

Kan.

52\%

Ky.

62\%

La.

39\%

Maine

64\%

Md.

59\%

Mass.

64\%

Mich.

32\%

Minn.

74\%

Miss.

43\%

Mo.

Mont.

13\%

Neb.

28\%

Nev.

19\%

N.H.

82\%

N.J.

43\%

N.M.

35\%

N.Y.

20\%

N.C.

48\%

N.D.

61\%

Ohio

54\%

Okla.

44\%

Ore.

47\%

Pa.

67\%

R.I.

78\%

S.C.

35\%

S.D.

29\%

Tenn.

24\%

Texas

31\%

Utah

42\%

Vt.

56\%

Va.

56\%

Wash.

51\%

W.Va.

37\%

Wis.

Wyo.

23\%

\hypertarget{cases-and-deaths-in-long-term-care-facilities-by-state}{%
\subsubsection{Cases and deaths in long-term care facilities, by
state}\label{cases-and-deaths-in-long-term-care-facilities-by-state}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
& Facilities & Cases & Deaths & Share of Covid‑19
Deaths~▼\tabularnewline
\midrule
\endhead
United States & 16,000 & 362,000 & 62,000 & 41\%\tabularnewline
New Hampshire & 27 & 2,113 & 335 & 82\%\tabularnewline
Rhode Island & 67 & 2,870 & 790 & 78\%\tabularnewline
Minnesota & 892 & 5,777 & 1,207 & 74\%\tabularnewline
Connecticut & 287 & 10,311 & 3,262 & 74\%\tabularnewline
Pennsylvania & 835 & 23,093 & 4,857 & 67\%\tabularnewline
Maine & 22 & 649 & 78 & 64\%\tabularnewline
Massachusetts & 702 & 24,059 & 5,472 & 64\%\tabularnewline
Kentucky & 233 & 3,532 & 465 & 62\%\tabularnewline
North Dakota & 77 & 580 & 65 & 61\%\tabularnewline
Maryland & 300 & 13,774 & 2,066 & 59\%\tabularnewline
\bottomrule
\end{longtable}

Show more

*In New York, the case count is often the same as the death count
because the state only reports the number of people who have died but
not the number of overall infections.·States with insufficient data to
calculate a share of Covid-19 deaths are shaded gray.

The share of deaths linked to long-term care facilities for older adults
is even starker at the state level. In 20 states, the number of
residents and workers who have died accounts for either half or more
than half of all deaths from the virus.

Infected people linked to nursing homes also die at a higher rate than
the general population. The median case fatality rate --- the number of
deaths divided by the number of cases --- at facilities with reliable
data is 16 percent, significantly higher than the 3 percent case
fatality rate nationwide.

\hypertarget{facility-fatality-rates-are-much-higher-than-the-national-average}{%
\subsubsection{Facility fatality rates are much higher than the national
average}\label{facility-fatality-rates-are-much-higher-than-the-national-average}}

\hypertarget{number-of-long-term-care-facilities-by-case-fatality-rate}{%
\paragraph{Number of long-term care facilities by case fatality
rate}\label{number-of-long-term-care-facilities-by-case-fatality-rate}}

20facilities 40facilities 60facilities 80facilities 0\% 10\% 20\% 30\%
40\% 50\% 60\%

The U.S. case fatality rate is 3\%.

The median case fatality rate in long-term care facilities is 16\%.

Note: Only facilities with reliable case and death data and at least 50
cases are included.

In the absence of comprehensive data from some states and the federal
government, The Times has been assembling its own database of
coronavirus cases and deaths at long-term care facilities for older
adults. These include nursing homes, assisted-living facilities, memory
care facilities, retirement and senior communities and rehabilitation
facilities. This tracker will be updated periodically.

Some states, including Colorado, Illinois, Nevada, New Jersey and South
Carolina, regularly release cumulative data on cases and deaths at
specific facilities. New York regularly releases facility-level
information about deaths, but not about cases. Ohio, Wisconsin and
Minnesota, among others, provide some details on the number of cases at
specific facilities --- but not on deaths. Others report aggregate
totals for their states but provide no information on where the
infections or deaths have occurred. Some report very little or nothing
at all.

\hypertarget{there-are-at-least-16000-long-term-care-facilities-with-one-or-more-coronavirus-case}{%
\subsubsection{There are at least 16,000 long-term care facilities with
one or more coronavirus
case}\label{there-are-at-least-16000-long-term-care-facilities-with-one-or-more-coronavirus-case}}

States that provide some facility data

States that provide no facility data

Ala.

Alaska

Ariz.

Colo.

Fla.

Ga.

Ind.

Kan.

Maine

Mass.

Minn.

N.J.

N.C.

N.D.

Okla.

Pa.

S.D.

Texas

Wyo.

Conn.

Mo.

W.Va.

Ill.

N.M.

Ark.

Calif.

Del.

D.C.

Hawaii

Iowa

Ky.

Md.

Mich.

Miss.

Mont.

N.H.

N.Y.

Ohio

Ore.

Tenn.

Utah

Va.

Wash.

Wis.

Neb.

S.C.

Idaho

Nev.

Vt.

La.

R.I.

The Times's numbers are based on official confirmations from states,
counties and the facilities themselves, as well as some data provided by
the federal government. They include residents and, in cases in which
reporting is available, employees of the facilities. Given the wide
variability in the type of information available, the totals shown here
almost certainly represent an undercount of the true toll.

The New York Times is tracking the coronavirus at nursing homes and
long-term care centers. Do you or a family member live or work in one of
these facilities? If so,
\href{https://www.nytimes.com/2020/04/11/business/nursing-home-callout.html}{we
would like to hear from you}.

Here is a list of cases and deaths at long-term care facilities that
have had at least 50 cases. We are updating the numbers as we are able
to confirm them with state, county and facility officials.

\hypertarget{cases-and-deaths-by-facility}{%
\subsubsection{Cases and deaths, by
facility}\label{cases-and-deaths-by-facility}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Name & Location & Cases & Deaths~▼\tabularnewline
\midrule
\endhead
Parker Jewish Institute for Health Care \& Rehabilitation & Queens, N.Y.
& 82 & 82\tabularnewline
Paramus Veterans Memorial Home & Paramus, N.J. & 292 & 82\tabularnewline
Conestoga View Nursing and Rehabilitation & Lancaster, Pa. & 282 &
77\tabularnewline
Gracedale Nursing Home & Nazareth, Pa. & 299 & 75\tabularnewline
Fair Acres Geriatric Center & Lima, Pa. & 347 & 75\tabularnewline
Soldiers Home in Holyoke veterans center and hospital & Holyoke, Mass. &
161 & 74\tabularnewline
Brighton Rehabilitation \& Wellness Center & Beaver, Pa. & 445 &
73\tabularnewline
Long Island State Veterans Home & Stony Brook, N.Y. & 72 &
72\tabularnewline
The Plaza Rehab and Nursing Center & Bronx, N.Y. & 71 &
71\tabularnewline
Isabella Geriatric Center & New York, N.Y. & 68 & 68\tabularnewline
Lincoln Park Care Center rehabilitation facility & Lincoln Park, N.J. &
266 & 66\tabularnewline
New Jersey Veterans Memorial Home at Menlo Park & Edison, N.J. & 282 &
66\tabularnewline
Bergen New Bridge Medical Center nursing home & Paramus, N.J. & 373 &
66\tabularnewline
Father Baker Manor nursing home & Orchard Park, N.Y. & 65 &
65\tabularnewline
Andover Subacute \& Rehabilitation II & Andover, N.J. & 232 &
65\tabularnewline
\bottomrule
\end{longtable}

Show more

*In New York facilities, the case count is often the same as the death
count because the state only reports the number of people who have died
but not the number of overall infections.

\hypertarget{tracking-the-coronavirus}{%
\subsection{Tracking the Coronavirus}\label{tracking-the-coronavirus}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes.com/interactive/2020/world/coronavirus-maps.html}{World}
\item
  \href{https://www.nytimes.com/interactive/2020/04/21/world/coronavirus-missing-deaths.html}{World
  Deaths}
\item
  \href{https://www.nytimes.com/interactive/2020/04/23/upshot/five-ways-to-monitor-coronavirus-outbreak-us.html}{U.S.
  Cities}
\item
  \href{https://www.nytimes.com/interactive/2020/05/05/us/coronavirus-death-toll-us.html}{U.S.
  Deaths}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-testing.html}{Testing}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-nursing-homes.html}{Nursing
  homes}
\item
  \href{https://www.nytimes.com/interactive/2020/nyregion/new-york-city-coronavirus-cases.html}{New
  York City}
\item
  \href{https://www.nytimes.com/interactive/2020/us/states-reopen-map-coronavirus.html}{Reopening}
\item
  \href{https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html}{Vaccines}
\end{itemize}

Countries

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes.com/interactive/2020/world/americas/brazil-coronavirus-cases.html}{Brazil}
\item
  \href{https://www.nytimes.com/interactive/2020/world/canada/canada-coronavirus-cases.html}{Canada}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/france-coronavirus-cases.html}{France}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/germany-coronavirus-cases.html}{Germany}
\item
  \href{https://www.nytimes.com/interactive/2020/world/asia/india-coronavirus-cases.html}{India}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/italy-coronavirus-cases.html}{Italy}
\item
  \href{https://www.nytimes.com/interactive/2020/world/americas/mexico-coronavirus-cases.html}{Mexico}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/spain-coronavirus-cases.html}{Spain}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/united-kingdom-coronavirus-cases.html}{U.K.}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html}{United
  States}
\end{itemize}

State by state

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes.com/interactive/2020/us/alabama-coronavirus-cases.html}{Alabama}
\item
  \href{https://www.nytimes.com/interactive/2020/us/alaska-coronavirus-cases.html}{Alaska}
\item
  \href{https://www.nytimes.com/interactive/2020/us/arizona-coronavirus-cases.html}{Arizona}
\item
  \href{https://www.nytimes.com/interactive/2020/us/arkansas-coronavirus-cases.html}{Arkansas}
\item
  \href{https://www.nytimes.com/interactive/2020/us/california-coronavirus-cases.html}{California}
\item
  \href{https://www.nytimes.com/interactive/2020/us/colorado-coronavirus-cases.html}{Colorado}
\item
  \href{https://www.nytimes.com/interactive/2020/us/connecticut-coronavirus-cases.html}{Connecticut}
\item
  \href{https://www.nytimes.com/interactive/2020/us/delaware-coronavirus-cases.html}{Delaware}
\item
  \href{https://www.nytimes.com/interactive/2020/us/florida-coronavirus-cases.html}{Florida}
\item
  \href{https://www.nytimes.com/interactive/2020/us/georgia-coronavirus-cases.html}{Georgia}
\item
  \href{https://www.nytimes.com/interactive/2020/us/hawaii-coronavirus-cases.html}{Hawaii}
\item
  \href{https://www.nytimes.com/interactive/2020/us/idaho-coronavirus-cases.html}{Idaho}
\item
  \href{https://www.nytimes.com/interactive/2020/us/illinois-coronavirus-cases.html}{Illinois}
\item
  \href{https://www.nytimes.com/interactive/2020/us/indiana-coronavirus-cases.html}{Indiana}
\item
  \href{https://www.nytimes.com/interactive/2020/us/iowa-coronavirus-cases.html}{Iowa}
\item
  \href{https://www.nytimes.com/interactive/2020/us/kansas-coronavirus-cases.html}{Kansas}
\item
  \href{https://www.nytimes.com/interactive/2020/us/kentucky-coronavirus-cases.html}{Kentucky}
\item
  \href{https://www.nytimes.com/interactive/2020/us/louisiana-coronavirus-cases.html}{Louisiana}
\item
  \href{https://www.nytimes.com/interactive/2020/us/maine-coronavirus-cases.html}{Maine}
\item
  \href{https://www.nytimes.com/interactive/2020/us/maryland-coronavirus-cases.html}{Maryland}
\item
  \href{https://www.nytimes.com/interactive/2020/us/massachusetts-coronavirus-cases.html}{Massachusetts}
\item
  \href{https://www.nytimes.com/interactive/2020/us/michigan-coronavirus-cases.html}{Michigan}
\item
  \href{https://www.nytimes.com/interactive/2020/us/minnesota-coronavirus-cases.html}{Minnesota}
\item
  \href{https://www.nytimes.com/interactive/2020/us/mississippi-coronavirus-cases.html}{Mississippi}
\item
  \href{https://www.nytimes.com/interactive/2020/us/missouri-coronavirus-cases.html}{Missouri}
\item
  \href{https://www.nytimes.com/interactive/2020/us/montana-coronavirus-cases.html}{Montana}
\item
  \href{https://www.nytimes.com/interactive/2020/us/nebraska-coronavirus-cases.html}{Nebraska}
\item
  \href{https://www.nytimes.com/interactive/2020/us/nevada-coronavirus-cases.html}{Nevada}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-hampshire-coronavirus-cases.html}{New
  Hampshire}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-jersey-coronavirus-cases.html}{New
  Jersey}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-mexico-coronavirus-cases.html}{New
  Mexico}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-york-coronavirus-cases.html}{New
  York}
\item
  \href{https://www.nytimes.com/interactive/2020/us/north-carolina-coronavirus-cases.html}{North
  Carolina}
\item
  \href{https://www.nytimes.com/interactive/2020/us/north-dakota-coronavirus-cases.html}{North
  Dakota}
\item
  \href{https://www.nytimes.com/interactive/2020/us/ohio-coronavirus-cases.html}{Ohio}
\item
  \href{https://www.nytimes.com/interactive/2020/us/oklahoma-coronavirus-cases.html}{Oklahoma}
\item
  \href{https://www.nytimes.com/interactive/2020/us/oregon-coronavirus-cases.html}{Oregon}
\item
  \href{https://www.nytimes.com/interactive/2020/us/pennsylvania-coronavirus-cases.html}{Pennsylvania}
\item
  \href{https://www.nytimes.com/interactive/2020/us/puerto-rico-coronavirus-cases.html}{Puerto
  Rico}
\item
  \href{https://www.nytimes.com/interactive/2020/us/rhode-island-coronavirus-cases.html}{Rhode
  Island}
\item
  \href{https://www.nytimes.com/interactive/2020/us/south-carolina-coronavirus-cases.html}{South
  Carolina}
\item
  \href{https://www.nytimes.com/interactive/2020/us/south-dakota-coronavirus-cases.html}{South
  Dakota}
\item
  \href{https://www.nytimes.com/interactive/2020/us/tennessee-coronavirus-cases.html}{Tennessee}
\item
  \href{https://www.nytimes.com/interactive/2020/us/texas-coronavirus-cases.html}{Texas}
\item
  \href{https://www.nytimes.com/interactive/2020/us/utah-coronavirus-cases.html}{Utah}
\item
  \href{https://www.nytimes.com/interactive/2020/us/vermont-coronavirus-cases.html}{Vermont}
\item
  \href{https://www.nytimes.com/interactive/2020/us/virginia-coronavirus-cases.html}{Virginia}
\item
  \href{https://www.nytimes.com/interactive/2020/us/washington-coronavirus-cases.html}{Washington}
\item
  \href{https://www.nytimes.com/interactive/2020/us/washington-dc-coronavirus-cases.html}{Washington,
  D.C.}
\item
  \href{https://www.nytimes.com/interactive/2020/us/west-virginia-coronavirus-cases.html}{West
  Virginia}
\item
  \href{https://www.nytimes.com/interactive/2020/us/wisconsin-coronavirus-cases.html}{Wisconsin}
\item
  \href{https://www.nytimes.com/interactive/2020/us/wyoming-coronavirus-cases.html}{Wyoming}
\end{itemize}

Long-term care facility data is as of July 30 and will be updated
periodically. The New York Times's data is based on confirmed reports
from federal, state and local government sources, as well as facilities
themselves. The data may not match the numbers reported by any one
federal, state or local agency. The federal government, states, counties
and facilities report different portions of long-term care data, so
exercise caution when comparing facilities or aggregated data in
different states. The federal government and states frequently revise
their long-term care data up and down, for a variety of reasons.

By Matthew Conlen, Danielle Ivory, Karen Yourish, K.K. Rebecca Lai,
Adeel Hassan, Julia Calderone, Mitch Smith, Alex Lemonides, Jordan
Allen, Samone Blair, Maddie Burakoff, Sarah Cahalan, Zak Cassel, Matt
Craig, Yves De Jesus, Brandon Dupré, Timmy Facciola, Bianca Fortis,
Grace Gorenflo, Lauryn Higgins, Jake Holland, Ann Hinga Klein, Jacob
LaGesse, Alex Lim, Andrea Michelson, Jaylynn Moffat-Mowatt, Ashlyn
O'Hara, Miles McKinley, Lauren Messman, Paul Moon, Cierra S. Queen,
Thomas Rivas, Alison Saldanha, Alex Schwartz, Emily Schwing, Sarena
Snider, Alex Traub, Brandon Thorp, Alyssa Burr and Natasha Rodriguez

\textbf{Correction:}~June 27, 2020

An earlier version of this article misstated the formula for case
fatality rate. It is the number of deaths divided by the number of
cases, not the number of cases divided by the number of deaths.

\textbf{Correction:}~July 8, 2020

An earlier version of this article transposed the national case fatality
rate and the median case fatality rate in nursing homes. As of July 8,
the national case fatality rate was 4 percent and the median case
fatality rate~in~nursing homes~was 17 percent, not the other way around.

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
