Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/politics}{Politics}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/politics}{Politics}\textbar{}`Super PAC' Supporting
Donald Trump Makes First Ad Buy for General Election

\url{https://nyti.ms/1TUnWhz}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{super-pac-supporting-donald-trump-makes-first-ad-buy-for-general-election}{%
\section{`Super PAC' Supporting Donald Trump Makes First Ad Buy for
General
Election}\label{super-pac-supporting-donald-trump-makes-first-ad-buy-for-general-election}}

By \href{http://www.nytimes.com/by/nick-corasaniti}{Nick Corasaniti}

\begin{itemize}
\item
  June 7, 2016
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Rebuilding America PAC, one of the
\href{http://www.nytimes.com/aponline/2016/06/03/us/politics/ap-us-gop-2016-trump-money.html}{new
``super PACs'' that recently sprouted in support of Donald J. Trump},
has made its first advertising buy of the general election campaign,
reserving roughly \$1.1 million on national cable outlets, according to
two strategists with knowledge of the purchase.

The group, which released
\href{https://www.youtube.com/watch?v=9t54Ly_mvuk}{its first ad over the
weekend} tying Hillary Clinton's use of her private email to her
husband's past scandals, is being backed by Tom Barrack, a real estate
developer and an old friend of Mr. Trump. The group
\href{http://www.nytimes.com/2016/06/06/us/politics/trump-super-pac-alex-castellanos.html}{recently
hired Alex Castellanos}, a Republican strategist and ad maker.

Mr. Barrack said that the group had
\href{http://www.wsj.com/articles/real-estate-investor-tom-barrack-raised-32-million-for-super-pac-backing-donald-trump-1464924565?tesla=y}{raised
\$32 million}, but it has not yet filed its fund-raising report with the
Federal Election Commission.

The initial ad purchase is the first step in the group's plan to counter
an advertising blitz of more than \$90 million planned by Priorities USA
Action, the super PAC supporting Hillary Clinton.

It also is the first time Mr. Trump's candidacy will be supported in a
significant ad campaign since he became the presumptive Republican
nominee. Another group, Great America PAC, has been running
advertisements on
\href{http://www.nytimes.com/politics/first-draft/2016/04/06/super-pac-emerges-to-support-donald-trump-who-criticizes-such-groups/?version=meter+at+0\&module=meter-Links\&pgtype=Blogs\&contentId=\&mediaId=\&referrer=https\%3A\%2F\%2Fwww.google.com\%2F\&priority=true\&action=click\&contentCollection=meter-links-click}{select
DirecTV and Dish services}, but has also focused more on push polling
and fund-raising ads.

The ad is currently slotted to run only from June 9 through June 16, but
that period could be extended

Previously, Mr. Trump had eschewed any support of super PACs, telling
groups supporting him last year
\href{https://www.washingtonpost.com/news/post-politics/wp/2015/10/23/donald-trump-tells-super-pacs-supporting-his-candidacy-to-return-all-money-to-donors/}{to
return any donations to donors}. A major theme of his campaign for the
Republican nomination was a pledge to ``self-fund'' his bid to show he
couldn't be bought by the wealthy donors who pour millions of dollars
into super PACs.

But as his campaign has slowly made the transition toward the general
election, numerous super PACs have sprung up in support of the
candidate, and he hasn't made any effort to quash their existence. There
are
\href{http://blogs.wsj.com/washwire/2016/06/07/whos-who-meet-the-super-pacs-backing-donald-trump/}{currently
at least four super PACs} set up to help Mr. Trump win the general
election.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
