 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.} \textbar{}4
Ways Trump Is Weakening Obamacare, Even After Repeal Plan's Failure

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2vDytIK}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-us-}{%
\subsection{\texorpdfstring{
\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}
}{ U.S. }}\label{-us-}}

\hypertarget{4-ways-trump-is-weakening-obamacare-even-after-repeal-plans-failure}{%
\section{4 Ways Trump Is Weakening Obamacare, Even After Repeal Plan's
Failure}\label{4-ways-trump-is-weakening-obamacare-even-after-repeal-plans-failure}}

Senate Republicans' latest effort to repeal the Affordable Care Act
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/09/25/us/republicans-who-opposed-the-senate-health-care-bills.html}{has
collapsed}, but President Trump has already made moves to undermine
important provisions of the health law, and there is still more he could
do.

\begin{longtable}[]{@{}ll@{}}
\toprule
\textbf{What Trump can do} & \textbf{Status}\tabularnewline
\midrule
\endhead
Weaken enforcement of the individual mandate. & In
progress\tabularnewline
Impose work requirements for Medicaid recipients. & In
progress\tabularnewline
Fail to do advertising or outreach. & In progress\tabularnewline
Make tax credits for premiums less generous. & In
progress\tabularnewline
Defund subsidies that help people pay out-of-pocket costs. & A
possibility\tabularnewline
Redefine essential health benefits. & A possibility\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{in-progress}{%
\subsection{In progress}\label{in-progress}}

\hypertarget{1-weaken-enforcement-of-the-individual-mandate}{%
\subsection{\texorpdfstring{\emph{\textbf{1.}} \textbf{Weaken
enforcement of the individual
mandate.}}{1. Weaken enforcement of the individual mandate.}}\label{1-weaken-enforcement-of-the-individual-mandate}}

\hypertarget{how-this-would-hurt-obamacare-fewer-healthy-people-may-sign-up-for-insurance-driving-up-prices-for-those-who-need-it-most-like-older-people-and-the-sick}{%
\subsection{\texorpdfstring{\emph{How this would hurt Obamacare:} Fewer
healthy people may sign up for insurance, driving up prices for those
who need it most, like older people and the
sick.}{How this would hurt Obamacare: Fewer healthy people may sign up for insurance, driving up prices for those who need it most, like older people and the sick.}}\label{how-this-would-hurt-obamacare-fewer-healthy-people-may-sign-up-for-insurance-driving-up-prices-for-those-who-need-it-most-like-older-people-and-the-sick}}

The Affordable Care Act requires all Americans to buy health insurance
or pay a penalty, with exceptions for people with
\href{https://www.healthcare.gov/glossary/hardship-exemption/}{hardships}.

While Mr. Trump cannot eliminate the mandate, as Republicans in Congress
sought to do, the Internal Revenue Service has said it
\href{https://www.nytimes3xbfgragh.onion/2017/02/15/us/politics/affordable-care-act-obamacare-trump.html}{will
continue accepting tax returns} that do not say whether a filer has been
uninsured, weakening its enforcement of the provision.

The administration could also allow for more exceptions, making it
easier to avoid the tax penalty. It could instruct the I.R.S. to
scrutinize people's returns less closely. And it could signal publicly
that it does not care about the mandate, which may cause people to be
less likely to sign up, even if they later get hit with a tax penalty.

\hypertarget{in-progress-1}{%
\subsection{In progress}\label{in-progress-1}}

\hypertarget{2-impose-work-requirements-for-medicaid-recipients}{%
\subsection{\texorpdfstring{\emph{\textbf{2.}} \textbf{Impose work
requirements for Medicaid
recipients.}}{2. Impose work requirements for Medicaid recipients.}}\label{2-impose-work-requirements-for-medicaid-recipients}}

\hypertarget{how-this-would-hurt-obamacare-many-people-who-gained-coverage-through-medicaid-expansion-may-not-be-able-to-afford-insurance-or-participate-in-the-program}{%
\subsection{\texorpdfstring{\emph{How this would hurt Obamacare:} Many
people who gained coverage through Medicaid expansion may not be able to
afford insurance or participate in the
program.}{How this would hurt Obamacare: Many people who gained coverage through Medicaid expansion may not be able to afford insurance or participate in the program.}}\label{how-this-would-hurt-obamacare-many-people-who-gained-coverage-through-medicaid-expansion-may-not-be-able-to-afford-insurance-or-participate-in-the-program}}

Under the Affordable Care Act, 31 states expanded Medicaid coverage to
poor adults who were previously uncovered. And Republicans in Congress
sought to sharply curtail federal support for the expansion, likely
causing many states to end it.

Mr. Trump cannot unilaterally prevent states from expanding Medicaid in
the future. He could, however, allow states that apply to impose work
requirements or charge premiums for more Medicaid beneficiaries, through
a process that lets the government waive the normal Medicaid rules.
Those changes might make it difficult for as many poor Americans to
access the system.

In March, the Health and Human Services Department said it would be open
to states'
\href{https://www.hhs.gov/healthcare/empowering-patients/providing-relief-right-now-for-patients/making-medicaid-work-for-patients-and-states/index.html}{proposing
work requirements} for Medicaid recipients.

\hypertarget{in-progress-2}{%
\subsection{In progress}\label{in-progress-2}}

\hypertarget{3-fail-to-do-advertising-or-outreach}{%
\subsection{\texorpdfstring{\emph{\textbf{3.}} \textbf{Fail to do
advertising or
outreach.}}{3. Fail to do advertising or outreach.}}\label{3-fail-to-do-advertising-or-outreach}}

\hypertarget{how-this-would-hurt-obamacare-without-outreach-the-number-of-americans-who-learn-about-the-affordable-care-act-and-sign-up-for-coverage-could-dwindle}{%
\subsection{\texorpdfstring{\emph{How this would hurt Obamacare:}
Without outreach, the number of Americans who learn about the Affordable
Care Act and sign up for coverage could
dwindle.}{How this would hurt Obamacare: Without outreach, the number of Americans who learn about the Affordable Care Act and sign up for coverage could dwindle.}}\label{how-this-would-hurt-obamacare-without-outreach-the-number-of-americans-who-learn-about-the-affordable-care-act-and-sign-up-for-coverage-could-dwindle}}

The Trump administration said in August that it would
\href{https://www.nytimes3xbfgragh.onion/2017/08/31/health/affordable-care-act-trump-spending.html}{slash
spending on advertising and promotion} for enrollment to \$10 million
from \$100 million. It also said it would cut funding, by about 40
percent, to groups that help people enroll.

The Department of Health and Human Services, which is in charge of
administering the health law, has also been waging a
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/09/04/us/hhs-anti-obamacare-campaign.html?mcubz=0}{multipronged}\href{https://www.nytimes3xbfgragh.onion/interactive/2017/09/04/us/hhs-anti-obamacare-campaign.html?mcubz=0}{media
campaign} to undermine it, using videos, Twitter posts and the agency's
website.

The last sign-up period for the Affordable Care Act ended 11 days after
\href{https://www.nytimes3xbfgragh.onion/2017/01/20/us/politics/trump-inauguration-day.html}{Mr.
Trump was inaugurated}. During the those final days of enrollment, the
Trump administration
\href{https://www.nytimes3xbfgragh.onion/2017/01/26/us/politics/donald-trump-obamacare-ads.html?rref=collection\%2Fbyline\%2Frobert-pear\&action=click\&contentCollection=undefined\&region=stream\&module=stream_unit\&version=latest\&contentPlacement=5\&pgtype=collection}{pulled
advertisements and outreach} off the air that encouraged people to sign
up for health insurance under the law.

In the last few years, large number of consumers generally signed up
just before the deadline, and sign-ups for health plans in states
managed by the federal government were down slightly compared to the
same period the previous year. Lower signups tend to mean higher prices,
since the sickest customers are more likely to investigate their
insurance options, regardless of government outreach.

\hypertarget{in-progress-3}{%
\subsection{In progress}\label{in-progress-3}}

\hypertarget{4-make-tax-credits-for-premiums-less-generous}{%
\subsection{\texorpdfstring{\emph{\textbf{4.}} \textbf{Make tax credits
for premiums less
generous.}}{4. Make tax credits for premiums less generous.}}\label{4-make-tax-credits-for-premiums-less-generous}}

\hypertarget{how-this-would-hurt-obamacare-many-customers-may-end-up-with-plans-with-higher-deductibles-and-co-payments}{%
\subsection{\texorpdfstring{\emph{How this would hurt Obamacare:} Many
customers may end up with plans with higher deductibles and
co-payments.}{How this would hurt Obamacare: Many customers may end up with plans with higher deductibles and co-payments.}}\label{how-this-would-hurt-obamacare-many-customers-may-end-up-with-plans-with-higher-deductibles-and-co-payments}}

The Affordable Care Act gives tax credits to middle-income Americans to
offset the cost of premiums. Those subsidies are based on a particular
plan, meant to cover 70 percent of the average customer's medical bills.

The administration put in place a
\href{https://www.cms.gov/Newsroom/MediaReleaseDatabase/Press-releases/2017-Press-releases-items/2017-04-13-2.html}{new
rule} that in 2018 will make the credits apply to a slightly less
generous plan for all Obamacare customers. The size of the changes will
be much smaller than reductions that had been proposed in the Republican
health care bills. But many customers will end up with either more
expensive insurance or plans that have higher deductibles and
co-payments in 2018.

\hypertarget{a-possibility}{%
\subsection{A possibility}\label{a-possibility}}

\hypertarget{5-defund-subsidies-that-help-people-pay-out-of-pocket-costs}{%
\subsection{\texorpdfstring{\emph{\textbf{5.}} \textbf{Defund subsidies
that help people pay out-of-pocket
costs.}}{5. Defund subsidies that help people pay out-of-pocket costs.}}\label{5-defund-subsidies-that-help-people-pay-out-of-pocket-costs}}

\hypertarget{how-this-would-hurt-obamacare-insurance-companies-would-take-a-big-financial-hit-since-they-assumed-they-would-get-the-subsidies-when-pricing-their-plans}{%
\subsection{\texorpdfstring{\emph{How this would hurt Obamacare:}
Insurance companies would take a big financial hit, since they assumed
they would get the subsidies when pricing their
plans.}{How this would hurt Obamacare: Insurance companies would take a big financial hit, since they assumed they would get the subsidies when pricing their plans.}}\label{how-this-would-hurt-obamacare-insurance-companies-would-take-a-big-financial-hit-since-they-assumed-they-would-get-the-subsidies-when-pricing-their-plans}}

Obamacare provides subsidies to help insurance companies reduce
out-of-pocket costs, like deductibles and co-payments, for lower-income
customers. Insurance companies price their plans assuming payments will
be based on how many eligible customers they serve. The House and Senate
health bills would have eliminated the subsidies, allowing insurers to
charge those customers higher deductibles.

Mr. Trump could effectively defund the subsidies if he
\href{https://www.nytimes3xbfgragh.onion/2017/03/24/upshot/trumps-choice-on-obamacare-sabotage-or-co-opt.html}{stops
the appeal of a lawsuit} that was started under the Obama
administration. President Barack Obama's lawyers had appealed a court
ruling that said the subsidy payments were made without proper
congressional authority.

Removing the subsidies this year would cause insurers to lose money
right away, and it could create substantial financial distress for
smaller insurers. On Wednesday, insurers must sign final contracts for
2018 policies. Because of the uncertainty, many have increased their
prices and some have decided to exit the market, reducing consumer
choices.

The White House has
\href{https://www.nytimes3xbfgragh.onion/2017/07/18/upshot/obamacares-future-now-depends-on-an-unhappy-white-house.html}{declined
to say} whether it will continue to pay the subsidies.

\hypertarget{a-possibility-1}{%
\subsection{A possibility}\label{a-possibility-1}}

\hypertarget{6-redefine-essential-health-benefits}{%
\subsection{\texorpdfstring{\emph{\textbf{6.}} \textbf{Redefine
essential health
benefits.}}{6. Redefine essential health benefits.}}\label{6-redefine-essential-health-benefits}}

\hypertarget{how-this-would-hurt-obamacare-customers-with-health-problems-may-end-up-with-really-high-insurance-costs}{%
\subsection{\texorpdfstring{\emph{How this would hurt Obamacare:}
Customers with health problems may end up with really high insurance
costs.}{How this would hurt Obamacare: Customers with health problems may end up with really high insurance costs.}}\label{how-this-would-hurt-obamacare-customers-with-health-problems-may-end-up-with-really-high-insurance-costs}}

Under the current law, all insurers must offer
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/03/24/us/essential-health-benefits.html}{10
categories of essential health benefits}, like maternity treatment and
hospital care. Conservatives considered the requirements too
restrictive.

Congress tried to loosen these rules by letting states apply to waive
them. Republicans in the Senate also tried to let insurers get away with
offering plans that don't meet the rules as long as they offered ones
that did.

Mr. Trump cannot eliminate the 10 broad categories of benefits, but his
administration has some discretion on how the categories are defined.

For example, the administration could redefine preventive care in a way
that eliminates a current rule requiring insurers to cover every form of
contraception that is approved by the Food and Drug Administration.

Sources: Kaiser Family Foundation; Brookings Institution; Nicholas
Bagley, University of Michigan Law School

Additional work by Wilson Andrews.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
