Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/movies}{Movies}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/movies}{Movies}\textbar{}`Scoop': Shades of Nick and
Nora, With Woody Allen's Shtick

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

Movie Review

\hypertarget{scoop-shades-of-nick-and-nora-with-woody-allens-shtick}{%
\section{`Scoop': Shades of Nick and Nora, With Woody Allen's
Shtick}\label{scoop-shades-of-nick-and-nora-with-woody-allens-shtick}}

\begin{itemize}
\tightlist
\item
  Scoop\\
  **NYT Critic's Pick Directed by Woody Allen Comedy, Crime, Mystery
  PG-13 1h 36m
\end{itemize}

By \href{https://www.nytimes3xbfgragh.onion/by/manohla-dargis}{Manohla
Dargis}

\begin{itemize}
\item
  July 28, 2006
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

IN ``Scoop,'' his not especially funny yet oddly appealing new comedy,
Woody Allen manages to act his age and prove there's life in those old
jokes yet. Like his last outing, the pitch-black drama ``Match Point,''
the new one revisits a number of Mr. Allen's favorite themes, including
money, conscience and luscious young women ripe for the plucking, this
time for laughs. As in the earlier film, Scarlett Johansson plays the
succulent morsel, though with a performance set in the key of screwball
rather than noir. Her sweaters are looser, as is her smile. The film, in
turn, is positively slack, which turns out to be one of its virtues.

The casting of Ms. Johansson and the announcement that Mr. Allen would
return to the front of the camera were worrisome. He had stayed out of
sight for ``Match Point,'' which was largely sold on its leads and its
enthusiastic reviews. The name of its writer and director was
conspicuously played down in the advertisements, the consequence of the
string of flops he had lately churned out. With its fierce performances
and writing, ``Match Point'' proved very much a return to fine form, if
not for the comic Woody Allen, then for the serious Woody Allen, the one
who didn't try to hide his misanthropy, his fear and his loathing behind
jokes and shtick. Another plus: he wasn't in the film groping the
starlet.

Relax. Mr. Allen doesn't manhandle Ms. Johansson, though his camera
tends to linger appreciatively over her form. In her role as Sondra
Pransky, an American journalism student in London, Ms. Johansson tends
to wear roomy, almost dowdy clothes, the exception being a screaming-red
maillot that she fills out beautifully, bringing to mind Cathy Moriarty
baking under the sun and Robert De Niro's hotter gaze in ``Raging
Bull.'' Sondra is more the Nancy Drew type, particularly when dressed
and wearing her glasses, though she is also the kind of girl reporter
who thinks nothing of sleeping with her interviewees to get the story.
Nancy Drew probably didn't go past first base, but neither did she chase
ghosts and aristocrats while running with a magician called Splendini.

The premise of ``Scoop'' sounds like the windup to a joke: a journalist
walks into a magician's trick closet, where she meets an actual ghost,
and --- presto, changeo --- walks out with a news lead of a lifetime.
The ghost, a recently deceased journalist, Joe Strombel (Ian McShane),
believing he knows the identity of a serial killer on the hunt, gives
Sondra the scoop. This, in turn, leads to an affectionately testy
partnership with Splendini, a k a Sid Waterman (Mr. Allen, of course),
and, through some twists and turns, to Peter Lyman (Hugh Jackman), an
aristocrat who enters the thick of things after making an acquaintance
with that screaming-red bathing suit. None of it makes much sense, but,
like slackness, nonsense proves a virtue here.

Mr. Allen doesn't seem to be working terribly hard in ``Scoop,'' and
while that makes for some apparent goofs and lots of ragged edges, it
gives the whole thing a pleasantly carefree vibe. After the first 20 or
so clunky minutes, the film settles into a groove and then, ever so
slightly, deepens. Mr. Allen's invocation of the ``Thin Man'' films in
an interview makes sense, even if he's no William Powell and Ms.
Johansson is certainly no Myrna Loy. ``Scoop'' was made by someone who
understands that what makes the ``Thin Man'' series enduring isn't
whodunit and why, but the way Nick and Nora look at each other as they
sip their martinis, Asta nipping at their heels.

Image

From left, Hugh Jackman, Scarlett Johansson and Woody Allen in
``Scoop,'' a comic murder mystery.Credit...Clive Coote

Sondra and Sid do all the nipping here, playfully tossing insults at
each other. Mr. Allen's apparent realization, at long last, that neither
his diehard fans nor more agnostic viewers want to watch him paw a much
younger woman does wonders. It not only removes the distracting ``eew''
factor, it also allows him to settle into a more paternal role, which he
does with persuasive naturalness.

More important, it also means ``Scoop'' isn't just another one of those
narcissistic revues in which a Woody Allen-like character, sometimes
played by the filmmaker himself, sometimes by an unsettling surrogate
(Kenneth Branagh, Will Ferrell and so on), gobbles up the screen, the
woman, our attention and our presumed love. In ``Scoop'' he has to
share, and he does.

That Mr. Allen has opted to share the limelight with an actress he is
content to look at but not touch adds an interesting kink to what may be
an entire new chapter in his life's work. Just barely out of her teens,
Ms. Johansson has yet to learn how to control either the husk in her
voice or that lovely lush body, which makes for moments both charmingly
awkward and just awkward. Mr. Allen is a famously reticent director, at
least when it comes to his actors, who often seem to direct themselves.
Ms. Johansson's performance is all over the place in ``Scoop,'' but
finally works for a film that is itself all over the place. Mr. Allen
seems happy to just watch her strut her stuff, and after a while so are
we.

\emph{``Scoop'' is rated PG-13 (Parents strongly cautioned). There's a
murder subplot, but it's all very gentle.}

\textbf{SCOOP}

\emph{Opens today nationwide.}

Written and directed by Woody Allen; director of photography, Remi
Adefarasin; edited by Alisa Lepselter; production designer, Maria
Djurkovic; produced by Letty Aronson and Gareth Wiley; released by Focus
Features. Running time: 96 minutes.

WITH: Woody Allen (Sid Waterman), Hugh Jackman (Peter Lyman), Scarlett
Johansson (Sondra Pransky) and Ian McShane (Joe Strombel).

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
