 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{/news-event/2020-election}{Elections} \textbar{}2018 Midterm
Election Results

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2G6a8l4}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-elections-}{%
\subsection{\texorpdfstring{ \href{/news-event/2020-election}{Elections}
}{ Elections }}\label{-elections-}}

\hypertarget{2018-midterm-election-results}{%
\section{2018 Midterm Election
Results}\label{2018-midterm-election-results}}

Follow live election results from The New York Times

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-house-elections.html}{House}
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-senate-elections.html}{Senate}
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/06/us/elections/results-governor-elections.html}{Governor}

The 2018 midterm elections, which featured hundreds of congressional,
state and local primaries, culminated with the Nov. 6 general election.
Democrats gained control of the House while Republicans kept power in
the Senate.

\hypertarget{upcoming-elections}{%
\subsection{Upcoming Elections}\label{upcoming-elections}}

Nov. 27

Elections near you

Mississippi special Senate runoff election

Voters will decide the outcome of the
\href{https://www.nytimes3xbfgragh.onion/elections/results/mississippi-senate-special}{special
Senate race}, which forced a runoff election when no candidate won a
majority of the vote on Nov. 6.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/11/27/us/elections/results-mississippi-senate-runoff-special-election.html}{Full
results »}

Dec. 4

Elections near you

Georgia runoff election for state and local offices

A runoff election for federal offices is set for Jan. 8, 2019.

Dec. 8

Elections near you

Louisiana general election

\hypertarget{past-elections}{%
\subsection{Past Elections}\label{past-elections}}

Feb. 27

Elections near you

Arizona special House primaries

The Republican Debbie Lesko and the Democrat Hiral Tipirneni
\href{https://www.nytimes3xbfgragh.onion/2018/03/28/us/arizona-race-trump-stormy-daniels-lesko-tipirneni.html}{advanced
to the general election} on April 24. The seat, which Ms. Lesko went on
to win, had been vacated when Representative Trent Franks resigned over
\href{https://www.nytimes3xbfgragh.onion/2017/12/08/us/politics/trent-franks-sexual-surrogacy-harassment.html}{sexual
misconduct accusations.}

\href{https://www.nytimes3xbfgragh.onion/elections/results/arizona-house-special-election-primary}{Full
results »}

March 6

Elections near you

Texas primaries

Senate: Ted Cruz is up for re-election.

House:

4 out of 36 races are competitive in the general election.

Texas Democrats surged to the polls, demonstrating a wave of
Trump-inspired energy, but also revealing internal divisions at the
outset of a midterm campaign that looks otherwise promising to the
party.
\href{https://www.nytimes3xbfgragh.onion/2018/03/07/us/politics/texas-primary-race-trump.html}{Read
more about the primaries}.

\href{https://www.nytimes3xbfgragh.onion/elections/results/texas-primary-election}{Full
results »}

March 13

Elections near you

Pennsylvania special House general election

Conor Lamb, a Democrat and former Marine,
\href{https://www.nytimes3xbfgragh.onion/2018/03/14/us/politics/democrats-republicans-pennsylvania-special-election.html}{scored
a razor-thin but extraordinary upset} in a special House election in
southwestern Pennsylvania, in the heart of President Trump's Rust Belt
base. The State Supreme Court
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/02/19/upshot/pennsylvania-new-house-districts-gerrymandering.html}{recently
issued a new map} with redrawn boundaries, though, so Mr. Lamb
\href{https://www.nytimes3xbfgragh.onion/2018/03/30/us/midterm-elections-pennsylvania.html}{ran
in a different district} in May.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/03/13/us/elections/results-pennsylvania-house-special-election.html}{Full
results »}

March 20

Elections near you

Illinois primaries

House:

4 out of 18 races are competitive in the general election.

Gov. Bruce Rauner, a Republican first-term incumbent, and J.B. Pritzker,
a Democratic billionaire heir and businessman,
\href{https://www.nytimes3xbfgragh.onion/2018/03/20/us/politics/bruce-rauner-governor-illinois.html}{emerged
from the gubernatorial primaries}, while the incumbent in a closely
watched Democratic congressional primary overcame a progressive
challenge. The governor's race promises to be be fiercely fought and
dominated by big money, with each candidate controlling tremendous sums
of personal wealth.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/03/20/us/elections/results-illinois-primary-elections.html}{Full
results »}

April 24

Elections near you

Arizona special House general election

Debbie Lesko, a Republican former state senator, fended off an unusually
strong Democratic challenge to win a special election in the Eighth
District, near Phoenix. Her victory demonstrated the resilience of the
Republican base, but also showed how eager liberals are to compete even
in reliably conservative districts.
\href{https://www.nytimes3xbfgragh.onion/2018/04/24/us/politics/debbie-lesko-arizona-congress.html}{Read
more}.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/04/24/us/elections/results-arizona-house-special-election.html}{Full
results »}

May 8

Three vulnerable Democratic senators run for re-election.

Elections near you

Indiana primaries

Senate: Joe Donnelly is up for re-election.

Mr. Donnelly, who is believed to be
\href{https://www.nytimes3xbfgragh.onion/2017/10/20/us/politics/trump-donnelly-reelection.html}{one
of the most vulnerable Democrats in the Senate}, will face Mike Braun, a
business executive who won the
\href{https://www.nytimes3xbfgragh.onion/2018/04/02/us/politics/republican-senate-primary-fights-indiana.html}{bruising
Republican primary}, in November.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/08/us/elections/results-indiana-primary-elections.html}{Full
results »}

Elections near you

North Carolina primaries

House:

3 out of 13 races are competitive in the general election.

Mark Harris, a Baptist minister who opposes same-sex marriage,
\href{https://www.nytimes3xbfgragh.onion/2018/05/09/us/politics/mark-harris-north-carolina-republican-pittenger.html}{defeated
Representative Robert Pittenger} in a Republican primary, making Mr.
Pittenger the first incumbent from either party to lose a seat in
Congress because of a primary challenger this year.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/08/us/elections/results-north-carolina-primary-elections.html}{Full
results »}

Elections near you

Ohio primaries

Senate: Sherrod Brown is up for re-election.

House:

2 out of 16 races are competitive in the general election.

The race to succeed Gov. John Kasich will be a bruising national fight
because the nominees --- Attorney General Mike DeWine, a Republican, and
Richard Cordray,
\href{https://www.nytimes3xbfgragh.onion/2018/04/29/us/politics/ohio-governor-richard-cordray-dennis-kucinich.html}{a
consumer advocate and Democrat} --- are ideological opposites.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/08/us/elections/results-ohio-primary-elections.html}{Full
results »}

Elections near you

West Virginia primaries

Senate: Joe Manchin III is up for re-election.

House:

1 out of 3 races is competitive in the general election.

Mr. Manchin,
\href{https://www.nytimes3xbfgragh.onion/2018/01/23/us/politics/manchin-reelection-this-place-sucks.html}{a
Democrat in a red state that Mr. Trump won handily}, will face Attorney
General Patrick Morrisey, a Republican, in the general election. Mr.
Morrisey defeated Don Blankenship,
\href{https://www.nytimes3xbfgragh.onion/2018/04/25/us/politics/don-blankenship-china-west-virginia.html}{a
former coal mining executive who spent a year in prison for his role in
a fatal mining explosion}, and Representative Evan Jenkins in the
primary.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/08/us/elections/results-west-virginia-primary-elections.html}{Full
results »}

May 15

Elections near you

Idaho primaries

Lt. Gov. Brad Little won the Republican nomination to replace the
three-term incumbent Butch Otter, who is retiring. Mr. Little is
expected to easily win the general election in November.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/15/us/elections/results-idaho-primary-elections.html}{Full
results »}

Elections near you

Nebraska primaries

Senate: Deb Fischer is up for re-election.

House:

1 out of 3 races is competitive in the general election.

Kara Eastman, a liberal Democrat, narrowly won the primary to challenge
Representative Don Bacon, a Republican, in what is expected to be a
competitive race in November. The Democratic primary focused heavily on
abortion, with Ms. Eastman supporting abortion rights and her opponent,
Brad Ashford, supporting more restrictions.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/15/us/elections/results-nebraska-primary-elections.html}{Full
results »}

Elections near you

Oregon primaries

State Representative Knute Buehler defeated nine other Republicans in
Oregon's gubernatorial primary and will face Gov. Kate Brown, a
Democrat, in November. The seat is considered safe for Democrats.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/15/us/elections/results-oregon-primary-elections.html}{Full
results »}

Elections near you

Pennsylvania primaries

Senate: Bob Casey is up for re-election.

House:

4 out of 18 races are competitive in the general election.

The first test of Pennsylvania's redrawn congressional districts
resulted in
\href{https://www.nytimes3xbfgragh.onion/2018/05/15/us/politics/pennsylvania-primaries.html}{primary
victories for several Democratic women}. The new map is
\href{https://www.nytimes3xbfgragh.onion/2018/02/21/upshot/gerrymandering-pennsylvania-democrats-republicans-court.html}{more
favorable to Democrats than even the Democrats expected}, and the party
could well pick up four or more seats here in November.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/15/us/elections/results-pennsylvania-primary-elections.html}{Full
results »}

May 22

Elections near you

Georgia primaries

House:

2 out of 14 races are competitive in the general election.

Stacey Abrams, a Democratic former State House leader, became Georgia's
first black nominee for governor, a prize that has eluded earlier
generations of African-American candidates in the state. Her candidacy
will test just how much the state's traditionally conservative politics
are shifting.
\href{https://www.nytimes3xbfgragh.onion/2018/05/22/us/politics/georgia-primary-abrams-results.html}{Read
more here.}

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/22/us/elections/results-georgia-primary-elections.html}{Full
results »}

Elections near you

Kentucky primaries

House:

1 out of 6 races is competitive in the general election.

In the Democratic primary to challenge Representative Andy Barr, Amy
McGrath, a former Marine fighter pilot running for office for the first
time,
\href{https://www.nytimes3xbfgragh.onion/2018/05/22/us/politics/kentucky-election-mcgrath.html}{upset
national Democrats' candidate of choice}, Mayor Jim Gray of Lexington.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/22/us/elections/results-kentucky-primary-elections.html}{Full
results »}

Elections near you

Arkansas primaries

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/22/us/elections/results-arkansas-primary-elections.html}{Full
results »}

Elections near you

Texas primaries runoff

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/05/22/us/elections/results-texas-primary-runoff-elections.html}{Full
results »}

June 5

Democrats look to swing seats in California and New Jersey.

Elections near you

California primaries

Senate: Dianne Feinstein is up for re-election.

House:

6 out of 53 races are competitive in the general election.

Gavin Newsom, the Democratic lieutenant governor, and John Cox, a
Republican businessman, emerged from a crowded field in the governor's
race in California to advance to the general election, as did Ms.
Feinstein, a Democrat, in the Senate race. In key House districts they
hope to capture in November, Democrats avoided being shut out of the
general election under the state's ``top two" primary system. Read more
about
\href{https://www.nytimes3xbfgragh.onion/2018/06/06/us/politics/california-primary.html}{the
primary night in California}.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-california-primary-elections.html}{Full
results »}

Elections near you

Mississippi primaries

Senate: Roger Wicker is up for re-election.

Senator Thad Cochran's decision to retire set off a game of musical
chairs. Instead of Senator Roger Wicker having to defending his seat
from a major rival in a Republican primary in June, the state's big
battle is expected in November, when there will be a special election to
finish Mr. Cochran's term. Chris McDaniel, a state senator who almost
unseated Mr. Cochran in 2014 and had
\href{https://www.nytimes3xbfgragh.onion/2018/02/26/us/politics/mississippi-mcdaniel-wicker-primary-fight.html}{previously
decided to challenge} Mr. Wicker,
\href{https://www.nytimes3xbfgragh.onion/2018/03/16/us/politics/bannon-republican-senate-primary-challengers.html}{will
run}
\href{https://www.nytimes3xbfgragh.onion/2018/03/20/us/politics/mississippi-senate-appointee-trump.html}{in
a growing field} for Mr. Cochran's seat instead. Mr. Wicker won his
primary handily in this deeply red state.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-mississippi-primary-elections.html}{Full
results »}

Elections near you

Montana primaries

Senate: Jon Tester is up for re-election.

House:

1 race is competitive in the general election.

Republicans nominated their state auditor, Matt Rosendale, a Maryland
native, to challenge Senator Jon Tester, one of the nation's most
vulnerable Democrats.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-montana-primary-elections.html}{Full
results »}

Elections near you

New Jersey primaries

Senate: Robert Menendez is up for re-election.

House:

3 out of 12 races are competitive in the general election.

A former Navy pilot, a veteran White House national security adviser and
a conservative pro-gun state senator won Democratic nominations to
represent battleground congressional districts in New Jersey, officially
earning their spots on the front lines in a state that could determine
control of the House.
\href{https://www.nytimes3xbfgragh.onion/2018/06/05/us/politics/primary-elections-new-jersey.html}{Read
more in our analysis}.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-new-jersey-primary-elections.html}{Full
results »}

Elections near you

New Mexico primaries

Senate: Martin Heinrich is up for re-election.

House:

1 out of 3 races is competitive in the general election.

Representative Michelle Lujan Grisham, who prevailed in the Democratic
primary for governor, will face Steve Pearce, a Republican congressman,
in the general election. If Ms. Lujan Grisham were elected, she would be
the first Latina Democratic governor in the United States, replacing
Gov. Susana Martinez, a term-limited Republican who is also Latina.
\href{https://www.nytimes3xbfgragh.onion/2018/06/05/us/politics/primary-elections-new-jersey.html}{Read
more here}.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-new-mexico-primary-elections.html}{Full
results »}

Elections near you

Alabama primaries

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-alabama-primary-elections.html}{Full
results »}

Elections near you

Iowa primaries

House:

3 out of 4 races are competitive in the general election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-iowa-primary-elections.html}{Full
results »}

Elections near you

South Dakota primaries

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/05/us/elections/results-south-dakota-primary-elections.html}{Full
results »}

June 12

Elections near you

Nevada primaries

Senate: Dean Heller is up for re-election.

House:

2 out of 4 races are competitive in the general election.

The Senate race is expected to be one of the most competitive in
November, but the primaries were quiet. Representative Jacky Rosen, a
Democrat, and Senator Dean Heller, a Republican, both easily won their
respective nominations.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/12/us/elections/results-nevada-primary-elections.html}{Full
results »}

Elections near you

South Carolina primaries

House:

1 out of 7 races is competitive in the general election.

In one of the biggest upsets so far this year, Representative Mark
Sanford, a Republican former governor once seen as a possible
presidential candidate,
\href{https://www.nytimes3xbfgragh.onion/2018/06/12/us/politics/primary-south-carolina-virginia-nevada.html}{lost
to a conservative primary challenger, Katie Arrington}.
\href{https://www.nytimes3xbfgragh.onion/2018/06/12/us/politics/mark-sanford-trump.html}{Read
more}.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/12/us/elections/results-south-carolina-primary-elections.html}{Full
results »}

Elections near you

Virginia primaries

Senate: Tim Kaine is up for re-election.

House:

4 out of 11 races are competitive in the general election.

Corey Stewart, a Republican
\href{https://www.nytimes3xbfgragh.onion/2018/06/17/us/politics/corey-stewart-virginia.html}{who
has defended the Confederacy and praised white nationalists}, won his
primary and will face Senator Tim Kaine, a Democrat, in November.
Republican officials are worried that his primary victory
\href{https://www.nytimes3xbfgragh.onion/2018/06/13/us/corey-stewart-virginia-republicans.html}{may
hurt down-ballot candidates}.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/12/us/elections/results-virginia-primary-elections.html}{Full
results »}

Elections near you

Maine primaries

Senate: Angus King is up for re-election.

House:

1 out of 2 races is competitive in the general election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/12/us/elections/results-maine-primary-elections.html}{Full
results »}

Elections near you

North Dakota primaries

Senate: Heidi Heitkamp is up for re-election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/12/us/elections/results-north-dakota-primary-elections.html}{Full
results »}

June 19

Elections near you

District of Columbia primaries

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/19/us/elections/results-district-of-columbia-primary-election.html}{Full
results »}

Elections near you

Arkansas primaries runoff

June 26

New York Democrats are energized to run in Republican-held districts.

Elections near you

New York primaries

Senate: Kirsten Gillibrand is up for re-election.

House:

5 out of 27 races are competitive in the general election.

In a major upset, Alexandria Ocasio-Cortez, a 28-year-old former Bernie
Sanders campaign organizer,
\href{https://www.nytimes3xbfgragh.onion/2018/06/27/nyregion/alexandria-ocasio-cortez-bio-profile.html}{defeated
longtime congressman} and Democratic leader Joseph Crowley in the
primary for a House district in the Bronx and Queens.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/26/us/elections/results-new-york-primary-elections.html}{Full
results »}

Elections near you

Colorado primaries

House:

1 out of 7 races is competitive in the general election.

Four candidates from each party ran for Colorado's open governorship, in
a race that will test whether social and economic changes are turning
Colorado more reliably blue. The state's 1.2 million independent voters
were able to participate in party primaries for the first time.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/26/us/elections/results-colorado-primary-elections.html}{Full
results »}

Elections near you

Maryland primaries

Senate: Benjamin L. Cardin is up for re-election.

Chelsea Manning, a former Army private convicted of disclosing
classified information, lost in the Democratic primary against Mr.
Cardin.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/26/us/elections/results-maryland-primary-elections.html}{Full
results »}

Elections near you

Oklahoma primaries

Mick Cornett won the Republican gubernatorial primary and will aim to
replace Gov. Mary Fallon, who has reached her term limit.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/26/us/elections/results-oklahoma-primary-elections.html}{Full
results »}

Elections near you

Utah primaries

Senate: The Senate race is open. (Senator Orrin G. Hatch is not seeking
re-election.)

House:

1 out of 4 races is competitive in the general election.

Mitt Romney, a former Republican presidential candidate and a critic of
Mr. Trump, cruised to victory in the primary.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/26/us/elections/results-utah-primary-elections-ul.html}{Full
results »}

Elections near you

South Carolina primaries runoff

Gov. Henry McMaster, a Republican who has aligned himself closely with
President Trump, defeated the businessman John Warren after being forced
into a primary runoff.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/26/us/elections/results-south-carolina-primary-runoff-elections.html}{Full
results »}

Elections near you

Mississippi primaries runoff

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/26/us/elections/results-mississippi-primary-runoff-elections.html}{Full
results »}

June 30

Elections near you

Texas special House election

A Republican, Michael Cloud, won the special election in Texas for the
Congressional seat of Blake Farenthold, a Republican who resigned in
April amid a sexual harassment scandal.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/30/us/politics/election-results-texas-house-district-27.html}{Full
results »}

July 17

Elections near you

Alabama primaries runoff

Representative Martha Roby
\href{https://www.nytimes3xbfgragh.onion/2018/07/17/us/politics/martha-roby-alabama-primary.html}{won
her Republican primary election} that unfolded as a test of fealty to
President Trump, defeating a challenger who assailed her for withdrawing
her support for Mr. Trump in the last days of the 2016 campaign.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/07/17/us/elections/results-alabama-primary-runoff-elections.html}{Full
results »}

July 24

Elections near you

Georgia primaries runoff

Brian Kemp, Georgia's secretary of state,
\href{https://www.nytimes3xbfgragh.onion/2018/07/24/us/politics/kemp-cagle-georgia.html}{captured
the Republican nomination for governor}, easily dispatching the
preferred candidate of the state party establishment after a series of
provocative ads that evoked President Trump's incendiary politics and a
well-timed endorsement from the president himself.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/07/24/us/elections/results-georgia-primary-runoff-elections.html}{Full
results »}

Aug. 2

Elections near you

Tennessee primaries

Senate: The Senate race is open. (Senator Bob Corker is not seeking
re-election.)

Bill Lee, a wealthy businessman,
\href{https://www.nytimes3xbfgragh.onion/2018/08/02/us/politics/tennessee-primary.html}{won
the Republican nomination for governor}, beating five other candidates,
including Representative Diane Black, who had aggressively tied herself
to the Trump administration. Mr. Lee will face Karl Dean, a former
Nashville mayor who easily won the Democratic primary, in the race to
succeed Gov. Bill Haslam, a term-limited Republican.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/02/us/elections/results-tennessee-primary-elections.html}{Full
results »}

Aug. 7

Elections near you

Ohio special House general election

Republicans
\href{https://www.nytimes3xbfgragh.onion/2018/08/24/us/politics/troy-balderson-ohio.html}{succeeded}
in holding on to a traditionally safe congressional district when State
Senator Troy Balderson eked out a narrow victory over a Democratic
challenger, Danny O'Connor in a special election whose result was too
close to call for nearly three weeks. Mr. Balderson will hold the seat
for just over two months before he faces Mr. O'Connor again in the
general election in November.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/07/us/elections/results-ohio-special-house-election-district-12.html}{Full
results »}

Elections near you

Kansas primaries

House:

2 out of 4 races are competitive in the general election.

A week after voters went to the polls in Kansas, Gov. Jeff Colyer
conceded in the race for the Republican nomination for governor,
\href{https://www.nytimes3xbfgragh.onion/2018/08/14/us/politics/kansas-kobach-colyer.html}{handing
a razor-thin victory} to Secretary of State Kris W. Kobach.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/07/us/elections/results-kansas-primary-elections.html}{Full
results »}

Elections near you

Michigan primaries

Senate: Debbie Stabenow is up for re-election.

House:

3 out of 14 races are competitive in the general election.

Gretchen Whitmer, a former leader in the Michigan State Senate,
\href{https://www.nytimes3xbfgragh.onion/2018/08/07/us/politics/gretchen-whitmer-michigan-election-results.html}{captured
the Democratic nomination for governor} and will face off against the
state's Republican attorney general, Bill Schuette, in a race that looms
as a pivotal test of whether Democrats can reclaim power in a state
President Trump won two years ago.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/07/us/elections/results-michigan-primary-elections.html}{Full
results »}

Elections near you

Missouri primaries

Senate: Claire McCaskill is up for re-election.

House:

1 out of 8 races is competitive in the general election.

After a succession of political setbacks in onetime strongholds and a
landmark defeat in the Supreme Court, organized labor
\href{https://www.nytimes3xbfgragh.onion/2018/08/07/business/economy/missouri-labor-right-to-work.html}{notched
a hard-won victory} as Missouri voters overrode a legislative move to
curb union power.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/07/us/elections/results-missouri-primary-elections.html}{Full
results »}

Elections near you

Washington primaries

Senate: Maria Cantwell is up for re-election.

House:

3 out of 10 races are competitive in the general election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/07/us/elections/results-washington-primary-elections.html}{Full
results »}

Aug. 11

Elections near you

Hawaii primaries

Senate: Mazie K. Hirono is up for re-election.

A crowded Democratic primary is likely to determine who takes the open
House seat in the Honolulu-based First District.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/11/us/elections/results-hawaii-primary-elections.html}{Full
results »}

Aug. 14

Democratic senators are up for re-election.

Elections near you

Minnesota primaries

Senate: Tina Smith is running to continue serving the rest of Senator Al
Franken's term.

Senate: Amy Klobuchar is up for re-election.

House:

4 out of 8 races are competitive in the general election.

Ms. Smith, a Democrat,
\href{https://www.nytimes3xbfgragh.onion/2017/12/13/us/tina-smith-minnesota-senate.html}{took
office in January} as a temporary replacement after Mr. Franken
\href{https://www.nytimes3xbfgragh.onion/2017/12/07/us/politics/al-franken-senate-sexual-harassment.html}{resigned
amid sexual misconduct accusations}. Now, she is running for the final
two years of the term; Republicans see an opening to pick off the seat.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/14/us/elections/results-minnesota-primary-elections.html}{Full
results »}

Elections near you

Wisconsin primaries

Senate: Tammy Baldwin is up for re-election.

House:

1 out of 8 races is competitive in the general election.

Speaker Paul D. Ryan's mid-April announcement
\href{https://www.nytimes3xbfgragh.onion/2018/04/11/us/politics/paul-ryan-speaker.html}{that
he will not seek re-election} for the First District signaled the peril
that the Republican majority in the House faces.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/14/us/elections/results-wisconsin-primary-elections.html}{Full
results »}

Elections near you

Connecticut primaries

Senate: Christopher S. Murphy is up for re-election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/14/us/elections/results-connecticut-primary-elections.html}{Full
results »}

Elections near you

Vermont primaries

Senate: Bernie Sanders is up for re-election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/14/us/elections/results-vermont-primary-elections.html}{Full
results »}

Aug. 21

Elections near you

Alaska primaries

House:

1 race is competitive in the general election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/21/us/elections/results-alaska-primary-elections.html}{Full
results »}

Elections near you

Wyoming primaries

Senate: John Barrasso is up for re-election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/21/us/elections/results-wyoming-primary-elections.html}{Full
results »}

Aug. 28

Two states hold critical primaries for the Senate and House.

Elections near you

Arizona primaries

Senate: The Senate race is open. (Senator Jeff Flake is not seeking
re-election.)

House:

2 out of 9 races are competitive in the general election.

Republican primary
\href{https://www.nytimes3xbfgragh.onion/2018/08/28/us/politics/florida-arizona-election-results.html}{voters
chose the establishment favorite}, Representative Martha McSally, to
replace Mr. Trump's most outspoken G.O.P. critic in the Senate, Jeff
Flake, in a contest that evolved into a test of which candidate could
embrace Mr. Trump most snugly.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/28/us/elections/arizona-primary-elections.html}{Full
results »}

Elections near you

Florida primaries

Senate: Bill Nelson is up for re-election.

House:

7 out of 27 races are competitive in the general election.

Florida Democrats nominated Andrew Gillum, the Tallahassee mayor, and
Republicans tapped Representative Ron DeSantis for governor,
\href{https://www.nytimes3xbfgragh.onion/2018/08/28/us/politics/florida-arizona-election-results.html}{setting
the stage} for a ferocious general election in the country's largest
swing state between one of President Trump's most unabashed allies and
an outspoken progressive who would be Florida's first black governor.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/28/us/elections/florida-primary-elections.html}{Full
results »}

Elections near you

Oklahoma primaries runoff

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/08/28/us/elections/oklahoma-primary-runoff-elections.html}{Full
results »}

Sept. 4

Elections near you

Massachusetts primaries

Senate: Elizabeth Warren is up for re-election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/09/04/us/elections/results-massachusetts-primary-elections.html}{Full
results »}

Sept. 6

Elections near you

Delaware primaries

Senate: Thomas R. Carper is up for re-election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/09/06/us/elections/results-delaware-primary-elections.html}{Full
results »}

Sept. 11

Elections near you

New Hampshire primaries

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/09/11/us/elections/results-new-hampshire-primary-elections.html}{Full
results »}

Sept. 12

Elections near you

Rhode Island primaries

Senate: Sheldon Whitehouse is up for re-election.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/09/12/us/elections/results-rhode-island-primary-elections.html}{Full
results »}

Sept. 13

Elections near you

New York primaries for state and local offices

Gov. Andrew M. Cuomo, a Democrat, is facing a primary challenge
\href{https://www.nytimes3xbfgragh.onion/2018/03/19/nyregion/cynthia-nixon-new-york-governor-cuomo.html}{from
the actress Cynthia Nixon}.

\href{https://www.nytimes3xbfgragh.onion/interactive/2018/09/13/us/elections/results-new-york-primary-elections.html}{Full
results »}

Nov. 6

The general election will decide who controls the Senate and House.

\textbf{In the Senate midterm elections}, Democrats hope to win at least
two new seats to regain control of the chamber, but their margin for
error is slim. A majority of the seats up for election in 2018 are
currently held by Democrats.
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/02/07/us/politics/senate-midterm-elections.html}{Get
a full preview here.}

26 Democratic incumbents*

STATE

INCUMBENT

RATING

Fla.

Bill Nelson Nelson, FL

Tossup

Ind.

Joe Donnelly Donnelly, IN

Tossup

Mo.

Claire McCaskill McCaskill, MO

Tossup

Mont.

Jon Tester Tester, MT

Tossup

N.J.

Robert Menendez Menendez, NJ

Tossup

Minn.

Tina Smith Smith, MN

Lean D

N.D.

Heidi Heitkamp Heitkamp, ND

Lean R

W.Va.

Joe Manchin III Manchin III, WV

Lean D

Mich.

Debbie Stabenow Stabenow, MI

Likely D

Ohio

Sherrod Brown Brown, OH

Likely D

Pa.

Bob Casey Casey, PA

Likely D

Wis.

Tammy Baldwin Baldwin, WI

Likely D

Calif.

Dianne Feinstein Feinstein, CA

Solid D

Conn.

Christopher S. Murphy Murphy, CT

Solid D

Del.

Thomas R. Carper Carper, DE

Solid D

Hawaii

Mazie K. Hirono Hirono, HI

Solid D

Mass.

Elizabeth Warren Warren, MA

Solid D

Md.

Benjamin L. Cardin Cardin, MD

Solid D

Maine

Angus King King, ME

Solid D

Minn.

Amy Klobuchar Klobuchar, MN

Solid D

N.M.

Martin Heinrich Heinrich, NM

Solid D

N.Y.

Kirsten Gillibrand Gillibrand, NY

Solid D

R.I.

Sheldon Whitehouse Whitehouse, RI

Solid D

Va.

Tim Kaine Kaine, VA

Solid D

Vt.

Bernie Sanders Sanders, VT

Solid D

Wash.

Maria Cantwell Cantwell, WA

Solid D

9 Republican incumbents

STATE

INCUMBENT

RATING

Ariz.

Open (Jeff Flake) Open, AZ

Tossup

Nev.

Dean Heller Heller, NV

Tossup

Tenn.

Open (Bob Corker) Open, TN

Tossup

Tex.

Ted Cruz Cruz, TX

Tossup

Miss.

Cindy Hyde-Smith Hyde-Smith, MS

Lean R

Miss.

Roger Wicker Wicker, MS

Solid R

Neb.

Deb Fischer Fischer, NE

Solid R

Utah

Open (Orrin G. Hatch) Open, UT

Solid R

Wyo.

John Barrasso Barrasso, WY

Solid R

\textbf{In the House midterm elections}, Democrats need to flip 23 seats
to capture the 218 seats necessary for control of the chamber. There are
\textbf{194 likely or solidly Democratic} seats and \textbf{166 likely
or solidly Republican} seats. The competitive races below are listed by
state and district number.
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/house-race-ratings.html}{Get
the latest updates here.}

16 races lean Dem.

Arizona 1AZ-01

Arizona 2AZ-02

Colorado 6CO-06

Florida 27FL-27

Iowa 1IA-01

Illinois 6IL-06

Kansas 3KS-03

Michigan 11MI-11

Minnesota 2MN-02

Minnesota 3MN-03

New Jersey 11NJ-11

Nevada 3NV-03

Nevada 4NV-04

Pennsylvania 7PA-07

Virginia 10VA-10

Washington 8WA-08

30 races are tossups

California 10CA-10

California 25CA-25

California 39CA-39

California 45CA-45

California 48CA-48

Florida 15FL-15

Florida 26FL-26

Georgia 6GA-06

Iowa 3IA-03

Illinois 14IL-14

Kansas 2KS-02

Kentucky 6KY-06

Maine 2ME-02

Michigan 8MI-08

Minnesota 1MN-01

North Carolina 9NC-09

North Carolina 13NC-13

New Jersey 3NJ-03

New Jersey 7NJ-07

New Mexico 2NM-02

New York 19NY-19

New York 22NY-22

Ohio 12OH-12

Pennsylvania 1PA-01

Pennsylvania 10PA-10

Texas 7TX-07

Texas 32TX-32

Utah 4UT-04

Virginia 2VA-02

Virginia 7VA-07

29 races lean Rep.

Alaska at-largeAK-00

California 50CA-50

Florida 6FL-06

Florida 16FL-16

Florida 18FL-18

Florida 25FL-25

Georgia 7GA-07

Iowa 4IA-04

Illinois 12IL-12

Illinois 13IL-13

Michigan 6MI-06

Minnesota 8MN-08

Missouri 2MO-02

Montana at-largeMT-00

North Carolina 2NC-02

Nebraska 2NE-02

New York 11NY-11

New York 24NY-24

New York 27NY-27

Ohio 1OH-01

Pennsylvania 16PA-16

South Carolina 1SC-01

Texas 22TX-22

Texas 23TX-23

Virginia 5VA-05

Washington 3WA-03

Washington 5WA-05

Wisconsin 1WI-01

West Virginia 3WV-03

In addition to congressional elections, there are also \textbf{36
governor's races} on the ballot in 2018. With the next redistricting
process set for after the 2020 election, winning gubernatorial and state
legislative control will be crucial for both parties.

Nov. 6

Elections near you

Louisiana primaries

\hypertarget{have-questions-about-subscribing-to-this-calendar-here-are-some-answers}{%
\paragraph{\texorpdfstring{Have questions about
\protect\hyperlink{promo-button-holder}{subscribing} to this calendar?
Here are some
answers:}{Have questions about subscribing to this calendar? Here are some answers:}}\label{have-questions-about-subscribing-to-this-calendar-here-are-some-answers}}

\begin{itemize}
\tightlist
\item
  Does the calendar work with Android devices?
\item
  Yes. Use the \protect\hyperlink{promo-button-holder}{signup} at the
  top of this page to subscribe using your Google account. The calendar
  will be synced to your phone.
\item
  Is there a webcal/iCal feed I can use to subscribe directly?
\item
  Use the link below:
\item
  I subscribed to the calendar on my iPhone but it isn't showing up on
  my computer or tablet. How do I fix that?
\item
  You will need to add
  \href{https://support.apple.com/en-us/HT202361}{an iCloud Calendar
  subscription}. Use the webcal link mentioned above.
\item
  Can I subscribe if I use Outlook?
\item
  Yes. Using the webcal link above, you can add the calendar to
  \href{https://support.office.com/en-us/article/Import-or-subscribe-to-a-calendar-in-Outlook-com-or-Outlook-on-the-web-cff1429c-5af6-41ec-a5b4-74f2c278e98c}{Outlook.com}
  or an
  \href{https://support.office.com/en-us/article/View-and-subscribe-to-Internet-Calendars-7CD5D35A-4A90-4D70-A2F7-F6FADD7E2D9A}{Outlook
  desktop client}.
\item
  How do I submit feedback, or suggest another important event that I
  think you missed?
\item
  Email us at
  \href{mailto:elections@NYTimes.com}{\nolinkurl{elections@NYTimes.com}}.
\item
  How do I unsubscribe?
\item
  Google Calendar:
  \href{https://support.google.com/calendar/answer/37188}{Unsubscribe
  using a desktop computer}\\
  iCloud: \href{https://support.apple.com/kb/PH2679?locale=en_US}{Delete
  the calendar from iCloud.com}\\
  iPhone/iPad: Open ``Settings,'' then ``Accounts,'' and remove the
  calendar subscription. If you do not see any entry for the calendar,
  follow the directions for Google Calendar or iCloud.
\end{itemize}

Race ratings are by \href{https://www.cookpolitical.com/ratings/}{Cook
Political Report}. *Senate Democratic totals include two independents
who caucus with the Democrats. Runoff elections will be held only if
necessary on the dates noted.

Sources: Associated Press, offices of secretaries of state, National
Governors Association, United States Senate, Federal Election
Commission.

By Keith Collins. Reporting was contributed by Kitty Bennett, Alan
Blinder, Nate Cohn, Manny Fernandez, Trip Gabriel, Patricia Mazzei, Adam
Nagourney and Mitch Smith. Britt Binler contributed calendar production.
Dagny Salas contributed research.

\textbf{Correction: Jan. 25, 2018}

An earlier version of this calendar misspelled the name of the senator
from New York up for re-election. It is Kirsten Gillibrand, not Kristen.

\textbf{Correction: May 31, 2018}

An earlier version of this calendar misstated the number of states won
by President Trump that will have primaries on Aug. 14. It is one, not
two.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
