Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/politics}{Politics}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/politics}{Politics}\textbar{}Democrats Use Trump's 'It Is
What It Is' to Make Their Case

\url{https://nyti.ms/3aFqyQX}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{democrats-use-trumps-it-is-what-it-is-to-make-their-case}{%
\section{Democrats Use Trump's 'It Is What It Is' to Make Their
Case}\label{democrats-use-trumps-it-is-what-it-is-to-make-their-case}}

By The Associated Press

\begin{itemize}
\item
  Aug. 19, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

LAS VEGAS --- Democrats working to depict President Donald Trump as an
ineffective and negligent leader are summing up their case by quoting
the president's own words on coronavirus deaths: ``It is what it is.''

Democratic leaders, including former first lady Michelle Obama and
former President Bill Clinton, highlighted Trump's comment during each
of the first two nights of the Democratic National Convention.

Trump's comment came in an interview with ``Axios on HBO'' earlier this
month, when he was asked how he could say the coronavirus was under
control with 1,000 Americans dying every day from it.

``They are dying. That's true. And it is what it is. But that doesn't
mean we aren't doing everything we can. It's under control as much as
you can control it. This is a horrible plague that beset us,'' Trump
said in the interview.

Obama, headlining the all-virtual convention's opening night, made a
reference to the comment during her prerecorded 18-minute speech where
she gave a dire assessment of Trump. She said Trump ``cannot meet this
moment'' and ``simply cannot be who we need him to be for us.''

``It is what it is,'' Obama said, with a slight shake of her head.

Clinton quoted Trump during his Tuesday night remarks as he accused
Trump of a flailing response to the COVID-19 pandemic, saying Trump
``shrugged.''

``Did it have to be this way?'' Clinton asked.

His wife, Hillary Clinton, will deliver her own spin on Trump's comment
Wednesday night.

``I wish Donald Trump had been a better president. But, sadly, he is who
he is,'' she says, according to excerpts of her remarks released ahead
of the third night of the convention.

On Tuesday, Senate Minority Leader Chuck Schumer put Trump's remark in
historical context, framing it as something that would never be said by
a president facing a national crisis.

``President Lincoln, honoring the great sacrifice at Gettysburg, didn't
say `it is what it is.' President Roosevelt, seeing a third of the
nation ill-housed, ill-clad and ill-nourished, didn't say 'it it's what
it is,'' Schumer said Tuesday. ``America, Donald Trump has quit on
you.''

Trump campaign spokesman Tim Murtaugh responded to the repeated use of
the president's comment at the convention by saying: "Democrats would
rather talk about anything but their own terrible candidate, who rarely
comes out of hiding, has an abysmal economic record, and would raise
taxes by \$4 trillion if elected. To be fair, we wouldn't want to talk
about Joe Biden either.''

Adam Green, co-founder of the Progressive Change Campaign Committee,
said Wednesday that Trump's comment has taken on a life of its own
because it was ``a stand-in for the broader theme of complacency under
this administration."

``Like, if you want any proactive effort for higher wages, more jobs,
addressing the climate crisis, or this pandemic and healthcare crisis,
Donald Trump's administration really could be summarized with 'it is
what it is. I will let you suffer,''' Green said.

Mathew Littman, a former Biden speechwriter and the executive director
of pro-Biden super PAC Win the West, said Obama's use of the line was
particularly effective because, while most people may not be watching
the entire convention, Obama is a popular figure and there's a good
chance more people might be watching and replaying her remarks.

Littman said Trump's comment stood out because it showed ``a certain
dismissiveness,'' and Democrats are highlighting it because it shows the
president doesn't want to talk about the pandemic.

``I think what people are highlighting at the convention is that Donald
Trump doesn't care about this issue. Donald Trump wants to tell you good
news about the economy. He's a game show host.''

``I'm sure that we're going to see this come up a lot,'' Littman said.
``All the time. In ads.''

\_\_\_

Associated Press writers Sara Burnett in Chicago and Jill Colvin in
Washington contributed to this report.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
