Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

Poem: Parrot

\url{https://nyti.ms/2vakpvo}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{poem-parrot}{%
\section{Poem: Parrot}\label{poem-parrot}}

By Nick Flynn

Selected by Naomi Shihab Nye

\begin{itemize}
\item
  Feb. 6, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

A moment on a sidewalk becomes a koan, a fragment bearing a mysterious
pronoun. Who needs it more: the person who tells it or the person who
receives? Is it gift or intrusion? Repeating in memory the way a
parrot's cackled mantra hovers --- random comments on subways, in
waiting rooms, connect us. And what about this emptiness? Is it empty or
full? \emph{Selected by Naomi Shihab Nye}

Image

\hypertarget{parrot}{%
\subsection{Parrot}\label{parrot}}

By Nick Flynn

 Stranger, uninvited, you\\
come up to us on the sidewalk,

my daughter's hand in mine, you\\
look at her \&

coo, \emph{It goes so fast.} What, stranger,\\
is this unnamed \emph{it} --- this day?

her life? our

happiness? Stranger, maybe you\\
missed it, but just now

my daughter \& I hurled

rocks into the emptiness\\
\& we created more

emptiness.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{Naomi Shihab Nye} is the 2019-21 Young People's Poet Laureate of
the Poetry Foundation in Chicago and the 2019 recipient of the National
Book Critics Circle's Ivan Sandrof Award for Lifetime Achievement.
\textbf{Nick Flynn} teaches at the University of Houston. His fifth book
of poetry, ``I Will Destroy You,'' is from Graywolf Press.

Illustration by R.O. Blechman

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
