Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/corrections}{Corrections}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/corrections}{Corrections}\textbar{}Corrections: April 19,
2020

\url{https://nyti.ms/2RRdbFn}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{corrections-april-19-2020}{%
\section{Corrections: April 19, 2020}\label{corrections-april-19-2020}}

Corrections that appeared in print on Sunday, April 19, 2020.

April 18, 2020

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{arts--leisure}{%
\subsection{ARTS \& LEISURE}\label{arts--leisure}}

An
\href{https://www.nytimes3xbfgragh.onion/2020/04/10/arts/television/mrs-america-cate-blanchett.html}{article}
last Sunday about the FX series ``Mrs. America'' misstated the
publication status of the historian Rick Perlstein's book ``The
Invisible Bridge: The Fall of Nixon and the Rise of Reagan.'' It has
been published; it is not forthcoming.

\hypertarget{travel}{%
\subsection{TRAVEL}\label{travel}}

An
\href{https://www.nytimes3xbfgragh.onion/2020/04/08/travel/coronavirus-wine-tastings.html}{article}
last Sunday about remote wine tastings misstated the starting time of a
session on Thursdays held by the St. Supéry Estate Vineyards and Winery.
It is 8:30 p.m. Eastern time, not 8:50 p.m.?

An
\href{https://www.nytimes3xbfgragh.onion/2020/04/08/travel/cruises-coronavirus-stimulus.html}{article}
last Sunday about the lack of assistance for cruise companies in the \$2
trillion federal coronavirus relief package misstated the name of a
trade group. It is the Cruise Lines International Association, not the
Cruise Line Industry Association.

The 36 Hours
\href{https://www.nytimes3xbfgragh.onion/2020/04/02/travel/36-hours-quarantine.html}{article}
on April 5, with submissions from readers, misidentified the singer who
recorded ``That's Amore.'' It was Dean Martin, not Frank Sinatra.

\hypertarget{real-estate}{%
\subsection{REAL ESTATE}\label{real-estate}}

The Right at Home
\href{https://www.nytimes3xbfgragh.onion/2020/04/10/realestate/couples-quality-time-all-the-time.html}{article}
last Sunday, about how couples are dealing with one another in
quarantine, misspelled the surname of one of its subjects. He is Pierre
Forien, not Sorien.

Because of an editing error, the Calculator
\href{https://www.nytimes3xbfgragh.onion/2020/04/09/realestate/how-long-does-it-take-to-binge-watch-every-real-estate-tv-show.html}{article}
last Sunday, about real estate television shows, misstated the given
name of one of the stars of ``Property Brothers.'' He is Drew Scott, not
Dave.

\hypertarget{t-magazine}{%
\subsection{T MAGAZINE}\label{t-magazine}}

A
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/04/13/t-magazine/italian-fashion-design-houses.html}{picture
caption} with an article on Page 58 misstates Alberta Ferretti's title
with Aeffe. She is the vice president and creative director, not the
product director. The caption also misstates Stefano Canali's title with
Canali. He is the president and chief executive officer, not the general
manager. And it misidentifies the brand for which Andrea Molteni is the
director of product development. It is Molteni \& C Dada, not Molteni \&
C.

An
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/04/13/t-magazine/royal-academy-antwerp.html}{article}
on Page 70 about alumni of the Royal Academy of Fine Arts in Antwerp
misstates the years that the Belgian artist Luc Tuymans studied painting
there. It was from 1978 to 1979, not 1980 to 1982.

\hypertarget{book-review}{%
\subsection{BOOK REVIEW}\label{book-review}}

Because of an editing error, a
\href{https://www.nytimes3xbfgragh.onion/2020/04/03/books/review/freddy-the-pig-and-the-electoral-college-readers-respond.html}{letter}
to the editor on April 5 about voter representation in the United States
Senate misstated the relative populations of California and Wyoming.
California has more than 65 times as many people as Wyoming, not
``almost four'' times as many.

Because of an editing error, a
\href{https://www.nytimes3xbfgragh.onion/2020/03/13/books/review/history-of-islam-21-women-hossein-kamaly.html}{review}
on April 5 about ``A History of Islam in 21 Women,'' by Hossein Kamaly,
referred incorrectly to the schism that occurred after the death of
Muhammad. It was the Shiites, not the Sunnis, who supported Muhammad's
daughter Fatima and her husband, Ali; the Sunnis did not believe that
Fatima ``should inherit leadership of the faith.''

The Inside the List
\href{https://www.nytimes3xbfgragh.onion/2020/04/02/books/review/my-dark-vanessa-kate-elizabeth-russell.html}{column}
last Sunday misidentified a book festival that was canceled because of
the coronavirus. It was the Tucson Festival of Books, not the Texas Book
Festival (which is scheduled for November).

\emph{Errors are corrected during the press run whenever possible, so
some errors noted here may not have appeared in all editions.}

\emph{To contact the newsroom regarding correction requests, complaints
or other comments about our coverage, please email}
\href{mailto:nytnews@NYTimes.com}{\emph{nytnews@NYTimes.com}}\emph{.}

\emph{Comments on editorials may be emailed to}
\href{mailto:letters@NYTimes.com}{\emph{letters@NYTimes.com}}\emph{.}

\emph{For newspaper delivery questions: 1-800-NYTIMES (1-800-698-4637)
or email}
\href{mailto:customercare@NYTimes.com}{\emph{customercare@NYTimes.com}}\emph{.}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
