Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/books}{Books}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/books}{Books}\textbar{}Novel About Henry VIII Wins Booker
Prize

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{novel-about-henry-viii-wins-booker-prize}{%
\section{Novel About Henry VIII Wins Booker
Prize}\label{novel-about-henry-viii-wins-booker-prize}}

By \href{https://www.nytimes.com/by/motoko-rich}{Motoko Rich}

\begin{itemize}
\item
  Oct. 6, 2009
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Hilary Mantel won the 41st annual Man Booker Prize on Tuesday night for
``Wolf Hall,'' a historical novel about Henry VIII's court centered on
the king's adviser, Thomas Cromwell.

In the run-up to Tuesday's ceremony at the Guildhall in London, Ms.
Mantel, 57, was the overwhelming favorite, with the bookmakers William
Hill giving ``Wolf Hall'' odds of 10-11, the shortest odds ever for a
nominee.

Ms. Mantel beat out the literary lions J. M. Coetzee and A. S. Byatt,
both previous winners of the prize, and deprived Mr. Coetzee of the
chance to become a three-time winner of the award. She was the first
favorite to win since Yann Martel won for ``Life of Pi'' in 2002.

Accepting the award, Ms. Mantel said, ``I had to interest the
historians, I had to amuse the jaded palate of the critical
establishment and most of all I had to capture the imagination of the
general reader.''

James Naughtie, a BBC broadcaster who led the panel of judges, described
``Wolf Hall'' as ``a thoroughly modern novel set in the 16th century,''
praising it for the way it ``probes the mysteries of power by examining
and describing the meticulous dealings in Henry VIII's court, revealing
in thrilling prose how politics and history is made by men and women.''

Mr. Naughtie revealed that the decision was not unanimous and that the
five-judge panel was split this year 3 to 2 in favor of ``Wolf Hall.''
In a report on the Web site of the Guardian newspaper, guardian.co.uk,
Mr. Naughtie said the panel's decision ``was based on the sheer bigness
of the book, the boldness of its narrative and scene-setting, the gleam
that there is in its detail.''

The Man Booker Prize, Britain's most prestigious literary award, is
conferred every year to a novel written by an author from Britain,
Ireland or the Commonwealth nations. The award comes with a check for
about \$80,000 and usually results in a bump in sales. Last year's
winner, ``The White Tiger'' by Aravind Adiga, for example, has sold
236,000 copies in paperback in the United States, according to Nielsen
BookScan, which tracks about 70 percent of retail sales. ``The
Gathering'' by Anne Enright, which won in 2007, has sold 300,000
paperback copies.

Ms. Mantel, who has written 10 novels, a collection of short stories and
a memoir, spent five years writing ``Wolf Hall'' and is already working
on a sequel. This was her first time being nominated for the Booker
Prize.

``Wolf Hall,'' published by Fourth Estate in Britain and Henry Holt \&
Company in the United States, was widely praised among reviewers.
Writing in The New York Times on Monday, Janet Maslin said the book's
``main characters are scorchingly well rendered,'' adding that ``their
sharp-clawed machinations are presented with nonstop verve in a book
that can compress a wealth of incisiveness into a very few well-chosen
words.''

And in The Sunday Telegraph of London, Lucy Hughes-Hallett wrote that
Ms. Mantel ``makes that world at once so concrete you can smell the
rain-drenched wool cloaks and feel the sharp fibers of the rushes
underfoot.''

The Booker Prize was perhaps most notable this year for its lack of
controversy. In previous years, details of the judges' deliberations
have been catnip for London's literary society and the shortlists have
often been scrutinized as much for who is left off as for who is
included. This year, several heavyweights --- and former winners ---
were left off the long list of finalists, but that was largely viewed as
a measure of the strength of the year's offerings in literary fiction.

The shortlist of finalists for the award were Ms. Byatt for ``The
Children's Book,'' ; Mr. Coetzee for ``Summertime,'' Adam Foulds for
``The Quickening Maze,'' Simon Mawer for ``The Glass Room,'' and Sarah
Waters for ``The Little Stranger.''

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
