 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{/section/politics}{Politics} \textbar{}Which Obama-Era Rules Are
Being Reversed in the Trump Era

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2pn4aWG}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-politics-}{%
\subsection{\texorpdfstring{ \href{/section/politics}{Politics}
}{ Politics }}\label{-politics-}}

\hypertarget{which-obama-era-rules-are-being-reversed-in-the-trump-era}{%
\section{Which Obama-Era Rules Are Being Reversed in the Trump
Era}\label{which-obama-era-rules-are-being-reversed-in-the-trump-era}}

In his first 100 days, President Trump and congressional Republicans
have repeatedly employed a once rarely used power granted to Congress to
nullify rules recently adopted by federal agencies.

Enacted in 1996,
the\href{https://www.nytimes3xbfgragh.onion/2017/01/30/us/politics/congressional-review-act-obama-regulations.html}{}\href{https://www.nytimes3xbfgragh.onion/2017/01/30/us/politics/congressional-review-act-obama-regulations.html}{Congressional
Review Act} gives Congress 60 ​legislative ​days to ​revoke rules with
the help of the president. ​Before this year, it had only been used
once; since Mr. Trump took office, lawmakers have used it to reverse 14
Obama-era rules.

Below are the rules being challenged, and the status of each repeal
effort, based on data compiled by Curtis W. Copeland, a former senior
staff member at the Congressional Research Service.

Of \textbf{33} rules challenged under the Congressional Review
Act\ldots{}

14 have been reversed

0 have been approved for reversal by Congress

1 has been rejected

They cover the following topics:

Environment/energy (20)

Labor (5)

Education (2)

Finance (2)

Gun control (1)

Health (1)

Telecommunications (1)

Transportation (1)

14 regulations reversed

Labor

Reversed: Required companies seeking significant federal contracts to
\textbf{disclose violations of labor standards}.

\href{https://www.nytimes3xbfgragh.onion/2017/03/13/business/us-worker-safety-rules-osha.html}{More
→}

Environment/energy

Reversed: Limited \textbf{the way mines dump debris} when clearing earth
in order to prevent the destruction of area streams.

\href{https://www.nytimes3xbfgragh.onion/2017/02/02/business/energy-environment/senate-coal-regulations.html}{More
→}

The regulation would have protected an estimated 6,000 miles of streams
and 52,000 acres of forests over the next two decades.

Health

Reversed: \textbf{Barred states from withholding federal family-planning
funds} from Planned Parenthood affiliates and other health clinics that
provide abortions.

\href{https://www.nytimes3xbfgragh.onion/2016/12/14/us/politics/obama-administration-planned-parenthood.html}{More
→}

Gun control

Reversed: Required the Social Security Administration to turn over to
the Department of Justice information on \textbf{individuals with
disabling mental illnesses} --- about 75,000 a year --- to include in a
\textbf{registry of those not allowed to buy a gun}.

\href{https://www.nytimes3xbfgragh.onion/2017/03/05/us/politics/trump-deregulation-guns-wall-st-climate.html}{More
→}

Gun rights groups and others said it unfairly assumed those with mental
illness have a tendency toward violence.

Environment/energy

Reversed: Required oil, gas and mining companies to \textbf{disclose
payments made to foreign governments} in exchange for access to drilling
or mining rights.

\href{https://www.nytimes3xbfgragh.onion/2017/02/04/us/politics/republicans-oil-gas-regulations.html}{More
→}

The rule was part of an effort to prevent corruption in foreign
countries. The industry argued it would put American oil and gas
companies at a competitive disadvantage.

Labor

Reversed: Set federal limits on state-based \textbf{drug testing} of
people seeking unemployment insurance benefits.

\href{https://www.whitehouse.gov/the-press-office/2017/02/07/hjr-42-disapproving-rule-submitted-department-labor-relating-drug}{More
→}

The repeal clears the way for the expansion of drug testing of anyone
applying for jobless benefits.

Environment/energy

Reversed: \textbf{Revised the way the federal government conducts
land-use planning} on 245 million acres controlled by the Bureau of Land
Management.

\href{https://www.whitehouse.gov/the-press-office/2017/02/07/hjr-44-disapproving-rule-submitted-department-interior-relating-bureau}{More
→}

Critics said the rule would make energy development difficult and give
the federal government too much power.

Environment/energy

Reversed: \textbf{Tightened restrictions on efforts by state officials
to allow hunting of certain animals}, like wolves and grizzly bears,​ on
some Alaskan federal wildlife refuges.

\href{https://www.adn.com/alaska-news/wildlife/2017/04/10/congress-and-trump-revoked-the-predator-control-ban-on-alaskas-refuges-now-what/}{More
→}

Backers of the rule said it prohibited inhumane hunting methods used to
reduce predator populations.​ State officials argued that the rule too
broadly blocked the hunting of predators, making it harder for Alaska to
raise its populations of moose and caribou, which are more coveted by
hunters.

Education

Reversed: Told school districts how to \textbf{rate their schools}.

\href{https://www.nytimes3xbfgragh.onion/2017/03/09/us/every-student-succeeds-act-essa-congress.html}{More
→}

The regulations pushed states to weight student achievement measures,
like test scores and graduation rates, more heavily than other factors
in labeling schools as underperforming.​ Critics said the rules were too
aggressive and far-reaching.

Education

Reversed: Created regulations on \textbf{collecting data on the quality
of teacher preparation programs}.

\href{https://www.nytimes3xbfgragh.onion/2017/03/09/us/every-student-succeeds-act-essa-congress.html}{More
→}

Labor

Reversed: Changed rules by which states may establish
\textbf{I.R.A.-based payroll-deduction programs} for private-sector
workers whose employers do not offer a retirement plan.

\href{https://www.nytimes3xbfgragh.onion/2017/03/03/upshot/state-ira-plans-are-ready-if-congress-doesnt-interfere.html}{More
→}

Labor

Reversed: Changed rules by which local governments may establish
\textbf{I.R.A.-based payroll-deduction programs} for private-sector
workers whose employers do not offer a retirement plan.

\href{https://www.nytimes3xbfgragh.onion/2017/03/03/upshot/state-ira-plans-are-ready-if-congress-doesnt-interfere.html}{More
→}

Labor

Reversed: Clarified that employers have a continuing obligation to
\textbf{maintain accurate records of serious workplace injuries} and
illnesses for up to five years.

\href{https://www.nytimes3xbfgragh.onion/2017/03/13/business/us-worker-safety-rules-osha.html}{More
→}

Telecommunications

Reversed: Required broadband providers to \textbf{get permission from
customers to collect and use their online information}.

\href{https://www.nytimes3xbfgragh.onion/2017/03/28/technology/congress-votes-to-overturn-obama-era-online-privacy-rules.html}{More
→}

Consumer groups condemned the repeal of the rule, saying it would allow
broadband companies to continue to make money by selling consumers'
data, like their browsing history.

1 regulation rejected for reversal by Congress

Environment/energy

Rejected by Senate: \textbf{Limits venting, flaring and leaking of
methane, a powerful greenhouse gas,} from oil and gas wells on federal
lands, while also ensuring proper royalty payments to the government.

\href{https://www.nytimes3xbfgragh.onion/2017/05/10/us/politics/regulations-methane-climate-change.html}{More
→}

0 regulations approved for reversal by both chambers of Congress

0 regulations approved for reversal by one chamber of Congress

18 regulations brought to Congress to be reversed

Environment/energy

Considered for reversal: \textbf{Toughens oversight of oil and gas
operations} within the National Wildlife Refuge System.

\href{https://www.fws.gov/news/ShowNews.cfm?ref=service-finalizes-improvements-to-50-year-old-regulations-governing-oil-\&_ID=35889}{More
→}

The regulation prevents drillers from abandoning potentially hazardous
equipment and requires them to immediately report spills.

Environment/energy

Considered for reversal: \textbf{Tightens oversight of oil and gas
operations} in national parks in all states except Alaska.

\href{https://www.federalregister.gov/documents/2016/11/04/2016-26489/general-provisions-and-non-federal-oil-and-gas-rights}{More
→}

Environment/energy

Considered for reversal: \textbf{Sets safety and environmental
regulations for offshore drilling} in the Arctic Ocean off the Alaskan
coast.

\href{https://www.nytimes3xbfgragh.onion/2016/07/08/us/politics/latest-of-obamas-safety-rules-on-arctic-drilling-are-released.html}{More
→}

Oil companies complain that the regulations will stymie new energy
exploration. Environmentalists
\href{http://rulesatrisk.org/arctic-drilling-safeguards/}{argue that the
rule} incorporates the lessons of the 2010 BP Deepwater Horizon disaster
in the Gulf of Mexico.

Environment/energy

Considered for reversal: Revises the way the \textbf{federal government
decides what steps are necessary to mitigate impact on wildlife} and
other ecological resources, before it allows certain land development
projects in sensitive areas to move ahead.

\href{https://www.federalregister.gov/documents/2016/11/21/2016-27751/us-fish-and-wildlife-service-mitigation-policy}{More
→}

Finance

Considered for reversal: Revamps the process companies must use when
\textbf{evaluating whether a stake in a corporation should be treated as
stock or debt for federal tax purposes.}

\href{https://www.federalregister.gov/documents/2016/10/21/2016-25105/treatment-of-certain-interests-in-corporations-as-stock-or-indebtedness}{More
→}

This proposal is aimed at preventing multinational corporations from
engaging in "earnings-stripping" to minimize their U.S. taxes by
undergoing a so-called corporate inversion.

Environment/energy

Considered for reversal: \textbf{Expands civil penalty regulations to
all federal oil, gas and coal leases} on land and on the Outer
Continental Shelf, as well as to Indian and Tribal lands.

\href{https://www.federalregister.gov/documents/2016/08/01/2016-17598/amendments-to-civil-penalty-regulations}{More
→}

Environment/energy

Considered for reversal: \textbf{Sets minimum standards for the security
of oil and gas facilities}, and provides resources to ensure that oil
and gas produced from federal and Indian leases (except on Osage land)
are properly handled.

\href{https://www.federalregister.gov/documents/2016/11/17/2016-25407/onshore-oil-and-gas-operations-federal-and-indian-oil-and-gas-leases-site-security}{More
→}

Environment/energy

Considered for reversal: Covers 12,500 facilities that use or store
highly toxic or highly flammable chemicals to try to \textbf{reduce
chances of an accident, and to help local authorities better respond
should one occur}.

\href{https://www.federalregister.gov/documents/2017/03/16/2017-05288/accidental-release-prevention-requirements-risk-management-programs-under-the-clean-air-act-further}{More
→}

The rule was adopted in part in response to the 2013 explosion at a
fertilizer plant in Texas that killed 15 people and injured more than
200​. The industry argues that existing requirements have been effective
in reducing accidents.

Environment/energy

Considered for reversal: Makes policies on mitigating the impact of
development on \textbf{endangered species} consistent.

\href{https://www.federalregister.gov/documents/2016/12/27/2016-30929/endangered-and-threatened-wildlife-and-plants-endangered-species-act-compensatory-mitigation-policy}{More
→}

Finance

Considered for reversal: Requires that companies offering
\textbf{prepaid debit cards disclose fees} and offer protection against
fraud and unauthorized charges.

\href{https://www.nytimes3xbfgragh.onion/2016/10/05/business/prepaid-debit-cards-users-will-get-new-federal-protections.html}{More
→}

Environment/energy

Considered for reversal: Sets minimum standards for \textbf{accurate
measurement and proper reporting of all gas removed or sold} under
federal and Indian leases, excluding Osage land. The regulation also
establishes standards for the measurement and recordkeeping of gas
production.

\href{https://www.federalregister.gov/documents/2016/11/17/2016-25410/onshore-oil-and-gas-operations-federal-and-indian-oil-and-gas-leases-measurement-of-gas}{More
→}

Environment/energy

Considered for reversal: Provides \textbf{more consistency, clarity and
accuracy in product valuation} of the oil and gas produced under federal
onshore and offshore leases, and of the coal mined under federal and
Indian leases.

\href{https://www.federalregister.gov/documents/2016/07/01/2016-15420/consolidated-federal-oil-and-gas-and-federal-and-indian-coal-valuation-reform}{More
→}

Environment/energy

Considered for reversal: Revises the rules governing the way
\textbf{water in a Georgia-area reservoir is used, directing more of the
water to the Atlanta area, instead of feeding rivers in the Apalachicola
Bay region of Florida.}

\href{http://www.sam.usace.army.mil/Missions/Planning-Environmental/ACF-Master-Water-Control-Manual-Update/}{More
→}

The rule provoked intense opposition in Florida and Alabama, where local
officials argued it would result in a decline in river levels, hurting
hydropower dams and commercial oyster fisheries that rely on steady
water flow.

Environment/energy

Considered for reversal: Ensures that the \textbf{oil produced under
federal and Indian leases is accurately measured and accounted for} so
proper royalty dues are paid.

\href{https://www.federalregister.gov/documents/2016/11/17/2016-25405/onshore-oil-and-gas-operations-federal-and-indian-oil-and-gas-leases-measurement-of-oil}{More
→}

Royalties from federal leases are split between the U.S. Treasury and
the state where the oil is produced.

Transportation

Considered for reversal: \textbf{Improves coordination of transportation
planning in urban areas}, and requires that planning be regional,
instead of at the city level.

\href{https://www.fhwa.dot.gov/planning/mpocoordination.cfm}{More →}

The rule covers public transit, driving, cycling and walking.

Environment/energy

Considered for reversal: Requires \textbf{upgrades at two power plants
in Utah} to improve air quality.

\href{https://www.federalregister.gov/documents/2016/07/05/2016-14645/approval-disapproval-and-promulgation-of-air-quality-implementation-plans-partial-approval-and}{More
→}

The two plants contribute to regional haze that can muddy the views at
national parks in the area, including the Grand Canyon and Arches.

Environment/energy

Considered for reversal: Reduces ozone pollution by \textbf{lowering
summertime emissions limits from power plants} in 22 eastern states.

\href{https://www.federalregister.gov/documents/2016/10/26/2016-22240/cross-state-air-pollution-rule-update-for-the-2008-ozone-naaqs}{More
→}

Environment/energy

Considered for reversal: Sets procedures for \textbf{testing
compressors.}

\href{https://www.federalregister.gov/documents/2017/01/04/2016-29427/energy-conservation-program-test-procedures-for-compressors}{More
→}

Back to the top ↑

Kitty Bennett contributed research. Additional work by Jugal K. Patel.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
