\href{//www.nytimes3xbfgragh.onion}{}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{
Elections 2018}

\href{//www.nytimes3xbfgragh.onion}{ Home}

June 20, 2018, 4:49 PM ET

\hypertarget{dc-primary-election-results}{%
\section{D.C. Primary Election
Results}\label{dc-primary-election-results}}

By THE NEW YORK TIMES

\textbf{What to watch:} Voters will cast ballots in primary races for
mayor, attorney general and a slew of city council seats. The city does
not have a governor or voting representation in Congress.
\protect\hyperlink{}{Read more}

Mayor Muriel E. Bowser, a Democrat, faces a challenge from Ernest E.
Johnson and James Butler. Eleanor Holmes Norton, the long-serving
delegate to the House of Representatives, faces a challenge from Kim R.
Ford, a former Obama administration official.

Voters will also vote on Initiative 77, which would end an exemption
that allows businesses to pay tipped workers, like restaurant servers
and bartenders, less than minimum wage. If it passes, employers would be
required to pay all their employees a minimum wage of \$15 an hour by
2025.

Washington is a Democratic stronghold and the winner of the Democratic
primary has usually gone on to win the general election. The only
Republican running for any office in the city is attorney Michael
Bekesha, who is running for a seat on the city council.

--- LIAM STACK

\hypertarget{initiative-77-minimum-wage-increase-for-tipped-workers}{%
\subsection{Initiative 77: Minimum Wage Increase for Tipped
Workers}\label{initiative-77-minimum-wage-increase-for-tipped-workers}}

Voters will decide on Initiative 77, which would end an exemption that
allows businesses to pay tipped workers, like restaurant servers and
bartenders, less than minimum wage. If it passes, employers would be
required to pay all their employees a minimum wage of \$15 an hour by
2025.

\begin{longtable}[]{@{}llll@{}}
\toprule
Answer & Votes & Pct. &\tabularnewline
\midrule
\endhead
 Yes Yes & 44,353 & 55.1\% &\tabularnewline
 No No & 36,090 & 44.9\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/district-of-columbia}{Full
D.C. Results »}

80,443 votes, 100\% reporting (143 of 143 precincts)

\hypertarget{mayor}{%
\subsection{Mayor}\label{mayor}}

\hypertarget{democratic-primary}{%
\subsubsection{Democratic Primary}\label{democratic-primary}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Candidate & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Bowser* Muriel E. Bowser* & 58,431 & 83.0\% &\tabularnewline
 Butler James Butler & 7,532 & 10.7\% &\tabularnewline
 Johnson Ernest E. Johnson & 4,444 & 6.3\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/district-of-columbia}{Full
D.C. Results »}

70,407 votes, 100\% reporting (143 of 143 precincts)

* Incumbent

\hypertarget{city-council-chairman}{%
\subsection{City Council Chairman}\label{city-council-chairman}}

\hypertarget{democratic-primary-1}{%
\subsubsection{Democratic Primary}\label{democratic-primary-1}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Candidate & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Mendelson* Phil Mendelson* & 45,793 & 62.7\% &\tabularnewline
 Lazere Ed Lazere & 27,261 & 37.3\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/district-of-columbia}{Full
D.C. Results »}

73,054 votes, 100\% reporting (143 of 143 precincts)

* Incumbent

\hypertarget{city-council}{%
\subsection{City Council}\label{city-council}}

Race

Leader

Rpt.

At-Large Dem.

 52\%Anita Bonds*

 24\%Jeremiah Lowery

100\%

Ward 1 Dem.

 48\%Brianne Nadeau*

 25\%Kent Boese

100\%

Ward 3 Dem.

 0\%Mary Cheh*

Uncontested

Ward 5 Dem.

 69\%Kenyan R. McDuffie*

 15\%Gayle Carley

100\%

Ward 6 Dem.

 68\%Charles Allen*

 32\%Lisa Hunter

100\%

Ward 6 Rep.

 0\%Michael Bekesha

Uncontested

* Incumbent~

\hypertarget{us-representative}{%
\subsection{U.S. Representative}\label{us-representative}}

\hypertarget{democratic-primary-2}{%
\subsubsection{Democratic Primary}\label{democratic-primary-2}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Candidate & Vote & Pct.\tabularnewline
\midrule
\endhead
 Garcia* Franklin Garcia* Uncontested & 0 & 0.0\%\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/district-of-columbia}{Full
D.C. Results »}

0\% reporting (0 of 0 precincts)

* Incumbent

\hypertarget{us-delegate}{%
\subsection{U.S. Delegate}\label{us-delegate}}

\hypertarget{democratic-primary-3}{%
\subsubsection{Democratic Primary}\label{democratic-primary-3}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Candidate & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Norton* Eleanor Holmes Norton* & 57,298 & 76.7\% &\tabularnewline
 Ford Kim R. Ford & 17,438 & 23.3\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/district-of-columbia}{Full
D.C. Results »}

74,736 votes, 100\% reporting (143 of 143 precincts)

* Incumbent

\hypertarget{dc-senate}{%
\subsection{D.C. Senate}\label{dc-senate}}

\hypertarget{democratic-primary-4}{%
\subsubsection{Democratic Primary}\label{democratic-primary-4}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Candidate & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Brown* Michael D. Brown* & 33,366 & 51.9\% &\tabularnewline
 Thomas Andria Thomas & 30,920 & 48.1\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/district-of-columbia}{Full
D.C. Results »}

64,286 votes, 100\% reporting (143 of 143 precincts)

* Incumbent

\hypertarget{attorney-general}{%
\subsection{Attorney General}\label{attorney-general}}

\hypertarget{democratic-primary-5}{%
\subsubsection{Democratic Primary}\label{democratic-primary-5}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Candidate & Vote & Pct.\tabularnewline
\midrule
\endhead
 Racine* Karl Racine* Uncontested & 0 & 0.0\%\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/district-of-columbia}{Full
D.C. Results »}

0\% reporting (0 of 0 precincts)

* Incumbent

Source: Election results and race calls from The Associated Press

By Sarah Almukhtar, Wilson Andrews, Matthew Bloch, Jeremy Bowers, Tom
Giratikanon, Jasmine C. Lee and Paul Murray.

\hypertarget{see-election-results-for-2018-2017-2016-2014-2012-2010-2008}{%
\subsubsection{\texorpdfstring{See election results for
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{2018}
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/us/elections/election-calendar.html}{2017}
\href{https://www.nytimes3xbfgragh.onion/elections/results/president}{2016}
\href{https://www.nytimes3xbfgragh.onion/elections/2014/results/senate}{2014}
\href{https://www.nytimes3xbfgragh.onion/elections/2012/results/president.html}{2012}
\href{https://www.nytimes3xbfgragh.onion/elections/2010/results/senate.html}{2010}
\href{https://www.nytimes3xbfgragh.onion/elections/2008/results/president/map.html}{2008}}{See election results for 2018 2017 2016 2014 2012 2010 2008}}\label{see-election-results-for-2018-2017-2016-2014-2012-2010-2008}}

\hypertarget{more-on-nytimescom}{%
\subsubsection{More on NYTimes.com}\label{more-on-nytimescom}}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2018 The New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2018 The New York Times Company}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/infoservdirectory.html}{Contact
  Us}
\item
  \href{http://www.nytco.com/careers}{Work With Us}
\item
  \href{http://www.nytimes.whsites.net/mediakit}{Advertise}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/privacy/policy/privacy-policy.html\#pp}{Your
  Ad Choices}
\item
  \href{http://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/agree.html}{Terms
  of Service}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/sale/terms-of-sale.html}{Terms
  of Sale}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{http://www.nytimes3xbfgragh.onion/membercenter/sitehelp.html}{Help}
\item
  \href{https://myaccount.nytimes3xbfgragh.onion/membercenter/feedback.html}{Site
  Feedback}
\item
  \href{http://www.nytimes3xbfgragh.onion/subscriptions/Multiproduct/lp5558.html?campaignId=37WXW}{Subscriptions}
\end{itemize}
