Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/nyregion}{New York}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/nyregion}{New York}\textbar{}School Closings Over
Coronavirus in New York and New Jersey

\url{https://nyti.ms/2TOpW3K}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{school-reopenings}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/spotlight/schools-reopening?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=f07eaa90-efba-11ea-9794-7776d1fd3dae\&variant=undefined}{School
Reopenings}}{School Reopenings}}\label{school-reopenings}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/04/us/bar-exam-coronavirus.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=f07eaa91-efba-11ea-9794-7776d1fd3dae\&variant=undefined}{Delayed
  Licensing Exams}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/08/31/us/coronavirus-cases-children.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=f07ed1a0-efba-11ea-9794-7776d1fd3dae\&variant=undefined}{Rising
  Cases Among Children}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/01/world/schools-reopen-globe-students.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=f07ed1a1-efba-11ea-9794-7776d1fd3dae\&variant=undefined}{School
  Around the World}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/covid-college-cases-tracker.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=f07ed1a2-efba-11ea-9794-7776d1fd3dae\&variant=undefined}{Tracking
  College Cases}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{school-closings-over-coronavirus-in-new-york-and-new-jersey}{%
\section{School Closings Over Coronavirus in New York and New
Jersey}\label{school-closings-over-coronavirus-in-new-york-and-new-jersey}}

March 9, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Latest Updates

\href{https://www.nytimes3xbfgragh.onion/2020/03/12/nyregion/coronavirus-new-york-update.html?action=click\&module=RelatedLinks\&pgtype=Article}{Read
our live coverage of the coronavirus outbreak in the New York area.}

Gov. Andrew Cuomo said all public schools in New York City, Long Island
and Westchester County would be closing down in response to deepening
concerns about the coronavirus outbreak. New York City's school system
is the largest in the country, with 1.1 million students.

Some schools will open as ``enrichment centers'' to serve vulnerable
children. The district has 750,000 children who are low-income and rely
on school for basic services.

In New Jersey, Gov. Philip D. Murphy has ordered all public and private
schools, including colleges, to close no later than March 18.

New York Schools

\href{https://www.nytimes3xbfgragh.onion/2020/03/15/nyregion/coronavirus-schools-close-nyc.html?action=click\&module=RelatedLinks\&pgtype=Article}{All
New York City public schools will close starting Monday.}

This list is not inclusive of all decisions and is no longer being
updated. Check with a school district for the latest information.

\begin{itemize}
\item ~
  \hypertarget{new-york-city-public-schools}{%
  \subsection{New York City Public
  Schools}\label{new-york-city-public-schools}}

  \subsubsection{}

  All public schools will close the week of March 16. Remote learning
  will begin on March 23, and last until at least April 20. Programs
  will be implemented to provide access to childcare and meals.
\item ~
  \hypertarget{new-jersey-schools}{%
  \subsection{New Jersey Schools}\label{new-jersey-schools}}

  \hypertarget{-1}{%
  \subsubsection{}\label{-1}}

  All public and private schools and colleges are closed until further
  notice.
\item ~
  \hypertarget{westchester-public-schools}{%
  \subsection{Westchester Public
  Schools}\label{westchester-public-schools}}

  \hypertarget{westchester-county}{%
  \subsubsection{Westchester County}\label{westchester-county}}

  All schools will close starting the week of March 16 until further
  notice.
\item ~
  \hypertarget{long-island-public-schools}{%
  \subsection{Long Island Public
  Schools}\label{long-island-public-schools}}

  \hypertarget{-2}{%
  \subsubsection{}\label{-2}}

  All schools will close starting March 16 until further notice.
\item ~
  \hypertarget{cuny-and-suny-public-university-systems}{%
  \subsection{CUNY and SUNY public university
  systems}\label{cuny-and-suny-public-university-systems}}

  \hypertarget{new-york-state}{%
  \subsubsection{New York State}\label{new-york-state}}

  No on-campus classes from March 12 through March 18. Most classes will
  move to distance learning on March 19.
\item ~
  \hypertarget{adelphi-university}{%
  \subsection{Adelphi University}\label{adelphi-university}}

  \hypertarget{new-york-city}{%
  \subsubsection{New York City}\label{new-york-city}}

  In-person classes are canceled in Garden City, Manhattan, Hudson
  Valley, and Suffolk Centers through March 22 and will resume online on
  March 23 until further notice.
\item ~
  \hypertarget{archdiocese-of-new-york-elementary-schools}{%
  \subsection{Archdiocese of New York elementary
  schools}\label{archdiocese-of-new-york-elementary-schools}}

  \hypertarget{new-york-city-1}{%
  \subsubsection{New York City}\label{new-york-city-1}}

  Closed through at least March 20.
\item ~
  \hypertarget{barnard-college}{%
  \subsection{Barnard College}\label{barnard-college}}

  \hypertarget{manhattan-new-york-city}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city}}

  All classes will be conducted online for the remainder of the
  semester.
\item ~
  \hypertarget{brooklyn-friends-school}{%
  \subsection{Brooklyn Friends School}\label{brooklyn-friends-school}}

  \hypertarget{brooklyn-new-york-city}{%
  \subsubsection{Brooklyn, New York City}\label{brooklyn-new-york-city}}

  Closed until at least April 20. Virtual classes will begin after
  Spring Break.
\item ~
  \hypertarget{brooklyn-prospect-charter-schools}{%
  \subsection{Brooklyn Prospect Charter
  Schools}\label{brooklyn-prospect-charter-schools}}

  \hypertarget{brooklyn-new-york-city-1}{%
  \subsubsection{Brooklyn, New York
  City}\label{brooklyn-new-york-city-1}}

  Brooklyn Prospect Charter Schools middle and high schools will be
  closed starting March 16. Downtown Elememtary School will be closed
  starting March 17.
\item ~
  \hypertarget{challenge-charter-school}{%
  \subsection{Challenge Charter School}\label{challenge-charter-school}}

  \hypertarget{queens-new-york-city}{%
  \subsubsection{Queens, New York City}\label{queens-new-york-city}}

  School is closed through at least April 20.
\item ~
  \hypertarget{columbia-grammar--preparatory-school}{%
  \subsection{Columbia Grammar \& Preparatory
  School}\label{columbia-grammar--preparatory-school}}

  \hypertarget{manhattan-new-york-city-1}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-1}}

  Closed until at least March 30.
\item ~
  \hypertarget{columbia-university}{%
  \subsection{Columbia University}\label{columbia-university}}

  \hypertarget{manhattan-new-york-city-2}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-2}}

  All classes will be conduction online for the remainder of the
  semester.
\item ~
  \hypertarget{convent-of-the-sacred-heart}{%
  \subsection{Convent of the Sacred
  Heart}\label{convent-of-the-sacred-heart}}

  \hypertarget{manhattan-new-york-city-3}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-3}}

  Closed until at least March 30.
\item ~
  \hypertarget{cornell-university}{%
  \subsection{Cornell University}\label{cornell-university}}

  \hypertarget{ithaca-tompkins-county}{%
  \subsubsection{Ithaca, Tompkins County}\label{ithaca-tompkins-county}}

  Will switch to online learning starting April 6 through the end of the
  semester.
\item ~
  \hypertarget{democracy-prep-public-schools}{%
  \subsection{Democracy Prep Public
  Schools}\label{democracy-prep-public-schools}}

  \hypertarget{manhattan-new-york-city-4}{%
  \subsubsection{Manhattan, New York
  CIty}\label{manhattan-new-york-city-4}}

  Schools are closed starting at 1 p.m. on March 13, through April 19.
  Remote learning will begin on March 23. Spring break will be as
  scheduled, April 13-17.
\item ~
  \hypertarget{dwight-school}{%
  \subsection{Dwight School}\label{dwight-school}}

  \hypertarget{manhattan-new-york-city-5}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-5}}

  Closed through at least April 20.
\item ~
  \hypertarget{east-ramapo-central-school-district}{%
  \subsection{East Ramapo Central School
  District}\label{east-ramapo-central-school-district}}

  \hypertarget{rockland-county}{%
  \subsubsection{Rockland County}\label{rockland-county}}

  All schools are closed and will begin remote learning on March 17.
\item ~
  \hypertarget{ethical-culture-fieldston-school}{%
  \subsection{Ethical Culture Fieldston
  School}\label{ethical-culture-fieldston-school}}

  \hypertarget{bronx-new-york-city}{%
  \subsubsection{Bronx, New York City}\label{bronx-new-york-city}}

  Closed starting March 10.
\item ~
  \hypertarget{fordham-university}{%
  \subsection{Fordham University}\label{fordham-university}}

  \hypertarget{bronx-and-manhattan-new-york-city}{%
  \subsubsection{Bronx and Manhattan, New York
  City}\label{bronx-and-manhattan-new-york-city}}

  All classes canceled through March 10 and will be taught remotely
  after March 11.
\item ~
  \hypertarget{hofstra-university}{%
  \subsection{Hofstra University}\label{hofstra-university}}

  \hypertarget{hempstead-nassau-county}{%
  \subsubsection{Hempstead, Nassau
  County}\label{hempstead-nassau-county}}

  All buildings are closed. Remote classes will begin on March 23.
\item ~
  \hypertarget{horace-mann-school}{%
  \subsection{Horace Mann School}\label{horace-mann-school}}

  \hypertarget{bronx-new-york-city-1}{%
  \subsubsection{Bronx, New York City}\label{bronx-new-york-city-1}}

  Closed through at least March 31.
\item ~
  \hypertarget{iona-college}{%
  \subsection{Iona College}\label{iona-college}}

  \hypertarget{new-rochelle-westchester-county}{%
  \subsubsection{New Rochelle, Westchester
  County}\label{new-rochelle-westchester-county}}

  All classes will be remote starting March 23 through at least April
  10.
\item ~
  \hypertarget{john-jay-college-of-criminal-justice}{%
  \subsection{John Jay College of Criminal
  Justice}\label{john-jay-college-of-criminal-justice}}

  \hypertarget{manhattan-new-york-city-6}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-6}}

  Classes cancelled March 10 through at least March 18.
\item ~
  \hypertarget{manhattan-college}{%
  \subsection{Manhattan College}\label{manhattan-college}}

  \hypertarget{bronx-new-york-city-2}{%
  \subsubsection{Bronx, New York City}\label{bronx-new-york-city-2}}

  Classes are canceled through March 10 and will resume online on March
  11.
\item ~
  \hypertarget{new-york-institute-of-technology}{%
  \subsection{New York Institute of
  Technology}\label{new-york-institute-of-technology}}

  \hypertarget{manhattan-and-long-island-new-york-city}{%
  \subsubsection{Manhattan and Long Island, New York
  City}\label{manhattan-and-long-island-new-york-city}}

  In-person classes are suspended for the rest of the week and will
  resume online on March 23.
\item ~
  \hypertarget{new-york-university}{%
  \subsection{New York University}\label{new-york-university}}

  \hypertarget{manhattan-new-york-city-7}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-7}}

  All classes will take place online until further notice.
\item ~
  \hypertarget{pace-university}{%
  \subsection{Pace University}\label{pace-university}}

  \hypertarget{manhattan-new-york-city-8}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-8}}

  Will switch to online learning on all three campuses through at least
  March 29.
\item ~
  \hypertarget{princeton-university}{%
  \subsection{Princeton University}\label{princeton-university}}

  \hypertarget{princeton-mercer-county}{%
  \subsubsection{Princeton, Mercer
  County}\label{princeton-mercer-county}}

  The campus will move to virtual instruction on March 23, following
  spring break.
\item ~
  \hypertarget{rensselaer-polytechnic-institute}{%
  \subsection{Rensselaer Polytechnic
  Institute}\label{rensselaer-polytechnic-institute}}

  \hypertarget{troy-rensselaer-county}{%
  \subsubsection{Troy, Rensselaer County}\label{troy-rensselaer-county}}

  In-person classes are suspended through at least March 30.
\item ~
  \hypertarget{riverdale-country-school}{%
  \subsection{Riverdale Country School}\label{riverdale-country-school}}

  \hypertarget{bronx-new-york-city-3}{%
  \subsubsection{Bronx, New York City}\label{bronx-new-york-city-3}}

  All classes will be remote starting March 30.
\item ~
  \hypertarget{sar-academy}{%
  \subsection{SAR Academy}\label{sar-academy}}

  \hypertarget{bronx-new-york-city-4}{%
  \subsubsection{Bronx, New York City}\label{bronx-new-york-city-4}}

  Closed until further notice.
\item ~
  \hypertarget{sar-high-school}{%
  \subsection{SAR High School}\label{sar-high-school}}

  \hypertarget{bronx-new-york-city-5}{%
  \subsubsection{Bronx, New York City}\label{bronx-new-york-city-5}}

  Closed until further notice.
\item ~
  \hypertarget{saint-anns-school}{%
  \subsection{Saint Ann's School}\label{saint-anns-school}}

  \hypertarget{brooklyn-new-york-city-2}{%
  \subsubsection{Brooklyn, New York
  City}\label{brooklyn-new-york-city-2}}

  Online classes will resume until at least March 27.
\item ~
  \hypertarget{saint-johns-university}{%
  \subsection{Saint John's University}\label{saint-johns-university}}

  \hypertarget{queens-new-york-city-1}{%
  \subsubsection{Queens, New York City}\label{queens-new-york-city-1}}

  All classes will be held remotely for the rest of the semester.
\item ~
  \hypertarget{sarah-lawrence-college}{%
  \subsection{Sarah Lawrence College}\label{sarah-lawrence-college}}

  \hypertarget{bronxville-westchester-county}{%
  \subsubsection{Bronxville, Westchester
  County}\label{bronxville-westchester-county}}

  Closed on March 12 and March 13. Classes will resume online on March
  23 through at least April 3.
\item ~
  \hypertarget{school-of-visual-arts}{%
  \subsection{School of Visual Arts}\label{school-of-visual-arts}}

  \hypertarget{manhattan-new-york-city-9}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-9}}

  Undergraduate and graduate classes will resume online on March 16.
  In-person SVA Continuing Education classes are suspended until further
  notice.
\item ~
  \hypertarget{st-josephs-college}{%
  \subsection{St. Joseph's College}\label{st-josephs-college}}

  \hypertarget{brooklyn-new-york-city-3}{%
  \subsubsection{Brooklyn, New York
  City}\label{brooklyn-new-york-city-3}}

  The college is closed through at least March 30.
\item ~
  \hypertarget{stony-brook-university}{%
  \subsection{Stony Brook University}\label{stony-brook-university}}

  \hypertarget{stony-brook-suffolk-county}{%
  \subsubsection{Stony Brook, Suffolk
  County}\label{stony-brook-suffolk-county}}

  Starting March 23, classes will be online only.
\item ~
  \hypertarget{success-academy}{%
  \subsection{Success Academy}\label{success-academy}}

  \hypertarget{manhattan-new-york-city-10}{%
  \subsubsection{Manhattan, New York
  CIty}\label{manhattan-new-york-city-10}}

  Classes will shift to remote learning starting March 19, until further
  notice.
\item ~
  \hypertarget{syracuse-university}{%
  \subsection{Syracuse University}\label{syracuse-university}}

  \hypertarget{syracuse-onondaga-county}{%
  \subsubsection{Syracuse, Onondaga
  County}\label{syracuse-onondaga-county}}

  In-person classes will be suspended from March 13 until at least March
  30.
\item ~
  \hypertarget{the-brearley-school}{%
  \subsection{The Brearley School}\label{the-brearley-school}}

  \hypertarget{manhattan-new-york-city-11}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-11}}

  All classes will be held online until Spring Break. The school is
  tentatively scheduled to open back up on March 30.
\item ~
  \hypertarget{the-browning-school}{%
  \subsection{The Browning School}\label{the-browning-school}}

  \hypertarget{manhattan-new-york-city-12}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-12}}

  Closed until at least March 30.
\item ~
  \hypertarget{the-juilliard-school}{%
  \subsection{The Juilliard School}\label{the-juilliard-school}}

  \hypertarget{manhattan-new-york-city-13}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-13}}

  All college-division in-person classes, activities and performances
  are suspended until at least March 29.
\item ~
  \hypertarget{the-kings-college}{%
  \subsection{The King's College}\label{the-kings-college}}

  \hypertarget{manhattan-new-york-city-14}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-14}}

  Campus will be closed until at least March 30.
\item ~
  \hypertarget{the-new-school}{%
  \subsection{The New School}\label{the-new-school}}

  \hypertarget{manhattan-new-york-city-15}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-15}}

  In-person classes will not meet on March 23 through March 27. Classes
  will resume online on March 30 through at least April 12.
\item ~
  \hypertarget{the-nightingale-bamford-school}{%
  \subsection{The Nightingale-Bamford
  School}\label{the-nightingale-bamford-school}}

  \hypertarget{manhattan-new-york-city-16}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-16}}

  Closed until at least March 30.
\item ~
  \hypertarget{united-nations-international-school}{%
  \subsection{United Nations International
  School}\label{united-nations-international-school}}

  \hypertarget{manhattan-and-queens-new-york-city}{%
  \subsubsection{Manhattan and Queens, New York
  City}\label{manhattan-and-queens-new-york-city}}

  In-person classes will be suspended through March 20.
\item ~
  \hypertarget{william-t-dillon-child-study-center}{%
  \subsection{William T. Dillon Child Study
  Center}\label{william-t-dillon-child-study-center}}

  \hypertarget{brooklyn-new-york-city-4}{%
  \subsubsection{Brooklyn, New York
  City}\label{brooklyn-new-york-city-4}}

  Closed until at least April 10.
\item ~
  \hypertarget{windward-school}{%
  \subsection{Windward School}\label{windward-school}}

  \hypertarget{westchester-county-and-manhattan}{%
  \subsubsection{Westchester County and
  Manhattan}\label{westchester-county-and-manhattan}}

  Closed until March 30.
\item ~
  \hypertarget{yeshiva-university}{%
  \subsection{Yeshiva University}\label{yeshiva-university}}

  \hypertarget{manhattan-new-york-city-17}{%
  \subsubsection{Manhattan, New York
  City}\label{manhattan-new-york-city-17}}

  All undergraduate and graduate courses will be conducted online
  through at least April
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
\end{enumerate}

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
