Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

Judge John Hodgman on Proper Borrowing Etiquette

\url{https://nyti.ms/2Y1ZZ4V}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{judge-john-hodgman-on-proper-borrowing-etiquette}{%
\section{Judge John Hodgman on Proper Borrowing
Etiquette}\label{judge-john-hodgman-on-proper-borrowing-etiquette}}

By Judge John Hodgman

\begin{itemize}
\item
  July 9, 2019
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

\textbf{Matt writes:} \emph{Years ago, my sister, Brooke, borrowed a
camera lens of mine. I forgot about it until I needed it a year later.
That's when she told me she had sold it to our friend, Evan. I asked her
to replace it, and she said that because we both forgot about it, I
should just replace it myself. It cost me \$115. Having you settle a
claim that small feels petty. I want a genuine apology from her.}

You're a good brother, but I can't honor your request, because Brooke is
a bad sister. As an only child, I don't understand \emph{all} the
nuances of brother/sister relationships and the complicated psy-ops and
gaslighting that lasts well into adulthood. But my lonely status does
afford me the moral clarity to say that Brooke is a thief, and on some
level she knows it. So I order her to pay not \$115 but \$215, as
damages. Also, I would stay away from Evan if I were you. He seems like
a creep, too.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
