Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/opinion}{Opinion}\textbar{}How Trump's Upbringing Molded
His Personality

\url{https://nyti.ms/3iaZprV}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\href{/section/opinion}{Opinion}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

letterS

\hypertarget{how-trumps-upbringing-molded-his-personality}{%
\section{How Trump's Upbringing Molded His
Personality}\label{how-trumps-upbringing-molded-his-personality}}

Readers respond to an article about how empathy was a sign of weakness
in the Trump family and to revelations by the president's niece.

Aug. 4, 2020, 11:43 a.m. ET

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Image

Credit...Simon \& Schuster, via Associated Press

Image

Fred and Mary Anne Trump with their son Donald, in 1992.Credit...Alamy

\textbf{To the Editor:}

Re
``\href{https://www.nytimes3xbfgragh.onion/2020/07/28/us/politics/donald-fred-trump.html}{Trump
Family Legacy: Empathy Is for the Weak}'' (front page, July 29):

This is the main reason that Joe Biden will decisively defeat Donald
Trump in November. I am reading Mary Trump's daring exposé of her uncle
and now fully understand the complete lack of compassion or empathy
displayed by this faux president. The patriarch, Fred Trump, ruled his
family with an iron hand and abhorred any sign of weakness in his brood.

We can no longer abide a president who doesn't show any remorse for the
more than 150,000 people in the United States who lost their lives
because of his idiotic handling of the Covid-19 pandemic.

Mr. Trump has had opportunity after opportunity to show remorse and
empathy over the death of George Floyd, and express empathy to the
families of all the coronavirus victims, but has failed miserably to do
so. Even after the death of the civil rights icon John Lewis, Mr. Trump
passed on the opportunity to express his regrets by visiting the Capitol
Rotunda where the representative was lying in state.

We the people have had enough of Mr. Trump's coldhearted and
compassionless presidency, and we will do away with it on Nov. 3.

Henry A. Lowenstein\\
Newport, R.I.

\textbf{To the Editor:}

Donald Trump is forcing me to relive my childhood. Born the same year as
Mr. Trump, and in a nearby neighborhood (which was far less exclusive),
I heard the polemics he's still touting today. Redlining, fear of
``invasion'' and the like. The difference is that I grew up, learned to
value differences in people, and saw life in full color instead of in
black and white. So did most of us in Queens.

We're all products of our parents' beliefs and actions, but the
challenge and excitement of maturing is leaving those misconceptions
behind and discovering the wider, more beautiful world.

C. Berglie\\
Sea Cliff, N.Y.

\textbf{To the Editor:}

You quote one of President Trump's allies, Representative Peter T. King
of New York, as saying: ``His style as a leader is having to be a tough
guy. You can't show any type of weakness. He doesn't want to show that
this is getting the best of him.''

Then why does Mr. Trump spend most of his waking hours whining on
Twitter about almost everything?

Brad Newton\\
Greensboro, N.C.

\textbf{To the Editor:}

After reading Mary Trump's new book about her uncle, I started to feel
something toward President Trump that as a Democrat I've never felt
before: sympathy. I'm pretty sure this wasn't the intent of the writer,
but I feel sympathy for our president's childhood, for the lack of
emotional support from his father, and for the long-lasting negative
effects that this had on him as an adult.

I feel sympathy for the tragic ways in which this lack of emotional
support is now affecting millions of Americans every day, as he
repeatedly fails to feel any genuine empathy for the tens of thousands
of lives being lost to the virus.

Mary Trump's book should be a reminder to us all about the crucial
importance of loving your children each and every day.

Chris Lang\\
Bethlehem, Pa.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
