 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

\hypertarget{-magazine-}{%
\subsubsection{\texorpdfstring{
\href{https://www.nytimes3xbfgragh.onion/section/magazine}{Magazine}
}{ Magazine }}\label{-magazine-}}

 \href{https://www.nytimes3xbfgragh.onion/section/magazine}{Magazine}
\textbar{}New York's Collective Love Story

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2xKVvDD}

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

\hypertarget{new-yorks-collective-love-story}{%
\section{New York's Collective Love
Story}\label{new-yorks-collective-love-story}}

A city where romance is an atmospheric condition.

\hypertarget{love-city}{%
\subsection{Love City}\label{love-city}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/06/magazine/love-city-new-york-introduction.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/06/magazine/love-city-new-york-24-covers.html\%0A}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#clinton-hill-1-04-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-couples-in-bedrooms.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-club-lust.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-staten-island-ferry.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#mount-eden-3-30-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#times-square-4-56-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#astoria-5-15-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-watching-royal-wedding.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-nostrand-avenue-couples.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-wedding-proposal-planners.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#nomad-12-10-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-holding-hands-subway.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#chelsea-2-42-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-four-weddings.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-three-kids.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-couples-40-years-together.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bed-stuy-4-22-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#gramercy-park-5-20-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-rikers-jail-visit.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#red-hook-6-16-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-separation.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bed-stuy-8-37-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#flatiron-9-21-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bronx-center-9-25-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bushwick-11-27-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-lost-husband-grief.html}{}
\end{itemize}

\hypertarget{the-hearts-of-new-york}{%
\section{The Hearts of New York}\label{the-hearts-of-new-york}}

\hypertarget{new-yorks-collective-love-story-1}{%
\subsection{New York's Collective Love
Story}\label{new-yorks-collective-love-story-1}}

 By Sam Anderson JUNE 6, 2018

\textbf{May 19, 2018}, was a Saturday. It was rainy in New York. Out on
the streets of Manhattan, tourists tried and failed to hail occupied
cabs. Overhead, airplanes dropped through the storm to deposit further
loads of drivers and pedestrians. At Citi Field, in Queens, after the
tarps were finally rolled away, the Mets eked out a precious win on a
sacrifice fly in the bottom of the ninth. In London, five time zones
east, Prince Harry and Meghan Markle pledged their eternal devotion to
each other in a fizz of international splendor; New Yorkers set their
alarms to gather at the crack of dawn and watch the ceremony on their
various screens. The day was devoted to the spectacle of love, famous
and anonymous. It filled the city's streets and the trains under the
streets and the air-conditioned rooms hundreds of feet up in the sky.
Open love, secret love, proud love, tainted love. Physical love and
spiritual love, self-love and selfless love. Love on every point of the
continuum between requited and unrequited.

If you have been to New York City, for any length of time --- if your
body has occupied space on any of its sprawling islands --- you will
have been immersed in this enormous civic love-fest. The romance drifts
around like fog. Not ``romance,'' of course, in the old-fashioned,
idealized sense of the word --- perfectly appointed young couples
twirling blissfully through the streets while doormen and butchers erupt
into song. Real-world love does not require youth or choreography or
even necessarily couples. Love is ambient and omnidirectional, as tough
as lichen and as flexible as a flock of pigeons; it finds its own forms.
Stroll for 20 minutes anywhere in the modern city, and you will pass
human beings engaged in love in all its many phases: kindling, growing,
surging, peaking, stalling and receding.

Even if you happen to be totally oblivious to all of this, walking
around with your earbuds in, you are still a part of it, a member of the
supporting cast --- one thread in the tight weave of bodies and voices
and gazes that make up the city. You will be an unwitting witness to
good dates and bad dates, to the fluid beginnings of relationships and
their solid, absolute ends. Perhaps you will be the woman at the
hardware store looking at ⅜-inch screws at precisely the moment that the
kid carrying the skateboard makes his 13th terrible joke in a row,
causing his date to turn abruptly and walk away, never to return. Maybe
you will be the man at the next table in the crowded restaurant who
overhears the embarrassing revelation that leads to the embarrassing
counterrevelation that leads to the end of the affair that saves the
teetering second marriage. Or you will be standing under your umbrella
near a fountain when a young man in the distance suddenly kneels, on the
dirty pavement, inside a heart of plastic roses, to propose. For
someone, somewhere, you will be trapped in the amber of a relationship's
earliest moment. You will be a blurry face on the edge of a photo. You
will be a part of someone's lore.

One of my favorite New York love stories, Edith Wharton's novel ``The
House of Mirth,'' begins in the middle of the city's defining crowd ---
``the afternoon rush of the Grand Central Station.'' Two acquaintances
see each other there and decide to escape the congestion and walk up
Madison Avenue. Everywhere they go, new crowds surge around them,
drifting and dispersing and clustering. ``He led her through the throng
of returning holiday-makers,'' Wharton writes, ``past sallow-faced girls
in preposterous hats, and flat-chested women struggling with paper
bundles and palm-leaf fans.'' The two exist in a tiny bubble suspended
in a sea of others. The crowds hardly see them, and they hardly see the
crowds. This is one of the strange luxuries of living in a major city:
this public privacy, the privilege of selective attention, the ability
to navigate masses of people without quite seeing them as individuals
but as something simultaneously more and less --- a kind of humanoid
weather. When the novel's final tragedy arrives, it is preceded by
another walk through the same Midtown streets: ``Night had now closed in
and the roar of traffic in Forty-second Street was dying out.'' No
matter how private your love feels, New York will find a way to
participate, always.

\textbf{In New York}, love tends to attach itself to the cityscape. It
infuses the concrete and lingers in particular places like ghosts:
buildings and awnings and outcroppings of rock in Central Park. Every
staircase and streetlamp is alive with infinite histories. My personal
New York love story includes some things that still exist and many
things that don't: a saintly dachshund, the blizzard of 2003, a
particular bakery's chocolate muffin, a Russian barber in Queens,
couples therapy, ice cream in winter and a huge pink cocktail at the
Algonquin Hotel. One spring evening, through a hospital-room window, my
wife and I watched the sun set over the rooftops of the West Village; by
the time we watched it rise again, our daughter had been born. In the
decades before that night, in the same hospital, thousands had watched
lovers and acquaintances and family and friends die of AIDS. Love
stories beginning, winding, unwinding and ending. The hospital has since
been torn down, and luxury apartments have risen in its place.

Last summer, the singer St. Vincent released a ballad called ``New
York'' --- a lament, over sad piano, about a lost New York love. It is a
type of song that has been popular for many generations, since at least
the days of Tin Pan Alley, and one that will exist as long as the city
exists. The song includes this lyric:

\begin{quote}
\emph{New York isn't New York}

\emph{Without you, love.}

\emph{Too few of our old crew}

\emph{Left on Astor.}
\end{quote}

If you played that verse to a thousand different people, throughout the
history of the city, they would fill in all of its variables --- you,
love, our old crew --- with a very wide range of specifics. Astor Place
is a tiny stitch of a street, two blocks long, between N.Y.U. and the
East Village. Today, its defining features include a subway station,
sidewalk tables full of used books, a Starbucks and a huge black
sculpture of a cube that will rotate if enough people lean against it at
once. This is the landscape the St. Vincent song conjures in my mind ---
populated by graduate students, late at night, laughing too loud on
their way to St. Mark's Bookshop. Play the song in 1850, however, and it
would have been a lament for the death of the old ruling class,
including the street's namesake, the real estate mogul John Jacob Astor.
Play it in 1900, translated into Yiddish, and it would have spoken to
Eastern European garment workers who had seen friends die of diseases
and hardships too numerous to name. Play it in 1950, and it would have
been about tough men and women who had managed to survive the Depression
in abandoned buildings.

But those worlds, and the people in them, are gone. Even St. Mark's
Bookshop has closed, and the grad students I knew have scattered across
North America, and new waves of shops and students have swept in to
replace them. I am confident that not a single one of these faces
overlaps with the faces St. Vincent is singing about. The sentiment,
however, is roughly the same. Our vastly different joys and regrets
attach to the exact same landscape.

A city both oversees you (it never stops looking) and undersees you
(there are just so many of you to be seen). Individuals inevitably get
lost in the abundance. Don DeLillo, who grew up in New York and went on
to become the poet laureate of American crowds, once described the place
as ``the city of overflowing faces.'' His work is, among other things, a
sustained chronicle of New York's overwhelmingness:

\begin{quote}
The rush of things, of shuffled sights, the mixed swagger of the avenue,
noisy storefronts, jewelry spread across the sidewalk, the deep stream
of reflections, heads floating in windows, towers liquefied on taxi
doors, bodies shivery and elongate, all of it interesting to Bill in the
way it blocked comment, the way it simply rushed at him, massively, like
your first day in Jalalabad, rushed and was. Nothing tells you what
you're supposed to think of this.
\end{quote}

Nothing tells you what you're supposed to think. It can be profoundly
lonely. And so we look for one another.

The culture teaches us to think of love as an eternal, universal,
formless thing --- the shimmering essence at the heart of every Disney
movie and medieval French poem and pop song and rom-com. And yet, when
we encounter love in real life, it is always hyperspecific and local.
Love is not some great abstract principle; it is not an airbrushed
fantasy. It exists out in the world, always, as deep particularity. It
is about wallpaper, face creases, a paisley blanket, a lisp, a smell,
the particular yield of particular flesh. It involves old-growth forests
of body hair, asymmetrical teeth, eyebrows, puffiness, discoloration.
When love comes for you, it comes not for a cartoon princess or any
other kind of cliché --- it comes for you, all of you, as you actually
are.

This special issue of The New York Times Magazine is about love in all
its glorious specificity. More than 20 photographers traveled around New
York City to document its grand passions and quiet affections and
exploratory glances. The aim was to parse the city's anonymous crowds,
to separate them into their component parts, to look at individuals
instead of just masses --- to see the particles that make up the waves.
All of the photos were taken on a single day: May 19, that rainy
Saturday, while the Mets were winning and the royals were wedding and
the taxis were honking at one another. One photographer went back and
forth on the Staten Island Ferry, chronicling moments of love that
bloomed on the water. Another rode in a bus that carried people kissing.
Another went from home to home capturing couples in bed.

Think of the issue as a kind of core sample: a way to measure the
precise state of love on Earth in a very specific place and time. We see
couples staring into the camera together --- a double presence,
projecting their relationship frankly out into the world. In other
cases, we see one lover staring ahead while the other sleeps or looks
away --- a study in shyness and boldness, presence and absence. Kisses
land on cheeks, lips, necks. Beards commingle. Some pairs joyously push
their affection right to the edge of public decency. Some have
hairstyles that subtly rhyme. We see whole folded architectures of hands
--- touching or delectably not-quite-touching or with fingers
elaborately interwoven. It is a collection of public-private images that
I find tremendously optimistic. Even the heartbreak --- the removal, for
instance, of an old tattoo --- is, in its way, encouraging. Someone is
moving on. ♦

Sam Anderson is a staff writer for the magazine.

\emph{Sign up for}
\href{http://www.nytimes3xbfgragh.onion/newsletters/magazine}{\emph{our
newsletter}} \emph{to get the best of The New York Times Magazine
delivered to your inbox every week.}

\hypertarget{love-city-24-hours-of-romance-lust-and-heartache-in-new-york}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html}{Love
City: 24 Hours of Romance, Lust and Heartache in New
York}}{Love City: 24 Hours of Romance, Lust and Heartache in New York}}\label{love-city-24-hours-of-romance-lust-and-heartache-in-new-york}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/06/magazine/love-city-new-york-introduction.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/06/magazine/love-city-new-york-24-covers.html\%0A}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#clinton-hill-1-04-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-couples-in-bedrooms.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-club-lust.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-staten-island-ferry.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#mount-eden-3-30-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#times-square-4-56-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#astoria-5-15-am}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-watching-royal-wedding.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-nostrand-avenue-couples.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-wedding-proposal-planners.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#nomad-12-10-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-holding-hands-subway.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#chelsea-2-42-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-four-weddings.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-three-kids.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-couples-40-years-together.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bed-stuy-4-22-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#gramercy-park-5-20-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-rikers-jail-visit.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#red-hook-6-16-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-separation.html}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bed-stuy-8-37-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#flatiron-9-21-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bronx-center-9-25-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-city.html\#bushwick-11-27-pm}{}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2018/06/07/magazine/new-york-love-lost-husband-grief.html}{}
\end{itemize}

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
