Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/us}{U.S.}\textbar{}Does My County Have an Epidemic?
Estimates Show Hidden Transmission

\url{https://nyti.ms/2JCZ6Xw}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{the-coronavirus-outbreak}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=3dcf04e0-e38e-11ea-b524-5975769cbb40}{The
Coronavirus
Outbreak}}{The Coronavirus Outbreak}}\label{the-coronavirus-outbreak}}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes3xbfgragh.onion/2020/08/20/world/coronavirus-covid.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=3dcf04e1-e38e-11ea-b524-5975769cbb40}{Latest
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/coronavirus-us-cases.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=3dcf04e2-e38e-11ea-b524-5975769cbb40}{Maps
  and Cases}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/science/coronavirus-vaccine-tracker.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=3dcf04e3-e38e-11ea-b524-5975769cbb40}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/08/19/us/colleges-closing-covid.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=3dcf04e4-e38e-11ea-b524-5975769cbb40}{Colleges
  Closing}
\item
  \href{https://www.nytimes3xbfgragh.onion/live/2020/08/20/business/stock-market-today-coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=3dcf04e5-e38e-11ea-b524-5975769cbb40}{Economy}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{Does My County Have an Epidemic? Estimates Show Hidden
Transmission}\href{}{Skip to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@NYTimes.com}{\nolinkurl{letters@NYTimes.com}}.

\hypertarget{does-my-county-have-an-epidemic-estimates-show-hidden-transmission}{%
\section{Does My County Have an Epidemic? Estimates Show Hidden
Transmission}\label{does-my-county-have-an-epidemic-estimates-show-hidden-transmission}}

By \href{https://www.nytimes3xbfgragh.onion/by/james-glanz}{James
Glanz},
\href{https://www.nytimes3xbfgragh.onion/by/matthew-bloch}{Matthew
Bloch} and
\href{https://www.nytimes3xbfgragh.onion/by/anjali-singhvi}{Anjali
Singhvi}April 4, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{560}
\end{itemize}

+

-

+

-

Estimated chance of epidemic

10

60

75

90\%

By The New York Times·Source: Emily Javan, Spencer Fox and Lauren Ancel
Meyers, the University of Texas at Austin

As the coronavirus spreads silently through American cities and towns,
people are struggling with questions about the benefits of
social-distancing guidelines --- especially in places that still have
few reported cases.

Is the epidemic here yet? Is staying home and limiting contact with
others really worth the trouble?

A
\href{https://cid.utexas.edu/sites/default/files/cid/files/covid-risk-maps_counties_4.3.2020.pdf?m=1585958755}{new
study} by disease modelers at the University of Texas at Austin gives an
answer: Even counties with just a single reported case have more than 50
percent likelihood that a sustained, undetected outbreak --- an epidemic
--- is already taking place.

``I worry that many local officials are waiting until there is clear
evidence of local transmission before taking action,'' said Lauren Ancel
Meyers, a professor of biology and statistics and one of the study's
authors. ``The message is, we should not wait.''

With no consistent federal policy, local officials have been left on
their own to decide when to enact control measures, Most should assume
it is already here, she said.

Over all, the study finds, 70 percent of all counties in the United
States --- making up 94 percent of the country's population --- are
likely to have epidemics. The study defines an epidemic as an outbreak
that grows exponentially instead of fizzling out on its own, eventually
infecting a large fraction of the population.

\begin{longtable}[]{@{}ll@{}}
\toprule
\textbf{Known cases in a county} & \textbf{Probability of community
transmission}\tabularnewline
\midrule
\endhead
0 & 9\%\tabularnewline
1 & 51\%\tabularnewline
2 & 70\%\tabularnewline
3 & 79\%\tabularnewline
4 & 84\%\tabularnewline
5 & 85\%\tabularnewline
10 & 95\%\tabularnewline
20 & 99\%\tabularnewline
43 or more & 100\%\tabularnewline
\bottomrule
\end{longtable}

By The New York Times·Source: Emily Javan, Spencer Fox and Lauren Ancel
Meyers, the University of Texas at Austin

The University of Texas research team simulated the spread of the
outbreak in every United States county to determine the most likely
outcome in each county, along with reported case counts compiled by The
New York Times.

People who have been infected and have mild symptoms, or none at all,
can pass the disease to others. Those cases, often undetected, are a
prime driver of the outbreaks, Dr. Meyers said. Even in counties with no
reported cases, there is roughly a 9 percent chance that an undetected
outbreak is already underway, she said.

For those reasons, social distancing should be practiced across the
United States, whether an outbreak now is visible or not, Dr. Meyers
said.

``This virus spreads quickly and sometimes silently,'' she said. ``It's
an unseen threat, and by the time you see it, it can be too late to
intervene. You have to intervene proactively against threats you can't
see.''

Social distancing can slow those outbreaks, giving local hospitals and
other healthcare facilities time to handle the cases rather than being
quickly overwhelmed, Dr. Meyers said.

``Most of us are probably living in communities where this virus is
beginning to spread widely,'' she said. ``The prudent measures at this
point are doing whatever possible to prevent an infected person from
spreading the virus to an uninfected person. The common theme is do what
you can to keep people from congregating.''

Read 560 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
