Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/world/africa}{Africa}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/world/africa}{Africa}\textbar{}Tanzania Opposition Leader
Returns, 3 Years After Being Shot

\url{https://nyti.ms/3g6mTNZ}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{tanzania-opposition-leader-returns-3-years-after-being-shot}{%
\section{Tanzania Opposition Leader Returns, 3 Years After Being
Shot}\label{tanzania-opposition-leader-returns-3-years-after-being-shot}}

By The Associated Press

\begin{itemize}
\item
  July 27, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

DAR ES SALAAM, Tanzania --- Tanzanian opposition politician and
presidential hopeful Tundu Lissu returned to the country on Monday,
three years after being shot 16 times. The gunmen have never been found.

Immediately upon his arrival at the international airport in Dar es
Salaam, the former lawmaker told reporters and CHADEMA opposition party
supporters he was well. ``My leg is shorter by several centimeters. I am
very fine now,'' he said.

His return from Belgium comes as the top opposition parties consider
joining forces behind a single candidate to challenge President John
Magufuli, who seeks a second five-year term. Human rights groups and
critics accuse his administration of shutting down dissenting voices by
banning opposition political gatherings, arresting opposition figures
and shutting down media outlets.

Hundreds of CHADEMA party supporters gathered at the airport Monday,
with some kneeling at the arrival gate in defiance of a police order
barring unlawful public gatherings.

Lissu has announced his presidential run and expects the CHADEMA party
to endorse him.

His party in a statement said he is expected to attend a memorial on
Tuesday for Tanzania's late President Benjamin Mkapa. There he could
cross paths with Magufuli.

Lissu still faces six criminal charges, including one related to his
calling Magufuli a dictator. In a statement on Facebook, Lissu has
declared he is a free man out on bail.

Rights groups and the opposition party have urged authorities to provide
him with appropriate security.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
