Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/us}{U.S.}\textbar{}Orlando Joins List of Cities With
Sharp Increase in Murders

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{orlando-joins-list-of-cities-with-sharp-increase-in-murders}{%
\section{Orlando Joins List of Cities With Sharp Increase in
Murders}\label{orlando-joins-list-of-cities-with-sharp-increase-in-murders}}

By The Associated Press

\begin{itemize}
\item
  July 23, 2006
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

ORLANDO, Fla., July 22 - In less than seven months, this city of about
215,000 has reported 33 homicides, only three killings shy of its 1982
record and on pace to have one of the 15 worst murder rates in the
country.

The dead include a 6-year-old who had severe head injuries, apparently a
victim of child abuse, and a 22-year-old shot in the back of the head
for unknown reasons. Shortly after New Year's Day, a transient who was
stabbed near a homeless camp bled to death on the same day an
18-year-old's bullet-riddled body lay on the street; two gunmen had
apparently mistaken the teenager for someone they were feuding with.

"People can attribute crime to failing schools, failing families;
there's a bunch of sociological things you can put your finger on," said
Sgt. Rich Ring, the supervisor of Orlando's homicide investigation unit.
"All we can do as police is say the biggest things are drugs and
robbery, and we're going to take action to attack those issues."

Federal Bureau of Investigation figures from 2005 released last month
showed a 2.5 percent increase in violent crime nationwide -\/- the
largest since 1991 -\/- and a 4.8 percent rise in murders.

Jacksonville, the Florida murder capital for 12 of the past 17 years, is
on track to hit more than 130 killings for the first time in more than a
decade. The Washington, D.C., police this month declared a crime
emergency amid rising incidences of robberies and armed assaults, and
Detroit is on pace to hit 460 killings, a 22 percent increase over 2005.

But this is new territory for this quickly growing tourism mecca, where
tens of millions flock to Universal Studios, SeaWorld and nearby Walt
Disney World every year. Orlando ranked only 107th in per-capita murders
in 2004, the most recent F.B.I. rankings available.

Most of this year's killings were committed with handguns. Most victims
were young men who were involved with drugs or were killed by someone
who was, Sergeant Ring said.

The crimes have been scattered across the city, but mostly in
neighborhoods west of downtown and away from the tourist attractions.

Chief Mike McCoy of the Orlando Police emphasized that no tourists had
been killed and said that most law-abiding citizens were not at risk.

"If you're not selling drugs, if you don't house people selling drugs,
if you don't have the proceeds of drugs in your home, then your chances
of being involved in a homicide are pretty slim," Chief McCoy said.

Visitors do not appear to be worried. Downtown bars and clubs still
crowd at night, families continue to arrive in droves at theme parks,
and joggers and dog-walkers still make their way around city parks after
dark.

Even many in the hardest-hit areas said they were not aware of an
increase in killings.

Sierra Cunningham, a 17-year-old carrying her 1-year-old daughter to the
bus stop, said she had heard that killings were on the rise but did not
know of anyone taking extra safety precautions.

"Around my neighborhood it's O.K.," Ms. Cunningham said. "Just a lot of
people hanging out drinking all the time."

Even before the increase, Orlando planned a new public safety initiative
to put 75 additional officers on the street, add two detectives to its
violent crime unit and create new police substations.

Mayor Buddy Dyer said he was confident that law enforcement had a handle
on the situation, noting that arrests had been made in most homicide
cases.

"We want to work on educating the public in terms of changing the
culture of silence that exists in some of our neighborhoods," Mr. Dyer
said, "and we want to look at some of the policing practices that other
cities that have experienced an increase in homicides have used
effectively."

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
