Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/world/europe}{Europe}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/world/europe}{Europe}\textbar{}UK's Johnson Names Brother
and Brexiteers to House of Lords

\url{https://nyti.ms/3jXlL1C}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{uks-johnson-names-brother-and-brexiteers-to-house-of-lords}{%
\section{UK's Johnson Names Brother and Brexiteers to House of
Lords}\label{uks-johnson-names-brother-and-brexiteers-to-house-of-lords}}

By The Associated Press

\begin{itemize}
\item
  July 31, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

LONDON --- British Prime Minister Boris Johnson named 36 new members to
Parliament's unelected House of Lords on Friday, including his brother,
several prominent Brexit supporters and a Russian-born newspaper owner
whose father was a KGB agent.

The list of new peers also includes Brexit-backing former lawmakers and
ex-cricket star Ian Botham, a vocal proponent of leaving the European
Union.

Former Treasury chiefs Ken Clarke and Philip Hammond, who both opposed
Brexit, were also appointed to the Lords. So was Evgeny Lebedev, owner
of the Independent and Evening Standard newspapers. His father, Russian
oligarch Alexander Lebedev, once worked for the KGB.

Former Scottish Conservative leader Ruth Davidson is on the list, along
with Johnson's chief of staff Eddie Lister and the prime minister's
anti-Brexit brother Jo Johnson, who quit the government last year in
opposition to its policies.

Most of the appointees are allied with Johnson's governing Conservative
Party, though the list also includes several former opposition Labour
Party lawmakers who supported Brexit, Britain historic departure from
the European Union.

A notable omission is former House of Commons Speaker John Bercow. It's
customary for ex-speakers to be appointed to the Lords, but Bercow
infuriated the Conservative government by aiding lawmakers' efforts to
change the course of Brexit.

The new members will be given aristocratic titles --- baron or baroness
--- and will join almost 800 others in the House of Lords.

The chamber reviews legislation passed by the elected House of Commons,
and for most of its 900-year history was composed of hereditary nobles.
Nowadays members are appointed for life by the government and are a mix
of former lawmakers, other notables and political donors.

There are frequent calls to reform the Lords on the grounds that the
body is unwieldy, unaccountable and out of touch.

The Speaker of the Lords, Norman Fowler, accused the Conservative
government of reneging on a promise to trim the size of the upper house.

Scottish National Party lawmaker Pete Wishart, meanwhile, called
Johnson's appointments ``the worst kind of cronyism.''

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
