Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/us}{U.S.}\textbar{}Halloween Shooting at Airbnb in
Orinda, California, Leaves 5 Dead

\url{https://nyti.ms/337ul5c}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{halloween-shooting-at-airbnb-in-orinda-california-leaves-5-dead}{%
\section{Halloween Shooting at Airbnb in Orinda, California, Leaves 5
Dead}\label{halloween-shooting-at-airbnb-in-orinda-california-leaves-5-dead}}

Several others were injured in the shooting in Orinda, east of San
Francisco, the authorities said. Witnesses told local news outlets that
it happened at a Halloween party.

By \href{https://www.nytimes3xbfgragh.onion/by/thomas-fuller}{Thomas
Fuller}, \href{https://www.nytimes3xbfgragh.onion/by/jacey-fortin}{Jacey
Fortin},
\href{https://www.nytimes3xbfgragh.onion/by/elian-peltier}{Elian
Peltier} and
\href{https://www.nytimes3xbfgragh.onion/by/emily-s-rueb}{Emily S. Rueb}

\begin{itemize}
\item
  Published Nov. 1, 2019Updated Nov. 4, 2019
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

ORINDA, Calif. --- Five people were killed and several injured in a
shooting at a crowded Halloween party here on Thursday night, the police
said.

An officer was headed to the site of the party, at a short-term rental
home, at 10:48 p.m. to investigate noise complaints. Two minutes later,
the police received the first reports of gunfire, the Contra Costa
County Sheriff's Office
\href{https://www.facebookcorewwwi.onion/permalink.php?story_fbid=10156428769671561\&id=224837426560\&__xts__\%5B0\%5D=68.ARCXeP1wFCRNAU9OpvoWWFXS-TtmY3KBb2vlieuUR5OjOvtp2QDRET892rJ8vVptbzhb3kDh_i-HgZ7K2HYVdNrWobQAFZKZSU78r4YbHeu1My5BlnpAHqKp12AHb3qK05fTz8L9hv5YvdLJSjFlG185oo03rnYnKRWtajznUNy84H94HIJRYpPVhMuPoZH9PXUelAv0cZZYEa_gWwQ5a-sboAaHMM-CIY569nLOv9p2qIqQ_1l05LvNn4Q5cOUm3-U76-9kA04BEky7kpMrM1P12Lp7heuoxkPY_IrqQVnM_qPNfLrBElaPB1yGqfaJVwfXHZm1kqic5DGJ\&__tn__=-R}{said
in a statement on Friday night}.

Officers found ``a highly chaotic scene that included gunshot victims,
injured partygoers and numerous people fleeing the scene,'' the
statement said.

Three gunshot victims were pronounced dead at the scene and two others
died at a hospital.

The authorities identified the victims, all of California, as: Oshiana
Tompkins, 19, of Vallejo/Hercules; Tiyon Farley, 22, of Antioch; Omar
Taylor, 24, of Pittsburg; Ramon Hill Jr., 23, of San Francisco/Oakland;
and Javin County, 29, of Sausalito/Richmond.

Several other victims were taken by ambulance or took themselves to
hospitals, the statement said. The injured had gunshot wounds or were
hurt while fleeing, the statement said. Details on the number of injured
and their conditions were unavailable.

Two firearms were recovered in the house and the authorities were
analyzing them to determine if they were used in the shooting or any
other crimes, the sheriff's office said.

No arrests have been made, Chief David Cook of the Orinda Police
Department said at a news conference on Friday afternoon. He would not
discuss a potential motive.

Officers ``found a large house party with over 100 attendees'' after
they arrived at the residence in Orinda, which is about 15 miles east of
San Francisco, the sheriff's office said in an earlier
\href{https://www.facebookcorewwwi.onion/permalink.php?story_fbid=10156427464221561\&id=224837426560}{statement}.

The home is on a street shrouded with mature trees on a steep slope
above downtown Orinda, a white-collar bedroom community that is home to
technology executives, bankers and professors at the nearby University
of California, Berkeley. (Stephen Curry, the N.B.A. star,
\href{https://www.sfgate.com/realestate/article/Steph-Curry-puts-Orinda-home-on-market-for-3-895-7444269.php}{used
to live there} as well.)

Officials said the
\href{https://www.nytimes3xbfgragh.onion/2015/10/10/your-money/new-worry-for-home-buyers-a-party-house-next-door.html}{party
took place in a home that was listed on a short-term rental website}.
Though officials did not identify the website, the company Airbnb said
in a statement that it was ``horrified by this tragedy'' and offered
support to local officials in the investigation.

In response to the episode, Airbnb
\href{https://twitter.com/Airbnb/status/1190698126148960256}{said on
Twitter} on Saturday that it was stepping up its efforts to ``combat
unacceptable and abusive behavior on our platform that can lead to
tragic incidents.''

Brian Chesky, the company's chief executive,
\href{https://twitter.com/bchesky/status/1190675126594879489}{outlined
in a series of tweets} how the company plans to ban ``party houses'' and
``get rid of abusive host and guest conduct.''

The company will expand manual screening of high-risk reservations,
create a ``party house'' rapid response team and take immediate action
against users who violate guest policies, Mr. Chesky said.

An invitation for an ``Airbnb Mansion Party'' was posted to Instagram
and has since been deleted, according to the local news outlet
\href{https://www.ktvu.com/news/four-dead-others-injured-at-halloween-party-in-orinda-airbnb-horrified-about-tragedy}{KTVU}.
Guests were asked to bring their own alcohol.

Romond Reynolds, the father of one of the shooting victims, had come by
the property to retrieve his son's car and
\href{https://www.ktvu.com/news/four-dead-others-injured-at-halloween-party-in-orinda-airbnb-horrified-about-tragedy}{was
interviewed by KTVU}. His son, Armani, was in stable condition, he told
the station, but he had been ``in the wrong place at the wrong time.''

Mayor Inga Miller of Orinda called the shooting ``a tragedy of
unimaginable gravity'' and said the City Council would revisit existing
rules governing short-term rentals.

The city manager, Steve Salomon, said at the news conference that the
rental property had been the subject of two previous complaints months
ago regarding large parties and trash. Both of the complaints were
resolved.

He said a city ordinance requires short-term rentals to register with
the city, which this property did. The ordinance allows up to 13 people
at a short-term rental.

Referring to the city's rules, Mr. Salomon said: ``The challenge and the
underlying problem is these are not being followed. There are going to
be folks who don't follow the rules and, unfortunately, that's the way
the world works.''

The shooting occurred two days after three people were killed and nine
others injured at a
\href{https://www.nytimes3xbfgragh.onion/2019/10/30/us/long-beach-shooting.html?rref=collection\%2Fbyline\%2Felian-peltier\&action=click\&contentCollection=undefined\&region=stream\&module=stream_unit\&version=latest\&contentPlacement=2\&pgtype=collection}{Halloween
party in Long Beach}, Calif., 25 miles south of Los Angeles. Three
people were killed and at least 13 others were injured in a shooting at
a
\href{https://www.nytimes3xbfgragh.onion/2019/07/30/us/gilroy-garlic-fest-shooting.html?module=inline}{food
festival in Northern California} in July.

Thomas Fuller reported from Orinda, Jacey Fortin and Emily S. Rueb from
New York, and Elian Peltier from London. Christopher Mele and Mariel
Padilla contributed reporting from New York. Susan C. Beachy contributed
research.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
