Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/business/economy}{Economy}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/business/economy}{Economy}\textbar{}\$600 Unemployment:
What Happens When a Stimulus Lifeline Ends

\url{https://nyti.ms/3f1y8Ge}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{the-coronavirus-outbreak}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=8c437000-e39a-11ea-adda-c17bab336bc5}{The
Coronavirus
Outbreak}}{The Coronavirus Outbreak}}\label{the-coronavirus-outbreak}}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes3xbfgragh.onion/2020/08/21/world/covid-19-coronavirus.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=8c437001-e39a-11ea-adda-c17bab336bc5}{Latest
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/coronavirus-us-cases.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=8c437002-e39a-11ea-adda-c17bab336bc5}{Maps
  and Cases}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/science/coronavirus-vaccine-tracker.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=8c437003-e39a-11ea-adda-c17bab336bc5}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/08/19/us/colleges-closing-covid.html?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=8c437004-e39a-11ea-adda-c17bab336bc5}{Colleges
  Closing}
\item
  \href{https://www.nytimes3xbfgragh.onion/live/2020/08/20/business/stock-market-today-coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=8c439710-e39a-11ea-adda-c17bab336bc5}{Economy}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{600-unemployment-what-happens-when-a-stimulus-lifeline-ends}{%
\section{\$600 Unemployment: What Happens When a Stimulus Lifeline
Ends}\label{600-unemployment-what-happens-when-a-stimulus-lifeline-ends}}

By Ella KoezeUpdated July 27, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

After July 31, millions of out-of-work Americans will likely lose ****
\href{https://www.nytimes3xbfgragh.onion/2020/07/23/business/economy/unemployment-benefits.html}{an
additional \$600 a week} in unemployment benefits that have helped them
weather the coronavirus pandemic. Lawmakers are negotiating a new relief
package, and any extension of additional aid is expected to be
\href{https://www.nytimes3xbfgragh.onion/2020/07/27/world/coronavirus-covid-19.html}{a
fraction of what it currently is}.

Depending on income and where someone lives, regular unemployment
benefits replace only a portion of lost wages. The lower-income workers
who were benefiting the most from the \$600 lifeline will feel its loss
most acutely.

These are the estimated unemployment payments for each state and the
national average for different income levels.

Currently, with the additional \$600, an unemployed person who had been
making \$35,000 a year would, on average, receive about \$944 a week in
unemployment benefits.

We calculated how much of each person's previous income is replaced by
the unemployment payments they receive. It's what economists call the
replacement rate --- the share of someone's normal income that
unemployment benefits make up.

To put that in context, for the person earning \$35,000, their average
replacement rate is about 140 percent of what she or he would have
previously earned at work.

With the additional \$600, many lower-income workers earned more on
unemployment, on average, than they had in their previous jobs.

Without the additional \$600, the share of income replaced by the
unemployment benefit falls sharply for everyone, but lower-income
workers feel the hit the most.

The person who had been receiving 140 percent of their weekly income on
average would now receive only 51 percent of their income.

Democrats have made proposals to extend the \$600 additional benefit
through the end of the year. Republican leaders on Monday proposed a
plan to provide payments of up to \$500 that, when combined with normal
state benefits, could cover 70\% percent of many recipients' salaries.

If approved, the 70-percent plan would go into effect until October in
order to give states time to put in place the new system. As a stopgap
solution, Republicans have suggested adding a flat \$200 to unemployment
benefits when the \$600 payments expire.

Unemployment benefits are typically meant to keep people afloat while
staying low enough to spur them to find a job. But as the economy
hurtled into a recession early this year, and the pandemic has kept many
businesses closed or at limited capacity, jobs have disappeared for
many.

The extra \$600 unemployment benefits have injected billions into the
economy, and if those benefits shrink, that missing boost could cause
widespread damage.

The idea of basing benefits on workers' previous wages, which is central
to the Republican plan,
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/04/23/business/economy/unemployment-benefits-stimulus-coronavirus.html}{isn't
new}. It's a factor in how states determine the benefits they give out,
which is one reason benefits may vary depending on the location.

Here's how unemployment benefits could shift in every state if the \$600
expires, ordered from the lowest to the highest level of benefits for
someone who makes \$35,000 a year:

Plus \$600

70\% Plan

Regular

Estimated payments in each state were calculated using an
\href{https://github.com/ganong-noel/ui_calculator}{unemployment
benefits calculator} developed by researchers at the University of
Chicago. The calculator uses state unemployment eligibility requirements
and rules to estimate the regular unemployment benefits of a worker
without dependents, as of January 2020. The calculator may not capture
every rule in every state, and estimated payments may not match an
individual's actual payments. These estimates assume that annual income
was earned over 52 40-hour weeks. Averages do not include Washington
D.C. or any territories.

Source: Peter Ganong, Pascal Noel, Peter Robertson and Joseph Vavra,
University of Chicago

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
