Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/corrections}{Corrections}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/corrections}{Corrections}\textbar{}Corrections: Aug. 4,
2020

\url{https://nyti.ms/3i480MN}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{corrections-aug-4-2020}{%
\section{Corrections: Aug. 4, 2020}\label{corrections-aug-4-2020}}

Corrections that appeared in print on Monday, Aug. 4, 2020.

Aug. 3, 2020

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{front-page}{%
\subsection{FRONT PAGE}\label{front-page}}

An
\href{https://www.nytimes3xbfgragh.onion/2020/08/02/technology/florida-teenager-twitter-hack.html}{article}
on Monday about the teenager who recently hacked Twitter misattributed a
quote to Colby Meeds and referred incorrectly to his relationship with
Graham Ivan Clark. Referring to Mr. Clark, Mr. Meeds said, ``He scammed
me for a little bit of money when I was just a kid,'' not that Mr. Clark
``would do anything for money.'' Also, Mr. Meeds was a fellow player of
Minecraft, not a friend of Mr. Clark's.

An
\href{https://www.nytimes3xbfgragh.onion/2020/07/31/business/europe-economy-recovery-coronavirus.html}{article}
on Saturday about signs of economic recovery in Europe misstated the
total value of the bonds to be sold under an agreement reached by
European Union members this month. The countries agreed to sell 750
billion euros' worth of bonds, not 750 million.

\hypertarget{international}{%
\subsection{INTERNATIONAL}\label{international}}

An
\href{https://www.nytimes3xbfgragh.onion/2020/07/31/world/middleeast/Middle-East-heat-wave.html}{article}
on Saturday about a heat wave in the Middle East misspelled the surname
of the director of the World Weather Research Program. It is Paolo Ruti,
not Rutti.

\hypertarget{national}{%
\subsection{NATIONAL}\label{national}}

An
\href{https://www.nytimes3xbfgragh.onion/2020/08/01/us/politics/trump-suburban-voters-republicans-house.html}{article}
on Saturday referred incorrectly to the political affiliations of Cass
and Samantha Mattison of Texas. They are Republican, but they are not
registered Republicans. (In Texas, voters do not register by party
affiliation.)

\hypertarget{business}{%
\subsection{BUSINESS}\label{business}}

An
\href{https://www.nytimes3xbfgragh.onion/2020/08/01/business/video-game-remake-remaster-nostalgia.html}{article}
on Monday about remakes and remasters of popular video games misstated
the plans of the publisher Capcom for the game Resident Evil 4. The
company has not announced plans to remake the game.

\hypertarget{arts}{%
\subsection{ARTS}\label{arts}}

A television
\href{https://www.nytimes3xbfgragh.onion/2020/08/01/arts/television/whats-on-tv-saturday-seeing-america-with-megan-rapinoe-and-the-last-narc.html}{entry}
in the Listings Pages on Saturday about ``Sullivan's Travels'' misstated
the given name of an actor in ``Sullivan's Travels.'' He is Joel McCrea,
not Joe.

An
\href{https://www.nytimes3xbfgragh.onion/2020/07/31/arts/music/beyonce-black-is-king.html}{article}
on Monday about Beyoncé's ``Black Is King'' referred incorrectly to the
contribution by the musician Tekno. He performs background vocals on the
album, but he does not appear in the visual album.

\emph{Errors are corrected during the press run whenever possible, so
some errors noted here may not have appeared in all editions.}

\emph{To contact the newsroom regarding correction requests, complaints
or other comments about our coverage, please email}
\href{mailto:nytnews@NYTimes.com}{\emph{nytnews@NYTimes.com}}\emph{.}

\emph{Comments on editorials may be emailed to}
\href{mailto:letters@NYTimes.com}{\emph{letters@NYTimes.com}}\emph{.}

\emph{For newspaper delivery questions: 1-800-NYTIMES (1-800-698-4637)
or email}
\href{mailto:customercare@NYTimes.com}{\emph{customercare@NYTimes.com}}\emph{.}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
