 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{/section/politics}{Politics} \textbar{}The Russian Hacking in 200
Words

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2hxJszD}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-politics-}{%
\subsection{\texorpdfstring{ \href{/section/politics}{Politics}
}{ Politics }}\label{-politics-}}

\hypertarget{the-russian-hacking-in-200-words}{%
\section{The Russian Hacking in 200
Words}\label{the-russian-hacking-in-200-words}}

President Obama
\href{https://www.nytimes3xbfgragh.onion/2016/12/29/us/politics/russia-election-hacking-sanctions.html}{announced
sanctions} against Russia for trying to influence the 2016 election
through cyberattacks. Here's what led to the sanctions.

\hypertarget{the-hack}{%
\subsection{The Hack}\label{the-hack}}

Two state-sponsored hackers in Russia are believed to have broken into
the Democratic National Committee servers in 2015 and 2016.

Hackers are believed to have created outlets on the internet to make the
\href{https://www.nytimes3xbfgragh.onion/2016/12/09/us/obama-russia-election-hack.html}{Democratic
documents public}. Political bloggers and newspapers reported on the
hacked material.

\hypertarget{the-rift}{%
\subsection{The Rift}\label{the-rift}}

Leaks of documents stolen from the Democratic Congressional Campaign
Committee caused a backlash against Democrats in nearly a
\href{https://www.nytimes3xbfgragh.onion/2016/12/13/us/politics/house-democrats-hacking-dccc.html}{dozen
House races}.

Leaked emails forced the
\href{https://www.nytimes3xbfgragh.onion/2016/07/25/us/politics/debbie-wasserman-schultz-dnc-wikileaks-emails.html}{D.N.C.
chairwoman} to resign and fueled a rift between supporters of Senator
Bernie Sanders and Hillary Clinton.

Hacked emails from the account of
\href{https://www.nytimes3xbfgragh.onion/2016/10/12/us/politics/hillary-clinton-emails-wikileaks.html?_r=0}{Mrs.
Clinton's campaign chairman} revealed the campaign's internal dynamics
and dominated the news for days.

\hypertarget{the-response}{%
\subsection{The Response}\label{the-response}}

In September, President Obama
\href{https://www.nytimes3xbfgragh.onion/2016/12/16/us/politics/obama-putin-hacking-news-conference.html}{warned
President Vladimir V. Putin} of Russia to stay out of the American
elections.

On Thursday, the Obama administration
\href{https://www.nytimes3xbfgragh.onion/2016/12/29/us/politics/russia-election-hacking-sanctions.html}{imposed
sanctions} on two intelligence services, four top officers and three
companies in Russia.

The administration also expelled 35 Russian diplomats and their
families. Officials say some may have been linked to the cyberattacks.

The State Department shut down two ``recreational facilities'' in New
York and Maryland that were allegedly used for Russian intelligence
activities.

By Haeyoun Park and Larry Buchanan

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
