Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/politics}{Politics}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/politics}{Politics}\textbar{}The Donors Powering the
Campaign of Bernie Sanders

\url{https://nyti.ms/2GJWiq5}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\begin{itemize}
\item
  \href{https://www.nytimes.com/2020/07/31/us/elections/biden-vs-trump.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Election
  Updates}
\item
  \href{https://www.nytimes.com/article/biden-vice-president-2020.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Biden's
  V.P. Search}
\item
  \href{https://www.nytimes.com/interactive/2020/07/24/us/politics/trump-biden-campaign-donors.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Map
  of Donations}
\item
  \href{https://www.nytimes.com/interactive/2020/us/elections/delegate-count-primary-results.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Delegate
  Count}
\item
  \href{https://www.nytimes.com/interactive/2019/us/politics/2020-presidential-candidates.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{The
  Candidates}
\item
  \href{https://www.nytimes.com/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Politics
  Newsletter}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{the-donors-powering-the-campaign-of-bernie-sanders}{%
\section{The Donors Powering the Campaign of Bernie
Sanders}\label{the-donors-powering-the-campaign-of-bernie-sanders}}

By \href{https://www.nytimes.com/by/kk-rebecca-lai}{K.K. Rebecca Lai},
\href{https://www.nytimes.com/by/josh-katz}{Josh Katz},
\href{https://www.nytimes.com/by/rachel-shorey}{Rachel Shorey},
\href{https://www.nytimes.com/by/thomas-kaplan}{Thomas Kaplan} and
\href{https://www.nytimes.com/by/derek-watkins}{Derek Watkins}Feb. 2,
2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

\hypertarget{candidates-with-the-most-individual-donors}{%
\subsubsection{Candidates with the most individual
donors}\label{candidates-with-the-most-individual-donors}}

\hypertarget{darker-shades-on-the-map-indicate-a-greater-share-of-estimated-donors}{%
\paragraph{Darker shades on the map indicate a greater share of
estimated
donors.}\label{darker-shades-on-the-map-indicate-a-greater-share-of-estimated-donors}}

1. Sanders

1,395,000

1. Sanders

1,395,000

2. Warren

892,000

2. Warren

892,000

3. Buttigieg

741,000

3. Buttigieg

741,000

4. Biden

451,000

4. Biden

451,000

5. Yang

397,000

5. Yang

397,000

6. Klobuchar

227,000

6. Klobuchar

227,000

Note: Data is through Dec. 31.

Senator
\href{https://www.nytimes.com/interactive/2020/us/elections/bernie-sanders.html}{Bernie
Sanders} of Vermont received donations from an estimated 1.4 million
people through the end of 2019 --- far more than any other candidate in
the Democratic primary race, according to fund-raising records filed
with the Federal Election Commission. The map above shows his expansive
donor base around the country, including in Iowa, whose caucuses will be
held on Monday.

Mr. Sanders is powering his campaign with small donations from
supporters across the United States, and he collected
\href{https://www.nytimes.com/interactive/2020/02/01/us/elections/democratic-q4-fundraising.html}{\$96
million} from donors in 2019 without holding a single high-dollar
fund-raising event.

Our
\href{https://www.nytimes.com/interactive/2019/08/02/us/politics/2020-democratic-fundraising.html}{analysis
of fund-raising records} six months ago also showed his overwhelming
strength in attracting donors around the country.

The map below --- which includes the rest of the Democratic field
without Mr. Sanders --- provides a picture of where the other leading
candidates are attracting donors.

\hypertarget{candidates-with-the-most-individual-donors-when-sanders-is-excluded}{%
\subsubsection{Candidates with the most individual donors when Sanders
is
excluded}\label{candidates-with-the-most-individual-donors-when-sanders-is-excluded}}

\hypertarget{where-bernie-sanders-is-leading-the-runner-up-is-shown-darker-shades-on-the-map-indicate-a-greater-share-of-estimated-donors}{%
\paragraph{Where Bernie Sanders is leading, the runner-up is shown.
Darker shades on the map indicate a greater share of estimated
donors.}\label{where-bernie-sanders-is-leading-the-runner-up-is-shown-darker-shades-on-the-map-indicate-a-greater-share-of-estimated-donors}}

1. Sanders

1,395,000

1. Sanders

1,395,000

2. Warren

892,000

2. Warren

892,000

3. Buttigieg

741,000

3. Buttigieg

741,000

4. Biden

451,000

4. Biden

451,000

5. Yang

397,000

5. Yang

397,000

6. Klobuchar

227,000

6. Klobuchar

227,000

Senator
\href{https://www.nytimes.com/interactive/2020/us/elections/elizabeth-warren.html}{Elizabeth
Warren} of Massachusetts, who like Mr. Sanders is relying on grass-roots
support, has the second largest number of donors in most states. While
she, too, has found success with that strategy, she has not matched Mr.
Sanders's success.

\href{https://www.nytimes.com/interactive/2020/us/elections/pete-buttigieg.html}{Pete
Buttigieg}, the former mayor of South Bend, Ind., has the second largest
number of donors in Iowa as well as in New Hampshire, which will hold
the nation's first primary on Feb. 11.

\hypertarget{sanders-leads-in-early-states}{%
\subsection{Sanders Leads in Early
States}\label{sanders-leads-in-early-states}}

Looking at these numbers by state, Mr. Sanders is leading in all of the
early states as well as all of the Super Tuesday states, except for Ms.
Warren's home state, Massachusetts, and Senator
\href{https://www.nytimes.com/interactive/2020/us/elections/amy-klobuchar.html}{Amy
Klobuchar}'s home state, Minnesota.

\hypertarget{how-each-candidate-ranks-in-number-of-individual-donors-by-state}{%
\subsubsection{How each candidate ranks in number of individual donors,
by
state}\label{how-each-candidate-ranks-in-number-of-individual-donors-by-state}}

\hypertarget{sanderss-donor-base-has-multiplied-over-time}{%
\subsection{Sanders's Donor Base Has Multiplied Over
Time}\label{sanderss-donor-base-has-multiplied-over-time}}

This chart shows the estimated number of unique individuals who had
given to each candidate over the course of 2019. Mr. Sanders's huge base
of donors is evident from the moment he
\href{https://www.nytimes.com/2019/02/19/us/politics/bernie-sanders-2020.html}{joined
the race} last February.

Methodology

Data includes individual donations reported by campaigns to the Federal
Election Commission as well as those made through
\href{https://www.fec.gov/data/committee/C00401224/}{ActBlue}, an online
fund-raising platform that processes donations for Democratic
candidates. These sources combined account for roughly 91 percent of
dollars donated to candidates by individuals. Information about donors
giving \$200 or less directly to a campaign is not available.

The number of individual donors was estimated based on the name and ZIP
code of the donor. The New York Times approximated donors' locations
from their ZIP codes, then took a weighted average of the nearest donors
for each location. Shapes are combined census tracts, each containing at
least one donor.

Estimates of donor counts are based on data through Dec. 31.

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

\hypertarget{our-2020-election-guide}{%
\section{Our 2020 Election Guide}\label{our-2020-election-guide}}

Updated July 31, 2020

\begin{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{the-latest}{%
  \subsection{The Latest}\label{the-latest}}

  \begin{itemize}
  \tightlist
  \item
    President Trump's assault on the Postal Service is intersecting with
    his attacks on mail-in voting.
    \href{https://www.nytimes.com/2020/07/31/us/politics/trump-usps-mail-delays.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{Voting
    rights groups say it is a recipe for disaster.}
  \end{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{bidens-vp-search}{%
  \subsection{Biden's V.P. Search}\label{bidens-vp-search}}

  \begin{itemize}
  \tightlist
  \item
    \href{https://www.nytimes.com/article/biden-vice-president-2020.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{Here
    are 13 women} who have been under consideration to be Joe Biden's
    running mate, and why each might be chosen --- and might not be.
  \end{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{keep-up-with-our-coverage}{%
  \subsection{Keep Up With Our
  Coverage}\label{keep-up-with-our-coverage}}

  \begin{itemize}
  \tightlist
  \item
    Get an
    \href{https://www.nytimes.com/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{email}
    recapping the day's news
  \end{itemize}

  \begin{itemize}
  \tightlist
  \item
    Download our mobile app on
    \href{https://apps.apple.com/us/app/nytimes/id284862083?ls=1\&mat_click_id=5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\&referrer=mat_click_id\%3D5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\%26link_click_id\%3D722930677036718082}{iOS}
    and
    \href{http://a.localytics.com/android?id=com.nytimes.android\&referrer=utm_source\%3Dother_nyt_mobile_web\%26utm_medium\%3DWeb\%2520page\%26utm_term\%3DGeneral\%2520Mobile\%2520Page\%26utm_campaign\%3DNYT\%2520Mobile\%2520General\%2520Page}{Android}
    and turn on Breaking News and Politics alerts
  \end{itemize}
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
