Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/politics}{Politics}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/politics}{Politics}\textbar{}Who's Running for President
in 2020?

\url{https://nyti.ms/2HpNjgP}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\begin{itemize}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/08/03/us/elections/biden-vs-trump.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Election
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/article/biden-vice-president-2020.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Biden's
  V.P. Search}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/07/24/us/politics/trump-biden-campaign-donors.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Map
  of Donations}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/elections/delegate-count-primary-results.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Delegate
  Count}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2019/us/politics/2020-presidential-candidates.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{The
  Candidates}
\item
  \href{https://www.nytimes3xbfgragh.onion/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Politics
  Newsletter}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{whos-running-for-president-in-2020}{%
\section{Who's Running for President in
2020?}\label{whos-running-for-president-in-2020}}

By
\href{https://www.nytimes3xbfgragh.onion/by/alexander-burns}{Alexander
Burns},
\href{https://www.nytimes3xbfgragh.onion/by/matt-flegenheimer}{Matt
Flegenheimer},
\href{https://www.nytimes3xbfgragh.onion/by/jasmine-c-lee}{Jasmine C.
Lee}, \href{https://www.nytimes3xbfgragh.onion/by/lisa-lerer}{Lisa
Lerer} and
\href{https://www.nytimes3xbfgragh.onion/by/jonathan-martin}{Jonathan
Martin}Updated April 8, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Running

Biden

Trump

Dropped Out

27 Democrats 3 Republicans

Sanders

Gabbard

Warren

Bloomberg

Klobuchar

Buttigieg

Steyer

Patrick

Yang

Bennet

Delaney

Booker

Williamson

Castro

Harris

Bullock

Sestak

Messam

O'Rourke

Ryan

de Blasio

Gillibrand

Moulton

Inslee

Hickenlooper

Swalwell

Ojeda

Weld

Walsh

Sanford

Former Vice President Joseph R. Biden Jr. is the presumptive Democratic
nominee to challenge President Trump in the 2020 race.

The field of Democratic presidential candidates was
\href{https://www.nytimes3xbfgragh.onion/interactive/2019/02/14/us/politics/2020-democratic-candidates-president.html}{historically
large}, but all others have dropped out. Mr. Trump had also picked up a
few Republican challengers, but they have also ended their campaigns.

Running

Joseph R. Biden Jr., 77

Former vice president; former senator from Delaware

Democrat

``If we give Donald Trump eight years in the White House, he will
forever and fundamentally alter the character of this nation, who we
are, and I cannot stand by and watch that happen.''

Has run for president twice
\href{https://www.nytimes3xbfgragh.onion/2019/06/03/us/politics/biden-1988-presidential-campaign.html}{before}.

Is known for his down-to-earth personality and his
\href{https://www.nytimes3xbfgragh.onion/2019/11/19/us/politics/joe-biden-working-class.html}{ability
to connect} with working-class voters.

His eight years
\href{https://www.nytimes3xbfgragh.onion/2019/08/16/us/politics/biden-obama-history.html}{as
Barack Obama's vice president} are a major selling point for many
Democrats.

\textbf{Signature issues:} Restoring America's standing on the global
stage; adding a public option to the Affordable Care Act; strengthening
economic protections for low-income workers in industries like
manufacturing and fast food.

\href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/elections/joe-biden.html}{See
Joe Biden's candidate profile page »}

Donald J. Trump, 74

U.S. president; real estate developer; reality television star

Republican

``Considering that we have done more than any administration in the
first two years, this should be easy. More great things now in the
works!''

Main legislative accomplishment as president: a
\href{https://www.nytimes3xbfgragh.onion/2017/12/22/us/politics/trump-tax-bill.html?module=inline}{sweeping
tax cut} that chiefly benefited corporations and wealthy investors.

Has focused on undoing the policies of the Obama administration,
including on
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/07/19/us/what-trump-can-do-to-let-obamacare-fail.html}{health
care},
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/12/26/us/politics/donald-trump-environmental-regulation.html?module=inline}{environmental
regulation} and immigration.

\href{https://www.nytimes3xbfgragh.onion/2019/12/18/us/politics/trump-impeached.html}{Was
impeached} by the House of Representatives for seeking to pressure
Ukraine to smear his political rivals, but
\href{https://www.nytimes3xbfgragh.onion/2020/02/05/us/politics/trump-acquitted-impeachment.html}{was
acquitted} by the Senate.

\textbf{Signature issues:} Restricting immigration and building a wall
at the Mexican border; renegotiating or canceling international deals on
trade, arms control and climate change; withdrawing American troops from
overseas.

\href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/elections/donald-trump.html}{See
Donald Trump's candidate profile page »}

Dropped Out

Democrat

Ended campaign April 8, 2020

Bernie Sanders, 78

Senator from Vermont; former congressman

\href{https://www.nytimes3xbfgragh.onion/2020/04/08/us/politics/bernie-sanders-drops-out.html}{Ended
his second bid for the Democratic nomination} in April 2020, after a
series of losses to Mr. Biden.

Democrat

Ended campaign March 19, 2020

Tulsi Gabbard, 39

Congresswoman from Hawaii; Army National Guard veteran

\href{https://www.nytimes3xbfgragh.onion/2020/03/19/us/politics/tulsi-gabbard-drops-out.html}{Ended
her campaign} in March 2020 and said she would back Mr. Biden.

Democrat

Ended campaign March 5, 2020

Elizabeth Warren, 70

Senator from Massachusetts; former Harvard professor

Dropped
\href{https://www.nytimes3xbfgragh.onion/2020/03/05/us/politics/elizabeth-warren-drops-out.html}{out
of the race} following a steady decline in support and a poor showing on
Super Tuesday.

Democrat

Ended campaign March 4, 2020

Michael R. Bloomberg, 78

Billionaire media executive; former mayor of New York City

\href{https://www.nytimes3xbfgragh.onion/2020/03/04/us/politics/michael-bloomberg-drops-out.html}{Dropped
out of the race} on the day after Super Tuesday and endorsed Mr. Biden.
He spent hundreds of millions of dollars of his own fortune on a
campaign that lasted just over three months.

Democrat

Ended campaign March 2, 2020

Amy Klobuchar, 60

Senator from Minnesota; former Hennepin County, Minn., attorney

Decided to
\href{https://www.nytimes3xbfgragh.onion/2020/03/02/us/politics/amy-klobuchar-drops-out.html}{quit
the race} a day before Super Tuesday and endorse a rival, Mr. Biden.

Democrat

Ended campaign March 1, 2020

Pete Buttigieg, 38

Former mayor of South Bend, Ind.; military veteran

\href{https://www.nytimes3xbfgragh.onion/2020/03/01/us/politics/pete-buttigieg-drops-out.html}{Decided
to quit} the race after a crushing loss in the South Carolina primary.
The first openly gay major presidential candidate, he rose to the
primary's top tier, but was unable to build a broad coalition of voters.

Democrat

Ended campaign Feb. 29, 2020

Tom Steyer, 62

Billionaire former hedge fund executive; climate change and impeachment
activist

\href{https://www.nytimes3xbfgragh.onion/2020/02/29/us/politics/tom-steyer-drops-out.html}{Exited
the race} after a disappointing finish in South Carolina, a state where
he had spent considerable resources and pinned the hopes of his
campaign.

Democrat

Ended campaign Feb. 12, 2020

Deval Patrick, 63

Former governor of Massachusetts

\href{https://www.nytimes3xbfgragh.onion/2020/02/12/us/politics/deval-patrick-drops-out.html}{Dropped
out} the day after receiving less than 1 percent of the vote in the New
Hampshire primary. He entered a crowded field late in the game and
failed to catch on.

Democrat

Ended campaign Feb. 11, 2020

Andrew Yang, 45

Former tech executive who founded an economic development nonprofit

\href{https://www.nytimes3xbfgragh.onion/2020/02/11/us/politics/andrew-yang-drops-out.html}{Ended
his presidential bid} at a primary-night party in New Hampshire after a
yearslong campaign that endured even as those of members of Congress and
governors fell away. He had failed to win
any\href{https://www.nytimes3xbfgragh.onion/interactive/2020/02/04/us/elections/results-iowa-caucus.html}{}\href{https://www.nytimes3xbfgragh.onion/interactive/2020/02/04/us/elections/results-iowa-caucus.html}{pledged
delegates in Iowa}.

Democrat

Ended campaign Feb. 11, 2020

Michael Bennet, 55

Senator from Colorado

\href{https://www.nytimes3xbfgragh.onion/2020/02/11/us/politics/michael-bennet-drops-out.html}{Announced
in}\href{https://www.nytimes3xbfgragh.onion/2020/02/11/us/politics/michael-bennet-drops-out.html}{February
2020} that he was ending his bid for the Democratic nomination after a
dismal showing in the New Hampshire primary.

Democrat

Ended campaign Jan. 31, 2020

John Delaney, 57

Former congressman from Maryland; former businessman

\href{https://www.nytimes3xbfgragh.onion/2020/01/31/us/politics/john-delaney-drops-out.html}{Dropped
out of the race} just three days before the Iowa caucuses, ending a
two-and-a-half-year presidential campaign, one of the longest in
American history.

Democrat

Ended campaign Jan. 13, 2020

Cory Booker, 51

Senator from New Jersey; former mayor of Newark

\href{https://www.nytimes3xbfgragh.onion/2020/01/13/us/politics/cory-booker-drops-out.html}{Dropped
out of the race} in January 2020 just weeks before the Iowa caucuses
after failing to qualify for the debate stage twice in a row. He ended a
nearly yearlong quest built around a message of peace and unity that
failed to resonate with voters.

Democrat

Ended campaign Jan. 10, 2020

Marianne Williamson, 67

Self-help author, new age lecturer

Announced in January 2020 that she would
\href{https://www.nytimes3xbfgragh.onion/2020/01/10/us/politics/marianne-williamson-dropping-out.html}{end
her long-shot presidential campaign}. She had been averaging less than 1
percent in polls and had not qualified for a debate since July 2019.

Democrat

Ended campaign Jan. 2, 2020

Julián Castro, 45

Former housing secretary; former mayor of San Antonio

Ended his bid for the presidency in January 2020, after failing to break
into the upper tier of a crowded primary field. He quickly
\href{https://www.nytimes3xbfgragh.onion/2020/01/06/us/politics/julian-castro-endorsement-elizabeth-warren.html}{endorsed}
Senator Elizabeth Warren for president.

Democrat

Ended campaign Dec. 3, 2019

Kamala Harris, 55

Senator from California; former attorney general of California; former
San Francisco district attorney

\href{https://www.nytimes3xbfgragh.onion/2019/12/03/us/politics/kamala-harris-campaign-drops-out.html}{Dropped
out of the race} in December 2019 after months of slumping poll numbers.
She began in the top tier of candidates, but her campaign unraveled in
the second half of 2019 and she said she no longer had the money needed
to compete.

Democrat

Ended campaign Dec. 2, 2019

Steve Bullock, 54

Governor of Montana; former state attorney general

\href{https://www.nytimes3xbfgragh.onion/2019/12/02/us/politics/steve-bullock-2020-drops-out.html}{Dropped
out} in December 2019, saying that he wouldn't ``be able to break
through to the top tier of this still-crowded field of candidates.''

Democrat

Ended campaign Dec. 1, 2019

Joe Sestak, 68

Former congressman from Pennsylvania; former Navy admiral

\href{https://www.nytimes3xbfgragh.onion/2019/12/01/us/politics/joe-sestak-ends-presidential-campaign.html}{Ended
his campaign} in December 2019, after averaging zero percent in the
polls.

Democrat

Ended campaign Nov. 20, 2019

Wayne Messam, 46

Mayor of Miramar, Fla.; former college football champion

\href{https://www.nytimes3xbfgragh.onion/2019/11/20/us/politics/wayne-messam-2020.html}{Dropped
out} of the race in November 2019 after failing to qualify for any of
the Democratic debates.

Democrat

Ended campaign Nov. 1, 2019

Beto O'Rourke, 47

Former congressman from Texas; 2018 Senate candidate

\href{https://www.nytimes3xbfgragh.onion/2019/11/01/us/politics/beto-orourke-drops-out.html}{Ended
his campaign} in November 2019 after struggling for months to recapture
the energy of his 2018 Senate candidacy on national stage. He is not
expected to run for any other office in 2020.

Democrat

Ended campaign Oct. 24, 2019

Tim Ryan, 46

Congressman from Ohio; former congressional staff member

\href{https://www.nytimes3xbfgragh.onion/2019/10/24/us/politics/tim-ryan-drops-out.html}{Ended
his campaign} in October 2019 and said he would run for re-election to
his House seat.

Democrat

Ended campaign Sept. 20, 2019

Bill de Blasio, 59

Mayor of New York City

Announced he was
\href{https://www.nytimes3xbfgragh.onion/2019/09/20/nyregion/de-blasio-2020-drops-out.html}{ending
his presidential campaign} in September 2019 after it became clear that
he was unlikely to qualify for the October debate.

Democrat

Ended campaign Aug. 28, 2019

Kirsten Gillibrand, 53

Senator from New York; former congresswoman

\href{https://www.nytimes3xbfgragh.onion/2019/08/28/us/politics/kirsten-gillibrand-2020-drop-out.html}{Withdrew
from the presidential race} in August 2019, saying that failing to
qualify for the September debate was fatal to her candidacy. She said
she would continue to champion issues of women's equality and support
women running for Congress.

Democrat

Ended campaign Aug. 23, 2019

Seth Moulton, 41

Congressman from Massachusetts; Iraq War veteran

\href{https://www.nytimes3xbfgragh.onion/2019/08/23/us/politics/seth-moulton-2020-drop-out.html}{Withdrew
from the presidential race} in August 2019 and said he would run for
re-election to the House. He also said he would relaunch his political
action committee, Serve America, to promote issues related to veterans
and the military.

Democrat

Ended campaign Aug. 21, 2019

Jay Inslee, 69

Governor of Washington State; former congressman

\href{https://www.nytimes3xbfgragh.onion/2019/08/21/us/politics/jay-inslee-2020-campaign.html?action=click\&module=Latest\&pgtype=Homepage}{Dropped
out} of the 2020 race in August 2019, after struggling to earn a place
in the September debates. He plans to run for a third term for governor
and wants to advise the Democratic field on climate policy.

Democrat

Ended campaign Aug. 15, 2019

John Hickenlooper, 68

Former governor of Colorado; former mayor of Denver

Announced in August 2019 that he was
\href{https://www.nytimes3xbfgragh.onion/2019/08/15/us/politics/john-hickenlooper-drop-out-senate.html}{ending
his presidential campaign} after months of failing to gain significant
traction. He will instead
\href{https://www.nytimes3xbfgragh.onion/2019/08/22/us/politics/john-hickenlooper-senate-2020.html}{run
for}\href{https://www.nytimes3xbfgragh.onion/2019/08/22/us/politics/john-hickenlooper-senate-2020.html}{the
Republican-held Senate} seat in Colorado that is up for election in
2020.

Democrat

Ended campaign July 8, 2019

Eric Swalwell, 39

Congressman from California

Announced in July 2019 that he was
\href{https://www.nytimes3xbfgragh.onion/2019/07/08/us/politics/steyer-swalwell-2020.html}{ending
his campaign} and would seek a fifth term in the House, where he
represents Northern California's East Bay.

Democrat

Ended campaign Jan. 25, 2019

Richard Ojeda, 49

Former West Virginia state senator; military veteran

\href{https://www.facebookcorewwwi.onion/RichardOjeda2020/posts/2329884223911515}{Suspended
his short-lived campaign} in late January 2019, acknowledging that he
did ``not have the ability to compete.'' At that time, only a handful of
candidates had officially entered the race.

Republican

Ended campaign March 18, 2020

William F. Weld, 74

Former governor of Massachusetts; former federal prosecutor

\href{https://www.nytimes3xbfgragh.onion/2020/03/18/us/politics/bill-weld-drops-out.html}{Ended
his campaign} in March 2020, a day after Mr. Trump officially racked up
enough delegates to become the presumptive 2020 Republican nominee for
president.

Republican

Ended campaign Feb. 7, 2020

Joe Walsh, 58

Conservative radio show host; former congressman from Illinois

\href{https://www.nytimes3xbfgragh.onion/2020/02/07/us/politics/joe-walsh-drops-out.html}{Ended
his campaign} for the Republican nomination in February 2020.

Republican

Ended campaign Nov. 12, 2019

Mark Sanford, 60

Former congressman from South Carolina, former governor of the state

\href{https://www.nytimes3xbfgragh.onion/2019/11/12/us/politics/mark-sanford-2020.html}{Ended
his long-shot primary challenge} to President Trump in November 2019,
saying that the impeachment inquiry had made it impossible for his
message of fiscal conservatism to break through.

Additional reporting by Isabella Grullón Paz and Matt Stevens.
Additional work by Allison McCann.

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

\hypertarget{our-2020-election-guide}{%
\section{Our 2020 Election Guide}\label{our-2020-election-guide}}

Updated Aug. 3, 2020

\begin{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{the-latest}{%
  \subsection{The Latest}\label{the-latest}}

  \begin{itemize}
  \tightlist
  \item
    President Trump again assails mail-in voting,
    \href{https://www.nytimes3xbfgragh.onion/2020/08/03/us/politics/trump-mail-in-voting.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{claiming
    without evidence that the process is plagued by fraud}.
  \end{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{bidens-vp-search}{%
  \subsection{Biden's V.P. Search}\label{bidens-vp-search}}

  \begin{itemize}
  \tightlist
  \item
    \href{https://www.nytimes3xbfgragh.onion/article/biden-vice-president-2020.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{Here
    are 13 women} who have been under consideration to be Joe Biden's
    running mate, and why each might be chosen --- and might not be.
  \end{itemize}
\item
  \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

  \hypertarget{keep-up-with-our-coverage}{%
  \subsection{Keep Up With Our
  Coverage}\label{keep-up-with-our-coverage}}

  \begin{itemize}
  \tightlist
  \item
    Get an
    \href{https://www.nytimes3xbfgragh.onion/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{email}
    recapping the day's news
  \end{itemize}

  \begin{itemize}
  \tightlist
  \item
    Download our mobile app on
    \href{https://apps.apple.com/us/app/nytimes/id284862083?ls=1\&mat_click_id=5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\&referrer=mat_click_id\%3D5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\%26link_click_id\%3D722930677036718082}{iOS}
    and
    \href{http://a.localytics.com/android?id=com.nytimes.android\&referrer=utm_source\%3Dother_nyt_mobile_web\%26utm_medium\%3DWeb\%2520page\%26utm_term\%3DGeneral\%2520Mobile\%2520Page\%26utm_campaign\%3DNYT\%2520Mobile\%2520General\%2520Page}{Android}
    and turn on Breaking News and Politics alerts
  \end{itemize}
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
