Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/sports}{Sports}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/sports}{Sports}\textbar{}Remaining Tour Riders Cleared of
Virus but Not Director

\url{https://nyti.ms/2ZhZQJK}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{remaining-tour-riders-cleared-of-virus-but-not-director}{%
\section{Remaining Tour Riders Cleared of Virus but Not
Director}\label{remaining-tour-riders-cleared-of-virus-but-not-director}}

By The Associated Press

\begin{itemize}
\item
  Sept. 8, 2020Updated 8:30 a.m. ET
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

The remaining Tour de France riders were cleared to continue racing
ahead of Tuesday's Stage 10 after undergoing COVID-19 tests, but the
Tour director tested positive and left the race.

Less than two hours before the stage started, Tour organizers and
cycling governing body the UCI said all of the riders' tests performed
over the past two days returned negative. However, they announced that
director Christian Prudhomme tested positive along with four staff
members from four different teams who have been dropped from the race
bubble.

The four staff who tested positive work for Cofidis, AG2R La Mondiale,
defending champion Egan Bernal's Inos Grenadiers and Mitchelton Scott,
meaning those four squads were at greater risk of being excluded.

Under the race's health protocols, anyone who tests positive has to
leave the race and any team with two or more positive tests --- either
rider or staff --- within seven days also has to abandon.

Prudhomme's positive test might have an impact on French political
affairs as it came only days after he spent two hours in his car
following a stage in the Pyrenees in the company of Prime Minister Jean
Castex.

As a result, French President Emmanuel Macron said a government meeting
scheduled on Wednesday will be organized via videoconference, or
postponed.

Speaking to France Info radio, Prudhomme said he does not have virus
symptoms, adding that he will stay in isolation for seven days.

``Obviously the most important thing is that not a single rider tested
positive," Prudhomme said. ``I did not come close to the riders over the
past 10 days, we can see now how important it was to stay away from
them."

Organizers said 841 tests were performed on riders and team members,
with most of the riders tested during the first rest day on Monday. The
next wave of tests will be during the next rest day on Sept. 14.

Under threat of cancellation at some point --- more than 30,000 people
in France have died after contracting the coronavirus --- the Tour has
been salvaged by pushing it back from its traditional July date to the
end of the summer. The price paid for the race to be run are strict
health protocols which include mandatory testing for riders and team
staff on rest days.

All were tested before the Tour started in Nice and have since lived in
the race bubble, making sure they stay away from fans and sponsors
usually omnipresent during the race's three weeks.

To avoid false positive results that could rule healthy riders out of
contention, Tour organizers perform a retest and a blood analysis as
quickly as possible in case of a positive test. They have set up a
mobile coronavirus lab that can produce results in two hours.

Following Sunday's stage in the Pyrenees, where Primoz Roglic of
Slovenia seized the yellow jersey, the 22 Tour teams traveled by bus to
the western Charente region.

The race resumed on Tuesday with a flat stage linking two islands, the
Ile d'Oleron and the Ile de Re. Only 165 riders took the start after
Domenico Pozzovivo of Italy quit. He said he did not recover from a
crash on Stage 1 and hopes to return at the Giro d'Italia.

Roglic leads defending champion Egan Bernal by 21 seconds. Frenchman
Guillaume Martin was in third place, 28 seconds off the pace.

\_\_\_

\_\_\_

Sylvie Corbet in Paris contributed to this report.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
