Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

Poem: Dark Period

\url{https://nyti.ms/2RCeB6M}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{poem-dark-period}{%
\section{Poem: Dark Period}\label{poem-dark-period}}

By Garous Abdolmalekian

\begin{itemize}
\item
  Jan. 30, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Plays on words and tiny twists mean much in a poem. In ``Lean Against
This Late Hour,'' his mesmerizing seventh collection of poems, Garous
Abdolmalekian makes us wonder: What if we could put a period on an
entire period? Turn a corner, change the tune? And who is that little
disappearing girl we barely see --- what world is she being given?
Something calms in the simple repetition of a word or thought and the
hopeful conviction of ``there will be.''

Image

\hypertarget{dark-period}{%
\subsection{Dark Period}\label{dark-period}}

By Garous Abdolmalekian

In this line\\
or the next one\\
there will be a period,\\
an end to all the words.

Within the stark frame of the window,\\
tired silhouettes\\
and the dark dress\\
of a little girl growing distant\\
 growing distant\\
 growing distant

In the stark frame of the window\\
a dark period\\
grows distant.

A period\\
that is the end to all the words.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{Naomi Shihab Nye} is the 2019-21 Young People's Poet Laureate of
the Poetry Foundation in Chicago and the 2019 recipient of the National
Book Critics Circle Ivan Sandrof Award for Lifetime Achievement.
\textbf{Garous Abdolmalekian} lives in Tehran. His poem is translated by
Ahmad Nadalizadeh and Idra Novey from the Persian in ``Lean Against This
Late Hour,'' forthcoming by Penguin Books. He is the poetry editor of
Chesmeh Publications and executive editor of publications at the Youth
Poetry Office in Iran.

Illustration by R.O. Blechman

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
