Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/science}{Science}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/science}{Science}\textbar{}Different Approaches to a
Coronavirus Vaccine

\url{https://nyti.ms/2Xjx6yq}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{the-coronavirus-outbreak}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=47986300-f2ab-11ea-83ce-15100f254d71\&variant=undefined}{The
Coronavirus
Outbreak}}{The Coronavirus Outbreak}}\label{the-coronavirus-outbreak}}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes3xbfgragh.onion/2020/09/09/world/covid-19-coronavirus.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=47986301-f2ab-11ea-83ce-15100f254d71\&variant=undefined}{Latest
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/coronavirus-us-cases.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=47988a10-f2ab-11ea-83ce-15100f254d71\&variant=undefined}{Maps
  and Cases}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/science/coronavirus-vaccine-tracker.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=47988a11-f2ab-11ea-83ce-15100f254d71\&variant=undefined}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/02/your-money/eviction-moratorium-covid.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=47988a12-f2ab-11ea-83ce-15100f254d71\&variant=undefined}{Eviction
  Moratorium}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/09/upshot/coronavirus-surprise-test-fees.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=47988a13-f2ab-11ea-83ce-15100f254d71\&variant=undefined}{Surprise
  Test Fees}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{different-approaches-to-a-coronavirus-vaccine}{%
\section{Different Approaches to a Coronavirus
Vaccine}\label{different-approaches-to-a-coronavirus-vaccine}}

By \href{https://www.nytimes3xbfgragh.onion/by/jonathan-corum}{Jonathan
Corum}, \href{https://www.nytimes3xbfgragh.onion/by/knvul-sheikh}{Knvul
Sheikh} and
\href{https://www.nytimes3xbfgragh.onion/by/carl-zimmer}{Carl Zimmer}May
20, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Spike protein

RNA for the

spike protein

Spike

protein

RNA for the

spike protein

Spike

protein

RNA for

the spike

protein

Scientists are developing
\href{https://www.nytimes3xbfgragh.onion/2020/05/20/health/coronavirus-vaccines.html}{more
than}\href{https://www.nytimes3xbfgragh.onion/2020/05/20/health/coronavirus-vaccines.html}{100}\href{https://www.nytimes3xbfgragh.onion/2020/05/20/health/coronavirus-vaccines.html}{coronavirus
vaccines} using a range of techniques, some of which are
well-established and some of which have never been approved for medical
use before.

Most of these vaccines target the so-called
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/04/03/science/coronavirus-genome-bad-news-wrapped-in-protein.html}{spike
proteins} that cover the virus and help it
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/03/11/science/how-coronavirus-hijacks-your-cells.html}{invade
human cells}. The immune system can develop antibodies that latch onto
spike proteins and stop the virus.

A successful vaccine for the SARS-CoV-2 coronavirus would teach people's
immune systems to make antibodies against the virus without causing
disease.

\hypertarget{whole-virus-vaccines}{%
\subsection{\texorpdfstring{\textbf{Whole-Virus
Vaccines}}{Whole-Virus Vaccines}}\label{whole-virus-vaccines}}

\emph{Vaccines that modify the entire coronavirus to provoke an immune
response.}

\hypertarget{inactivated-and-live-attenuated-vaccines}{%
\subsubsection{\texorpdfstring{\textbf{Inactivated and Live Attenuated
Vaccines}}{Inactivated and Live Attenuated Vaccines}}\label{inactivated-and-live-attenuated-vaccines}}

Most vaccines in use today incorporate an inactivated or weakened form
of a virus that is not able to cause disease. When immune cells
encounter them, they make antibodies.

Making these vaccines means growing viruses --- and lots of them.
Influenza vaccines are typically grown in chicken eggs, and other
vaccines are grown in tanks full of floating cells. These procedures can
take months to produce a batch of new vaccines.

EXAMPLES: Conventional vaccines for influenza, chickenpox, measles,
\href{https://www.nytimes3xbfgragh.onion/2020/05/02/us/politics/vaccines-coronavirus-research.html}{mumps}
and rubella all fall into this category.

COMPANIES DEVELOPING SARS-COV-2 VACCINES:
\href{https://www.nytimes3xbfgragh.onion/2020/05/04/business/coronavirus-china-vaccine.html}{Sinovac}
and others.

\hypertarget{genetic-vaccines}{%
\subsection{\texorpdfstring{\textbf{Genetic
Vaccines}}{Genetic Vaccines}}\label{genetic-vaccines}}

\emph{Vaccines that use part of the coronavirus's genetic code.}

DNA for the

spike protein

DNA for the

spike protein

DNA for the

spike protein

\hypertarget{dna-vaccines}{%
\subsubsection{\texorpdfstring{\textbf{DNA
Vaccines}}{DNA Vaccines}}\label{dna-vaccines}}

A number of experimental coronavirus vaccines don't deliver whole
viruses. Instead, they deliver genetic instructions for building a viral
protein. The protein can then stimulate the immune system to make
antibodies and help mount other defenses against the coronavirus.

One of these genetic approaches is known as a DNA vaccine. A circle of
engineered DNA is delivered into cells. The cells read the viral gene,
make a copy in a molecule called messenger RNA, and then use the mRNA to
assemble viral proteins. The immune system detects the proteins and
mounts defenses.

Prototype DNA vaccines based on the spike protein
\href{https://www.nytimes3xbfgragh.onion/2020/05/20/health/coronavirus-vaccine-harvard.html}{protected
monkeys} from the coronavirus.

EXAMPLES: DNA vaccines have been approved for veterinary cases such as
canine melanoma and West Nile virus in horses. There are no approved DNA
vaccines for use in humans, but researchers are running trials to see if
they might be effective for diseases such as Zika and the flu.

COMPANIES: Inovio and others.

RNA

RNA

RNA

\hypertarget{rna-vaccines}{%
\subsubsection{\texorpdfstring{\textbf{RNA
Vaccines}}{RNA Vaccines}}\label{rna-vaccines}}

Some researchers want to skip DNA and instead deliver messenger RNA into
cells. The cells read the mRNA and make spike proteins that provoke an
immune response.

The biotech company Moderna recently completed a small safety trial with
eight volunteers that showed
\href{https://www.nytimes3xbfgragh.onion/2020/05/18/health/coronavirus-vaccine-moderna.html}{promising
early results} against the coronavirus.

Both RNA and DNA vaccines can be produced more quickly than traditional
methods.

EXAMPLES: There are no approved RNA vaccines, but they are in clinical
trials for MERS and other diseases.

COMPANIES:
\href{https://www.nytimes3xbfgragh.onion/2020/05/18/health/coronavirus-vaccine-moderna.html}{Moderna},
\href{https://www.nytimes3xbfgragh.onion/2020/05/05/health/pfizer-vaccine-coronavirus.html}{Pfizer
and BioNTech},
\href{https://www.nytimes3xbfgragh.onion/reuters/2020/05/14/world/europe/14reuters-health-coronavirus-curevac.html}{CureVac}
and others.

\hypertarget{viral-vector-vaccines}{%
\subsection{\texorpdfstring{\textbf{Viral Vector
Vaccines}}{Viral Vector Vaccines}}\label{viral-vector-vaccines}}

\emph{Vaccines that use a virus to deliver coronavirus genes into
cells.}

\hypertarget{vaccines-using-adenovirus-or-other-viruses}{%
\subsubsection{\texorpdfstring{\textbf{Vaccines Using Adenovirus or
Other
Viruses}}{Vaccines Using Adenovirus or Other Viruses}}\label{vaccines-using-adenovirus-or-other-viruses}}

Viruses are very good at getting into cells. Since the 1990s,
researchers have been investigating how to use them to deliver genes
into cells to immunize people against diseases.

To create a coronavirus vaccine, several teams have added the spike
protein gene to a virus called an adenovirus. The adenovirus slips into
cells and unloads the gene. Because the adenovirus is missing one of its
own genes, it cannot replicate and is therefore safe.

EXAMPLES: Several virus vector vaccines are used to vaccinate animals
against rabies and distemper. Johnson \& Johnson has developed H.I.V.
and Ebola vaccines using an adenovirus. Both have proven safe in humans
and are now in efficacy trials.

COMPANIES:
\href{https://www.nytimes3xbfgragh.onion/2020/05/20/health/coronavirus-vaccine-harvard.html}{Johnson
\& Johnson},
\href{https://www.nytimes3xbfgragh.onion/2020/05/04/business/coronavirus-china-vaccine.html}{CanSino},
\href{https://www.nytimes3xbfgragh.onion/2020/04/27/world/europe/coronavirus-vaccine-update-oxford.html}{University
of Oxford} and others.

\hypertarget{protein-based-vaccines}{%
\subsection{\texorpdfstring{\textbf{Protein-Based
Vaccines}}{Protein-Based Vaccines}}\label{protein-based-vaccines}}

\emph{Vaccines that use a coronavirus protein or a protein fragment.}

\hypertarget{virus-like-particle-vaccines}{%
\subsubsection{\texorpdfstring{\textbf{Virus-Like Particle
Vaccines}}{Virus-Like Particle Vaccines}}\label{virus-like-particle-vaccines}}

Some vaccines are particles that contain pieces of viral proteins. They
can't cause disease because they are not actual viruses, but they can
still show the immune system what coronavirus proteins look like.

EXAMPLES: The vaccine for
\href{https://www.nytimes3xbfgragh.onion/2019/06/27/health/hpv-vaccine-warts-cancer.html}{HPV}
falls into this category.

COMPANIES: Medicago, Doherty Institute and others.

\hypertarget{recombinant-vaccines}{%
\subsubsection{\texorpdfstring{\textbf{Recombinant
Vaccines}}{Recombinant Vaccines}}\label{recombinant-vaccines}}

Yeast or other cells can be engineered to carry a virus's gene and spew
out viral proteins, which are then harvested and put into a vaccine. A
coronavirus vaccine of this design would contain whole spike proteins or
small pieces of the protein.

EXAMPLES: This category includes some vaccines for shingles and
hepatitis B.

COMPANIES: Novavax and others.

Sources: World Health Organization, National Institute of Allergy and
Infectious Diseases, National Center for Biotechnology Information, NEJM

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
