 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{/section/politics}{Politics} \textbar{}Trump Has Publicly
Attacked the Russia Investigation More Than 1,100 Times

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2V15XxE}

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

\hypertarget{trump-has-publicly-attacked-the-russia-investigation-more-than-1100-times}{%
\section{Trump Has Publicly Attacked the Russia Investigation More Than
1,100
Times}\label{trump-has-publicly-attacked-the-russia-investigation-more-than-1100-times}}

I don't know Putin, have no deals in Russia, and the haters are going
crazy - yet Obama can make a deal with Iran, \#1 in terror, no problem!
The fake news media is going crazy with their conspiracy theories and
blind hatred. @MSNBC \& @CNN are unwatchable. @foxandfriends is great!
This Russian connection non-sense is merely an attempt to cover-up the
many mistakes made in Hillary Clinton's losing campaign. Information is
being illegally given to the failing @nytimes \& @washingtonpost by the
intelligence community (NSA and FBI?).Just like Russia Thank you to Eli
Lake of The Bloomberg View - "The NSA \& FBI...should not interfere in
our politics...and is" Very serious situation for USA Crimea was TAKEN
by Russia during the Obama Administration. Was Obama too soft on Russia?
The real scandal here is that classified information is illegally given
out by "intelligence" like candy. Very un-American! Leaking, and even
illegal classified leaking, has been a big problem in Washington for
years. Failing @nytimes (and others) must apologize! The spotlight has
finally been put on the low-life leakers! They will be caught! FAKE NEWS
media, which makes up stories and "sources," is far more effective than
the discredited Democrats - but they are fading fast! The Democrats had
to come up with a story as to why they lost the election, and so badly
(306), so they made up a story - RUSSIA. Fake news! The FBI is totally
unable to stop the national security "leakers" that have permeated our
government for a long time. They can't even...... find the leakers
within the FBI itself. Classified information is being given to media
that could have a devastating effect on U.S. FIND NOW Russia talk is
FAKE NEWS put out by the Dems, and played up by the media, in order to
mask the big election defeat and the illegal leaks! ...intentional. This
whole narrative is a way of saving face for Democrats losing an election
that everyone thought they were supposed..... ...to win. The Democrats
are overplaying their hand. They lost the election, and now they have
lost their grip on reality. The real story... ...is all of the illegal
leaks of classified and other information. It is a total "witch hunt!"
The first meeting Jeff Sessions had with the Russian Amb was set up by
the Obama Administration under education program for 100 Ambs......
Terrible! Just found out that Obama had my "wires tapped" in Trump Tower
just before the victory. Nothing found. This is McCarthyism! Just out:
The same Russian Ambassador that met Jeff Sessions visited the Obama
White House 22 times, and 4 times last year alone. Is it legal for a
sitting President to be "wire tapping" a race for president prior to an
election? Turned down by court earlier. A NEW LOW! I'd bet a good lawyer
could make a great case out of the fact that President Obama was tapping
my phones in October, just prior to Election! How low has President
Obama gone to tapp my phones during the very sacred election process.
This is Nixon/Watergate. Bad (or sick) guy! Is it true the DNC would not
allow the FBI access to check server or other equipment after learning
it was hacked? Can that be possible? Who was it that secretly said to
Russian President, "Tell Vladimir that after the election I'll have more
flexibility?" @foxandfriends For eight years Russia "ran over" President
Obama, got stronger and stronger, picked-off Crimea and added missiles.
Weak! @foxandfriends James Clapper and others stated that there is no
evidence Potus colluded with Russia. This story is FAKE NEWS and
everyone knows it! The Democrats made up and pushed the Russian story as
an excuse for running a terrible campaign. Big advantage in Electoral
College \& lost! The real story that Congress, the FBI and all others
should be looking into is the leaking of Classified information. Must
find leaker now! What about all of the contact with the Clinton campaign
and the Russians? Also, is it true that the DNC would not let the FBI in
to look? Just watched the totally biased and fake news reports of the
so-called Russia story on NBC and ABC. Such dishonesty! Why isn't the
House Intelligence Committee looking into the Bill \& Hillary deal that
allowed big Uranium to go to Russia, Russian speech.... ...money to
Bill, the Hillary Russian "reset," praise of Russia by Hillary, or
Podesta Russian Company. Trump Russia story is a hoax. \#MAGA! Watch
@foxandfriends now on Podesta and Russia! Why doesn't Fake News talk
about Podesta ties to Russia as covered by @FoxNews or money from Russia
to Clinton - sale of Uranium? Mike Flynn should ask for immunity in that
this is a witch hunt (excuse for big election loss), by media \& Dems,
of historic proportion! When will Sleepy Eyes Chuck Todd and @NBCNews
start talking about the Obama SURVEILLANCE SCANDAL and stop with the
Fake Trump/Russia story? It is the same Fake News Media that said there
is "no path to victory for Trump" that is now pushing the phony Russia
story. A total scam! Wow, @FoxNews just reporting big news. Source:
"Official behind unmasking is high up. Known Intel official is
responsible. Some unmasked.... ..not associated with Russia. Trump team
spied on before he was nominated." If this is true, does not get much
bigger. Would be sad for U.S. The real story turns out to be
SURVEILLANCE and LEAKING! Find the leakers. Such amazing reporting on
unmasking and the crooked scheme against us by @foxandfriends. "Spied on
before nomination." The real story. Was the brother of John Podesta paid
big money to get the sanctions on Russia lifted? Did Hillary know?
.@FoxNews from multiple sources: "There was electronic surveillance of
Trump, and people close to Trump. This is unprecedented." @FBI FBI
Director Comey was the best thing that ever happened to Hillary Clinton
in that he gave her a free pass for many bad deeds! The phony...
...Trump/Russia story was an excuse used by the Democrats as
justification for losing the election. Perhaps Trump just ran a great
campaign? Susan Rice, the former National Security Advisor to President
Obama, is refusing to testify before a Senate Subcommittee next week
on..... ...allegations of unmasking Trump transition officials. Not
good! When will the Fake Media ask about the Dems dealings with Russia
\& why the DNC wouldn't allow the FBI to check their server or
investigate? General Flynn was given the highest security clearance by
the Obama Administration - but the Fake News seldom likes talking about
that. Ask Sally Yates, under oath, if she knows how classified
information got into the newspapers soon after she explained it to W.H.
Counsel. Director Clapper reiterated what everybody, including the fake
media already knows- there is "no evidence" of collusion w/ Russia and
Trump. Sally Yates made the fake media extremely unhappy today -\/-\/-
she said nothing but old news! The Russia-Trump collusion story is a
total hoax, when will this taxpayer funded charade end? Biggest story
today between Clapper \& Yates is on surveillance. Why doesn't the media
report on this? \#FakeNews! Cryin' Chuck Schumer stated recently, "I do
not have confidence in him (James Comey) any longer." Then acts so
indignant. \#draintheswamp The Democrats have said some of the worst
things about James Comey, including the fact that he should be fired,
but now they play so sad! James Comey will be replaced by someone who
will do a far better job, bringing back the spirit and prestige of the
FBI. Comey lost the confidence of almost everyone in Washington,
Republican and Democrat alike. When things calm down, they will be
thanking me! Watching Senator Richard Blumenthal speak of Comey is a
joke. "Richie" devised one of the greatest military frauds in U.S.
history. For.... years, as a pol in Connecticut, Blumenthal would talk
of his great bravery and conquests in Vietnam - except he was never
there. When.... caught, he cried like a baby and begged for
forgiveness...and now he is judge \& jury. He should be the one who is
investigated for his acts. The Roger Stone report on @CNN is false -
Fake News. Have not spoken to Roger in a long time - had nothing to do
with my decision. Dems have been complaining for months \& months about
Dir. Comey. Now that he has been fired they PRETEND to be aggrieved.
Phony hypocrites! Russia must be laughing up their sleeves watching as
the U.S. tears itself apart over a Democrat EXCUSE for losing the
election. Again, the story that there was collusion between the Russians
\& Trump campaign was fabricated by Dems as an excuse for losing the
election. James Comey better hope that there are no "tapes" of our
conversations before he starts leaking to the press! When James Clapper
himself, and virtually everyone else with knowledge of the witch hunt,
says there is no collusion, when does it end? I have been asking
Director Comey \& others, from the beginning of my administration, to
find the LEAKERS in the intelligence community..... This is the single
greatest witch hunt of a politician in American history! With all of the
illegal acts that took place in the Clinton campaign \& Obama
Administration, there was never a special counsel appointed! Russian
officials must be laughing at the U.S. \& how a lame excuse for why the
Dems lost the election has taken over the Fake News. So now it is
reported that the Democrats, who have excoriated Carter Page about
Russia, don't want him to testify. He blows away their.... ...case
against him \& now wants to clear his name by showing "the false or
misleading testimony by James Comey, John Brennan..." Witch Hunt!
Crooked Hillary Clinton now blames everybody but herself, refuses to say
she was a terrible candidate. Hits Facebook \& even Dems \& DNC. The big
story is the "unmasking and surveillance" of people that took place
during the Obama Administration. I believe the James Comey leaks will be
far more prevalent than anyone ever thought possible. Totally illegal?
Very 'cowardly!' A.G. Lynch made law enforcement decisions for political
purposes...gave Hillary Clinton a free pass and protection. Totally
illegal! They made up a phony collusion with the Russians story, found
zero proof, so now they go for obstruction of justice on the phony
story. Nice You are witnessing the single greatest WITCH HUNT in
American political history - led by some very bad and conflicted people!
\#MAGA Why is that Hillary Clintons family and Dems dealings with Russia
are not looked at, but my non-dealings are? Crooked H destroyed phones
w/ hammer, 'bleached' emails, \& had husband meet w/AG days before she
was cleared- \& they talk about obstruction? After 7 months of
investigations \& committee hearings about my "collusion with the
Russians," nobody has been able to show any proof. Sad! Despite the
phony Witch Hunt going on in America, the economic \& jobs numbers are
great. Regulations way down, jobs and enthusiasm way up! I am being
investigated for firing the FBI Director by the man who told me to fire
the FBI Director! Witch Hunt Former Homeland Security Advisor Jeh
Johnson is latest top intelligence official to state there was no grand
scheme between Trump \& Russia. By the way, if Russia was working so
hard on the 2016 Election, it all took place during the Obama Admin. Why
didn't they stop them? ...Why did Democratic National Committee turn
down the DHS offer to protect against hacks (long prior to election).
It's all a big Dem HOAX! ...Why did the DNC REFUSE to turn over its
Server to the FBI, and still hasn't? It's all a big Dem scam and excuse
for losing the election! With all of the recently reported electronic
surveillance, intercepts, unmasking and illegal leaking of information,
I have no idea... ...whether there are "tapes" or recordings of my
conversations with James Comey, but I did not make, and do not have, any
such recordings. Just out: The Obama Administration knew far in advance
of November 8th about election meddling by Russia. Did nothing about it.
WHY? Since the Obama Administration was told way before the 2016
Election that the Russians were meddling, why no action? Focus on them,
not T! Obama Administration official said they "choked" when it came to
acting on Russian meddling of election. They didn't want to hurt
Hillary? The reason that President Obama did NOTHING about Russia after
being notified by the CIA of meddling is that he expected Clinton would
win.. ...and did not want to "rock the boat." He didn't "choke," he
colluded or obstructed, and it did the Dems and Crooked Hillary no good.
The real story is that President Obama did NOTHING after being informed
in August about Russian meddling. With 4 months looking at Russia...
..under a magnifying glass, they have zero "tapes" of T people
colluding. There is no collusion \& no obstruction. I should be given
apology! From @FoxNews "Bombshell: In 2016, Obama dismissed idea that
anyone could rig an American election." Check out his statement - Witch
Hunt! Wow, CNN had to retract big story on "Russia," with 3 employees
forced to resign. What about all the other phony stories they do? FAKE
NEWS! Fake News CNN is looking at big management changes now that they
got caught falsely pushing their phony Russian stories. Ratings way
down! So they caught Fake News CNN cold, but what about NBC, CBS \& ABC?
What about the failing @nytimes \& @washingtonpost? They are all Fake
News! Everyone here is talking about why John Podesta refused to give
the DNC server to the FBI and the CIA. Disgraceful! ...and safe.
Questions were asked about why the CIA \& FBI had to ask the DNC 13
times for their SERVER, and were rejected, still don't.... ...have it.
Fake News said 17 intel agencies when actually 4 (had to apologize). Why
did Obama do NOTHING when he had info before election? James Comey
leaked CLASSIFIED INFORMATION to the media. That is so illegal! My son
Donald did a good job last night. He was open, transparent and innocent.
This is the greatest Witch Hunt in political history. Sad! .@WashTimes
states "Democrats have willfully used Moscow disinformation to influence
the presidential election against Donald Trump." Why aren't the same
standards placed on the Democrats. Look what Hillary Clinton may have
gotten away with. Disgraceful! HillaryClinton can illegally get the
questions to the Debate \& delete 33,000 emails but my son Don is being
scorned by the Fake News Media? Thank you to former campaign adviser
Michael Caputo for saying so powerfully that there was no Russian
collusion in our winning campaign. A new INTELLIGENCE LEAK from the
Amazon Washington Post,this time against A.G. Jeff Sessions.These
illegal leaks, like Comey's, must stop! While all agree the U. S.
President has the complete power to pardon, why think of that when only
crime so far is LEAKS against us.FAKE NEWS So many people are asking why
isn't the A.G. or Special Council looking at the many Hillary Clinton or
Comey crimes. 33,000 e-mails deleted? ...What about all of the Clinton
ties to Russia, including Podesta Company, Uranium deal, Russian Reset,
big dollar speeches etc. My son Donald openly gave his e-mails to the
media \& authorities whereas Crooked Hillary Clinton deleted (\& acid
washed) her 33,000 e-mails! As the phony Russian Witch Hunt continues,
two groups are laughing at this excuse for a lost election taking hold,
Democrats and Russians! After 1 year of investigation with Zero evidence
being found, Chuck Schumer just stated that "Democrats should blame
ourselves,not Russia." So why aren't the Committees and investigators,
and of course our beleaguered A.G., looking into Crooked Hillarys crimes
\& Russia relations? Sleazy Adam Schiff, the totally biased Congressman
looking into "Russia," spends all of his time on television pushing the
Dem loss excuse! Ukrainian efforts to sabotage Trump campaign - "quietly
working to boost Clinton." So where is the investigation A.G.
@seanhannity Attorney General Jeff Sessions has taken a VERY weak
position on Hillary Clinton crimes (where are E-mails \& DNC server) \&
Intel leakers! Problem is that the acting head of the FBI \& the person
in charge of the Hillary investigation, Andrew McCabe, got \$700,000
from H for wife! Jared Kushner did very well yesterday in proving he did
not collude with the Russians. Witch Hunt. Next up, 11 year old Barron
Trump! Why didn't A.G. Sessions replace Acting FBI Director Andrew
McCabe, a Comey friend who was in charge of Clinton investigation but
got.... ...big dollars (\$700,000) for his wife's political run from
Hillary Clinton and her representatives. Drain the Swamp! "One of the
things that has been lost in the politics of this situation is that the
Russians collected and spread negative information..... ...about then
candidate Trump." Catherine Herridge @FoxNews. So why doesn't Fake News
report this? Witch Hunt! Purposely phony reporting. After many years of
LEAKS going on in Washington, it is great to see the A.G. taking action!
For National Security, the tougher the better! ...and West Virginia. The
fact is the Fake News Russian collusion story, record Stock Market,
border security, military strength, jobs..... Interesting to watch
Senator Richard Blumenthal of Connecticut talking about hoax Russian
collusion when he was a phony Vietnam con artist! Never in U.S.history
has anyone lied or defrauded voters like Senator Richard Blumenthal. He
told stories about his Vietnam battles and.... ...conquests, how brave
he was, and it was all a lie. He cried like a baby and begged for
forgiveness like a child. Now he judges collusion? E-mails show that the
AmazonWashingtonPost and the FailingNewYorkTimes were reluctant to cover
the Clinton/Lynch secret meeting in plane. @foxandfriends According to
report just out, President Obama knew about Russian interference 3 years
ago but he didn't want to anger Russia! James Clapper, who famously got
caught lying to Congress, is now an authority on Donald Trump. Will he
show you his beautiful letter to me? Wow, looks like James Comey
exonerated Hillary Clinton long before the investigation was over...and
so much more. A rigged system! The Russia hoax continues, now it's ads
on Facebook. What about the totally biased and dishonest Media coverage
in favor of Crooked Hillary? The greatest influence over our election
was the Fake News Media "screaming" for Crooked Hillary Clinton. Next,
she was a bad candidate! Wow, FBI confirms report that James Comey
drafted letter exonerating Crooked Hillary Clinton long before
investigation was complete. Many.. ...people not interviewed, including
Clinton herself. Comey stated under oath that he didn't do
this-obviously a fix? Where is Justice Dept? As it has turned out, James
Comey lied and leaked and totally protected Hillary Clinton. He was the
best thing that ever happened to her! Uranium deal to Russia, with
Clinton help and Obama Administration knowledge, is the biggest story
that Fake Media doesn't want to follow! Workers of firm involved with
the discredited and Fake Dossier take the 5th. Who paid for it, Russia,
the FBI or the Dems (or all)? .@foxandfriends "Russia sent millions to
Clinton Foundation" Officials behind the now discredited "Dossier" plead
the Fifth. Justice Department and/or FBI should immediately release who
paid for it. Crooked Hillary Clinton spent hundreds of millions of
dollars more on Presidential Election than I did. Facebook was on her
side, not mine! "Clinton campaign \& DNC paid for research that led to
the anti-Trump Fake News Dossier. The victim here is the President."
@FoxNews It is now commonly agreed, after many months of COSTLY looking,
that there was NO collusion between Russia and Trump. Was collusion with
HC! Never seen such Republican ANGER \& UNITY as I have concerning the
lack of investigation on Clinton made Fake Dossier (now
\$12,000,000?),.... ...the Uranium to Russia deal, the 33,000 plus
deleted Emails, the Comey fix and so much more. Instead they look at
phony Trump/Russia,.... ..."collusion," which doesn't exist. The Dems
are using this terrible (and bad for our country) Witch Hunt for evil
politics, but the R's... ...are now fighting back like never before.
There is so much GUILT by Democrats/Clinton, and now the facts are
pouring out. DO SOMETHING! All of this "Russia" talk right when the
Republicans are making their big push for historic Tax Cuts \& Reform.
Is this coincidental? NOT! Report out that Obama Campaign paid \$972,000
to Fusion GPS. The firm also got \$12,400,000 (really?) from DNC. Nobody
knows who OK'd! Sorry, but this is years ago, before Paul Manafort was
part of the Trump campaign. But why aren't Crooked Hillary \& the Dems
the focus????? ....Also, there is NO COLLUSION! The Fake News is working
overtime. As Paul Manaforts lawyer said, there was "no collusion" and
events mentioned took place long before he... ....came to the campaign.
Few people knew the young, low level volunteer named George, who has
already proven to be a liar. Check the DEMS! The biggest story
yesterday, the one that has the Dems in a dither, is Podesta running
from his firm. What he know about Crooked Dems is.... ....earth
shattering. He and his brother could Drain The Swamp, which would be yet
another campaign promise fulfilled. Fake News weak! Donna Brazile just
stated the DNC RIGGED the system to illegally steal the Primary from
Bernie Sanders. Bought and paid for by Crooked H.... ....This is real
collusion and dishonesty. Major violation of Campaign Finance Laws and
Money Laundering - where is our Justice Department? The @TuckerCarlson
opening statement about our once cherished and great FBI was so sad to
watch. James Comey's leadership was a disaster! Everybody is asking why
the Justice Department (and FBI) isn't looking into all of the
dishonesty going on with Crooked Hillary \& the Dems.. ...New Donna B
book says she paid for and stole the Dem Primary. What about the deleted
E-mails, Uranium, Podesta, the Server, plus, plus... ....People are
angry. At some point the Justice Department, and the FBI, must do what
is right and proper. The American public deserves it! The real story on
Collusion is in Donna B's new book. Crooked Hillary bought the DNC \&
then stole the Democratic Primary from Crazy Bernie! Pocahontas just
stated that the Democrats, lead by the legendary Crooked Hillary
Clinton, rigged the Primaries! Lets go FBI \& Justice Dept. The rigged
Dem Primary, one of the biggest political stories in years, got ZERO
coverage on Fake News Network TV last night. Disgraceful! Does the Fake
News Media remember when Crooked Hillary Clinton, as Secretary of State,
was begging Russia to be our friend with the misspelled reset button?
Obama tried also, but he had zero chemistry with Putin. Since the first
day I took office, all you hear is the phony Democrat excuse for losing
the election, Russia, Russia,Russia. Despite this I have the economy
booming and have possibly done more than any 10 month President. MAKE
AMERICA GREAT AGAIN! Charles McCullough, the respected fmr Intel Comm
Inspector General, said public was misled on Crooked Hillary Emails.
``Emails endangered National Security.''? Why aren't our deep State
authorities looking at this? Rigged \& corrupt? @TuckerCarlson
@seanhannity The House of Representatives seeks contempt citations(?)
against the JusticeDepartment and the FBI for withholding key documents
and an FBI witness which could shed light on surveillance of associates
of Donald Trump. Big stuff. Deep State. Give this information NOW!
@FoxNews I had to fire General Flynn because he lied to the Vice
President and the FBI. He has pled guilty to those lies. It is a shame
because his actions during the transition were lawful. There was nothing
to hide! So General Flynn lies to the FBI and his life is destroyed,
while Crooked Hillary Clinton, on that now famous FBI holiday
``interrogation''? with no swearing in and no recording, lies many
times...and nothing happens to her? Rigged system, or just a double
standard? Many people in our Country are asking what the ``Justice''?
Department is going to do about the fact that totally Crooked Hillary,
AFTER receiving a subpoena from the United States Congress, deleted and
``acid washed''? 33,000 Emails? No justice! Congratulations to @ABC News
for suspending Brian Ross for his horrendously inaccurate and dishonest
report on the Russia, Russia, Russia Witch Hunt. More Networks and
``papers''? should do the same with their Fake News! I never asked Comey
to stop investigating Flynn. Just more Fake News covering another Comey
lie! Tainted (no, very dishonest?) FBI ``agent's role in Clinton probe
under review.''? Led Clinton Email probe. @foxandfriends Clinton money
going to wife of another FBI agent in charge. After years of Comey, with
the phony and dishonest Clinton investigation (and more), running the
FBI, its reputation is in Tatters - worst in History! But fear not, we
will bring it back to greatness. Report: ``ANTI-TRUMP FBI AGENT LED
CLINTON EMAIL PROBE''? Now it all starts to make sense! A must watch:
Legal Scholar Alan Dershowitz was just on @foxandfriends talking of what
is going on with respect to the greatest Witch Hunt in U.S. political
history. Enjoy! How can FBI Deputy Director Andrew McCabe, the man in
charge, along with leakin' James Comey, of the Phony Hillary Clinton
investigation (including her 33,000 illegally deleted emails) be given
\$700,000 for wife's campaign by Clinton Puppets during investigation?
Wow, ``FBI lawyer James Baker reassigned,''? according to @FoxNews.
.@FoxNews-FBI's Andrew McCabe, ``in addition to his wife getting all of
this money from M (Clinton Puppet), he was using, allegedly, his FBI
Official Email Account to promote her campaign. You obviously cannot do
this. These were the people who were investigating Hillary Clinton.''?
WOW, @foxandfrlends ``Dossier is bogus. Clinton Campaign, DNC funded
Dossier. FBI CANNOT (after all of this time) VERIFY CLAIMS IN DOSSIER OF
RUSSIA/TRUMP COLLUSION. FBI TAINTED.''? And they used this Crooked
Hillary pile of garbage as the basis for going after the Trump Campaign!
Crooked Hillary Clinton's top aid, Huma Abedin, has been accused of
disregarding basic security protocols. She put Classified Passwords into
the hands of foreign agents. Remember sailors pictures on submarine?
Jail! Deep State Justice Dept must finally act? Also on Comey \& others
Well, now that collusion with Russia is proving to be a total hoax and
the only collusion is with Hillary Clinton and the FBI/Russia, the Fake
News Media (Mainstream) and this phony new book are hitting out at every
new front imaginable. They should try winning an election. Sad! Now that
Russian collusion, after one year of intense study, has proven to be a
total hoax on the American public, the Democrats and their lapdogs, the
Fake News Mainstream Media, are taking out the old Ronald Reagan
playbook and screaming mental stability and intelligence..... The fact
that Sneaky Dianne Feinstein, who has on numerous occasions stated that
collusion between Trump/Russia has not been found, would release
testimony in such an underhanded and possibly illegal way, totally
without authorization, is a disgrace. Must have tough Primary! The
single greatest Witch Hunt in American history continues. There was no
collusion, everybody including the Dems knows there was no collusion, \&
yet on and on it goes. Russia \& the world is laughing at the stupidity
they are witnessing. Republicans should finally take control! Disproven
and paid for by Democrats ``Dossier used to spy on Trump Campaign. Did
FBI use Intel tool to influence the Election?''? @foxandfriends Did Dems
or Clinton also pay Russians? Where are hidden and smashed DNC servers?
Where are Crooked Hillary Emails? What a mess! ``House votes on
controversial FISA ACT today.''? This is the act that may have been
used, with the help of the discredited and phony Dossier, to so badly
surveil and abuse the Trump Campaign by the previous administration and
others? In one of the biggest stories in a long time, the FBI now says
it is missing five months worth of lovers Strzok-Page texts, perhaps
50,000, and all in prime time. Wow! Where are the 50,000 important text
messages between FBI lovers Lisa Page and Peter Strzok? Blaming Samsung!
Great jobs numbers and finally, after many years, rising wages- and
nobody even talks about them. Only Russia, Russia, Russia, despite the
fact that, after a year of looking, there is No Collusion! ``The four
page memo released Friday reports the disturbing fact about how the FBI
and FISA appear to have been used to influence the 2016 election and its
aftermath....The FBI failed to inform the FISA court that the Clinton
campaign had funded the dossier....the FBI became.... ...a tool of
anti-Trump political actors. This is unacceptable in a democracy and
ought to alarm anyone who wants the FBI to be a nonpartisan enforcer of
the law....The FBI wasn't straight with Congress, as it hid most of
these facts from investigators.''? Wall Street Journal Little Adam
Schiff, who is desperate to run for higher office, is one of the biggest
liars and leakers in Washington, right up there with Comey, Warner,
Brennan and Clapper! Adam leaves closed committee hearings to illegally
leak confidential information. Must be stopped! NEW FBI TEXTS ARE
BOMBSHELLS! The Democrats sent a very political and long response memo
which they knew, because of sources and methods (and more), would have
to be heavily redacted, whereupon they would blame the White House for
lack of transparency. Told them to re-do and send back in proper form!
Peoples lives are being shattered and destroyed by a mere allegation.
Some are true and some are false. Some are old and some are new. There
is no recovery for someone falsely accused - life and career are gone.
Is there no such thing any longer as Due Process? ``My view is that not
only has Trump been vindicated in the last several weeks about the
mishandling of the Dossier and the lies about the Clinton/DNC Dossier,
it shows that he's been victimized. He's been victimized by the Obama
Administration who were using all sorts of....... ....agencies, not just
the FBI \& DOJ, now the State Department to dig up dirt on him in the
days leading up to the Election. Comey had conversations with Donald
Trump, which I don't believe were accurate...he leaked information
(corrupt).''? Tom Fitton of Judicial Watch on @FoxNews Russia started
their anti-US campaign in 2014, long before I announced that I would run
for President. The results of the election were not impacted. The Trump
campaign did nothing wrong - no collusion! ``Charges Deal Don A Big
Win,''? written by Michael Goodwin of the @nypost, succinctly states
that ``the Russians had no impact on the election results.''? There was
no Collusion with the Trump Campaign. ``She lost the old-fashioned way,
by being a terrible candidate. Case closed.''? Deputy A.G. Rod
Rosenstein stated at the News Conference: ``There is no allegation in
the indictment that any American was a knowing participant in this
illegal activity. There is no allegation in the indictment that the
charged conduct altered the outcome of the 2016 election. Funny how the
Fake News Media doesn't want to say that the Russian group was formed in
2014, long before my run for President. Maybe they knew I was going to
run even though I didn't know! Very sad that the FBI missed all of the
many signals sent out by the Florida school shooter. This is not
acceptable. They are spending too much time trying to prove Russian
collusion with the Trump campaign - there is no collusion. Get back to
the basics and make us all proud! General McMaster forgot to say that
the results of the 2016 election were not impacted or changed by the
Russians and that the only Collusion was between Russia and Crooked H,
the DNC and the Dems. Remember the Dirty Dossier, Uranium, Speeches,
Emails and the Podesta Company! Finally, Liddle' Adam Schiff, the
leakin' monster of no control, is now blaming the Obama Administration
for Russian meddling in the 2016 Election. He is finally right about
something. Obama was President, knew of the threat, and did nothing.
Thank you Adam! I never said Russia did not meddle in the election, I
said ``it may be Russia, or China or another country or group, or it may
be a 400 pound genius sitting in bed and playing with his computer.''?
The Russian ``hoax''? was that the Trump campaign colluded with Russia -
it never did! Now that Adam Schiff is starting to blame President Obama
for Russian meddling in the election, he is probably doing so as yet
another excuse that the Democrats, lead by their fearless leader,
Crooked Hillary Clinton, lost the 2016 election. But wasn't I a great
candidate? If it was the GOAL of Russia to create discord, disruption
and chaos within the U.S. then, with all of the Committee Hearings,
Investigations and Party hatred, they have succeeded beyond their
wildest dreams. They are laughing their asses off in Moscow. Get smart
America! Thank you to KenStarr, former Independent Counsel, Whitewater,
for your insight and powerful words on FISA abuse, Russian meddling etc.
Really great interview with @MariaBartiromo Obama was President up to,
and beyond, the 2016 Election. So why didn't he do something about
Russian meddling? Thank you to @foxandfriends for the great timeline on
all of the failures the Obama Administration had against Russia,
including Crimea, Syria and so much more. We are now starting to win
again! ....The President Obama quote just before election. That's
because he thought Crooked Hillary was going to win and he didn't want
to ``rock the boat.''? When I easily won the Electoral College, the
whole game changed and the Russian excuse became the narrative of the
Dems. I have been much tougher on Russia than Obama, just look at the
facts. Total Fake News! Bad ratings @CNN \& @MSNBC got scammed when they
covered the anti-Trump Russia rally wall-to-wall. They probably knew it
was Fake News but, because it was a rally against me, they pushed it
hard anyway. Two really dishonest newscasters, but the public is wise!
Question: If all of the Russian meddling took place during the Obama
Administration, right up to January 20th, why aren't they the subject of
the investigation? Why didn't Obama do something about the meddling? Why
aren't Dem crimes under investigation? Ask Jeff Sessions! Dem Memo: FBI
did not disclose who the clients were - the Clinton Campaign and the
DNC. Wow! ``Russians had no compromising information on Donald Trump''?
@FoxNews Of course not, because there is none, and never was. This whole
Witch Hunt is an illegal disgrace...and Obama did nothing about Russia!
``Congressman Schiff omitted and distorted key facts''? @FoxNews So,
what else is new. He is a total phony! ``He's got a very good point.
Somebody in the Justice Department has a treasure trove of evidence of
Mrs. Clinton's criminality at her own hands, or through others, that
ought to be investigated. I fully agree with the President on that.''?
@judgenapolitano on @marthamaccallum Show ``I've been skeptical about
the collusion and obstruction claims for the last year. I just don't see
the evidence....in terms of the collusion, it's all a bit implausible
based on the evidence we have.''? Jonathan Turley on @FoxNews ``We've
seen NO EVIDENCE OF COLLUSION....I have seen nothing, the firing of
James Comey and all of the aftermath, that suggests that the President
has obstructed justice because he's exercising his power as the
President of the U.S. I just don't see it.''? Judge Ken Starr WITCH
HUNT! Why is A.G. Jeff Sessions asking the Inspector General to
investigate potentially massive FISA abuse. Will take forever, has no
prosecutorial power and already late with reports on Comey etc. Isn't
the I.G. an Obama guy? Why not use Justice Department lawyers?
DISGRACEFUL! Why did the Obama Administration start an investigation
into the Trump Campaign (with zero proof of wrongdoing) long before the
Election in November? Wanted to discredit so Crooked H would win.
Unprecedented. Bigger than Watergate! Plus, Obama did NOTHING about
Russian meddling. The Failing New York Times purposely wrote a false
story stating that I am unhappy with my legal team on the Russia case
and am going to add another lawyer to help out. Wrong. I am VERY happy
with my lawyers, John Dowd, Ty Cobb and Jay Sekulow. They are doing a
great job and..... ...have shown conclusively that there was no
Collusion with Russia..just excuse for losing. The only Collusion was
that done by the DNC, the Democrats and Crooked Hillary. The writer of
the story, Maggie Haberman, a Hillary flunky, knows nothing about me and
is not given access. THE HOUSE INTELLIGENCE COMMITTEE HAS, AFTER A 14
MONTH LONG IN-DEPTH INVESTIGATION, FOUND NO EVIDENCE OF COLLUSION OR
COORDINATION BETWEEN THE TRUMP CAMPAIGN AND RUSSIA TO INFLUENCE THE 2016
PRESIDENTIAL ELECTION. As the House Intelligence Committee has
concluded, there was no collusion between Russia and the Trump Campaign.
As many are now finding out, however, there was tremendous leaking,
lying and corruption at the highest levels of the FBI, Justice \& State.
\#DrainTheSwamp The Fake News is beside themselves that McCabe was
caught, called out and fired. How many hundreds of thousands of dollars
was given to wife's campaign by Crooked H friend, Terry M, who was also
under investigation? How many lies? How many leaks? Comey knew it all,
and much more! Wow, watch Comey lie under oath to Senator G when asked
``have you ever been an anonymous source...or known someone else to be
an anonymous source...?''? He said strongly ``never, no.''? He lied as
shown clearly on @foxandfriends. Spent very little time with Andrew
McCabe, but he never took notes when he was with me. I don't believe he
made memos except to help his own agenda, probably at a later date. Same
with lying James Comey. Can we call them Fake Memos? Why does the
Mueller team have 13 hardened Democrats, some big Crooked Hillary
supporters, and Zero Republicans? Another Dem recently added...does
anyone think this is fair? And yet, there is NO COLLUSION! A total WITCH
HUNT with massive conflicts of interest! ...there was no probable cause
for believing that there was any crime, collusion or otherwise, or
obstruction of justice!''? So stated by Harvard Law Professor Alan
Dershowitz. I called President Putin of Russia to congratulate him on
his election victory (in past, Obama called him also). The Fake News
Media is crazed because they wanted me to excoriate him. They are wrong!
Getting along with Russia (and others) is a good thing, not a bad
thing....... ``Special Council is told to find crimes, whether a crime
exists or not. I was opposed to the selection of Mueller to be Special
Council. I am still opposed to it. I think President Trump was right
when he said there never should have been a Special Council appointed
because..... House Intelligence Committee votes to release final report.
FINDINGS: (1) No evidence provided of Collusion between Trump Campaign
\& Russia. (2) The Obama Administrations Post election response was
insufficient. (3) Clapper provided inconsistent testimony on media
contacts. Many lawyers and top law firms want to represent me in the
Russia case...don't believe the Fake News narrative that it is hard to
find a lawyer who wants to take this on. Fame \& fortune will NEVER be
turned down by a lawyer, though some are conflicted. Problem is that a
new...... ....lawyer or law firm will take months to get up to speed (if
for no other reason than they can bill more), which is unfair to our
great country - and I am very happy with my existing team. Besides,
there was NO COLLUSION with Russia, except by Crooked Hillary and the
Dems! So sad that the Department of ``Justice''? and the FBI are slow
walking, or even not giving, the unredacted documents requested by
Congress. An embarrassment to our country! Lawmakers of the House
Judiciary Committee are angrily accusing the Department of Justice of
missing the Thursday Deadline for turning over UNREDACTED Documents
relating to FISA abuse, FBI, Comey, Lynch, McCabe, Clinton Emails and
much more. Slow walking - what is going on? BAD! What does the
Department of Justice and FBI have to hide? Why aren't they giving the
strongly requested documents (unredacted) to the HOUSE JUDICIARY
COMMITTEE? Stalling, but for what reason? Not looking good! ``The FBI
closed the case on Hillary, which was a rigged investigation. They
exonerated her even before they ever interviewed her, they never even
put her under oath.....''? and much more. So true Jesse! @WattersWorld
Attorney''``client privilege is dead! A TOTAL WITCH HUNT!!! The Failing
New York Times wrote another phony story. It was political pundit Doug
Schoen, not a Ukrainian businessman, who asked me to do a short speech
by phone (Skype), hosted by Doug, in Ukraine. I was very positive about
Ukraine-another negative to the Fake Russia C story! Much of the bad
blood with Russia is caused by the Fake \& Corrupt Russia Investigation,
headed up by the all Democrat loyalists, or people that worked for
Obama. Mueller is most conflicted of all (except Rosenstein who signed
FISA \& Comey letter). No Collusion, so they go crazy! If I wanted to
fire Robert Mueller in December, as reported by the Failing New York
Times, I would have fired him. Just more Fake News from a biased
newspaper! James Comey is a proven LEAKER \& LIAR. Virtually everyone in
Washington thought he should be fired for the terrible job he did-until
he was, in fact, fired. He leaked CLASSIFIED information, for which he
should be prosecuted. He lied to Congress under OATH. He is a weak
and..... ....untruthful slime ball who was, as time has proven, a
terrible Director of the FBI. His handling of the Crooked Hillary
Clinton case, and the events surrounding it, will go down as one of the
worst ``botch jobs''? of history. It was my great honor to fire James
Comey! DOJ just issued the McCabe report - which is a total disaster. He
LIED! LIED! LIED! McCabe was totally controlled by Comey - McCabe is
Comey!! No collusion, all made up by this den of thieves and lowlifes!
Unbelievably, James Comey states that Polls, where Crooked Hillary was
leading, were a factor in the handling (stupidly) of the Clinton Email
probe. In other words, he was making decisions based on the fact that he
thought she was going to win, and he wanted a job. Slimeball! The big
questions in Comey's badly reviewed book aren't answered like, how come
he gave up Classified Information (jail), why did he lie to Congress
(jail), why did the DNC refuse to give Server to the FBI (why didn't
they TAKE it), why the phony memos, McCabe's \$700,000 \& more? Comey
throws AG Lynch ``under the bus!''? Why can't we all find out what
happened on the tarmac in the back of the plane with Wild Bill and
Lynch? Was she promised a Supreme Court seat, or AG, in order to lay off
Hillary. No golf and grandkids talk (give us all a break)! I never asked
Comey for Personal Loyalty. I hardly even knew this guy. Just another of
his many lies. His ``memos''? are self serving and FAKE! Attorney Client
privilege is now a thing of the past. I have many (too many!) lawyers
and they are probably wondering when their offices, and even homes, are
going to be raided with everything, including their phones and
computers, taken. All lawyers are deflated and concerned! Slippery James
Comey, a man who always ends up badly and out of whack (he is not
smart!), will go down as the WORST FBI Director in history, by far!
Comey drafted the Crooked Hillary exoneration long before he talked to
her (lied in Congress to Senator G), then based his decisions on her
poll numbers. Disgruntled, he, McCabe, and the others, committed many
crimes! Slippery James Comey, the worst FBI Director in history, was not
fired because of the phony Russia investigation where, by the way, there
was NO COLLUSION (except by the Dems)! James Comey just threw Andrew
McCabe ``under the bus.''? Inspector General's Report on McCabe is a
disaster for both of them! Getting a little (lot) of their own medicine?
James Comey Memos just out and show clearly that there was NO COLLUSION
and NO OBSTRUCTION. Also, he leaked classified information. WOW! Will
the Witch Hunt continue? So General Michael Flynn's life can be totally
destroyed while Shadey James Comey can Leak and Lie and make lots of
money from a third rate book (that should never have been written). Is
that really the way life in America is supposed to work? I don't think
so! Just heard the Campaign was sued by the Obstructionist Democrats.
This can be good news in that we will now counter for the DNC Server
that they refused to give to the FBI, the Debbie Wasserman Schultz
Servers and Documents held by the Pakistani mystery man and Clinton
Emails. James Comey illegally leaked classified documents to the press
in order to generate a Special Council? Therefore, the Special Council
was established based on an illegal act? Really, does everybody know
what that means? The New York Times and a third rate reporter named
Maggie Haberman, known as a Crooked H flunkie who I don't speak to and
have nothing to do with, are going out of their way to destroy Michael
Cohen and his relationship with me in the hope that he will ``flip.''?
They use.... ....it means lying or making up stories. Sorry, I don't see
Michael doing that despite the horrible Witch Hunt and the dishonest
media! So funny, the Democrats have sued the Republicans for Winning.
Now he R's counter and force them to turn over a treasure trove of
material, including Servers and Emails! James Comey's Memos are
Classified, I did not Declassify them. They belong to our Government!
Therefore, he broke the law! Additionally, he totally made up many of
the things he said I said, and he is already a proven liar and leaker.
Where are Memos on Clinton, Lynch \& others? The Washington Post said I
refer to Jeff Sessions as ``Mr. Magoo''? and Rod Rosenstein as ``Mr.
Peepers.''? This is ``according to people with whom the president has
spoken.''? There are no such people and don't know these
characters...just more Fake \& Disgusting News to create ill will! ``At
least two Memos Comey shared with a friend contained Classified
Information.''? Wall Street Journal ``GOP Lawmakers asking Sessions to
Investigate Comey and Hillary Clinton.''? @FoxNews Good luck with that
request! A complete Witch Hunt! Kim Strassel of the WSJ just said, after
reviewing the dumb Comey Memos, ``you got to ask, what was the purpose
of the Special Counsel? There's no there there.''? Dan Henninger of the
WSJ said Memos would show that this would be one of the weakest
obstruction cases ever brought! Just Out: House Intelligence Committee
Report released. ``No evidence''? that the Trump Campaign ``colluded,
coordinated or conspired with Russia.''? Clinton Campaign paid for
Opposition Research obtained from Russia- Wow! A total Witch Hunt! MUST
END NOW! House Intelligence Committee rules that there was NO COLLUSION
between the Trump Campaign and Russia. As I have been saying all along,
it is all a big Hoax by the Democrats based on payments and lies. There
should never have been a Special Counsel appointed. Witch Hunt!
``Clapper lied about (fraudulent) Dossier leaks to CNN''? @foxandfriends
FoxNews He is a lying machine who now works for Fake News CNN. So
disgraceful that the questions concerning the Russian Witch Hunt were
``leaked''? to the media. No questions on Collusion. Oh, I see...you
have a made up, phony crime, Collusion, that never existed, and an
investigation begun with illegally leaked classified information. Nice!
It would seem very hard to obstruct justice for a crime that never
happened! Witch Hunt! There was no Collusion (it is a Hoax) and there is
no Obstruction of Justice (that is a setup \& trap). What there is is
Negotiations going on with North Korea over Nuclear War, Negotiations
going on with China over Trade Deficits, Negotiations on NAFTA, and much
more. Witch Hunt! ``The questions are an intrusion into the President's
Article 2 powers under the Constitution to fire any Executive Branch
Employee...what the President was thinking is an outrageous.....as to
the President's unfettered power to fire anyone...''? Joe Digenova,
former US Attorney NEW BOOK - A MUST READ! ``The Russia Hoax - The
Illicit Scheme to Clear Hillary Clinton and Frame Donald Trump''? by the
brilliant Fox News Legal Analyst Gregg Jarrett. A sad chapter for law
enforcement. A rigged system! A Rigged System - They don't want to turn
over Documents to Congress. What are they afraid of? Why so much
redacting? Why such unequal ``justice?''? At some point I will have no
choice but to use the powers granted to the Presidency and get involved!
The Russia Witch Hunt is rapidly losing credibility. House Intelligence
Committee found No Collusion, Coordination or anything else with Russia.
So now the Probe says OK, what else is there? How about Obstruction for
a made up, phony crime.There is no O, it's called Fighting Back The 13
Angry Democrats in charge of the Russian Witch Hunt are starting to find
out that there is a Court System in place that actually protects people
from injustice...and just wait ''˜till the Courts get to see your
unrevealed Conflicts of Interest! Lisa Page, who may hold the record for
the most Emails in the shortest period of time (to her Lover, Peter S),
and attorney Baker, are out at the FBI as part of the Probers getting
caught? Why is Peter S still there? What a total mess. Our Country has
to get back to Business! Is this Phony Witch Hunt going to go on even
longer so it wrongfully impacts the Mid-Term Elections, which is what
the Democrats always intended? Republicans better get tough and smart
before it is too late! Senator Cryin' Chuck Schumer fought hard against
the Bad Iran Deal, even going at it with President Obama, \& then Voted
AGAINST it! Now he says I should not have terminated the deal - but he
doesn't really believe that! Same with Comey. Thought he was terrible
until I fired him! Can you believe that with all of the made up,
unsourced stories I get from the Fake News Media, together with the
\$10,000,000 Russian Witch Hunt (there is no Collusion), I now have my
best Poll Numbers in a year. Much of the Media may be corrupt, but the
People truly get it! Congratulations America, we are now into the second
year of the greatest Witch Hunt in American History...and there is still
No Collusion and No Obstruction. The only Collusion was that done by
Democrats who were unable to win an Election despite the spending of far
more money! Wow, word seems to be coming out that the Obama FBI ``SPIED
ON THE TRUMP CAMPAIGN WITH AN EMBEDDED INFORMANT.''? Andrew McCarthy
says, ``There's probably no doubt that they had at least one
confidential informant in the campaign.''? If so, this is bigger than
Watergate! Despite the disgusting, illegal and unwarranted Witch Hunt,
we have had the most successful first 17 month Administration in U.S.
history - by far! Sorry to the Fake News Media and ``Haters,''? but
that's the way it is! ``Apparently the DOJ put a Spy in the Trump
Campaign. This has never been done before and by any means necessary,
they are out to frame Donald Trump for crimes he didn't commit.''? David
Asman @LouDobbs @GreggJarrett Really bad stuff! Why isn't disgraced FBI
official Andrew McCabe being investigated for the \$700,000 Crooked
Hillary Democrats in Virginia, led by Clinton best friend Terry M (under
FBI investigation that they killed) gave to McCabe's wife in her run for
office? Then dropped case on Clinton! Reports are there was indeed at
least one FBI representative implanted, for political purposes, into my
campaign for president. It took place very early on, and long before the
phony Russia Hoax became a ``hot''? Fake News story. If true - all time
biggest political scandal! If the FBI or DOJ was infiltrating a campaign
for the benefit of another campaign, that is a really big deal. Only the
release or review of documents that the House Intelligence Committee
(also, Senate Judiciary) is asking for can give the conclusive answers.
Drain the Swamp! Things are really getting ridiculous. The Failing and
Crooked (but not as Crooked as Hillary Clinton) @nytimes has done a long
\& boring story indicating that the World's most expensive Witch Hunt
has found nothing on Russia \& me so now they are looking at the rest of
the World! ....At what point does this soon to be \$20,000,000 Witch
Hunt, composed of 13 Angry and Heavily Conflicted Democrats and two
people who have worked for Obama for 8 years, STOP! They have found no
Collussion with Russia, No Obstruction, but they aren't looking at the
corruption... ...in the Hillary Clinton Campaign where she deleted
33,000 Emails, got \$145,000,000 while Secretary of State, paid McCabes
wife \$700,000 (and got off the FBI hook along with Terry M) and so much
more. Republicans and real Americans should start getting tough on this
Scam. Now that the Witch Hunt has given up on Russia and is looking at
the rest of the World, they should easily be able to take it into the
Mid-Term Elections where they can put some hurt on the Republican Party.
Don't worry about Dems FISA Abuse, missing Emails or Fraudulent Dossier!
What ever happened to the Server, at the center of so much Corruption,
that the Democratic National Committee REFUSED to hand over to the hard
charging (except in the case of Democrats) FBI? They broke into homes \&
offices early in the morning, but were afraid to take the Server?
....and why hasn't the Podesta brother been charged and arrested, like
others, after being forced to close down his very large and successful
firm? Is it because he is a VERY well connected Democrat working in the
Swamp of Washington, D.C.? The Witch Hunt finds no Collusion with Russia
- so now they're looking at the rest of the World. Oh' great! I hereby
demand, and will do so officially tomorrow, that the Department of
Justice look into whether or not the FBI/DOJ infiltrated or surveilled
the Trump Campaign for Political Purposes - and if any such demands or
requests were made by people within the Obama Administration! ``John
Brennan is panicking. He has disgraced himself, he has disgraced the
Country, he has disgraced the entire Intelligence Community. He is the
one man who is largely responsible for the destruction of American's
faith in the Intelligence Community and in some people at the....
....top of the FBI. Brennan started this entire debacle about President
Trump. We now know that Brennan had detailed knowledge of the (phony)
Dossier...he knows about the Dossier, he denies knowledge of the
Dossier, he briefs the Gang of 8 on the Hill about the Dossier,
which.... ...they then used to start an investigation about Trump. It is
that simple. This guy is the genesis of this whole Debacle. This was a
Political hit job, this was not an Intelligence Investigation. Brennan
has disgraced himself, he's worried about staying out of Jail.''? Dan
Bongino The Wall Street Journal asks, ``WHERE IN THE WORLD WAS BARACK
OBAMA?''? A very good question! ...Follow the money! The spy was there
early in the campaign and yet never reported Collusion with Russia,
because there was no Collusion. He was only there to spy for political
reasons and to help Crooked Hillary win - just like they did to Bernie
Sanders, who got duped! If the person placed very early into my campaign
wasn't a SPY put there by the previous Administration for political
purposes, how come such a seemingly massive amount of money was paid for
services rendered - many times higher than normal... @foxandfriends
``New Bombshell in the Obama Spying Scandal. Did other Agencies SPY on
Trump Campaign?''? Even Clapper, worlds dumbest former Intelligence
Head, who has the problem of lying a lot, used the word SPY when
describing the illegal activities! Look how things have turned around on
the Criminal Deep State. They go after Phony Collusion with Russia, a
made up Scam, and end up getting caught in a major SPY scandal the likes
of which this country may never have seen before! What goes around,
comes around! ``It's clear that they had eyes and ears all over the
Trump Campaign''? Judge Andrew Napolitano SPYGATE could be one of the
biggest political scandals in history! ``Trump should be happy that the
FBI was SPYING on his campaign''? No, James Clapper, I am not happy.
Spying on a campaign would be illegal, and a scandal to boot! WITCH
HUNT! Clapper has now admitted that there was Spying in my campaign.
Large dollars were paid to the Spy, far beyond normal. Starting to look
like one of the biggest political scandals in U.S. history. SPYGATE - a
terrible thing! Not surprisingly, the GREAT Men \& Women of the FBI are
starting to speak out against Comey, McCabe and all of the political
corruption and poor leadership found within the top ranks of the FBI.
Comey was a terrible and corrupt leader who inflicted great pain on the
FBI! \#SPYGATE The Democrats are now alluding to the the concept that
having an Informant placed in an opposing party's campaign is different
than having a Spy, as illegal as that may be. But what about an
``Informant''? who is paid a fortune and who ``sets up''? way earlier
than the Russian Hoax? Can anyone even imagine having Spies placed in a
competing campaign, by the people and party in absolute power, for the
sole purpose of political advantage and gain? And to think that the
party in question, even with the expenditure of far more money, LOST!
``Everyone knows there was a Spy, and in fact the people who were
involved in the Spying are admitting that there was a Spy...Widespread
Spying involving multiple people.''? Mollie Hemingway, The Federalist
Senior Editor But the corrupt Mainstream Media hates this monster story!
With Spies, or ``Informants''? as the Democrats like to call them
because it sounds less sinister (but it's not), all over my campaign,
even from a very early date, why didn't the crooked highest levels of
the FBI or ``Justice''? contact me to tell me of the phony Russia
problem? This whole Russia Probe is Rigged. Just an excuse as to why the
Dems and Crooked Hillary lost the Election and States that haven't been
lost in decades. 13 Angry Democrats, and all Dems if you include the
people who worked for Obama for 8 years. \#SPYGATE \& CONFLICTS OF
INTEREST! When will the 13 Angry Democrats (\& those who worked for
President O), reveal their disqualifying Conflicts of Interest? It's
been a long time now! Will they be indelibly written into the Report
along with the fact that the only Collusion is with the Dems, Justice,
FBI \& Russia? Who's going to give back the young and beautiful lives
(and others) that have been devastated and destroyed by the phony Russia
Collusion Witch Hunt? They journeyed down to Washington, D.C., with
stars in their eyes and wanting to help our nation...They went back home
in tatters! Why didn't the 13 Angry Democrats investigate the campaign
of Crooked Hillary Clinton, many crimes, much Collusion with Russia? Why
didn't the FBI take the Server from the DNC? Rigged Investigation! Why
didn't President Obama do something about the so-called Russian Meddling
when he was told about it by the FBI before the Election? Because he
thought Crooked Hillary was going to win, and he didn't want to upset
the apple cart! He was in charge, not me, and did nothing. ``The
President deserves some answers.''? @FoxNews in discussing ``SPYGATE.''?
``Sally Yates is part of concerns people have raised about bias in the
Justice Dept. I find her actions to be really quite unbelievable.''?
Jonathan Turley ``We now find out that the Obama Administration put the
opposing campaigns presidential candidate, or his campaign, under
investigation. That raises legitimate questions. I just find this really
odd...this goes to the heart of our electoral system.''? Jonathan Turley
on @FoxNews ``This investigation involved far more surveillance than we
ever had any idea about. It wasn't just a wiretap against a campaign
aide...it was secretly gathering information on the Trump
Campaign...people call that Spying...this is unprecedented and
scandalous.''? Mollie Hemingway The 13 Angry Democrats (plus people who
worked 8 years for Obama) working on the rigged Russia Witch Hunt, will
be MEDDLING with the mid-term elections, especially now that Republicans
(stay tough!) are taking the lead in Polls. There was no Collusion,
except by the Democrats! Why aren't the 13 Angry and heavily conflicted
Democrats investigating the totally Crooked Campaign of totally Crooked
Hillary Clinton. It's a Rigged Witch Hunt, that's why! Ask them if they
enjoyed her after election celebration! Sorry, I've got to start
focusing my energy on North Korea Nuclear, bad Trade Deals, VA Choice,
the Economy, rebuilding the Military, and so much more, and not on the
Rigged Russia Witch Hunt that should be investigating
Clinton/Russia/FBI/Justice/Obama/Comey/Lynch etc. The Fake Mainstream
Media has, from the time I announced I was running for President, run
the most highly sophisticated \& dishonest Disinformation Campaign in
the history of politics. No matter how well WE do, they find fault. But
the forgotten men \& women WON, I'm President! Rep.Trey Gowdy, ``I don't
think so, I think what the President is doing is expressing frustration
that Attorney General Sessions should have shared these reasons for
recusal before he took the job, not afterward. If I were the President
and I picked someone to be the country's.... ....chief law enforcement
officer, and they told me later, ''˜oh by the way I'm not going to be
able to participate in the most important case in the office, I would be
frustrated too...and that's how I read that - Senator Sessions, why
didn't you tell me before I picked you..... ....There are lots of really
good lawyers in the country, he could have picked somebody else!''? And
I wish I did! The soon to be released book, ``The Russia Hoax, The
Illicit Scheme To Clear Hillary Clinton And Frame Donald Trump,''?
written by Gregg Jarrett, looks like a real deal big hit. The Phony
Witch Hunt will be opened up for the world to see! Out in 5 weeks. ``The
recusal of Jeff Sessions was an unforced betrayal of the President of
the United States.''? JOE DIGENOVA, former U.S. Attorney. RUSH LIMBAUGH
``If the FBI was so concerned, and if they weren't targeting Trump, they
should have told Trump. If they were really concerned about the Russians
infiltrating a campaign (hoax), then why not try to stop it? Why not
tell Trump? Because they were pushing this scam.''? Iger, where is my
call of apology? You and ABC have offended millions of people, and they
demand a response. How is Brian Ross doing? He tanked the market with an
ABC lie, yet no apology. Double Standard! The corrupt Mainstream Media
is working overtime not to mention the infiltration of people, Spies
(Informants), into my campaign! Surveillance much? Not that it matters
but I never fired James Comey because of Russia! The Corrupt Mainstream
Media loves to keep pushing that narrative, but they know it is not
true! A.P. has just reported that the Russian Hoax Investigation has now
cost our government over \$17 million, and going up fast. No Collusion,
except by the Democrats! ``John Brennan, no single figure in American
history has done more to discredit the intelligence community than this
liar. Not only is he a liar, he's a liar about being a liar.''? Dan
Bongino on @foxandfriends ....``\$17 million spent, it's a scam
Investigation. Americans are being worked. We now know there was Russian
collusion, with Russians and the Democrats. The Mueller team is stacked
with anti-Trumpers, who actually represented Clinton people (\& gave
\$'s to Crooked H).''? Dan Bongino There was No Collusion with Russia
(except by the Democrats). When will this very expensive Witch Hunt Hoax
ever end? So bad for our Country. Is the Special Counsel/Justice
Department leaking my lawyers letters to the Fake News Media? Should be
looking at Dems corruption instead? Jesse Watters ``The only thing Trump
obstructed was Hillary getting to the White House.''? So true! As only
one of two people left who could become President, why wouldn't the FBI
or Department of ``Justice''? have told me that they were secretly
investigating Paul Manafort (on charges that were 10 years old and had
been previously dropped) during my campaign? Should have told me!
....Paul Manafort came into the campaign very late and was with us for a
short period of time (he represented Ronald Reagan, Bob Dole \& many
others over the years), but we should have been told that Comey and the
boys were doing a number on him, and he wouldn't have been hired! Mark
Penn ``Why are there people from the Clinton Foundation on the Mueller
Staff? Why is there an Independent Counsel? To go after people and their
families for unrelated offenses...Constitution was set up to prevent
this...Stormtrooper tactics almost.''? A disgrace! As has been stated by
numerous legal scholars, I have the absolute right to PARDON myself, but
why would I do that when I have done nothing wrong? In the meantime, the
never ending Witch Hunt, led by 13 very Angry and Conflicted Democrats
(\& others) continues into the mid-terms! The appointment of the Special
Counsel is totally UNCONSTITUTIONAL! Despite that, we play the game
because I, unlike the Democrats, have done nothing wrong! The Fake News
Media is desperate to distract from the economy and record setting
economic numbers and so they keep talking about the phony Russian Witch
Hunt. What is taking so long with the Inspector General's Report on
Crooked Hillary and Slippery James Comey. Numerous delays. Hope Report
is not being changed and made weaker! There are so many horrible things
to tell, the public has the right to know. Transparency! The Russian
Witch Hunt Hoax continues, all because Jeff Sessions didn't tell me he
was going to recuse himself...I would have quickly picked someone else.
So much time and money wasted, so many lives ruined...and Sessions knew
better than most that there was No Collusion! Wow, Strzok-Page, the
incompetent \& corrupt FBI lovers, have texts referring to a
counter-intelligence operation into the Trump Campaign dating way back
to December, 2015. SPYGATE is in full force! Is the Mainstream Media
interested yet? Big stuff! Great interview by @LouDobbs with Chris
Farrell of Judicial Watch concerning the governments
counter-intelligence operation into the Trump Campaign. SPYGATE at the
highest level. Who would believe? Chris Farrell, Judicial Watch. ``They
were running an operation to undermine a candidate for President of the
U.S. These are all violations of law. This is intelligence tradecraft to
steer an election. There's nothing more grave when it comes to abuse of
our intelligence system... ...This is a level of criminality beyond the
pale. This is such a grave abuse of power and authority, it's like
nothing else we've seen in our history. This makes the Nixon Watergate
burglary look like keystone cop stuff ....The greatest Witch Hunt in
political history! Alan Dershowitz, Harvard Law Professor: ``It all
proves that we never needed a Special Counsel....All of this could have
been done by the Justice Dept. Don't need a multi-million dollar group
of people with a target on someone's back. Not the way Justice should
operate.''? So true! When and where will all of the many conflicts of
interest be listed by the 13 Angry Democrats (plus) working on the Witch
Hunt Hoax. There has never been a group of people on a case so biased or
conflicted. It is all a Democrat Excuse for LOSING the Election. Where
is the server? Our Justice Department must not let Awan \& Debbie
Wasserman Schultz off the hook. The Democrat I.T. scandal is a key to
much of the corruption we see today. They want to make a ``plea deal''?
to hide what is on their Server. Where is Server? Really bad! When will
people start saying, ``thank you, Mr. President, for firing James
Comey?''? The Obama Administration is now accused of trying to give Iran
secret access to the financial system of the United States. This is
totally illegal. Perhaps we could get the 13 Angry Democrats to divert
some of their energy to this ``matter''? (as Comey would call it).
Investigate! Now that I am back from Singapore, where we had a great
result with respect to North Korea, the thought process must sadly go
back to the Witch Hunt, always remembering that there was No Collusion
and No Obstruction of the fabricated No Crime. So, the Democrats make up
a phony crime, Collusion with the Russians, pay a fortune to make the
crime sound real, illegally leak (Comey) classified information so that
a Special Councel will be appointed, and then Collude to make this pile
of garbage take on life in Fake News! FBI Agent Peter Strzok, who headed
the Clinton \& Russia investigations, texted to his lover Lisa Page, in
the IG Report, that ``we'll stop''? candidate Trump from becoming
President. Doesn't get any lower than that! The IG Report is a total
disaster for Comey, his minions and sadly, the FBI. Comey will now
officially go down as the worst leader, by far, in the history of the
FBI. I did a great service to the people in firing him. Good Instincts.
Christopher Wray will bring it proudly back! ``Why in the world didn't
Barack Obama fire this guy (Comey)?''? asks Mark Levin! ``Donald Trump
was 100\% right to fire James Comey.''? Mark Levin Wow, what a tough
sentence for Paul Manafort, who has represented Ronald Reagan, Bob Dole
and many other top political people and campaigns. Didn't know Manafort
was the head of the Mob. What about Comey and Crooked Hillary and all of
the others? Very unfair! I've had to beat 17 very talented people
including the Bush Dynasty, then I had to beat the Clinton Dynasty, and
now I have to beat a phony Witch Hunt and all of the dishonest people
covered in the IG Report...and never forget the Fake News Media. It
never ends! The IG Report totally destroys James Comey and all of his
minions including the great lovers, Peter Strzok and Lisa Page, who
started the disgraceful Witch Hunt against so many innocent people. It
will go down as a dark and dangerous period in American History! Daniel
Henninger of The Wall Street Journal: ``This IG Report makes it clear,
as did Rod Rosenstein's memo, that Trump was absolutely justified,
unquestionably justified, in firing Jim Comey. So I think the Mueller
Investigation is on pretty weak grounds right now.''? Witch Hunt! WITCH
HUNT! There was no Russian Collusion. Oh, I see, there was no Russian
Collusion, so now they look for obstruction on the no Russian Collusion.
The phony Russian Collusion was a made up Hoax. Too bad they didn't look
at Crooked Hillary like this. Double Standard! Why was the FBI giving so
much information to the Fake News Media. They are not supposed to be
doing that, and knowing the enemy of the people Fake News, they put
their own spin on it - truth doesn't matter to them! Why was the FBI's
sick loser, Peter Strzok, working on the totally discredited Mueller
team of 13 Angry \& Conflicted Democrats, when Strzok was giving Crooked
Hillary a free pass yet telling his lover, lawyer Lisa Page, that
``we'll stop''? Trump from becoming President? Witch Hunt! ``The highest
level of bias I've ever witnessed in any law enforcement officer.''?
Trey Gowdy on the FBI's own, Peter Strzok. Also remember that they all
worked for Slippery James Comey and that Comey is best friends with
Robert Mueller. A really sick deal, isn't it? Comey gave Strozk his
marching orders. Mueller is Comey's best friend. Witch Hunt! I can't
think of something more concerning than a law enforcement officer
suggesting that their going to use their powers to affect an
election!''? Inspector General Horowitz on what was going on with
numerous people regarding my election. A Rigged Witch Hunt!p ``FBI texts
have revealed anti-Trump Bias.''? @FoxNews Big News, but the Fake News
doesn't want to cover. Total corruption - the Witch Hunt has turned out
to be a scam! At some point soon the Mainstream Media will have to cover
correctly, too big a story! Our great Judge Jeanine Pirro is out with a
new book, ``Liars, Leakers and Liberals, the Case Against the Anti-Trump
Conspiracy,''? which is fantastic. Go get it! .@FoxNews Poll numbers
plummet on the Democrat inspired and paid for Russian Witch Hunt. With
all of the bias, lying and hate by the investigators, people want the
investigators investigated. Much more will come out. A total scam and
excuse for the Dems losing the Election! The Russian Witch Hunt is
Rigged! Former Attorney General Michael Mukasey said that President
Trump is probably correct that there was surveillance on Trump Tower.
Actually, far greater than would ever have been believed! I have tried
to stay uninvolved with the Department of Justice and FBI (although I do
not legally have to), because of the now totally discredited and very
expensive Witch Hunt currently going on. But you do have to ask why the
DOJ \& FBI aren't giving over requested documents? Why is Senator Mark
Warner (D-VA), perhaps in a near drunken state, claiming he has
information that only he and Bob Mueller, the leader of the 13 Angry
Democrats on a Witch Hunt, knows? Isn't this highly illegal. Is it being
investigated? The hearing of Peter Strzok and the other hating frauds at
the FBI \& DOJ should be shown to the public on live television, not a
closed door hearing that nobody will see. We should expose these people
for what they are - there should be total transparency! ``The most
profound question of our era: Was there a conspiracy in the Obama
Department of Justice and the FBI to prevent Donald Trump from becoming
President of the U.S., and was Strzok at the core of the conspiracy?''?
Judge Andrew Napolitano Lover FBI Agent Peter Strzok was given poor
marks on yesterday's closed door testimony and, according to most
reports, refused to answer many questions. There was no Collusion and
the Witch Hunt, headed by 13 Angry Democrats and others who are totally
conflicted, is Rigged! Russia continues to say they had nothing to do
with Meddling in our Election! Where is the DNC Server, and why didn't
Shady James Comey and the now disgraced FBI agents take and closely
examine it? Why isn't Hillary/Russia being looked at? So many questions,
so much corruption! Peter Strzok worked as the leader of the Rigged
Witch Hunt for a long period of time - he got it started and was only
fired because the gig was up. But remember, he took his orders from
Comey and McCabe and they took their orders from you know who.
Mueller/Comey best friends! When is Bob Mueller going to list his
Conflicts of Interest? Why has it taken so long? Will they be listed at
the top of his \$22,000,000 Report...And what about the 13 Angry
Democrats, will they list their conflicts with Crooked H? How many
people will be sent to jail and...... ....persecuted on old and/or
totally unrelated charges (there was no collusion and there was no
obstruction of the no collusion)...And what is going on in the FBI \&
DOJ with Crooked Hillary, the DNC and all of the lies? A disgraceful
situation! Just won lawsuit filed by the DNC and a bunch of Democrat
crazies trying to claim the Trump Campaign (and others), colluded with
Russia. They haven't figured out that this was an excuse for them losing
the election! Public opinion has turned strongly against the Rigged
Witch Hunt and the ``Special''? Counsel because the public understands
that there was no Collusion with Russia (so ridiculous), that the two
FBI lovers were a fraud against our Nation \& that the only Collusion
was with the Dems! The Rigged Witch Hunt, originally headed by FBI lover
boy Peter S (for one year) \& now, 13 Angry Democrats, should look into
the missing DNC Server, Crooked Hillary's illegally deleted Emails, the
Pakistani Fraudster, Uranium One, Podesta \& so much more. It's a
Democrat Con Job! Ex-FBI LAYER Lisa Page today defied a House of
Representatives issued Subpoena to testify before Congress! Wow, but is
anybody really surprised! Together with her lover, FBI Agent Peter
Strzok, she worked on the Rigged Witch Hunt, perhaps the most tainted
and corrupt case EVER! How can the Rigged Witch Hunt proceed when it was
started, influenced and worked on, for an extended period of time, by
former FBI Agent/Lover Peter Strzok? Read his hate filled and totally
biased Emails and the answer is clear! As I head out to a very important
NATO meeting, I see that FBI Lover/Agent Lisa Page is dodging a Subpoena
\& is refusing to show up and testify. What can she possibly say about
her statements and lies. So much corruption on the other side. Where is
the Attorney General? @FoxNews ....Where is the DNC Server, and why
didn't the FBI take possession of it? Deep State? The stories you heard
about the 12 Russians yesterday took place during the Obama
Administration, not the Trump Administration. Why didn't they do
something about it, especially when it was reported that President Obama
was informed by the FBI in September, before the Election? These Russian
individuals did their work during the Obama years. Why didn't Obama do
something about it? Because he thought Crooked Hillary Clinton would
win, that's why. Had nothing to do with the Trump Administration, but
Fake News doesn't want to report the truth, as usual! Heading to
Helsinki, Finland -- looking forward to meeting with President Putin
tomorrow. Unfortunately, no matter how well I do at the Summit, if I was
given the great city of Moscow as retribution for all of the sins and
evils committed by Russia... President Obama thought that Crooked
Hillary was going to win the election, so when he was informed by the
FBI about Russian Meddling, he said it couldn't happen, was no big deal,
\& did NOTHING about it. When I won it became a big deal and the Rigged
Witch Hunt headed by Strzok! Our relationship with Russia has NEVER been
worse thanks to many years of U.S. foolishness and stupidity and now,
the Rigged Witch Hunt! The meeting between President Putin and myself
was a great success, except in the Fake News Media! While I had a great
meeting with NATO, raising vast amounts of money, I had an even better
meeting with Vladimir Putin of Russia. Sadly, it is not being reported
that way - the Fake News is going Crazy! Thank you @RandPaul. ``The
President has gone through a year and a half of totally partisan
investigations - what's he supposed to think?''? So many people at the
higher ends of intelligence loved my press conference performance in
Helsinki. Putin and I discussed many important subjects at our earlier
meeting. We got along well which truly bothered many haters who wanted
to see a boxing match. Big results will come! Some people HATE the fact
that I got along well with President Putin of Russia. They would rather
go to war than see this. It's called Trump Derangement Syndrome! The
Fake News Media wants so badly to see a major confrontation with Russia,
even a confrontation that could lead to war. They are pushing so
recklessly hard and hate the fact that I'll probably have a good
relationship with Putin. We are doing MUCH better than any other
country! ``Trump recognized Russian Meddling MANY TIMES.''? Thank you to
@foxandfriends and @FoxNews for actually showing the clips. The Fake
News wants no part of that narrative! Too bad they don't want to focus
on all of the ECONOMIC and JOBS records being set. I got severely
criticized by the Fake News Media for being too nice to President Putin.
In the Old Days they would call it Diplomacy. If I was loud \& vicious,
I would have been criticized for being too tough. Remember when they
said I was too tough with Chairman Kim? Hypocrites! Inconceivable that
the government would break into a lawyer's office (early in the morning)
- almost unheard of. Even more inconceivable that a lawyer would tape a
client - totally unheard of \& perhaps illegal. The good news is that
your favorite President did nothing wrong! The Rigged Witch Hunt, headed
by the 13 Angry Democrats (and now 4 more have been added, one who
worked directly for Obama W.H.), seems intent on damaging the Republican
Party's chances in the November Election. This Democrat excuse for
losing the ''˜16 Election never ends! No Collusion, No Obstruction - but
that doesn't matter because the 13 Angry Democrats, who are only after
Republicans and totally protecting Democrats, want this Witch Hunt to
drag out to the November Election. Republicans better get smart fast and
expose what they are doing! Congratulations to @JudicialWatch and
@TomFitton on being successful in getting the Carter Page FISA
documents. As usual they are ridiculously heavily redacted but confirm
with little doubt that the Department of ``Justice''? and FBI misled the
courts. Witch Hunt Rigged, a Scam! Looking more \& more like the Trump
Campaign for President was illegally being spied upon (surveillance) for
the political gain of Crooked Hillary Clinton and the DNC. Ask her how
that worked out - she did better with Crazy Bernie. Republicans must get
tough now. An illegal Scam! Andrew McCarthy - ``I said this could never
happen. This is so bad that they should be looking at the judges who
signed off on this stuff, not just the people who gave it. It is so bad
it screams out at you.''? On the whole FISA scam which led to the rigged
Mueller Witch Hunt! I had a GREAT meeting with Putin and the Fake News
used every bit of their energy to try and disparage it. So bad for our
country! .@PeteHegseth on @FoxNews ``Source \#1 was the (Fake) Dossier.
Yes, the Dirty Dossier, paid for by Democrats as a hit piece against
Trump, and looking for information that could discredit Candidate \#1
Trump. Carter Page was just the foot to surveil the Trump campaign...''?
ILLEGAL! So President Obama knew about Russia before the Election. Why
didn't he do something about it? Why didn't he tell our campaign?
Because it is all a big hoax, that's why, and he thought Crooked Hillary
was going to win!!! So we now find out that it was indeed the unverified
and Fake Dirty Dossier, that was paid for by Crooked Hillary Clinton and
the DNC, that was knowingly \& falsely submitted to FISA and which was
responsible for starting the totally conflicted and discredited Mueller
Witch Hunt! When you hear the Fake News talking negatively about my
meeting with President Putin, and all that I gave up, remember, I gave
up NOTHING, we merely talked about future benefits for both countries.
Also, we got along very well, which is a good thing, except for the
Corrupt Media! ``It was classified to cover up misconduct by the FBI and
the Justice Department in misleading the Court by using this Dossier in
a dishonest way to gain a warrant to target the Trump Team. This is a
Clinton Campaign document. It was a fraud and a hoax designed to target
Trump.... ....and the DOJ, FBI and Obama Gang need to be held to
account. Source \#1 was the major source. Avoided talking about it being
the Clinton campaign behind it. Misled the Court to provide a pretext to
SPY on the Trump Team. Not about Carter Page..was all about getting
Trump..... .....''?Carter Page wasn't a spy, wasn't an agent of the
Russians - he would have cooperated with the FBI. It was a fraud and a
hoax designed to target Trump.''? Tom Fitton @JudicialWatch A disgrace
to America. They should drop the discredited Mueller Witch Hunt now!
``The Russia Hoax, The Illicit Scheme To Clear Hillary Clinton \& Frame
Donald Trump''? is a Hot Seller, already Number One! More importantly,
it is a great book that everyone is talking about. It covers the Rigged
Witch Hunt brilliantly. Congratulations to Gregg Jarrett! What kind of a
lawyer would tape a client? So sad! Is this a first, never heard of it
before? Why was the tape so abruptly terminated (cut) while I was
presumably saying positive things? I hear there are other clients and
many reporters that are taped - can this be so? Too bad! .@AlanDersh, a
brilliant lawyer, who although a Liberal Democrat who probably didn't
vote for me, has discussed the Witch Hunt with great clarity and in a
very positive way. He has written a new and very important book...
...called ``The Case Against Impeaching Trump,''? which I would
encourage all people with Trump Derangement Syndrome to read! ....,the
only Collusion with Russia was with the Democrats, so now they are
looking at my Tweets (along with 53 million other people) - the rigged
Witch Hunt continues! How stupid and unfair to our Country....And so the
Fake News doesn't waste my time with dumb questions, NO,.... .....I did
NOT know of the meeting with my son, Don jr. Sounds to me like someone
is trying to make up stories in order to get himself out of an unrelated
jam (Taxi cabs maybe?). He even retained Bill and Crooked Hillary's
lawyer. Gee, I wonder if they helped him make the choice! There is No
Collusion! The Robert Mueller Rigged Witch Hunt, headed now by 17
(increased from 13, including an Obama White House lawyer) Angry
Democrats, was started by a fraudulent Dossier, paid for by Crooked
Hillary and the DNC. Therefore, the Witch Hunt is an illegal Scam! Is
Robert Mueller ever going to release his conflicts of interest with
respect to President Trump, including the fact that we had a very nasty
\& contentious business relationship, I turned him down to head the FBI
(one day before appointment as S.C.) \& Comey is his close friend..
....Also, why is Mueller only appointing Angry Dems, some of whom have
worked for Crooked Hillary, others, including himself, have worked for
Obama....And why isn't Mueller looking at all of the criminal activity
\& real Russian Collusion on the Democrats side-Podesta, Dossier?
Collusion is not a crime, but that doesn't matter because there was No
Collusion (except by Crooked Hillary and the Democrats)! ``FBI Agent
Peter Strzok (on the Mueller team) should have recused himself on day
one. He was out to STOP THE ELECTION OF DONALD TRUMP. He needed an
insurance policy. Those are illegal, improper goals, trying to influence
the Election. He should never, ever been allowed to........ .....remain
in the FBI while he himself was being investigated. This is a real
issue. It won't go into a Mueller Report because Mueller is going to
protect these guys. Mueller has an interest in creating the illusion of
objectivity around his investigation.''? ALAN DERSHOWITZ.... ..This is a
terrible situation and Attorney General Jeff Sessions should stop this
Rigged Witch Hunt right now, before it continues to stain our country
any further. Bob Mueller is totally conflicted, and his 17 Angry
Democrats that are doing his dirty work are a disgrace to USA! Paul
Manafort worked for Ronald Reagan, Bob Dole and many other highly
prominent and respected political leaders. He worked for me for a very
short time. Why didn't government tell me that he was under
investigation. These old charges have nothing to do with Collusion - a
Hoax! Russian Collusion with the Trump Campaign, one of the most
successful in history, is a TOTAL HOAX. The Democrats paid for the phony
and discredited Dossier which was, along with Comey, McCabe, Strzok and
his lover, the lovely Lisa Page, used to begin the Witch Hunt.
Disgraceful! Looking back on history, who was treated worse, Alfonse
Capone, legendary mob boss, killer and ``Public Enemy Number One,''? or
Paul Manafort, political operative \& Reagan/Dole darling, now serving
solitary confinement - although convicted of nothing? Where is the
Russian Collusion? ``We already have a smoking gun about a campaign
getting dirt on their opponent, it was Hillary Clinton. How is it OK for
Hillary Clinton to proactively seek dirt from the Russians but the Trump
campaign met at the Russians request and that is bad?''? Marc Thiessen,
Washington Post Congratulations to @GreggJarrett on The TREMENDOUS
success of his just out book, ``The Russia Hoax, The Illicit Scheme To
Clear Hillary Clinton \& Frame Donald Trump.''? Already number one on
Amazon. Hard work from a brilliant guy. It's the Real Story of the
Rigged Witch Hunt! Congratulations to Gregg Jarrett on his book, ``THE
RUSSIA HOAX, THE ILLICIT SCHEME TO CLEAR HILLARY CLINTON AND FRAME
DONALD TRUMP,''? going to \#1 on @nytimes and Amazon. It is indeed a
HOAX and WITCH HUNT, illegally started by people who have already been
disgraced. Great book! Fake News reporting, a complete fabrication, that
I am concerned about the meeting my wonderful son, Donald, had in Trump
Tower. This was a meeting to get information on an opponent, totally
legal and done all the time in politics - and it went nowhere. I did not
know about it! ...Why aren't Mueller and the 17 Angry Democrats looking
at the meetings concerning the Fake Dossier and all of the lying that
went on in the FBI and DOJ? This is the most one sided Witch Hunt in the
history of our country. Fortunately, the facts are all coming out, and
fast! Too bad a large portion of the Media refuses to report the lies
and corruption having to do with the Rigged Witch Hunt - but that is why
we call them FAKE NEWS! ``Collusion with Russia was very real. Hillary
Clinton and her team 100\% colluded with the Russians, and so did Adam
Schiff who is on tape trying to collude with what he thought was
Russians to obtain compromising material on DJT. We also know that
Hillary Clinton paid through.... ....a law firm, eventually Kremlin
connected sources, to gather info on Donald Trump. Collusion is very
real with Russia, but only with Hillary and the Democrats, and we should
demand a full investigation.''? Dan Bongino on @foxandfriends Looking
forward to the new IG Report! ``There has been no evidence whatsoever
that Donald Trump or the campaign was involved in any kind of collusion
to fix the 2016 election. In fact the evidence is the opposite, that
Hillary Clinton \& the Democrats colluded with the Russians to fix the
2016 election.''? @GrahamLedger This is an illegally brought Rigged
Witch Hunt run by people who are totally corrupt and/or conflicted. It
was started and paid for by Crooked Hillary and the Democrats. Phony
Dossier, FISA disgrace and so many lying and dishonest people already
fired. 17 Angry Dems? Stay tuned! @LindseyGrahamSC ``Why didn't the FBI
tell President Trump that they had concerns about Carter Page? Is there
a double standard here?''? They told Senator Diane Feinstein that she
had a spy - but not Trump. Is that entrapment or did they just want to
use Page as an excuse to SPY? Jenna Ellis ``FBI thought they wouldn't
get caught because they thought that Hillary was going to win. There is
overt bias and that depends on whether you are Democrat or Republican -
a double standard that needs to stop.''? .@MariaBartiromo ``No evidence
to launch even an investigation into potential collusion between Donald
Trump and the Russians - and here we are, a year and a half later.''?
Why isn't the FBI giving Andrew McCabe text messages to Judicial Watch
or appropriate governmental authorities. FBI said they won't give up
even one (I may have to get involved, DO NOT DESTROY). What are they
hiding? McCabe wife took big campaign dollars from Hillary people.....
.....Will the FBI ever recover it's once stellar reputation, so badly
damaged by Comey, McCabe, Peter S and his lover, the lovely Lisa Page,
and other top officials now dismissed or fired? So many of the great men
and women of the FBI have been hurt by these clowns and losers! The big
story that the Fake News Media refuses to report is lowlife Christopher
Steele's many meetings with Deputy A.G. Bruce Ohr and his beautiful
wife, Nelly. It was Fusion GPS that hired Steele to write the phony \&
discredited Dossier, paid for by Crooked Hillary \& the DNC....
.@JudgeJeanine ``Bob Mueller, isn't your whole investigation premised on
a Fake Dossier, paid for by Hillary, created by a man who hates Donald
Trump, \& used to con a FISA Court Judge. Bob, I really think it's time
for you to give up your phony investigation.''? No Collusion! ``Seems
like the Department of Justice (and FBI) had a program to keep Donald
Trump from becoming President''?. @DarrellIssa @foxandfriends If this
had happened to the other side, everybody involved would be in jail.
This is a Media coverup of the biggest story of our time. Agent Peter
Strzok was just fired from the FBI - finally. The list of bad players in
the FBI \& DOJ gets longer \& longer. Based on the fact that Strzok was
in charge of the Witch Hunt, will it be dropped? It is a total Hoax. No
Collusion, No Obstruction - I just fight back! Just fired Agent Strzok,
formerly of the FBI, was in charge of the Crooked Hillary Clinton sham
investigation. It was a total fraud on the American public and should be
properly redone! Tom Fitton of Judicial Watch: ``The Strzok firing is as
much about the Mueller operation as anything else. There would be no
Mueller Special Councel to investigate so called collusion but for the
machinations of Strzok \& his colleagues at the top levels of the FBI.
We know this... ....guy was corrupt and had anti-Trump animus. Strzok
and others at the FBI should be criminally investigated for the way the
conducted this investigation. Instead, Mueller is pretending nothing
went wrong. He used Strzok, he used the Clinton DNC Dossier...the whole
thing.... ....should be shut down. The Strzok firing shows that the
fundamental underpinnings of the investigation were corrupt. It should
be shut down by the courts or by honest prosecutors.''? Thank you
Judicial Watch, I couldn't have said it better myself! Bruce Ohr of the
``Justice''? Department (can you believe he is still there) is accused
of helping disgraced Christopher Steele ``find dirt on Trump.''? Ohr's
wife, Nelly, was in on the act big time - worked for Fusion GPS on Fake
Dossier. @foxandfriends ``They were all in on it, clear Hillary Clinton
and FRAME Donald Trump for things he didn't do.''? Gregg Jarrett on
@foxandfriends If we had a real Attorney General, this Witch Hunt would
never have been started! Looking at the wrong people. Fired FBI Agent
Peter Strzok is a fraud, as is the rigged investigation he started.
There was no Collusion or Obstruction with Russia, and everybody,
including the Democrats, know it. The only Collusion and Obstruction was
by Crooked Hillary, the Democrats and the DNC! Strzok started the
illegal Rigged Witch Hunt - why isn't this so-called ``probe''? ended
immediately? Why aren't these angry and conflicted Democrats instead
looking at Crooked Hillary? Lou Dobbs: ``This cannot go forward...this
Special Counsel with all of his conflicts, with his 17 Angry Democrats,
without any evidence of collusion by the Trump Campaign and Russia. The
Dems are the ones who should be investigated.''? Thank you Lou, so true!
The Rigged Russian Witch Hunt goes on and on as the ``originators and
founders''? of this scam continue to be fired and demoted for their
corrupt and illegal activity. All credibility is gone from this terrible
Hoax, and much more will be lost as it proceeds. No Collusion! ``The
action (the Strzok firing) was a decisive step in the right direction in
correcting the wrongs committed by what has been described as Comey's
skinny inner circle.''? Chris Swecker, former FBI Assistant Director.
``John Brennan is a stain on the Country, we deserve better than
this.''? Former Secret Service Agent and author of new book, ``Spygate,
the Attempted Sabotage of Donald J. Trump,''? Dan Bongino. Thank you
Dan, and good luck with the book! ``Hillary Clinton clearly got a pass
by the FBI. We have the unfortunate situation where they then decided
they were going to frame Donald Trump''? concerning the Rigged Witch
Hunt. JOE DIGENOVA, former U.S. Attorney. Mark Levin ``When they had
power they didn't stop the Russians, the Chinese, the North Koreans,
they funded the Iranians \& are responsible for the greatest scandal in
American history by interfering with our election \& trying to undermine
the Trump Campaign and Trump Presidency.''? ``I'd strip the whole bunch
of them. They're all corrupt. They've all abused their power. They've
all betrayed the American people with a political agenda. They tried to
steal and influence an election in the United States.''? @seanhannity
``The FBI received documents from Bruce Ohr (of the Justice Department
\& whose wife Nelly worked for Fusion GPS).''? Disgraced and fired FBI
Agent Peter Strzok. This is too crazy to be believed! The Rigged Witch
Hunt has zero credibility. ``While Steele shopped the document to
multiple media outlets, he also asked for help with a RUSSIAN
Oligarch.''? Catherine Herridge of @FoxNews @LouDobbs In other words,
they were colluding with Russia! ``Very concerned about Comey's firing,
afraid they will be exposed,''? said Bruce Ohr. DOJ's Emails \& Notes
show Bruce Ohr's connection to (phony \& discredited) Trump Dossier. A
creep thinking he would get caught in a dishonest act. Rigged Witch
Hunt! .@TuckerCarlson speaking of John Brennan: ``How did somebody so
obviously limited intellectually get to be CIA Director in the first
place?''? Now that is a really good question! Then followed by ``Richard
Blumenthal of Connecticut is a FAKE War Hero...''? So true, a total
Fake! How can ``Senator''? Richard Blumenthal, who went around for
twenty years as a Connecticut politician bragging that he was a great
Marine war hero in Vietnam (then got caught and sobbingly admitted he
was neither a Marine nor ever in Vietnam), pass judgement on anyone?
Loser! ``....An incredibly corrupt FBI \& DOJ trying to steer the
outcome of a Presidential Election. Brennan has gone off the deep end,
he's disgraced and discredited himself. His conduct has been
outrageous.''? Chris Farrell, Judicial Watch. ``Director Brennan's
recent statements purport to know as fact that the Trump campaign
colluded with a foreign power. If Director Brennan's statement is based
on intelligence he received while leading the CIA, why didn't he include
it in the Intelligence Community Assessment...... .....released in 2017.
If his statement is based on intelligence he has seen since leaving
office, it constitutes an intelligence breach......''? Richard Burr
(R-NC) Senate Intel Cmte Chair @LouDobbs ``Fox News has learned that
Bruce Ohr wrote Christopher Steele following the firing of James Comey
saying that he was afraid the anti-Trump Russia probe will be
exposed.''? Charles Payne @FoxBusiness How much more does Mueller have
to see? They have blinders on - RIGGED! ``Bruce Ohr of DOJ is in legal
jeopardy, it's astonishing that he's still employed. Bruce \& Nelly
Ohr's bank account is getting fatter \& fatter because of the Dossier
that they are both peddling. He doesn't disclose it under Fed Regs.
Using your Federal office for personal....... ....financial gain is a
Federal Gratuity Statute Violation, Bribery Statute Violation, Honest
Services Violation....all Major Crimes....because the DOJ is run by
BLANK Jeff Sessions......''? Gregg Jarrett. So when does Mueller do what
must be done? Probably never! @FoxNews All of the fools that are so
focused on looking only at Russia should start also looking in another
direction, China. But in the end, if we are smart, tough and well
prepared, we will get along with everyone! Has anyone looked at the
mistakes that John Brennan made while serving as CIA Director? He will
go down as easily the WORST in history \& since getting out, he has
become nothing less than a loudmouth, partisan, political hack who
cannot be trusted with the secrets to our country!

President Trump has publicly criticized dozens of people and groups
related to federal inquiries into
\href{https://www.nytimes3xbfgragh.onion/interactive/2019/01/26/us/politics/trump-contacts-russians-wikileaks.html}{contacts
between his campaign and Russia}, according to a New York Times analysis
of nearly every public statement or Twitter post that he has made while
in office.

67 attacks

Number of attacks

by Trump, each month

Russia investigations

2017

2018

2019

July

July

F.B.I., Justice Dept.

and intelligence agencies

41

Hillary Clinton and

her 2016 campaign

James B. Comey

26

Obama

administration

23

News media

14

2017

July

2018

July

2019

67 attacks

Number of attacks by Trump,

each month

Russia investigations

60

2017

April

July

October

2018

April

July

October

2019

F.B.I., Justice Dept. and intelligence agencies

41

Hillary Clinton and her 2016 campaign

James B. Comey

26

Obama administration

23

News media

14

2017

April

July

October

2018

April

July

October

2019

The attacks, which number nearly 1,200, are part of
\href{https://www.nytimes3xbfgragh.onion/2019/02/19/us/politics/trump-investigations.html}{a
strategy to beat back the investigations}. They have also opened him to
\href{https://www.nytimes3xbfgragh.onion/2018/07/26/us/politics/trump-tweets-mueller-obstruction.html}{possible
obstruction of justice charges}. They include statements made on
Twitter, in official speeches, at rallies and during news media
interviews and other press events.

While it is highly unusual for anyone --- let alone the president of the
United States --- to comment on continuing criminal investigations, Mr.
Trump has done so at least once on 330 days, or more than 43 percent of
his time in office as of Feb. 14.

 Each day that Trump attacked the investigations

2017

Jan.

Feb.

March

April

May

June

July

Aug.

Sept.

Oct.

Nov.

Dec.

2018

Jan.

Feb.

March

April

May

June

July

Aug.

Sept.

Oct.

Nov.

Dec.

2019

Jan.

Feb.

Mr. Trump has employed a wide range of attacks in what appears to be an
attempt to discredit the people and organizations associated with the
investigations.

According to the president, the inquiry by Robert S. Mueller III, the
special counsel, into Russian interference in the 2016 election is the
``single greatest witch hunt in political history.''

Special counsel investigation

Attacked 361 times

Manafort convicted

52

Mueller is

appointed

2017

April

July

October

2018

April

July

October

2019

Manafort convicted

Mueller is

appointed

2017

July

2018

July

2019

Mr. Trump has said that Russian meddling was fabricated ``as an excuse
by the Democrats as to why Crooked Hillary Clinton'' lost.

Hillary Clinton and her campaign

Attacked 295 times

41 attacks

2017

April

July

October

2018

April

July

October

2019

41 attacks

2017

July

2018

July

2019

This ``illegal hoax,'' Mr. Trump said, is perpetuated by the ``fake news
media'' \ldots{}

News media

Attacked 151 times

The Times reports

details of Trump

Tower meeting

13

attacks

2017

April

July

October

2018

April

July

October

2019

The Times reports

details of Trump

Tower meeting

13

attacks

2017

July

2018

July

2019

\ldots{} and ``low-life leakers'' at the F.B.I., including the former
director, James B. Comey, whom Mr. Trump called a ``proven liar and
leaker.'' The president said that the news media and the F.B.I. refuse
to investigate the ``real collusion'' between the Democrats and Russia.

James B. Comey

Attacked 148 times

Comey's book

is published

Trump

fires

Comey

26

attacks

24

43

F.B.I., Justice Dept. and

intelligence agencies

Attacked 277 times

2017

April

July

October

2018

April

July

October

2019

James B. Comey

Attacked 148 times

Comey's book

is published

Trump

fires

Comey

26

attacks

24

F.B.I., Justice Dept.

and intelligence

agencies

Attacked 277 times

43

2017

July

2018

July

2019

He also regularly emphasized, ``we wouldn't even be talking about this
subject'' if Jeff Sessions, the former attorney general, had not recused
himself from any investigation into the campaign.

Jeff Sessions

Attacked 57 times

Sessions

fired

14

attacks

Sessions's

recusal

2017

April

July

October

2018

April

July

October

2019

Sessions's

recusal

Sessions

fired

14

attacks

2017

July

2018

July

2019

Mr. Trump
\href{https://www.nytimes3xbfgragh.onion/2018/11/07/us/politics/sessions-resigns.html}{fired
Mr. Sessions} in November. The next month he said on Twitter, ``Jeff
Sessions should be ashamed of himself for allowing this total HOAX to
get started in the first place!''

Mr. Trump, however, does not disparage everyone involved.

Number of times Trump defended someone, by month

Manafort

convicted

30

defenses

Flynn pleaded

guilty

Stone

indicted

2017

April

July

October

2018

April

July

October

2019

Manafort

convicted

30

defenses

Flynn pleaded

guilty

Stone

indicted

2017

July

2018

July

2019

Trump has described Paul Manafort, his onetime campaign chairman --- who
has been convicted of 10 felonies and is awaiting sentencing --- as a
``very decent man'' and ``honorable person.''

The president has also said he felt ``badly'' for Michael T. Flynn, his
former national security adviser, who pleaded guilty to lying to the
F.B.I.

Mr. Trump praised Roger J. Stone Jr., a longtime associate who has
pleaded not guilty to felony charges in the special counsel
investigation, for having ``guts'' for saying he would refuse to testify
against him.

And Mr. Trump called his eldest son, Donald Trump Jr., a ``good boy''
who did nothing wrong in arranging a meeting at Trump Tower with a
Kremlin-connected lawyer who promised damaging information on Mrs.
Clinton.

But whom or what does he defend the most? President Vladimir V. Putin
and Russia.

Putin and the Russians

Defended 61 times

Trump and Putin

press conference

in Helsinki

Trump meets

Putin

2017

April

July

October

2018

April

July

October

2019

Trump and Putin

press conference

in Helsinki

Trump

meets

Putin

2017

July

2018

July

2019

Source: \href{https://factba.se/}{Factba.se}, a service of FactSquared

Additional work by K.K. Rebecca Lai and Kevin Quealy.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
