 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{/section/politics}{Politics} \textbar{}How Democrats and
Republicans Voted on Witnesses in the Trump Impeachment Trial

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2tljsjy}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-politics-}{%
\subsection{\texorpdfstring{ \href{/section/politics}{Politics}
}{ Politics }}\label{-politics-}}

\hypertarget{how-democrats-and-republicans-voted-on-witnesses-in-the-trump-impeachment-trial}{%
\section{How Democrats and Republicans Voted on Witnesses in the Trump
Impeachment
Trial}\label{how-democrats-and-republicans-voted-on-witnesses-in-the-trump-impeachment-trial}}

JAN. 31, 2020

Motion to Consider Witnesses or Documents

Vote expected later

Total

Dem.Democrats

Rep.Republicans

Yes

49

47

2

More than 50 votes will ensure passage

No

51

0

51

The Senate on Friday rejected a measure to consider calling new
witnesses and evidence in President Trump's impeachment trial. The vote,
51 to 49, was largely along party lines. See how every senator voted
below.

The vote came after eight days of presentations and questioning. The
Senate was divided over whether to compel testimony from additional
witnesses including John R. Bolton, the former national security
adviser.

Democrats needed four Republicans to join them in supporting the motion.
Only two Republican senators, Mitt Romney of Utah and Susan Collins of
Maine, broke with their party and supported the proposal.

\emph{For the latest updates,}
\href{https://www.nytimes3xbfgragh.onion/live/2020/trump-impeachment-trial-01-31}{follow
our live coverage of the impeachment trial}\emph{.}

\hypertarget{how-every-senator-voted}{%
\subsection{How Every Senator Voted}\label{how-every-senator-voted}}

Democrats

 \#1 Witnesses

Tammy Baldwin Wis.

Y

Michael Bennet Colo.

Y

Richard Blumenthal Conn.

Y

Cory Booker N.J.

Y

Sherrod Brown Ohio

Y

Maria Cantwell Wash.

Y

Benjamin L. Cardin Md.

Y

Thomas R. Carper Del.

Y

Bob Casey Pa.

Y

Chris Coons Del.

Y

Catherine Cortez Masto Nev.

Y

Tammy Duckworth Ill.

Y

Richard J. Durbin Ill.

Y

Dianne Feinstein Calif.

Y

Kirsten Gillibrand N.Y.

Y

Kamala Harris Calif.

Y

Maggie Hassan N.H.

Y

Martin Heinrich N.M.

Y

Mazie K. Hirono Hawaii

Y

Doug Jones Ala.

Y

Tim Kaine Va.

Y

Amy Klobuchar Minn.

Y

Patrick J. Leahy Vt.

Y

Joe Manchin III W.Va.

Y

Edward J. Markey Mass.

Y

Robert Menendez N.J.

Y

Jeff Merkley Ore.

Y

Christopher S. Murphy Conn.

Y

Patty Murray Wash.

Y

Gary Peters Mich.

Y

Jack Reed R.I.

Y

Jacky Rosen Nev.

Y

Brian Schatz Hawaii

Y

Chuck Schumer N.Y.

Y

Jeanne Shaheen N.H.

Y

Kyrsten Sinema Ariz.

Y

Tina Smith Minn.

Y

Debbie Stabenow Mich.

Y

Jon Tester Mont.

Y

Tom Udall N.M.

Y

Chris Van Hollen Md.

Y

Mark Warner Va.

Y

Elizabeth Warren Mass.

Y

Sheldon Whitehouse R.I.

Y

Ron Wyden Ore.

Y

Angus King Me.

Y

Bernie Sanders Vt.

Y

Republicans

 \#1 Witnesses

Susan Collins Me.

Y

Mitt Romney Utah

Y

Lamar Alexander Tenn.

N

John Barrasso Wyo.

N

Marsha Blackburn Tenn.

N

Roy Blunt Mo.

N

John Boozman Ark.

N

Mike Braun Ind.

N

Richard M. Burr N.C.

N

Shelley Moore Capito W.Va.

N

Bill Cassidy La.

N

John Cornyn Tex.

N

Tom Cotton Ark.

N

Kevin Cramer N.D.

N

Michael D. Crapo Idaho

N

Ted Cruz Tex.

N

Steve Daines Mont.

N

Michael B. Enzi Wyo.

N

Joni Ernst Iowa

N

Deb Fischer Neb.

N

Cory Gardner Colo.

N

Lindsey Graham S.C.

N

Charles E. Grassley Iowa

N

Josh Hawley Mo.

N

John Hoeven N.D.

N

Cindy Hyde-Smith Miss.

N

James M. Inhofe Okla.

N

Ron Johnson Wis.

N

John Kennedy La.

N

James Lankford Okla.

N

Mike Lee Utah

N

Kelly Loeffler Ga.

N

Mitch McConnell Ky.

N

Martha E. McSally Ariz.

N

Jerry Moran Kan.

N

Lisa Murkowski Alaska

N

Rand Paul Ky.

N

David Perdue Ga.

N

Rob Portman Ohio

N

Jim Risch Idaho

N

Pat Roberts Kan.

N

Michael Rounds S.D.

N

Marco Rubio Fla.

N

Ben Sasse Neb.

N

Rick Scott Fla.

N

Tim Scott S.C.

N

Richard C. Shelby Ala.

N

Dan Sullivan Alaska

N

John Thune S.D.

N

Thom Tillis N.C.

N

Patrick J. Toomey Pa.

N

Roger Wicker Miss.

N

Todd Young Ind.

N

Note: Democratic totals include two independents who caucus with the
Democrats.

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
