Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/realestate}{Real Estate}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/realestate}{Real Estate}\textbar{}Where Are the Best (and
Worst) Cities for Renters?

\url{https://nyti.ms/2Xev4AG}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\href{https://www.nytimes.com/news-event/coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{The
Coronavirus Outbreak}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes.com/2020/08/01/world/coronavirus-covid-19.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Latest
  Updates}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Maps
  and Cases}
\item
  \href{https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes.com/interactive/2020/07/29/us/schools-reopening-coronavirus.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{What
  School May Look Like}
\item
  \href{https://www.nytimes.com/live/2020/07/31/business/stock-market-today-coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Economy}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

Calculator

\hypertarget{where-are-the-best-and-worst-cities-for-renters}{%
\section{Where Are the Best (and Worst) Cities for
Renters?}\label{where-are-the-best-and-worst-cities-for-renters}}

A guide for renters on the move, whether fleeing the pandemic,
considering a professional change or just looking for a change.

By \href{https://www.nytimes.com/by/michael-kolomatsky}{Michael
Kolomatsky}

\begin{itemize}
\item
  July 30, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Like coronavirus, relocation is in the air. The pandemic has sent many
Americans packing, often
\href{https://www.nytimes.com/2020/07/28/realestate/buying-selling-moving-during-coronavirus.html}{moving}
from highly infected areas to places with lower infection rates or with
more
\href{https://www.nytimes.com/2018/12/14/realestate/forget-the-suburbs-its-country-or-bust.html}{green}
space. Others have been forced to move in with friends or
\href{https://www.nytimes.com/2020/06/25/realestate/more-adults-than-ever-live-with-parents-or-grandparents.html}{family}
because of job losses.

As more companies discover that having employees work from home is
\href{https://www.nytimes.com/2020/07/02/upshot/is-the-five-day-office-week-over.html}{feasible},
and as some who have already moved begin to see the benefits of their
new locales, more permanent relocation could follow.

For now, a recent study by
\href{https://wallethub.com/edu/best-cities-for-renters/23010/}{Wallethub}
considered the options for renters in this period of ``pandemic
pricing,'' with lower rents attracting new customers in a volatile
market. The study weighed the pros and cons of hundreds of rental
markets across the country, including the 150 largest U.S. cities along
with other highly populated areas for a total of more than 180 rental
markets covering every state.

The rankings (the source for this week's chart) were determined by
rating each market in two categories: quality of life and attractiveness
of the rental market. Within each, 24 separate factors were considered
and individually weighed.

Quality-of-life rankings took into account, among other factors, the
local job market, school systems, weather, recreation friendliness,
crime and the availability of coronavirus support. Attractiveness of
rental market included the area's share of renters, vacancy rates,
median square footage, median rents and incomes, laws protecting
renters, and the cost of living.

Although the study didn't examine coronavirus infection rates, current
\href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html}{data}
show that among its top 10 rated cities --- most in less densely
populated states like the Dakotas and Maine --- the infection rate is
about 15 per 100,000 residents, while in the bottom 10, largely in
coronavirus hot-spot Southern states, the average is about 44 cases per
100,000.

A general takeaway, for now and possibly for the long term: Head out to
where there are fewer people.

Best Cities for Renters

Worst Cities for Renters

~

OVERALL

RANK

RENTAL

MARKET

RANK

QUALITY

OF LIFE

RANK

~

OVERALL

RANK

RENTAL

MARKET

RANK

QUALITY

OF LIFE

RANK

182

167

82

143

124

181

119

125

121

165

90

167

182

173

179

80

174

172

175

118

182

181

180

179

178

177

176

175

174

173

Hialeah, Fla.

Huntington, W. Va.

Memphis

Cleveland

Detroit

Miami

Jackson, Miss.

Gulfport, Miss.

Augusta, Ga.

Tacoma, Wash.

1

16

23

2

3

62

8

4

43

85

72

21

15

120

113

1

69

96

17

3

1

2

3

4

5

6

7

8

9

10

Bismarck, N.D.

Lewiston, Maine

Lincoln, Neb.

Rapid City, S.D.

Sioux Falls, S.D.

Portland, Maine

Cedar Rapids, Iowa

Fargo, N.D.

Fremont, Calif.

Scottsdale, Ariz.

Best Cities for Renters

~

OVERALL

RANK

RENTAL

MARKET

RANK

QUALITY

OF LIFE

RANK

1

16

23

2

3

62

8

4

43

85

72

21

15

120

113

1

69

96

17

3

1

2

3

4

5

6

7

8

9

10

Bismarck, N.D.

Lewiston, Maine

Lincoln, Neb.

Rapid City, S.D.

Sioux Falls, S.D.

Portland, Maine

Cedar Rapids, Iowa

Fargo, N.D.

Fremont, Calif.

Scottsdale, Ariz.

Worst Cities for Renters

~

OVERALL

RANK

RENTAL

MARKET

RANK

QUALITY

OF LIFE

RANK

182

181

180

179

178

177

176

175

174

173

Hialeah, Fla.

Huntington, W. Va.

Memphis

Cleveland

Detroit

Miami

Jackson, Miss.

Gulfport, Miss.

Augusta, Ga.

Tacoma, Wash.

182

167

82

143

124

181

119

125

121

165

90

167

182

173

179

80

174

172

175

118

Wallethub

By The New York Times

For weekly email updates on residential real estate news, sign up here.
Follow us on Twitter: @nytrealestate.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
