Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/world/europe}{Europe}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/world/europe}{Europe}\textbar{}Carter Page, Ex-Trump
Adviser With Russian Ties, Visits Moscow

\url{https://nyti.ms/2h0uiTm}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{carter-page-ex-trump-adviser-with-russian-ties-visits-moscow}{%
\section{Carter Page, Ex-Trump Adviser With Russian Ties, Visits
Moscow}\label{carter-page-ex-trump-adviser-with-russian-ties-visits-moscow}}

By \href{https://www.nytimes.com/by/ivan-nechepurenko}{Ivan
Nechepurenko}

\begin{itemize}
\item
  Dec. 8, 2016
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

MOSCOW --- Carter Page, an early foreign policy adviser to Donald J.
Trump who was
\href{http://www.nytimes.com/2016/11/01/us/politics/fbi-russia-election-donald-trump.html}{scrutinized
by the F.B.I.} on suspicion of private communications with senior
Russian officials over the summer, was back in Moscow on Thursday.

Mr. Page was closelipped about the purpose of his visit,
\href{https://sputniknews.com/russia/201612081048303433-trump-adviser-russia-talks/}{telling
RIA Novosti}, a Russian state-run news agency, that he would stay in
Moscow until Tuesday and would meet with ``business leaders and thought
leaders.''

Mr. Page, who founded an investment company in New York called
\href{http://globalenergycapital.com/}{Global Energy Capital}, drew
attention during the summer for a speech that criticized the United
States and other Western nations for a ``hypocritical focus on ideas
such as democratization, inequality, corruption and regime change'' in
Russia and in other parts of the former Soviet Union.

He worked as an investment banker in Russia for at least three years in
the 2000s, advising on
\href{http://globalenergycap.com/management/}{several major
transactions} involving Russian state companies. Mr. Page's extensive
business links in Russia prompted suggestions that he might be serving
Mr. Trump as a
\href{https://www.yahoo.com/news/u-s-intel-officials-probe-ties-between-trump-adviser-and-kremlin-175046002.html}{back-channel
liaison} with senior Kremlin officials.

Image

Carter Page in Moscow in July.Credit...Pavel Golovkin/Associated Press

Mr. Page dismissed the accusations, calling the F.B.I. investigation a
``witch hunt.''

Dmitri S. Peskov, the Kremlin's spokesman, told journalists that
government leaders in Moscow had no plans to meet with Mr. Page and that
they had never had any contact with him. ``We have learned about this
from the press,'' Mr. Peskov told the news agency Interfax.

Russia's deputy foreign minister, Sergei A. Ryabkov, said officials at
his department had no plans to meet with Mr. Page.

In Russia's Parliament, Leonid E. Slutsky of the international affairs
committee dismissed talk of Mr. Page as a foreign policy adviser to Mr.
Trump, even though the American president-elect
\href{https://www.washingtonpost.com/blogs/post-partisan/wp/2016/03/21/a-transcript-of-donald-trumps-meeting-with-the-washington-post-editorial-board/?utm_term=.e7c8cc4f1c13}{told
the Washington Post editorial board} in March that he was.

``He is not Mr. Trump's adviser. He is an impostor who likes to make a
lot of media noise about himself,'' Mr. Slutsky said.

In his previous visit to Moscow, in July, Mr. Page gave a speech at a
graduation ceremony at the New Economic School, a Moscow university. At
the time, he insisted that he had traveled to Russia as a private
person.

\href{http://edition.cnn.com/videos/tv/2016/09/25/sotu-carter-page-2.cnn}{Speaking
to CNN} in September, Kellyanne Conway, Mr. Trump's campaign manager,
said that Mr. Page was not part of the Trump team and that he was not
authorized to speak to Russian officials on its behalf.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
