Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/style}{Style}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/style}{Style}\textbar{}Love Letter: The Last Full Moon of
Summer

\url{https://nyti.ms/3bsAg9I}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{love-letter-the-last-full-moon-of-summer}{%
\section{Love Letter: The Last Full Moon of
Summer}\label{love-letter-the-last-full-moon-of-summer}}

Plus: The Modern Love column is again accepting submissions.

By Miya Lee

\begin{itemize}
\item
  Sept. 4, 2020
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Welcome to September.

As you may have known (or seen outside your window), the beginning of
this month brought a full moon. This moon, called the ``Corn Moon'' by
the Algonquin people, is the last full moon of summer.

September's full moon coincides with a number of celebrations in various
religions and cultures, including the Chinese Hungry Ghost Festival and
the Hindu Pitri Paksha, in which deceased people and ancestors are
remembered and honored.

With
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/world/coronavirus-maps.html}{hundreds
of thousands of people} killed by the coronavirus pandemic worldwide, we
thought we would begin this newsletter by remembering and honoring them.

As the seasons change, we hope that the health of the world will change
for the better as well. In the meantime, let's get involved in the
causes that are important to us and, of course, celebrate love.

{[}\emph{Like this newsletter?}
\href{https://www.nytimes3xbfgragh.onion/newsletters/love-letter?module=inline}{\emph{Sign
up here}} \emph{to receive it in your inbox!{]}}

On Sept. 1, Modern Love reopened submissions to its main column and Tiny
Love Stories. If you have a story --- long or short --- please consider
submitting before the inboxes temporarily close again in January.

Black and Indigenous people and other people of color are especially
encouraged to submit, as well as writers outside of the United States,
those with disabilities, and those who identify as members of
\href{https://www.nytimes3xbfgragh.onion/2018/06/21/style/lgbtq-gender-language.html}{L.G.B.T.Q}.
communities.

While love may be universal, individual experiences can differ
immensely. Modern Love is committed to publishing a range of experiences
and perspectives.

\hypertarget{we-want-to-hear-from-you}{%
\subsubsection{\texorpdfstring{\textbf{We want to hear from
you.}}{We want to hear from you.}}\label{we-want-to-hear-from-you}}

We want to deliver content that truly matters to you and your feedback
is helpful. Email your thoughts to
\href{mailto:loveletter@NYTimes.com}{\nolinkurl{loveletter@NYTimes.com}}.

Also, here's how to
\href{https://nl.nytimes3xbfgragh.onion/f/newsletter/jO3tQFgT0oTtrEkB_1KMDg~~/AAAAAQA~/RgRgIBzaP4RqAWh0dHBzOi8vd3d3Lm55dGltZXMuY29tLzIwMTkvMDgvMDYvc3R5bGUvaG93LXRvLXN1Ym1pdC1tb2Rlcm4tbG92ZS1lc3NheXMuaHRtbD90ZT0xJm5sPWxvdmUtbGV0dGVyJmVtYz1lZGl0X2xsXzIwMTkwOTIwJTNGY2FtcGFpZ25faWQlM0QwJmluc3RhbmNlX2lkPTAmc2VnbWVudF9pZD0wJnVzZXJfaWQ9NTdhZTExODUyNjIyNWE4MWE0MmQwNWFmNTQ5NDNkNDYmcmVnaV9pZD0wJm1vZHVsZT1pbmxpbmUmY2FtcGFpZ25faWQ9MTM4Jmluc3RhbmNlX2lkPTE1ODIwJnNlZ21lbnRfaWQ9MjEwNzQmdXNlcl9pZD1hMzc0OWZiMzUxNzkzNWIxZTQyNzBhZWQyZjIyMGY2YiZyZWdpX2lkPTg3MDEzNjQ4O3JlZ2lfaWQ9MCZtb2R1bGU9aW5saW5lVwNueXRCCgAv2pc9XruHOHtSF2VtbWEuZ3JpbGxvQG55dGltZXMuY29tWAQAAAAA}{submit
a Modern Love essay} or how to be featured in
\href{https://nl.nytimes3xbfgragh.onion/f/a/VUmOvPA8RQFKQ8aEcY3i7Q~~/AAAAAQA~/RgRgIBzaP4RpAWh0dHBzOi8vd3d3Lm55dGltZXMuY29tL2ludGVyYWN0aXZlLzIwMTgvMDEvMDQvc3R5bGUvYm9vbWVyLWRpdm9yY2UtMjAxNy5odG1sP3RlPTEmbmw9bG92ZS1sZXR0ZXImZW1jPWVkaXRfbGxfMjAxOTA5MjAlM0ZjYW1wYWlnbl9pZCUzRDAmaW5zdGFuY2VfaWQ9MCZzZWdtZW50X2lkPTAmdXNlcl9pZD01N2FlMTE4NTI2MjI1YTgxYTQyZDA1YWY1NDk0M2Q0NiZyZWdpX2lkPTAmbW9kdWxlPWlubGluZSZjYW1wYWlnbl9pZD0xMzgmaW5zdGFuY2VfaWQ9MTU4MjAmc2VnbWVudF9pZD0yMTA3NCZ1c2VyX2lkPWEzNzQ5ZmIzNTE3OTM1YjFlNDI3MGFlZDJmMjIwZjZiJnJlZ2lfaWQ9ODcwMTM2NDg7cmVnaV9pZD0wJm1vZHVsZT1pbmxpbmVXA255dEIKAC_alz1eu4c4e1IXZW1tYS5ncmlsbG9Abnl0aW1lcy5jb21YBAAAAAA~}{an
Unhitched column}. Don't feel like writing more than a tweet, an
Instagram caption or a Facebook post? Consider
\href{https://nl.nytimes3xbfgragh.onion/f/newsletter/950f6-aK170HA-bgDMlF_Q~~/AAAAAQA~/RgRgIBzaP4RnAWh0dHBzOi8vd3d3Lm55dGltZXMuY29tLzIwMTgvMDkvMTkvc3R5bGUvbW9kZXJuLWxvdmUtdGlueS1sb3ZlLXN0b3JpZXMuaHRtbD90ZT0xJm5sPWxvdmUtbGV0dGVyJmVtYz1lZGl0X2xsXzIwMTkwOTIwJTNGY2FtcGFpZ25faWQlM0QwJmluc3RhbmNlX2lkPTAmc2VnbWVudF9pZD0wJnVzZXJfaWQ9NTdhZTExODUyNjIyNWE4MWE0MmQwNWFmNTQ5NDNkNDYmcmVnaV9pZD0wJm1vZHVsZT1pbmxpbmUmY2FtcGFpZ25faWQ9MTM4Jmluc3RhbmNlX2lkPTE1ODIwJnNlZ21lbnRfaWQ9MjEwNzQmdXNlcl9pZD1hMzc0OWZiMzUxNzkzNWIxZTQyNzBhZWQyZjIyMGY2YiZyZWdpX2lkPTg3MDEzNjQ4O3JlZ2lfaWQ9MCZtb2R1bGU9aW5saW5lVwNueXRCCgAv2pc9XruHOHtSF2VtbWEuZ3JpbGxvQG55dGltZXMuY29tWAQAAAAA}{submitting
to Tiny Love Stories}, which are no more than 100 words. Getting
married? Here's how to
\href{https://nl.nytimes3xbfgragh.onion/f/newsletter/er3_tn9RUSsoSb6-Pk2jUA~~/AAAAAQA~/RgRgIBzaP4QAAWh0dHBzOi8vd3d3Lm55dGltZXMuY29tLzIwMTgvMDEvMDkvZmFzaGlvbi93ZWRkaW5ncy93ZWRkaW5nLXN1Ym1pc3Npb24tZmFxcy5odG1sP21vZHVsZT1pbmxpbmUmdGU9MSZubD1sb3ZlLWxldHRlciZlbWM9ZWRpdF9sbF8yMDIwMDIwNyZjYW1wYWlnbl9pZD0xMzgmaW5zdGFuY2VfaWQ9MTU4MjAmc2VnbWVudF9pZD0yMTA3NCZ1c2VyX2lkPWEzNzQ5ZmIzNTE3OTM1YjFlNDI3MGFlZDJmMjIwZjZiJnJlZ2lfaWQ9ODcwMTM2NDhfbGxfMjAyMDAyMDdXA255dEIKAC_alz1eu4c4e1IXZW1tYS5ncmlsbG9Abnl0aW1lcy5jb21YBAAAAAA~}{submit
a wedding announcement.}

\emph{Continue following our fashion and lifestyle coverage on Facebook
(}\href{https://www.facebookcorewwwi.onion/nytimesstyles}{\emph{Styles}}
\emph{and}
\href{https://www.facebookcorewwwi.onion/modernlove}{\emph{Modern
Love}}\emph{), Twitter
(}\href{https://twitter.com/nytstyles}{\emph{Styles}}\emph{,}
\href{https://twitter.com/nytfashion}{\emph{Fashion}} \emph{and}
\href{https://twitter.com/nytimesvows}{\emph{Weddings}}\emph{) and}
\href{https://instagram.com/nytimesfashion}{\emph{Instagram}}\emph{.}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
