Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/politics}{Politics}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/politics}{Politics}\textbar{}How Bloomberg Outspent His
Rivals, and Sanders Outraised Them All

\url{https://nyti.ms/2V5BQbH}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\begin{itemize}
\item
  \href{https://www.nytimes3xbfgragh.onion/live/2020/09/11/us/trump-vs-biden?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Election
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/elections/election-states-biden-trump.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Paths
  to 270}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2019/us/elections/2020-presidential-election-calendar.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Key
  Dates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/08/31/us/politics/vote-by-mail-deadlines.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Voting
  by Mail}
\item
  \href{https://www.nytimes3xbfgragh.onion/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Politics
  Newsletter}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{How Bloomberg Outspent His Rivals, and Sanders Outraised Them
All}\href{}{Skip to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@NYTimes.com}{\nolinkurl{letters@NYTimes.com}}.

\hypertarget{how-bloomberg-outspent-his-rivals-and-sanders-outraised-them-all}{%
\section{How Bloomberg Outspent His Rivals, and Sanders Outraised Them
All}\label{how-bloomberg-outspent-his-rivals-and-sanders-outraised-them-all}}

By \href{https://www.nytimes3xbfgragh.onion/by/sarah-almukhtar}{Sarah
Almukhtar},
\href{https://www.nytimes3xbfgragh.onion/by/thomas-kaplan}{Thomas
Kaplan},
\href{https://www.nytimes3xbfgragh.onion/by/kk-rebecca-lai}{K.K. Rebecca
Lai} and
\href{https://www.nytimes3xbfgragh.onion/by/rachel-shorey}{Rachel
Shorey}Feb. 21, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{41}
\end{itemize}

\hypertarget{these-six-candidates-have-spent-the-most-money-in-the-race-so-far}{%
\subsubsection{These six candidates have spent the most money in the
race so
far.}\label{these-six-candidates-have-spent-the-most-money-in-the-race-so-far}}

Note: Numbers are cumulative. Candidates are ordered by the total amount
spent through January. Mr. Biden entered the race in the second quarter
of 2019, Mr. Steyer in the third quarter and Mr. Bloomberg in the fourth
quarter.

By the end of January, Michael R. Bloomberg had spent \$409 million on
his presidential campaign, more than what four other leading candidates
--- Bernie Sanders, Joseph R. Biden Jr., Elizabeth Warren and Pete
Buttigieg --- had spent combined since they started running.

Mr. Bloomberg joined the race only in November, while those candidates
have been running since last winter or spring. Three-quarters of his
spending through January was on television and digital advertising.

\emph{{[}See who led the money race in the}
\href{https://www.nytimes3xbfgragh.onion/interactive/2019/us/politics/campaign-finance-2020-fundraising.html}{first}\emph{,}
\href{https://www.nytimes3xbfgragh.onion/interactive/2019/07/16/us/politics/democratic-fundraising-2020.html}{second}\emph{,}
\href{https://www.nytimes3xbfgragh.onion/interactive/2019/10/16/us/elections/democratic-q3-fundraising.html}{third}
\emph{and}
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/02/01/us/elections/democratic-q4-fundraising.html}{fourth}
\emph{quarters of 2019.{]}}

\hypertarget{once-again-mr-sanders-raised-the-most}{%
\subsection{Once again, Mr. Sanders raised the
most.}\label{once-again-mr-sanders-raised-the-most}}

Mr. Sanders, whose campaign is being
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/02/01/us/politics/democratic-presidential-campaign-donors.html?action=click\&module=Top\%20Stories\&pgtype=Homepage}{fueled
by contributions} from a huge roster of online donors, had the biggest
haul in January, according to fund-raising reports filed on Thursday.
Mr. Sanders also raised the most in three of the four quarters in 2019.
(Mr. Bloomberg, a billionaire, is running a self-funded campaign and is
not accepting contributions from donors.)

\hypertarget{amount-raised-from-individual-contributions-in-millions}{%
\subsubsection{Amount Raised From Individual Contributions (in
millions)}\label{amount-raised-from-individual-contributions-in-millions}}

January

Cycle total

1

Bernie SandersSenator from Vermont

\$25.1

\$121.0

2

Elizabeth WarrenSenator from Massachusetts

10.4

81.5

3

Joseph R. Biden Jr.Former vice president

8.9

69.7

4

Pete ButtigiegFormer mayor of South Bend, Ind.

6.2

82.4

5

Amy KlobucharSenator from Minnesota

5.5

30.8

6

Tulsi GabbardCongresswoman from Hawaii

1.1

11.1

7

Tom SteyerFormer hedge fund manager

0.6

3.6

8

Michael R. BloombergFormer mayor of New York City

---

---

Note: Cycle totals include all activity in the 2020 election cycle.

\hypertarget{ms-warren-was-low-on-cash-at-the-end-of-january}{%
\subsection{Ms. Warren was low on cash at the end of
January.}\label{ms-warren-was-low-on-cash-at-the-end-of-january}}

Among the candidates relying on donors to fund their campaigns, Mr.
Sanders had the most money on hand entering February, just before the
Iowa caucuses, the first nominating contest of the primary race.

Ms. Warren entered February with only \$2.3 million on hand. In January,
her campaign obtained a \$3 million line of credit and tapped \$400,000
of it.

The candidates are in the midst of a costly stretch of the calendar,
with the first four contests in February followed by Super Tuesday on
March 3, when 14 states have primaries.

\hypertarget{cash-on-hand-in-millions}{%
\subsubsection{Cash on Hand (in
millions)}\label{cash-on-hand-in-millions}}

Note: Figures are as of Jan. 31. Candidates who are largely or entirely
self-funding their campaigns are excluded.

\hypertarget{mr-buttigieg-and-ms-warren-burned-through-cash-at-a-rapid-clip}{%
\subsection{Mr. Buttigieg and Ms. Warren burned through cash at a rapid
clip.}\label{mr-buttigieg-and-ms-warren-burned-through-cash-at-a-rapid-clip}}

Mr. Buttigieg began January with \$14.5 million in cash on hand and
ended the month with less than half that amount. Ms. Warren began the
month with \$13.7 million and depleted most of her war chest.

Both campaigns gave a more up-to-date glimpse at their fund-raising on
Thursday. Ms. Warren's campaign said it had already raised more than
\$17 million in February, while Mr. Buttigieg said his campaign had
already raised \$11 million.

\hypertarget{burn-rate}{%
\subsubsection{Burn Rate}\label{burn-rate}}

Note: The burn rate shown is a candidate's spending in January relative
to individual contributions he or she received. Contribution refunds are
excluded from the spending figures. The burn rate is greater than 100
percent if a candidate spent more than he or she raised. Candidates who
are largely or entirely self-funding their campaigns are excluded.

\hypertarget{in-january-mr-bloomberg-dropped-about-5000-per-minute}{%
\subsection{In January, Mr. Bloomberg dropped about \$5,000 per
minute.}\label{in-january-mr-bloomberg-dropped-about-5000-per-minute}}

Mr. Bloomberg's campaign spent an eye-popping \$7 million per day in
January --- or roughly \$300,000 per hour, \$5,000 per minute and \$82
per second.

He spent more than \$8 for every dollar spent by Mr. Sanders, the
biggest spender among the candidates relying on donors rather than their
own personal wealth.

\hypertarget{amount-spent-in-millions}{%
\subsubsection{Amount Spent (in
millions)}\label{amount-spent-in-millions}}

January

Cycle total

1

Michael R. BloombergFormer mayor of New York City

\$220.6

\$409.0

2

Tom SteyerFormer hedge fund manager

52.9

253.8

3

Bernie SandersSenator from Vermont

26.5

117.3

4

Elizabeth WarrenSenator from Massachusetts

22.4

90.7

5

Pete ButtigiegFormer mayor of South Bend, Ind.

14.1

76.4

6

Joseph R. Biden Jr.Former vice president

10.7

62.8

7

Amy KlobucharSenator from Minnesota

7.6

31.6

8

Tulsi GabbardCongresswoman from Hawaii

1.8

11.2

Note: Totals include all activity in the 2020 election cycle.

Source: Federal Election Commission

Read 41 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

\hypertarget{our-2020-election-guide}{%
\section{Our 2020 Election Guide}\label{our-2020-election-guide}}

Updated ~Sept. 11, 2020

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{itemize}
\item ~
  \hypertarget{the-latest}{%
  \subsection{The Latest}\label{the-latest}}

  \begin{itemize}
  \item
    Joe Biden and President Trump put
    \href{https://www.nytimes3xbfgragh.onion/2020/09/11/us/politics/shanksville-trump-biden.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{hostilities
    on hold today to travel to ground zero and then to Shanksville, Pa.,
    where they separately honored 9/11 victims}.
  \end{itemize}
\item ~
  \hypertarget{how-to-win-270}{%
  \subsection{How to Win 270}\label{how-to-win-270}}

  \begin{itemize}
  \item
    Joe Biden and Donald Trump need 270 electoral votes to reach the
    White House. Try building
    \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/elections/election-states-biden-trump.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{your
    own coalition of battleground states}~to see potential outcomes.
  \end{itemize}
\item ~
  \hypertarget{voting-by-mail}{%
  \subsection{Voting by Mail}\label{voting-by-mail}}

  \begin{itemize}
  \item
    Will you have enough time to vote by mail in your state? Yes, but
    it's risky to procrastinate.
    \href{https://www.nytimes3xbfgragh.onion/interactive/2020/08/31/us/politics/vote-by-mail-deadlines.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{Check
    your state's deadline.}
  \item
    \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/elections/joe-biden.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{}

    \hypertarget{joe-biden}{%
    \section{Joe Biden}\label{joe-biden}}

    \hypertarget{democrat}{%
    \subsection{Democrat}\label{democrat}}

    \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/elections/donald-trump.html?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{}

    \hypertarget{donald-trump}{%
    \section{Donald Trump}\label{donald-trump}}

    \hypertarget{republican}{%
    \subsection{Republican}\label{republican}}
  \end{itemize}
\item
  \hypertarget{keep-up-with-our-coverage}{%
  \subsection{Keep Up With Our
  Coverage}\label{keep-up-with-our-coverage}}

  \begin{itemize}
  \item
    Get an
    \href{https://www.nytimes3xbfgragh.onion/newsletters/politics?action=click\&pgtype=Article\&state=default\&region=BELOW_MAIN_CONTENT\&context=storylines_guide}{email}~recapping
    the day's news
  \item
    Download our mobile app on
    \href{https://apps.apple.com/us/app/nytimes/id284862083?ls=1\&mat_click_id=5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\&referrer=mat_click_id\%3D5c79ae7455014fd1bd66b5610c05b8f2-20191112-16948\%26link_click_id\%3D722930677036718082}{iOS}~and
    \href{http://a.localytics.com/android?id=com.nytimes.android\&referrer=utm_source\%3Dother_nyt_mobile_web\%26utm_medium\%3DWeb\%2520page\%26utm_term\%3DGeneral\%2520Mobile\%2520Page\%26utm_campaign\%3DNYT\%2520Mobile\%2520General\%2520Page}{Android}~and
    turn on Breaking News and Politics alerts
  \end{itemize}
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
