\href{//www.nytimes3xbfgragh.onion}{}\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{
Election 2018}

\href{//www.nytimes3xbfgragh.onion}{ Home}

\hypertarget{washington-primary-election-results}{%
\section{Washington Primary Election
Results}\label{washington-primary-election-results}}

By THE NEW YORK TIMES Sept. 24, 2018, 6:06 PM ET

\textbf{What to watch:} Two of Washington's 10 congressional districts
have competitive races on Tuesday. The primaries will be ``top two,''
meaning that --- as in California --- the top two finishers will move on
to the general election, regardless of party. \protect\hyperlink{}{Read
more}

In the Eighth District, four main candidates are running to replace
Representative David Reichert, a retiring Republican whose seat is
considered a tossup. Former State Senator Dino Rossi, a Republican, is
expected to make the top two in the primary. The big question is which
Democrat will make it along with him: Shannon Hader, a former official
at the Centers for Disease Control and Prevention; Jason Rittereiser, a
lawyer; or Kim Schrier, a pediatrician.

In the solidly Democratic Ninth District, Representative Adam Smith, a
longtime congressman with a top position on the House Armed Services
Committee, is facing a primary challenge from Sarah Smith, a democratic
socialist. On the surface, this looks a lot like New York's 14th
District, where another democratic socialist, Alexandria Ocasio-Cortez,
beat Joseph Crowley, a longtime congressman with a powerful leadership
position. Ms. Smith has encouraged the comparison, while Mr. Smith has
emphasized the differences between the two races --- including that Ms.
Ocasio-Cortez was born and raised in her district, while Ms. Smith lives
a bit outside this one.

--- MAGGIE ASTOR

\href{https://www.nytimes3xbfgragh.onion/2018/08/07/us/politics/primary-election-today.html}{\emph{Read
more about today's most important races.}}

\hypertarget{us-senate-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-senate-open-primary-election}{U.S.
Senate »}}{U.S. Senate »}}\label{us-senate-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Cantwell* Maria Cantwell* & Democrat Dem. & 929,961 & 54.7\%
&\tabularnewline
 Hutchison Susan Hutchison & Republican Rep. & 413,317 & 24.3\%
&\tabularnewline
 Swank Keith Swank & Republican Rep. & 39,818 & 2.3\% &\tabularnewline
 Gibson Joey Gibson & Republican Rep. & 38,676 & 2.3\% &\tabularnewline
 Tannehill Clint Tannehill & Democrat Dem. & 35,770 & 2.1\%
&\tabularnewline
 Bryant Dave Bryant & Republican Rep. & 33,962 & 2.0\% &\tabularnewline
 Coday Art Coday & Republican Rep. & 30,654 & 1.8\% &\tabularnewline
 Ferguson Jennifer Ferguson & Independent I.P. & 25,224 & 1.5\%
&\tabularnewline
 Owen Tim Owen & Republican Rep. & 23,167 & 1.4\% &\tabularnewline
 Hawkins Matt Hawkins & Republican Rep. & 13,324 & 0.8\%
&\tabularnewline
 Rivers Don Rivers & Democrat Dem. & 12,634 & 0.7\% &\tabularnewline
 Luke Mike Luke & Libertarian Lib. & 12,302 & 0.7\% &\tabularnewline
 Stockwell Glen Stockwell & Republican Rep. & 11,611 & 0.7\%
&\tabularnewline
 Amundson Thor Amundson & Independent I.P. & 9,393 & 0.5\%
&\tabularnewline
 Said Mohammad Said & Democrat Dem. & 8,649 & 0.5\% &\tabularnewline
 Heines Matthew Heines & Republican Rep. & 7,737 & 0.4\%
&\tabularnewline
 Hoffman Steve Hoffman & Soc Soc & 7,390 & 0.4\% &\tabularnewline
 GoodSpaceGuy GoodSpaceGuy & Republican Rep. & 7,057 & 0.4\%
&\tabularnewline
 Orlinski John Orlinski & Republican Rep. & 6,905 & 0.4\%
&\tabularnewline
 Strider Dave Strider & Independent I.P. & 6,821 & 0.4\%
&\tabularnewline
 De La Fuente Rocky De La Fuente & Republican Rep. & 5,724 & 0.3\%
&\tabularnewline
 Deal Jimmie Deal & Green Green & 3,849 & 0.2\% &\tabularnewline
 Wright Sam Wright & Independent Ind. & 3,761 & 0.2\% &\tabularnewline
 Chase Brad Chase & Independent Ind. & 2,655 & 0.2\% &\tabularnewline
 Kalberer George Kalberer & Democrat Dem. & 2,448 & 0.1\%
&\tabularnewline
 Jackson Charlie Jackson & Independent I.P. & 2,411 & 0.1\%
&\tabularnewline
 Smith RC Smith & Republican Rep. & 2,238 & 0.1\% &\tabularnewline
 Butler Jon Butler & Independent I.P. & 2,016 & 0.1\% &\tabularnewline
 Tsimerman Alex Tsimerman & Independent Ind. & 1,366 & 0.1\%
&\tabularnewline
 Others Others & & 317,744 & 18.7\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

1,700,840 votes, 100\% reporting (2,000 of 2,000 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

* Incumbent

Leader

 Cantwell

 Hutchison

\protect\hyperlink{}{+ Show all counties -- Collapse counties}

\hypertarget{us-house-district-1-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-1-primary-election}{U.S.
House District 1
»}}{U.S. House District 1 »}}\label{us-house-district-1-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 DelBene* Suzan DelBene* & Democrat Dem. & 106,107 & 59.3\%
&\tabularnewline
 Beeler Jeffrey Beeler & Republican Rep. & 45,830 & 25.6\%
&\tabularnewline
 Stafne Scott Stafne & Republican Rep. & 20,354 & 11.4\%
&\tabularnewline
 Pilskog Adam Pilskog & Independent I.P. & 5,007 & 2.8\%
&\tabularnewline
 Mair Robert Mair & Independent I.P. & 1,622 & 0.9\% &\tabularnewline
 Others Others & & 6,629 & 3.7\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

178,920 votes, 100\% reporting (214 of 214 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

* Incumbent

\hypertarget{us-house-district-2-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-2-primary-election}{U.S.
House District 2
»}}{U.S. House District 2 »}}\label{us-house-district-2-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Larsen* Rick Larsen* & Democrat Dem. & 101,497 & 64.8\%
&\tabularnewline
 Luke Brian Luke & Libertarian Lib. & 12,320 & 7.9\% &\tabularnewline
 Franco Gary Franco & Independent I.P. & 12,269 & 7.8\% &\tabularnewline
 Carlson Collin Carlson & Democrat Dem. & 12,058 & 7.7\%
&\tabularnewline
 Mover Uncle Mover & Republican Rep. & 11,832 & 7.6\% &\tabularnewline
 Bird Stoney Bird & Green Green & 6,525 & 4.2\% &\tabularnewline
 Others Others & & 30,415 & 19.4\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

156,501 votes, 100\% reporting (197 of 197 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

* Incumbent

\hypertarget{us-house-district-3-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-3-primary-election}{U.S.
House District 3
»}}{U.S. House District 3 »}}\label{us-house-district-3-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Herrera Beutler* Jaime Herrera Beutler* & Republican Rep. & 68,961 &
42.1\% &\tabularnewline
 Long Carolyn Long & Democrat Dem. & 57,798 & 35.3\% &\tabularnewline
 McDevitt David McDevitt & Democrat Dem. & 13,124 & 8.0\%
&\tabularnewline
 Bowerman Earl Bowerman & Republican Rep. & 9,018 & 5.5\%
&\tabularnewline
 Gasque Dorothy Gasque & Democrat Dem. & 7,983 & 4.9\% &\tabularnewline
 Cortney Michael Cortney & Republican Rep. & 5,528 & 3.4\%
&\tabularnewline
 Hash Martin Hash & Democrat Dem. & 1,498 & 0.9\% &\tabularnewline
 Others Others & & 24,027 & 14.7\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

163,910 votes, 100\% reporting (202 of 202 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

* Incumbent

\hypertarget{us-house-district-4}{%
\subsection{U.S. House District 4}\label{us-house-district-4}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Newhouse* Dan Newhouse* & Republican Rep. & 77,203 & 63.2\%
&\tabularnewline
 Brown Christine Brown & Democrat Dem. & 44,868 & 36.8\%
&\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

122,071 votes, 100\% reporting (0 of 0 precincts)

* Incumbent

\hypertarget{us-house-district-5-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-5-primary-election}{U.S.
House District 5
»}}{U.S. House District 5 »}}\label{us-house-district-5-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 McMorris Rodgers* Cathy McMorris Rodgers* & Republican Rep. & 99,689 &
49.3\% &\tabularnewline
 Brown Lisa Brown & Democrat Dem. & 91,738 & 45.4\% &\tabularnewline
 Saulibio Dave Saulibio & Independent Ind. & 4,845 & 2.4\%
&\tabularnewline
 Bonneau Jered Bonneau & Republican Rep. & 4,453 & 2.2\%
&\tabularnewline
 Ilonummi Kari Ilonummi & Republican Rep. & 1,507 & 0.8\%
&\tabularnewline
 Others Others & & 5,960 & 2.9\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

202,232 votes, 100\% reporting (206 of 206 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

* Incumbent

\hypertarget{us-house-district-6-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-6-primary-election}{U.S.
House District 6
»}}{U.S. House District 6 »}}\label{us-house-district-6-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Kilmer* Derek Kilmer* & Democrat Dem. & 117,848 & 63.5\%
&\tabularnewline
 Dightman Douglas Dightman & Republican Rep. & 60,651 & 32.7\%
&\tabularnewline
 Vega Tyler Vega & Progressive Prog. & 7,080 & 3.8\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

185,579 votes, 100\% reporting (211 of 211 precincts)

* Incumbent

\hypertarget{us-house-district-7}{%
\subsection{U.S. House District 7}\label{us-house-district-7}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Jayapal* Pramila Jayapal* & Democrat Dem. & 189,175 & 82.7\%
&\tabularnewline
 Keller Craig Keller & Republican Rep. & 39,657 & 17.3\%
&\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

228,832 votes, 100\% reporting (0 of 0 precincts)

* Incumbent

\hypertarget{us-house-district-8-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-8-primary-election}{U.S.
House District 8
»}}{U.S. House District 8 »}}\label{us-house-district-8-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Rossi Dino Rossi & Republican Rep. & 73,288 & 43.1\% &\tabularnewline
 Schrier Kim Schrier & Democrat Dem. & 31,837 & 18.7\% &\tabularnewline
 Rittereiser Jason Rittereiser & Democrat Dem. & 30,708 & 18.1\%
&\tabularnewline
 Hader Shannon Hader & Democrat Dem. & 21,317 & 12.5\% &\tabularnewline
 Hughes-Hageman Jack Hughes-Hageman & Republican Rep. & 4,270 & 2.5\%
&\tabularnewline
 Pross Gordon Pross & Republican Rep. & 2,081 & 1.2\% &\tabularnewline
 Cramer Tom Cramer & Democrat Dem. & 1,468 & 0.9\% &\tabularnewline
 Grassie Bill Grassie & Independent I.P. & 1,163 & 0.7\%
&\tabularnewline
 Reyes Richard Reyes & Libertarian Lib. & 1,154 & 0.7\% &\tabularnewline
 Arnold Keith Arnold & Independent I.P. & 1,090 & 0.6\% &\tabularnewline
 Dillon Patrick Dillon & Independent I.P. & 898 & 0.5\% &\tabularnewline
 Mahaffey Todd Mahaffey & Independent I.P. & 673 & 0.4\%
&\tabularnewline
 Others Others & & 34,114 & 20.1\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

169,947 votes, 100\% reporting (201 of 201 precincts)

\protect\hyperlink{}{-- Show fewer candidates}

\hypertarget{us-house-district-9-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-9-primary-election}{U.S.
House District 9
»}}{U.S. House District 9 »}}\label{us-house-district-9-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Smith* Adam Smith* & Democrat Dem. & 71,035 & 48.4\% &\tabularnewline
 Smith Sarah Smith & Democrat Dem. & 39,409 & 26.9\% &\tabularnewline
 Basler Doug Basler & Republican Rep. & 36,254 & 24.7\% &\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

146,698 votes, 100\% reporting (184 of 184 precincts)

* Incumbent

\hypertarget{us-house-district-10-}{%
\subsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/elections/results/washington-house-district-10-primary-election}{U.S.
House District 10
»}}{U.S. House District 10 »}}\label{us-house-district-10-}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Candidate & Party & Vote & Pct. &\tabularnewline
\midrule
\endhead
 Heck* Denny Heck* & Democrat Dem. & 82,552 & 58.2\% &\tabularnewline
 Brumbles Joseph Brumbles & Republican Rep. & 45,270 & 31.9\%
&\tabularnewline
 Borrelli Tamborine Borrelli & Independent Ind. & 7,997 & 5.6\%
&\tabularnewline
 Slotnick Nancy Slotnick & Independent I.P. & 6,127 & 4.3\%
&\tabularnewline
\bottomrule
\end{longtable}

\href{https://www.nytimes3xbfgragh.onion/elections/results/washington}{Full
Wash. Results »}

141,946 votes, 100\% reporting (191 of 191 precincts)

* Incumbent

\hypertarget{state-senate}{%
\subsection{State Senate}\label{state-senate}}

Seat Seat

Leader

Rpt.

6

 0\%Jessa Lewis

~

0\%

~

 0\%Jeff Holy

~

~

7

 0\%Karen Hardy

~

0\%

~

 0\%Shelly Short*

~

~

8

 60\%Sharon Brown*

~

95\%

~

 35\%Leo Perales

~

~

13

 0\%Judy Warnick*

Uncontested

15

 0\%Bengie Aguilar

~

0\%

~

 0\%Jim Honeyford*

~

~

21

 49\%Marko Liias*

~

100\%

~

 31\%Mario Lotmore

~

~

26

 50\%Emily Randall

~

84\%

~

 46\%Marty McClendon

~

~

29

 0\%Steve Conway*

~

0\%

~

 0\%Pierre Malebranche

~

~

30

 49\%Mark Miloscia*

~

68\%

~

 39\%Claire Wilson

~

~

31

 56\%Phil Fortunato*

~

86\%

~

 38\%Immaculate Ferreria

~

~

32

 38\%Maralyn Chase*

~

93\%

~

 37\%Jesse Salomon

~

~

33

 69\%Karen Keiser*

~

67\%

~

 25\%Kun Wang

~

~

34

 30\%Joe Nguyen

~

91\%

~

 26\%Shannon Braddock

~

~

35

 39\%Irene Bowling

~

84\%

~

 35\%Tim Sheldon*

~

~

36

 0\%Reuven Carlyle*

~

0\%

~

 0\%Bryan Simonson

~

~

37

 0\%Rebecca Saldana

~

0\%

~

 0\%Beth Broadway

~

~

38

 40\%John McCoy*

 31\%Savio Pham

81\%

39 - Unexpired term

 39\%Claus Joens

 29\%Keith Wagoner*

78\%

42

 46\%Doug Ericksen*

~

98\%

~

 29\%Pinky Vargas

~

~

43

 0\%Jamie Pedersen*

~

0\%

~

 0\%Dan Harder

~

~

44

 56\%Steve Hobbs*

~

95\%

~

 41\%Doug Roulstone

~

~

45

 0\%Manka Dhingra*

~

0\%

~

 0\%Dale Fonk

~

~

46

 0\%David Frockt*

~

0\%

~

 0\%Beth Daranciang

~

~

47

 0\%Mona Das

~

0\%

~

 0\%Joe Fain*

~

~

48

 60\%Patty Kuderer*

~

79\%

~

 29\%Rodney Tom

~

~

* Incumbent~

\protect\hyperlink{}{+ Show all races-- Show fewer races}

\hypertarget{state-house}{%
\subsection{State House}\label{state-house}}

District Dist.

Leader

Rpt.

1 - Position 1

 67\%Derek Stanford*

~

86\%

~

 26\%Josh Colver

~

~

1 - Position 2

 63\%Shelley Kloba*

~

86\%

~

 31\%Debra Blodgett

~

~

2 - Position 1

 0\%Anneliese Feld

~

0\%

~

 0\%Andrew Barkis*

~

~

2 - Position 2

 0\%JT Wilcox*

Uncontested

3 - Position 1

 0\%Marcus Riccelli*

~

0\%

~

 0\%Tom Taylor

~

~

3 - Position 2

 0\%Timm Ormsby*

~

0\%

~

 0\%Dave Lucas

~

~

4 - Position 1

 0\%Ted Cummings

~

0\%

~

 0\%Matt Shea*

~

~

4 - Position 2

 0\%Mary May

~

0\%

~

 0\%Bob McCaslin*

~

~

5 - Position 1

 0\%Bill Ramos

~

0\%

~

 0\%Chad Magendanz

~

~

5 - Position 2

 53\%Lisa Callan

~

89\%

~

 45\%Paul Graves*

~

~

6 - Position 1

 0\%Kay Murano

~

0\%

~

 0\%Mike Volz*

~

~

6 - Position 2

 42\%Dave Wilson

~

76\%

~

 32\%Jenny Graham

~

~

7 - Position 1

 0\%Randy Michaelis

~

0\%

~

 0\%Jacquelin Maycumber*

~

~

7 - Position 2

 63\%Joel Kretz*

 17\%Mike Bell

73\%

8 - Position 1

 49\%Brad Klippert*

~

92\%

~

 34\%Shir Regev

~

~

8 - Position 2

 39\%Matt Boehnke

~

92\%

~

 38\%Christopher Tracy

~

~

9 - Position 1

 0\%Jenn Goulet

~

0\%

~

 0\%Mary Dye*

~

~

9 - Position 2

 0\%Matthew Sutherland

~

0\%

~

 0\%Joe Schmick*

~

~

10 - Position 1

 0\%Scott McMullen

~

0\%

~

 0\%Norma Smith*

~

~

10 - Position 2

 0\%Dave Paul

~

0\%

~

 0\%Dave Hayes*

~

~

11 - Position 1

 0\%Zack Hudgins*

Uncontested

11 - Position 2

 0\%Steve Bergquist*

Uncontested

12 - Position 1

 45\%Keith Goehner

 29\%Ann Diamond

66\%

12 - Position 2

 61\%Mike Steele*

~

66\%

~

 32\%Valerie Sarratt

~

~

13 - Position 1

 0\%Jesse Hegstrom Oakey

~

0\%

~

 0\%Tom Dent*

~

~

13 - Position 2

 0\%Sylvia Hammond

~

0\%

~

 0\%Matt Manweller*

~

~

14 - Position 1

 41\%Chris Corry

~

87\%

~

 32\%Sasha Bentley

~

~

14 - Position 2

 60\%Gina Mosbrucker*

~

85\%

~

 28\%Liz Hallock

~

~

15 - Position 1

 0\%Jack McEntire

~

0\%

~

 0\%Bruce Chandler*

~

~

15 - Position 2

 47\%Jeremie Dufault

 26\%A.J. Cooper

85\%

16 - Position 1

 0\%Everett Maroon

~

0\%

~

 0\%Bill Jenkin*

~

~

16 - Position 2

 39\%Rebecca Francik

~

74\%

~

 35\%Skyler Rude

~

~

17 - Position 1

 49\%Vicki Kraft*

~

87\%

~

 44\%Tanisha Harris

~

~

17 - Position 2

 0\%Damion Jiles

~

0\%

~

 0\%Paul Harris*

~

~

18 - Position 1

 0\%Chris Thobaben

~

0\%

~

 0\%Brandon Vick*

~

~

18 - Position 2

 0\%Kathy Gillespie

~

0\%

~

 0\%Larry Hoff

~

~

19 - Position 1

 0\%Erin Frasier

~

0\%

~

 0\%Jim Walsh*

~

~

19 - Position 2

 58\%Brian Blake*

 22\%Joel McEntire

92\%

20 - Position 1

 0\%John Thompson

~

0\%

~

 0\%Richard DeBolt*

~

~

20 - Position 2

 57\%Ed Orcutt*

~

95\%

~

 34\%Brennan Bailey

~

~

21 - Position 1

 0\%Strom Peterson*

~

0\%

~

 0\%Amy Schaper

~

~

21 - Position 2

 0\%Lillian Ortiz-Self*

~

0\%

~

 0\%Petra Bigea

~

~

22 - Position 1

 0\%Laurie Dolan*

~

0\%

~

 0\%C Davis

~

~

22 - Position 2

 0\%Beth Doglio*

~

0\%

~

 0\%Allen Acosta

~

~

23 - Position 1

 0\%Sherry Appleton*

~

0\%

~

 0\%Becky Erickson

~

~

23 - Position 2

 0\%Drew Hansen*

Uncontested

24 - Position 1

 0\%Mike Chapman*

~

0\%

~

 0\%Jodi Wilke

~

~

24 - Position 2

 0\%Steve Tharinger*

~

0\%

~

 0\%Jim McEntire

~

~

25 - Position 1

 37\%Kelly Chambers

~

85\%

~

 28\%Jamie Smith

~

~

25 - Position 2

 47\%Chris Gildon

~

83\%

~

 45\%Brian Duthie

~

~

26 - Position 1

 49\%Connie FitzPatrick

~

84\%

~

 42\%Jesse Young*

~

~

26 - Position 2

 43\%Joy Stanford

~

84\%

~

 35\%Michelle Caldier*

~

~

27 - Position 1

 0\%Laurie Jinkins*

~

0\%

~

 0\%Kyle Paskewitz

~

~

27 - Position 2

 0\%Jake Fey*

~

0\%

~

 0\%Donald Golden

~

~

28 - Position 1

 0\%Mari Leavitt

~

0\%

~

 0\%Dick Muri*

~

~

28 - Position 2

 0\%Christine Kilduff*

~

0\%

~

 0\%Maia Espinoza

~

~

29 - Position 1

 41\%Melanie Morgan

 25\%Terry Harder

68\%

29 - Position 2

 0\%Steve Kirby*

Uncontested

30 - Position 1

 0\%Mike Pellicciotti*

~

0\%

~

 0\%Linda Kochmar

~

~

30 - Position 2

 0\%Kristine Reeves*

~

0\%

~

 0\%Mark Greene

~

~

31 - Position 1

 0\%Victoria Mena

~

0\%

~

 0\%Drew Stokesbary*

~

~

31 - Position 2

 55\%Morgan Irwin*

~

84\%

~

 40\%Mark Boswell

~

~

32 - Position 1

 72\%Cindy Ryu*

~

93\%

~

 22\%Dio Boucsieguez

~

~

32 - Position 2

 52\%Lauren Davis

 25\%Frank Deisler

93\%

33 - Position 1

 0\%Tina Orwall*

Uncontested

33 - Position 2

 0\%Mia Gregerson*

~

0\%

~

 0\%Anthony Lamb

~

~

34 - Position 1

 0\%Eileen Cody*

Uncontested

34 - Position 2

 0\%Joe Fitzgibbon*

Uncontested

35 - Position 1

 0\%James Thomas

~

0\%

~

 0\%Dan Griffey*

~

~

35 - Position 2

 0\%David Daggett

~

0\%

~

 0\%Drew MacEwen*

~

~

36 - Position 1

 0\%Noel Frame*

~

0\%

~

 0\%Sydney Wissel

~

~

36 - Position 2

 0\%Gael Tarleton*

~

0\%

~

 0\%Matt Dubin

~

~

37 - Position 1

 0\%Sharon Tomiko Santos*

Uncontested

37 - Position 2

 89\%Eric Pettigrew*

 8\%Tamra Smilanich

83\%

38 - Position 1

 0\%June Robinson*

~

0\%

~

 0\%Bert Johnson

~

~

38 - Position 2

 0\%Mike Sells*

Uncontested

39 - Position 1

 47\%Ivan Lewis

~

76\%

~

 39\%Robert Sutherland

~

~

39 - Position 2

 0\%Eric Halvorson

~

0\%

~

 0\%Carolyn Eslick*

~

~

40 - Position 1

 29\%Debra Lekanoff

 20\%Alex Ramel

86\%

40 - Position 2

 0\%Jeff Morris*

Uncontested

41 - Position 1

 64\%Tana Senn*

~

85\%

~

 34\%Tim Cruickshank

~

~

41 - Position 2

 43\%My-Linh Thai

~

85\%

~

 32\%Michael Appleby

~

~

42 - Position 1

 51\%Justin Boneau

~

98\%

~

 44\%Luanne Van Werven*

~

~

42 - Position 2

 0\%Sharon Shewmake

~

0\%

~

 0\%Vincent Buys*

~

~

43 - Position 1

 0\%Nicole Macri*

~

0\%

~

 0\%John Peeples

~

~

43 - Position 2

 87\%Frank Chopp*

~

96\%

~

 9\%Claire Torstenbo

~

~

44 - Position 1

 0\%John Lovick*

~

0\%

~

 0\%Jeff Sax

~

~

44 - Position 2

 0\%Jared Mead

~

0\%

~

 0\%Mark Harmsworth*

~

~

45 - Position 1

 0\%Roger Goodman*

~

0\%

~

 0\%Michael Curtis

~

~

45 - Position 2

 0\%Larry Springer*

~

0\%

~

 0\%Amber Krabach

~

~

46 - Position 1

 0\%Gerry Pollet*

~

0\%

~

 0\%Jeff Patton

~

~

46 - Position 2

 0\%Javier Valdez*

~

0\%

~

 0\%Jerry Zeiger-Buccola

~

~

47 - Position 1

 50\%Mark Hargrove*

~

78\%

~

 47\%Debra Entenman

~

~

47 - Position 2

 58\%Pat Sullivan*

 24\%Ted Cooke

78\%

48 - Position 1

 0\%Vandana Slatter

Uncontested

48 - Position 2

 0\%Amy Walen

~

0\%

~

 0\%Cindi Bright

~

~

49 - Position 1

 0\%Sharon Wylie*

Uncontested

49 - Position 2

 0\%Monica Stonier*

Uncontested

* Incumbent~

\protect\hyperlink{}{+ Show all races-- Show fewer races}

Source: Election results and race calls from The Associated Press.
Official statewide congressional results from the Washington State
secretary of state

By Sarah Almukhtar, Wilson Andrews, Matthew Bloch, Jeremy Bowers, Tom
Giratikanon, Jasmine C. Lee and Paul Murray.

\hypertarget{see-election-results-for-2018-2017-2016-2014-2012-2010-2008}{%
\subsubsection{\texorpdfstring{See election results for
\href{https://www.nytimes3xbfgragh.onion/interactive/2018/us/elections/calendar-primary-results.html}{2018}
\href{https://www.nytimes3xbfgragh.onion/interactive/2017/us/elections/election-calendar.html}{2017}
\href{https://www.nytimes3xbfgragh.onion/elections/results/president}{2016}
\href{https://www.nytimes3xbfgragh.onion/elections/2014/results/senate}{2014}
\href{https://www.nytimes3xbfgragh.onion/elections/2012/results/president.html}{2012}
\href{https://www.nytimes3xbfgragh.onion/elections/2010/results/senate.html}{2010}
\href{https://www.nytimes3xbfgragh.onion/elections/2008/results/president/map.html}{2008}}{See election results for 2018 2017 2016 2014 2012 2010 2008}}\label{see-election-results-for-2018-2017-2016-2014-2012-2010-2008}}

\hypertarget{more-on-nytimescom}{%
\subsubsection{More on NYTimes.com}\label{more-on-nytimescom}}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2018 The New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://www.nytco.com}{© 2018 The New York Times Company}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/infoservdirectory.html}{Contact
  Us}
\item
  \href{http://www.nytco.com/careers}{Work With Us}
\item
  \href{http://www.nytimes.whsites.net/mediakit}{Advertise}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/privacy/policy/privacy-policy.html\#pp}{Your
  Ad Choices}
\item
  \href{http://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{http://www.nytimes3xbfgragh.onion/ref/membercenter/help/agree.html}{Terms
  of Service}
\item
  \href{http://www.nytimes3xbfgragh.onion/content/help/rights/sale/terms-of-sale.html}{Terms
  of Sale}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{http://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{http://www.nytimes3xbfgragh.onion/membercenter/sitehelp.html}{Help}
\item
  \href{https://myaccount.nytimes3xbfgragh.onion/membercenter/feedback.html}{Site
  Feedback}
\item
  \href{http://www.nytimes3xbfgragh.onion/subscriptions/Multiproduct/lp5558.html?campaignId=37WXW}{Subscriptions}
\end{itemize}
