Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{How the El Paso Killer Echoed the Incendiary Words of
Conservative Media Stars}\href{}{Skip to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@NYTimes.com}{\nolinkurl{letters@NYTimes.com}}.

\hypertarget{how-the-el-paso-killer-echoed-the-incendiary-words-of-conservative-media-stars}{%
\section{How the El Paso Killer Echoed the Incendiary Words of
Conservative Media
Stars}\label{how-the-el-paso-killer-echoed-the-incendiary-words-of-conservative-media-stars}}

By \href{https://www.nytimes3xbfgragh.onion/by/jeremy-w-peters}{Jeremy
W. Peters},
\href{https://www.nytimes3xbfgragh.onion/by/michael-m-grynbaum}{Michael
M. Grynbaum},
\href{https://www.nytimes3xbfgragh.onion/by/keith-collins}{Keith
Collins}, Rich Harris and Rumsey TaylorAug. 11, 2019

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{647}
\end{itemize}

Language like ``invasion'' and the ``replacement'' of Americans has
increasingly become a regular part of Fox News broadcasts, Rush Limbaugh
shows and other prominent conservative media.

By Jeremy W. Peters, Michael M. Grynbaum, Keith Collins, Rich Harris and
Rumsey Taylor

Aug. 11, 2019

Tucker Carlson went on his prime-time Fox News show in April last year
and told his viewers not to be fooled. The thousands of Central
Americans on their way to the United States were ``border jumpers,'' not
refugees, he said. ``Will anyone in power do anything to protect America
this time,'' he asked, ``or will leaders sit passively back as the
invasion continues?''

When another group approached the border six months later, Ann Coulter,
appearing as a guest on Jeanine Pirro's Fox News show, offered a
dispassionately violent suggestion about what could be done to stem the
flow of migrants: ``You can shoot invaders.''

A few days after, Rush Limbaugh issued a grim prognosis to his millions
of radio listeners: If the immigrants from Central America weren't
stopped, the United States would lose its identity. ``The objective is
to dilute and eventually eliminate or erase what is known as the
distinct or unique American culture,'' Mr. Limbaugh said, adding: ``This
is why people call this an invasion.''

There is a striking degree of overlap between the words of right-wing
media personalities and the language used by the Texas man who confessed
to
\href{https://www.nytimes3xbfgragh.onion/2019/08/04/us/el-paso-shooting-updates.html}{killing
22 people at a Walmart in El Paso} this month. In
\href{https://www.nytimes3xbfgragh.onion/2019/08/03/us/patrick-crusius-el-paso-shooter-manifesto.html?module=inline}{a
2,300-word screed} posted on the website 8chan, the killer wrote that he
was ``simply defending my country from cultural and ethnic replacement
brought on by an invasion.''

It remains unclear what, or who, ultimately shaped the views of the
white, 21-year-old gunman, or whether he was aware of the media
commentary. But his post contains numerous references to
``\textbf{invasion}'' and cultural ``\textbf{replacement}'' --- ideas
that, until recently, were relegated to the fringes of the nationalist
right.

An extensive New York Times review of popular right-wing media platforms
found hundreds of examples of language, ideas and ideologies that
overlapped with the mass killer's written statement --- a shared
vocabulary of intolerance that stokes fears centered on immigrants of
color. The programs, on television and radio, reach an audience of
millions.

 ``We are so overwhelmed by this ---~it literally is an
\textbf{invasion} of people crossing into Texas.'' \emph{--- Laura
Ingraham on ``The O'Reilly Factor,'' May 29, 2014} ``We are letting
folks \textbf{invade} our home, walk into our home, and we won't even
defend it or protect it.'' \emph{--- Patrick Buchanan on ``Hannity,''
June 9, 2014} ``This isn't reunification. This is a
government-sanctioned \textbf{invasion} of our country.'' \emph{--- Todd
Starnes on ``Fox \& Friends Sunday,'' July 6, 2014} ``The
\textbf{invasion} of illegal immigrants, and in particular unaccompanied
children, at our southern border continues to spiral out of control.''
\emph{--- Sean Hannity on ``Hannity,'' July 12, 2014} ``When the federal
government is not able or is not willing to protect from an
\textbf{invasion}, a state has the right to reach its own agreements,
levy its own taxes and do whatever it has to, to secure its border from
further \textbf{invasion}. And this is an \textbf{invasion}. Twice as
big already than D-Day and twice as many again still coming.'' \emph{---
Louie Gohmert on ``Justice With Judge Jeanine,'' July 13, 2014} ``The
other top story is the fact that we've got this \textbf{invasion} across
our southern border of all these illegals. Many are children.''
\emph{--- Steve Doocy on ``Fox \& Friends,'' July 16, 2014} ``In the
Constitution, the founding fathers called it repelling
\textbf{invasion}.'' \emph{--- Allen West on ``On the Record With Greta
Van Susteren,'' Aug. 11, 2015} ``Trump's great accomplishment is to
expose the fact that the establishment of this country is responsible
for insecure borders, the masses coming across our borders,
\textbf{invading} our country.'' \emph{--- Patrick Buchanan on
``Hannity,'' Oct. 21, 2016} ``It's a mass of humanity right now, just
walking across the border, coming across the Rio Grande. This is a
peacetime \textbf{invasion} of the United States.'' \emph{--- Laura
Ingraham on ``Special Report With Bret Baier,'' Nov. 16, 2016} ``These
are illegal aliens who have \textbf{invaded} our country. And illegal
alien equals criminal.'' \emph{--- Mary Ann Mendoza on ``Fox \&
Friends,'' March 29, 2017} ``They used to call that an
\textbf{invasion}. And they used to fight wars over stuff like that. But
these days it's a voter registration drive for the D.N.C.'' \emph{---
Todd Starnes on ``Fox \& Friends,'' May 9, 2017} ``We're going to be
confronted by even more serious \textbf{invasion}, in terms of those
crossing the border with drugs.'' \emph{--- Jeanine Pirro on ``Fox \&
Friends,'' July 28, 2017} ``Will anyone in power do anything to protect
America this time, or will our leaders sit passively back while the
\textbf{invasion} continues?'' \emph{--- Tucker Carlson on ``Tucker
Carlson Tonight,'' April 2, 2018} ``What else would you call it? It's
gotta be --- it's an \textbf{invasion} of our country and of our rights.
It's just --- it's despicable.'' \emph{--- Art Del Cueto on ``The
Ingraham Angle,'' April 9, 2018} ``You use the word `\textbf{invasion},'
people say `oh, that's so mean.' What else do you call this?'' \emph{---
Laura Ingraham on ``The Ingraham Angle,'' April 12, 2018} ``We'll also
expose the Americans aiding and abetting a mass \textbf{invasion} of
illegal immigrants looking to exploit our laws.'' \emph{--- Laura
Ingraham on ``The Ingraham Angle,'' April 26, 2018} ``It doesn't look
like people seeking asylum, it looks more like an \textbf{invasion} of
our country. And that's sad.'' \emph{--- Art Del Cueto on ``America's
Newsroom,'' May 1, 2018} ``We're going to abolish ICE? I mean that's the
second line of defense to prevent an \textbf{invasion} of the United
States and to kick out people who are criminals and child molesters,
MS-13.'' \emph{--- Patrick Buchanan on ``Cavuto Live,'' July 7, 2018}
``I don't think we should sit back and get \textbf{invaded} by
foreigners. I don't. That doesn't make me a racist, it makes me an
American.'' \emph{--- Tucker Carlson on ``Tucker Carlson Tonight,'' Aug.
20, 2018} ``When MS-13 \textbf{invades} our country --- 10,000 members
across 40 states ---~Nancy Pelosi talks about the spark of divinity.''
\emph{--- Kayleigh McEnany on ``America's Newsroom,'' Aug. 23, 2018}
``The reality is, our southern border is on the verge of an
\textbf{invasion}.'' \emph{--- Herman Cain on ``Hannity,'' Nov. 15,
2018} ``This is not migrants coming into the country. This is nothing
short of an \textbf{invasion}.'' \emph{--- Art Del Cueto on ``America's
Newsroom,'' Nov. 16, 2018} ``You have our troops at the border and they
are meant there for a deterrence effect, to say, don't come here, don't
\textbf{invade}, you have to go to the proper channels.'' \emph{---
Morgan Ortagus on ``Hannity,'' Nov. 17, 2018} ``I.C.E. are the agents
--- they're just police officers --- who protect this nation from
\textbf{invading} illegal immigrants.'' \emph{--- Sebastian Gorka on
``Justice With Judge Jeanine,'' Nov. 17, 2018} ``You can't shoot
Americans. You can shoot \textbf{invaders}.'' \emph{--- Ann Coulter on
``Justice With Judge Jeanine,'' Nov. 25, 2018} ``This isn't going to
stop the flow of illegals who are \textbf{invading} our country.''
\emph{--- Mary Ann Mendoza on ``Fox \& Friends First,'' Feb. 1, 2019}
``There is an \textbf{invasion} going on right now.'' \emph{--- Jeff
Crouere on ``America's News HQ,'' March 10, 2019} ``What about us? What
about our country? We're being \textbf{invaded}.'' \emph{--- Tucker
Carlson on ``Tucker Carlson Tonight,'' April 9, 2019} ``We are going to
change the underlying broken laws to stop what I think is literally an
\textbf{invasion} of people from Central America.'' \emph{--- Lindsey
Graham on ``Sunday Morning Futures With Maria Bartiromo,'' May 12, 2019}
``You guys know what it's like. This is a walking \textbf{invasion}.
Where's the action?'' \emph{--- Brian Kilmeade on ``Fox \& Friends,''
June 3, 2019} ``Calling it anything but an \textbf{invasion} at this
point is just not being honest with people.'' \emph{--- Laura Ingraham
on ``The Ingraham Angle,'' July 10, 2019}

Here are three dozen instances on Fox News when immigration along the
Mexican border was discussed in terms of an \textbf{invasion}.

In November 2018 --- as Republicans, who were facing a tough midterm
election, pushed the notion of a migrant ``caravan'' --- references to
immigrants as invaders came up on more than three shows a day on
average.

``Calling it anything but an invasion at this point is just not being
honest with people,'' Laura Ingraham, host of ``The Ingraham Angle,''
said on her show on July 10.

Days after the shooting, the ``Fox \& Friends'' co-host Brian Kilmeade
dismissed a connection between words used by the gunman and by President
Trump, saying: ``If you use the term `invasion,' that's not
anti-Hispanic. It's a fact.''

In the four years since Mr. Trump electrified Republican voters with
slashing comments about Muslims and Mexicans, demonizing references to
immigrants have become more widespread in the news media, the Times
review found.

Sometimes the hosts are repeating the president's signature phrases.
Sometimes the president appears to take his cues from television
pundits. The cumulative effect is a public dialogue in which denigrating
sentiments about immigrants are common.

Before the first groups of Central American migrants received heavy news
media coverage in 2018, words like ``invaders'' or ``invasion'' were
rarely used by American outlets. In the last year, the use of such terms
has surged, with references to an immigrant ``invasion'' appearing on
more than 300 Fox News broadcasts. The vast majority of those were
spoken by Fox News hosts and guests, but some included clips of Mr.
Trump using that language at rallies and other public appearances.

The Times analysis examined the last five years of show transcripts from
Fox News, CNN and MSNBC to measure the frequency of terms like
``invasion'' and ``replacement.'' Segments that included this language
were verified by watching clips of the shows to determine whether hosts
and guests were speaking in their own words or reporting on the language
of others.

``It's a bit of a vicious cycle,'' said the conservative writer William
Kristol, a Republican critic of Mr. Trump's who has worked at Fox News
and other networks. ``Something is said on Fox News, and Trump repeats
it, and that legitimizes it --- and then someone else goes a little
further.''

He added, ``The use of what once would have been viewed as really
extreme and inappropriate and sometimes conspiratorial, sometimes
dehumanizing language is really striking.''

While the notion of immigrants as a national threat was a feature of the
conservative Patrick Buchanan's unsuccessful bids to win the Republican
presidential nominations in 1992 and 1996 (he used the phrase ``illegal
invasion'' then), they ran counter to the Republican Party's efforts to
make itself more appealing to Hispanics and other minorities in the two
decades before Mr. Trump became its front-runner.

The portrayal of immigration as a menace has returned with force, a
shift brought on not just by radio and TV hosts, but by Republican
leaders in Congress and the president himself. This year Mr. Trump has
used the terms ``invasion'' or ``invaded'' seven times on Twitter to
describe the situation at the border, at one point referring to the
approach of the migrants as ``the attempted Invasion of Illegals.'' At
rallies, he has injected terms like ``predator,'' ``killer,'' and
``animal'' in his
\href{https://www.usatoday.com/story/news/politics/elections/2019/08/08/trump-immigrants-rhetoric-criticized-el-paso-dayton-shootings/1936742001/}{descriptions
of immigrants}.

The Trump-friendly media world --- from outlets like Sinclair Broadcast
Group and The Drudge Report to platforms like Breitbart News and Gateway
Pundit --- has used similar incendiary rhetoric. ``The fact of the
matter is that this is an attempted invasion of our country ---
period,'' Boris Epshteyn, a former Trump campaign adviser,
\href{https://www.nytimes3xbfgragh.onion/2018/11/28/business/media/sinclair-broadcast-segment-trump-migrants.html}{said
last year in a commentary on migrants} that aired on nearly 200 Sinclair
television stations.

At the start of the El Paso suspect's screed, he refers to the
``\href{https://www.nytimes3xbfgragh.onion/2019/08/06/us/politics/grand-replacement-explainer.html}{great
replacement},'' a white supremacist conspiracy theory based on a French
book that claims the migration of minority groups can lead to a
``genocide'' of white culture.

The El Paso suspect, who
\href{https://www.nytimes3xbfgragh.onion/2019/08/09/us/el-paso-suspect-confession.html}{confessed}
to the mass shooting last week, claimed in the document he posted to be
defending against a ``Hispanic invasion of Texas.'' The words
``invasion'' and ``invaders'' appear six times in the text, a stark
parallel to the language heard on conservative television and talk radio
today.

Before the El Paso shootings, others with deadly or hateful motives used
the same language.

The replacement theory was prominent in a document posted on 8chan by
the suspect in
\href{https://www.nytimes3xbfgragh.onion/2019/06/13/world/australia/christchurch-shootings-not-guilty-plea.html?rref=collection\%2Fspotlightcollection\%2Fchristchurch-attack-new-zealand\&action=click\&contentCollection=world\&region=stream\&module=stream_unit\&version=latest\&contentPlacement=8\&pgtype=collection}{the
massacre that killed 51 people} in a mosque in Christchurch, New
Zealand, in March.

The man who is alleged to have killed 11 people in a Pittsburgh
synagogue last October had expressed his contempt for
``\href{https://www.nytimes3xbfgragh.onion/2018/10/27/us/active-shooter-pittsburgh-synagogue-shooting.html}{invaders}''
before he opened fire on the congregation with an AR-15-style assault
rifle, the authorities say. During the white supremacist demonstrations
in Charlottesville, Va., in 2017 that left one woman dead, marchers
shouted, ``You will not replace us.''

Lawrence Rosenthal, a professor at the Berkeley Center for Right-Wing
Studies, said that the shared vocabulary of white nationalists and many
prominent conservatives was chilling. ``Where that intersects with the
Republican Party today,'' he added, ``is the Republican argument that
the Democrats are in favor of immigration because that will give them a
permanent majority.''

Mr. Limbaugh, whose syndicated radio show has a weekly audience of 15
million, has trafficked in similar themes.

 ``So here we've got hundreds of people \textbf{flooding} our southern
border claiming refugee status. '' \emph{--- ``The Rush Limbaugh Show,''
Aug. 12, 2013} ``When you \textbf{flood} the country with millions of
people who are predestined to vote Democrat, in a vast majority sense,
who are inexperienced and low wage, what in the world is going to
happen? When you bring in that many or legalize that many and you've
given up your assimilation, the assimilation aspect of immigration?''
\emph{--- ``The Rush Limbaugh Show,'' Jan. 30, 2014} ``So now the regime
is considering a plan to stem the surge of migrants, but what instead is
actually going to happen --- and any fool should know this --- this is
going to encourage a \textbf{flood} of new illegal immigrants to try
their luck using the refugee excuse.'' \emph{--- ``The Rush Limbaugh
Show,'' July 25, 2014} ``Meanwhile, the flow of illegal immigrant
children into the U.S. is expected to rise this year. Record breaking
numbers. This is an untold story. We think it was the story of last
year, where you had all these minors from Central America
\textbf{flooding} the border, and they were.'' \emph{--- ``The Rush
Limbaugh Show,'' Feb. 24, 2016} `` If just threatening to enforce the
law has slowed the \textbf{flood} of illegal immigrants, think what
actually enforcing it will do.'' \emph{--- ``The Rush Limbaugh Show,''
April 11, 2017} ``And Trump is exactly right. They do want the country
\textbf{flooded} with illegal immigrants and refugees. '' \emph{---
``The Rush Limbaugh Show,'' Nov. 28, 2017} ``You think it's not an
immigration issue; it is. Their express purpose is to \textbf{flood} the
United States. Their express purpose is to storm the border and flood
in. '' \emph{--- ``The Rush Limbaugh Show,'' Oct. 23, 2018} ``They're
headed this way, and if the \textbf{flood} is not stopped, this is all
--- it's gonna become demographically axiomatic after a while. It has to
be stopped. It has to be stopped.'' \emph{--- ``The Rush Limbaugh
Show,'' Jan. 21, 2019} ``I think they're gonna continue to
\textbf{flood} the border no matter what Trump does because I think this
is all politics. I don't think that the root of this is people escaping
disease and poverty and what have you.'' \emph{--- ``The Rush Limbaugh
Show,'' March 6, 2019} ``There's something behind this, folks, all these
caravans amassing. This just doesn't happen organically. This is part of
a targeted political project to \textbf{flood} this country and to
paralyze the Trump administration.'' \emph{--- ``The Rush Limbaugh
Show,'' April 2, 2019} ``They want the illegal immigrants, and they want
the \textbf{flood}. They want invasion because they don't like America,
and they want to restructure America and erase all aspects of the
founding. '' \emph{--- ``The Rush Limbaugh Show,'' April 15, 2019} ``My
memory is there are three different funding organizations with U.S.
dollars and U.S. organizations that are behind the assemblage of these
caravans, including the drug cartels and human traffickers who are
attempting to participate in this swarming and \textbf{flooding} of the
border. '' \emph{--- ``The Rush Limbaugh Show,'' July 16, 2019}

Mr. Limbaugh has repeatedly described the flow of migrants across the
Mexico border as a \textbf{flood} that will overtake America with cheap
labor and dilute the country's identity.

On Wednesday, responding to the El Paso shootings, Mr. Limbaugh said,
``What is it about the word `invasion' that so bothers these people? Is
it because that's what it is? Have we ever seen anything like this?''

On Fox News, Mr. Carlson has proffered a version of this idea, albeit in
less extreme language than that of the 8chan message boards where the El
Paso killer lurked.

 ``Their political success does not depend on good policies but on
demographic \textbf{replacement}, and they'll do anything to make sure
it happens.'' \emph{--- Tucker Carlson on ``Tucker Carlson Tonight,''
Dec. 20, 2017} ``Have they ever proposed shutting the government down to
protest on behalf of American workers? Who've been harmed by immigration
policies that have \textbf{replaced} them with cheap foreign labor?''
\emph{--- Michelle Malkin on ``Fox \& Friends,'' Jan. 19, 2018} ``This
is really destroying one culture and \textbf{replacing} it with the new
foreign culture.'' \emph{--- Tucker Carlson on ``Tucker Carlson
Tonight,'' Aug. 3, 2018} ``Of this my friends you can be sure --- your
views on immigration will have zero impact and zero influence on a House
dominated by Democrats who want to \textbf{replace} you, the American
voters, with newly amnestied citizens and an ever increasing number of
chain migrants.'' \emph{--- Laura Ingraham on ``The Ingraham Angle,''
Oct. 16, 2018} ``I'm not against the immigrants. I'm just --- I'm for
Americans, and nobody cares about them. It's like, shut up, you're
dying. We're going to \textbf{replace} you.'' \emph{--- Tucker Carlson
on ``Tucker Carlson Tonight,'' Dec. 4, 2018} ``So our plan here in the
West is to just let the depressed people die off and \textbf{replace}
them with people from other countries. What do you think of that plan?''
\emph{--- Tucker Carlson on ``Tucker Carlson Tonight,'' Feb. 13, 2019}
``If the city's unemployment rate is high, it's just more proof that
they deserve \textbf{replacement} by foreign workers of some kind.''
\emph{--- Tucker Carlson on ``Tucker Carlson Tonight,'' March 4, 2019}
``We need to stop viewing struggling Americans as defective people who
deserve to be \textbf{replaced} by superior foreign immigrants --- the
Pelosi model.'' \emph{--- Tucker Carlson on ``Tucker Carlson Tonight,''
May 17, 2019}

Mr. Carlson's shows routinely feature discussions of being
\textbf{replaced} by immigrants.

Mr. Carlson, whose show averages about three million viewers a night,
has featured guests who subscribe to the replacement theory, like Peter
Szijjarto, the foreign minister to Hungary's nationalistic president,
Viktor Orban. In February, Mr. Carlson and Mr. Szijjarto discussed the
need to increase birthrates in their respective countries. Otherwise,
Mr. Carlson said, ``our plan here in the West is to just let the
depressed people die off and replace them with people from other
countries.''

Another prime-time Fox News host, Laura Ingraham, who was considered for
a communications job in the Trump administration, has used similar
language. Last October, she warned viewers that their opinions ``will
have zero impact and zero influence on a House dominated by Democrats
who want to replace you, the American voters, with newly amnestied
citizens and an ever-increasing number of chain migrants.''

Fox News had no comment.

The overlap between fringe ideology and the words of conservative talk
show hosts is not accidental, critics say. ``They're putting that into
the zeitgeist,'' said Carl Cameron, the former chief political
correspondent for Fox News, who is now working for a news aggregator
aimed at a progressive audience, Front Page Live.

``Fox goes out and looks for stuff that is inherently on fire and
foments fear and anger,'' Mr. Cameron added.

The use of ``invasion'' and ``invaders'' has also surfaced on outlets
away from right-wing media. The Times review of demonizing terms for
immigrants found a spike in such terms in 2018 on CNN and MSNBC, but
almost exclusively in the context of reporting how leading conservatives
had been using such language.

Fox News, it should be noted, is not monolithic. While its prime-time
lineup of Mr. Carlson, Sean Hannity and Ms. Ingraham is devoted to
right-wing commentary, some of the network's news reporters, like the
anchor Shepard Smith, have taken pains to refute misleading language
about migrants. Chris Wallace, the ``Fox News Sunday'' host, recently
grilled the White House chief of staff, Mick Mulvaney, about the racism
inherent in Mr. Trump's critical remarks about Baltimore.

Days after the El Paso massacre,
\href{https://www.nytimes3xbfgragh.onion/2019/08/08/business/media/tucker-carlson-white-supremacy.html}{Mr.
Carlson said on-air} that white supremacy was ``actually not a real
problem in America'' and likened it to a ``hoax.'' His words ignited
widespread criticism, including from fellow conservative commentators
like Erick Erickson and a Fox News weekend anchor,
\href{https://twitter.com/ArthelNeville/status/1159470690132619265}{Arthel
Neville}.

The next night, Mr. Carlson returned to his show and urged his critics
to ``calm down,'' warning about the roiling divisions in the country,
before announcing that he was leaving on a vacation that he and Fox News
said had been previously planned.

Source: Internet Archive's TV News Archive; Rush Limbaugh Show
transcripts from rushlimbaugh.com

Melissa Guerrero and Rebecca Chao contributed research.

Read 647 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
