Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/politics}{Politics}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/politics}{Politics}\textbar{}Jason Miller Backs Out of
White House Communications Job Under Trump

\url{https://nyti.ms/2hjyspn}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{jason-miller-backs-out-of-white-house-communications-job-under-trump}{%
\section{Jason Miller Backs Out of White House Communications Job Under
Trump}\label{jason-miller-backs-out-of-white-house-communications-job-under-trump}}

By \href{http://www.nytimes.com/by/michael-d-shear}{Michael D. Shear}

\begin{itemize}
\item
  Dec. 24, 2016
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

Jason Miller, who was named as White House communications director by
President-elect Donald J. Trump two days ago, has informed Mr. Trump
that he will not take the job, according to a statement from Mr. Miller.

In the statement, Mr. Miller said he wanted to spend more time with his
family. His wife is expecting their second child in January, he said.

``It's clear they need to be my top priority right now, and this is not
the time to start a new job as demanding as White House communications
director,'' Mr. Miller wrote.

A veteran of several Republican campaigns, Mr. Miller was an avid
supporter of Mr. Trump, appearing regularly on television on his behalf
throughout the campaign. He had been a principal spokesman during the
transition period.

In the statement, Mr. Miller said that Sean Spicer, who was recently
named press secretary, would serve as communications director, as well.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
