Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/world/asia}{Asia Pacific}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/world/asia}{Asia Pacific}\textbar{}Lightning in India
Kills More Than 70, Mostly Farmworkers

\url{https://nyti.ms/28PTHNg}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{lightning-in-india-kills-more-than-70-mostly-farmworkers}{%
\section{Lightning in India Kills More Than 70, Mostly
Farmworkers}\label{lightning-in-india-kills-more-than-70-mostly-farmworkers}}

By \href{https://www.nytimes.com/by/suhasini-raj}{Suhasini Raj}

\begin{itemize}
\item
  June 22, 2016
\item
  \begin{itemize}
  \item
  \item
  \item
  \item
  \item
  \end{itemize}
\end{itemize}

NEW DELHI --- Farmers in India have been fervently awaiting this year's
monsoon season after two consecutive years of inadequate rains. But they
were ill prepared for the lightning.

In what may be a record, lightning strikes that punctuated the season's
inaugural heavy rains killed more than 70 people in India on Tuesday and
Wednesday, disaster management officials said. Some reports in the
Indian news media put the toll at nearly 100.

Many of those fatally struck were agricultural workers and shepherds in
open areas with little or no protection. An unspecified number were
injured.

More than half the fatalities were in the northeastern state of Bihar,
but many were hit in the neighboring states of Uttar Pradesh and
Jharkhand. Locals described the strikes as some of the worst they had
ever seen.

Rakesh Kumar Singh, the leader of a farmer's collective in Bihar, said
in a telephone interview that he had been driving on Tuesday when the
sky turned pitch dark and a lightning bolt hit a nearby tree, which
erupted in flames.

``It seemed at that moment as if two meteors had collided in the sky,''
he said. ``I had to shield my eyes with my hands.''

As lightning struck repeatedly, farmers ran for their lives, he said.
Many are so poor that they live in thatched-roof huts, and Mr. Singh
said the homes that were hit had caught fire.

``There is fear among the farmers that God knows from where this
lightning will strike!'' he said. ``Nature has unleashed its fury on
thousands of them, first as drought and now as lightning.''

Twelve people --- half of them children --- were killed in Uttar
Pradesh, India's most populous state. Ten were reported killed in
Jharkhand.

Prime Minister Narendra Modi, who had been preoccupied with sweeping
economic changes
\href{http://www.nytimes.com/2016/06/21/world/asia/india-needing-jobs-eases-rules-on-foreign-investment.html}{his
government announced on Monday} and the celebrations of
\href{http://www.thehindu.com/news/national/make-yoga-a-part-of-your-life-says-pm-modi/article8754725.ece}{International
Yoga Day on Tuesday}, expressed anguish about the lightning disaster.

``My thoughts \& prayers are with those who lost their near \& dear ones
due to the lightning,'' he wrote
\href{https://twitter.com/PMOIndia/status/745530357642993664}{on his
Twitter account}. ``May the injured recover quickly.''

Lightning strikes are common during the monsoon season, which lasts from
June to October, but it is highly unusual for scores of people to be
fatally struck in such a short period. Farmworkers and farm animals are
often hit.

The National Crime Records Bureau, which classifies lightning strikes as
a cause of accidental death, reported that 2,582 people were killed in
India by lightning in 2014, the most recent year for which figures were
available.

Lightning deaths in developed nations are, by contrast, extremely rare.
In the United States, six deaths have been
\href{http://www.lightningsafety.noaa.gov/fatalities.shtml}{attributed
to lightning} so far in 2016, according to the National Weather Service.

The onset of the monsoon season has prompted tempered optimism that
India may be spared a third straight year of drought. A
\href{http://indianexpress.com/article/india/india-news-india/maharashtra-gujarat-drought-waterless-monsoon-crisis-years-may-become-more-frequent-in-india-says-study-2826500/}{recent
study} by the Indian Meteorological Department said the country might
endure more frequent drought years in the future.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
