Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/upshot}{The Upshot}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/upshot}{The Upshot}\textbar{}How Public Opinion Has Moved
on Black Lives Matter

\url{https://nyti.ms/2zkV2d1}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{race-and-america}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/george-floyd-protests-minneapolis-new-york-los-angeles?name=styln-george-floyd\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=5e073410-e3a9-11ea-87d2-81bdd276209e}{Race
and America}}{Race and America}}\label{race-and-america}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/07/03/us/george-floyd-protests-crowd-size.html?name=styln-george-floyd\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=5e073411-e3a9-11ea-87d2-81bdd276209e}{Black
  Lives Matter Movement}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/06/28/us/i-cant-breathe-police-arrest.html?name=styln-george-floyd\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=5e073412-e3a9-11ea-87d2-81bdd276209e}{History
  of `I Can't Breathe'}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/06/10/upshot/black-lives-matter-attitudes.html?name=styln-george-floyd\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=5e073413-e3a9-11ea-87d2-81bdd276209e}{How
  Public Opinion Shifted}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/07/16/us/black-lives-matter-protests-louisville-breonna-taylor.html?name=styln-george-floyd\&region=TOP_BANNER\&variant=undefined\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=5e073414-e3a9-11ea-87d2-81bdd276209e}{45
  Days in Louisville}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{How Public Opinion Has Moved on Black Lives Matter}\href{}{Skip
to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@NYTimes.com}{\nolinkurl{letters@NYTimes.com}}.

Upshot

\hypertarget{how-public-opinion-has-moved-on-black-lives-matter}{%
\section{How Public Opinion Has Moved on Black Lives
Matter}\label{how-public-opinion-has-moved-on-black-lives-matter}}

By \href{https://www.nytimes3xbfgragh.onion/by/nate-cohn}{Nate Cohn} and
\href{https://www.nytimes3xbfgragh.onion/by/kevin-quealy}{Kevin
Quealy}June 10, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{227}
\end{itemize}

\hypertarget{in-the-last-two-weeks-american-voters-support-for-the-black-lives-matter-movement-increased-almost-as-much-as-it-had-in-the-preceding-two-years}{%
\paragraph{In the last two weeks, American voters' support for the Black
Lives Matter movement increased almost as much as it had in the
preceding two
years.}\label{in-the-last-two-weeks-american-voters-support-for-the-black-lives-matter-movement-increased-almost-as-much-as-it-had-in-the-preceding-two-years}}

\paragraph{}

Net support is a measure showing the percent of respondents who
supported a policy minus the percent who said they did not support
it.·\href{https://civiqs.com/results/black_lives_matter?uncertainty=true\&annotations=true\&zoomIn=true}{Civiqs}
daily tracking poll of registered voters

American public opinion can sometimes seem stubborn. Voters
\href{https://www.nytimes3xbfgragh.onion/2015/06/30/upshot/why-gun-control-and-abortion-are-different-from-gay-marriage.html}{haven't
really changed} their views on abortion in 50 years. Donald J. Trump's
\href{https://projects.fivethirtyeight.com/trump-approval-ratings/}{approval
rating} among registered voters has fallen within a five-point range for
just about every day of his presidency.

But the Black Lives Matter movement has been an exception from the
start.

Public opinion on race and criminal justice issues has been steadily
moving left since the first protests ignited over the fatal shootings of
Trayvon Martin and Michael Brown. And since the death of George Floyd in
police custody on May 25, public opinion on race, criminal justice and
the Black Lives Matter movement has leaped leftward.

Over the last two weeks, support for Black Lives Matter increased by
nearly as much as it had over the previous two years, according to data
from \href{https://civiqs.com/}{Civiqs}, an online survey research firm.
By a 28-point margin, Civiqs finds that a majority of American voters
support the movement, up from a 17-point margin before the most recent
wave of protests began.

\hypertarget{how-voters-views-on-black-lives-matter-have-changed-in-the-last-two-weeks}{%
\paragraph{How voters' views on Black Lives Matter have changed in the
last two
weeks}\label{how-voters-views-on-black-lives-matter-have-changed-in-the-last-two-weeks}}

\hypertarget{though-they-started-from-different-places-all-kinds-of-voters-moved-sharply-in-the-direction-of-supporting-the-movement}{%
\paragraph{Though they started from different places, all kinds of
voters moved sharply in the direction of supporting the
movement.}\label{though-they-started-from-different-places-all-kinds-of-voters-moved-sharply-in-the-direction-of-supporting-the-movement}}

Net support, two weeks ago vs. now

Change equivalent to previous \ldots{}

All registered voters

+28

21 months

By party

Age

Education

Race

Source: Civiqs

The survey is not the only one to suggest that recent protests enjoy
broad public support. Weekly polling for the Democracy Fund's
\href{https://www.voterstudygroup.org/nationscape}{U.C.L.A./Nationscape}
survey shows a significant increase in unfavorable views of the police,
and an increase in the belief that African-Americans face a lot of
discrimination.

Perhaps most significant, the Civiqs data is not alone in suggesting
that an outright majority of Americans agree with the central arguments
of Black Lives Matter.

A Monmouth University
\href{https://www.monmouth.edu/polling-institute/reports/monmouthpoll_us_060220/}{poll}
found that 76 percent of Americans consider racism and discrimination a
``big problem,'' up 26 points from 2015. The poll found that 57 percent
of voters thought the anger behind the demonstrations was fully
justified, while a further 21 percent called it somewhat justified.
Polls show that a majority of Americans believe that the police are more
likely to use deadly force against African-Americans, and that there's a
lot of discrimination against black Americans in society. Back in 2013,
when Black Lives Matter began, a majority of voters disagreed with all
of these statements.

Will the recent shift in opinion last? News events can sometimes cause a
shift in public opinion that quickly dissipates. After mass shootings,
for instance, big spikes in support for gun control typically ebb as
soon as memories of the bloodshed fade.

\hypertarget{how-voters-views-on-other-issues-have-changed-in-the-last-two-years}{%
\paragraph{How voters' views on other issues have changed in the last
two
years}\label{how-voters-views-on-other-issues-have-changed-in-the-last-two-years}}

\hypertarget{large-swings-in-public-opinion-in-short-periods-are-not-typical-two-week-periods-with-the-biggest-shifts-in-movement-are-highlighted}{%
\paragraph{Large swings in public opinion in short periods are not
typical. Two-week periods with the biggest shifts in movement are
highlighted.}\label{large-swings-in-public-opinion-in-short-periods-are-not-typical-two-week-periods-with-the-biggest-shifts-in-movement-are-highlighted}}

Some groups have always had close to universal support for Black Lives
Matter.·Source: Civiqs

But there are reasons to think that the Black Lives Matter movement
might be different. For one, the shift continues a long-term trend in
public opinion that preceded the death of Mr. Floyd. By the time of the
2016 election, many white liberal Democrats held some views on race that
were to the left of African-Americans over all, in what some branded the
``\href{https://www.vox.com/2019/3/22/18259865/great-awokening-white-liberals-race-polling-trump-2020}{Great
Awokening}.''

Perhaps surprisingly, the election of Mr. Trump may have helped move
public opinion even more. There's a longstanding tendency for voters to
drift toward the views of the party out of power on various issues,
sometimes called
\href{https://pages.uncc.edu/mary-atkinson/wp-content/uploads/sites/619/2014/02/BeyondThermostat.pdf}{thermostatic
public opinion}.

And whether on gay marriage or civil rights, American public opinion
tends to drift toward the side advocating equal treatment. Public
opinion doesn't have nearly as clear a record of drifting toward the
left on issues that don't hinge on equal treatment under the law, like
gun control and abortion.

With a majority of Americans backing the protests, it's also possible
that steps by political actors could move opinion further. The support
of Republican elected officials, like Senator Mitt Romney, could give
permission for some potentially sympathetic Republican voters to
re-evaluate their views on the issue. In general, public consensus
becomes likelier when the two parties reach a consensus.

Of course, it's also possible that events could move public opinion the
other way. The tactics of some protesters could be a factor. Kneeling
during the national anthem may be less effective at appealing to
persuadable Americans than the recent peaceful protests, for instance. A
sense that protests were getting out of control, with looting and
violence, could also harm the public image of the movement. And it is
possible that the movement will face fresh obstacles as it transitions
from a critique of the status quo to proposing new policies. Some of the
policies under discussion, like
\href{https://www.nytimes3xbfgragh.onion/2020/06/08/us/what-does-defund-police-mean.html}{defunding
the police}, may hold more limited support than police reforms.

There's no way to know what will happen next. After all, no one just a
few years ago would have predicted that a majority of Americans would
say they have a favorable view of Black Lives Matter.

Read 227 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
