Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/us}{U.S.}\textbar{}See Which States and Cities Have Told
Residents to Stay at Home

\url{https://nyti.ms/2y5j9LN}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{the-coronavirus-outbreak}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/news-event/coronavirus?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=dadc2200-f2ba-11ea-841f-fb518d5e9681\&variant=undefined}{The
Coronavirus
Outbreak}}{The Coronavirus Outbreak}}\label{the-coronavirus-outbreak}}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes3xbfgragh.onion/2020/09/09/world/covid-19-coronavirus.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=dadc2201-f2ba-11ea-841f-fb518d5e9681\&variant=undefined}{Latest
  Updates}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/coronavirus-us-cases.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=dadc2202-f2ba-11ea-841f-fb518d5e9681\&variant=undefined}{Maps
  and Cases}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/science/coronavirus-vaccine-tracker.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=dadc4910-f2ba-11ea-841f-fb518d5e9681\&variant=undefined}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/02/your-money/eviction-moratorium-covid.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=dadc4911-f2ba-11ea-841f-fb518d5e9681\&variant=undefined}{Eviction
  Moratorium}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/09/upshot/coronavirus-surprise-test-fees.html?name=styln-coronavirus-national\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=dadc4912-f2ba-11ea-841f-fb518d5e9681\&variant=undefined}{Surprise
  Test Fees}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{See Which States and Cities Have Told Residents to Stay at
Home}\href{}{Skip to Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@NYTimes.com}{\nolinkurl{letters@NYTimes.com}}.

\hypertarget{see-which-states-and-cities-have-told-residents-to-stay-at-home}{%
\section{See Which States and Cities Have Told Residents to Stay at
Home}\label{see-which-states-and-cities-have-told-residents-to-stay-at-home}}

By \href{https://www.nytimes3xbfgragh.onion/by/sarah-mervosh}{Sarah
Mervosh}, \href{https://www.nytimes3xbfgragh.onion/by/denise-lu}{Denise
Lu} and
\href{https://www.nytimes3xbfgragh.onion/by/vanessa-swales}{Vanessa
Swales}Updated April 20, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{221}
\end{itemize}

This page is no longer being updated. Visit
\href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/states-reopen-map-coronavirus.html}{this
page} to see the latest.

 Statewide order Order in parts of state

Click a state to see more detail

In a desperate race to stunt the spread of the coronavirus, millions of
Americans have been asked to do what would have been unthinkable only a
few months ago: Don't go to work, don't go to school, don't leave the
house at all, unless you have to.

The directives to keep people at home, which
\href{https://www.nytimes3xbfgragh.onion/2020/03/20/us/coronavirus-california-stay-at-home-order.html}{began
in California} in mid-March, quickly swept the nation. Today, residents
in a vast majority of states,
\href{https://navajotimes.com/reznews/covid-cases-now-at-29-people-not-heeding-stay-at-home-warning/}{the
Navajo Nation} and many cities and counties are under instructions to
stay at home as much as possible, in an act of solidarity that public
health experts say is crucial to controlling the virus.

This means at least 316 million people in at least 42 states, three
counties, 10 cities, the District of Columbia and Puerto Rico are being
urged to stay home.

See how the directives spread across the country:

Source: Times research, local governments and news reports.

The orders --- or lack thereof --- have divided the American public. In
a handful of more rural states --- Arkansas, Iowa, Nebraska, North
Dakota and South Dakota --- governors held off on imposing stay-at-home
orders, favoring other restrictions
\href{https://www.nytimes3xbfgragh.onion/2020/04/03/us/coronavirus-states-without-stay-home.html}{amid
intense pressure to take stricter action}. A few other states have
partial orders in place, issued locally by cities or counties.

In other states, the orders to stay at home have lasted for weeks,
drawing political ire and intensifying concerns about the economy. Some
conservative demonstrators have even taken to statehouses and city
streets,
\href{https://www.nytimes3xbfgragh.onion/2020/04/16/us/coronavirus-rules-protests.html}{in
defiance of the stay-at-home orders they are protesting}.

Still, the number of Americans under instructions to stay at home has
persisted at an astonishing level this spring, accounting for a stunning
95 percent of the population.

Here is a guide to how the orders affect each state in the list below.

Choose a state Alabama Alaska Arizona California Colorado Connecticut
Delaware District of Columbia Florida Georgia Hawaii Idaho Illinois
Indiana Kansas Kentucky Louisiana Maine Maryland Massachusetts Michigan
Minnesota Mississippi Missouri Montana Nevada New Hampshire New Jersey
New Mexico New York North Carolina Ohio Oklahoma Oregon Pennsylvania
Puerto Rico Rhode Island South Carolina Tennessee Texas Utah Vermont
Virginia Washington West Virginia Wisconsin Wyoming

\hypertarget{alabama-about-49-million-people}{%
\subsubsection{Alabama About 4.9 million
people}\label{alabama-about-49-million-people}}

Gov. Kay Ivey had resisted a statewide order, saying that she wanted to
balance the health of the state's residents with the health of the
economy. "We are not California," she said on a conference call with
reporters, according to AL.com. But after Birmingham, the largest city
in the state, issued a shelter-in-place order for its residents, and
amid growing pressure, the governor issued a statewide order. ``You need
to understand we are past urging people to stay at home," she said. "It
is now the law.''

Stay at home, effective April 4 at 5 p.m.

\href{https://www.al.com/news/2020/04/gov-kay-ivey-to-give-update-on-coronavirus-response.html}{Read
local coverage}

\hypertarget{alaska-about-737000-people}{%
\subsubsection{Alaska About 737,000
people}\label{alaska-about-737000-people}}

"We crossed a line today," Gov. Mike Dunleavy said, issuing instructions
for people to stay home or remain six feet or more from one another when
outside. The mayor of Anchorage had previously asked residents to
"hunker down."

Stay at home, effective March 28 at 5 p.m.

\href{http://dhss.alaska.gov/News/Documents/press/2020/FAQs_03272020-SOA-COVID-19-Health-Mandate-011-012.pdf}{See
announcement} \textbar{}
\href{https://www.adn.com/alaska-news/2020/03/27/anchorage-sees-first-covid-19-death-in-alaska-hospital-officials-say/}{Read
local coverage}

\hypertarget{arizona-about-72-million-people}{%
\subsubsection{Arizona About 7.2 million
people}\label{arizona-about-72-million-people}}

Gov. Doug Ducey said he issued the order at the recommendation of health
officials. "I'm grateful to everyone making adjustments to fight this
virus and protect others," he said. "We need to keep these efforts up."

Stay at home, effective March 31 at 5 p.m.

\href{https://azgovernor.gov/governor/news/2020/03/new-executive-order-stay-home-stay-healthy-stay-connected}{See
announcement} \textbar{}
\href{https://www.azcentral.com/story/news/local/arizona-health/2020/03/30/arizona-coronavirus-stay-home-order-issued-gov-doug-ducey/5088109002/}{Read
local coverage}

\hypertarget{california-about-396-million-people}{%
\subsubsection{California About 39.6 million
people}\label{california-about-396-million-people}}

California, America's most populous state, was the first to order all
residents to stay home. Others quickly followed suit. ``This is not a
permanent state, this is a moment in time,'' Gov. Gavin Newsom said.
``We will look back at these decisions as pivotal.''

Stay at home, effective March 19

\href{https://covid19.ca.gov/img/Executive-Order-N-33-20.pdf}{See
announcement} \textbar{}
\href{https://www.latimes.com/california/story/2020-03-20/coronavirus-and-california-landmarks-empty-and-surreal}{Read
local coverage}

\hypertarget{colorado-about-57-million-people}{%
\subsubsection{Colorado About 5.7 million
people}\label{colorado-about-57-million-people}}

A number of counties and cities in the state, including Denver and
Boulder, had issued their own stay-at-home orders, but Gov. Jared Polis
also issued a statewide order, reiterating the need for everyone to stay
at home. ``We owe it to ourselves and our fellow Americans in order to
save lives,'' he said.

Stay at home, effective March 26 at 6 a.m.

\href{https://twitter.com/GovofCO/status/1242943191394877441?s=20}{See
announcement} \textbar{}
\href{https://gazette.com/news/colorado-stay-at-home-order-issued-by-gov-polis-wednesday/article_7b3e0834-6ed7-11ea-84db-678f7b49011f.html}{Read
local coverage}

\hypertarget{connecticut-about-36-million-people}{%
\subsubsection{Connecticut About 3.6 million
people}\label{connecticut-about-36-million-people}}

``At this critical time it is essential that everyone just stay home,''
Gov. Ned Lamont said.

Stay at home, effective March 23 at 8 p.m.

\href{https://portal.ct.gov/Office-of-the-Governor/News/Press-Releases/2020/03-2020/Governor-Lamont-Signs-Executive-Order-Asking-Connecticut-Businesses-and-Residents-Stay-Safe}{See
announcement} \textbar{}
\href{https://www.courant.com/coronavirus/hc-news-coronavirus-update-0320-20200320-m5oro7ss3vb3nlqsormcmt6nty-story.html}{Read
local coverage}

\hypertarget{delaware-about-973000-people}{%
\subsubsection{Delaware About 973,000
people}\label{delaware-about-973000-people}}

``I don't want Delaware to be the example of what not to do in response
to this crisis,'' Gov. John Carney said.

Shelter in place, effective March 24 at 8 a.m.

\href{https://governor.delaware.gov/wp-content/uploads/sites/24/2020/03/Fifth-Modification-to-State-of-Emergency-03222020.pdf}{See
announcement} \textbar{}
\href{https://www.delawareonline.com/story/news/coronavirus-in-delaware/2020/03/22/coronavirus-delaware-count-up-47-confirmed-cases-state/2894015001/}{Read
local coverage}

\hypertarget{district-of-columbia-about-702000-people}{%
\subsubsection{District of Columbia About 702,000
people}\label{district-of-columbia-about-702000-people}}

Mayor Muriel E. Bowser issued a stay-at-home order for all residents,
joining the nearby states of Maryland and Virginia in a move that
virtually shut down the nation's capital region. "Many people want to
know how they can help right now," the mayor said. "For most people this
is how --- by staying home."

Stay at home, effective April 1 at 12:01 a.m.

\href{https://coronavirus.dc.gov/stayhome}{See announcement} \textbar{}
\href{https://www.washingtonpost.com/dc-md-va/2020/03/30/coronavirus-dc-maryland-virginia-live-updates/}{Read
local coverage}

\hypertarget{florida-about-215-million-people}{%
\subsubsection{Florida About 21.5 million
people}\label{florida-about-215-million-people}}

Gov. Ron DeSantis, who for weeks resisted more stringent statewide
measures even as cities and counties took action, announced that he
would order the state's more than 21 million residents to largely stay
at home. The governor said he started coming around to the necessity of
a statewide order once the White House extended national guidelines to
combat the coronavirus until April 30. ``To me, that was, 'People aren't
just going to back to work,''' Mr. DeSantis said at a news conference in
Tallahassee, the state capital. ``That's a national pause button.''

Stay at home, effective April 3 at 12:01 a.m.

\href{https://www.tampabay.com/news/health/2020/04/01/florida-gov-ron-desantis-issues-statewide-stay-at-home-order/}{Read
local coverage}

\hypertarget{georgia-about-106-million-people}{%
\subsubsection{Georgia About 10.6 million
people}\label{georgia-about-106-million-people}}

Gov. Brian Kemp announced that he would issue a statewide order for all
residents to shelter in place, following a similar stay-at-home order in
Atlanta and other areas. He said he made the decision, in part, after
learning that many people without symptoms are transmitting the virus.
"At this point," he said, "I think it's the right thing to do."

Shelter in place, effective April 3

\href{https://www.ajc.com/blog/politics/breaking-georgia-governor-orders-shelter-place-curb-coronavirus/vdAoWkjq39W2usr9e8W8BL/}{Read
local coverage}

\hypertarget{hawaii-about-14-million-people}{%
\subsubsection{Hawaii About 1.4 million
people}\label{hawaii-about-14-million-people}}

As in other states, there are exceptions to the stay-at-home order in
Hawaii, including leaving the house to go surfing and swimming. But the
governor's office said violations could be punishable by a fine of up to
\$5,000, or as much as one year in jail. ``The threat of COVID-19 is
unprecedented and requires aggressive action," Gov. David Ige said.

Stay at home, effective March 25 at 12:01 a.m.

\href{https://governor.hawaii.gov/wp-content/uploads/2020/03/2003162-ATG_Third-Supplementary-Proclamation-for-COVID-19-signed.pdf}{See
announcement} \textbar{}
\href{https://www.hawaiinewsnow.com/2020/03/24/live-governor-expected-issue-statewide-stay-at-home-order-coronavirus-cases-swell/}{Read
local coverage}

\hypertarget{idaho-about-18-million-people}{%
\subsubsection{Idaho About 1.8 million
people}\label{idaho-about-18-million-people}}

``Our health care and public safety workers are putting themselves in
harm's way to respond to the coronavirus emergency, and we owe it to
them to do our part by following this statewide stay-home order,'' Gov.
Brad Little said.

Stay at home, effective March 25 at 1:30 p.m.

\href{https://coronavirus.idaho.gov/statewide-stay-home-order/}{See
announcement} \textbar{}
\href{https://amp.idahostatesman.com/news/coronavirus/article241495446.html}{Read
local coverage}

\hypertarget{illinois-about-127-million-people}{%
\subsubsection{Illinois About 12.7 million
people}\label{illinois-about-127-million-people}}

``I don't come to this decision easily,'' Gov. J.B. Pritzker said. ``I
fully recognize that, in some cases, I am choosing between people's
lives and saving people's livelihood. But ultimately, you can't have a
livelihood if you don't have your life.''

Stay at home, effective March 21 at 5 p.m.

\href{https://www2.illinois.gov/Pages/news-item.aspx?ReleaseID=21288}{See
announcement} \textbar{}
\href{https://www.chicagotribune.com/coronavirus/ct-coronavirus-illinois-shelter-in-place-lockdown-order-20200320-teedakbfw5gvdgmnaxlel54hau-story.html}{Read
local coverage}

\hypertarget{indiana-about-67-million-people}{%
\subsubsection{Indiana About 6.7 million
people}\label{indiana-about-67-million-people}}

Gov. Eric J. Holcomb asked "Hoosiers to hunker down." He added: ``You
must be part of the solution, not the problem.''

Stay at home, effective March 24 at 11:59 p.m.

\href{https://www.in.gov/gov/3232.htm}{See announcement} \textbar{}
\href{https://www.indystar.com/story/news/health/2020/03/23/indiana-coronavirus-updates-indianapolis-covid-19-latest-news/2896967001/}{Read
local coverage}

\hypertarget{kansas-about-29-million-people}{%
\subsubsection{Kansas About 2.9 million
people}\label{kansas-about-29-million-people}}

After several municipalities in Kansas issued stay-at-home instructions
in quick succession, including in the greater Kansas City region, Gov.
Laura Kelly issued a statewide order. "While I left these decisions to
local health departments as long as possible," she said, "the reality is
that the patchwork approach that has developed is inconsistent and is a
recipe for chaos."

Stay at home, effective March 30 at 12:01 a.m.

\href{https://governor.kansas.gov/governor-kelly-issues-temporary-statewide-stay-home-order-in-ongoing-effort-to-combat-covid-19/}{See
announcement} \textbar{}
\href{https://www.cjonline.com/news/20200328/kansas-coronavirus-update-gov-laura-kelly-imposes-statewide-stay-at-home-order-state-logs-5th-death-261-cases}{Read
local coverage}

\hypertarget{kentucky-about-45-million-people}{%
\subsubsection{Kentucky About 4.5 million
people}\label{kentucky-about-45-million-people}}

Gov. Andy Beshear ordered all non-essential businesses to stop operating
in-person services by March 26 and urged residents to stay "healthy at
home." In a news conference on March 27, he clarified that the state's
campaign amounted to telling residents to stay home. "That doesn't mean
you need to cower down in your home," he said. But "you stay at home,
unless you are getting groceries or other supplies that you may need."~

Healthy at home, effective March 26 at 8 p.m.

\href{https://kentucky.gov/Pages/Activity-stream.aspx?n=GovernorBeshear\&prId=105}{See
announcement} \textbar{}
\href{https://www.courier-journal.com/story/news/local/2020/03/23/coronavirus-kentucky-healthy-at-home-shelter-in-place-andy-beshear/2899060001/}{Read
local coverage}

\hypertarget{louisiana-about-46-million-people}{%
\subsubsection{Louisiana About 4.6 million
people}\label{louisiana-about-46-million-people}}

``If we want to flatten the curve, we have to take action today,'' Gov.
John Bel Edwards said. New Orleans had previously issued its own order.

Stay at home, effective March 23 at 5 p.m.

\href{https://gov.louisiana.gov/assets/Proclamations/2020/JBE-33-2020.pdf}{See
announcement} \textbar{}
\href{https://www.theadvocate.com/baton_rouge/news/coronavirus/article_922869e8-6c6d-11ea-aeee-6b6fd5e8f4bd.html}{Read
local coverage}

\hypertarget{maine-about-13-million-people}{%
\subsubsection{Maine About 1.3 million
people}\label{maine-about-13-million-people}}

``We are in the midst of one of the greatest public health crises this
world has seen in more than a century," Gov. Janet Mills said. "This
virus will continue to sicken people across our state; our cases will
only grow, and more people will die. I say this to be direct, to be as
honest with you as I can. Because saving lives will depend on us.''

Stay at home, effective April 2 at 12:01 a.m.

\href{https://www.maine.gov/governor/mills/sites/maine.gov.governor.mills/files/inline-files/An\%20Order\%20Regarding\%20Further\%20Restrictions\%20on\%20Public\%20Contact\%20and\%20Movement\%2C\%20Schools\%2C\%20Vehicle\%20Travel\%20and\%20Retail\%20Business\%20Operations.pdf}{See
announcement} \textbar{}
\href{https://www.wabi.tv/content/news/Gov-Mills-issues-stay-at-home-order-for-Maine-569260011.html}{Read
local coverage}

\hypertarget{maryland-about-6-million-people}{%
\subsubsection{Maryland About 6 million
people}\label{maryland-about-6-million-people}}

Citing a drastic uptick in cases and deaths in Maryland and the United
States, Gov. Larry Hogan issued a statewide stay-at-home order. "We are
no longer asking or suggesting that Marylanders stay home," he said. "We
are directing them to do so."

Stay at home, effective March 30 at 8 p.m.

\href{https://governor.maryland.gov/2020/03/30/as-covid-19-crisis-escalates-in-capital-region-governor-hogan-issues-stay-at-home-order-effective-tonight/}{See
announcement} \textbar{}
\href{https://www.baltimoresun.com/coronavirus/bs-md-stay-at-home-hogan-covid-19-20200330-pmid22rvirdwbppx4xpgjadoim-story.html}{Read
local coverage}

\hypertarget{massachusetts-about-69-million-people}{%
\subsubsection{Massachusetts About 6.9 million
people}\label{massachusetts-about-69-million-people}}

Gov. Charlie Baker stopped short of declaring a formal order, but
announced an advisory for residents to stay home. ``I do not believe I
can or should order U.S. citizens to be confined to their home for days
on end,'' he said. ``It doesn't make sense from a public health point of
view, and it's not realistic.''

Stay at home advisory, effective March 24 at 12 p.m.

\href{https://www.mass.gov/news/governor-charlie-baker-orders-all-non-essential-businesses-to-cease-in-person-operation}{See
announcement} \textbar{}
\href{https://www.bostonglobe.com/2020/03/23/metro/list-what-can-stay-open-during-bakers-stay-at-home-advisory/}{Read
local coverage}

\hypertarget{michigan-about-10-million-people}{%
\subsubsection{Michigan About 10 million
people}\label{michigan-about-10-million-people}}

``Without a comprehensive national strategy, we, the states, must take
action,'' Gov. Gretchen Whitmer said, urging residents to stay home.

Stay at home, effective March 24 at 12:01 a.m.

\href{https://www.michigan.gov/whitmer/0,9309,7-387-90499_90705-522626--,00.html}{See
announcement} \textbar{}
\href{https://www.freep.com/story/news/local/michigan/2020/03/23/michigan-shelter-in-place-order-coronavirus/2887578001/}{Read
local coverage}

\hypertarget{minnesota-about-56-million-people}{%
\subsubsection{Minnesota About 5.6 million
people}\label{minnesota-about-56-million-people}}

Gov. Tim Walz emphasized the need to slow the spread of the virus over
time and not overwhelm hospitals in Minnesota. "We are asking you ---
because it is going to take cooperation and collaboration --- stay
home," he said.

Stay at home, effective March 27 at 11:59 p.m.

\href{https://mn.gov/governor/covid-19/}{See announcement} \textbar{}
\href{https://www.startribune.com/gov-tim-walz-to-order-new-covid-19-restrictions-on-minnesotans/569095212/}{Read
local coverage}

\hypertarget{mississippi-about-3-million-people}{%
\subsubsection{Mississippi About 3 million
people}\label{mississippi-about-3-million-people}}

Gov. Tate Reeves announced a shelter-in-place order and asked all
residents to take enforcement seriously. "If you will self-enforce this,
it will go a long way to slowing the spread," he said.

Shelter in place, effective April 3 at 5 p.m.

\href{https://yallpolitics.com/2020/04/01/mississippi-governor-tate-reeves-orders-statewide-shelter-at-home/unnamed-13-2/}{See
announcement} \textbar{}
\href{https://yallpolitics.com/2020/04/01/mississippi-governor-tate-reeves-orders-statewide-shelter-in-place/}{Read
local coverage}

\hypertarget{missouri-about-61-million-people}{%
\subsubsection{Missouri About 6.1 million
people}\label{missouri-about-61-million-people}}

Residents in the Kansas City, St. Louis and St. Louis County areas were
among those under instructions to stay at home before Gov. Mike Parson
issued a statewide order. The governor had previously rejected the step,
but issued the order to "stay ahead of the battle."

Stay at home, effective April 6 at 12:01 a.m.

\href{https://twitter.com/GovParsonMO/status/1246196795107160064?s=20}{See
announcement} \textbar{}
\href{https://www.kansascity.com/news/politics-government/article241743921.html}{Read
local coverage}

\hypertarget{montana-about-11-million-people}{%
\subsubsection{Montana About 1.1 million
people}\label{montana-about-11-million-people}}

"We cannot rebuild our economic strength without doing everything we can
now to flatten the curve and slow the spread of this virus," Gov. Steve
Bullock said.

Stay at home, effective March 28 at 12:01 a.m.

\href{https://covid19.mt.gov/Portals/223/Documents/Stay\%20at\%20Home\%20Directive.pdf?ver=2020-03-26-173332-177}{See
announcement} \textbar{}
\href{https://helenair.com/news/state-and-regional/govt-and-politics/montana-sees-first-covid--death-residents-ordered-to-stay/article_f92d251e-cfe6-5e99-ab9f-0aa9dd433b91.html}{Read
local coverage}

\hypertarget{nevada-about-31-million-people}{%
\subsubsection{Nevada About 3.1 million
people}\label{nevada-about-31-million-people}}

Gov. Steve Sisolak had shut down all nonessential businesses and
encouraged residents to stay home for weeks before issuing a formal
order, codifying a message he had been trying to send for weeks: "STAY
HOME for our State," he said on Twitter.

Stay at home, effective April 1

\href{https://nvhealthresponse.nv.gov/wp-content/uploads/2020/04/Declaration-of-Emergency-Directive-010-Stay-at-Home-3-31-20.pdf}{See
announcement} \textbar{}
\href{https://www.reviewjournal.com/news/politics-and-government/nevada/sisolak-issues-stay-at-home-order-1996415/}{Read
local coverage}

\hypertarget{new-hampshire-about-14-million-people}{%
\subsubsection{New Hampshire About 1.4 million
people}\label{new-hampshire-about-14-million-people}}

Gov. Chris Sununu had earlier described a stay-at-home order as not a
"practical ask" of residents, but later put one in place. "We can't
stress this enough --- you should stay at your house unless absolutely
necessary," he said.

Stay at home, effective March 27 at 11:59 p.m.

\href{https://www.governor.nh.gov/news-media/emergency-orders/documents/emergency-order-17-1.pdf}{See
announcement} \textbar{}
\href{https://www.concordmonitor.com/Thursday-update-NH-covid-cases-disease-spread-33554702}{Read
local coverage}

\hypertarget{new-jersey-about-89-million-people}{%
\subsubsection{New Jersey About 8.9 million
people}\label{new-jersey-about-89-million-people}}

``We know the virus spreads through person-to-person contact, and the
best way to prevent further exposure is to limit our public
interactions,'' Gov. Phil Murphy said.

Stay at home, effective March 21 at 9 p.m.

\href{https://nj.gov/infobank/eo/056murphy/pdf/EO-107.pdf}{See
announcement} \textbar{}
\href{https://www.nj.com/coronavirus/2020/03/new-jersey-lockdown-rules-what-residents-need-to-know-about-stay-at-home-order.html}{Read
local coverage}

\hypertarget{new-mexico-about-21-million-people}{%
\subsubsection{New Mexico About 2.1 million
people}\label{new-mexico-about-21-million-people}}

Addressing questions about whether she was issuing a shelter-in-place
order, Gov. Michelle Lujan Grisham said that ``the tantamount effect of
what we're doing is basically the same.'' She added: ``This is quite
frankly an instruction to stay home.''

Stay at home, effective March 24 at 8 a.m.

\href{https://www.governor.state.nm.us/wp-content/uploads/2020/03/COVID-19-DOH-Order-fv.pdf}{See
announcement} \textbar{}
\href{https://www.abqjournal.com/1435599/lujan-grisham-to-announce-stay-at-home-instruction.html}{Read
local coverage}

\hypertarget{new-york-about-195-million-people}{%
\subsubsection{New York About 19.5 million
people}\label{new-york-about-195-million-people}}

Gov. Andrew M. Cuomo has shied away from the language of a
shelter-in-place order, which he said evoked images of shooter
situations or nuclear war. ``Words matter,'' the governor said, instead
describing it as putting all of New York on pause. ``This is the most
drastic action we can take,'' he said.

Stay at home, effective March 22 at 8 p.m.

\href{https://coronavirus.health.ny.gov/new-york-state-pause}{See
announcement} \textbar{}
\href{https://www.nytimes3xbfgragh.onion/article/what-is-shelter-in-place-coronavirus.html}{Read
local coverage}

\hypertarget{north-carolina-about-104-million-people}{%
\subsubsection{North Carolina About 10.4 million
people}\label{north-carolina-about-104-million-people}}

A number of cities and counties in North Carolina had already ordered
their residents to stay home, but Gov. Roy Cooper made it official
statewide. "Even if you don't think you have to worry about yourself,
consider our nurses, doctors, custodial staff \& other hospital workers
who will be stretched beyond their capacity if we are unable to slow the
spread of this disease," he said on Twitter.

Stay at home, effective March 30 at 5 p.m.

\href{https://twitter.com/NC_Governor/status/1243629131646078976?s=20}{See
announcement} \textbar{}
\href{https://www.newsobserver.com/news/coronavirus/article241469211.html}{Read
local coverage}

\hypertarget{ohio-about-117-million-people}{%
\subsubsection{Ohio About 11.7 million
people}\label{ohio-about-117-million-people}}

Gov. Mike DeWine has been notably aggressive in his response to the
coronavirus, and Ohio was among the first wave of states to adopt this
measure. ``We haven't faced an enemy like we are facing today in 102
years,'' he said. ``We are at war.''

Stay at home, effective March 23 at 11:59 pm.

\href{https://content.govdelivery.com/attachments/OHOOD/2020/03/22/file_attachments/1407840/Stay\%20Home\%20Order.pdf}{See
announcement} \textbar{}
\href{https://www.dispatch.com/news/20200322/coronavirus-ohio-issues-stay-at-home-order-allows-only-essential-businesses-and-day-cares-at-6-children-per-room}{Read
local coverage}

\hypertarget{oklahoma}{%
\subsubsection{Oklahoma}\label{oklahoma}}

Gov. Kevin Stitt has told older and vulnerable people across Oklahoma to
stay home, but mayors in the state's major cities, including Oklahoma
City, Tulsa and Norman, ordered all residents to do so. "We want to
leave no doubt," Mayor David Holt of Oklahoma City said. "The safest
course of action during this public health crisis is to stay home."

Ardmore About 25,000 people

Shelter in place, effective April 6 at 11:59 p.m.

\href{https://www.ardmorecity.org/DocumentCenter/View/2193/emergency-resolution?bidId=}{See
announcement} \textbar{}
\href{http://www.kten.com/story/41982515/ardmore-residents-ordered-to-shelter-in-place}{Read
local coverage}

Claremore About 19,000 people

Stay at home, effective April 6 at 8 a.m.

\href{https://www.claremorecity.com/DocumentCenter/View/4999/Emergency-Management-Order-3}{See
announcement} \textbar{}
\href{https://ktul.com/news/local/claremore-issues-stay-at-home-order}{Read
local coverage}

Edmond About 93,000 people

Shelter in place, effective March 30 at 11:59 p.m.

\href{http://edmondok.com/1568/COVID-19-Coronavirus-Information}{See
announcement} \textbar{}
\href{https://www.edmondsun.com/news/shelter-in-place-close-non-essential-businesses-in-edmond/article_9351d77a-72ec-11ea-baf9-efe3ccd9894e.html}{Read
local coverage}

Moore About 62,000 people

Shelter in place, effective April 4 at 11:59 p.m.

\href{https://www.cityofmoore.com/uploads/Parks/EMERGENCY-PROCLAMATION-00382020.pdf}{See
announcement} \textbar{}
\href{https://www.normantranscript.com/news/local_news/moore-issues-shelter-in-place-order-schools-update-distance-learning/article_e429efb1-025d-54ea-bc4c-d5afbcf1799f.html}{Read
local coverage}

Norman About 123,000 people

Stay at home, effective March 25 at 11:59 p.m.

\href{https://static1.squarespace.com/static/5e73c3526ab9182890fd4c29/t/5e7a745761495f27e26b1e5c/1585083479590/Proclamation+2020-04.pdf}{See
announcement} \textbar{}
\href{https://oklahoman.com/article/5658480/coronavirus-in-oklahoma-norman-mayor-to-announce-shelter-in-place-order}{Read
local coverage}

Oklahoma City About 649,000 people

Shelter in place, effective March 28 at 11:59 p.m.

\href{https://www.okc.gov/Home/Components/News/News/3321/18}{See
announcement} \textbar{}
\href{https://oklahoman.com/article/5658851/coronavirus-in-oklahoma-oklahoma-city-to-implement-shelter-in-place-order}{Read
local coverage}

Sallisaw About 9,000 people

Shelter in place, effective April 4 at 11:59 p.m.

\href{http://www.sallisawok.org/DocumentCenter/View/1505/COVID19PROCLAMATIONSallisaw}{See
announcement} \textbar{}
\href{https://www.4029tv.com/article/sallisaw-mayor-orders-people-to-shelter-in-place/32038696}{Read
local coverage}

Stillwater About 50,000 people

Shelter in place, effective March 30 at 11:59 p.m.

\href{http://stillwater.org/files/news-releases/covid-declarations/copiers_20200330_114236.pdf}{See
announcement} \textbar{}
\href{https://www.stwnewspress.com/covid-19/shelter-in-place-for-stillwater-going-into-effect-just-before/article_245f9bd0-72b6-11ea-8fc8-63cef71d9e5e.html}{Read
local coverage}

Tulsa About 401,000 people

Shelter in place, effective March 28 at 11:59 p.m.

\href{http://www.cityoftulsa.org/media/12617/2020-04.pdf}{See
announcement} \textbar{}
\href{https://www.tulsaworld.com/news/not-a-recommendation-mayor-g-t-bynum-issues-shelter-in/article_5d2fda2b-0b00-5119-80fd-a3f25e7cde81.html}{Read
local coverage}

\hypertarget{oregon-about-42-million-people}{%
\subsubsection{Oregon About 4.2 million
people}\label{oregon-about-42-million-people}}

Gov. Kate Brown took the action after seeing the state's scenic trails
and beaches packed with people over the weekend. ``If you're still not
sure about an activity, skip it,'' she said. ``Staying home will save
lives.''

Stay at home, effective March 23

\href{https://govsite-assets.s3.amazonaws.com/jkAULYKcSh6DoDF8wBM0_EO\%2020-12.pdf}{See
announcement} \textbar{}
\href{https://www.oregonlive.com/coronavirus/2020/03/its-a-matter-of-life-or-death-gov-kate-brown-begs-oregonians-to-stay-home-as-people-crowd-coast-gorge.html}{Read
local coverage}

\hypertarget{pennsylvania-about-128-million-people}{%
\subsubsection{Pennsylvania About 12.8 million
people}\label{pennsylvania-about-128-million-people}}

Starting March 23, Gov. Tom Wolf began ordering an expanding number of
counties to stay at home, including in the Philadelphia and Pittsburgh
regions. On April 1, he announced he was enacting the order statewide.
``We appreciate the shared sacrifice of all 12.8 million
Pennsylvanians," he said. "We are in this together."

Stay at home, effective April 1 at 8 p.m.

\href{https://www.governor.pa.gov/wp-content/uploads/2020/04/20200401-GOV-Statewide-Stay-at-Home-Order.pdf}{See
announcement} \textbar{}
\href{https://www.inquirer.com/news/pennsylvania/spl/pennsylvania-pa-coronavirus-stay-at-home-order-statewide-20200401.html}{Read
local coverage}

\hypertarget{puerto-rico-about-32-million-people}{%
\subsubsection{Puerto Rico About 3.2 million
people}\label{puerto-rico-about-32-million-people}}

Gov. Wanda Vázquez issued an order imposing a nightly curfew and
allowing people to leave their homes during the day only to buy
groceries or medicine, go to the bank, attend medical appointments, tend
to caregiving responsibilities or work in businesses deemed essential.
``All citizens will have to stay home to stop the spread of this
virus,'' she said.

Curfew, effective March 15 at 6 p.m.

\href{https://www.scribd.com/document/451785912/Orden-ejecutiva-de-la-gobernadora-para-combatir-el-coronavirus\#from_embed}{See
announcement} \textbar{}
\href{https://www.elnuevodia.com/noticias/locales/nota/wandavazquezdecretatoquedequedaparatodopuertoricoparacontenerelcoronavirus-2552934/}{Read
local coverage}

\hypertarget{rhode-island-about-11-million-people}{%
\subsubsection{Rhode Island About 1.1 million
people}\label{rhode-island-about-11-million-people}}

Gov. Gina Raimondo issued a stay-at-home order in a state that has gone
to great lengths to protect itself from outsiders, especially people
fleeing New York City. She said a surge in cases was inevitable. "This
is going to get very real very fast for all of us," she said.

Stay at home, effective March 28

\href{http://governor.ri.gov/documents/orders/Executive-Order-20-13.pdf}{See
announcement} \textbar{}
\href{https://www.providencejournal.com/news/20200328/ri-tightens-restrictions-after-2-virus-deaths}{Read
local coverage}

\hypertarget{south-carolina-about-51-million-people}{%
\subsubsection{South Carolina About 5.1 million
people}\label{south-carolina-about-51-million-people}}

Charleston and Columbia had previously ordered residents in those cities
to stay at home before Gov. Henry McMaster issued a statewide "home or
work order," which requires all South Carolinians to limit movement
outside their home or place of work except for essential activities.
South Carolina became the last state on the East Coast to issue such an
order.

Stay at home , effective April 7 at 5 p.m.

\href{https://governor.sc.gov/sites/default/files/Documents/Executive-Orders/2020-04-06\%20eFILED\%20Executive\%20Order\%20No.\%202020-21\%20-\%20Stay\%20at\%20Home\%20or\%20Work\%20Order.pdf}{See
announcement} \textbar{}
\href{https://www.postandcourier.com/health/covid19/sc-issues-coronavirus-stay-at-home-order-limits-number-of-shoppers-in-stores/article_144481a6-7834-11ea-b747-9324c93bd43b.html}{Read
local coverage}

\hypertarget{tennessee-about-68-million-people}{%
\subsubsection{Tennessee About 6.8 million
people}\label{tennessee-about-68-million-people}}

Residents in the Nashville and Memphis areas were already under
instructions to stay at home as much as possible when Gov. Bill Lee
issued statewide guidelines urging everyone to do so. "We need you to do
that to protect the lives of your neighbors," he said.

Stay at home, effective March 31 at 11:59 p.m.

\href{https://publications.tnsosfiles.com/pub/execorders/exec-orders-lee22.pdf}{See
announcement} \textbar{}
\href{https://www.tennessean.com/story/news/health/2020/03/30/tennessee-governor-bill-lee-stay-at-home-order-to-stop-coronavirus/2937429001/}{Read
local coverage}

\hypertarget{texas-about-29-million-people}{%
\subsubsection{Texas About 29 million
people}\label{texas-about-29-million-people}}

For weeks, Gov. Greg Abbott left it to local officials to impose the
most restrictive orders. Millions of people in certain cities and
counties were told to stay home, including in Harris County, which
includes Houston; Dallas and Tarrant Counties in the Dallas-Fort Worth
region; and Bexar County, which includes San Antonio. On March 31, Mr.
Abbott tightened guidelines, but said that "this is not a stay-at-home
strategy." The next day, he released a video message to Texans, saying
he had ordered "all Texans to stay at home, except to provide essential
services or do essential things like going to the grocery store.'' A
spokesman for Mr. Abbott later confirmed that Texas was under a
statewide stay-at-home mandate.

Stay at home, effective April 2 at 12:01 a.m.

\href{https://gov.texas.gov/uploads/files/press/EO-GA-14_Statewide_Essential_Service_and_Activity_COVID-19_IMAGE_03-31-2020.pdf}{See
announcement} \textbar{}
\href{https://www.texastribune.org/2020/03/31/greg-abbott-texas-executive-order-closures/}{Read
local coverage}

\hypertarget{utah}{%
\subsubsection{Utah}\label{utah}}

Summit County, a popular area for skiing and tourism, became the first
in Utah to issue such a restriction, The Salt Lake Tribune reported.
Salt Lake County also issued a similar order. ``The goals are to save
lives and stop our hospital system from being overrun,'' Mayor Jenny
Wilson of Salt Lake County said.

Davis County About 352,000 people

Stay at home, effective April 1 at 11:59 p.m.

\href{http://www.co.davis.ut.us/docs/librariesprovider5/covid-19/public-health-order-4-1-20/public-health-order-april-1-2020.pdf?sfvrsn=4b453153_2}{See
announcement} \textbar{}
\href{https://www.sltrib.com/news/2020/04/01/davis-county-issues/}{Read
local coverage}

Salt Lake County About 1.2 million people

Stay at home, effective March 30 at 12:01 a.m.

\href{https://slco.org/globalassets/1-site-files/health/programs/covid/pho/pho3.pdf}{See
announcement} \textbar{}
\href{https://www.sltrib.com/news/2020/03/29/coronavirus-cases-utah/}{Read
local coverage}

Summit County About 42,000 people

Stay at home, effective March 27 at 12:01 a.m.

\href{https://summitcountyhealth.org/public-announcements/3-25-20-summit-county-issues-stay-at-home-order-to-residents/}{See
announcement} \textbar{}
\href{https://www.sltrib.com/news/2020/03/25/summit-county-orders/}{Read
local coverage}

\hypertarget{vermont-about-626000-people}{%
\subsubsection{Vermont About 626,000
people}\label{vermont-about-626000-people}}

``I need all Vermonters to understand that the more quickly and closely
we follow these stay-at-home measures, the faster and safer we can get
through this and get our daily lives, and our economy, moving again,"
Gov. Phil Scott said.

Stay at home, effective March 25 at 5 p.m.

\href{https://governor.vermont.gov/sites/scott/files/documents/ADDENDUM\%206\%20TO\%20EXECUTIVE\%20ORDER\%2001-20.pdf}{See
announcement} \textbar{}
\href{https://www.burlingtonfreepress.com/story/news/local/2020/03/24/vermont-gov-phil-scott-all-vermonters-should-stay-home-order/2909062001/}{Read
local coverage}

\hypertarget{virginia-about-85-million-people}{%
\subsubsection{Virginia About 8.5 million
people}\label{virginia-about-85-million-people}}

Gov. Ralph Northam, who shut down schools and nonessential businesses
and banned gatherings of more than 10 people, had said that issuing a
stay-at-home order was a matter of semantics. But after seeing beaches
and other public areas packed with people, he issued a formal order. "It
is clear more people still need to hear this basic message: Stay home."

Stay at home, effective March 30

\href{https://www.governor.virginia.gov/newsroom/all-releases/2020/march/headline-855702-en.html}{See
announcement} \textbar{}
\href{https://www.roanoke.com/news/virginia/gov-northam-to-issue-stay-at-home-order/article_b80fb621-1eca-57dd-b8e4-67c8a7dd8ebc.html}{Read
local coverage}

\hypertarget{washington-about-75-million-people}{%
\subsubsection{Washington About 7.5 million
people}\label{washington-about-75-million-people}}

Gov. Jay Inslee tried begging people to stay at home in Washington
State, which has among the worst outbreaks of the virus in the country.
Then he made it mandatory. ``The fastest way to get back to normal is to
hit this hard,'' he said.

Stay at home, effective March 23

\href{https://www.documentcloud.org/documents/6817957-20-25-Coronovirus-Stay-Safe-Stay-Healthy.html}{See
announcement} \textbar{}
\href{https://www.seattletimes.com/seattle-news/inslee-to-hold-televised-address-monday-evening-to-announce-enhanced-strategies-on-covid-19/}{Read
local coverage}

\hypertarget{west-virginia-about-18-million-people}{%
\subsubsection{West Virginia About 1.8 million
people}\label{west-virginia-about-18-million-people}}

West Virginia was the last state to have a confirmed case of the virus,
but Gov. Jim Justice quickly joined a chorus of other governors calling
on residents to stay inside. ``A stay-at-home order is not martial
law,'' he said, reminding residents that they could still leave their
homes for food and outdoor activity. But he warned: ``The magnitude of
this is unbelievable.''

Stay at home, effective March 24 at 8 p.m.

\href{https://dhhr.wv.gov/COVID-19/Pages/Governor-Issues-Stay-at-Home-Order.aspx}{See
announcement} \textbar{}
\href{https://www.wvgazettemail.com/coronavirus/justice-issues-stay-at-home-order-closes-non-essential-businesses/article_37bc0158-d9b4-5255-83d1-cc4dd57f409b.html}{Read
local coverage}

\hypertarget{wisconsin-about-58-million-people}{%
\subsubsection{Wisconsin About 5.8 million
people}\label{wisconsin-about-58-million-people}}

Gov. Tony Evers initially thought he would not have to issue such an
order, but later changed his mind. ``You can still get out and walk the
dogs --- it's good exercise and it's good for everyone's mental health
--- but please don't take any other unnecessary trips," he said. "Limit
your travel to essential needs like going to the doctor, grabbing
groceries or getting medication.''

Stay at home, effective March 25 at 8 a.m.

\href{https://www.wpr.org/sites/default/files/health_order_12_safer_at_home.pdf}{See
announcement} \textbar{}
\href{https://www.wpr.org/evers-administration-issues-stay-home-order-wisconsin}{Read
local coverage}

\hypertarget{wyoming}{%
\subsubsection{Wyoming}\label{wyoming}}

Jackson, a popular tourist destination for skiers in the Jackson Hole
valley, was the first town in the state to issue a stay-at-home order,
according to the Casper Star-Tribune.

Jackson About 10,000 people

Stay at home, effective March 28

\href{https://www.jacksonwy.gov/DocumentCenter/View/3048/Mar28-EmOrd1249-StayAtHomeOrder?bidId=}{See
announcement} \textbar{}
\href{https://trib.com/news/local/casper/jackson-issues-shelter-in-place-order-to-limit-spread-of/article_40c9fa29-c59b-540f-b4cd-7b211b6eb335.html}{Read
local coverage}

Note: All times are local. Sources: State and local governments, local
news reports, Census Bureau

Vanessa Swales, Patricia Mazzei and Mike Baker contributed reporting.

\textbf{Correction:}~March 31, 2020

A label on some maps in an earlier version of this article incorrectly
included a U.S. territory in the total number of statewide orders. While
Puerto Rico did have a stay-at-home order in place, it is a territory,
not a state.

Read 221 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
