Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}

\href{https://myaccount.nytimes3xbfgragh.onion/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes3xbfgragh.onion/section/todayspaper}{Today's
Paper}

\href{/section/us}{U.S.}\textbar{}U.S. Coronavirus Rates Are Rising Fast
Among Children

\url{https://nyti.ms/3hMPbOG}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

\hypertarget{school-reopenings}{%
\subsubsection{\texorpdfstring{\href{https://www.nytimes3xbfgragh.onion/spotlight/schools-reopening?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=d26638d0-f1e9-11ea-90a7-1f8163516127\&variant=undefined}{School
Reopenings}}{School Reopenings}}\label{school-reopenings}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/04/us/bar-exam-coronavirus.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=d26638d1-f1e9-11ea-90a7-1f8163516127\&variant=undefined}{Delayed
  Licensing Exams}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/08/upshot/children-testing-shortfalls-virus.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=d26638d2-f1e9-11ea-90a7-1f8163516127\&variant=undefined}{Limited
  Testing for Children}
\item
  \href{https://www.nytimes3xbfgragh.onion/2020/09/01/world/schools-reopen-globe-students.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=d26638d3-f1e9-11ea-90a7-1f8163516127\&variant=undefined}{School
  Around the World}
\item
  \href{https://www.nytimes3xbfgragh.onion/interactive/2020/us/covid-college-cases-tracker.html?name=styln-coronavirus-schools-reopening\&region=TOP_BANNER\&block=storyline_menu_recirc\&action=click\&pgtype=Interactive\&impression_id=d26638d4-f1e9-11ea-90a7-1f8163516127\&variant=undefined}{Tracking
  College Cases}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{us-coronavirus-rates-are-rising-fast-among-children}{%
\section{U.S. Coronavirus Rates Are Rising Fast Among
Children}\label{us-coronavirus-rates-are-rising-fast-among-children}}

By \href{https://www.nytimes3xbfgragh.onion/by/lauren-leatherby}{Lauren
Leatherby} and Lisa Waananen JonesAug. 31, 2020

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

As some schools begin in-person classes, data compiled by the American
Academy of Pediatrics from the summer show that cases, hospitalizations
and deaths from the coronavirus have increased at a faster rate in
children and teenagers than among the general public.

\hypertarget{cumulative-change-since-may-21}{%
\subsubsection{Cumulative change since May
21}\label{cumulative-change-since-may-21}}

Cases

+720\%Children +270\%All May 21Aug. 20

Hospitalizations

+356\%Children +122\%All May 21Aug. 20

Deaths

+229\%Children +115\%All May 21Aug. 20

Source: The American Academy of Pediatrics

The
\href{https://services.aap.org/en/pages/2019-novel-coronavirus-covid-19-infections/children-and-covid-19-state-level-data-report/}{data
set}, which spans from May 21 to Aug. 20, varies from state to state,
possibly obscuring differences in how the virus affects infants, young
children and adolescents.

For example, many states group infants and teenagers into the same
category. One state even includes people up to age 24. But the rise
remains similar across states.

Young children seem to catch and transmit the virus
\href{https://www.nytimes3xbfgragh.onion/2020/07/20/parenting/coronavirus-children-spread-covid-19.html}{less
than adults}, and children of all ages tend not to experience severe
complications from it. But Dr. Sean O'Leary, vice chairman of the
American Academy of Pediatrics' committee on infectious diseases, said
that substantial community spread in many parts of the United States
corresponded with more infections among children.

The rise in reported cases comes in part from more widespread testing,
but Dr. O'Leary said there was evidence that minors were becoming
infected at a higher rate now than earlier in the year because
hospitalizations and deaths among children had increased as well.

Although much is still unknown about how the virus affects young people,
like adults, Black and Latino children who contract the virus are
\href{https://www.cdc.gov/mmwr/volumes/69/wr/mm6932e3.htm}{more likely
to be hospitalized}.

``Anyone who has been on the front lines of this pandemic in a
children's hospital can tell you we've taken care of lots of kids that
are very sick,'' Dr. O'Leary said. ``Yes, it's less severe in children
than adults, but it's not completely benign.''

Since the beginning of the summer, every state in the country has had an
increase in the number of young people who have tested positive for the
coronavirus, as a share of all cases. In late May, about 5 percent of
the nation's cases were documented in minors. By Aug. 20, that number
had risen to more than 9 percent.

\hypertarget{change-in-share-of-reported-coronavirus-cases-in-minors-since-may-28}{%
\subsubsection{Change in share of reported coronavirus cases in minors
since May
28}\label{change-in-share-of-reported-coronavirus-cases-in-minors-since-may-28}}

Alaska

Maine

10 pct. pts.

5

0

May 28

Aug. 20

Wis.

Vt.

N.H.

10

5

0

Wash.

Idaho

Mont.

N.D.

Minn.

Ill.

Mich.

N.Y.

Mass.

10

5

0

Ore.

Nev.

Wyo.

S.D.

Iowa

Ind.

Ohio

Pa.

N.J.

Conn.

R.I.

10

5

0

Calif.

Utah

Colo.

Neb.

Mo.

Ky.

W.Va.

Va.

Md.

Del.

10

5

0

Ariz.

N.M.

Kan.

Ark.

Tenn.

S.C.

N.C.

D.C.

10

5

0

Okla.

La.

Miss.

Ala.

Ga.

10

5

0

Hawaii

Texas

Fla.

10

5

0

10 pct.

pts.

Alaska

Maine

5

0

May 28

Aug. 20

Wis.

Vt.

N.H.

10

5

0

Wash.

Idaho

Mont.

N.D.

Minn.

Ill.

Mich.

N.Y.

Mass.

10

5

0

Ore.

Nev.

Wyo.

S.D.

Iowa

Ind.

Ohio

Pa.

N.J.

Conn.

R.I.

10

5

0

Calif.

Utah

Colo.

Neb.

Mo.

Ky.

W.Va.

Va.

Md.

Del.

10

5

0

Ariz.

N.M.

Kan.

Ark.

Tenn.

S.C.

N.C.

D.C.

10

5

0

Okla.

La.

Miss.

Ala.

Ga.

10

5

0

Hawaii

Texas

Fla.

10

5

0

10 pct.

pts.

10 pct.

pts.

Alaska

Maine

0

May 28

Aug. 20

Wis.

Vt.

N.H.

10

0

Wash.

Idaho

Mont.

N.D.

Minn.

Ill.

Mich.

N.Y.

Mass.

10

0

Ore.

Nev.

Wyo.

S.D.

Iowa

Ind.

Ohio

Pa.

N.J.

Conn.

R.I.

10

0

Calif.

Utah

Colo.

Neb.

Mo.

Ky.

W.Va.

Va.

Md.

Del.

10

0

Ariz.

N.M.

Kan.

Ark.

Tenn.

S.C.

N.C.

D.C.

10

0

Okla.

La.

Miss.

Ala.

Ga.

10

0

Hawaii

Texas

Fla.

10

0

Source: The American Academy of Pediatrics \textbar{} Note: Data as of
Aug. 20. States use varying age ranges for children. Forty-six states
and Washington, D.C., count those up to the age of 17, 18 or 19 in their
data. Florida and Utah count only those through age 14, Tennessee and
South Carolina count those through age 20, and Alabama counts those up
to 24 years old. In New York, only New York City reports the age
distribution of cases.

Some lawmakers have cited the lower likelihood of transmission among
school-age children as a reason schools should reopen for in-person
classes.

President Trump has said he would like to see
\href{https://www.whitehouse.gov/briefings-statements/president-donald-j-trump-working-give-students-parents-flexibility-schools-support-need-reopen-fall/}{schools
fully
re}\href{https://www.whitehouse.gov/briefings-statements/president-donald-j-trump-working-give-students-parents-flexibility-schools-support-need-reopen-fall/}{open}and
falsely claimed in a video posted by his campaign that children were
``\href{https://www.nytimes3xbfgragh.onion/2020/08/05/technology/trump-facebook-coronavirus-video.html}{virtually
immune}'' to the virus. Facebook and Twitter later removed the video,
saying it violated policies about misinformation around the virus. In
July, Gov. Ron DeSantis of Florida, a Republican, claimed that
``\href{https://www.c-span.org/video/?473818-1/florida-governor-desantis-coronavirus-news-conference}{schoolchildren
actually are not vectors for this}.''

Dr. William Raszka Jr., a pediatric infectious disease expert at the
Robert Larner, M.D. College of Medicine at the University of Vermont in
Burlington, said research consistently showed that adults --- not
children --- were driving the spread of the virus. Outbreaks at
\href{https://www.nytimes3xbfgragh.onion/2020/07/31/health/coronavirus-children-camp.html}{summer
camps} and schools, however, have demonstrated that transmission can, in
fact, happen among children.

At a sleepaway summer camp in Georgia where
\href{https://www.nytimes3xbfgragh.onion/2020/07/31/health/coronavirus-children-camp.html}{hundreds
were infected}, 76 percent of campers and staff members whose test
results were available to researchers had tested positive. The youngest
campers, ages 6 to 10, were more likely to be infected than older
campers.

It is clear that the virus can spread among children under certain
circumstances, Dr. Raszka said. He worries about opening schools in
places where infection rates are high, especially in areas that do not
require people to wear masks or other proven mitigation measures to stop
the spread of the virus.

Unlike the summer camp where children interacted almost entirely with
other children and teenagers, schools holding in-person classes require
interactions between students and their adult teachers and caregivers,
who may be more vulnerable to severe complications.

``One of the challenges is that you just can't separate schools from the
community,'' Dr. Raszka said. ``When there's a really high prevalence
rate in the community and you open schools, there's going to be a lot of
transmission in schools.''

In June, a study published in Nature found that people under age 20 were
\href{https://www.nature.com/articles/s41591-020-0962-9}{approximately
half as susceptible} to contracting the virus as those older than 20.
That lower likelihood of infection is reflected across many states. In
Arizona, for instance, about 2,800 of every 100,000 residents have
tested positive, whereas just over 1,300 of every 100,000 children in
the state have tested positive.

That likelihood changes by age. Research consistently shows that
teenagers are more likely to catch and transmit the virus than younger
children, though the reasons are uncertain. Those 10 to 19 years old
make up a larger share of cases than young children in all of the states
that track the age groups separately.

\hypertarget{young-children-make-up-fewer-of-the-reported-cases-than-adolescents}{%
\subsubsection{Young children make up fewer of the reported cases than
adolescents}\label{young-children-make-up-fewer-of-the-reported-cases-than-adolescents}}

Alaska Connecticut Florida Georgia Kansas Kentucky Maryland Michigan
Missouri Montana Nevada New Hampshire New Mexico North Dakota Oregon
Pennsylvania Rhode Island South Carolina South Dakota Tennessee Texas
Vermont Virginia West Virginia Wisconsin 0 20 40 60 80 100\% Age 9 and
under Ages 10 to 19

Source: State health departments \textbar{} Note: Data as of Aug. 26.
Only states that divide their data at 10 years old are included.
Georgia's older range is ages 10 to 17. North Dakota, South Carolina and
Tennessee report groups as ages 0 to 10 and 11 to 20.

The total number of children infected has doubled since the American
Academy of Pediatrics and education groups
\href{https://services.aap.org/en/news-room/news-releases/aap/2020/pediatricians-educators-and-superintendents-urge-a-safe-return-to-school-this-fall/}{recommended}
in early July that schools should reopen wherever possible. Despite the
overall increases, experts said those guidelines still applied.

``There are a lot of places in the U.S. where it is potentially safe to
reopen schools, even knowing that, yes, kids can get infected and, yes,
sometimes kids can get severely infected,'' Dr. O'Leary said.

Some success stories show that it is possible to stop transmission among
children in places with low community levels of virus.

At four summer camps in Maine, a state with one of the nation's lowest
infection rates, aggressive testing and quarantining prevented those who
tested positive after arrival
\href{https://www.cdc.gov/mmwr/volumes/69/wr/mm6935e1.htm?s_cid=mm6935e1_w}{from
spreading the virus}. Germany, Denmark and Norway have been able
\href{https://www.nytimes3xbfgragh.onion/2020/08/26/world/europe/germany-schools-virus-reopening.html}{to
keep schools open}, thanks to a combination of low community
transmission, fast and free testing, and rigorous contact tracing.

Many states report incomplete demographic information for Covid-19
cases. The number of cases with age information is smaller than the
total number of reported cases.

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes3xbfgragh.onion/privacy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
