Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/us}{U.S.}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/us}{U.S.}\textbar{}Is Your State Doing Enough Coronavirus
Testing?

\url{https://nyti.ms/2Od1kPO}

\begin{itemize}
\item
\item
\item
\item
\item
\item
\end{itemize}

\href{https://www.nytimes.com/news-event/coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{The
Coronavirus Outbreak}

\begin{itemize}
\tightlist
\item
  live\href{https://www.nytimes.com/2020/08/02/world/coronavirus-updates.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Latest
  Updates}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Maps
  and Cases}
\item
  \href{https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Vaccine
  Tracker}
\item
  \href{https://www.nytimes.com/interactive/2020/07/29/us/schools-reopening-coronavirus.html?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{What
  School May Look Like}
\item
  \href{https://www.nytimes.com/live/2020/07/31/business/stock-market-today-coronavirus?action=click\&pgtype=Article\&state=default\&region=TOP_BANNER\&context=storylines_menu}{Economy}
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

\hypertarget{comments}{%
\subsection{\texorpdfstring{\protect\hyperlink{commentsContainer}{Comments}}{Comments}}\label{comments}}

\href{}{Is Your State Doing Enough Coronavirus Testing?}\href{}{Skip to
Comments}

The comments section is closed. To submit a letter to the editor for
publication, write to
\href{mailto:letters@nytimes.com}{\nolinkurl{letters@nytimes.com}}.

\hypertarget{is-your-state-doing-enough-coronavirus-testing}{%
\section{Is Your State Doing Enough Coronavirus
Testing?}\label{is-your-state-doing-enough-coronavirus-testing}}

By \href{https://www.nytimes.com/by/keith-collins}{Keith Collins}Updated
August 2, 2020

\begin{itemize}
\item
\item
\item
\item
\item
  \emph{197}
\end{itemize}

\href{https://www.nytimes.com/interactive/2020/world/coronavirus-maps.html}{World}~

COUNTRIES

\textbar{}
\href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html}{U.S.A.}~

STATES

~
\href{https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html}{Vaccines}

\href{https://www.nytimes.com/interactive/2020/world/americas/brazil-coronavirus-cases.html}{Brazil}\href{https://www.nytimes.com/interactive/2020/world/canada/canada-coronavirus-cases.html}{Canada}\href{https://www.nytimes.com/interactive/2020/world/europe/france-coronavirus-cases.html}{France}\href{https://www.nytimes.com/interactive/2020/world/europe/germany-coronavirus-cases.html}{Germany}\href{https://www.nytimes.com/interactive/2020/world/asia/india-coronavirus-cases.html}{India}\href{https://www.nytimes.com/interactive/2020/world/europe/italy-coronavirus-cases.html}{Italy}\href{https://www.nytimes.com/interactive/2020/world/americas/mexico-coronavirus-cases.html}{Mexico}\href{https://www.nytimes.com/interactive/2020/world/europe/spain-coronavirus-cases.html}{Spain}\href{https://www.nytimes.com/interactive/2020/world/europe/united-kingdom-coronavirus-cases.html}{U.K.}

\href{https://www.nytimes.com/interactive/2020/us/alabama-coronavirus-cases.html}{Alabama}\href{https://www.nytimes.com/interactive/2020/us/alaska-coronavirus-cases.html}{Alaska}\href{https://www.nytimes.com/interactive/2020/us/arizona-coronavirus-cases.html}{Arizona}\href{https://www.nytimes.com/interactive/2020/us/arkansas-coronavirus-cases.html}{Arkansas}\href{https://www.nytimes.com/interactive/2020/us/california-coronavirus-cases.html}{California}\href{https://www.nytimes.com/interactive/2020/us/colorado-coronavirus-cases.html}{Colorado}\href{https://www.nytimes.com/interactive/2020/us/connecticut-coronavirus-cases.html}{Connecticut}\href{https://www.nytimes.com/interactive/2020/us/delaware-coronavirus-cases.html}{Delaware}\href{https://www.nytimes.com/interactive/2020/us/florida-coronavirus-cases.html}{Florida}\href{https://www.nytimes.com/interactive/2020/us/georgia-coronavirus-cases.html}{Georgia}\href{https://www.nytimes.com/interactive/2020/us/hawaii-coronavirus-cases.html}{Hawaii}\href{https://www.nytimes.com/interactive/2020/us/idaho-coronavirus-cases.html}{Idaho}\href{https://www.nytimes.com/interactive/2020/us/illinois-coronavirus-cases.html}{Illinois}\href{https://www.nytimes.com/interactive/2020/us/indiana-coronavirus-cases.html}{Indiana}\href{https://www.nytimes.com/interactive/2020/us/iowa-coronavirus-cases.html}{Iowa}\href{https://www.nytimes.com/interactive/2020/us/kansas-coronavirus-cases.html}{Kansas}\href{https://www.nytimes.com/interactive/2020/us/kentucky-coronavirus-cases.html}{Kentucky}\href{https://www.nytimes.com/interactive/2020/us/louisiana-coronavirus-cases.html}{Louisiana}\href{https://www.nytimes.com/interactive/2020/us/maine-coronavirus-cases.html}{Maine}\href{https://www.nytimes.com/interactive/2020/us/maryland-coronavirus-cases.html}{Maryland}\href{https://www.nytimes.com/interactive/2020/us/massachusetts-coronavirus-cases.html}{Massachusetts}\href{https://www.nytimes.com/interactive/2020/us/michigan-coronavirus-cases.html}{Michigan}\href{https://www.nytimes.com/interactive/2020/us/minnesota-coronavirus-cases.html}{Minnesota}\href{https://www.nytimes.com/interactive/2020/us/mississippi-coronavirus-cases.html}{Mississippi}\href{https://www.nytimes.com/interactive/2020/us/missouri-coronavirus-cases.html}{Missouri}\href{https://www.nytimes.com/interactive/2020/us/montana-coronavirus-cases.html}{Montana}\href{https://www.nytimes.com/interactive/2020/us/nebraska-coronavirus-cases.html}{Nebraska}\href{https://www.nytimes.com/interactive/2020/us/nevada-coronavirus-cases.html}{Nevada}\href{https://www.nytimes.com/interactive/2020/us/new-hampshire-coronavirus-cases.html}{New
Hampshire}\href{https://www.nytimes.com/interactive/2020/us/new-jersey-coronavirus-cases.html}{New
Jersey}\href{https://www.nytimes.com/interactive/2020/us/new-mexico-coronavirus-cases.html}{New
Mexico}\href{https://www.nytimes.com/interactive/2020/us/new-york-coronavirus-cases.html}{New
York}\href{https://www.nytimes.com/interactive/2020/us/north-carolina-coronavirus-cases.html}{North
Carolina}\href{https://www.nytimes.com/interactive/2020/us/north-dakota-coronavirus-cases.html}{North
Dakota}\href{https://www.nytimes.com/interactive/2020/us/ohio-coronavirus-cases.html}{Ohio}\href{https://www.nytimes.com/interactive/2020/us/oklahoma-coronavirus-cases.html}{Oklahoma}\href{https://www.nytimes.com/interactive/2020/us/oregon-coronavirus-cases.html}{Oregon}\href{https://www.nytimes.com/interactive/2020/us/pennsylvania-coronavirus-cases.html}{Pennsylvania}\href{https://www.nytimes.com/interactive/2020/us/puerto-rico-coronavirus-cases.html}{Puerto
Rico}\href{https://www.nytimes.com/interactive/2020/us/rhode-island-coronavirus-cases.html}{Rhode
Island}\href{https://www.nytimes.com/interactive/2020/us/south-carolina-coronavirus-cases.html}{South
Carolina}\href{https://www.nytimes.com/interactive/2020/us/south-dakota-coronavirus-cases.html}{South
Dakota}\href{https://www.nytimes.com/interactive/2020/us/tennessee-coronavirus-cases.html}{Tennessee}\href{https://www.nytimes.com/interactive/2020/us/texas-coronavirus-cases.html}{Texas}\href{https://www.nytimes.com/interactive/2020/us/utah-coronavirus-cases.html}{Utah}\href{https://www.nytimes.com/interactive/2020/us/vermont-coronavirus-cases.html}{Vermont}\href{https://www.nytimes.com/interactive/2020/us/virginia-coronavirus-cases.html}{Virginia}\href{https://www.nytimes.com/interactive/2020/us/washington-coronavirus-cases.html}{Washington}\href{https://www.nytimes.com/interactive/2020/us/washington-dc-coronavirus-cases.html}{Washington,
D.C.}\href{https://www.nytimes.com/interactive/2020/us/west-virginia-coronavirus-cases.html}{West
Virginia}\href{https://www.nytimes.com/interactive/2020/us/wisconsin-coronavirus-cases.html}{Wisconsin}\href{https://www.nytimes.com/interactive/2020/us/wyoming-coronavirus-cases.html}{Wyoming}

~

The number of daily coronavirus tests being conducted in the United
States is only \textbf{43 percent} of the level considered necessary to
mitigate the spread of the virus, as many states struggle to increase
testing and catch up to the recent surge in cases.

9

states* meet the testing target

5

states are near the target

37

states are far below the target

AlaskaAla.Ark.Ariz.Calif.Colo.Conn.D.C.Del.Fla.Ga.HawaiiIowaIdahoIll.Ind.Kan.Ky.La.Mass.Md.MaineMich.Minn.Mo.Miss.Mont.N.C.N.D.Neb.N.H.N.J.N.M.Nev.N.Y.OhioOkla.Ore.Pa.R.I.S.C.S.D.Tenn.TexasUtahVa.Vt.Wash.Wis.W.Va.Wyo.

*Includes 8 states and Washington, D.C. States within 20 percent of the
testing target are considered ``near'' the target.

An average of \textbf{790,000 people per day} were tested over the past
week, according to data collected by
\href{https://covidtracking.com/}{the Covid Tracking Project}, far below
the current nationwide target of \textbf{1.8 million daily tests}. The
target, which is based on a methodology developed by researchers at the
Harvard Global Health Institute, is different for each state and varies
over time as infection rates change.

\hypertarget{how-each-states-current-testing-measures-up}{%
\subsubsection{How each state's current testing measures
up}\label{how-each-states-current-testing-measures-up}}

\hypertarget{average-daily-testing-and-hospitalizations-in-the-last-two-weeks}{%
\paragraph{Average daily testing and hospitalizations in the last two
weeks}\label{average-daily-testing-and-hospitalizations-in-the-last-two-weeks}}

Note: In many states, if a person is tested more than once, each test is
counted in data for total tests. Some states, including Nevada, Rhode
Island and Wyoming, report the actual number of people tested, which is
a more accurate way to measure the share of a population that has been
tested, but can result in a lower number of total tests. Positive test
rates and percentages of targets are calculated using cumulative figures
from the last 14 days. All other values are 14-day rolling averages.
Trendlines for daily tests and hospitalizations show averages for the
last two weeks.

Testing operations in the United States were delayed at the start of the
outbreak after tests developed by the Centers for Disease Control and
Prevention were found to be faulty. Since then, testing levels have
steadily increased across the country, but many states have
\href{https://www.nytimes.com/2020/07/06/us/coronavirus-test-shortage.html}{struggled
to stay ahead of new outbreaks} as overwhelmed labs report processing
delays and shortages of crucial testing supplies. The resulting backlog
can leave sick people undiagnosed, with the potential to further spread
the virus as states reopen.

The Harvard researchers say that at minimum there should be enough daily
capacity to test anyone who has flu-like symptoms and an additional 10
people for any symptomatic person who tests positive for the virus. That
level of testing --- which, according to researchers, is the minimum
necessary to mitigate the disease --- would require more than double the
number of daily tests currently being performed. Their estimates for the
testing required to \emph{suppress} the spread of the virus are
\href{https://globalepidemics.org/july-6-2020-state-testing-targets/}{much
higher}.

Aside from current testing levels, another important indicator of a
state's testing performance is its positive test rate, which is the
percent of tests that come back positive. Lower rates suggest that
testing is more widespread and that it is not limited to those with
severe symptoms. Positive rates should be at or below 5 percent for at
least 14 days before a state or country can safely reopen, according to
the World Health Organization. In the United States, the current
positive rate is \textbf{8 percent}.

\hypertarget{where-testing-is-far-below-recommended-levels}{%
\subsection{Where testing is far below recommended
levels}\label{where-testing-is-far-below-recommended-levels}}

Most states remain far from the minimum level of testing needed to
reduce the spread of the virus.

\hypertarget{rate-of-testing-compared-to-target}{%
\subsubsection{Rate of testing compared to
target}\label{rate-of-testing-compared-to-target}}

\hypertarget{states-are-ordered-by-current-testing-shortfall}{%
\paragraph{States are ordered by current testing
shortfall}\label{states-are-ordered-by-current-testing-shortfall}}

Mississippi

Miss.

0 100\% of target 15 -\/-\textgreater{}

May 3

Aug. 1

0 100\% of target 15 -\/-\textgreater{}

May 3

Aug. 1

Alabama

Ala.

17 -\/-\textgreater{}

17 -\/-\textgreater{}

Arizona

Ariz.

18 -\/-\textgreater{}

18 -\/-\textgreater{}

Georgia

Ga.

21 -\/-\textgreater{}

21 -\/-\textgreater{}

Florida

Fla.

23 -\/-\textgreater{}

23 -\/-\textgreater{}

Missouri

Mo.

23 -\/-\textgreater{}

23 -\/-\textgreater{}

Arkansas

Ark.

24 -\/-\textgreater{}

24 -\/-\textgreater{}

Idaho

Idaho

26 -\/-\textgreater{}

26 -\/-\textgreater{}

Kansas

Kan.

27 -\/-\textgreater{}

27 -\/-\textgreater{}

South Carolina

S.C.

27 -\/-\textgreater{}

27 -\/-\textgreater{}

Nevada

Nev.

29 -\/-\textgreater{}

29 -\/-\textgreater{}

Louisiana

La.

29 -\/-\textgreater{}

29 -\/-\textgreater{}

Tennessee

Tenn.

33 -\/-\textgreater{}

33 -\/-\textgreater{}

Texas

Texas

34 -\/-\textgreater{}

34 -\/-\textgreater{}

Iowa

Iowa

34 -\/-\textgreater{}

34 -\/-\textgreater{}

Oklahoma

Okla.

35 -\/-\textgreater{}

35 -\/-\textgreater{}

Nebraska

Neb.

37 -\/-\textgreater{}

37 -\/-\textgreater{}

Utah

Utah

38 -\/-\textgreater{}

38 -\/-\textgreater{}

Wisconsin

Wis.

39 -\/-\textgreater{}

39 -\/-\textgreater{}

Colorado

Colo.

39 -\/-\textgreater{}

39 -\/-\textgreater{}

North Dakota

N.D.

42 -\/-\textgreater{}

42 -\/-\textgreater{}

Kentucky

Ky.

47 -\/-\textgreater{}

47 -\/-\textgreater{}

South Dakota

S.D.

51 -\/-\textgreater{}

51 -\/-\textgreater{}

North Carolina

N.C.

52 -\/-\textgreater{}

52 -\/-\textgreater{}

California

Calif.

52 -\/-\textgreater{}

52 -\/-\textgreater{}

Washington

Wash.

52 -\/-\textgreater{}

52 -\/-\textgreater{}

Minnesota

Minn.

54 -\/-\textgreater{}

54 -\/-\textgreater{}

Maryland

Md.

55 -\/-\textgreater{}

55 -\/-\textgreater{}

Pennsylvania

Pa.

57 -\/-\textgreater{}

57 -\/-\textgreater{}

Indiana

Ind.

59 -\/-\textgreater{}

59 -\/-\textgreater{}

Virginia

Va.

60 -\/-\textgreater{}

60 -\/-\textgreater{}

Rhode Island

R.I.

60 -\/-\textgreater{}

60 -\/-\textgreater{}

Oregon

Ore.

62 -\/-\textgreater{}

62 -\/-\textgreater{}

Delaware

Del.

64 -\/-\textgreater{}

64 -\/-\textgreater{}

Ohio

Ohio

65 -\/-\textgreater{}

65 -\/-\textgreater{}

Montana

Mont.

69 -\/-\textgreater{}

69 -\/-\textgreater{}

Illinois

Ill.

73 -\/-\textgreater{}

73 -\/-\textgreater{}

\hypertarget{where-testing-is-above-or-near-recommended-levels}{%
\subsection{Where testing is above or near recommended
levels}\label{where-testing-is-above-or-near-recommended-levels}}

Over time, some states have reached the minimum testing target, and a
few have exceeded it.

\hypertarget{rate-of-testing-compared-to-target-1}{%
\subsubsection{Rate of testing compared to
target}\label{rate-of-testing-compared-to-target-1}}

\hypertarget{states-are-ordered-by-current-testing-levels}{%
\paragraph{States are ordered by current testing
levels}\label{states-are-ordered-by-current-testing-levels}}

Maine

Maine

0 100\% of target 336 -\/-\textgreater{}

May 3

Aug. 1

0 100\% of target 336 -\/-\textgreater{}

May 3

Aug. 1

Connecticut

Conn.

301 -\/-\textgreater{}

301 -\/-\textgreater{}

New York

N.Y.

279 -\/-\textgreater{}

279 -\/-\textgreater{}

Michigan

Mich.

215 -\/-\textgreater{}

215 -\/-\textgreater{}

New Jersey

N.J.

174 -\/-\textgreater{}

174 -\/-\textgreater{}

Alaska

Alaska

143 -\/-\textgreater{}

143 -\/-\textgreater{}

Washington, D.C.

D.C.

128 -\/-\textgreater{}

128 -\/-\textgreater{}

West Virginia

W.Va.

122 -\/-\textgreater{}

122 -\/-\textgreater{}

Hawaii

Hawaii

119 -\/-\textgreater{}

119 -\/-\textgreater{}

Massachusetts

Mass.

112 -\/-\textgreater{}

112 -\/-\textgreater{}

New Hampshire

N.H.

90 -\/-\textgreater{}

90 -\/-\textgreater{}

New Mexico

N.M.

88 -\/-\textgreater{}

88 -\/-\textgreater{}

Wyoming

Wyo.

82 -\/-\textgreater{}

82 -\/-\textgreater{}

Note: States with fewer than 2,000 total cases are not shown.

\hypertarget{tracking-the-coronavirus}{%
\subsection{Tracking the Coronavirus}\label{tracking-the-coronavirus}}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes.com/interactive/2020/world/coronavirus-maps.html}{World}
\item
  \href{https://www.nytimes.com/interactive/2020/04/21/world/coronavirus-missing-deaths.html}{World
  Deaths}
\item
  \href{https://www.nytimes.com/interactive/2020/04/23/upshot/five-ways-to-monitor-coronavirus-outbreak-us.html}{U.S.
  Cities}
\item
  \href{https://www.nytimes.com/interactive/2020/05/05/us/coronavirus-death-toll-us.html}{U.S.
  Deaths}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-testing.html}{Testing}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-nursing-homes.html}{Nursing
  homes}
\item
  \href{https://www.nytimes.com/interactive/2020/nyregion/new-york-city-coronavirus-cases.html}{New
  York City}
\item
  \href{https://www.nytimes.com/interactive/2020/us/states-reopen-map-coronavirus.html}{Reopening}
\item
  \href{https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html}{Vaccines}
\end{itemize}

Countries

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes.com/interactive/2020/world/americas/brazil-coronavirus-cases.html}{Brazil}
\item
  \href{https://www.nytimes.com/interactive/2020/world/canada/canada-coronavirus-cases.html}{Canada}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/france-coronavirus-cases.html}{France}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/germany-coronavirus-cases.html}{Germany}
\item
  \href{https://www.nytimes.com/interactive/2020/world/asia/india-coronavirus-cases.html}{India}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/italy-coronavirus-cases.html}{Italy}
\item
  \href{https://www.nytimes.com/interactive/2020/world/americas/mexico-coronavirus-cases.html}{Mexico}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/spain-coronavirus-cases.html}{Spain}
\item
  \href{https://www.nytimes.com/interactive/2020/world/europe/united-kingdom-coronavirus-cases.html}{U.K.}
\item
  \href{https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html}{United
  States}
\end{itemize}

State by state

\begin{itemize}
\tightlist
\item
  \href{https://www.nytimes.com/interactive/2020/us/alabama-coronavirus-cases.html}{Alabama}
\item
  \href{https://www.nytimes.com/interactive/2020/us/alaska-coronavirus-cases.html}{Alaska}
\item
  \href{https://www.nytimes.com/interactive/2020/us/arizona-coronavirus-cases.html}{Arizona}
\item
  \href{https://www.nytimes.com/interactive/2020/us/arkansas-coronavirus-cases.html}{Arkansas}
\item
  \href{https://www.nytimes.com/interactive/2020/us/california-coronavirus-cases.html}{California}
\item
  \href{https://www.nytimes.com/interactive/2020/us/colorado-coronavirus-cases.html}{Colorado}
\item
  \href{https://www.nytimes.com/interactive/2020/us/connecticut-coronavirus-cases.html}{Connecticut}
\item
  \href{https://www.nytimes.com/interactive/2020/us/delaware-coronavirus-cases.html}{Delaware}
\item
  \href{https://www.nytimes.com/interactive/2020/us/florida-coronavirus-cases.html}{Florida}
\item
  \href{https://www.nytimes.com/interactive/2020/us/georgia-coronavirus-cases.html}{Georgia}
\item
  \href{https://www.nytimes.com/interactive/2020/us/hawaii-coronavirus-cases.html}{Hawaii}
\item
  \href{https://www.nytimes.com/interactive/2020/us/idaho-coronavirus-cases.html}{Idaho}
\item
  \href{https://www.nytimes.com/interactive/2020/us/illinois-coronavirus-cases.html}{Illinois}
\item
  \href{https://www.nytimes.com/interactive/2020/us/indiana-coronavirus-cases.html}{Indiana}
\item
  \href{https://www.nytimes.com/interactive/2020/us/iowa-coronavirus-cases.html}{Iowa}
\item
  \href{https://www.nytimes.com/interactive/2020/us/kansas-coronavirus-cases.html}{Kansas}
\item
  \href{https://www.nytimes.com/interactive/2020/us/kentucky-coronavirus-cases.html}{Kentucky}
\item
  \href{https://www.nytimes.com/interactive/2020/us/louisiana-coronavirus-cases.html}{Louisiana}
\item
  \href{https://www.nytimes.com/interactive/2020/us/maine-coronavirus-cases.html}{Maine}
\item
  \href{https://www.nytimes.com/interactive/2020/us/maryland-coronavirus-cases.html}{Maryland}
\item
  \href{https://www.nytimes.com/interactive/2020/us/massachusetts-coronavirus-cases.html}{Massachusetts}
\item
  \href{https://www.nytimes.com/interactive/2020/us/michigan-coronavirus-cases.html}{Michigan}
\item
  \href{https://www.nytimes.com/interactive/2020/us/minnesota-coronavirus-cases.html}{Minnesota}
\item
  \href{https://www.nytimes.com/interactive/2020/us/mississippi-coronavirus-cases.html}{Mississippi}
\item
  \href{https://www.nytimes.com/interactive/2020/us/missouri-coronavirus-cases.html}{Missouri}
\item
  \href{https://www.nytimes.com/interactive/2020/us/montana-coronavirus-cases.html}{Montana}
\item
  \href{https://www.nytimes.com/interactive/2020/us/nebraska-coronavirus-cases.html}{Nebraska}
\item
  \href{https://www.nytimes.com/interactive/2020/us/nevada-coronavirus-cases.html}{Nevada}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-hampshire-coronavirus-cases.html}{New
  Hampshire}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-jersey-coronavirus-cases.html}{New
  Jersey}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-mexico-coronavirus-cases.html}{New
  Mexico}
\item
  \href{https://www.nytimes.com/interactive/2020/us/new-york-coronavirus-cases.html}{New
  York}
\item
  \href{https://www.nytimes.com/interactive/2020/us/north-carolina-coronavirus-cases.html}{North
  Carolina}
\item
  \href{https://www.nytimes.com/interactive/2020/us/north-dakota-coronavirus-cases.html}{North
  Dakota}
\item
  \href{https://www.nytimes.com/interactive/2020/us/ohio-coronavirus-cases.html}{Ohio}
\item
  \href{https://www.nytimes.com/interactive/2020/us/oklahoma-coronavirus-cases.html}{Oklahoma}
\item
  \href{https://www.nytimes.com/interactive/2020/us/oregon-coronavirus-cases.html}{Oregon}
\item
  \href{https://www.nytimes.com/interactive/2020/us/pennsylvania-coronavirus-cases.html}{Pennsylvania}
\item
  \href{https://www.nytimes.com/interactive/2020/us/puerto-rico-coronavirus-cases.html}{Puerto
  Rico}
\item
  \href{https://www.nytimes.com/interactive/2020/us/rhode-island-coronavirus-cases.html}{Rhode
  Island}
\item
  \href{https://www.nytimes.com/interactive/2020/us/south-carolina-coronavirus-cases.html}{South
  Carolina}
\item
  \href{https://www.nytimes.com/interactive/2020/us/south-dakota-coronavirus-cases.html}{South
  Dakota}
\item
  \href{https://www.nytimes.com/interactive/2020/us/tennessee-coronavirus-cases.html}{Tennessee}
\item
  \href{https://www.nytimes.com/interactive/2020/us/texas-coronavirus-cases.html}{Texas}
\item
  \href{https://www.nytimes.com/interactive/2020/us/utah-coronavirus-cases.html}{Utah}
\item
  \href{https://www.nytimes.com/interactive/2020/us/vermont-coronavirus-cases.html}{Vermont}
\item
  \href{https://www.nytimes.com/interactive/2020/us/virginia-coronavirus-cases.html}{Virginia}
\item
  \href{https://www.nytimes.com/interactive/2020/us/washington-coronavirus-cases.html}{Washington}
\item
  \href{https://www.nytimes.com/interactive/2020/us/washington-dc-coronavirus-cases.html}{Washington,
  D.C.}
\item
  \href{https://www.nytimes.com/interactive/2020/us/west-virginia-coronavirus-cases.html}{West
  Virginia}
\item
  \href{https://www.nytimes.com/interactive/2020/us/wisconsin-coronavirus-cases.html}{Wisconsin}
\item
  \href{https://www.nytimes.com/interactive/2020/us/wyoming-coronavirus-cases.html}{Wyoming}
\end{itemize}

Sources: \href{https://covidtracking.com/}{The Covid Tracking Project};
the
\href{https://globalepidemics.org/july-6-2020-state-testing-targets/}{Harvard
Global Health Institute};
\href{https://github.com/youyanggu/covid19_projections}{Youyang Gu's
Cov}\href{https://github.com/youyanggu/covid19_projections}{id}\href{https://github.com/youyanggu/covid19_projections}{-19
Forecasts}; and the Centers for Disease Control and Prevention

Note: Testing targets are calculated daily using the methodology
\href{https://globalepidemics.org/july-6-2020-state-testing-targets/}{developed}
by the Harvard Global Health Institute (exact figures may differ because
of recent changes in underlying projections). Two-week rolling averages
are calculated using the most recent 14 days for which data is
available. Some states may include non-diagnostic tests, like antibody
tests, in the data they release, which can affect reported testing
rates. Some states don't consistently release data on current
hospitalizations (see more information about missing data
\href{https://covidtracking.com/data}{here}.) Case data is from the
Covid Tracking Project for consistency with daily testing data.

Read 197 Comments

\begin{itemize}
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
