Sections

SEARCH

\protect\hyperlink{site-content}{Skip to
content}\protect\hyperlink{site-index}{Skip to site index}

\href{https://www.nytimes.com/section/books/review}{Book Review}

\href{https://myaccount.nytimes.com/auth/login?response_type=cookie\&client_id=vi}{}

\href{https://www.nytimes.com/section/todayspaper}{Today's Paper}

\href{/section/books/review}{Book Review}\textbar{}How to Listen to the
Book Review Podcast

\url{https://nyti.ms/2n9fW4W}

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Advertisement

\protect\hyperlink{after-top}{Continue reading the main story}

Supported by

\protect\hyperlink{after-sponsor}{Continue reading the main story}

\hypertarget{how-to-listen-to-the-book-review-podcast}{%
\section{How to Listen to the Book Review
Podcast}\label{how-to-listen-to-the-book-review-podcast}}

Aug. 3, 2018

\begin{itemize}
\item
\item
\item
\item
\item
\end{itemize}

Each week on
\href{https://www.nytimes.com/column/book-review-podcast}{The New York
Times Book Review's podcast}, the Book Review's editor, Pamela Paul,
speaks with authors, critics and Times reporters about the latest
releases and news in the literary world. Here's how to listen:

From a desktop or laptop, you can listen by pressing play on the button
at the top of each podcast article.

Or if you're on a mobile device, the instructions below will help you
find and subscribe to the series.

\textbf{1. Open your podcast app.} It's a pre-loaded app called
``Podcasts'' with a purple icon.

\textbf{2. Search for the series.} Tap on the ``search'' magnifying
glass icon at the bottom of the screen, type in ``Inside The New York
Times Book Review'' and select it from the list of results.

\textbf{3. Subscribe.} Once on the series page, tap on the ``subscribe''
button to have new episodes sent to your phone free. You may want to
adjust your notifications to be alerted when a new episode arrives.

\textbf{4. Or just sample.} If you would rather listen to an episode or
two before deciding to subscribe, just tap on the episode title from the
list on the series page. If you have an internet connection, you'll be
able to stream the episode.

On your Android phone or tablet:

\textbf{1. Open your podcast app.} It's a pre-loaded app called ``Play
Music'' with an orange-and-yellow icon.

\textbf{2. Search for the series.} Click on the magnifying glass icon at
the top of the screen, search for the name of the series, and select it
from the list of results. You might have to scroll down to find the
``Podcasts'' search results.

\textbf{3. Subscribe.} Once on the series page, click on the word
``subscribe'' to have new episodes sent to your phone for free.

\textbf{4. Or just sample.} If you would rather listen to an episode or
two before deciding to subscribe, just click on the episode title from
the list on the series page. If you have an internet connection, you'll
be able to stream the episode.

Advertisement

\protect\hyperlink{after-bottom}{Continue reading the main story}

\hypertarget{site-index}{%
\subsection{Site Index}\label{site-index}}

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014792127-Copyright-notice}{©~2020~The
  New York Times Company}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \href{https://www.nytco.com/}{NYTCo}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{http://www.tbrandstudio.com/}{T Brand Studio}
\item
  \href{https://www.nytimes.com/privacy/cookie-policy\#how-do-i-manage-trackers}{Your
  Ad Choices}
\item
  \href{https://www.nytimes.com/privacy}{Privacy}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes.com/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\item
  \href{https://spiderbites.nytimes.com}{Site Map}
\item
  \href{https://help.nytimes.com/hc/en-us}{Help}
\item
  \href{https://www.nytimes.com/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
