 **NYTimes.com no longer supports Internet Explorer 9 or earlier. Please
upgrade your browser.
\href{http://www.nytimes3xbfgragh.onion/content/help/site/ie9-support.html}{LEARN
MORE »}

**Sections

**Home

**Search

\hypertarget{the-new-york-times}{%
\subsection{\texorpdfstring{\href{http://www.nytimes3xbfgragh.onion/}{The
New York Times}}{The New York Times}}\label{the-new-york-times}}

 \href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}
\textbar{}What Are Sanctuary Cities?

Log In

**0

**Settings

**Close search

\hypertarget{site-search-navigation}{%
\subsection{Site Search Navigation}\label{site-search-navigation}}

Search NYTimes.com

**Clear this text input

Go

\url{https://nyti.ms/2ci8Fco}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Loading...
\end{enumerate}

See next articles

See previous articles

\hypertarget{site-navigation}{%
\subsection{Site Navigation}\label{site-navigation}}

\hypertarget{site-mobile-navigation}{%
\subsection{Site Mobile Navigation}\label{site-mobile-navigation}}

Advertisement

\hypertarget{-us-}{%
\subsection{\texorpdfstring{
\href{https://www.nytimes3xbfgragh.onion/section/us}{U.S.}
}{ U.S. }}\label{-us-}}

\hypertarget{what-are-sanctuary-cities}{%
\section{What Are Sanctuary Cities?}\label{what-are-sanctuary-cities}}

Five days after taking office, President Trump
\href{https://www.nytimes3xbfgragh.onion/2017/01/25/nyregion/outraged-mayors-vow-to-defy-trumps-immigration-order.html}{signed
an executive order} to block federal funding to ``sanctuary cities,'' a
term that has been used to generally describe places that limit how
local law enforcement can cooperate with federal immigration agents.

It was not immediately clear which jurisdictions would be subject to
\href{https://www.whitehouse.gov/the-press-office/2017/01/25/presidential-executive-order-enhancing-public-safety-interior-united}{the
order}, said Lena Graber, a special projects lawyer at the
\href{https://www.ilrc.org/}{Immigrant Legal Resource Center}.

The order targets jurisdictions that hinder communication with the
Department of Homeland Security about a person's immigration status, Ms.
Graber said. She did not think the sanctuary policies now in place in
cities across the country were in violation of the order.

\emph{\textbf{At least five states}} have laws that limit how much the
local police can cooperate with federal immigration agents.

Vermont

Oregon

Connecticut

Rhode

Island

California

Vermont

Oregon

Connecticut

Rhode

Island

California

VT.

ORE.

CONN.

R.I.

CALIF.

The New York Times

The maps shown here are based on data collected by the Immigrant Legal
Resource Center, specifically looking at jurisdictions that limit how
much the local police cooperate with requests from federal authorities
to hold immigrants in detention.

The center found \emph{\textbf{at least 633 counties}} with these
policies.

WASH.

N.D.

VT.

MINN.

ORE.

N.Y.

S.D.

MASS.

WYO.

MICH.

WIS.

IOWA

PA.

NEB.

N.J.

OHIO

NEV.

IND.

ILL.

MD.

COLO.

CALIF.

VA.

KAN.

KY.

N.M.

GA.

LA.

FLA.

WASH.

VT.

N.D.

ORE.

MINN.

N.Y.

S.D.

WIS.

MICH.

WYO.

MASS.

IOWA

PA.

N.J.

NEB.

OHIO

NEV.

ILL.

IND.

COLO.

MD.

KAN.

VA.

CALIF.

KY.

N.M.

GA.

LA.

FLA.

WA

VT

ND

MN

OR

MA

NY

SD

WI

MI

WY

PA

IA

NJ

OH

NE

NV

IL

IN

MD

CO

VA

KS

KY

CA

NM

GA

LA

FL

The New York Times

Policies limiting cooperation with immigration detainers are typically
in place at the county and state level, Ms. Graber said. In cities,
sanctuary policies often mean local officials do not ask about a
person's immigration status, but there is no universal definition for a
sanctuary city.

Compiling a comprehensive list of cities that could be considered
sanctuaries is challenging. In some places, officials have publicly
declared their city to be a sanctuary, but the city may not have actual
policies in place.

County policies, Ms. Graber said, are actually the most relevant in the
debate over immigration enforcement.

Mr. Trump and many Republicans say sanctuary cities allow criminals to
go free, leading to crimes that could have been avoided if the
immigrants had been deported.

Many local law enforcement officials favor the policies, saying they do
not want the job of enforcing federal immigration laws. They say they
rely on immigrants in their communities to come forward to report
crimes.

None of the protective policies prevent the police from pursuing
immigrants who commit crimes.

Source: Data for maps from the Immigrant Legal Resource Center

\hypertarget{more-on-nytimescom}{%
\subsection{More on NYTimes.com}\label{more-on-nytimescom}}

Advertisement

\hypertarget{site-information-navigation}{%
\subsection{Site Information
Navigation}\label{site-information-navigation}}

\begin{itemize}
\tightlist
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014792127-Copyright-notice}{©
  2020 The New York Times Company}
\item
  \href{https://www.nytimes3xbfgragh.onion}{Home}
\item
  \href{https://www.nytimes3xbfgragh.onion/search/}{Search}
\item
  Accessibility concerns? Email us at
  \href{mailto:accessibility@NYTimes.com}{\nolinkurl{accessibility@NYTimes.com}}.
  We would love to hear from you.
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us}{Contact
  Us}
\item
  \href{https://www.nytco.com/careers/}{Work with us}
\item
  \href{https://nytmediakit.com/}{Advertise}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy\#pp}{Your
  Ad Choices}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014892108-Privacy-policy}{Privacy}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893428-Terms-of-service}{Terms
  of Service}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115014893968-Terms-of-sale}{Terms
  of Sale}
\end{itemize}

\hypertarget{site-information-navigation-1}{%
\subsection{Site Information
Navigation}\label{site-information-navigation-1}}

\begin{itemize}
\tightlist
\item
  \href{https://spiderbites.nytimes3xbfgragh.onion}{Site Map}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us}{Help}
\item
  \href{https://help.nytimes3xbfgragh.onion/hc/en-us/articles/115015385887-Contact-Us?redir=myacc}{Site
  Feedback}
\item
  \href{https://www.nytimes3xbfgragh.onion/subscription?campaignId=37WXW}{Subscriptions}
\end{itemize}
